\chapter{City Watch Novels}


\section{Guards! Guards!}


\subsection{}
\subsubsection{The library of the Unseen University faces is invaded by a thief}
\Gls{Vimes}, Captain of the City Watch, lies drunk in a gutter, as the \Gls{Libra} sleeps soundly
within the library of the Unseen University at Ankh-Morpork. An intruder sneaks into the library,
and steals a powerful magical tome, to take it to the meetup of a secret society in a dark alley
somewhere in the city.

\subsubsection{\Gls{BFinger} hands over the stolen book to the \Gls{SGM}}
\Gls{BFinger} supplies an elaborate password to gain entry into the dark chamber used by his group
for their meetup. He brings the stolen book to the \Gls{SGM}, clothed in the formal black robes of
the secret society, and watches the old man start their session. The \Gls{SGM} thinks about how the
other secret societies had all poached the talented and ambitious acolytes, with only the leftovers
in his own group.

\subsubsection{The \Gls{SGM} seeds the idea of a scion returning to Ankh-Morpork, to claim its
    throne}
\Gls{BWatch} and \Gls{BPlast} interrupt the \Gls{SGM}'s speech to talk about the usual tropes
surrounding a lost scion, who returns to the kingdom in its time of greatest need, and takes the
throne after proving his lineage and saving the city. Eventually, the argument veers in the
direction of the king proving his identity by vanquishing a worthy foe, like a dragon.

\subsubsection{The \Gls{SGM} tries to get his acolytes to join him in summoning a dragon}
The \Gls{SGM} is delighted to see his acolytes arrive at the dragon hypothesis, and lets slip the
fact that the stolen tome contains instructions to summon actual dragons from their hidden
dimension. \Gls{BWatch} warns the \Gls{SGM} about the wizards criminalizing the use of magic by
anyone outside their University, and is quickly shot down by \Gls{BPlast}, who resents them for
their white-collar lives.

\subsubsection{The \Gls{SGM} convinces his secret society to participate in the summoning}
The \Gls{SGM} hints at the fact that whoever summons the dragon has full control of it, as the
acolytes come to terms with the idea of using the magic spells contained in the book. Meanwhile,
a young boy from the mountains, named \Gls{Carrot}, is headed to Ankh-Morpork, with his ancestral
sword strapped to his back.

\subsubsection{\Gls{Vimes} recalls the funeral of \Gls{Gaskin}}
\Gls{Vimes} wakes up from his drunken stupor, to recall the funeral of his colleague \Gls{Gaskin}
earlier in the day, and faintly recalls the need for a replacement. \Gls{Carrot} recalls his father
breaking the news to him that he was adopted, and in truth was a human boy found wandering in the
forest, next to a trade caravan set aflame by bandits.

\subsubsection{\Gls{Carrot} recalls his father's decision to send him to the city}
\Gls{Carrot}'s father talks to his old friend \Gls{Varneshi}, who trades in precious metals with the
dwarves at their mines outside Ankh-Morpork, and is convinced to let his son mingle with human
society. \Gls{Varneshi} had given him a copy of the Ankh-Morpork laws, and told him that he was
expected to know it cover to cover, in order to qualify for a job as important as the City Watch.

\subsubsection{\Gls{Carrot} arrives at the city gates of Ankh-Morpork}
\Gls{Carrot} talks to a guard snoozing at his post on the city gates, and asks to see the
\Gls{Patri}. The guard instead points him to the tavern frequented by \Gls{Vimes}, and is appalled
to see someone volunteer for a punishment position like the Night Watch. Meanwhile, the \Gls{SGM}
convinces his acolytes to concentrate on the idea of a dragon, as he utters the single sentence
in the book meant to summon the creature.

\subsubsection{The dragon of Ankh-Morpork is successfully summoned for a few seconds}
\Gls{Death} comes in person, to collect a petty thief who runs into the dragon of Ankh-Morpork and
gets burned by its flames. A while later, the \Gls{SGM} wakes up from his spirit-walk into the
dragon's mind, as his acolytes argue about sensing the dragon's aura. The \Gls{SGM} notices the
magical trinkets gathered by his disciples crumble to dust, and explains to them that more magic
will be needed to make the dragon last longer.

\subsubsection{\Gls{Carrot} decides to confront the Thieves' Guild}
\Gls{Carrot} writes a letter to his father, informing him of how immoral the city is, in comparison
to \Gls{Varneshi}'s recollection of his great-grandfather's tales. He tells his father that the
Thieves' Guild is simply allowed to exist, and that he is going to try and destroy it to add to his
accomplishments as a City Guardsman.

\subsubsection{\Gls{Vetina} chastises the leader of the Thieves' Guild}
The leader of the Thieves' Guild complains to \Gls{Vetina}, the patrician of Ankh-Morpork, that a
lowly guardsman dragged him through the streets in handcuffs, and demands an apology from the
administration. \Gls{Vetina} in turn asks him why he is targeting unimportant magical trinkets
across the city, and reminds him that unlicensed theives needed to be reined in at all costs.

\subsubsection{\Gls{Vetina} thinks about taming the Thieves' Guild}
\Gls{Vetina} recalls his negotiation with the Thieves' Guild, legalizing them and converting them
into an informal insurance bureau, in exchange for the defunding of the City Watch. Once the
higher-ups in the guild had gotten a taste of social status and legitimacy, they had quickly
cracked down on any thieves taking more than the negotiated annual budgets.

\subsubsection{\Gls{Vimes} is berated by \Gls{LWonse} for letting for the commotion at the Thieves'
    Guild}
\Gls{Vimes}, still lost in a drunken haze, walks into \Gls{LWonse}'s office, and listens to the
complaint about the Thieves' Guild. He dimly recalls the tall young man who had spoken to him in the
tavern at noon, as \Gls{LWonse} reminds him about the letter written by a dwarf from the Ramtops
seeking employment for his son in the City Watch.

\subsubsection{\Gls{Vimes} reaches the Watch House to prepare for the night shift}
\Gls{Vimes} salutes \Gls{LWonse} when asked to chastise the new recruit, and limps back to the
City Watch headquarters, now a rundown ruin inhabited by rats and owls more than people. He thinks
about his two existing colleagues, corporal \Gls{Nobby} and lieutenant \Gls{Colon}, as he prepares
to start his night shift with a stiff drink and his work uniform.

\subsubsection{\Gls{Vimes} sets off in search of \Gls{Nobby}}
\Gls{Vimes} is alarmed by \Gls{Colon}'s idea of sending the newcomer out into the city with
\Gls{Nobby} showing him the ropes, and sets out to find them. Meanwhile, \Gls{BWatch} unscrews the
magical signboard used by the tavern next to the Watch House to fuel the dragon summoning ritual at
the secret society's hideout.

\subsubsection{\Gls{Nobby} tries to learn about \Gls{Carrot}'s motivations in joining the Watch}
\Gls{Nobby}, a world-weary man addicted to his cigarettes, tries to wring the truth out from
\Gls{Carrot} about why he wished to join the City Watch. He is amused by \Gls{Carrot}'s naivete,
and his belief in the rule of law as it existed before \Gls{Vetina}'s reforms. They come across a
dwarf bar, and hear sounds of a fight brewing inside. \Gls{Carrot} enters the bar, affronted by the
idea of dwarfs drinking, as \Gls{Nobby} tries to talk him out of interfering.

\subsubsection{\Gls{Carrot} and \Gls{Nobby} walk into the Mended Drum}
\Gls{Carrot} gives the dwarfs a speech about their mothers missing them from the old lands, and of
how their behaviour was shaming all of dwarf-kind. The fighting stops abruptly, with many dwarfs
moved to tears, as \Gls{Nobby} pulls \Gls{Carrot} out of the tavern, worried for his life. They go
next to the Mended Drum, where \Gls{Nobby} greets the troll bodyguard \Gls{Detri}, as he gets ready
for another night of drinking.

\subsubsection{\Gls{Carrot} gets into a fight with the regulars of the Mended Drum}
\Gls{Carrot} reads out some criminal charges to the owner of the Mended Drum, triggering a bar-fight
as the tavern regulars slowly realize what is happening to their favourite haunt. \Gls{Nobby}
crawls out of the bar, to see \Gls{Vimes} and \Gls{Colon} stumbling in, and advises them not to
bother saving their comrade. They carry \Gls{Carrot} upstairs into the inn as he collapses from
exhaustion, having beaten up every single denizen in the tavern.

\subsubsection{\Gls{Vimes} and his men accidentally end up in the Shades}
\Gls{Vimes} wonders how they will face the wrath of the assorted barbarians and mercenary cutthorats
once they woke up from \Gls{Carrot}'s pummeling, as they drag the recruit up the stairs to the
empty rooms. A while later, as they walk through the criminal district of the city, called the
Shades, \Gls{Colon} realizes all of a sudden that they might have taken a wrong turn in the dark,
and condemned themselves to a swift death by garroting in the dark alleyways of the Shades.

\subsubsection{\Gls{Vimes} comes across the aftermath of the dragon's flame-breath}
The thugs shadowing the Watch are burnt to a crisp by the \Gls{SGM}'s dragon, with \Gls{Vimes}
arriving too late to witness the dragon itself. He is horrified by the smoking remains of the gang
on the opposite wall, whose stones are still red-hot from the flames. At their hideout, the
\Gls{SGM} baits his acolytes into renewing their oath of secrecy, spurred by the idea of having a
dragon to heed their commands, if they manage to find enough magic fuel.

\subsubsection{\Gls{Vetina} chooses not to take the threat of the dragon seriously}
\Gls{Vetina} inspects the site of the thugs being incinerated, and refuses to take heed of the
footprints \Gls{Vimes} points out, as he dismisses the incident as gang warfare spilling over into
the open. \Gls{Colon} distracts \Gls{Carrot} at the last moment, as he is about to read out criminal
charges to the \Gls{Patri} himself for violation of carriage wheel laws, with \Gls{Vimes} breathing
a sigh of relief.

\subsubsection{\Gls{Vetina} issues orders to \Gls{LWonse} in his chambers}
The \Gls{Libra}, having witnessed the incineration first-hand from the safety of the rooftops,
hurries back to the library, to find the book about dragons missing. Meanwhile, \Gls{Vetina} asks
his assistant \Gls{LWonse} to demolish the wall holding the ceramic silhouettes of the poor men
burnt by the dragon, and asks someone more competent than the City Watch to be put to work tracking
down possible leads.

\subsubsection{\Gls{Vimes} gets to work investigating the dragon}
\Gls{Vimes} gets his two senior men to go out into the town in plainclothes, and try to gauge the
rumors going around regarding the accidents from the past night. He also thinks about the plaster
cast he had made of the dragon's footprints kept hidden in his office, in direct contravention of
the \Gls{Patri}'s orders. \Gls{Carrot} is delighted to be left in charge at the Watch House, free to
read his rule-book.

\subsubsection{\Gls{Vimes} visits Lady \Gls{Ramkin}, hoping to quiz her about dragons}
\Gls{Vimes} heads to Lady \Gls{Ramkin}'s manor in the aristocratic district of Ankh-Morpork, hoping
to find out something useful about dragons. He recalls her business of breeding miniature
swamp-dragons, kept as pets by the city's nobles, and notices the manor's outside wall crumbling.
Eventually, he finds a side gate that looks to be well-maintained, and is alarmed to hear someone
talk about dragons mating.

\subsection{}
\subsubsection{\Gls{Carrot} accompanies the \Gls{Libra} out into the city}
The \Gls{Libra} manages to persuade \Gls{Carrot} into following him out into the city, to track
down a lead on some heinous crime. Meanwhile, the \Gls{SGM} puts his acolytes to work channelling
their jealousy and resentment to the summoning ritual. \Gls{Nobby} and \Gls{Colon} go out of a
tavern to relieve themselves, when they spot the dragon landing on a nearby rooftop.

\subsubsection{\Gls{Ramkin} insists on showing off her swamp dragon pens to \Gls{Vimes}}
At \Gls{Ramkin}'s manor, \Gls{Vimes} is starstruck by the portraits and banners showing her
ancestors, all barbarian warlords proficient in the martial arts. He asks her about the maximum
size of swamp dragons, and tries to absorb the information about their lifestyle and mating habits.
She takes him to her dragon pen, where he spots a dragon with wings too small for flight, and other
bad phenotypic characteristics for breeding.

\subsubsection{\Gls{Vimes} shows the dragon footprint to \Gls{Ramkin}}
\Gls{Vimes} shows the plaster cast of the talon-print to \Gls{Ramkin}, leading her to immediately
respond that it was a prank being played on him, given how noble dragons were extinct. Suddenly,
the dragons in the pen go silent and stare up at the ceiling, causing \Gls{Vimes} to be alarmed.

\subsubsection{\Gls{Ramkin} and \Gls{Vimes} witness the dragon take flight}
\Gls{Vimes} and \Gls{Ramkin} watch the dragon fly through the air, setting fire to some buildings
as it tests out the full potency of its flame-breath. He hurries off into the streets, intent on
finding its secret hideout, where it must rest during the day. Meanwhile, \Gls{Carrot} is led to the
missing book in the University Library, with the \Gls{Libra} using charades to help him guess the
book's title.

\subsubsection{\Gls{Vimes} and the soldiers regroup at the Watch House}
\Gls{Vimes} notices how specific the damage done by the dragon is, and takes note of the businesses
burned down in that night. Just as he returns to his office in the Watch House and prepares to get
drunk, the rest of his squad return with the \Gls{Libra}, all abuzz with talk of the dragon.
\Gls{Nobby} recounts the myths surrounding dragons and their hoard of gold, leading \Gls{Vimes} to
conclude that the entire city would be on the lookout for its secret hideout.

\subsubsection{The \Gls{SGM} reveals the next stage of his plan to the acolytes}
At the secret society's hideout, the \Gls{SGM} plans the next idea of propping up a fake king, who
might kill the dragon and cement his authority as the city's ruler. He thinks about the elaborate
preparations he had made to supply one of his dim-witted cousins with the arms and armour befitting
a king, and of how he was currently cooped up in a farmhouse outside the city.

\subsubsection{The \Gls{SGM} thinks about his endgame}
The \Gls{SGM} learns of one of the acolytes being injured in a crocodile-related accident, and
pitches in some money for the relief fund. He thinks about his own role as the advisor to the newly
crowned king, and of how the rabble in his secret society would be promptly put to death to cover up
the loose ends.

\subsubsection{\Gls{Vimes} receives the latest news from \Gls{Dibbl}}
Outside the Patrician's office, \Gls{Vimes} is amused to see the usual crowd of litigants, as well
as the accompanying hot-dog salesmen circulating through the crowds. He runs into \Gls{Dibbl}, who
shows him a special burn-treatment cream guaranteed to counter dragon's flame, as well as other
bounty hunting equipment. He points out \Gls{Vetina}'s bounty on the dragon's head, and the
resulting surge in armed men enlisting as dragon-hunters.

\subsubsection{\Gls{Vimes} sees some local heroes express their disinterest in hunting the dragon}
\Gls{Vimes} spots a few minor heroes struggling to read the bounty poster, and discussing how the
bounty was nowhere close to covering their operating costs. \Gls{Vimes} tells them that \Gls{Vetina}
has no daughter he can offer as a prize for the dragon's head, leading to them losing even more
interest in the bounty.

\subsubsection{\Gls{Vetina} learns about his bounty being too small to attract dragon-hunters}
\Gls{Vetina} is dismayed to hear the guild leaders demand an  increase in the bounty value, with the
Archchancellor of the Unseen University claiming that the dragon might simply have adapted to city
life. Later, as \Gls{LWonse} insists on the traditional reward of the ruler's daughter and half the
kingdom being the reward for a dragon-slayer, \Gls{Vetina} wonders if the dragon can be bribed to
go away.

\subsubsection{\Gls{Vimes} discusses some leads with the \Gls{Libra}}
\Gls{Vimes} goes to the library at daytime, and finds the \Gls{Libra} looking anxiously for updates.
He tells the \Gls{Libra} that the book thief must have been a wizard or student, who was a regular
at the library, since the books hadn't made a fuss out of his night-time visit. The \Gls{Libra}
tells him that this is part of the reason he did not bring the issue to the University Council, and
took it to the City Watch instead.

\subsubsection{\Gls{Vimes} watches the dragon burn down the Watch House}
\Gls{Vimes} spots the dragon perched on the Tower of Art, the centerpiece of Unseen University, as
it drops down to swoop over the city. Eventually it circles back to the Watch House, and burns the
ancient building to ashes. Bounty hunters all over the city gather on rooftops to try and fire
arrows at the dragon, only to find its armoured skin resistant to all of their feeble projectiles.

\subsubsection{\Gls{Vimes} is rescued by \Gls{Carrot} and nursed by \Gls{Ramkin}}
\Gls{Vimes} recovers in \Gls{Ramkin}'s bedroom, and learns that \Gls{Carrot} had grabbed him as he
leapt off the roof, just as the dragon incinerated their headquarters. She had hurried to the
burning ruins of the Watch House, insisting that \Gls{Vimes} be brought to her manor for treatment.
\Gls{Ramkin} arrives a while later, with some food, and ointment for his cracked ribs. She tells him
that about the notes she took the previous night about the dragon's dive and subsequent flight.

\subsubsection{\Gls{Vimes} helps \Gls{Ramkin} deal with a mob outside her manor}
\Gls{Vimes} wakes up a while later to hear a commotion downstairs as \Gls{Ramkin} fends off a
gathering mob, intent on culling her swamp dragons. The leader of the mob states that one of her
pets might be shape-shifting into the noble dragon terrorizing the city, just as \Gls{Vimes}
descends with a particularly nasty swamp dragon breathing small jets of flame at them.

\subsubsection{\Gls{Vimes} comes up with a plan to track down the dragon}
\Gls{Vimes} manages to get the mob to disperse, after \Gls{Ramkin} coerces them into donating to her
swamp dragon rescue fund on their way out. He looks at one of the deformed dragons in the pen, and
asks \Gls{Ramkin} if one dragon can follow the scent of another, potentially leading to the lair of
the noble dragon.

\subsubsection{\Gls{Ramkin} inspects the new City Watch}
\Gls{Ramkin} arrives with \Gls{Vimes} to the new headquarters of the City Watch, a refurbished
building owned by her distant relative. She is delighted to see the \Gls{Libra} standing at
attention next to the three soldiers of the City Watch, with \Gls{Nobby} informing \Gls{Vimes} that
the \Gls{Libra} is a temporary addition to their squad.

\subsubsection{The \Gls{SGM} corrals his acolytes for the next summmoning}
The \Gls{SGM} listens to his acolytes talk about their vigor being drained by the summoning ritual,
and tries to distract them with talk of the endgame. He tells them that the dragon will simply be
banished by his cousin's enchanted sword, with some smoke and mirrors being used to justify the
absence of dragon viscera after the confrontation.

\subsubsection{\Gls{Vimes} and the City Watch travel to the Shades}
\Gls{Colon} gets treated by \Gls{Ramkin} when he accidentally lets slip the word monkey, and drives
the \Gls{Libra} into a rage. The deformed swamp dragon that \Gls{Vimes} adopted, gets the name
\Gls{Errol}, after \Gls{Nobby} compares its face to one of his brothers. \Gls{Vimes} hopes that
\Gls{Errol} can sniff out the trail of the noble dragon, as they head to the wall in the Shades
district where the thugs had been incinerated.

\subsubsection{\Gls{Vimes} faces the noble dragon at his new headquarters}
At the Shades, \Gls{Vimes} notices the denizens busy hunting for the dragon-hoard, and finds
\Gls{Errol} uninterested in sniffing out the trail of the noble dragon. When they return to the
new Watch House, \Gls{Vimes} is petrified by the noble dragon perched on the roof, staring intently
at \Gls{Errol}, cradled in his arms. A while later, a whistle rings as if to taunt the noble
dragon, causing it to fly off in search of the challenger.

\subsection{}
\subsubsection{\Gls{Vimes} and his party reach the city square to witness the challenge}
At a nearby square, the hero with the glittering sword waits on his horse for the dragon, as
citizens throng the streets, eager to see him get incinerated by the dragon's flame-breath.
\Gls{Vimes} arrives with his squad and \Gls{Ramkin}, to find \Gls{Dibbl} already plying his trade
amongst the crowd, and catches snippets of people discussing a return to monarchy.

\subsubsection{\Gls{Vimes} finds it odd that the nothing remains of the noble dragon}
Back home the next morning, \Gls{Vimes} tries to shut out the royalists celebrating all over the
city streets, and tries to focus on the lack of any viscera when the dragon had been impaled by
the hero's shining sword. He recalls \Gls{Ramkin} telling him about the mess swamp dragons made when
they exploded spontaneously due to indigestion, and finds it odd that the noble dragon vanished in
a puff of smoke.

\subsubsection{\Gls{Vimes} suspects foul play in the appearance of the noble dragon, and the hero}
\Gls{Vimes} casts further doubt on the convenient appearance of a young man claiming to be the scion
of the long-lost royal bloodline, and recalls how \Gls{Vetina} was forced to give up his position
by the thronging masses. He tries once again to make sense of the noble dragon failing to breathe
fire at the crucial juncture when facing the hero, and its vanishing afterward.

\subsubsection{\Gls{Ramkin} notices her swamp dragons acting strange}
\Gls{Ramkin} recalls the impromptu celebration and feast thrown by \Gls{Vetina} to celebrate the
coronation of the new king, as she prepares to feed her swamp dragons. In their pen, she notices
them silently staring up at the ceiling, as if waiting for something momentous. Meanwhile,
\Gls{Carrot} learns that the old guardsman \Gls{Gaskin} died trying to chase some petty thieves, and
running so fast his heart gave out.

\subsubsection{\Gls{Vimes} spots a magical tornado forming over the city}
The \Gls{Libra} decides to ply out a long ball of string behind him, as he heads deep into the
Library's pocket dimensions in search of a way to find the contents of the missing book. At the
city square where the noble dragon had been vanquished, \Gls{Vimes} tries to look for clues, and is
alarmed when \Gls{Errol} looks up at the sky where a magical tornado starts to take shape.

\subsubsection{\Gls{Ramkin} and \Gls{Vimes} escape the city square where the dragon materializes}
\Gls{Ramkin} arrives in her carriage at the city square, just as \Gls{Vimes} realizes the magical
tendrils are searching for some life-force in the city. The two of them ride off with \Gls{Errol}
as the tendrils focus on drawing energy from the University Library, enabling the dragon to take a
corporeal form in the square. It relishes the raw magical power available to consume in the Library,
and sets out to find the feeble minds that had banished it earlier.

\subsubsection{\Gls{Ramkin} and \Gls{Vimes} face the noble dragon}
\Gls{Ramkin} foolishly tries to talk to the noble dragon, and is pinned down by one of its talons.
\Gls{Errol} instinctively tries to challenge the dragon, and is swatted aside, just in time for
\Gls{Vimes} to catch it as it falls off a roof. He then brings \Gls{Ramkin} to safety, and notices
the noble dragon sniff them for a moment before flying off into the city.

\subsubsection{\Gls{Errol} pursues the noble dragon using its sense of smell}
\Gls{Errol} jogs through the streets to the merchant district, in pursuit of the dragon flying
through the fog-shrouded skies of Ankh-Morpork. \Gls{Vimes} finds his men observing the decorations
go up for the coming coronation, and asks them to get on the carriage, as they continue to follow
\Gls{Errol}.

\subsubsection{The noble dragon wipes out the \Gls{SGM}'s hideout and all his acolytes}
At the secret society's hideout, \Gls{BWatch} tries to lead another ritual in the absence of the
\Gls{SGM}, who is busy with the coronation. The noble dragon incinerates the entire building, along
with all of the acolytes, just as they reassure themselves of the reward coming their way, now that
the pretender had been successfully raised to the throne of Ankh-Morpork.

\subsubsection{\Gls{Vimes} and his squad arrest \Gls{BFinger}}
\Gls{Vimes} and the squad happen to find \Gls{BFinger}, who was out getting food for the meeting of
the secret society. They see the guilt on his face as he finds the hideout a burning ruin, and
decide to apprehend him. \Gls{Colon} identifies him as a low ranking thief working odd jobs at the
university, and \Gls{Vimes} realizes he was probably the person who stole the tome.

\subsubsection{\Gls{Vimes} arrests \Gls{BFinger}, realizing he is close to unraveling the
    conspiracy}
\Gls{Vimes} spots another hooded figure come looking for the secret society's hideout, and tries to
apprehend the suspect. \Gls{Carrot} refuses to chase after the mysterious man, reminding \Gls{Vimes}
that he had been forbidden from running by \Gls{Colon}. \Gls{Vimes} decides to take the matter to
\Gls{Vetina}, but is stopped at the palace gates by the newly appointed palace guard.

\subsubsection{\Gls{Carrot} apprehends the two palace guards threatening \Gls{Vimes}}
\Gls{Carrot} charges the two palace guards blocking their way with resisting arrest, and threatening
to assault a city guardsman, as \Gls{Vimes} realizes there is no other way of getting through them.
\Gls{Carrot} easily subdues the two guards using his dwarven martial arts, as \Gls{Vimes} watches
on with amusement. Meanwhile, the \Gls{Libra} manages to navigate the pocket dimension of the
Library to arrive at the spot where the stolen book was kept, a week ago.

\subsubsection{\Gls{Vimes} fails to convince \Gls{LWonse} about the return of the dragon}
\Gls{Vimes} barges into \Gls{LWonse}'s office, and tries to tell him that the noble dragon is back,
and that he just saw it burn down a secret hideout at night. \Gls{LWonse} dismisses his ramblings,
absorbed in the preparations for the coronation, and reminds him that the explosion might just have
been a wizard's experiments gone wrong.

\subsubsection{\Gls{Vimes} is taken back to the Watch House}
\Gls{Vimes} falls asleep from the exhaustion and is carried back to the new Watch House by
\Gls{Carrot}. \Gls{Colon} wakes him up the next morning, to tell him that the coronation requires
all soldiers to line the streets in their ceremonial uniforms. \Gls{Vimes} decides to have his squad
up on the rooftops, in case the dragon is still close to the city waiting for the fog to clear up.
A while later \Gls{Carrot} arrives with a chew toy for \Gls{Errol}, who seems to be upset, and
uninterested in his favourite foods.

\subsubsection{The \Gls{Libra} decides not to interfere with history by stopping the theft of the
    book}
\Gls{Vimes} is dismayed to see the citizens wholeheartedly embracing the idea of autocracy as he
walks into his regular breakfast place. Meanwhile, the \Gls{Libra} finishes reading the book on
summoning dragons, and realizes that he can prevent it being stolen if he hides it or knocks out the
thief. Instead, the \Gls{Libra} chooses to let the book get stolen, and follows one of the hooded
figures back to his home to know more about the secret society.

\subsubsection{\Gls{Vimes} is dismissed by \Gls{LWonse} for causing a commotion at the ceremony}
At the open amphitheater built for the coronation, \Gls{Vimes} spots a winged creature rising out
of the misty river, and yells out that the dragon is back. He is scolded by \Gls{LWonse}, for
stopping the procession over the flapping of a large raven. \Gls{LWonse} suspends \Gls{Vimes} after
asking him to surrender his badge. \Gls{Vimes} returns to the Watch House to find his bottle of
liquor broken, and \Gls{Errol} having eaten half the wooden furniture in the room.

\subsubsection{The three soldiers of the City Watch spot the dragon hiding up above the city}
\Gls{Carrot}, \Gls{Nobby} and \Gls{Colon} stand on top of the Temple of Small Gods, trying to peer
through the fog in search of the dragon. A while later, \Gls{Nobby} realizes that the statue he is
leaning on is moving, and spots the dragon unfurling its wings from atop the dome of the temple. It
takes flight, leaving the three of them flattened on the temple roof, hoping for the structure to
remain intact.

\subsubsection{\Gls{Vimes} reunites with \Gls{Ramkin} at the coronation square}
\Gls{Vimes} hears the cheering crowds start to scream, and puts on his helmet to return to the
coronation square. He spots the citizens stampeding their way out of the square, as the dragon
gently glides down to land in front of the amphitheater, to then incinerate it. \Gls{Ramkin} finds
\Gls{Vimes} hiding behind a water fountain, as the noble dragon waits patiently for someone to show
up.

\subsubsection{\Gls{LWonse} is caught by the noble dragon}
The noble dragon carries \Gls{LWonse} in one of its talons, as he struggles to get out of the
ruins of the amphitheater, and walks to the king's palace. \Gls{Vimes} hears the sounds of iron
melting, as the dragon breathes its flame on the front-door, and hears the sound of more destruction
from deep within. Meanwhile, \Gls{Vetina} smiles inwardly from deep within the dungeons of the
palace, as the dragon gets to work burning down the structure above ground.

\subsubsection{\Gls{LWonse} addresses the city's Guildmasters in the royal palace}
\Gls{Vimes} is sad to see the moarchists quickly adapting to the idea of having the noble dragon
be their king. The next morning, the city's council of Guildmasters is summoned by \Gls{LWonse},
who offers them lunch in the great hall of the palace. The noble dragon hangs upside down from the
palace roof watching over them, as \Gls{LWonse} outlines the change in foreign policy, designed to
grow the dragon's hoard of gold.

\subsubsection{\Gls{LWonse} talks about the dragon's traditional diet}
\Gls{LWonse} goes on to tell the Guildmasters that the dragon needs a steady diet of maidens, and
that they must consider fulfilling its requests to avoid the prospect of their entire city burning
down in a single day. The Guildmasters leave, with the head assassin noticing \Gls{LWonse} asking
silently for help as they depart.

\subsubsection{\Gls{LWonse} dreads his life in subservience to the noble dragon}
\Gls{LWonse}, who is secretly the \Gls{SGM}, goes to the main hall of the palace when the dragon
summons him telepathically. He tries to explain to it that the human mind will adapt in time to
the threat of its flame-breath, and automatically quell any challenge to its rule. The dragon is
horrified by the pragmatic nature of the human mind, and is amused by the idea that no hero will
ever rise to challenge it.

\subsubsection{\Gls{LWonse} fails to convince the dragon to turn away from human sacrifice}
\Gls{LWonse} tries to argue against the dragon's need for a steady supply off maidens, and it
tells him that tradition demands it more than any intrinsic need. It asks \Gls{LWonse} to arrange
for the supply of young women, and flies off into the city through a broken window of the palace.

\subsubsection{\Gls{Colon} and the remaining Night Watch receive new orders from the dragon}
\Gls{Colon} and the two other soldiers mourn the absence of \Gls{Vimes} and \Gls{Errol} in the
Guard House, just as some palace guard arrive with a proclamation from the dragon. With great
difficulty, the palace guardsman reads out the diktat asking for a maiden as the dragon's meal.
\Gls{Colon} is confident that the people will reject this order, as he prepares to spread the word
on the streets.

\subsubsection{\Gls{Vimes} parts with \Gls{Errol} at \Gls{Ramkin}'s manor}
\Gls{Vimes} leaves \Gls{Errol} in \Gls{Ramkin}'s care, believing that he has started to diversify
diet hoping to challenge the noble dragon with his flame-breath. He says goodbye to \Gls{Ramkin}
awkwardly, and wishes for nothing more than to banish the dragon and have his job back. He decides
to track down the acolyte who had evaded them earlier, and sets off down the street.

\subsubsection{\Gls{Colon} spreads the word about the virgin sacrifice demanded by the dragon}
\Gls{Colon} addresses a crowd at night, talking about the dragon's proclamation. He is dismayed to
see a significant number accede to the dragon's demands, even as others express opposition.
\Gls{Colon} notices the dragon gliding over them to settle down on a nearby rooftop, just as
one of the acolytes runs away, fearing for his daughters' lives. The dragon promptly burns the lone
citizen brave enough to voice his dissent to its face.

\subsubsection{\Gls{Colon} comes up with a plan to defeat the dragon, at \Gls{Carrot}'s suggestion}
The \Gls{Libra} emerges into the present Library after its trip to the past, and heads straight
for \Gls{LWonse}'s home. Meanwhile, \Gls{Colon} and \Gls{Carrot} discuss the possibility of
firing an arrow at the dragon's weak spot, and persuade \Gls{Nobby} to put his archery skills to the
ultimate test.

\subsubsection{\Gls{Vimes} confronts \Gls{LWonse}, and is imprisoned by the palace guards}
\Gls{Vimes} corners \Gls{LWonse} in his new chamber within the palace, as he fishes around for the
magical tome and his cultist robes. \Gls{LWonse} calls for the palace guards, and is dismayed to
see them hesitate when asked to deal with the intruder. \Gls{Vimes} decides to play along with the
palace guards, giving them the most heroic smile he can muster. He allows himself to be dragged to
the nearby dungeon, as the \Gls{Libra} observes the events from the ceiling beams.

\subsubsection{\Gls{Ramkin} knocks herself out trying to confront the palace guards}
\Gls{Ramkin} investigates her dragon pens when all sounds of their snoring ceases in the night, and
finds \Gls{Errol} deathly cold from some mysterious chemical rearrangement of his flame-production
system. A while later, she finds some palace guards asking her to come to the palace, and decides
to charge at them with her ancestral broadsword. Another guard trips her up, knocking her out when
she crashes into one of the statues in the garden.

\subsection{}
\subsubsection{\Gls{Vimes} learns about \Gls{Vetina}'s contingencies in the dungeon}
\Gls{Vimes} finds \Gls{Vetina} in the dungeon, busy training some magically mutated rats from the
Unseen University to bring him supplies and food. The rats' tunnel network extends all through the
city, and \Gls{Vimes} realizes that \Gls{Vetina} is building his own network of spies to keep
abreast of the going-on in the palace. \Gls{Vetina} shows him the dungeon's door, which has several
strong bolts that can lock it from the inside, keeping them safe from the palace guards.

\subsubsection{\Gls{Colon} tests out his old longbow}
\Gls{Colon} unwraps his treasured longbow, and prepares to fire an arrow at the nearby building's
weather vane, for target practice. \Gls{Carrot} helps him string the bow, and is alarmed when the
arrow completely misses its target, and ricochets off a nearby gargoyle. \Gls{Nobby} hopes that the
gods in Dunmanifestin are watching their one-in-a-million gambit, and know the rules of the game
when it comes to desperate last attempts.

\subsubsection{\Gls{Vimes} and \Gls{Vetina} bide their time in the dungeon}
\Gls{Vimes} gets to work scrubbing the mortar out of a small grille along the dungeon wall, meant
to allow light in. \Gls{Vetina} is busy reading the books brought to him by the rats of the
University, and takes little notice of \Gls{Vimes}. Meanwhile, the \Gls{Libra} chooses not to
pursue his vendetta, and retreats to the Library.

\subsubsection{The \Gls{Libra} breaks \Gls{Vimes} out of the dungeon}
The Night Watch wonder how to calculate the odds of \Gls{Colon} hitting the dragon's weak spot, and
get to work ensuring that it is a one-in-a-million chance. Meanwhile, the \Gls{Libra} manages to
find the dungeon grille, and twists the iron bars free, pulling up \Gls{Vimes} with little effort.
They run through the abandoned kitchens, and deal with some guards minding the gate out into the
city.

\subsubsection{\Gls{Colon} fires his lucky arrow at the dragon}
\Gls{Errol} suffers from more digestive issues in the dragon pen of \Gls{Ramkin}'s manor. Meanwhile,
the Night Watch notice \Gls{Ramkin} being chained to a rock, as sacrifice for the dragon.
\Gls{Colon} fires his lucky arrow at it, just as it glides over them, on its way to the sacrificial
offering. The arrow bounces off its scales, causing it to breathe flames at the distillery that
\Gls{Colon} fired from.

\subsubsection{\Gls{Vimes} frees \Gls{Ramkin} from her chains}
The distillery catches fire and explodes, with the debris rising to enshroud the dragon. \Gls{Vimes}
manages to use a cleaver from the palace kitchen to break the chains binding \Gls{Ramkin}, after
dealing with some palace guards trying to stop him. Meanwhile, \Gls{Nobby} and \Gls{Colon} manage
to escape the conflagration by jumping off the roof into an adjacent lake, dragging themselves out
slowly to the shore.

\subsubsection{\Gls{Errol} tries to fight the noble dragon using his flame-flatulence}
\Gls{Carrot} persuades his two superiors to follow him into the street where the dragon has landed,
and is probably busy eating the sacrificial maiden. \Gls{Errol} rises from the dragon pens, using
his own flame-flatulence as thrust, and fights the noble dragon. He manages to nimbly avoid all the
fire that the dragon throws at him, and eventually realizes the best option is fly away from the
city. Meanwhile, \Gls{Vetina} uses the spare key to the dungeon to unlock it, and strides out of the
palace.

\subsubsection{\Gls{Errol} stuns the noble dragon with its supersonic flight}
\Gls{Errol} manages to catch the noble dragon in his sonic boom, as he shoots past it, narrowly
avoiding its flame-breath. The noble dragon crashes into the city streets, disoriented by the loud
noise and shockwave. Citizens rush to butcher it in its moment of weakness, just as \Gls{Colon}
tells \Gls{Vimes} that \Gls{Carrot} is attempting to arrest the noble dragon.

\subsubsection{\Gls{Carrot}'s arrest of the noble dragon is interrupted by \Gls{Errol}}
\Gls{Carrot} tries to read the charge-sheet for the noble dragon, as it lies pinned down beneath
a pile of rubble. As the gathered citizens watch on in stunned silence, \Gls{Errol} eventually
flies back to hover over the noble dragon, seemingly gloating in his victory. \Gls{Ramkin} realizes
that the noble dragon is female, and that \Gls{Errol} has managed to bind to it mate. The two of
them slowly rise over the city, and start to glide away.

\subsubsection{\Gls{Vimes} and the Night Watch head for the palace}
\Gls{Vimes} and the Watch run for the palace, threatening the palace guardsmen with imprisonment,
lest they open the gates. \Gls{Vimes} asks \Gls{Carrot} to arrest them anyway, and jail them in the
guardhouse, as they make their way further into the palace. Meanwhile, \Gls{LWonse} tries to escape
the palace with the stolen tome, having spotted \Gls{Vetina}'s silhouette stalking the corridors.

\subsubsection{\Gls{Carrot} accidentally kills \Gls{LWonse}}
At the palace, \Gls{Vimes} walks in on \Gls{LWonse} and \Gls{Vetina} facing off, and asks
\Gls{Carrot} to throw the book at the mastermind. \Gls{Carrot} literally throws the rulebook at
\Gls{LWonse}, making him fall off a great height onto the palace floor. \Gls{Vetina} dismisses the
rest of the City Watch, and tells \Gls{Vimes} in private that the citizens of Ankh-Morpork are too
self-centered to stand up to evil.

\subsubsection{The \Gls{Libra} takes back the stolen book from \Gls{LWonse}}
The \Gls{Libra} retrieves the stolen tome on summoning dragons from the body of \Gls{LWonse}, as
\Gls{Vetina} tells him to take \Gls{Carrot}'s rule-book along with him, to be buried deep in the
Library. \Gls{Vimes} prepares to get a drink with the \Gls{Libra}, anxious about how \Gls{Vetina}
planned to reward them the next day.

\subsubsection{\Gls{Vetina} grants an audience to the Night Watch to hear their requests}
\Gls{Vetina} is amused by the paltry rewards that \Gls{Colon} asks for in front of the assembled
council of nobles. \Gls{Vimes} breaks out into long-suppressed laughter at the request for a wage
increase and a dartboard, as \Gls{Vetina} struggles to hide his amusement. Later in the day,
\Gls{Vimes} returns to \Gls{Ramkin}'s manor, and spots some women helping repair the damage done
by \Gls{Errol}.

\subsubsection{\Gls{Vimes} decides to take up \Gls{Ramkin}'s offer of a relationship}
\Gls{Vimes} stumbles his way through a dinner with \Gls{Ramkin}, as the rest of the Night Watch
relax at the Mended Drum, pleased by the newfound respect they commanded from the citizens.
\Gls{Colon} works out the fact that \Gls{Carrot} might be the long-lost heir of the kings of
Ankh-Morpork, after examining his birthmark and sword, just as \Gls{Vetina} had the night before. He
chooses not to voice his opinion, and continues to drink the night away.


\section{Men at Arms}


\subsection{}
\subsubsection{}
