\chapter{Rincewind Novels}

\section{The Colour of Magic}

\subsection{}
\subsubsection{The first expedition under the rim of the Discworld is successful}
Zoologists from the kingdom of Krull are lowered past the rim of the world's edge, to investigate
the nature of the \Gls{Atuin}, the cosmic turtle, and the four elephants riding it, who bear
Discworld on their shoulders. The two prevalent hypotheses about the purpose of \Gls{Atuin} are the
Steady Gait (Steady state) and the Big Mating (Big Bang).

\subsubsection{\Gls{Bravd} and \Gls{Wsl} spot a pair of riders fleeing Ankh-Morpork}
\Gls{Wsl} and \Gls{Bravd} watch the burning city of Ankh-Morpork from a nearby hill, scanning for
anyone who might be fleeing the city through its gates. \Gls{Bravd}'s attempts to waylay a
wealthy-looking man coming out of the city is thwarted when he gets recognized. \Gls{Wsl} emerges
from his hiding place, identifying the escapee as \Gls{Rince}, a poor wizard.

\subsubsection{\Gls{Rince} talks about the sentient chest}
\Gls{Rince} tells \Gls{Wsl} that his companion \Gls{Twofl} had originally set fire to the city,
using the fact that he was a lightning rod for bad luck. He runs back to get \Gls{Twofl}, who is
knocked out by his horse, and shows them the sentient chest that walks along with him. \Gls{Wsl}
is unimpressed by \Gls{Rince}'s claims of strange magic from the chest compelling him to help
\Gls{Twofl}, as \Gls{Bravd} offers some food and drink.

\subsubsection{\Gls{Twofl} arrives at the Ankh-Morpork by ship}
\Gls{Wsl} notices the river Ankh being forcefully diverted into the burning city to flood it,
quenching the fire and ruining everything left in it that was not flammable. A few days earlier,
\Gls{Twofl} arrives by ship at the city, with the sentient chest in tow. He uses a phrasebook to
try and find accommodation, causing a spectacle with his casual splurging of gold coins.

\subsubsection{\Gls{Hugh} leads \Gls{Twofl} to the Broken Drum}
\Gls{Hugh}, a beggar on the harbour with a preternatural sense for gold, accosts \Gls{Twofl} and
promises to take him to a nearby tavern. He is terrified by the sentient chest walking along behind
\Gls{Twofl}, as he leads the newcomer to the Broken Drum, a nearby inn. Elsewhere in the city,
underworld boss \Gls{Ymor} speculates that the newcomer is a spy or a merchant, as he thinks about
the gold that might be swindled from him.

\subsubsection{\Gls{Twofl} tries to pay for room and board with gold coins}
\Gls{Withel}, a thief in the employ of \Gls{Ymor}, informs him that the ship captain had taken on
\Gls{Twofl} as a trader, with a raven informing him of \Gls{Hugh} leading the newcomer to
\Gls{Broad}'s tavern. At the broken drum, \Gls{Hugh} holds up three fingers to indicate the cost
of board being three copper pieces. \Gls{Twofl} misunderstands, placing three fat gold coins on the
bar.

\subsubsection{\Gls{Rince} recognizes the value of the sentient chest}
\Gls{Broad} tries to mime food and drink, as \Gls{Rince} identifies the sapient pearwood that the
chest is made of, from a dark corner of the tavern. The wizard, who is a graduate of Unseen
University, and was dishonourably discharged some time ago, uses his proficiency with languages to
try and talk to \Gls{Twofl}.

\subsubsection{\Gls{Twofl} talks to \Gls{Rince} about meeting some adventurers}
\Gls{Broad} hastily tells \Gls{Rince} that his own boarding and meals will be free if he helps
scam the foreigner. For his part \Gls{Rince} reminds \Gls{Twofl} that he would be killed very soon
by the many gangs converging on the Inn, using the Torb language. \Gls{Twofl} introduces himself,
excited to visit one of the famed taverns of Ankh-Morpork, and wishes to meet some adventurers
frequenting such establishments.

\subsubsection{\Gls{Broad} verifies the gold content of \Gls{Twofl}'s coins}
\Gls{Twofl} explains that he is from the port city of Bes Pelargic in the Agatean Empire.
\Gls{Rince} is shocked to meet someone from the Counterweight Continent. Meanwhile, \Gls{Broad}
learns from an alchemist that \Gls{Twofl}'s gold coin is pure, unlike those of Ankh-Morpork, causing
him to hurry back to the tavern. The alchemist sends a message to someone by homing rat, as a
nearby fortune-teller happens to scry the burning of the city.

\subsubsection{\Gls{Twofl} explains his reasons for visiting the city}
\Gls{Twofl} talks about the drudgery of his life as a clerk in Bes Pelargic, and of how he had
decided to see the world for himself. \Gls{Rince} reminds him that the currency he has will pay for
much more in Ankh-Morpork, and that he has massively overpaid the innkeeper. \Gls{Twofl} insists on
paying \Gls{Rince} in advance, for his help as a guide, and drops a few gold coins in his hands.

\subsubsection{\Gls{Rince} is brought to stand before the \Gls{Patri} of Ankh-Morpork}
\Gls{Rince} is captured and brought to the \Gls{Patri}'s palace in Ankh-Morpork, where he is accused
of trying to buy the horse using bad currency. \Gls{Rince} tries to argue that solid gold is a valid
medium of exchange, but grows quiet when he realizes the \Gls{Patri} is merely trying to get him to
become the foreigner's companion.

\subsubsection{\Gls{Patri} asks \Gls{Rince} to act as a tour guide for \Gls{Twofl}}
The \Gls{Patri} talks about the wealth and hostility of the Agatean Empire, and of how the visitor
was likely undercover to survey the Circle Sea's many city-states. He asks \Gls{Rince} to guide
the foreigner, ensuring he returns home with a positive impression of Ankh-Morpork, thus making
trade-deals more feasible between the two empires.

\subsubsection{\Gls{Rince} reaches \Gls{Twofl} at the tavern}
\Gls{Rince} returns to the Broken Drum, to find a massive brawl in the main floor, with bodies
littering the ground. He manages to sneak up the stairs to the lodgings, and finds \Gls{Twofl}
fast asleep in his room. He is tempted to reach into the pearwood \Gls{Lugg} for the bag of gold,
as \Gls{Twofl} wakes up, oblivious to the bloodbath that had just taken place downstairs.

\subsubsection{\Gls{Rince} is horrified by \Gls{Twofl}'s desire to meet the barbarian heroes}
\Gls{Rince} thinks about the barbarian heroes from the frozen hubland wastes, and tries to explain
the grim reality of their questing around Ankh-Morpork. \Gls{Twofl} is insistent on meeting some of
the famous heroes like \Gls{Bravd} and \Gls{Hrun}, just as a Sergeant of the City Watch arrives at
the tavern. \Gls{Rince} notices the survivors being given plenty of time to escape, with the city
guardsmen cleaning up the bodies afterward.

\subsubsection{\Gls{Rince} escorts \Gls{Twofl} away from the Broken Drum}
\Gls{Rince} lies about the corpses in the tavern being minor heroes, causing \Gls{Twofl} to pull out
his iconograph (polaroid), and ask the city watch to pose for a picture. \Gls{Rince} explains to the
terrified guards that the box contains a demon that draws pictures, and marvels at the little piece
of glass with his picture on it. During lunch, \Gls{Twofl} explains that he is an risk assessor for
an insurance firm, leaving \Gls{Rince} flummoxed.

\subsubsection{\Gls{Rince} escapes from \Gls{Withel} using the \Gls{Lugg} as a distraction}
After a day out taking pictures of the city's sights, \Gls{Rince} is alarmed by the imp within
the iconograph poking its head out the side to warn him that there was no ink remaining. He finds
\Gls{Twofl} missing, and is held up by \Gls{Withel} at knife-point. When he runs into the riverbank,
desperate to get away from \Gls{Withel}, the single spell burrowed in his memory tries to show
itself.

\subsubsection{\Gls{Rince} is joined by the \Gls{Lugg} at the banks of the Ankh river}
\Gls{Rince} is surprised to see the \Gls{Lugg} catch up to him, speculating that he is now its
master in the absence of \Gls{Twofl}. He decides to wait for dusk, and to swim out through the
Ankh river gate, hoping that the \Gls{Lugg} is buoyant enough to bear his weight. He feels guilty
about leaving \Gls{Twofl} to his fate, before the idea of living a wealthy life in some faraway
kingdom entrances him.

\subsubsection{\Gls{Patri} receives a second message from the Golden Empire's \Gls{GViz}}
The \Gls{Patri} asks one of his veteran diplomats to explain why a second message had arrived by
albatross from the Golden Empire, asking \Gls{Twofl} to be executed. The diplomat states that the
first message from the \Gls{Empe} had asked for the visitor to be protected, whereas the second one
was from the \Gls{GViz}, who might dread the idea of someone bringing back stories of a free
society flourishing elsewhere.

\subsubsection{\Gls{Rince} talks to the imp in the iconograph}
The \Gls{Patri} asks for the president \Gls{Zlorf} of the Assassins' Guild to be tasked with
eliminating the foreigner. Meanwhile, \Gls{Rince} tries to argue with the imp in the iconograph
about the alternative to magic that \Gls{Twofl} had said was prevalent in his homeland (science).
The imp reminds him that the \Gls{Lugg} contains a reserve of food and drink, bringing him relief
from the hunger that had begun to creep up on him.

\subsubsection{\Gls{Twofl} is held by \Gls{Ymor} at teh Broken Drum}
\Gls{Rince} uses gold coins to lure a thug keeping standing watch outside \Gls{Ymor}'s hideout, and
learns from him that \Gls{Twofl} is being held captive at \Gls{Broad}'s tavern. Meanwhile, at the
Broken Drum, \Gls{Ymor} watches with amusement as \Gls{Twofl} explains insurance to \Gls{Broad},
even getting him to agree to a policy premium.

\subsubsection{\Gls{Ymor} meets \Gls{Zlorf} and then \Gls{Rerpf}}
\Gls{Zlorf} barges into the Broken Drum, asking to kill the tourist, only for \Gls{Ymor} to remind
him that he was surrounded by even more thugs. He asks \Gls{Zlorf} to sit down, only for \Gls{Rerpf}
to enter the tavern behind him, flanked by several armed trolls. He introduces himself as the
representative of the recently formed Guild of Merchants, here to protect the foreigner, who was
valuable to the tourism industry.

\subsubsection{\Gls{Rince} talks to \Gls{Death}, as it stalks the streets of Ankh-Morpork}
\Gls{Rince} runs into \Gls{Death} on his way through the city's markets, and is alarmed to learn
that his own demise was scheduled for later that day, in some far off place. \Gls{Death}, as a
spirit visible only to the fine-tuned senses of a wizard, tells him that the prediction system had
gone haywire recently, as he runs away horrified.

\subsubsection{\Gls{Rince} and \Gls{Twofl} reunite in the tavern}
\Gls{Rince} throws bags of gold through the windows of the Broken Drum, to distract from the
\Gls{Lugg} preparing to break down the door in a charge. Once inside, \Gls{Twofl} cuts down the
hanging light, from a rafter on the ceiling. The people in the tavern are horrified by the
\Gls{Lugg}, and run for the exit in the absolute darkness. Meanwhile, \Gls{Broad} works in the
basement, preparing for a great fire to consume his inn, to claim the insurance policy.

\subsubsection{\Gls{Rince} defeats \Gls{Withel} using \Gls{Twofl} as a distraction}
\Gls{Death} itself gives \Gls{Broad} the tinder necessary to start the fire, as \Gls{Withel}
challenges \Gls{Rince} to a duel outside the inn. \Gls{Rince} stays alive out of sheer luck, as
\Gls{Twofl} shows up to distract the thief. \Gls{Rince} knocks out \Gls{Withel} in the split-
second of confusion, as the inn explodes in a firestorm that spreads through the street.

\subsubsection{\Gls{Twofl} and \Gls{Rince} buy horses to escape the flaming city}
\Gls{Twofl} tells \Gls{Rince} that he had insured the Broken Drum for two hundred gold coins, making
\Gls{Rince} realize that the proprietor had probably destroyed his own inn to cash out on the
policy. He finds some horses to escape the city, and is amused to see \Gls{Twofl} incapable of
riding one. Meanwhile, the \Gls{Lugg} emerges from the Ankh river some distance form the city, and
immediately sets off towards its master.

\subsubsection{\Gls{Wsl} and \Gls{Bravd} prepare to raid Ankh-Morpork for abandoned riches}
The \Gls{Wsl} finishes listening to \Gls{Rince}'s story, and prepares to raid the burnt-out city
for possessions left behind by its fleeing inhabitants. He reveals the tourist's pocket-watch, that
he had stolen on the way out, only to be bitten by the imp inside it that kept the time on an
abacus. He smashes the watch on the ground, banishing the imp to its home-realm, as \Gls{Bravd}
reminds him of the riches waiting for them in the ruined city.

\subsection{}
\subsubsection{The Discworld gods play their latest game with in their abode}
At Dunmanifestin, the home of the Discworld Gods, a game-board resembling a miniature disc is laid
out, with pieces representing its many heroes. After most players cash out of the game, or go
bankrupt, \Gls{Lady} takes out two pieces resembling \Gls{Rince} and \Gls{Twofl}, to set them on
the board as her newest pawns.

\subsubsection{\Gls{Rince} and \Gls{Twofl} flee Ankh-Morpork on horseback}
\Gls{Rince} and \Gls{Twofl} ride through the mountain trail to Chirm, with \Gls{Twofl} exasperated
by the claims that some system more logical than the magic of Discworld had to exist somewhere.
\Gls{Rince} hears the faint noise of bones clattering, as if dies were being rolled, and is alarmed
to find no one next to them.

\subsubsection{\Gls{Rince} and \Gls{Twofl} face a troll on the road to Chirm}
An angry troll appears on the road in front of \Gls{Rince}, seemingly teleported there from its
home in a faraway land. It charges them, with \Gls{Rince} missing his thrown short-sword. The
sword rebounds from a boulder on the side of the road, and impales the troll's neck, killing it.
Wounds from the troll's claws scatter \Gls{Rince} and \Gls{Twofl}'s horses, making them gallop in
opposite directions offroad.

\subsubsection{\Gls{Twofl} finds a statue pointing him to the temple of \Gls{Belsh}}
\Gls{Twofl} thinks about the jungle predators that his horse had disturbed in its mad dash away
from the troll, as he spots a stone carving with strange runes etched into it. The message bypasses
his cognition, directly informing him that the temple of \Gls{Belsh} was nearby. He decides to find
shelter in the temple, and follows a dirt track, hoping to escape the wolves in pursuit.

\subsubsection{\Gls{Lady} and \Gls{Fate} continue their game in the abode of the Gods}
\Gls{Rince}, hanging desperately from the collapsing branch of a tree, watches a hornet's nest get
blown into the pack of hungry wolves waiting for him down below. Meanwhile, at the game board in
Dunmanifestin, \Gls{Fate} and \Gls{Lady} are the last two players left, with \Gls{Fate} taking out
an icon representing an ancient eldritch monster. \Gls{Lady} reaffirms her ability to match his
bet, and asks him to keep playing.

\subsubsection{\Gls{Rince} is saved by \Gls{Druell}}
\Gls{Rince} is rescued by the dryad of the tree, who introduces herself as \Gls{Druell}. She tells
him that his friend is entering a temple of \Gls{Belsh} nearby, bringing back memories of his time
in the Unseen University's library, and of how he had read the Octavo, the forbidden spellbook that
was kept chained in a magic-insulated room.

\subsubsection{\Gls{Rince} is held captive by the dryads, who plan to kill him}
\Gls{Rince} realizes he has been captured by the tree, when some male dryads arrive to stop him
from leaving. \Gls{Druell} tells him that he will have the privilege of watching his friend suffer
\Gls{Belsh}'s cruelty, before he is killed for the crime of injuring the tree. As he is escorted
through the tree, \Gls{Rince} realizes the dryads are like insects in a hive, and is reminded of
the fact they should be extinct by now.

\subsubsection{\Gls{Rince} tries and fails to escape the tree}
The dryads summon a magical hologram of the temple of \Gls{Belsh}, showing a large horse tethered
near its entrance. \Gls{Druell} laughs at the fact that someone other than \Gls{Twofl} is also
in the temple, with the male dryads watching the proceedings carefully. \Gls{Rince} uses the
distraction to try and escape, but is encircled by the guards. He asks \Gls{Druell} to peer into
his mind to see the one spell he knows, making her recoil in horror at its power.

\subsubsection{\Gls{Hrun} and \Gls{Twofl} navigate the temple of \Gls{Belsh}}
\Gls{Rince} runs through the center of the ritual circle sustained by the female dryads meditating
in harmony, causing it to collapse. Meanwhile, \Gls{Hrun} silently walks through the dark corridors
of the temple, in pursuit of the \Gls{Lugg}, having spotted the bags of gold inside it. \Gls{Twofl}
asks the imp in his iconograph why it is so unnerved, just as \Gls{Rince} appears out of a portal,
gradually growing to his full size.

\subsubsection{\Gls{Rince} and \Gls{Twofl} reunite within the temple}
\Gls{Rince} begs \Gls{Twofl} not to utter the forbidden number (eight), as he realizes he is in some
underground chamber of the temple. He recounts the laws around the storage of  powerful magical
tomes, and of how he had been expelled from the Unseen University once the spell from the Octavo
had vanished from the page and lodged itself in his mind.

\subsubsection{\Gls{Twofl} and \Gls{Rince} run into \Gls{Hrun}}
At a central chamber, \Gls{Twofl} prepares to take some pictures of a central dais with a stone slab
on it, as \Gls{Hrun} walks in, pointing to the \Gls{Lugg}. \Gls{Rince} reminds him not to utter the
forbidden number, only for his sentient sword \Gls{Kring} to say it nonchalantly. As \Gls{Belsh}
sends out tentacles from the pit in the center of the chamber to drag them in, \Gls{Rince} uses the
pink lizards in \Gls{Twofl}'s box to make a bright flash, blinding the monster.

\subsubsection{\Gls{Hrun} decides to pursue \Gls{Belsh} through the pit in the chamber}
\Gls{Belsh} lets go of the intruders and slithers back into its pit, leaving \Gls{Rince} to study
the magic salamanders in \Gls{Twofl}'s box. They had fed on the dense octarine radiation within the
temple and excreted it at the opportune moment, blinding \Gls{Belsh}, and forcing him to retreat.
\Gls{Hrun} recovers, and immediately starts dislodging the stone slab protecting the \Gls{Belsh}'s
pit, convinced there is treasure buried underneath.

\subsubsection{\Gls{Rince} and the adventurers make it out on \Gls{Hrun}'s warhorse}
\Gls{Rince} realizes that the magical gale blowing into the pit, was the accumulated effect of
Time on the temple, kept away so far by the intimidating presence of \Gls{Belsh}. The roof of the
chamber starts to sag, sending inlaid octagonal stones falling down. \Gls{Hrun} summons his massive
warhorse, which carries them out of the temple just as it collapses into ruin, with Time making
amends for centuries of inaction.

\subsubsection{\Gls{Rince} and \Gls{Twofl} consider the idea of hiring \Gls{Hrun} as protection}
Outside the temple, \Gls{Hrun} kills a bear for food, with \Gls{Twofl} sorting through the
silver statues plundered from the temple. \Gls{Rince} pre-empts his idea of traveling in the
company of \Gls{Hrun}, by reminding him that the barbarian would likely rob them, and leave them to
the jungle predators. \Gls{Rince} realizes that \Gls{Hrun} could be lured into protecting them,
by appealing to his sense of vanity.

\subsubsection{\Gls{Rince} uses the iconograph to pay for \Gls{Hrun}'s services}
\Gls{Hrun} insists on more attempts at posing, delighted by the pictures \Gls{Rince} takes of him
standing victorious over slain brigands and monsters. At Dunmanifestin, \Gls{Fate} resigns from the
game, pushing his soul-chips across the game board to \Gls{Lady}. Meanwhile, \Gls{Death} watches
\Gls{Rince} ride off from the ruined temple, annoyed by his repeated escape from his scheduled
demise.

\subsection{}
\subsubsection{\Gls{Rince} realizes the party is in a strong magical field}
At a small cave along a road, \Gls{Rince} suspects the presence of a strong magical field, and asks
\Gls{Hrun} to toss a coin. The wars between the First Men and the Discworld Gods had been so
destructive that the High Old Ones had exterminated the former, and confined the latter to a remote
hideout. \Gls{Rince} suggests backtracking through the magical radiation field, and using the coins
to check if they are safe.

\subsubsection{\Gls{Liessa} intends to capture the riders intruding in her realm}
\Gls{Liessa} observes \Gls{Rince}'s party through a scrying glass, taking great interest in the
sapient pearwood. Her father, a powerful wizard suspended in purgatory for the last few months, asks
her to pursue them before they escape her zone of influence. He secretly hopes that she will get
killed, as payback for her mortally wounding him.

\subsubsection{\Gls{Liessa} and her dragons catch up to \Gls{Hrun}'s party}
\Gls{Liessa} goes to the dragon roost in the hollow interior of Wyrmberg, the inverted mountain that
was her hideout. She thinks about the ease with which she could rule over Wyrmberg if she had a
dim-witted brute as her mate, and sets her eyes on capturing \Gls{Hrun}. \Gls{Rince} and his party
are chased by the dragons, with only \Gls{Rince} making it to the cover a dense canopy.

\subsubsection{\Gls{Rince} is compelled by \Gls{Kring} to try and rescue his companions}
\Gls{Rince} wakes up from his concussion, and manages to evade the gaze of a dragon perched on a
high branch, as he runs away. Eventually, he finds \Gls{Kring} lodged in the branches of a tree,
asking him to turn around and rescue the others. He decides to retrieve the magical sword, and head
back to town to sell it. \Gls{Kring} however, compels him to rescue the others, by hijacking the
sword arm and setting it to his throat.

\subsubsection{\Gls{Rince} forces a dragon-rider to take him to Wyrmberg}
\Gls{Kisdra}, the lone dragon-rider left to hunt down \Gls{Rince}, is subdued when \Gls{Kring} uses
its skills to disarm him, and hold him hostage. \Gls{Rince} asks to be taken to Wyrmberg so that he
might rescue his friends, and is horrified to learn that the only entrance is through the dragon
caves high up along its face.

\subsubsection{\Gls{Rince} arrives at the dragon perch within Wyrmberg}
\Gls{Rince} notices the strong magical fields surrounding Wyrmberg, and notices the dragon grow
less transparent as it approaches the mountain. As the dragon perches on its huge ring inside the
hollow central chamber of Wyrmberg, \Gls{Rince} notices other dragon-riders converging on him with
crossbows armed. \Gls{Kring} advises him to attack them head-on, and sends waves of pain through
his hands when he considers surrender.

\subsubsection{\Gls{Rince} miraculously escapes \Gls{Death} using bullet time}
\Gls{Liort}, a dragonlord, challenges \Gls{Rince} to mortal combat, believing him to be a hero.
\Gls{Kisdra} helps \Gls{Rince} don a harness and boots, and teaches him how to navigate the ceiling
using the system of hooks and rings. As \Gls{Liort} prepares to deliver a killing blow, \Gls{Rince}
enters bullet-time, ducking under \Gls{Death}'s swinging scythe, and alarming \Gls{Liort} with his
superhuman speed.

\subsubsection{\Gls{Twofl} and \Gls{Hrun} investigate their jail cell}
\Gls{Rince} hangs on desperately from \Gls{Liort}'s hand, as both of the rings suspending him
give way, and lets go when the other dragon-riders aim their crossbows at him. Meanwhile, \Gls{Hrun}
and \Gls{Twofl} argue about the translucent dragons being the real thing, as they inspect the
treasure in the rooms adjoining their cell.

\subsubsection{\Gls{Liessa} convinces \Gls{Hrun} to perform some feats for her}
\Gls{Liessa} walks in with some crossbowmen, and stabs the sleeping \Gls{Hrun}, and is satisfied
when he reflexively stops her. When he wakes up, she tells him that there are more tests he needs
to pass, in order to win a valuable reward. \Gls{Twofl} is escorted to an adjacent cell, as
\Gls{Liessa} gives \Gls{Hrun} the task of killing her two brothers, to put her in line for the
throne of Wyrmberg.

\subsubsection{\Gls{Twofl} and his dragon reach the throne room of Wyrmberg}
\Gls{Hrun} is pleased by the prospect of winning \Gls{Liessa}'s hand and the treasures heaped in
Wyrmberg, as \Gls{Twofl} notices a dragon occupying most of his cell. It tells him that his own
imagination summoned it into existence, and melts the metal door on his orders. He navigates the
dusty corridors of Wyrmberg, noticing the dragon-sized harnesses rotting along the walls. Finally,
he comes across a set of massive double doors, opening to the slightest touch.

\subsubsection{\Gls{Twofl} talks to \Gls{Greicha} in the throne room}
In the throne room, the wizened old corpse on the chair introduces himself as \Gls{Greicha}, a
First Human now locked in purgatory, free of the constraints of time. He tells \Gls{Twofl} that he
also has the Power (of imagination ?), enabling him to summon true dragons by imagining them in
great detail, while in a place impregnated with a strong magical field.

\subsubsection{\Gls{Greicha} explains his predicament to \Gls{Twofl}}
\Gls{Greicha} bemoans his daughter's lack of imagination, leading to her dragons being weak and
translucent, and reveals that succession in his family required the elimination of all competing
claimants. He tells \Gls{Twofl} that the same route used by \Gls{Liessa} will lead to \Gls{Rince},
who is in danger of being killed by \Gls{Liort}.

\subsubsection{\Gls{Twofl} saves \Gls{Rince} in the roosting chamber}
\Gls{Twofl} and his dragon arrive at the roosting chamber, in time to catch \Gls{Twofl} as he
falls from the ceiling. \Gls{Rince} almost finishes uttering the forbidden spell sealed in his mind,
as he is caught by \Gls{Twofl}, getting knocked out in the process.

\subsubsection{\Gls{Hrun} defeats \Gls{Liessa}'s brothers}
On top of the Wyrmberg, \Gls{Liort} and his brother \Gls{Liart} mount their dragons to face
\Gls{Hrun}, who \Gls{Liessa} chooses as her champion. \Gls{Hrun} manages to knock out both brothers,
making their dragons vanish. \Gls{Liessa} informs him that the dragons are imaginary, (Imagined
Dragons), and reminds him that there is one final test remaining.

\subsubsection{\Gls{Hrun} is rescued by \Gls{Twofl}'s dragon}
\Gls{Twofl} asks his dragon to fly to \Gls{Hrun}'s rescue, as \Gls{Rince} tries to deal with his
fear of heights. The dragon snatches \Gls{Hrun} in its claws, causing \Gls{Liessa} to furiously
summon her own golden dragon and gives chase (Freud comes up with his theory of girls subconsciously
sexualizing horse-riding). \Gls{Death} uses the commotion to snatch \Gls{Greicha}'s soul, ending
his self-imposed purgatory.

\subsubsection{\Gls{Twofl} and \Gls{Rince} shift into the real world}
\Gls{Twofl} passes out from the thinning air when his dragon flies high up, causing all of them
to fall. \Gls{Hrun} is caught by \Gls{Liessa}'s dragon, with \Gls{Death} appearing beside
\Gls{Rince} to taunt him once again. He crosses realities with \Gls{Twofl}, and is now a doctor on
an airplane helping defuse a bomb.

\subsubsection{\Gls{Rince} and \Gls{Twofl} are dragged back into their original reality}
When the \Gls{Lugg} crashes into the airplane, causing a large hole in it, \Gls{Twofl} and
\Gls{Rince} are banished back to their original reality by the multiverse trying to correct itself.
They fall into the Circle sea, having been displaced many miles during their reality shift.

\subsection{}
\subsubsection{\Gls{Archast} kills \Gls{GSDact} after he finishes building the bronze submersible}
In the secretive rimward kingdom of Krull, \Gls{Archast} supervises the completion of their latest
submersible, designed by \Gls{GSDact}, the greatest craftsman in all Discworld. \Gls{Archast}
patiently listens to his tales of losing parts of his body after completing each of his contracts,
and finally kills him, to prevent the possibility of an equally impressive piece of art ever being
recreated.

\subsubsection{\Gls{Rince} and \Gls{Twofl} accidentally get swept to a Rimfall}
\Gls{Rince} and \Gls{Twofl} try desperately to keep their ship afloat, after escaping some slavers,
and notice a current dragging them into the Rimfall on the outer rim of Discworld. As their ship
approaches the Rimfall, \Gls{Rince} rescues a frog struggling against the current, and shoves it
into an inside pocket. \Gls{Twofl} sees no point in worrying about their impending deaths, as
something metallic hits their hull, causing \Gls{Rince} to nearly drown.

\subsubsection{\Gls{Twofl} and \Gls{Rince} are rescued by \Gls{Tethis}}
The captain of the slaver ship that had fished out \Gls{Rince} and \Gls{Twofl} prepares his raft,
as the bloodbath wrought by the \Gls{Lugg} forces him to abandon his own ship. Meanwhile,
\Gls{Twofl} helps \Gls{Rince} get up, and tells him that a sea troll named \Gls{Tethis} had rescued
them, and that they were currently tethered to the Circumference, a system of ropes and pulleys
just inside the rim of Discworld.

\subsubsection{\Gls{Tethis} rows his boat to his home at the edge of the rim}
\Gls{Rince} notices a small island at the rim, with the troll's shack being built on it. He also
sees the system of ropes and bells attached to it, resembling a spiderweb, as the boat slides into
a makeshift jetty. He dares to look at the troll, and is pleased to find a humanoid shape made
entirely out of water, instead of the horribly disfigured monster he had imagined.

\subsubsection{\Gls{Twofl} learns about the Circumference}
\Gls{Twofl} recognizes the green drink offered by \Gls{Tethis}, as Ghlen Livid (GlenLivet whiskey),
a distilled fermented drink from his homeland. \Gls{Tethis} then talks about the Circumference being
a net constructed by the Krull, spanning the entirety of the rim of Discworld, and of how he had
been enslaved by them when he tried to sail into the Rimfall.

\subsubsection{\Gls{Tethis} talks about his journey to Discworld from his home of Bathys}
\Gls{Tethis} suspends \Gls{Rince} over the rimward edge of his island, allowing the wizard to
see the elephants and \Gls{Atuin} holding up the Disc. He talks about his own cowardice when it came
to jumping off the edge, and possibly returning to his home world of Bathys. He explains his journey
through the void between worlds, given how his body was capable of withstanding the cold, unlike
humans.

\subsubsection{\Gls{Rince} and \Gls{Twofl} learn about their imminent capture by the Krull}
\Gls{Rince} tries and fails to injure \Gls{Tethis} with a sword he finds in the boxes strewn around
the shack, with the troll reminding them of the moon's tides affecting its size throughout the day.
A message arrives by bell from the slavers of Krull, declaring that \Gls{Rince} and \Gls{Twofl}
were to be collected immediately by flyer, instaed of the usual salvage fleet that would visit the
island periodically.

\subsubsection{\Gls{Rince} and \Gls{Twofl} are forced on board the Krull flyer}
A Krull flyer arrives at the island, piloted by a squad of hydrophobe mages. \Gls{Rince} marvels
at the magical resources needed to construct such a vessel, as he is forced to climb aboard it, and
fasten himself to one of the rings on its floor. Some ferocious sea monster speeds towards
\Gls{Tethis}, as the Krull vessel lifts off, to return to the capital.

\subsubsection{The \Gls{Lugg} manages to escape the sinking of the pirate ship}
The \Gls{Lugg} sinks along with the pirate ship, and is swallowed by a sea monster in the depths of
Gorunna Trench. Later, the monster washes ashore dead on a small rimward island, and a straight line
of destructive force travels towards the rim, cutting through many other atolls.

\subsubsection{\Gls{Rince} and \Gls{Twofl} are taken to the city of Krull}
\Gls{Rince} is stunned into silence, by the wizard holding the wand of Negativity over him, as he
sees the hand shaking in fear. The witch introduces herself as \Gls{Marchesa}, and reveals that they
are not slaves, but ritual sacrifices. When he reaches the capital city of Krull, \Gls{Rince}
and \Gls{Twofl} are led into a richly appointed room, with a seafood feast laid out on a grand table
for them.

\subsubsection{\Gls{Garha} explains the ritual sacrifice in store for \Gls{Rince} and \Gls{Twofl}}
\Gls{Garha}, the Krull Guestmaster, introduces himself to \Gls{Rince}, explaining the delicacies
laid out on the dining table in front of them. He reveals that the sacrifice is due for the next
morning, and leaves them sealed in the guest chamber, to get ready for the ritual. Meanwhile,
the \Gls{Lugg} surfaces at the rim, and makes its way along the rope lines of the Circumference,
crashing through any islands along the way.

\subsubsection{\Gls{Rince} learns about the Krull expedition past the rim}
\Gls{Rince} takes the frog out of his robes, and sees it enshrouded in a tornado of magical
radiation. The magical field dissipates, to reveal the same frog, with \Gls{Lady} standing by its
side. She tells them that the Krullians intend to lower a submersible past the rim of Discworld, to
investigate \Gls{Atuin}. She tells them that \Gls{Fate} has been conspiring against them, demanding
that they be sacrificed to ensure the safety of the expedition.

\subsubsection{\Gls{Garha}'s own bottle knocks him out when his spell wears off}
The frog telepathically tells \Gls{Rince} to prepare for \Gls{Garha}, just as \Gls{Lady} vanishes,
and guards enter their room to escort them out. The bottle that \Gls{Rince} had thrown earlier at
the Guestmaster out of anger, now resumes its normal trajectory after the time-spell slowing it
down wears off, and knocks \Gls{Garha} out, allowing the two prisoners to escape.

\subsubsection{\Gls{Fate} is exasperated by \Gls{Death}'s ambivalence regarding \Gls{Rince}'s
    demise}
\Gls{Twofl} and \Gls{Rince} escape some hydrophobe wizards by pushing them into a pool, and make it
to the safety of a planetarium. Meanwhile, \Gls{Fate} viists \Gls{Death} in his hideout, and
insists that \Gls{Rince} and \Gls{Twofl} were certain to be claimed in the coming Krull sacrifice.
\Gls{Death} reminds him that he had bigger business to attend to, than chase after these two souls
that repeatedly eluded his grasp.

\subsubsection{\Gls{Twofl} and \Gls{Rince} take the place of the chelonauts}
\Gls{Twofl} suggests volunteering as the chelonauts, when he spots the two spacesuits hanging in
one corner of the planetarium, just as the two original astronauts step into the room, having
finished their bath. \Gls{Rince} is annoyed by the fact that he cannot make sense of their language,
They knock out the two youths, and prepare to come out of the room, wearing the suits.

\subsubsection{}
At the launch site, \Gls{Archast} is furious when told of the escape of the two prisoners, and
brushes off some news from the harbour, about a monster ravaging the docked ships (\Gls{Lugg}).
As the chelonauts are escorted into the arena set up for the citizens to witness the launch,
the \Gls{Archast} grows suspicious of \Gls{Rince}'s gait, and starts to prepare a levitation
Curse.

\subsubsection{\Gls{Twofl} and \Gls{Rince} are reunited with the \Gls{Lugg}}
The \Gls{Archast} is interrupted by the \Gls{Lugg} breaking into the launchpad, forcing him and his
underlings to fire all of their offensive magic at it. The confluence of magic makes a positive
feedback loop with the ambient magical field, causing a huge explosion that sends the mages
running. A while later, after the \Gls{Lugg} spits out \Gls{Tethis} at its master's feet, some
soldiers try to retake control of the arena.

\subsubsection{\Gls{Rince} and his party board the submsersible}
\Gls{Rince} wonders how the \Gls{Lugg} manages to swallow so many people, while keeping its master's
belongings completely isolated from the bloody aftermath. \Gls{Twofl} and \Gls{Tethis} manage to
undo the hatch leading into the ship, just as soldiers start to climb the ladder leading to it.
\Gls{Rince} hastily descends the ship's interior, just as an automated mechanism sets the ship in
motion along the rail designed to launch it over the Discworld's rim.

\subsubsection{\Gls{Rince} escapes \Gls{Death}'s apprentice}
\Gls{Rince} gets caught in a tree growing off the edge of the Rim, and is visited by \Gls{Death}'s
apprentice. The little demon tells him that \Gls{Death} cannot come in person because of a plague
in progress elsewhere, and is dismayed when \Gls{Rince} loses his grip on the branch, to fall into
the void of space.


\section{The Light Fantastic}


\subsection{}
\subsubsection{\Gls{GalderW} and his chain of command witness the Octavo produce its own magic}
\Gls{GalderW}, the Chancellor of Unseen University is summoned to the room holding the Octavo, as
the tome starts radiating raw magic, in response to \Gls{Rince} plunging to his death past the rim
of Discworld. The tome releases a giant ball of raw magic, that transmutes everything in its path,
as it rises through the underground levels to hover in the central hall of the university.

\subsubsection{\Gls{GalderW} reaches the top of a tower to observe the Discworld's rim}
\Gls{GalderW} and the wizards see the ball of raw magic resolve into a miniature model of the
Discworld, and head up to the University's terrace, to observe the model of Dunmanifestin. He
levitates himself up the Tower of Art, and observes a new dawn arise over Discworld, complete
with the shadow of Cori Celesti falling over the city.

\subsubsection{\Gls{Rince} is saved by the Spell of Change triggered by the Octavo}
\Gls{GalderW}'s second-in-command, \Gls{Trymon}, notices the miniature model of the Discworld expand
to life-size, and identifies it as a spell of change. The two of them notice no visible changes
around them, as it fades away with the coming of dawn. The spell moves \Gls{Rince} to a tall tree,
leading to a nasty fall into some pine needles. He is surprised when the tree replies to him, but
walks away after declaring its life boring.

\subsubsection{\Gls{Twofl} and the \Gls{Lugg} reunite with \Gls{Rince}}
\Gls{Twofl} and the \Gls{Lugg} also appear magically somewhere on the Disc, and manage to find
\Gls{Rince} wandering through the forest of talking trees. \Gls{Rince} tries to impress \Gls{Twofl}
with his knowledge of botany, as they struggle to find something edible in the vegetation. He is
alarmed at the small doors and windows in its cap, as \Gls{Twofl} tries to speculate why he
considers it inedible.

\subsubsection{\Gls{GalderW} and his inner council summon \Gls{Death} to interrogate him}
At the Unseen University, \Gls{GalderW} talks to the assembled council of eight powerful wizards,
about their inability to learn the reason behind the Spell of Change. They decide to summon
\Gls{Death}, and ask him about the events of that morning. \Gls{Death} tells them that the Octavo
had interfered in \Gls{Rince}'s death, in an effort to keep all of its spells intact.

\subsubsection{\Gls{Trymon} decides to beat \Gls{GalderW} and his council to the Library}
\Gls{Death} casually lets slip a prophecy that outlines the destruction of Discworld, unless all
eight Forbidden Spells are uttered in sequence sometime in the next two months. Meanwhile,
\Gls{Trymon} hurries to the Library, having observed the meeting of the inner council from a hidden
vantage point. He gives the head librarian, now morphed into an orangutan, some bananas in exchange
for a book about the Pyramids of Tsort.

\subsubsection{\Gls{Twofl} and \Gls{Rince} agree to follow \Gls{Swires} the gnome}
In the forest of Skund, \Gls{Twofl} and \Gls{Rince} argue about the identity of a small man living
in a mushroom cap, as \Gls{Twofl} narrates the fairy tale descriptions he had read as a child.
The gnome catches up to them, introduces itself as \Gls{Swires}, and points them to a nearby cottage
with food and shelter for full-sized humans. It turns out to be a gingerbread house belonging to a
long-dead witch.

\subsubsection{\Gls{Trymon} gets to work researching the Pyramids of Tsort}
Meanwhile, \Gls{Trymon} is busy trying to decipher the tome describing the construction of the Tsort
pyramids. A mysterious wizard with few teeth sits in a campfire along with some hubland barbarians,
and talks about the finer things in life.

\subsubsection{\Gls{GalderW} talks about the Spell burrowed in \Gls{Rince}'s mind}
\Gls{GalderW} receives \Gls{Trymon} in his workshop, and claims to know a better way to recapture
the spell hidden in \Gls{Rince}'s mind than mere brute force. \Gls{Trymon} is intrigued to learn
that the Great Spells will simply jump to another mind when their current owner dies, as
\Gls{GalderW} sends a homing arrow to kill \Gls{Rince}.

\subsubsection{\Gls{Trymon} tries and fails to kill \Gls{GalderW} to get the Great Spell}
\Gls{Trymon} tries to kill \Gls{GalderW} by throwing a kitchen knife at him, only for some defensive
spell to divert it harmlessly to the door. \Gls{Trymon} covets the Great Spell in \Gls{Rince}'s
mind, after reading about the rewards reserved for the person who recited all eight of them in the
Pyramid of Tsort.

\subsubsection{\Gls{Twofl} wishes to buy out the gingrebread house}
\Gls{Twofl} is interested in purchasing the gingerbread house of the old witch \Gls{Whitlow} to
turn it into a tourist attraction. Against \Gls{Rince}'s wishes, \Gls{Swires} arranges for the
forest council to sell it to \Gls{Twofl}, who believes he can pack it inside the pocket dimension
of the \Gls{Lugg}

\subsubsection{\Gls{Greyha} attempts to build a fortified room to keep \Gls{Death} at bay}
At the Unseen University, \Gls{Greyha}, one of \Gls{GalderW}'s fellow council members, and the
oldest wizard in the university, prepares a protective den meant to keep \Gls{Death} from getting
at him. The elaborate rituals fail, as \Gls{Death} simply enters the room through an airhole.

\subsubsection{\Gls{Twofl} and \Gls{Rince} escape the cottage on a flying broomstick}
A squad of junior wizards find the gingerbread cottage, and break in, just as \Gls{Twofl} and
\Gls{Rince} hide inside a small cupboard. As more young wizards converge on the cottage, and
get distracted by bumping off the other squads, \Gls{Twofl} finds a flying broomstick in the
cupboard. \Gls{Rince} drives it out of the cottage with \Gls{Twofl} riding pillion, just as
\Gls{GalderW}'s enchanted arrow zips into the building, and hits the \Gls{Lugg}.

\subsection{}
\subsubsection{\Gls{Rince} and \Gls{Twofl} notice the coming end of Discworld}
\Gls{Rince} and \Gls{Twofl} break through the thick layer of clouds covering the Disc, and notice
all the stars vanishing from the sky, with only one red dot approaching them in the distance.
\Gls{Rince} points the broomstick down, overcome with terror at the prospect of Discworld being
annihilated.

\subsubsection{\Gls{GalderW} finds the \Gls{Lugg} answering his spell of Recall}
In \Gls{GalderW}'s workshop, he completes the spell recalling his homing arrow, only for the
\Gls{Lugg} to land on him. Meanwhile, \Gls{Trymon}, who had been pushed back by a shockwave from
the spell, decides not to investigate whether the \Gls{Lugg} has eaten his master, and runs out of
the room.

\subsubsection{\Gls{Twofl} and \Gls{Rince} crash into \Gls{Belafon}'s flying rock}
\Gls{Twofl} and \Gls{Rince} crash into a rock flying high in the sky on their way down to the
ground, and find it being piloted by a young druid named \Gls{Belafon}. He claims to be delivering
a replacement stone for some time-measurement device (Stonehenge) in the mountains, and subscribes
to the druid system of magic based on persuasion and charm. \Gls{Rince} warns \Gls{Twofl} not to
insist on the utility of an almanac in telling the time, as opposed to the druid system of sun
shadows.

\subsubsection{\Gls{Belafon} lands his rock at the site of the Druid stonehenge}
At the University, \Gls{Trymon} is relieved to hear that the \Gls{Lugg} has left the premises, and
walked into the city. Meanwhile, \Gls{Rince} and \Gls{Twofl} land at the site of the Stonehenge,
to see the druids arguing about how it was already suffering inaccuracies in predicting the
sunrise. \Gls{Rince} is suddenly forced into sleep by the Great Spells, who talk to him about his
role in averting the coming calamity.

\subsection{}
\subsubsection{\Gls{Trymon} asks the Chief Astrologer of the University to read \Gls{Rince}'s
    horoscope}
At the observatory of the Unseen University, \Gls{Trymon} talks to the Chief Astrologer about the
prospect of the red dot in the sky being a massive star that might burn Discworld long before a
direct collision, and suggests the use of \Gls{Rince}'s horoscope to divine his current location.
The Astrologer reads the horoscope, which offers no specific information, except a warning about
druids.

\subsubsection{\Gls{Rince} tries to tell \Gls{Twofl} about the reality of priesthood}
\Gls{Twofl} is convinced that priests all over the world are men of poverty, chastity and discipline
the way they are in his homeland. \Gls{Rince} tries to explain that priests in his home deal in
ritual sacrifices, often involving the killing of innocent victims, all in the name of perpetuating
their religion. He sees the druids prepare for their festival by escorting a maiden in white to
the central ritual altar.

\subsubsection{\Gls{Rince} rescues \Gls{Twofl} with the help of heroic old man}
The old man, acclaimed as one of the greatest heroes of Discworld, breaks into the ritual circle,
just as \Gls{Twofl} tries to argue against the practice of human sacrifice. He starts to slaughter
the druids, allowing \Gls{Rince} to rescue the girl in white robes, as well as \Gls{Twofl}. He
notices the girl complain about her missed opportunity to reach heaven, as \Gls{Twofl} is grazed by
a druid's sickle.

\subsubsection{\Gls{Cohen} is rushed away from the commotion at the Stonehenge}
The old man, who reveals himself to be \Gls{Cohen} the Barbarian, takes a look at \Gls{Twofl},
and declares him mentally absent. \Gls{Rince} worries about the possibility of retrieving his mind,
as \Gls{Bethan}, the maiden in white robes, helps apply ointments on \Gls{Cohen}'s arthritic knees.
\Gls{Rince} notices the large white warhorse, matching his grandfather's descriptions of
\Gls{Cohen} and his majestic steed.

\subsubsection{\Gls{Rince} and the party are led to a necromancer of the stepp tribes}
Meanwhile, the \Gls{Lugg} barrels through a squad of wizards sent by \Gls{Trymon} to track
\Gls{Rince}, leaving them horrified by the prospect of facing a powerful necromancer. \Gls{Cohen}
leads the party to a chieftain of the steppe tribes, where an old woman tries to cast some Caroc
cards to divine \Gls{Twofl}'s location. \Gls{Rince} is made to drink a potion that sends him on a
spirit-walk, with only the old woman able to see his spirit rising from the tent.

\subsection{}
\subsubsection{\Gls{Trymon} takes charge of the council meeting at the University}
At the University's council hall, the six remaining old wizards worry about the threat presented by
\Gls{Trymon}, just as he walks into the room, distributing agenda sheets for the meeting.
\Gls{JigladW}, one of the original council members, is exasperated by his disregard for the archaic
ways of conducting University business, as they start to describe their failed attempts at tracking
down \Gls{Rince}.

\subsubsection{\Gls{Trymon} tells the council about the hero sent to track down \Gls{Rince}}
\Gls{Trymon} reveals to the council that he has sent a tracker to hunt down \Gls{Rince}, leading to
an argument breaking out about the need to hire heroes to do the work of wizrds. \Gls{Trymon}
reminds them that \Gls{Rince} is somehow able to evade magical detection, necessitating these
desperate measures.

\subsubsection{\Gls{Rince} travels to the house of \Gls{Death} as a spirit}
\Gls{Herrena}, the rare female hero of any renown in Discworld, rides with a posse of hired swords
to the Trollbone mountains, at the behest of \Gls{Trymon}. Meanwhile, \Gls{Rince} spirit-walks into
the realm of \Gls{Death}, where he finds his cottage. He sneaks into the cottage, to find an ornate
double staircase with a grandfather clock in between. The \Gls{Lugg}, which is waiting for him in
the garden next to the cottage, follows him inside.

\subsubsection{\Gls{Rince} finds \Gls{Twofl} inside \Gls{Death}'s cottage}
Inside the main hall of \Gls{Death}'s cottage, a woman takes hold of \Gls{Rince}'s hand, and guides
him into a room, surprised to finally have a living guest. She leads him to a study room, where he
overhears \Gls{Twofl} excitedly explaining the rules of a card game to \Gls{Death} and his horsemen.
She introduces herself as \Gls{Ysabell}, the adopted daughter of \Gls{Death}.

\subsubsection{\Gls{Ysabell} wishes to keep \Gls{Twofl} and \Gls{Rince} in the underworld}
\Gls{Twofl} gives \Gls{Death} a rulebook for his nations's version of Bridge, and is hastily
escorted out by \Gls{Rince}, as the gods are busy arguing the finer details of the card game.
\Gls{Ysabell} stops them from leaving, intending to cut their lifelines with her scythe. The
\Gls{Lugg} stops her by biting down on the blade, allowing \Gls{Rince} to run away with an
unconscious \Gls{Twofl} on his shoulder.

\subsubsection{\Gls{Rince} and \Gls{Twofl} escape the underworld}
The \Gls{Lugg} jumps off the platform holding \Gls{Death}'s house, into the gigantic funnel where
the souls of the dead were being sent. \Gls{Rince} also jumps off, when he notices the two lifelines
falling into the abyss below. \Gls{Death} and his horsemen arrive shortly after, and decide not to
pursue \Gls{Rince}, still being enchanted by the allure of Bridge.

\subsubsection{\Gls{Rince} is dragged once again into the Octavo by the Great Spells}
\Gls{Rince} finds himself inside the Octavo once again, where the Great Spells reveal the true
purpose of his existence. He was to prevent the wizards from uttering all eight Spells at the same
time, by keeping himself out of their clutches for as long as he could. Suddenly, \Gls{Rince}'s
homesickness grips his mind, and drags him back to his body, causing him to wake up from his
spirit-walk inside the chieftain's tent.

\subsubsection{\Gls{Rince} and the party set off for the Smarl river}
\Gls{Rince} eagerly looks at the pictures produced by \Gls{Twofl}'s iconograph, while asking the
painting imp what it saw in the underworld. \Gls{Cohen} and the party set out for Ankh-Morpork,
hoping to ride to the Smarl river and hire a boat to the Circle Sea. \Gls{Cohen} is amused by
\Gls{Twofl}'s star-struck babbling, and lets him recount the greatest tales from his childhood about
the most famous hero of the Disc.

\subsubsection{\Gls{Cohen} makes the party pitch camp for the night}
\Gls{Cohen} suspects the party has entered troll country, as \Gls{Rince} reluctantly sets out to
find herbs and roots for the next meal. \Gls{Cohen} is deeply suspicious of \Gls{Twofl}'s belief
that the wizard is well-versed in botany, as \Gls{Rince} receives some help from a disembodied
voice in the jungle. Hoping that it is not a troll, \Gls{Rince} sees the sun set, and is reminded of
the stories of trolls turning to stone when exposed to sunlight.

\subsubsection{\Gls{Cohen} is shocked to learn about dentures}
Back at camp, \Gls{Cohen} despairs at the loss of his teeth, and of how no one takes him seriously
anymore when they see his gummy smile. In response, \Gls{Twofl} takes out his own teeth, which are
a complete set of dentures, and offers a backup set to \Gls{Cohen}, who is left stunned by the
idea of removable teeth.

\subsubsection{}
In the forest, a family of trolls, introduce themselves to \Gls{Rince}, talking about some ancient
prophecy that mentioned him saving the Disc from the red star. He asks them for help making some
soup, with the head of the family, \Gls{Kwartz} being underwhelmed by how their prophecy was
being fulfilled. They return to \Gls{Cohen}'s camp, to find it deserted, with a blood trail and
several hoofprints riding away from it.

\subsubsection{\Gls{Herrena} captures \Gls{Rince}'s companions}
\Gls{Herrena} leads her mercenaries to a small hill, with the three captives in tow. The \Gls{Lugg}
is also bound and dragged along, as she looks at some troll caves to make camp for the night. She
asks \Gls{Gancia}, the leader of the hired thugs from Ankh-Morpork, to set up camp, while thinking
about the two men and the box that matched \Gls{Trymon}'s description.

\subsection{}
\subsubsection{\Gls{Twofl} tries to ask politely to be released}
\Gls{Kwartz} tells \Gls{Rince} that the fire lit in front of the mountain cave, is unlikely to
deter his grandfather, since he is the mountain itself. He also explains that normal-sized trolls
might keep away from fires because of the adverse effects on their brain. Meanwhile, \Gls{Twofl}
notices the teeth, tonsils and cheeks within \Gls{OldG}'s mouth, and asks \Gls{Herrena} to let them
out.

\subsubsection{\Gls{Herrena} orders her men to open the \Gls{Lugg} by force}
\Gls{Herrena} decides to disregard \Gls{Trymon}'s orders not to touch the chest, and asks
\Gls{Gancia} to force it open. \Gls{Twofl} tries to tell him that the chest opens only when it feels
in the mood, as the rest of the mercenaries notice someone approaching the cave from lower ground.
\Gls{OldG} moves his mouth, leading to everyone inside losing their footing.

\subsubsection{\Gls{Twofl} and the prisoners are set free by the last remaining mercenary}
As \Gls{OldG} tries slowly to stand up, waking from a centuries-long slumber,
\Gls{Herrena} and the mercenaries jump out of its mouth, leaving \Gls{Gancia} and \Gls{Weems} alone
with the prisoners. \Gls{Gancia} gets eaten by the \Gls{Lugg} when he tries to retrieve some gold
inside it, and \Gls{Weems} hastily unties the prisoners before leaping out of the rising cave mouth.

\subsubsection{\Gls{Rince} sees his friends on top of \Gls{OldG}}
With sunrise, the trolls helping \Gls{Rince} as well as \Gls{OldG} all turn to stone, with the
mercenaries having fled the scene. \Gls{Rince} notices \Gls{Twofl} and the \Gls{Lugg} high up in
\Gls{OldG}'s mouth, trying to find a way down to the ground.

\subsubsection{\Gls{Cohen} decides to square off against the \Gls{Lugg}}
\Gls{Cohen} tries to fight the \Gls{Lugg} with his bare hands, rambling about the gold he had seen
in it, and of how it had swallowed \Gls{Gancia}, never to be seen again. \Gls{Twofl} calls off his
pet, while reminiscing about the vanishing shop he had purchased it from when preparing for his
travels. \Gls{Rince} takes him aside, and recommends separating from the others, to improve their
chances of survival.

\subsubsection{\Gls{Herrena} takes \Gls{Rince} and \Gls{Twofl} to the Smarl river}
\Gls{Herrena} ambushes \Gls{Twofl} and \Gls{Rince} along with her men, while warning the \Gls{Lugg}
to stay away from her camp. The \Gls{Lugg} chooses to follow them on their ride to the Smarl river,
triggering paranoia and fear in \Gls{Weems}, much to \Gls{Rince}'s amusement. Eventually, they
reach the river crossing, and strike the gong for the winch-operated ferry. \Gls{Twofl} laughs
through his gag as he recognizes \Gls{Cohen} rowing the ferry.

\subsubsection{\Gls{Herrena} is ambushed by \Gls{Cohen} and the \Gls{Lugg}}
\Gls{Herrena} asks her men to seize the ferryman, growing suspicious of his voice, as \Gls{Cohen}
takes off his robe, and fights the mercenaries. The \Gls{Lugg} terrifies \Gls{Weems} by emerging
from the river, as \Gls{Rince} escapes his captor's grip, and runs into the bushes. A while later,
\Gls{Herrena} is knocked out by a log thrown by \Gls{Bethan}, and the rest of the mercenaries
scatter in the absence of their leader.

\subsubsection{\Gls{Cohen} leads the party to a nearby town}
\Gls{Cohen} and \Gls{Bethan} announce their desire to get married, and lead the group to a nearby
town hoping to find a priest who might officiate the ceremony. \Gls{Rince} tries and fails to warn
\Gls{Cohen} about the age-gap between himself and \Gls{Bethan}, before giving up and tagging along.
In the city, they notice the people evacuating to the mountains, with rumours about the red star's
arrival spreading like wildfire.

\subsubsection{\Gls{Rince} is surrounded by doomsday cultists}
\Gls{Rince} notices huge red stars painted on the temples in the city, as well as the foreheads of
the people left in it. As a doomsday preacher starts his speech, \Gls{Death} appears next to
\Gls{Rince} to bemoan the formation of cults. The mob starts to corner \Gls{Rince}, accusing him of
being a wizard, and revealing that they had killed all of the city's wizards a few days ago.

\subsubsection{\Gls{Rince} is dragged away from the temples by \Gls{Twofl} and \Gls{Bethan}}
The Great Spell within \Gls{Rince}'s mind emerges, to incinerate one of the cultists, leaving him
in a state of shock at casting his first ever spell. \Gls{Bethan} and \Gls{Twofl} try to run off
with \Gls{Rince} into the city's alleyways, only to be trapped in a dead end, with a mob of
cultists closing in. \Gls{Twofl} notices the vanishing shop appear in the brick wall where the
dead end was, causing the cultists to run away.

\subsubsection{\Gls{Cohen} gets new dentures made at a goldsmith's shop}
\Gls{Cohen} is busy with a dwarven goldsmith, trying to get some dentures made from the diamong
tooth that the \Gls{Lugg} had broken when coming out of \Gls{OldG}'s mouth. A group of cultists try
to intimidate the dwarf, claiming that the Red Star might spare the Discworld if they eliminated all
magical races. \Gls{Cohen} deals with the cultists, while the dwarf packs up his valuables and
readies to flee the town.

\subsubsection{\Gls{Cohen} and \Gls{Lackjaw} reunite with the \Gls{Lugg}}
\Gls{Cohen} runs away from more cultists, wondering why they burned all the magical books, instead
of using the pages judiciously as fuel during the winter. Eventually he runs into a dead end with
\Gls{Lackjaw}, the dwarven goldsmith, and finds the \Gls{Lugg} staring intently at a brick wall.
\Gls{Lackjaw} believes \Gls{Cohen} is going insane, as the old man talks to the \Gls{Lugg}, only
to see it run into the brick wall, causing it to collapse.

\subsubsection{\Gls{Rince} wakes up inside the wandering shop}
\Gls{Twofl} is taken by a cigarette holder in the dusty shelves of the wandering shop, as the
\Gls{Shopk} emerges from a counter, to berate him for fiddling with the goods. Meanwhile,
\Gls{Rince} slowly wakes up from his haze, angry that the Great Spell had stopped him from
memorizing other spells, and experiencing the pleasure of exercising magic.

\subsubsection{\Gls{Rince} asks the \Gls{Shopk} to let them out in Ankh-Morpork}
\Gls{Bethan} intimidates the \Gls{Shopk} into getting some water for \Gls{Rince}, as he bemoans the
spread of the red star cult across Discworld. The \Gls{Shopk} prepares to send \Gls{Rince} and his
companions back to Ankh-Morpork, as \Gls{Atuin} fights the influence of the red star, in its swim
through space.

\subsubsection{\Gls{Twofl} listens to the \Gls{Shopk} narrate his sad tale}
At his miniature model of the universe, the \Gls{Shopk} talks to \Gls{Twofl} about insulting a
wizard long ago, and being cursed to wander in the shop forever, traveling the multiverse with no
way to settle down, except to run into the same wizard again and give him what he was in search of.
\Gls{Twofl} commiserates with him, as he thinks back to the different shop from which he had
purchased the \Gls{Lugg}

\subsubsection{\Gls{Twofl} and his party land in Ankh-Morpork}
The \Gls{Shopk} hands \Gls{Twofl} his fancy cigarette holder, as he kicks them out onto an empty
street in Ankh-Morpork, before running back into his shop and vanishing. \Gls{Twofl} tries to
explain to \Gls{Bethan} that \Gls{Rince} not being afraid of the approaching red star must mean it
does not pose the slightest threat, as she grumbles about \Gls{Cohen}. They get swept away by a
procession of cultists marching through the city.

\subsubsection{\Gls{Trymon} initiates the ritual to open the Octavo}
Beneath the Unseen University, \Gls{Trymon} leads the inner council to the lead-lined chamber
holding the Octavo, as they prepare to open it using \Gls{GalderW}'s invocation. Outside its main
gate, the cultists demand that the wizards commit mass suicide, to rid the world of the approaching
red star, as \Gls{Rince} guides his party to a secret entrance in a narrow alleyway.

\subsection{}
\subsubsection{\Gls{Trymon} steals the Octavo from the council of Wizards}
\Gls{Trymon} locks the others in the council within the lead chamber, as he runs out with the
Octavo. He tries to ignore the mind-tricks being played by the book, and marches to his room in the
main level. Meanwhile, \Gls{Rince} hears the main gate being torn down by the cultists, and decides
to head for the safety of the underground cellars.

\subsubsection{\Gls{Rince} manages to rescue the council of Wizards from the Octavo's chamber}
\Gls{Rince} investigates the banging downstairs, and runs into the council of Wizards locked in
the lead-lined chamber underground. He uses the Great Spell's residual power to open the magical
lock, and \Gls{JigladW} comes out bemoaning the theft of the Octavo by \Gls{Trymon}. They run into
the Great Hall, to find the Dungeon Dimensions bleeding into the terrace of the Tower of Art, and
believe that \Gls{Trymon} has started to memorize the Great Spells one by one.

\subsubsection{\Gls{Rince} and \Gls{Twofl} march off into the Tower of Art}
\Gls{Rince} watches \Gls{Twofl} disappear into the tower's base, and decides against his better
judgment to follow him. \Gls{Bethan} scolds the council into helping them, even as they feel their
magic weaken with the closing of the red star. Eventually they catch up to \Gls{Twofl} and
\Gls{Rince} half-way up the spiral staircase, as the empty Octavo falls down on them.

\subsubsection{\Gls{Rince} confronts \Gls{Trymon} at the top of the Tower of Art}
\Gls{Rince} reaches the top of the tower, only to find the council of wizards standing very still
around \Gls{Trymon}, who is unchanged, except for his eyes being hollow pits through which a strange
force seems to be leaking. \Gls{Trymon} declares himself the elected leader of all eight Orders,
and threatens \Gls{Rince} with death, unless he surrenders the Great Spell in his mind.

\subsubsection{\Gls{Rince} defeats \Gls{Trymon} using brute force}
\Gls{Rince} fights \Gls{Trymon} with just his fists and knees, and is transported to an arena in
the Dungeon Dimension, where \Gls{Trymon} presents in his beastly form. \Gls{Rince} gains the upper
hand by tearing open a weak point in the monstrous exoskeleton of \Gls{Trymon}, bringing the two of
them back to Discworld, and resuming time. \Gls{Trymon}'s body falls into the spiral staircase, and
is destroyed, leading to the seven Great Spells in his mind returning to the Octavo.

\subsubsection{\Gls{Cohen} rescues \Gls{Rince} and \Gls{Twofl} at the top of the tower}
\Gls{Cohen} saves \Gls{Rince} from falling down the tower's staircase, and immediately gets to work
cutting the rings out of the stone statues that the council of wizards had been reduced to.
\Gls{Rince} forces the Great Spell to evacuate his head, and return to the Octavo, before starting
the ritual of reading out all eight spells.

\subsubsection{\Gls{Bethan} spots the problem with \Gls{Rince}'s ritual}
An audience of cultists and citizens gather to see \Gls{Rince} pronounce the eight Great Spells,
only for an anticlimactic end to the ritual. \Gls{Bethan} spots a possible mistake in the
pronunciation of the esoteric languages within the book, and asks him to try again. \Gls{Twofl}
accidentally provides the correct pronunciation, making the Octavo buzz with power, and fly off into
the sky.

\subsection{}
\subsubsection{The Octavo is swallowed by the \Gls{Lugg}}
The Octavo wisely chooses to be swallowed by the \Gls{Lugg} as it comes back down from the sky,
after triggering the hatching of baby Discworlds, filling \Gls{Atuin}'s mind with joy at the
completion of its reproductive cycle. The red star and the baby turtles orbiting it drift away,
with \Gls{Twofl} deciding to head back home to the Agateam Empire.

\subsubsection{\Gls{Rince} prepares to re-enroll at the Unseen University}
\Gls{Twofl} gifts the \Gls{Lugg} to \Gls{Rince} after emptying it of all his possessions, and gives
a bag of gold as a wedding gift for \Gls{Cohen} and \Gls{Bethan}. \Gls{Rince} tries to dismiss the
\Gls{Lugg}, before realizing it was incapable of existing without a master. He reluctantly asks it
to follow him into the University, as he prepares to re-enroll, his mind now free from the clutches
of the Great Spell.


\section{Sourcery}


\subsection{}
\subsubsection{\Gls{Ipslore} mourns the death of his wife}
\Gls{Ipslore} waits with his eighth child next to his burnt house, as \Gls{Death} comes to claim
his soul. He tells \Gls{Death} that he is leaving his octiron staff as a final gift for his
child, and decides to force a destiny upon him. \Gls{Death} advises against it, as \Gls{Ipslore}
curses the wizards of Unseen University for ostracizing him and his wife, forcing them to run to
the edge of the civilized world.

\subsubsection{\Gls{Ipslore} makes one last desperate play to evade \Gls{Death}}
\Gls{Death} takes \Gls{Ipslore} with a lightning bolt to his head, just as the wizard hands his
staff to his infant son. This results in his soul being trapped in the staff, which \Gls{Death}
cannot destroy, lest he interfere with the child's destiny. \Gls{Ipslore} agrees to the loophole
that his son willingly giving his staff away would lead to his downfall from the Archchancellorship
of the University, lording over the same wizards that had excommunicated \Gls{Ipslore}.

\subsubsection{\Gls{Rince} tries to report his findings to \Gls{Spelter}}
\Gls{Rince}, now assistant librarian to the orangutan in charge of the tomes, notices the
creatures in the university fleeing it in a panic, and runs to the bursar's office to investigate.
In his office, \Gls{Spelter} dismisses \Gls{Rince}'s concerns about the foundations trembling, and
the rats fleeing, while offering him some alcohol to calm down.

\subsubsection{\Gls{Rince} escapes the University compound with the \Gls{Lugg} and the \Gls{Libra}}
Out on the University lawn, \Gls{Rince} watches the insects and pests flee the University, along
with the stone gargoyles usually perched up on the rooftops. He goes to his quarters in the library
and wakes the \Gls{Lugg} up from its winter hibernation, and prepares to flee the University,
dragging the \Gls{Libra} with him.

\subsubsection{The Sourceror deals with the wizard set to become the new Archchancellor}
The Sourceror walks to the front entrance of the University, just as the wizards prepare for the
feast of Small Gods' Eve. Meanwhile, the Archchancellor-elect is ambushed in his room by some
unknown wizard, just as the thief lurking in the corridors reaches his chamber. The thief finds the
leather box he is in search of, and opens it to hear a faint voice berating him for being late.

\subsubsection{\Gls{Rince} bemoans his inability to prosper within the University system}
At the Mended Drum, \Gls{Rince} talks fondly of his memories as a child, learning about the old
ways of magic, before the University had formalized it into a system of academic instruction.
The \Gls{Libra} listens half-heartedly, busy nursing its beer, as the \Gls{Lugg} tries to steal
snacks from the other patrons.

\subsubsection{\Gls{Spelter} watches \Gls{Coin} interrupt the crowing of the Archchancellor}
\Gls{Spelter} leads the wizards in the banquet hall as they prepare to welcome the Archchancellor,
and is shocked to find a young boy in white robes burst in through the door, now reduced to a
glowing liquid. \Gls{Skarmer}, a member of the inner council of wizards, tries to ask the boy why
he has barged into the University, and is amused to learn that the boy \Gls{Coin} wants to duel the
strongest wizard present in the hall.

\subsubsection{\Gls{Coin} shocks the assembled wizards by one-upping \Gls{Skarmer}}
\Gls{Skarmer} summons a pocket-dimension created by one of the last sourcerors, a feat considered
difficult even by the standards of eighth-level wizards. He finishes summoning the spherical
orb containing the garden, and is annoyed to see \Gls{Coin} complain about its size. \Gls{Coin}
manages to transport all of the wizards gathered in the dining hall to the pocket dimension, before
returning to them to the University, and making \Gls{Skarmer} vanish in a cloud of smoke.

\subsubsection{\Gls{Spelter} recommends a negotiated truce with \Gls{Coin}}
After letting \Gls{Coin} sit on the Archchancellor's chair per his wishes, and sending him to bed
with a hearty meal, the council of Wizards sit down to debate their future. \Gls{Spelter}, surprised
to see them so rattled that they take his opinion seriously, starts to talk about letting the boy
sit on the ceremonial chair, and guiding his decision-making instead of confronting him head-on.

\subsubsection{\Gls{Carding} and \Gls{Spelter} decide to enter an uneasy alliance}
\Gls{Carding}, one of the council members, shows support for \Gls{Spelter}'s idea, and dismisses
the other senior wizards for the night. \Gls{Carding} and \Gls{Spelter} stay in the meeting hall,
and launch surprise attacks at each other simultaneously. They agree reluctantly to a temporary
truce in trying to mould the boy's mind, fully realizing that betrayal lurked around the corner
waiting for either of them lose their utility.

\subsubsection{\Gls{Carding} talks about the end of sourcery at large}
\Gls{Carding} reveals the old legends of wizards being able to birth sourcerors as their eighth
child, and of how the Gods had found it terribly inconvenient to have such powerful beings on the
Discworld to interfere with their plans. He asks for the enchanted hat of the Archchancellor to
be retrieved, so that they might crown \Gls{Coin}, and continue to shape his mind as they see fit.

\subsubsection{The thief with the Archchancellor's hat forcibly drags \Gls{Rince} along with her}
The mysterious thief who had stolen the Archchancellor's hat from the University greets \Gls{Rince}
in the Mended Drum, and asks him to take on a mission. He declines, telling her he has had his
fill of adventure, just as the \Gls{Patri}'s guards show up to arrest her. A bar fight breaks out,
allowing the two of them to escape upstairs, and escape through a window.

\subsubsection{\Gls{Conina} leads \Gls{Rince} to the Shades district}
The \Gls{AHat} tells \Gls{Rince} that terrible events are in progress at the University, and that
it needs to be taken to Klatch, as soon as possible. The female thief sets off down an alley,
intent on walking into the run-down criminal district of Ankh-Morpork, and makes short work of
the petty thieves that accost them on their way in. She introduces herself as \Gls{Conina}, and
heads into an inn at the center of the district.

\subsubsection{The \Gls{AHat} defends itself from a petty thief}
Someone steals the box containing the \Gls{AHat} from \Gls{Rince}, during the minor scuffle that
breaks out in the tavern, with \Gls{Conina} hurrying out into the back-alley in pursuit. The thief
gets frozen to death by the \Gls{AHat}'s own magic, with \Gls{Rince} accidentally toppling the
frozen man, and making him shatter. \Gls{Conina} notices more criminals start to take an interest
in the \Gls{AHat}, and asks \Gls{Rince} to keep moving.

\subsubsection{\Gls{Conina} and \Gls{Rince} reach the city docks}
\Gls{Conina} explains that she is \Gls{Cohen}'s daughter, and that she has inherited his mad urge
to steal, and his impulse to greet strangers with a knife to the throat. \Gls{Rince} muses that it
must be great for an aspiring barbarian to have these qualities, and she reveals that her dream is
to be a hairdresser, in complete opposition to her violent instincts.

\subsubsection{The \Gls{Lugg} is reunited with \Gls{Rince}}
The \Gls{AHat} tells \Gls{Rince} that it represents the combined power of every archchancellor at
the Unseen University, going back millennia. It uses its magical persuasion to force him to find a
ship ready to sail out of the city, as the \Gls{Lugg} slowly ambles up to them, with many crossbow
bolts and swords sticking out of its body.

\subsubsection{\Gls{Spelter} and \Gls{Carding} talk about the sourceror infusing magic into the
    University}
At the Unseen University, the aura of sourcery seeping into the campus enables the wizards to
perform feats of magic they had only every dreamt of. The \Gls{Libra} locks himself in the main hall
of the library, and reads the history of sourcerors with growing alarm. In the Great Hall,
\Gls{Carding} is pleased by the resurgence of magic into the University, and tells \Gls{Spelter}
that wizarding levels and orders are no longer meaningful.

\subsubsection{\Gls{Coin} makes some changes in the Great Hall of the University}
\Gls{Coin}'s staff flings \Gls{Carding} across the Great Hall when he dares to touch it without
the boy's permission. \Gls{Coin} warns him not to touch the staff, as he sets about redoing the
Great Hall's architecture, turning it into a well-lit modern lobby, complete with glass windows and
marble pillars.

\subsubsection{\Gls{Hakar} is chastised by \Gls{Coin}}
\Gls{Hakar}, a scholar of magical lore, confronts \Gls{Coin}, reminding him of the traditional
process of selecting an archchancellor. \Gls{Coin} in turn, ridicules the wizards, calling them
little more than insects fighting over their few acres of land in the city, and leaving the
\Gls{Patri} to wield real power in the outside world.

\subsubsection{\Gls{Vetina} is teleported against his will to the University}
In the palace of Ankh-Morpork, the \Gls{Patri} reads the latest intelligence reports from his
network of spies, as he thinks back to the centuries of trading-guilds ruling over the city.
As the head of the \Gls{Vetina} family, he thinks about the headache of administering the city,
as he is suddenly teleported to the renovated Great Hall of the University.

\subsubsection{\Gls{Carding} transmutes the \Gls{Patri} into a lizard}
The \Gls{Patri} gets angry at \Gls{Carding} as his pet dog, which was also transported with him,
growls at the octiron staff in \Gls{Coin}'s arms. \Gls{Carding} orders the \Gls{Patri} to be
imprisoned in the wine cellars under the University, reminding him that the wizards had finally
awakened to their true power. He accidentally morphs the \Gls{Patri} into a lizard, and is pleased
at the power now available to him.

\subsection{}
\subsubsection{\Gls{Conina} spots Klatchian slavers approaching their ship}
\Gls{Conina} gives \Gls{Rince} a haircut on board the ship sailing to Al Khali, on the coast of
Klatch across the Circle Sea. She spots some slaver ships approaching them in the distance using
her superhuman vision, leaving \Gls{Rince} to confirm the grim news with the \Gls{AHat}. It asks
him to wear the hat, so that it might use his eyes to see into the distance.

\subsubsection{\Gls{Rince}'s ship is set upon by Klatchian slavers}
On wearing the \Gls{AHat}, \Gls{Rince} sees the dead archchancellors staring at him through his
mind, and is overwhelmed by their combined experience weighing down on him. He takes it off, in
time to hear the alarm being rung as the slaver boats close in. The slavers manage to subdue the
ship's crew using blunt weapons, with the leader making for the afterdeck, where \Gls{Rince}
and \Gls{Conina} are hiding.

\subsubsection{\Gls{Conina} and the \Gls{Lugg} deal with the slavers}
The head slaver talks to \Gls{Rince} about the opportunity of being a eunuch in the emperor's
harem, as the only viable path for a physically feeble wizard, as \Gls{Conina} uses the distraction
to kill his bodyguards. The \Gls{Lugg} swallows the head slaver, trapping him in its pocket
dimension, as \Gls{Conina} jumps down to the main deck, to kill the rest of the slavers.

\subsubsection{The wizards emerge into the city from the gates of the University}
In the city square next to the Unseen University, the stalls and tenements that had sprouted up
over the years are all pushed away by a magical shockwave, with one enterprising merchant made to
vanish for daring to question the wizards marching out of the gates. The rest of them see the
wizards materialize fresh food out of thin air, and realize their livelihoods are under threat in
addition to their lives.

\subsubsection{\Gls{Rince} decides to help the \Gls{AHat} after it is captured by the slavers}
\Gls{Conina} tells \Gls{Rince} that the slavers fled with the \Gls{AHat}, and that they were
likely taking it to Al Khali. \Gls{Rince} initially decides to leave the \Gls{AHat} to its fate,
before his conscience bullies him into going into the city to rescue it.

\subsubsection{\Gls{Spelter} presents his newly sewn archchancellor's hat to \Gls{Carding}}
At the University, the wizards discover the incompatibility of sourcery with intrinsically magical
things, such as their own bodies. \Gls{Spelter} hand-sews a replica of the \Gls{AHat}, which manages
to fool \Gls{Carding}'s critical eye. Meanwhile, the city of Ankh-Morpork receives a facelift,
with the grime and dirt magically swept away, leaving a clean city and sparkling river.

\subsubsection{\Gls{Coin} insists on a coronation ceremony for himself}
The inner council of wizards present the new archchancellor's hat to \Gls{Coin}, who insists on a
grand coronation ceremony, so that the world might know of the true power of wizardkind. He tells
\Gls{Carding} that the wizards living in far away lands will now have the gift of his sourcery to
transport themselves instantly to the site of the new coronation. He also intends to move his seat
of power to a newly constructed palace, condemning the University as a symbol of weakness.

\subsubsection{\Gls{Coin} almost detects the dissent taking shape in \Gls{Spelter}'s mind}
\Gls{Coin} reminds the wizards that they no longer had to depend on dusty tomes and arcane rituals
to perform magic, since he had given them the gift of sourcery. \Gls{Spelter}'s mind starts to
remember the old ways fondly, but \Gls{Carding} stomps on his toes just as he prepares to voice his
nostalgia. The city is put under a midnight curfew, with the citizens being forced to enter a
magical slumber at the appropriate time.

\subsubsection{\Gls{Spelter} talks to the \Gls{Libra} about the possible shuttering of the Library}
\Gls{Spelter} creeps through the University corridors at night, to warn the \Gls{Libra} about the
impending closure of the Library. The \Gls{Libra} tells him about a secret entrance that it uses to
go in and out of the sealed Library, and reassures him that it is keeping the \Gls{Patri} safe in a
glass jar. On his way back to his chambers, \Gls{Spelter} decides to investigate some quiet sobs
coming from the rooms of a senior wizard.

\subsubsection{\Gls{Rince} and \Gls{Conina} get surrounded by thugs in Al Khali}
\Gls{Rince} and \Gls{Conina} reach the Temple of Al Khali, with its famous frescoes and carvings,
while thinking about the best way to track down the \Gls{AHat}. Eventually, \Gls{Conina} decides to
seek out the criminal district, hoping to be ambushed by someone with knowledge of the slavers.
They are ambushed by some thugs armed with crossbows, leading \Gls{Conina} to recall her father's
words about projectile weapons and impossible odds.

\subsubsection{\Gls{Coin} builds the new wizard stronghold out of pure magic}
\Gls{Spelter} tries to tell \Gls{Carding} about the sobbing from last night, but is brushed off,
as \Gls{Coin} is busy crafting a new home for the wizards. He puts the final touches on the
stronghold, before opening a portal to it using his staff. In the oxbow bend of the Ankh river,
\Gls{Coin} summons the new fortress, rising high in the air, and made of solidified magic.

\subsubsection{\Gls{Coin} wishes the death of the wizarding system}
\Gls{Coin} declares his coronation will take place in a week, and that he will force a full moon
on the appointed day. \Gls{Spelter} suppresses the dissent in his heart, and plays along with
\Gls{Coin}'s plan to dissolve the wizarding system, as well as burn down the Library in the
University.

\subsubsection{\Gls{Spelter} is chased by \Gls{Ipslore} through the university's basement}
\Gls{Spelter} is cornered by the \Gls{Ipslore}, trapped in the octiron wand, as he tries to warn
the \Gls{Libra} about the destruction of the Library. He tries to run into the underground kitchens,
but \Gls{Ipslore} keeps up with him easily, melting the cleaver that he attempts to use in
self-defense.

\subsubsection{\Gls{Conina} and \Gls{Rince} sit in \Gls{Creo}'s garden}
\Gls{Conina} and \Gls{Rince} are brought to a walled garden in the middle of Al Khali, where the
mayor of the city, \Gls{Creo}, introduces himself. He orders his men to back off, and offers food
and drink to his guests. \Gls{Rince} recognizes him as the son of the famed assassin, who was
rumoured to be richest man on the Disc. He summons his Grand Vizier \Gls{Abrim}, who reminds the
mayor that the \Gls{AHat} had warned them about the arrival of these two foreigners.

\subsubsection{\Gls{Abrim} decides to talk to the \Gls{AHat} directly}
\Gls{Abrim} has \Gls{Conina} escorted to the seraglio, as \Gls{Rince} is interrogated about the
nature of the \Gls{AHat}. Eventually, the \Gls{AHat} decides to communicate telepathically with
\Gls{Abrim}, promising him a favourable bargain if he were to cut the wizard out of the negotiation.
\Gls{Rince} gets thrown in the snake pit, where he meets a barbarian, wearing woolen underwear.

\subsubsection{\Gls{Rince} accidentally helps \Gls{Nijel} break open a wall in the snake pit}
The \Gls{Lugg} walks into a bar on the outskirts of Al Khali, and gets drunk on the powerful local
liquor, to deal with its separation from \Gls{Conina}. Meanwhile, \Gls{Rince} learns that the
teenage barbarian is named \Gls{Nijel}, and notices the lone snake in the pit trying its best to
go unnoticed. \Gls{Nijel} attempts to open a weak stone block in the wall, and \Gls{Rince} is
shocked that his subconscious attempt to summon magic works, with a fireball blasting the wall
apart.

\subsubsection{\Gls{Rince} and \Gls{Nijel} make it to the palace grounds}
\Gls{Rince} manages to use the magical energy gathering in the palace to summon an elevator to
the surface, where \Gls{Nijel} notices a tall tower erupting from the ground. \Gls{Rince} notices
some familiar old wizards marching out of the white tower, making short work of \Gls{Creo}'s
guards, as they attempt to rush them with swords and sickles. \Gls{Nijel} is horrified by the
dismissive way in which the wizards kill the armed thugs, prompting \Gls{Rince} to ask if this was
the first time he was witnessing murder.

\subsection{}
\subsubsection{\Gls{Nijel} and \Gls{Rince} refocus on rescuing \Gls{Conina}}
\Gls{Nijel} suggests \Gls{Rince} to stop wearing his wizard robes and hat, if he is worried about
being hunted down along with the newly ascended wizards from Ankh-Morpork. \Gls{Rince} is horrified
by the idea, and eventually remembers his original objective of rescuing \Gls{Conina} from the
seraglio. Searching through the palace corridors, they eventually find the entrance to the
seraglio, with only a few guards left inside to protect the women.

\subsubsection{\Gls{Sconn} leads a party to the Library, with orders to burn it down}
A squad of wizards, led by \Gls{Sconn} are tasked with burning down the Library of the Unseen
University, in the middle of the night. \Gls{Sconn} makes quick work of the heavy door leading into
the Library, and asks his men to prepare their matchsticks. One of the wizards spots something
moving close to the domed ceiling.

\subsubsection{\Gls{Sconn} is thrashed by the \Gls{Libra}}
\Gls{Sconn} is attacked by the \Gls{Libra}, and thrown out of the Library with enough force to
bowl over the other wizards cowering in fear. They remind him of the risk in using magic next to
the tomes kept in the Library, and prepare to find some flammable oil to systematically burn down
the bookshelves.

\subsubsection{\Gls{Nijel} and \Gls{Rince} are reunited with \Gls{Conina}}
\Gls{Nijel} manages to perform some sword acrobatics using the guide to barbarian lifestyle written
by \Gls{Cohen}, but manages to get his sword stuck in the ceiling. The harem guards close in on
him, until \Gls{Conina} arrives and sneakily stabs them from behind. \Gls{Rince} is relieved that
he did not have to resort to magic again, as he notices \Gls{Conina} and \Gls{Nijel} staring at
each other, lovestruck.

\subsubsection{\Gls{Conina} and \Gls{Nijel} are smitten with each other}
\Gls{Conina} privately threatens \Gls{Rince} not to reveal her parentage to \Gls{Nijel}, as she
talks about the mayor asking her to tell him stories, as part of her duties in the harem. For his
part, \Gls{Nijel} begs \Gls{Rince} not to reveal how much of a novice he is. Meanwhile, the
\Gls{Lugg} wakes up from its drunken stupor, despondent at being banished by \Gls{Conina}. It
drifts down the Tsort river, and is ambushed midway by some logs.

\subsubsection{\Gls{Rince} and his party reach the sourceror's tower in Al Khali}
At the new tower of sourcery in Al Khali, \Gls{Rince} notices the city guards being transfigured
into small reptiles and rodents, with the architecture being slowly converted into the white marble
preferred by \Gls{Coin}. As they argue about confronting the wizards in the tower, \Gls{Abrim}
steps out of a ruined building, wearing the \Gls{AHat}.

\subsubsection{\Gls{Rince} and his party are mind-controlled by the \Gls{AHat}}
The \Gls{Lugg} shakes off the crocodile ambush, and trots through the desert, reaching a basilisk's
hunting grounds. The beast tries to stare down the \Gls{Lugg} with its magical sight, supposed to
petrify any souls caught in it, and feels the sudden urge to blink. Meanwhile, the \Gls{AHat}
declares its intent to use \Gls{Abrim} as a useful host, and mind-controls \Gls{Rince} into
marching against the sourcerors, along with his companions.

\subsubsection{\Gls{Rince} recalls the history of the Mage Wars}
\Gls{Rince} recounts the story of the Mage Wars aeons ago, with common people being caught in the
crossfire as evenly matched wizards unleashed weapons of mass destruction on each other, stretching
the fabric of reality to its very limit. The \Gls{Lugg} deals with the basilisk, and then a chimera
that ambushes it. It decides to give up the life of freedom, and seek out a master.

\subsubsection{\Gls{Abrim} becomes the \Gls{AHat}'s unwitting host}
\Gls{Abrim}, now possessed by the \Gls{AHat}, seeks out a fight at the entrance to the sourceror's
tower. A wizard shows at the gate, and challenged \Gls{Abrim} to a magical duel. \Gls{Abrim} tells
him that he can also harness sourcery using his centuries of knowledge, and shrugs off all the
magic thrown at him. The \Gls{AHat} lets \Gls{Rince} and his companions loose from its mind-control,
as it focuses on destroying the wizards holed up in the tower.

\subsubsection{\Gls{Rince} and his party meet up with an intoxicated \Gls{Creo}}
\Gls{Rince} and his party run from the magical overload taking over the space around the tower,
and find \Gls{Creo} waking up from a stupor, surrounded by the rubble of his palace. He tells them
that he has never stepped out of his palace grounds, and has no idea where his famed horse stables
are located. Eventually, \Gls{Creo} regains his composure enough to remember the fact that his
magic carpet is in the treasury, causing \Gls{Rince} to recoil in horror.

\subsubsection{\Gls{Rince} and his party traverse the tunnel into the treasury}
The \Gls{Lugg} manages to evade the collateral damage from the Mage War erupting in Al Khali, and
climbs out of the Tsort river, to pursue its new master. Meanwhile, \Gls{Creo} takes \Gls{Rince}
and his party to the palace treasury, where a secret tunnel hidden behind a statue of \Gls{Offler}
leads to the room containing magical artifacts.

\subsubsection{\Gls{Rince} and his party are trapped in the treasury}
\Gls{Rince} is amused by the silly traps laid by \Gls{Creo}'s grandfather, the original architect
of the palace and treasury, until the tunnel roof collapses, trapping him and his party in the
treasury. \Gls{Conina} looks at the magic carpet, lamp and gold ring on a central pedestal, as
\Gls{Creo} mumbles something about his grandfather using those artifacts to build his fortune.

\subsubsection{\Gls{Rince} commandeers the magic carpet, and escapes the collapsing palace}
\Gls{Rince} manages to figure out how the magic carpet works, by speculating that it was programmed
to fly in the opposite direction of any commands spoken to it. He escapes the treasury with his
party, just as the stones of the palace are broken off by the \Gls{AHat}, and magically reassembled
to create a new tower where the sourcerors had formerly assembled their own. \Gls{Rince} believes
that the \Gls{AHat} has won the first battle, and is consolidating its power in Al Khali, before
venturing out into the rest of the Disc.

\subsubsection{\Gls{Rince} negotiates with his conscience on board the magic carpet}
\Gls{Rince} thinks about the helplessness of the common-folk in the Disc, in the face of another
Mage War, as he realizes his conscience is flying the carpet bypassing his conscious mind. It
chastises him for trying to run away from the sourceror at the root of the magic saturating the
world, instead of confronting him, even at the cost of his own life.

\subsubsection{\Gls{Rince} sleepwalks to the waterline, trying to assemble a stone tower}
\Gls{Rince} manages to land the carpet on the coast of the Circle Sea, with \Gls{Conina} building a
simple campfire to allow them to take turns sleeping. She wakes the other up in the middle of the
night, to point out \Gls{Rince} sleepwalking to and from the beach, subconsciously assembling a pile
of stones to build a tower.

\subsubsection{\Gls{Rince} slips away from his party on the magic carpet}
\Gls{Rince} gets shaken awake by \Gls{Nijel}, and notices the magical artillery being exchanged
across the Circle Sea. As the others get busy arguing about the value of wizards to the Disc,
\Gls{Rince} sneaks off with the magic carpet, intent on flying across the Sea to some abstract
enemy waiting in Ankh-Morpork.

\subsubsection{\Gls{Abrim}'s ritual in Al Khali is interrupted by a knock on the door}
In the wizards' tower of Al Khali, \Gls{Abrim} is busy channelling the raw power originating from
the others now subservient to him, as he hears a knock on the door. Surprised at the possibility
of any living thing being left unscathed by the reality-bending effects of their ritual, one of the
junior wizards opens the door to investigate.

\subsubsection{\Gls{Rince} returns to the revamped Ankh-Morpork}
\Gls{Rince} comes out of his angry haze midway to Ankh-Morpork, and realizes the Mage Wars would
eventually lead to the extinction of all life on the Disc. He lands in his home city, and finds it
unrecognizable, alarmed by the cleanliness and orderliness of the streets. He sees the University
deserted, and heads for the ruins of the Library, frantically trying to find the \Gls{Libra} in the
burnt rubble.

\subsubsection{\Gls{Nijel} uses \Gls{Creo}'s magic lamp to summon a \Gls{Genie}}
\Gls{Nijel} pulls out the magic lamp he had nicked from the treasury, as \Gls{Creo} argues with
\Gls{Conina} about their carelessness in allowing \Gls{Rince} to escape. He rubs it and summons a
\Gls{Genie}, in spite of \Gls{Creo}'s insistence that the original lamp that his grandfather had
used to build his fortune was a different one.

\subsection{}
\subsubsection{\Gls{Conina} threatens the \Gls{Genie} into obeying their command}
The \Gls{Genie} tries to get out of his obligations to \Gls{Nijel}, intent on securing his next
home in a lamp-shop, close to the harbour of Ankh-Morpork. \Gls{Conina} threatens the \Gls{Genie}
with the destruction of the lamp, making it take their request seriously. It tells them that it has
little experience with teleportation, and agrees to try to send them to Ankh-Morpork regardless.

\subsubsection{\Gls{Nijel} and his party travel to Ankh-Morpork inside the \Gls{Genie}'s lamp}
\Gls{Nijel} figures out the fact that the \Gls{Genie} has imprisoned them in the lamp, which is
being carried by another version of himself. The \Gls{Genie} tries to explain that this fractal
trick only works as long as the universe fails to catch on to the deception, as \Gls{Nijel} starts
to think really hard about the logistics of their trip to Ankh-Morpork.

\subsubsection{\Gls{Rince} meets up with the \Gls{Libra} and the remnants of the Library}
\Gls{Rince} finds the \Gls{Libra} holed up in the Tower of Art, now abandoned by the wizards, and
is shocked to learn that the tomes of magic all flew away from the Library, to seek refuge in the
tower. He finds the \Gls{Patri} safe in his glass jar, and his pet dog licking his boots. The
\Gls{Libra} gets to work repairing some damaged tomes, as \Gls{Rince} hands it surgical tools from
at impromptu operating table.

\subsubsection{\Gls{Rince} tries to crawl away from his mission to defeat sourcery}
\Gls{Rince} agrees with the \Gls{Libra} that the emergence of sourcery would spell the end of the
world eventually, but insists that someone else should be the one to face the threat this time.
The \Gls{Libra} snatches his hat from him, and threatens to cut it with its shears, as \Gls{Rince}
watches on helplessly. It then places the hat back on his head, to remind him that his instincts
made him the best candidate to stand up to sourcery.

\subsubsection{\Gls{Conina} and her companions steal some horses}
\Gls{Conina} and her party are transported to the outskirts of Quirm, where they notice the Mage
Wars in progress, and the exchange of magical artillery with other strongholds across the Disc.
They find some horses tethered to the rear entrance of a tavern, and decide to steal them, unaware
of the fact that those steeds belonged to \Gls{Death} and his horsemen, currently busy drinking
themselves into a stupor inside the inn.

\subsubsection{\Gls{Carding} defeats \Gls{Abrim} and the \Gls{AHat}}
\Gls{Carding} starts to feel nostalgic about the world before the emergence of \Gls{Coin}, as he
defeats the wizards holed up in Quirm, from the stronghold newly constructed in Ankh-Morpork.
As the wizards under \Gls{Coin}'s control turn their attention to Al Khali, \Gls{Carding} manages
to find a weakness in \Gls{Abrim}'s mental defenses, making him vanish under the weight of the
\Gls{AHat}'s pressure, and causing a chain reaction within the \Gls{AHat}'s tower.

\subsubsection{\Gls{Carding} dies in his attempt to destroy \Gls{Ipslore}}
\Gls{Carding}'s mind returns to \Gls{Coin}'s tower, and he berates the sourceror for allowing
the denizens of the Dungeon Dimensions to appear in the Discworld, along with the flow of raw magic.
\Gls{Ipslore} incinerates \Gls{Carding} when he tries to destroy the staff, leaving the other
wizards stunned at the horror of his body melting into a puddle.

\subsubsection{\Gls{Death} rides away from his horsemen stuck at the tavern}
\Gls{Death} is affronted by his horsemen asking to ride pillion on his steed, and rides off to
harvest some more wizard souls. \Gls{War} and \Gls{Famine} are busy trying to figure out how to
get around, as \Gls{Pesti} raids the tavern's kitchen, looking for food. They decide to wile away
some more time drinking, disregarding the Mage Wars that required their presence.

\subsubsection{\Gls{Hakar} tries to dissuade \Gls{Coin} from  antagonizing the gods}
Meanwhile, \Gls{Hakar} tries to explain the Dungeon Dimension, and speculates that the gods in Cori
Celesti might soon be forced to act against the sourcery. \Gls{Coin} declares war against the gods,
dismissing \Gls{Hakar}'s fears about their power.

\subsubsection{\Gls{Rince} raeches the main chamber at the top of the sourceror's tower}
The \Gls{Libra} reminds \Gls{Rince} that he had the weight of saving the entire world on his
shoulders, as he sets out to confront \Gls{Ipslore} and \Gls{Coin} atop the white tower of the
sourceror. Meanwhile, \Gls{Coin} imprisons the gods in Cori Celesti in a small sphere the size of
a pearl, as \Gls{Rince} manages to reach the top of the tower on his magic carpet.

\subsubsection{\Gls{Rince} gets attacked by \Gls{Ipslore}, against \Gls{Coin}'s wishes}
\Gls{Rince} is puzzled by the famed sourceror being a small boy, and starts to explain the brick
inserted into his sock, that he intends to use as a lethal weapon. \Gls{Coin} resists
\Gls{Ipslore}'s orders to kill the diseenter, insisting that \Gls{Rince} is a harmless jester.
\Gls{Ipslore} flies out of \Gls{Coin}'s arms, and knocks \Gls{Rince} down by slamming into his head
at great speed.

\subsubsection{\Gls{Coin} stops \Gls{Ipslore} from killing \Gls{Rince}}
\Gls{Rince} sees \Gls{Death} materialize next to him, as he enters bullet time, waiting for
\Gls{Ipslore} to slam into his head for the last time. \Gls{Rince} asks \Gls{Death} which wizard's
soul he is here to harvest, and time resumes before he can get an answer. \Gls{Coin} grabs
\Gls{Ipslore} midway through his trajectory, and breaks it into two pieces. \Gls{Hakar} is convinced
that \Gls{Coin} and \Gls{Ipslore} are evenly matched, and recommends fleeing the tower.

\subsubsection{\Gls{Rince} decides to try and help \Gls{Coin} defeat \Gls{Ipslore}}
\Gls{Coin} and \Gls{Ipslore} are locked in a mental battle, \Gls{Rince}'s conscience forces him
to jump into the circle of magical fire to try and help the boy. \Gls{Hakar} and the others
levitate down from the tower, as \Gls{Rince}'s burning hat falls down to the ground, to be quickly
covered in a layer of snow. Meanwhile, the horsemen of \Gls{Death} lounge around in the bar,
having forgotten the Apocalypse that they were supposed to be supervising.

\subsubsection{\Gls{Nijel} recalls the stories about the Apocalypse}
\Gls{Conina} and her party manage to gain control of the flying horses, in time to see clouds
drifting over the land, bringing heavy snow. \Gls{Nijel} asks the \Gls{Genie} about the snow, and
learns that the fable Apocalypse has arrived, signified by the gods vanishing and the Ice Giants
reclaiming the Disc. The \Gls{Genie} decides to repossess his lamp, and vanishes from the Disc,
believing that the end of sentient life is imminent.

\subsubsection{\Gls{Rince} and \Gls{Coin} defeat \Gls{Ipslore}}
\Gls{Rince} wakes up in the Dungeon Dimensions, vaguely recalling \Gls{Death} claiming
\Gls{Ipslore}'s soul when he is distracted by the fight against \Gls{Coin}. He then finds some
Things busy trying to widen a portal into the Discworld so that they can invade, and shakes
\Gls{Coin} awake. Meanwhile, refugees start to return to Al Khali, sensing the end of hostilities
against the mages from Ankh-Morpork.

\subsubsection{\Gls{Nijel} tries to talk the Ice Giants out of their conquest}
\Gls{Nijel} and his party fly hubwards, to find the Ice Giants starting their migration across the
Disc, using their magic to push massive glaciers in front of them to grind down the land. He tries
to negotiate with one of the leaders of the Ice Giants, and is rescued by \Gls{Conina} when forced
off his horse.

\subsubsection{\Gls{Rince} helps \Gls{Coin} escape the Dungeon Dimensions}
\Gls{Rince} decides to use his other sock, after filling it with sand, to distract the Things,
allowing \Gls{Coin} to jump into the portal back to the Discworld. \Gls{Coin} makes it through,
with the \Gls{Libra} beating back a tentacle that wraps around his legs, and is astonished to see
the \Gls{Lugg} jumping into the portal after \Gls{Rince}. The portal flickers and closes, with the
\Gls{Libra} reminding him that \Gls{Rince}'s fate cannot be ascertained from here.

\subsubsection{The \Gls{Libra} frees the Gods of Discworld from their imprisonment}
\Gls{Coin} hands the pearl containing Cori Celesti to the \Gls{Libra}, who throws it far away,
hoping to break the spell of imprisonment by shattering it. The gods of the Discworld emerge, angry
at the Ice Giants for pre-empting their apocalypse, and intervene in the advance of the glaciers.
\Gls{Conina} and \Gls{Nijel} watch fascinated as the snow melts all of a sudden, and the glaciers
retreat back towards the hub.

\subsubsection{\Gls{Conina} and \Gls{Nijel} are turned away by \Gls{Coin} when they ask after
    \Gls{Rince}}
\Gls{Coin} tells \Gls{Conina} and \Gls{Nijel} a story about \Gls{Rince} successfully defeating
\Gls{Ipslore}, before using his magic to alter their memories. He sends them on their way to live a
happy life, and asks the \Gls{Libra} how he can live in Discworld, while resisting the urge to use
his magical powers to alter it. It reveals to him the eventual path chosen by all sourcerors, and
wishes him the best as he steps into a pocket dimension of his own creation.

\subsubsection{\Gls{Creo} and the \Gls{Patri} resume their lives}
\Gls{Creo} finds the daughter of the innkeeper at the Mended Drum eager to tell him all the stories
she knows, and believes he has found his paradise. Meanwhile, the \Gls{Patri} is back to his human
form, only missing his memories for the past few weeks. He struggles to control his instinctive urge
to swipe at some moths with his tongue. The \Gls{Libra} mounts the tattered remains of \Gls{Rince}'s
hat in the Library, hoping he will come back for it some day.


\section{(Faust) Eric}


\subsection{}
\subsubsection{\Gls{Death} senses someone in an alternate dimension running past his cottage}
In his realm, \Gls{Death} is disturbed from his beekeeping routine, by a strong gust of air blowing
through his cottage, and the faint sounds of someone running away from trouble. Meanwhile, the
\Gls{Libra} is startled in his makeshift hammock withing the ice chamber of the Library, as a
disembodied voice runs past him, to disappear into the walls.

\subsubsection{The disembodied voice runs through many places in Ankh-Morpork}
As the sun sets on a blistering summer day in Ankh-Morpork, more citizens hear the disembodied voice
run past them, and notice the magical after-effects left in its wake. The new Archchancellor of
Unseen University meets with his inner council at night, and decides not to take the haunting
seriously. The council members decide to let him rest for the night, and prepare to summon
\Gls{Death} for answers.

\subsubsection{\Gls{Death} tells the inner council of wizards that the ghostly voice is \Gls{Rince}}
The inner council of the University summon \Gls{Death}, who tells them that \Gls{Rince} is trying
to escape the Dungeon Dimensions, and is the cause of the voices they hear. The council members,
anxious that he might refute their alibis during the reign of the sourceror \Gls{Coin}, try to
brush off the escape as near impossible.

\subsubsection{\Gls{Rince} is summoned into the Discworld by a ritual}
\Gls{Rince} escapes the Dungeon Dimensions, as someone summons him to the Discworld using the ritual
used to conjure and bind demons to one's will. He tries to argue that he is human, and cannot be
banished back to the Dungeon Dimensions, but the summoner is adamant about the three wishes he
is now contractually obligated to receive.

\subsubsection{\Gls{Rince} realizes that \Gls{Eric} is a child pretending to be a wizened old man}
\Gls{Rince} learns that he is in Pseudopolis, and that \Gls{Eric} has summoned him by accident,
while looking for a demon that grants wishes. \Gls{Rince} recognizes the demonologist as a little
boy wearing an old man's disguise, just as his mother calls out from downstairs for dinner. After
\Gls{Eric} goes downstairs, leaving \Gls{Rince} confined to his room, the stuffed parrot speaks up,
revealing that \Gls{Eric}'s grandfather had been a prodigious demonologist long ago.

\subsubsection{\Gls{Rince} learns about the rules of demonology}
The \Gls{Parrot} reminds \Gls{Rince} that the rules binding demons would apply to him since he
emerged onto the Discworld using a demonic portal. \Gls{Rince} gets electrocuted by magic when he
tries to escape through a window, and settles down to wait for \Gls{Eric}'s return. Meanwhile, in
the city of Pandemonium, at the center of the Demon realm, Demon King \Gls{Astf} receives the news
that someone else went through \Gls{Eric}'s portal, causing it to close automatically.

\subsubsection{\Gls{Astf} determines the identity of the interloper}
\Gls{Astf} learns that \Gls{Eric}, a self-centered savant he had long hoped to seduce into the
demon world, using \Gls{Vassen} as his messenger, had successfully summoned someone else using his
ritual. In his private chamber, \Gls{Astf} uses his CCTV mirror to watch the events in \Gls{Eric}'s
room, and learns that the interloper's name is \Gls{Rince}. He bemoans the lack of a formal census
in the Demon world, so that he might cross-verify \Gls{Rince}'s identity.

\subsubsection{\Gls{Rince} is reunited with the \Gls{Lugg} in \Gls{Eric}'s room}
When the \Gls{Lugg} materializes in \Gls{Eric}'s room, the boy loses interest in setting \Gls{Rince}
free, and goes back to his earlier demands of world domination. \Gls{Rince} is shocked to find that
he can summon a miniature model of the Disc with a snap of his fingers, and is annoyed to see
\Gls{Eric} demand tribute from the kingdoms of the Disc.

\subsubsection{\Gls{Rince} teleports \Gls{Eric} and the party to Klatch}
\Gls{Rince} next teleports himself and \Gls{Eric} into the dense jungles of Klatch, where they
trek for a while, until they find some buildings of the Tezuman kingdom. \Gls{Rince} is surprised
when the Tezuman warriors bow down to \Gls{Eric}, as the \Gls{Parrot} expresses its satisfaction at
his demonic capabilities.

\subsubsection{\Gls{Eric} is celebrated by the Tezumen with a grand festival in his name}
The Tezumen procession brings \Gls{Eric} and \Gls{Rince} to one of the stone pyramids, with the
common-folk throwing coins and flowers at them, as if to celebrate a hero. \Gls{Rince} spots the
treasure chests lined up at the entrance to the pyramid, where Tezuman royalty await their arrival.
He starts to believe that he is indeed capable of granting \Gls{Eric}'s wishes, after all the time
spent in the Dungeon Dimensions.

\subsection{}
\subsubsection{\Gls{Rince} runs into a prisoner condemned to death as a human sacrifice}
\Gls{Rince} wanders away from the festivities, and finds a hollow pyramid, holding a large statue
of \Gls{Quezo}, the patron God of the Tezuman kingdom. A voice from underground begs him to be set
free, and tells him that it is scheduled to be flayed alive as a sacrifice to \Gls{Quezo}. The
\Gls{Parrot}, riding \Gls{Rince}'s shoulder, agrees with the idea to rescue the prisoner, even as
\Gls{Rince} is not sure about escaping the city with him.

\subsubsection{\Gls{Astf} makes \Gls{Quezo} repent for his mistakes}
\Gls{Astf} asks \Gls{Quezo} to be brough to him, and berates him for infesting the minds of the
Tezumen priests with a religion based on human sacrifice. He bemoans the belligerence seeping into
Tezuman culture, making them enter pointless feuds with every neighbouring kingdom in the jungles of
Klatch. He asks \Gls{Quezo} to manifest physically in the Tezuman capital, and tell them to pivot
their civilization to a path of progress.

\subsubsection{\Gls{Rince} reads the hieroglyphs predicting his death in the pyramid}
The prisoner in the pyramid introduces himself as \Gls{Ponce}, and asks \Gls{Rince} to study the
hieroglyps lining its inner walls. \Gls{Rince} spots the likenesses of \Gls{Eric} and himself, both
being subjected to ritualized torture, and decides to run from the city. He emerges from the
pyramid's back door, and is surrounded by Tezuman soldiers pointing crude spears at hibernation

\subsubsection{\Gls{Quezo} is accidentally killed by the \Gls{Lugg}}.
\Gls{Rince}, \Gls{Ponce} and \Gls{Eric} are all bound at the top of the flattened pyramid, ready to
be offered to \Gls{Quezo} as sacrifice. The \Gls{Lugg} bulldozes its way through the jungle, heading
for \Gls{Rince}, just as \Gls{Quezo} chooses to manifest at the ritual site. Being a six inch tall
imp, \Gls{Quezo} gets bulldozed by the \Gls{Lugg} as it runs over him, leading to the Tezumen
placing it at the center of their faith, and freeing the prisoners condemned to death.

\subsubsection{\Gls{Rince} and his companions leave the Tezuman kingdom}
\Gls{Rince} gifts the \Gls{Parrot} to \Gls{Ponce}, calling it a valuable asset in his search for
the Fonutain of Youth, as they exit the Tezuman city and make it to the cover of the jungle.
Meanwhile, the priestly class of Tezuma decide to replace \Gls{Quezo} with a new God, instead of
letting the absurdity of their religious rituals become common knowledge.

\subsubsection{\Gls{Rince} teleports himself and \Gls{Eric} into a huge wooden horse}
\Gls{Astf} is relieved by \Gls{Quezo} being condemned to several centuries of hell before his next
rebirth, and gets to work on his CCTV mirror, examining recent events. When \Gls{Rince} snaps his
fingers to grant \Gls{Eric}'s second wish, to get the most beautiful woman in the world, they are
transported into a huge wooden horse, and captured the moment they use a rope ladder to descend to
the ground.

\subsubsection{\Gls{Eric} and \Gls{Rince} are trapped in Tsort during the war for \Gls{Elenor}}
\Gls{Eric} realizes that he has been transported to Tsort thousands of years ago, during the war
to retrieve \Gls{Elenor}, famed to be the most beautiful woman in the realm. The guard captain
leaves them imprisoned in a room, and leaves with his men to investigate a disturbance at the city
gates. The \Gls{Lugg} smashes the city gates, and eats a squad of soldiers sent out to open it,
as \Gls{Rince} convinces the soldier guarding them to join his comrades in their valiant defense of
the city.

\subsubsection{\Gls{Rince} initiates the battle for \Gls{Elenor}}
\Gls{Rince} and \Gls{Eric}, running through the streets of the city, find an abandoned gate.
\Gls{Rince} unlocks it, hoping to find a way out, and accidentally lets in the sieging army instead.
He is exasperated by \Gls{Eric}'s single-mindedness in meeting \Gls{Elenor}, completely oblivious
to the bloody battle that is imminent.

\subsection{}
\subsubsection{\Gls{Rince} watches the fight happen in parallel to civilian life in the city}
As the battle between the Ephebians and Tsortians rages on in the streets, civilian life continues
unperturbed. In a bar, \Gls{Rince} learns that a civilian is being hunted for the crime of letting
the invaders in through the city gates, and is relieved when there is no description out for the
fugitive. A Tsortian soldier finds him in the bar, and takes him into custody.

\subsubsection{\Gls{Rince} and \Gls{Eric} meet the Ephebian general}
At the Ephebian command post, one of the generals casually feeds the \Gls{Lugg} some bread, as
\Gls{Rince} and \Gls{Eric} are escorted in. The other nobles choose to ignore them, as the general
asks \Gls{Rince} where he is from. \Gls{Rince} is surprised to see no surprise on the general's face
when he reveals that he is from the future, and that the \Gls{Lugg} is bound to him by magic.

\subsubsection{\Gls{Rince}, \Gls{Eric} and the \Gls{Lugg} follow \Gls{Laveo} through tunnel}
\Gls{Laveo}, the captain who was the brain behind the wooden horse, invites \Gls{Rince} and
\Gls{Eric} to an expedition into the Tsortian citadel, by way of a secret underground tunnel their
spies had discovered. The squad accompanying them praise \Gls{Laveo} for eschewing the pomp and show
attached to traditional military strategy, in favour of getting results by any means necessary.

\subsubsection{}
Inside the citadel, \Gls{Laveo} emerges into a secret chamber, where \Gls{Elenor} is cowering in
fear, with several children clinging to her. \Gls{Eric} recalls the legends of \Gls{Laveo}, hailed
as a hero in the Classics, and asks \Gls{Rince} if they should warn him of the misfortunes waiting
for him in the future. He is then dismayed to see \Gls{Elenor} not match the descriptions from the
history books, as the Ephebian sergeant explains literary metaphor.

\subsubsection{\Gls{Elenor} wishes to stay back in Tsort with the King}
\Gls{Elenor} tells \Gls{Laveo} that she has grown to like the Tsortian King, and that she does not
care to leave her life behind to return to Ephebe. \Gls{Laveo} laments the years he has wasted
sieging Tsort, and wonders if his soldiers will burn the city down, when they hear the news of their
campaign being futile.

\subsubsection{\Gls{Laveo} bids farewell to \Gls{Rince}}
The \Gls{Lugg} rescues the civilians stuck inside the palace, as the city is burned down, with the
two armies declaring a truce. \Gls{Laveo} asks \Gls{Rince} if he will make it home in one piece,
and \Gls{Rince} decides not to tell him about the tribulations he is to face along the way. After
\Gls{Laveo} sets sail on his ship, \Gls{Eric} speculates that he is \Gls{Rince}'s distant ancestor.

\subsubsection{\Gls{Rince} ends up in outer space with \Gls{Eric}}
Meanwhile, \Gls{Astf}, from his realm outside space and time, notices that \Gls{Eric} is becoming
more personable, and thinks about some means of breaking the boy's heart. \Gls{Rince} snaps his
fingers again, teleporting himself and \Gls{Eric} to the vacuum of space. \Gls{Astf} loses track
of the two of them, and guesses they have to be in one of two possible places he cannot observe in
his CCTV mirror.

\subsubsection{\Gls{Astf} talks to \Gls{Death} at the end of the Universe}
A mysterious man accosts \Gls{Rince}, offering him some food, as \Gls{Eric} notices the absence of
stars, and of any physical sensation in his body. The man tells them that they are in the time
before creation, even before light is summoned into existence. Meanwhile, \Gls{Astf} runs into
\Gls{Death} at the end of the Universe, and learns that \Gls{Rince} is a mere human, accidentally
trapped in the Dungeon Dimensions.

\subsubsection{\Gls{Rince} sees the \Gls{Creat} bring the Discworld into existence}
\Gls{Death} is pleased to see the cycle of the Universe start again, when a paperclip and a button
pop into existence from nothingness. At the start of the universe, \Gls{Rince} learns that the
little man is a \Gls{Creat}, tasked with the job of designing and creating universes. The man asks
them to remain silent, as the universe starts to take shape from raw matter and energy.

\subsubsection{\Gls{Rince} and \Gls{Eric} are left at the beginning of the Discworld}
The Discworld's gravity starts to pull \Gls{Rince} and \Gls{Eric}, with the creator struggling to
think of a way to save them. Eventually, he tinkers with their positions and velocities to leave
them on a beach, before vanishing. \Gls{Rince} realizes that \Gls{Eric}'s third wish of living
forever has been interpreted to mean a life that stretches the entire timespan of the Discworld. He
is alarmed by the prospect of hanging around in the Disc for millennia before life evolves, and
sentience finally emerges.

\subsubsection{\Gls{Rince} and \Gls{Eric} accidentally end up at the gates of Hell}
\Gls{Rince} thinks about getting \Gls{Eric} to draw a magic circle to take them back to the present,
and tosses his half-eaten sandwich on the beach. \Gls{Astf} materializes some time later to find
his quarry gone, and notices the bacteria in the sandwich kickstarting life on the Disc.
\Gls{Eric}'s portal takes the two of them to the gates of Hell, where an abomination welcomes them
by reciting a customer-service script.

\subsubsection{\Gls{Rince} hoodwinks \Gls{Urgle}}
The demon, who has a badge identifying him as \Gls{Urgle}, the guardian of the Gates of Hell,
bemoans the changes instituted by his new master, including a change in decor, and the dispassionate
tone adopted in welcoming new entrants. \Gls{Rince} commiserates with the demon at the gate,
who despises the changes being pushed on the workers, and manages to march into Hell, before
\Gls{Urgle} can fully process the fact that the two newcomers are not dead.

\subsubsection{\Gls{Rince} and \Gls{Eric} explore the revamped depths of Hell}
Inside Hell, \Gls{Rince} finds the demons subjecting souls to eternal boredom, designed to numb
their minds in a way that physical torture never could. \Gls{Rince} thinks back to his own life,
and of how he valued boredom, simply becuase it meant he was out of trouble. They hear \Gls{Astf}
roaring in anger, and decide to run, until they bump into \Gls{Ponce} and the \Gls{Parrot}.

\subsubsection{\Gls{Astf} gets his underlings to search for \Gls{Rince} and \Gls{Eric}}
\Gls{Astf} asks his vassals to hunt down the intruders, alarmed at the prospect of live humans
making it to Hell. \Gls{Vassen} reminds him that it is demonic culture to foment rebellion and
mutiny against any authority figures, as he reluctantly complies with the orders. \Gls{Urgle} is
condemned to disassembly in the lowers circle of Hell for his crime of letting \Gls{Rince} in.

\subsubsection{\Gls{Rince} reunites with \Gls{Ponce} and the \Gls{Parrot}}
\Gls{Rince} learns that \Gls{Ponce} died from drinking the water at the fountain of youth, since he
did not boil it first to make it safe. He is pleased to see the \Gls{Parrot} also condemned to Hell,
as he leads the party away from the demons trying to hunt them down. Meanwhile, the gates of Hell
open up to allow the \Gls{Lugg} to pass through, seeing the certainty with which they were about to
be torn down if it was forced to charge in.

\subsubsection{\Gls{Rince} learns from \Gls{Laveo} that a staircase leads out of Hell}
\Gls{Rince} then finds \Gls{Laveo}, who points out a staircase leading out of Hell at the opposite
end of the circle of Hades. The \Gls{Lugg} gets on the infinite treadmill that \Gls{Rince} and his
party are on, and runs so fast that it breaks off its handles, and starts to roll through Hades
like a bulldozer, crushing any demons caught in its path.

\subsubsection{\Gls{Vassen} plans to undo the changes wrought by \Gls{Astf}}
\Gls{Vassen} convinces the other senior demons to buy into his plan to usurp \Gls{Astf}'s throne,
as he thinks back to how useful \Gls{Rince} has been as a distraction. He laughs at \Gls{Rince}'s
naivete in believing that he had granted \Gls{Eric}'s three wishes using some magic of his own, and
is satisfied with his own plan to use \Gls{Rince} as an unwilling puppet.

\subsubsection{\Gls{Astf} accepts a promotion to an emeritus position with no impact on Hell}
When \Gls{Astf} captures \Gls{Rince} and \Gls{Eric}, he finds the great hall decorated in his
honour, with \Gls{Vassen} waiting to inform him of his promotion. He is overjoyed at the idea of
spending the next few eons drawing up elaborate plans for the demon world, and does not realize that
he is being trapped in a never-ending treadmill designed to keep him busy forever. As the demons
celebrate the return to the old ways of Hell, \Gls{Rince} decides to make a run for it.

\subsubsection{\Gls{Rince} and \Gls{Eric} emerge into the Discworld from Hell}
\Gls{Vassen} decides to let \Gls{Rince} and \Gls{Eric} escape, in exchange for their help in
ousting \Gls{Astf}. Meanwhile, the demons of hell are happy to get back to the old ways of torture
and eternal pain, leaving \Gls{Astf} stuck in his chamber of eternal paperwork, delighted to start
the greatest task of organization in the universe.


\section{Interesting Times}


\subsection{}
\subsubsection{\Gls{Fate} starts a new board game on \Gls{Lady}'s request}
At the game board in Dunmanifestin, \Gls{Lady} challenges \Gls{Fate} to a game of Kingdoms, to be
played using the five factions vying for control of the Counterweight Continent. \Gls{Fate} accepts
her request, while forbidding the use of dice to play the turns.

\subsubsection{\Gls{Vetina} shows \Gls{Ridcu} the messenger albatross from the Agatean Empire}
\Gls{Vetina}, now Patrician of Ankh-Morpork, thinks about the uneasy truce between the bureaucracy,
and the wizards of Unseen University, now headed by Archchancellor \Gls{Ridcu}. On one of his social
visits, \Gls{Ridcu} is amused to see the \Gls{Patri} lead him through his garden, and into the
oversized coop for his messenger pigeons. He is alarmed to see a messenger albatross from the
Agatean Empire, as \Gls{Vetina} reminds him of the need for secrecy.

\subsubsection{\Gls{Vetina} asks \Gls{Ridcu} to find a great wizard for the Agatean empire}
The \Gls{Patri} decodes the Agatean pictograms in the message, asking for the Great Wizard to be
sent there as soon as possible. He asks \Gls{Ridcu} to find a scapegoat on whom they can pin this
responsibility, and he immediately starts to think about his rival, the \Gls{Dean} of the
University. Meanwhile, a shark converging on \Gls{Rince} as he lounges on seawater, is alarmed by
the \Gls{Lugg} appearing behind it.

\subsubsection{\Gls{Ridcu} talks to his inner council}
\Gls{Ridcu} summons the inner council and tells them about the Agatean empire's request, only to
see the \Gls{Libra} run out of the room as if to warn someone. He turns to the \Gls{Dean}, trying
to appeal to his ego and declaring him the greatest wizard in the room. \Gls{Stibb}, a budding
mathematician and inventor, tries to reassure everyone that his computing machine can perform the
calculations needed to teleport to the other side of the Disc, just as the \Gls{Libra} runs in with
\Gls{Rince}'s old pointy hat.

\subsubsection{\Gls{Rince} is forcibly teleported by \Gls{Stibb} to the Unseen University}
The inner council bickers about \Gls{Rince}, and their whereabouts during the reign of the
Sourceror, as \Gls{Ridcu} loses his temper, and calls them to order. \Gls{Stibb} rudely interrupts
\Gls{Rince}'s encounter with some Amazonian tribeswomen on a deserted island, and drags him back
to the inner council's chamber using the calculations supplied by his computer, named \Gls{Hex}.

\subsubsection{\Gls{Rince} indulges in some greasy junk food outside the University}
\Gls{Rince} runs into the market outside the University, and gorges on some junk food, having
developed a craving for it in his time on the deserted island. He is slapped by an old man, but
seems to be lost in the deliciousness of the snacks, much to the amusement of \Gls{Ridcu} and his
inner council. \Gls{Rince} comes to his senses as the \Gls{Libra} hands him his old hat.

\subsubsection{\Gls{Hong} speaks to his spy \Gls{TFHerb} about the summons for \Gls{Rince}}
\Gls{Hong}, newly ascended to the Lordship of one of the ruling families of the Counterweight
Continent, thinks about the recent assassination of his father, as he receives the news of his
albatross successfully flying away to the Circle Sea. The spy named \Gls{TFHerb} tells \Gls{Hong}
that the Great Wizard is famously incompetent, and will lead to the fizzling out of the Red
Revolution slowly taking root among the proletariat.

\subsubsection{\Gls{Rince} realizes he is being coerced into undertaking a dangerous mission}
Once he is awake, \Gls{Rince} is threatened by \Gls{Ridcu} with prosecution for impersonating a
wizard, and subtly corners him into taking on the quest outlined by \Gls{Vetina}. Meanwhile,
\Gls{Stibb} thinks about the self-assembling pieces of his computer \Gls{Hex}, as he receives a
spell in response to his latest enquiry. He thanks it, before going back to \Gls{Ridcu} thinking
about the absurdity of emergent intelligence.

\subsubsection{\Gls{Rince} prepares for his mission to the Agatean Empire}
\Gls{Rince} sees his shabby room preserved in its entirety, as he puts on his old robe, and sends
off the \Gls{Lugg} to stock up on potatoes from the underground kitchen. \Gls{Ridcu} finds him
midway through his preparations, and commends him on his eagerness to perform the act of great
service to wizardkind. \Gls{Rince} looks forward to the dullness and boredom supposedly available
in plenty inside the Agatean Empire.

\subsection{}
\subsubsection{\Gls{Stibb} gets the council to agree to his plan}
As the Red Army holds another secret meeting, with the mole \Gls{TFHerb} in attendance, they learn
that the Great Wizard is coming to the Agatean Empire to help their movement. Meanwhile, \Gls{Stibb}
successfully persuades the inner council and \Gls{Rince} to undertake the journey to the Agatean
Empire using the teleportation spell computed by \Gls{Hex}.

\subsubsection{\Gls{Stibb} sends \Gls{Rince} on his way using \Gls{Hex} and its computations}
\Gls{Stibb} starts to explain the issues with traditional traveling spells, as \Gls{Rince} listens
with growing horror. The other members of the council grow impatient with his mathematical lecture,
and ask him to get on with the spell-casting. \Gls{Rince} travels through the Discworld as he is
exchanged for an Agatean cannon, shaped to resemble a dog's mouth.

\subsubsection{\Gls{Rince} arrives in the Agatean Empire}
\Gls{Stibb} extinguishes the cannon's burning fuse, as \Gls{Ridcu} investigates the large ball
lodged inside its barrel, oblivious to the danger of a cannonball exploding in his face. He knocks
over some prison guards in the Agatean Empire, as he arrives in a snow-covered hillside holding a
long chain of manacled prisoners.

\subsubsection{\Gls{Rince} reunites with \Gls{Cohen}}
\Gls{Rince} recognizes \Gls{Cohen} among the prisoners, by his diamond dentures, and is relieved to
know that the prison guards will be dispatched by the legendary hero. \Gls{Cohen} then frees the
other prisoners chained to him, and asks them to run to safety. \Gls{Cohen} realizes that the slaves
he just freed had never experienced freedom in their lives, and were looking to him for orders. He
commands them to follow on foot, as he finds horses for himself and \Gls{Rince}.

\subsubsection{\Gls{Hong} learns of the arrival of the Great Wizard}
\Gls{Rince} learns of the siege underway in the capital city of HungHung, with the death of the
Emperor, and the resultant politicking between the five ruling families. Meanwhile, \Gls{Hong}
receives news from a messenger that \Gls{Rince} has arrived, and seemingly magicked away one of the
prototype cannons. He casually beheads the girl sent to serve him his tea, and searches her robes
for the poison meant to kill him.

\subsubsection{\Gls{Cohen} talks about the dictatorial ruling class of the Agatean Empire}
\Gls{Cohen} explains to \Gls{Rince} that the Agatean Empire runs on a tyrannical ruling class
treating the common-folk like slaves, depriving them of even the most basic human rights. He
believes that the isolationism and traditionalism in the Empire have convinced the people that the
governance they are experiencing is normal, and an improvement over the other kingdoms of the Disc.

\subsubsection{\Gls{Cohen} reaches his hideout in the mountains}
\Gls{Cohen} tries to dismiss the freed slaves following him, and is exasperated by their desperate
need for orders from an authority figure. He threatens them with death unless they go back to their
village, and is glad to see them shamble away. \Gls{Cohen} then leads \Gls{Rince} to his mountain
hideout, while talking about something worse than whips used to break the spirits of the peasants.

\subsubsection{\Gls{Hong} meets with the other lords to talk about the Red Army}
\Gls{Hong} envies the simplicity of the writing system in Ankh-Morpork, as the eunuch recording his
meeting with the lords of the other ruling families struggles with his calligraphic decorations.
He tells the gathered lords a Great Wizard has arrived from Ankh-Morpork to assist the Red Army in
their plot to assassinate the Emperor. The other lords are shocked by the news, and quickly recite
their own efforts to quell the revolution growing in their lands.

\subsubsection{\Gls{Hong} reassures the other lords about the quelling of the Red Revolution}
\Gls{Tang} claims not to have any knowledge of the foreigner's arrival, as \Gls{Hong} speculates
about the possibility that someone in a position of power is assissting the Red Army. \Gls{Hong}
dismisses the nobles, and retires to his private chamber, where he dreams of conquering
Ankh-Morpork, to taste its riches, and experience the efficiency of free-market enterprise.

\subsubsection{\Gls{Cohen} and the Silver Horder terrify \Gls{Rince}}
\Gls{Cohen} introduces \Gls{Rince} to the Silver Horde, his handpicked squad of old barbarian
heroes, all over the age of eighty, as \Gls{Rince} muses on the propsect of facing entire armies in
Hunghung. \Gls{Cohen} explains that the Red Revolution will give them the cover they need to sneak
into the capital city and steal something of great value, as he dismisses \Gls{Rince}'s concerns
about the Horde's age.

\subsubsection{\Gls{Rince} talks to \Gls{Saveloy} about the situation in Hunghung}
\Gls{Rince} walks up to a slim old man busy reading a book, who introduces himself as \Gls{Saveloy},
a geography teacher who decided to take up the barbarian lifestyle after retirement. He talks about
the ongoing cold-war in Hunghung, and is nonplussed by \Gls{Rince}'s insistence on riding away to
the coastline, to find a ship back to the Circle Sea.

\subsubsection{\Gls{Rince} is appalled by the state of the Agatean peasants}
\Gls{Rince} rides through a farming village, and is shocked to see the peasants toil away at their
fields, trying not to notice the strange man on horseback. He uses his broken Agatean to ask one
of the farmers for some food, and is shocked to see them run away in terror when he offers his horse
as payment.

\subsubsection{\Gls{Rince} reads \Gls{Twofl}'s book about Ankh-Morpork}
\Gls{Rince} reads the book lent to him by \Gls{Saveloy}, talking about an Agatean traveler
experiencing the city of Ankh-Morpork (\Gls{Twofl} ?), and is intrigued by mentions of a Great
Wizard in the scibblings. He fails to hear someone sneaking up on the peasant track behind him, and
gets knocked out. Meanwhile, the \Gls{Lugg} materializes in the mountains of the Agatean empire, and
starts to make sense of \Gls{Rince}'s position.

\subsubsection{\Gls{Rince} is sent to the Emperor's palace as a slave}
\Gls{Rince} is accosted by a minor noble in a palanquin, as his guards hold take him into custody
for stealing a horse. The noble issues a formal punishment of slavery in the royal palace, and
simultaneously talks to him in Morporkian, about a false story concocted to justify his presence in
the Agatean Empire without any identifying papers. \Gls{Rince} fails to recognize the nobleman as a
leader of the Read Army, intent on sneaking the prophesized leader in the Emperor's palace.

\subsubsection{\Gls{Rince} reaches a tavern in the Agatean countryside}
\Gls{Rince} runs away from the guards, and hides in a nearby village, pretending to be the officer
administering an examination for the position of sewage hauler. Eventually, \Gls{Rince} hears the
guards wander off, and walks to an Inn some distance away from the village. The landlord loudly
proclaims his refusal to serve any Red Army rebels, while giving him free bowl of soup upon seeing
the revolutionary book hidden in his robes.

\subsubsection{\Gls{Rince} recognizes \Gls{Twofl} as the author of the revolutionary book}
\Gls{Rince} peruses \Gls{Twofl}'s book of travels, and realizes that his descriptions of a free
country across the seas, has accidentally sparked a revolution within the Agatean peasants, who were
used to centuries of regimented chattel slavery. The landlord knocks \Gls{Rince} out, presumably to
take him to the Red Army hideout, as an impromptu drama troupe puts on a play in the tavern.

\subsubsection{\Gls{Rince} is kidnapped by the theatre actors}
\Gls{Cohen} almost entertains doubts about his Plan to storm the capital, as he asks \Gls{Saveloy}
about the secret route through the mountains. Meanwhile, \Gls{Rince} realizes he is being kidnapped
with a sack over his head, as a young girl talks to him from the front of the carriage. She is
skeptical about his claims of being the Great Wizard mentioned in \Gls{Twofl}'s book, even as he
tries desperately to defend his supposed feats of magic.

\subsubsection{\Gls{PrettyB} warns \Gls{Rince} about his value as a symbol of hope for the Red Army}
The woman holding \Gls{Rince} hostage reaveals herself as \Gls{PrettyB}, part of a traveling
troupe of artists, and instigators of the Red Revolution. She tells \Gls{Rince} that he his life was
in great danger if he turned out to be a phony wizard, and weakened the revolution by showing his
true nature.

\subsubsection{\Gls{Saveloy} thinks about breaching the Forbidden City within Hunghung}
\Gls{Saveloy} studies the geography surrounding the city of Hunghung, speculating that the Forbidden
City must have a secret water supply tunnel, which could be their means of breaking and entering.
\Gls{Cohen} fails utterly to grasp the intricacies of the plan, nodding along as if he has a rough
idea of \Gls{Saveloy}'s direction of inquiry.

\subsection{}
\subsubsection{\Gls{PrettyB} warns \Gls{Rince} to act the part of the Great Wizard}
\Gls{PrettyB} supervises \Gls{Rince} being deposited in an abandoned barn outside Hunghung, as two
other members of the Red Army greet him, identifying themselves as \Gls{LotusB} and \Gls{ThreeYO}.
\Gls{PrettyB} talks about the legend of a Great Wizard who had led another revolution thousands of
years ago, and warns him that he has inadvertently been trapped in the same role.

\subsubsection{\Gls{Rince} gets cornered by some city guards in Hunghung}
\Gls{Rince} manages to run away from the Red Army hideout, and emerges onto a bustling street market
in Hunghung. He elbows his way through the crowds, until he finds an empty square. Guards step out
of the trees around it, surrounding him, and ask him to bow down for the crime of tresspassing on
Imperial land. He realizes that they are ill-equipped to chase him, since they expect absolute
obedience from any peasant.

\subsubsection{\Gls{Cohen} allows himself to get captured by the city guards}
With the help of \Gls{Saveloy}'s rigorous training, \Gls{Cohen} and the Silver Horde manage to
submit to the city guardsmen examining their papers at the gates of Hunghung. They are dragged off
to the jailhouse nearby, where \Gls{Cohen} slits the guard captain's throat. The other soldiers,
confused about the chain of command, bow down expecting new orders from \Gls{Cohen}, as
\Gls{Saveloy} reminds him about the need to treat unarmed prisoners humanely.

\subsubsection{\Gls{Rince} talks to \Gls{Dibha} about trade opportunities in Ankh-Morpork}
\Gls{Rince} runs into street food vendor who reminds him of another in the square outside the
Unseen University. The vendor, named \Gls{Dibha}, starts to explain paper money, making \Gls{Rince}
recognize the counterfeiting opportunities to be had in exchanging them for the gold coins that were
the base currency. He sees a Red Army youth being dragged through the streets for the crime of
putting up posters, and learns that the likely punishment is getting is limbs chopped off.

\subsubsection{\Gls{Saveloy} tries to get the Silver Horde to play by the rules of civilization}
\Gls{Saveloy} is dismayed to see \Gls{Cohen} almost complete a transaction with a fruit merchant in
the markets of Hunghung, before he loses patience and knocks him out. \Gls{Saveloy} tries to get
\Gls{Caleb} to purchase a duck from a woman in the market, and is pleased to see him resisting
his barbarian instincts when talking to her.

\subsubsection{\Gls{PrettyB} forces \Gls{Rince} to rescue \Gls{ThreeYO}}
\Gls{TFHerb} and \Gls{LotusB} talk about \Gls{Rince} being the Great Wizard, and of the stories
written by \Gls{Twofl} in his book detailing his magical prowess. \Gls{TFHerb} remains skeptical of
the claims in the book, until \Gls{PrettyB} corners \Gls{Rince} into mounting an expedition into
the dungeons beneath the Forbidden City, in the hopes of rescuing \Gls{ThreeYO}.

\subsubsection{\Gls{Rince} is coerced into mounting a rescue operation for \Gls{ThreeYO}}
\Gls{Rince} is alarmed to find children surrounding him in the musty cellar, describing themselves
as the Hunghung cadre of the Red Army. He resolves to play along with \Gls{PrettyB}'s plan, and
make a run for it at the first opportunity that presented itself. Meanwhile, the \Gls{Lugg} breaks
into an enclosure for other sentient pearwood trunks, and beats up some other chests seeking to
bully one of their own.

\subsubsection{\Gls{Saveloy} thinks about his plan to penetrate the Forbidden City}
\Gls{Saveloy} works out the finer details of the plan to use fireworks purchased from the market,
as the Silver Horde enjoy their first taste of civilization. Meanwhile, \Gls{PrettyB} pulls
\Gls{Rince} to the side, and tells him that she immediately recognized him as an unskilled, but
extremely lucky wizard, from her readings of \Gls{Twofl}'s book.

\subsubsection{\Gls{TLWang} hears the barbarians in the water pipes underneath the Forbidden City}
\Gls{TLWang}, newly appointed assistant to the \Gls{Empe}, bemoans the descent of the Agatean
Empire, into a land of inequality, decadence, authoritarianism, and martial law. He hears some
sounds coming from under the grounds of the palace, when out for a stroll, and follows them across
the garden.

\subsubsection{\Gls{Saveloy} uses his knowledge of the water supply system to infiltrate the
    Forbidden City}
\Gls{Saveloy} tries to explain to the Silver Horde that the fireworks are rigged to blow a hole in
the Forbidden City's outer wall, as a distraction meant to enable their infiltration. Meanwhile,
\Gls{Rince} is egged on by \Gls{TFHerb} at the walls of the Forbidden city, prompting him to think
that \Gls{TFHerb} is a double agent sent by the Empire to ensure the failure of the Red Revolution.

\subsubsection{\Gls{Rince} pretends to be responsible for \Gls{Saveloy}'s explosion}
\Gls{Rince} is surprised to see \Gls{Saveloy}'s fireworks punch a hole in the wall of the Forbidden
City, flattening all the Red Army members gathered around him to witness his magic. A while later,
some city guards capture \Gls{Rince}, and send him to the \Gls{Empe}'s jail, as the Red Army
cadre start to recover from the shockwave of the blast.

\subsubsection{\Gls{Saveloy} gets the Silver Horde to don their eunuch disguises}
Once inside the water supply room of the Forbidden city, \Gls{Saveloy} asks the barbarians to put
on the eunuch costumes they had purchased earlier. \Gls{OldVin} worries about the songs that will
be sung about their cowardly approach to the mission, until \Gls{Cohen} reminds him of the fact
that minstrels can be bribed.

\subsubsection{\Gls{Hong} deals with the latest threat to his life}
\Gls{Hong} kills an elite assassin sent to kill him, while distracted by the imperfections in his
latest sword, fresh from the forge. He sends new orders via messenger to a guard captain in the
city, while distracted by the sloppiness of the latest attempt at his life. Meanwhile, \Gls{Rince}
is brought to the \Gls{Empe}'s court, where he is alarmed to see a frail old man, confined to an
ornate bed.

\subsubsection{\Gls{Rince} faces the Agatean \Gls{Empe} in his throne room}
\Gls{Hong} arrives at the throne room, in time for the \Gls{Empe} to declare his liking for
\Gls{Rince}, and his intention to keep the foreigner around as a funny pet. The \Gls{Empe} dismisses
his courtiers, and retires for the night, after ordering \Gls{Rince} to be confined to the special
dungeon. \Gls{Rince} is alarmed by the sly wink \Gls{Hong} gives him, as the \Gls{Empe} sentences
a courtier to death for some perceived insult.

\subsubsection{\Gls{Saveloy} and the barbarians hide in plain sight}
\Gls{Hong}, now the \Gls{GViz} of the Agatean Empire, thinks about his efforts to make the Red Army
appear stronger than it was, including the gift of the Great Wizard. He eagerly anticipates the
Red Army's eventual slaughter, and the counter-revolution that he would ignite in the aftermath.
Meanwhile, \Gls{Saveloy} leads the Silver Horde through the corridors of the Forbidden City, in the
guise of eunuchs carrying paperwork to some office.

\subsubsection{\Gls{Rince} is reunited with \Gls{Twofl} in the Forbidden City's prison}
Inside his prison cell, \Gls{Rince} is alarmed to hear \Gls{Twofl}'s muffled voice from the cell
next to his. He manages to push a brick free and learns that \Gls{Twofl} is likely stuck in jail
because of errors in paperwork. \Gls{Twofl} innocently states that he only meant his book as a form
of light entertainment, and not a document that might foment a revolution.

\subsubsection{\Gls{Saveloy} finds a tax-collector inside the Forbidden City's offices}
\Gls{Saveloy} and the horde walk into an important-looking office within the Forbidden City, to find
a tax-collector inside, lost in his paperwork. The official, who identifies himself as \Gls{SixBW},
quickly realizes that the old men are not eunuchs, and quite happy to kill him should he call for
the guards. \Gls{Saveloy} forces \Gls{SixBW} to show them around the Forbidden City complex, as the
barbarians resist the urge to cut his head off.

\subsection{}
\subsubsection{\Gls{Twofl} and \Gls{Rince} spend time in the prison}
\Gls{Twofl} spends the night remembering his time in Ankh-Morpork, as \Gls{Rince} tries desperately
to make a dent in the stone blocks making up the jail cell. In the morning, they hear a scream in
the distance, which \Gls{Twofl} believes is the sign that the \Gls{Empe} has woken up. Someone stabs
the guard outside \Gls{Rince}'s cage, and uses his keyring to unlock the cell. \Gls{Rince} uses the
opportunity to free the other prisoners.

\subsubsection{\Gls{Rince} frees the Red Army in the Forbidden City's prison}
\Gls{Rince} is shocked to discover that \Gls{PrettyB} and \Gls{LotusB} are \Gls{Twofl}'s daughters.
He frees the rest of the Red Army children, and comments on the curious absence of \Gls{TFHerb}.
He sees \Gls{PrettyB} coming to the same realization as him, that \Gls{TFHerb} is probably a double
agent, sent to monitor the Revolution and ensure its failure.

\subsubsection{\Gls{SixBW} is amazed to see the invaders take on the ninjas of the Agatean Empire}
\Gls{SixBW} takes advantage of the barbarians being lost, to lead them to the ninja training
grounds. A group of ninjas surround them, with \Gls{SixBW} asking the invaders to surrender, or
face the finest warriors in the kingdom. He watches the barbarians casually face down the ninjas,
as \Gls{Saveloy} explains the lifetime of experience they have staying alive while being
outnumbered.

\subsubsection{\Gls{SixBW} wishes to join \Gls{Cohen}'s troop}
\Gls{Truckle} holds a sword at \Gls{Saveloy}'s throat when the teacher reveals the true meaning of
their disguises. \Gls{Cohen} gets him to back down, by reminding his fellow barbarian that the
mission merely required them to pretend to be harmless old eunuchs to hide in plain sight.
\Gls{Saveloy} is happy to see \Gls{SixBW} mulling over the idea of joining their group as an
accountant, and is shocked to see the stagnation of technology in the Empire.

\subsubsection{\Gls{Rince} explains the futility of a violent rebellion}
\Gls{Rince} tries to persudae the Red Army that the night's events were very suspicious, as they
find all the prison guards dead, with a map leading to the Emperor's chamber conveniently lying
beside one of the soldiers. He asks the children to go back to the safety of the prison, intending
to run away from the Forbidden City, but is cornered by \Gls{PrettyB} into investigating the
palace.

\subsubsection{\Gls{SixBW} understands \Gls{Cohen}'s plan}
\Gls{SixBW} tries to explain the idea of taxation to the Horde, who fail to see the point of taking
only a fraction of the money from a merchant, and letting him live afterward. \Gls{Saveloy} keeps
saying no to all of his guesses regarding the tresure they were planning to steal, until
\Gls{SixBW} works out their intentino to kidnap the \Gls{Empe}.

\subsubsection{\Gls{PrettyB} and \Gls{Rince} reach the \Gls{Empe}'s chamber}
\Gls{PrettyB} refuses to heed \Gls{Rince}'s warnings about the Red Army being set up for the
\Gls{Empe}'s murder, and guides him deeper into the residential area of the Forbidden City. They
eventually come to the Emperor's chamber, to find him lying very still in his ornate bed. The
guards turn on \Gls{Rince}, framing him for the death of the \Gls{Empe}, causing him to flee the
chamber.

\subsubsection{\Gls{SixBW} watches \Gls{Cohen} take over the Agatean throne}
\Gls{PrettyB} considers the idea that \Gls{TFHerb} is a double agent meant to guide the Revolution,
and to provide his master the excuse for a counter-revolutionary tightening of laws. \Gls{SixBW}
watches \Gls{Cohen} walk up to the empty throne and sit on it, realizing that the current \Gls{Empe}
led a reclusive life, with only a handful of people even knowing what he looked like. \Gls{Saveloy}
promises to elevate him to the highest position in the civil service, and asks him to gather all
those who know the \Gls{Empe}'s face for disposal.

\subsubsection{\Gls{TFHerb}'s plan to use the Red Army as a scapegoat fails}
\Gls{Rince} stumbles into the sumo wrestler quarters, and convinces them into ganging up on the
palace guards. Meanwhile, \Gls{Hong} receives news of the Red Army not showing themselves at the
\Gls{Empe}'s chamber, to act as scapegoats for his murder. He orders \Gls{TFHerb} to be imprisoned,
pending execution. Meanwhile, \Gls{Cohen} witnesses the handful of courtiers assembled in front of
him, asking them if they had any problems accepting him as their new ruler.

\subsubsection{\Gls{Cohen} kills the old \Gls{Empe}'s chamberlain for rejecting his claim to the
    throne}
\Gls{Rince} runs into the laundry hall, and realizes that a sudden change of disguise might throw
off the guards chasing him, and allow him to blend into the bureaucrats milling about in the
Forbidden City. The head chamberlain raises his voice against \Gls{Cohen} and is swiftly killed,
as the rest of the Silver Horde deal with the \Gls{Empe}'s elite guards. The other courtiers pledge
their allegiance to \Gls{Cohen}, in the hopes of maintaining their decadent lifestyle under the new
regime.

\subsubsection{\Gls{Rince} outsmarts the guards chasing him}
\Gls{Rince} pretends to be a servant in the laundry hall, and touches his wizard hat daintily, to
make a show of falling down, bent over in great pain. The guards pursuing him take the hint, and
run away from the cursed hat, only for \Gls{Rince} to get whipped by the chief laundryman, in
response for shirking his duties for the day.

\subsubsection{\Gls{Hong} poisons the food meant for \Gls{Cohen}}
\Gls{Hong} walks in on the courtiers trying to get the kitchen staff to prepare food for their
new \Gls{Empe}, and decides to poison the meat right in front of them. The courtiers make no attempt
to stop this subterfuge, believing that their lives would remain the same regardless of who sits on
the throne. \Gls{Rince}, in the disguise of a kitchen servant, wheels the tray of food from the
kitchen to the throne room.

\subsubsection{\Gls{Rince} saves \Gls{Cohen} from the poisoned food}
\Gls{Rince} warns \Gls{Cohen} about the poisoned food, causing him to summon two shifty looking
courtiers, to taste the food. One of them dies in a small explosion, and \Gls{Cohen} orders the
other to be imprisoned. Meanwhile, \Gls{Saveloy} goes off on a rant about the Silver Horde having
wasted their lives looting and pillaging, and of how the reformation of the Agatean Empire was a
unique opportunity for them to leave their mark on world history.

\subsubsection{\Gls{Rince} reminds himself of the Red Army still stuck in prison}
\Gls{Rince} asks for the Red Army still stuck in the prison to be rescued, and \Gls{Cohen} sends one
of his friends to oversee their safe transfer to the throne room. Meanwhile, the newly ascended
Chamberlain warns \Gls{Cohen} about \Gls{Hong}'s scheming, and the possibility of the warlords
forming an alliance to march on Hunghung. \Gls{Hong} and some other generals enter the throne room,
to parley with \Gls{Cohen}.

\subsubsection{\Gls{Cohen} parleys with \Gls{Hong}}
\Gls{Cohen} rejects \Gls{Hong}'s offer of surrender, and carefully avoids any mention of the true
size of his invading force. \Gls{Rince} tries to scare the other warlords with the rumours of
invisible ghosts being led by the barbarian generals, but \Gls{Hong} refuses to fall for the bait.
\Gls{Saveloy} believes that no more assassination attempts will happen, now that war has been
formally declared.

\subsubsection{\Gls{Rince} hopes to use misinformation and rumours to break the enemy camp's spirit}
\Gls{Rince} uses \Gls{Dibha} to spread rumours about the coming army of invisible vampire ghosts
through the enemy camp, believing that centuries of propaganda about the lands outside the Agatean
Empire might prove useful in winning the war against \Gls{Hong}. \Gls{Rince} sets the children of
the Red Army loose within the enemy camp, spreading rumours about the invisible ghost army that
may or may not be marching to devour them.

\subsubsection{\Gls{Rince} finds \Gls{Death} and \Gls{War} at \Gls{Hong}'s army camp}
\Gls{Rince} runs into \Gls{Death} and \Gls{War} surveying \Gls{Hong}'s encamped army, and is
surprised to learn that even \Gls{Death} does not know the outcome of the coming battle. He returns
to the safety of the palace, leaving \Gls{Death} and \Gls{War} to set up their picnic, invisible to
everyone else.

\subsubsection{\Gls{Hong} decides to take morale for granted}
\Gls{Hong} asks his diviner to give a false prediction saying they would win the coming battle with
overwhelming advantage, as the gathered warlords express their doubts about the invading army of
vampire ghosts. \Gls{Hong} orders the circulation of new rumours stating that the Agatean ancestors
were also rising as a ghost army to counter the enemeies, believing that the common soldiers would
remain unfazed by ghosts on both sides.

\subsubsection{\Gls{Stibb} sets his computer to finding \Gls{Rince}'s position}
\Gls{Hong} takes out his secret outfit, that makes him look like a minor noble of Ankh-Morpork, and
anticipates the opportunity to wear it as the ruler of the city. Meanwhile, \Gls{Hex} is put to task
finding the location of \Gls{Rince}, at the behest of the inner council, who want to retrieve him
so they can send back the huge Agatean cannon that they inadvertently received during the
teleportation process.

\subsubsection{\Gls{Cohen} and the barbarians prepare for the battle at dawn}
\Gls{Cohen} and the Silver Horde discuss their chances in the coming fight, and reject
\Gls{Saveloy}'s offer of a tactical retreat. \Gls{Saveloy} eventually realizes that death in the
field of battle is preferable to life as a school teacher, and pledges to fight beside \Gls{Cohen},
in spite of having no knowledge about war.

\subsubsection{\Gls{Rince} is reunited with the \Gls{Lugg}}
\Gls{Rince} repeatedly tells the Red Army that there are no Great Wizards ready to perform feats of
magic to solve their problems, and that the barbarians are foolish for taking on astronomical odds
on the battlefield. He decides to desert the city, and is joined by the \Gls{Lugg} and its mate.

\subsubsection{\Gls{Cohen} parleys with \Gls{Hong}}
\Gls{Cohen} parleys with \Gls{Hong} before the battle, causing \Gls{Saveloy} some amusement as he
asks for the Agateans to surrender and avoid unnecessary death. Afterward, \Gls{Truckle} speculates
that the enemy warlords might want them alive, making it easier for them to slaughter the enemy
troops.

\subsubsection{\Gls{Rince} gets to the top of the small hill outside Hunghung}
\Gls{Rince} talks to a farmer next to the circular hill outside Hunghung, and learns that he has no
conception of the impending change in rulership, given how much his life is confined to his
farmland. He walks to the small hill, to find a rusty building in ruins. He takes no notice of the
sapient pears growing in large numbers at its base, and climbs the hill, as a thunderstorm gathers
over Hunghung.

\subsubsection{\Gls{Hong} decides to take charge of the battle}
\Gls{Hong} is incensed by the warlords hesitating to charge the barbarians head on, and of the
reports of increasing desertion among their armies. He decides to lead the charge himself, and
dismisses the new rumours stating that the barbarians are the Indestructible Great Sages from some
distant land.

\subsubsection{\Gls{Rince} falls into the cavern underneath the hill}
\Gls{Rince} holds on to a rotting log, as the ground beneath him starts to give way, indicating an
uncertain fall in the darkness. He spots a small yellow butterfly landing on his hat and shoos it
away. As self defense, the butterfly of chaos summons a miniature thunderstorm to haunt \Gls{Rince},
and causes the log holding him up to collapse.

\subsubsection{\Gls{Rince} navigates through the dark cave}
\Gls{Rince} spots a large warrior staring at him when he lights a match to dispel the darkness
inside the cave. Meanwhile, \Gls{Cohen} notices the strange yellow cloud approaching from the
horizon, and marvels at the swarm of butterflies as they approach the hill outside Hunghung.
\Gls{Rince} stumbles around in the dark cave, and pulls a lever he finds, believeing it could not
possibly be a trap.

\subsubsection{\Gls{Cohen} and the horde face off against \Gls{Hong}'s elite warriors}
\Gls{Cohen} and the Silver Horde charge into the Agatean army, who refuse to engage them out of
fear for the closing thunderstorm. The storm induced by the swarm of chaos butterflies starts to
send lightning down into the massed ranks of the Agatean army, forcing them to back off. \Gls{Hong}
arrives with his samurai warriors, only to see the barbarians cut them down as \Gls{Cohen}
distracts them with a party trick.

\subsubsection{\Gls{Rince} dons the magical armour of \Gls{OSMirr}}
\Gls{Rince} sees some magical globes suspended from the ceiling absorb the lightning from the storm,
and illuminate the cavern. He notices a large pool of mercury, with an ornate gold sarcophagus on
its edge, bearing the inscription \Gls{OSMirr}, the founding Agatean Emperor. He dons the magical
armour and stands up, noticing the Red terracotta Army wake up from their magical slumber.

\subsubsection{\Gls{Hex} outputs the spell to retrieve \Gls{Rince}}
\Gls{Stibb}'s request for the spell to retrieve \Gls{Rince} goes wrong, when a butterfly of chaos
lands on \Gls{Hex}, disturbing one of its computational ants with a drop of nectar. He believes that
naming the machine, might have induced some unintentional sentience in it, as his assisstant informs
him of \Gls{Hex} providing answers for questions he had not asked it yet.

\subsubsection{\Gls{Cohen} and the Silver Horde are saved by the Red terracotta Army}
\Gls{Rince} tests out the controls in the magical gloves, allowing him to control the Red Army, and
is pleased that they are on his side. Meanwhile, the Red terracotta Army rise from the ground to
march on the Agatean army, scattering the five warlords into chaos and mutual suspicion. \Gls{Cohen}
and the barbarians decide to return to the palace, believing \Gls{Hong} is also headed there. The
gathering clouds burst, making the battlefield muddy, and making it even more difficult for the
five Agatean clans to distinguish each other's uniforms.

\subsubsection{\Gls{Cohen} officially becomes the Agatean Emperor}
\Gls{Cohen} walks into Hunghung through the gates, with some Red Army golems acting as an honor
guard. He asks \Gls{Saveloy} to make a proclamation ending chattel slavery, and giving a fair share
of the profits to the peasants. \Gls{Cohen} sits down on the Agatean throne, with \Gls{SixBW}
announcing to the court that he has been accepted as the reincarnation of \Gls{OSMirr}. Meanwhile,
\Gls{Rince} tries to use the terracotta golems to scribble on the city walls that he needs help
taking off the magical armour.

\subsubsection{\Gls{Twofl} works out \Gls{Rince}'s desperate attempt to ask for help}
\Gls{Saveloy} is dismayed to learn that there can be no empire without a cleansing of the old guard,
and is amused by a terracotta golem walking into the throne room and doing charades. \Gls{Twofl}
recognizes \Gls{Rince} trying to send a message, and rescues him from the mudslide in the tomb of
\Gls{OSMirr}. He tells \Gls{Rince} that \Gls{Cohen} has offered him the position of Chief Wizard,
given how he reanimated the terracotta army to turn the tides of battle.

\subsubsection{\Gls{Rince} is paraded in front of \Gls{Cohen} by \Gls{Hong}}
\Gls{Hong} kidnaps \Gls{Rince} as he walks back to the palace with \Gls{Twofl}, and tells him that
will be publicly executed to send a message to the people about the false myth of the Great Wizard.
\Gls{Hong} holds \Gls{Rince} hostage as \Gls{Cohen} comes out of the palace to face him, just as
\Gls{Stibb} casts his teleportation spell, making \Gls{Rince} vanish into thin air.

\subsubsection{\Gls{Twofl} decides to confront \Gls{Hong} for the murder of his wife}
\Gls{Twofl} tells his daughters that \Gls{Hong}'s men had killed their mother many years ago in some
minor scuffle, and declares his vengeance. As \Gls{Hong} draws his sword, amused at the clerk's
inability to handle his own blade, the ornate cannon arrives at \Gls{Rince}'s position, with its
fuse lit, and blows him to pieces when it fires.

\subsubsection{\Gls{Stibb} realizes that his teleportation spell has misfired}
\Gls{Twofl} sees the \Gls{Lugg} arrive with its mate and their children, as \Gls{Cohen} appoints him
Grand Vizier. He is eager to take on his new role in the court, as a valkyrie takes \Gls{Saveloy}
towards a barbarian conception of heaven. Meanwhile, \Gls{Stibb} realizes that his spell has gone
wrong, leading to a three way substitution, with \Gls{Rince} being teleported to the unknown
continent of XXXX, and a strange beast sent to the Unseen University in his place.

\subsubsection{\Gls{Rince} ends up in XXXX as a result of \Gls{Hex} botching its calculations}
The inner council discourage \Gls{Stibb} from searching for \Gls{Rince} again, and trying to
retrieve him, afraid of what strange object might fly into them next time. Meanwhile, \Gls{Rince}
is shaken awake in XXXX by some tribal men wearing loincloths and pointing spears at thim. They
give him a boomerang, which he throws away with all the force he can muster, tired of going on any
more adventures.


\section{The Last Continent}


\subsection{}
\subsubsection{The \Gls{Libra} suffers from a magical shape-shifting illness in the Unseen
    University}
The inner council of Unseen University watch over the \Gls{Libra}, as he struggles with a magical
disease that makes him morph unpredictably into a variety of objects. \Gls{Stibb} tries to explain
to \Gls{Ridcu} that the \Gls{Libra} is highly vulnerable to the illness, since he has already been
morphed from a human to an orangutan. They lose hope in the \Gls{Libra}'s recovery, and wander off
to let him rest.

\subsubsection{\Gls{Stibb} works on his unseen books initiative using \Gls{Hex}}
A miner in some mine discovers a box shaped opal deposit deep underground, and is shocked when
little feet drop out from its bottom surface and start to wriggle their toes. Meanwhile, \Gls{Stibb}
gets to work reading pages from unwritten books, by exploiting the time delay between trying
something impossible, and the universe moving its causality particles to make the newly tried thing
extremely difficult.

\subsubsection{\Gls{Ridcu} happens upon \Gls{Stibb} and his book of micromanagement}
\Gls{Ridcu} gets to work implementing his new leadership program, and starts to take a keen interest
in the daily lives of the inner council, leaving them irritated at the intrusion. \Gls{Stibb} is
woken up one night by a commotion at the library entrance, and learns that the books have barred
entry to all wizards, with the \Gls{Libra} no longer there to placate them.

\subsubsection{The inner council realize they have no way of knowing the \Gls{Libra}'s name}
The \Gls{Dean} suggests using some magic to heal the \Gls{Libra}'s illness, but \Gls{Runes} points
out the need to know his real name before trying anything. \Gls{Ridcu} is dismayed to learn that no
one knows the \Gls{Libra}'s name, and that he has torn out any reference to it in order to stop the
others from turning him back into a human.

\subsubsection{\Gls{Ridcu} and the inner council decide to try and locate \Gls{Rince}}
The \Gls{Libra} approaches the library entrance, and suddenly morphs into a tome with a furry
leather cover. \Gls{Stibb} points out that the illness is making him morph into objects as a crude
form of camouflage, as \Gls{Indef} remembers the time when \Gls{Rince} had been assisstant librarian
and was likely to know his real name.

\subsubsection{The inner council of wizards search the chambers of the geography professor}
Realizing that \Gls{Rince} is stuck on the mythical continent of XXXX, \Gls{Ridcu} leads the inner
council through the University's endless corridors, until they arrive at a geography professor's
room. The council barge into the professor's room, and notice sounds of water splashing from the
attached bathroom. After spending some time persuing through his books for mentions of XXXX, they
decide to open the bathroom, and find a portal to some tropical beach.

\subsubsection{\Gls{Rince} stumbles his way through the arid desert of XXXX}
\Gls{Rince} eats some insects salvaged from a water-hole, as the dry desert drains his energy day
after day. He is puzzled by the small indigenous tribes acting hostile the moment he starts to make
polite conversation by talking about the weather, as a mysterious spirit keeps an eye on him from a
nearby water-hole. \Gls{Rince} fails to notice the spirit keeping him alive and hydrated by ensuring
he always ends the day next to a water source, as he fills in the latest entry in his journal.

\subsubsection{\Gls{Rince} sleeps on the deserts of XXXX}
As \Gls{Rince} settles down to sleep, the land itself animates, to go check on the mine where the
opal encrusted \Gls{Lugg} had been unearthed, and starts to form some patterns on a rock next to
\Gls{Rince}. Meanwhile, the miners hastily climb out of the mining shaft, with the \Gls{Lugg}
following them soon after.

\subsubsection{\Gls{Death} is amused by the sheer danger in the biosphere of Terror Incognita}
\Gls{Death} asks his model of the Disc to zoom in on \Gls{Rince}, and is amused to see him stuck on
the forbidding continent of Terror Incognita. His butler \Gls{Albert} describes it as a hot, arid
land surrounded by a permanent anti-cyclone, thus guaranteeing zero precipitation. \Gls{Death}
walks into his library, and is buried under an avalanche of books in response to his request for
the dangers of Terror Incognita. He then asks for the list of harmless creatures and receives a
single piece of paper with some sheep drawn on it.

\subsubsection{\Gls{Ridcu} observes the portal to the beach}
\Gls{Stibb} is amazed at the two way wormhole created by the professor of geography, allowing him
to get his suntan on the beach leading out of his chamber. He immediately starts to think about
perpetual motion machines that might be built using a pair of such portals, as the others in the
council debate the idea of exploring the beach directly.

\subsubsection{\Gls{Ridcu} leads the inner council into the geography professor's beach}
\Gls{Ridcu}'s inner angler is roused by \Gls{Indef} describing the varied fish and sharks inhabiting
the rimward seas, as the rest of them prepare to spend some time on the beach, hoping to improve the
\Gls{Libra}'s condition. \Gls{Ridcu} insists that they are not using the beach as a vacation, as
they come up with flimsy excuses to research the fauna and the natives in the unknown coastline.

\subsubsection{\Gls{Rince} spots a tribal warrior watching him sleep}
\Gls{Rince} wakes up to see a heavily armed tribal warrior observing him, and walking away into the
desert the moment he tries to make conversation. Later, a disembodied voice casts a spell on him,
after telling him that he will be able to find food underneath some nearby shrubbery. The shapes on
the rock made by the sentient desert spirits fade away, as \Gls{Rince} eats the chicken sandwich
buried under the shrubs.

\subsubsection{\Gls{Rince} becomes the unwitting pawn of a trickser spirit of Terror Incognita}
On the other side of the rock, the trickster spirit appears on the desert in his own dimension,
and asks his pet bird to guide \Gls{Rince} to the object he was interested in stealing. He tells
the bird that a hero is necessary, since he cannot be accused of interfering directly in the
Discworld's affairs.

\subsubsection{The \Gls{Libra} watches his colleagues enjoy their time on the beach}
The \Gls{Libra}, now restored to his ape form by the lush vegetation of the beach, looks at the
plants and birds surrounding him, and feels uneasy about the whole thing. He notices the portal
through which they had originally come to the beach, now propped open by \Gls{Ridcu} using a wooden
plank with a warning written on it.

\subsubsection{\Gls{Whitlow} strands the inner council on the tropical beach}
\Gls{Rince} sees a kangaroo hop up to him, and start to talk about some important mission that he
was needed for. He pre-empts it, by running away, and falls into a dark pit, as it keeps up with him
using its powerful legs. Meanwhile, the head housekeeper of the university, \Gls{Whitlow}, shows up
at the window shaped portal to the beach, and tries to climb through. When the wizards ask her for
some food, she returns with a large tray and accidentally closes the portal by knocking over
\Gls{Ridcu}'s plank.

\subsection{}
\subsubsection{\Gls{Rince} and \Gls{Scrappy} look at the underground cave}
In the waterhole, \Gls{Rince} notices the absence of any flies, and sees a small lake underground,
together with the collapsed remains of a tunnel network. \Gls{Scrappy} points out a cave painting
resembling a group of University wizards, and tells him that it wasn't there a week ago. \Gls{Rince}
realizes he has been receiving help from an unknown source with his uncanny luck in finding food
under rocks, and water sources every night.

\subsubsection{\Gls{Ridcu} realizes the extent of the trouble they are in}
\Gls{Ridcu} gets to work fishing for dinner, as the rest of the wizards try to forage for food and
fresh water. \Gls{Whitlow}, convinced that the council is pulling a harmless prank on her, starts to
get anxious about returning to the university. Meanwhile,

\subsubsection{\Gls{Scrappy} talks about the trouble in the last continent}
\Gls{Scrappy} tries to tell \Gls{Rince} that Terror Incongnita was the last continent to be
designed, and had different rules of space and time. \Gls{Rince} fails to make sense of the assetion
that his arrival on the continent had changed history thousands of years ago, leading to trouble in
the present. \Gls{Scrappy} then tells him that it is his mission to integrate the continent into the
rest of Discworld by righting the wrongs.

\subsubsection{The inner council find some strange food in the forest}
\Gls{Indef} arrives from the nearby forest with some nuts and berries, including a curious looking
cigarette. \Gls{Ridcu} is desperate to find the bush where the cigarettes grow, and immediately
lights one up, to relieve his nicotine itch. The rest of the council are surprised to see fruits
having baked confections stuffed inside them, as the others notice the \Gls{Bursar} gorging on the
nuts.

\subsubsection{\Gls{Scrappy} talks about rescuing the last continent}
\Gls{Scrappy} tells \Gls{Rince} that he as already saved the continent, just that the jumbled nature
of time makes it so that he must be egged on to do it again to complete the causal loop. \Gls{Rince}
is annoyed at the tedium of a trek through the dangerous desert, and learns that his mission will
have succeeded when the continent receives rainfall again.

\subsubsection{\Gls{Rince} decides to run away from the underground oasis}
\Gls{Scrappy} explains that someone had come along and added the last continent as a sneaky extra
after the \Gls{Creat} had initially designed the Discworld. \Gls{Rince} pretends to sleep as night
falls, and waits till \Gls{Scrappy} leaves him alone to run away from the underground cave. A
drawing of \Gls{Scrappy} fades away at a nearby rock, satisfied that \Gls{Rince} has inadvertently
embarked on the mission.

\subsubsection{The inner council scavenge a meal for the night}
\Gls{Whitlow} eats at a makeshift table made out of wood, as the rest of the wizards dine on the
local enchanted flora at a campfire. They notice the empty pair of boots, seemingly belonging to
the geography professor, and surmise that the desserts are an after-effect of his magic. Meanwhile,
the \Gls{Libra} notices something important about the island, but sneezes and turns into a giant
conch before he can inform the council.

\subsubsection{\Gls{Stibb} argues with \Gls{Ridcu} about evolution}
\Gls{Stibb} realizes that the \Gls{Libra} had been trying to point out the fact that there was
only one of each kind of tree or fish, and that there was not time for evolution to take its course
naturally. All of a sudden, an alligator-like creature emerges from the forest, and charges at the
wizards. \Gls{Ridcu} and the rest prepare their magic, even as \Gls{Stibb} questions the ethics of
killing an endangered animal.

\subsubsection{\Gls{Rince} meets up with the dwarf named \Gls{Mad}}
The monster turns into a chicken after undergoing rapid changes in its shape, and \Gls{Ridcu}
decides to cook it using the fireball he had charged up. Meanwhile, \Gls{Rince} runs into an armored
cart being pulled by a team of horses, and gets captured by the dwarf riding it. The dwarf calls
himself \Gls{Mad}, and asks \Gls{Rince} to hold off some pirates pursuing him with a crossbow.

\subsubsection{\Gls{Mad} and \Gls{Rince} flee the desert pirates}
\Gls{Mad} tells \Gls{Rince} that he has been journeying through the roads of Terror Incognita for
many years, and warns him of the emu-riding gangs giving chase. \Gls{Rince} is almost killed by
the gang's arrows, as \Gls{Mad} prepares the supercharger for his carriage. Another pirate on a
camel falls off his mount all of a sudden, causing a pile up that destroys all of the pirate wagons.

\subsubsection{\Gls{Rince} learns about the vagaries of life in the XXXX desert}
\Gls{Rince} and \Gls{Mad} inspect the wreckage of the pile-up, with the camel grazing nearby.
\Gls{Mad} inspects and discards several shoddy weapons used by the pirates, and asks \Gls{Rince}
to take the bale of hay to his cart, recognizing it as quality feed for his horses. \Gls{Rince}
finds the pirate's corpse, and notices a large spider hidden in his robes, as he retrieves his
hat.

\subsubsection{\Gls{Stibb} is frustrated by the old heads in the inner council}
\Gls{Stibb} tries and fails to get the council to take him seriously, as his hypotheses about
evolution are dismissed without a second thought. He asks the \Gls{Libra} if he has noticed the
absence of any flotsam in the driftwood they found, and is dismayed when the \Gls{Libra} morphs
into a furry red penguin. The wizards retire for the night, after constructing a hut for
\Gls{Whitlow}, and \Gls{Stibb} is left to stand guard.

\subsubsection{\Gls{Rince} talks about precipitation with \Gls{Mad}}
\Gls{Rince} asks \Gls{Mad} about his early life, and learns that the dwarf migrated to the mainland
of XXXX from the nearby island city of Nothingfjord, after their voyage was hit by a sea-storm.
\Gls{Mad} is incredulous at \Gls{Rince}'s suggestion that rainfall is real, and that water falls
from the sky. He insists that water belongs deep underground, and asks how something as heavy as
water rises so high in the first place.

\subsubsection{\Gls{Stibb} tells the inner council that they are stuck in the distant past}
\Gls{Stibb} works out the fact that the portal has taken them many millennia in the past, from the
change in the night sky, and tries to tell the rest of the wizards that they could end up changing
the future unintentionally. \Gls{Ridcu} remains obtuse when presented with the idea of accidentally
killing his own ancestor, and thus erasing his own existence.

\subsubsection{\Gls{Ridcu} and \Gls{Stibb} argue about the nature of predestination}
\Gls{Ridcu} comes up with the idea of determinism, and tells \Gls{Stibb} that they cannot actually
do anything to change history, since that would mean they could not come back to the past to make
that change in the first place. He tells the other wizards not to worry about affecting the future,
as \Gls{Stibb} conceals his anger at the cavalier attitude of the Archchancellor.

\subsubsection{The \Gls{EGod} decides to hasten the wizards' escape from his island}
The \Gls{EGod} ponders the idea of shooing away the intruders on his island, as he congratulates
himself on the rapid evolution of his custom-designed cigarette bush. He gets back to work
designing more bizarre plants, in his temple on the mountain deep inland. Meanwhile, \Gls{Mad} leads
\Gls{Rince} to the largest settlement in XXXX, which turns out to be a small street and a single
run-down tavern.

\subsubsection{\Gls{Dean} and the other wizards are alarmed by the trees showing up around them}
The \Gls{Dean} and the other council members talk about their failure to find a library on the
island to help them learn how to build a boat, as \Gls{Ridcu} gets to work exercising first thing
in the morning. \Gls{Indef} makes note of the bizarre flora that \Gls{Stibb} has found for
breakfast, and wishes to get off the island as soon as possible.

\subsubsection{\Gls{Dongo} talks to \Gls{Rince} about the local liquor}
The half-crocodile barman, \Gls{Dongo}, tells \Gls{Rince} that they have some quality beer, as he
notices the other half-animal denizens of the tavern. A while later, \Gls{Mad} enters the bar to
ask another customer to put down \Gls{Rince}, and takes out his crossbow to prepare for the
inevitable bar-fight.

\subsubsection{The \Gls{Bursar} finds a strange log throbbing with fluid}
The \Gls{Bursar}, tired of \Gls{Ridcu}'s enforced morale-building exercises, temporarily shakes
out of his insanity, to stomp on some ants that might be lead to \Gls{Ridcu} never existing. He
follows a long stem lying on the ground, that sounds like a pipe with liquid flowing through it.
Meanwhile, \Gls{Ridcu} is happy to see the rest of the wizards find a log suitable for building a
raft.

\subsubsection{\Gls{Rince} wakes up from a night of heavy drinking}
\Gls{Rince} wakes up the next day hungover, and tries to recall the details of \Gls{Mad} fighting
some animals at the tavern. \Gls{Scrappy} tells him that his mission is still waiting, as he notices
more etching representing the council of wizards on a makeshift toilet behind the bar. He decides to
head to the town of Bugarup, believing it might have a port, and some ships to take him home.

\subsection{}
\subsubsection{\Gls{Ridcu} and the wizards find the boat made of pumpkin}
The \Gls{Bursar} tries to explain to \Gls{Ridcu} that he has found a ship floating along the
coast, complete with sails, and a mermaid-shaped figurehead. \Gls{Wrangler} is flustered by
\Gls{Whitlow}'s sarong, as she asks them for directions to a pool inland. Meanwhile, the wizards
inspect the pumpkin-ship, with \Gls{Ridcu} voting for an immediate escape from the island.

\subsubsection{\Gls{EGod} talks to the inner council of wizards}
The \Gls{EGod} materializes as a three-foot tall old man in white robes, and tries to threaten
the wizards with dire consequences, unless they flee his island. \Gls{Ridcu} refuses to take him
seriously, as he narrates his tale of despair and hopelessness, bemoaning the spread of organized
religion. He had decided to leave his dwindling group of followers and come back to the small
island, to put his practice of gene splicing and evolution to work designing a better world.

\subsubsection{\Gls{Ridcu} and the other wizards prepare to leave the island}
\Gls{Ridcu} suggests that there might be multiple Gods of evolution, and that the best among them
might eventually win, leading to the \Gls{EGod} vanishing. \Gls{Stibb} realizes that he might have
hit upon the idea of natural selection by competition, as the final puzzle piece to his idea of
evolution. \Gls{Stibb} is dismayed at the eagerness of the other wizards to set sail immediately,
ignoring the island's potential as a research subject.

\subsubsection{\Gls{Rince} wakes up from his drinking binge}
\Gls{Rince} tries to recall the events of last night, as he wakes up from his blackout. \Gls{Dongo}
tells him that he had placed an outrageous wager last night in a sheep shearing face-off against a
local champion, after blowing all the money \Gls{Mad} had given him in betting on coin tosses.
He notices the poster with \Gls{Scrappy} changing in place, with the kangaroo vanishing, and
eventually reappearing facing the opposite direction.

\subsubsection{\Gls{Rince} goes to the sheep pen to make good on his bet}
The \Gls{Lugg} walks along a desert track, unsure of where to go in search of its owner, and is
picked up by a purple carriage, bearing the name Desert Princess. Meanwhile, \Gls{Rince} makes a
mess of his first sheep, making the assembled shearers suspect his ability to win the challenge.
\Gls{Daggy}, the head shearer, tells him that the challenge is simply one of speed, and backs off
as a huge ram paces towards them from the pen.

\subsubsection{\Gls{Scrappy} helps \Gls{Rince} win his shearing challenge}
\Gls{Scrappy} whispers to \Gls{Rince} that the sheep will be enchanted into cutting their fur
automatically on his shears, and disappears into the barn's rear wall. \Gls{Rince} wins the
challenge, and the sheares tell him that they do not have the money yet. He rejects the reward, and
asks for the fastest way to Bugarup. Terrified of his magic, the shearers give him their only horse,
named \Gls{Snowy} and point him in the direction of the coastal city.

\subsubsection{\Gls{Ridcu} inspects the melon-boat as the others load supplies}
One of the shearers asks \Gls{Daggy} if he has indeed owned \Gls{Snowy} for many years, and if his
story of winning it off someone in a bet is a false memory. He tries to think through the fog in
his mind, and gives up, accepting whatever he had just said as the truth. Meanwhile, \Gls{Ridcu}
learns of \Gls{Stibb} wandering off into the island, and decides to look for him. He believes that
\Gls{Stibb} is miffed at their decision to leave the island, instead of probing its secrets further.

\subsubsection{\Gls{Rince} helps some sheep with groundwater}
\Gls{Rince} comes across a broken-down windmill, and finds a herd of thirsty sheep looking at him
for water. He decides to dig into the ground, and finds a dwindling reservoir. He manages to carry
some of the groundwater to a trough for the sheep, and notices \Gls{Snowy} unperturbed by all the
commotion. A while later, he comes across a well-worn trader track, and spots a group of horsemen
chasing some wild horses through the desert cliffs.

\subsubsection{\Gls{Snowy} accidentally corners the herd of wild horses}
\Gls{Snowy} reaches a steep canyon, and walks down the wall nonchalantly, before scaling the
opposite wall with equal ease. \Gls{Rince} hangs on desperately, recalling \Gls{Daggy}'s words about
the breed being selected for its sure-footedness, as \Gls{Snowy} walks upside down onto an overhang.
Eventually, \Gls{Snowy} manages to engineer a small rockslide to trap the wild horses in a narrow
canyon, just as the herders catch up. They marvel at \Gls{Snowy}'s skills, and offer to buy the
horse off \Gls{Rince}.

\subsubsection{\Gls{Rince} sets off to Bugarup with help from \Gls{Remorse} and \Gls{Clancy}}
\Gls{Remorse}, the lead shepherd, tells \Gls{Rince} that Bugarup is a dangerous place, as his
underling \Gls{Clancy} talks about rangers in the desert who might help him on the way. \Gls{Rince}
refuses their offer of hospitality, and is grateful for the bag of rations they give him, along with
some cash for herding the wild horses. He sets off in the direction of Bugarup, leaving the
horsemen to discuss the fine art of metaphor as an adjective.

\subsubsection{\Gls{Stibb} talks to the \Gls{EGod} in his mountain abode}
\Gls{Stibb} walks into the workshop of the \Gls{EGod} at the top of his mountain, and notices an
elephant being assembled. He points out the futility of wheels on the elephant, leading the
\Gls{EGod} to design another beetle to deal with his despondence. \Gls{Stibb} realizes that the
\Gls{EGod} has not worked out reproduction, and is designing the next iteration of each creature by
hand, making whatever improvements he deems necessary.

\subsubsection{\Gls{Ridcu} and \Gls{Whitlow} talk to the \Gls{EGod}}
\Gls{Ridcu} and the other wizards walk into the workshop, just as \Gls{Stibb} tries to explain
reproduction to the \Gls{EGod}, and makes him realize that a lot of his workload might be dealt with
if his creations could make copies of themselves. \Gls{Whitlow} walks in to explain reproduction to
the \Gls{EGod}, satisfying his curiosity, and convincing him to let the wizards leave his cave.
\Gls{Stibb} chooses to stay on as the god's assistant, as \Gls{Ridcu} and the inner council take
their leave.

\subsubsection{\Gls{Ridcu} and the council return to the melon-ship}
On their way back to the melon-ship, the wizards discuss the idea of sexual selection, and wonder
how the \Gls{EGod} will work with the idea of attractive traits in different species. \Gls{Ridcu}
is glad that a wizard from the Unseen University will contribute to the design of all life on the
island, as he leads the rest of them down the mountain.

\subsubsection{\Gls{Rince} invents vegemite and gets caught by rangers}
\Gls{Rince} dumps his supply of beer into a cooking pot filled with vegetables, and passes out from
exhaustion as it stews overnight. The next morning, he finds some sheep wandering into his camp,
hungry for food, and looks at the brown sludge left in the pot (vegemite). He digs another hole in
search of groundwater, and finds himself surrounded by armoured horsemen pointing crossbows at
him.

\subsubsection{\Gls{Stibb} is happy to participate in the design of intelligent life}
\Gls{Stibb} is happy to learn that the \Gls{EGod} is working on a fancy project, involving an
adaptable and resourceful life-form that is not confined to one habitat, or to one food source. He
eagerly walks into the hidden chamber with the \Gls{EGod}, expecting to find some sort of prototype
human, and is shocked to see a cockroach.

\subsubsection{\Gls{Stibb} reunites with the inner council of wizards}
The wizards on board the melon-ship fall over each other in their attempts to serve \Gls{Whitlow},
as \Gls{Ridcu} notices the \Gls{Libra} turn into a deck chair when he boards the ship. After a
while, \Gls{Stibb} swims out to the ship, horrified by the cockroach that the \Gls{EGod} had
claimed as his masterpiece.

\subsubsection{\Gls{Rince} is captured pending execution}
\Gls{Rince} learns from the jailer that he is to be hanged the next morning for the crime of
sheep-stealing, and is amused to find the sheep in the same jail cell. One of the song-writers
prepares a song to memorialize him for his crimes, and lets slip the fact that another prisoner had
managed to break out of the same jail cell multiple times. \Gls{Death} materialized in front of
him a while later, and tells him that he is due to escape his hanging, before vanishing through a
wall.

\subsubsection{\Gls{Rince} escapes the jail cell after \Gls{Death} tells him that he will live}
\Gls{Rince} sees a message scribbled on the jail cells's ceiling, telling him to undo the hinges to
the cell door. He decides to try lifting the heavy door off its hinges, hoping to put them back in
place after he slips out. After \Gls{Rince} leaves the jail cell in Bugarup city, the sheep in his
cell dissolves into the wall, becoming a painting of \Gls{Scrappy} before fading away.

\subsubsection{\Gls{Ridcu} talks to \Gls{Stibb} about the side effects of strong magical fields}
\Gls{Stibb} notices the perpetual storm-front encircling XXXX, and wonders if the intense magical
field is going to affect the wizards. He starts to grow irritable, and the \Gls{Dean} becomes
civil, causing \Gls{Ridcu} to suspect the handiwork of the magical field. The ship hits the
storm-front, just as \Gls{Ridcu} sees the excessive magic in the air surrounding them.

\subsection{}
\subsubsection{\Gls{Rince} talks to \Gls{FGDibb} outside the prison}
Out in an alley beside the prison, \Gls{Rince} runs into \Gls{FGDibb}, yet another member of the
expansive Dibbler diaspora, and immediately starts to see through his sales pitch. He decides to
buy one of \Gls{FGDibb}'s meat pies, and is spotted by a patrolling guardsman as he is distracted
by the pie's flavour.

\subsubsection{\Gls{Rince} manages to evade the pursuing guardsmen}
\Gls{Rince} finds the opera house of Bugarup next to the harbour, and enters it, afraid of the
heavy footsteps closing in from the city center. The chef at the opera house mistakes him for a
substitute cook, and tasks him with designing a gimmick dessert for the prima donna in their next
big show.

\subsubsection{\Gls{Whitlow} and the wizards lose their ship in the rough seas}
A fight breaks out on the melon-ship, as it breaches through the storm-front, and comes in view of
the XXXX coast. \Gls{Whitlow} decides to let the wizards float along on the pumpkin seeds, and
swims for the shore, disregarding the warnings about sharks. Meanwhile, \Gls{Ridcu} gets into an
argument with the \Gls{Dean} and the \Gls{Indef} about who fired the magic that breached the ship's
hull, as \Gls{Stibb} spots the sharks also heading for the shore.

\subsubsection{\Gls{Rince} notices some guardsmen passing by the opera house}
\Gls{Rince} hides in the depths of the kitchen, as the guardsmen come searching through the street,
as the head chef \Gls{Ron} tells them about the night's show reaching half-time. \Gls{Charley}, the
cook originally in charge of making dessert, comes up with some suggestions for peach and ice cream,
which \Gls{Rince} agrees to.

\subsubsection{\Gls{Rince} learns of the bizarre traditions of XXXX}
\Gls{Rince} invents a new dessert, just in time for the jailer to barge into the kitchen, and
threaten \Gls{Rince} with dire consequences once he gets caught. He is amused to hear that the
guards will give him a ten second head start, so that the ballads singing of his last stand can be
suitably heroic. \Gls{Rince} decides to defy their traditions of a fight to the death, and runs for
the safety of the harbour.

\subsubsection{\Gls{Rince} runs into \Gls{Letitia} in the grand carnival of Bugarup}
\Gls{Scrappy} appears in front of \Gls{Rince} to remind him that a legend was steadily being
built up around his exploits, and that he was close to becoming the hero that the continent needed.
He then runs into a carnival, where \Gls{Letitia}, one of the carnival float managers, takes him
on board her carriage.

\subsubsection{\Gls{Rince} is reunited with the \Gls{Lugg}}
\Gls{Rince} sees the crowds gathering around the carnival procession, and hopes that the city
watch will find it difficult to track him down. Someone in the crowds recognizes him from his
wizard's hat, and he is forced to bid goodbye to \Gls{Letitia}, and jump off the carriage. He runs
into a dead end alleyway, with some guardsmen who recognize him, just as the \Gls{Lugg}, now wearing
hundreds of heels on its feet, lands next to him from \Gls{Letitia}'s wagon.

\subsubsection{\Gls{Stibb} and the wizards reach the shores of XXXX}
The wizards crash into the beach, after being sucked into an undersea current that spits them out
close to the shore. Meanwhile, the \Gls{Bursar} elegantly surfs a wave using his melon-seed, and
lands on his feet, before wandering off inland. \Gls{Ridcu} accidentally melts a rock when he tries
to demonstrate a small fireball to lift the spirits of his council. \Gls{Stibb} reminds him of the
intense magical field pervading the continent, and of how the place still had no vegetation.

\subsubsection{\Gls{Stibb} is shown a glimpse of his mortality}
\Gls{Stibb} morphs into an old man under the influece of the magical instability, just as the other
wizards morph into children. A while later, as they manage to regain control of their minds, and
morph back to their old forms, \Gls{Stibb} comments on the physical weakness he felt as an old man,
and immediately sets about finding the \Gls{Creat} in charge of designing the place.

\subsubsection{The \Gls{Bursar} finds a \Gls{Creat} making life on the continent}
\Gls{Whitlow} joins the wizards with the \Gls{Libra} in her arms, now morphed into a baby orangutan.
\Gls{Ridcu} warns her to loosen her clothing as her own temporal instability resolves, returning her
to her original age. Meanwhile, the \Gls{Bursar} wanders into a forest, where an old black man
draws on a cliff wall, using simple white paint, and creates new life from the very lines of his
artwork.

\subsubsection{\Gls{Rince} learns about \Gls{Neilette}'s past}
\Gls{Rince} finds \Gls{Neilette} hiding inside the \Gls{Lugg}, after it beats up the guardsmen in
the alley. She talks about her brother coming out as a transgender woman, and their father disowning
him for it. She then mentions the beer factory that had failed, leaving the family destitute, and
forcing her to find work in \Gls{Darleen}'s troupe.

\subsubsection{\Gls{Rince} escapes the brewery as it collapses in a fiery ruin}
\Gls{Rince} sees another earthquake start to collapse the brewery, and hides inside the \Gls{Lugg}
with \Gls{Neilette}. A while later, as the city watch try to put out the burning brewery and find
the water pumps running dry, \Gls{Rince} asks \Gls{Neilette} if there is a University for wizards in
the city. She says yes, before mumbling about how useless they are, and agrees to help him find
the place.

\subsubsection{\Gls{Rince} sneaks into the University of Bugarup}
\Gls{Ridcu} and the council find the \Gls{Bursar} and the old man painting the animals, and get to
work drawing a duck. They accidentally design the duck-billed platypus, as they revise each other's
drawings, adding their own touches to the figure. Meanwhile, \Gls{Rince} finds a secret side
entrance into the University of Bugarup, and walks in, to find the inner council mistaking him for
a demon. They ask him about the water table receding, and are shocked when he mentions the idea of
rainfall.

\subsubsection{\Gls{Rince} marvels at the magical tower of the Bugarup University}
\Gls{Rince} learns of the failed attempts at summoning clouds, and tells the Archchancellor that
his university's tower is very small. Miffed by the insult, the Archchancellor takes him to the
top of the tower, which turns out to be a hundred times higher than it looks from the outside.
Meanwhile, \Gls{Stibb} helps the \Gls{Libra} untangle himself from a string toy, as he plays with
the other objects in his leather sack.

\subsubsection{\Gls{Rince} meets his distant cousin \Gls{BillR}}
\Gls{Stibb} notices the \Gls{Creat} draw the council of wizards using his enchanted white paint, as
the rainfall stops and night falls on the land. Meanwhile, the Archchancellor of Bugarup University,
named \Gls{BillR}, offers some beer to help \Gls{Rince} unwind, and is dismayed to hear more talk 
of precipitation. He decides to take \Gls{Rince} to the abandoned brewery, to investigate the
drawing of the council of wizards.

\subsubsection{\Gls{Rince} descends into the cellars under the brewery}
\Gls{Rince} climbs down into the brewery's cellar, now drunk on beer, and is happy to see the 
\Gls{Lugg} join him. \Gls{BillR} and his council descend shortly after, with some meat pies from 
\Gls{FGDibb} per \Gls{Rince}'s request. \Gls{Rince} keeps himself in a constant state of tipsiness,
which allows him to think clearly about the cave system underneath the city.

\subsubsection{\Gls{Rince} pulls the inner council into the present using the magical paint}
\Gls{Rince} guesses that the cave system just appeared beneath the city because of some abrupt 
change in the timeline, and probably wasn't present when the brewery was built. He decides to paint 
an impression of the Unseen University's inner council on the enchanted rock at the center of the 
cave, and drags them into the present using its magic. The lot of them hastily flee the cave as it 
closes in on itself, having been erased from the past.

\subsubsection{\Gls{Rince} talks to the \Gls{Libra} about his yo-yo}
\Gls{Ridcu} tries to impress \Gls{BillR} with his knowledge of rain-making spells, as they sit 
around in the central chamber of Bugarup University, discussing possible means of getting off the 
continent. At the top of the University's tower, \Gls{Rince} plays with the \Gls{Libra}'s yo-yo,
and notices it spin on its own at the slightest bit of effort. He sniffs the smell of rain when he 
spins it, and decides to heave it around in big circles.

\subsubsection{\Gls{Rince} destroys the magical storm-front preventing rainclouds in XXXX}
The magical air currents created by the yo-yo nullify the storm-front circling the continent, and 
enable the rain-bearing clouds to finally float over the landmass. Meanwhile, \Gls{Clancy} and 
\Gls{Remorse} tend to the wild horses, slowly dying of thirst, and are shocked to see rainclouds 
floating over them, starting to drizzle rain.

\subsubsection{\Gls{Rince} and the \Gls{Libra} escape the University's tower burning down}
At Bugarup University, \Gls{Rince} and the \Gls{Libra} almost get burnt up when a massive lightning 
discharge hits the metal tower, but manage to get away from the rubble at the last moment. The
sudden rain brings in permanent ecological change to XXXX, as the city of Bugarup hails the wizards 
as their saviors.

\subsubsection{\Gls{Rince} departs to Ankh-Morpork along with the wizards}
\Gls{Rince} says goodbye to all of his friends from the last few months, and climbs aboard the 
ship waiting to take them home. Meanwhile, a tribal elder throws his ancestral boomerang into the 
sky, prompting the gathered rainclouds to disperse all over the continent. His grandson is happy to 
have witnessed the Wet, finally realizing why a word for the smell of rain had been passed down 
through the generations.


\section{The Last Hero}


\subsection{}
\subsubsection{}
