\section{A Hat Full of Sky}


\subsection{}
\subsubsection{A disembodied spirit senses \Gls{Tiff}'s mind}
A disembodied spirit searches for some living thing to possess, preferably one that has more
brain power than a sheep. Just as it senses \Gls{Tiff}'s powerful mind, she tries out a spirit-walk
that lasts a few seconds. She gets ready to be picked up by \Gls{Tick}, for the start of her
apprenticeship with a witch, and decides to keep her newly gained ability to herself.

\subsubsection{\Gls{Tiff} sets off with \Gls{Tick} for her witching apprenticeship}
\Gls{Tiff} goes to \Gls{GAch}'s ruined hut to pay her respects, and promises to come back to the
village after her training. \Gls{Tick} helps her lie to her mother about the exact nature of the
apprenticeship when she talks to \Gls{Tiff}'s parents about her cheese-making skills. \Gls{Tiff}
then sets off with \Gls{Tick} after saying her goodbyes to her parents, and recalls the new
leader \Gls{Jeannie} of the Feegle clan that she was temporarily in charge of.

\subsubsection{\Gls{Tiff} thinks about the witch named Miss \Gls{Level} who is going to host her}
\Gls{Tiff} receives a present from \Gls{Roland} when she waits at the edge of town for the goods
wagon along with \Gls{Tick}. \Gls{Tick} asks her if she is going to open the package, and is
surprised when \Gls{Tiff} seems busier noticing some ancient carvings on the chalk cliffs outside
their village. \Gls{Tiff} is surprised by her complete lack of homesickness, and looks forward
to staying with Miss \Gls{Level}.

\subsubsection{\Gls{Jeannie} brings literacy to the clan, starting with her husband \Gls{RobA}}
\Gls{Yan} trails the wagon with \Gls{Hamish}, believing that they cannot warn \Gls{Tiff} about the
spirit chasing her while in the presence of \Gls{Tick}. They decide to head back to their colony to
warn \Gls{Jeannie}, where she is busy trying to get her husband \Gls{RobA} to write his own name
on a piece of paper. He overcomes his morbid fear of the written word with great effort, and is
proud of his work in spite of the errors pointed out by the \Gls{Toad}.

\subsubsection{\Gls{Jeannie} stops \Gls{RobA} and the others in her clan from helping \Gls{Tiff}}
\Gls{Hamish} blurts out the news to \Gls{RobA} that a \Gls{Hiver} is chasing after \Gls{Tiff}, and
that he had sensed it by the distinct sound of swarming flies. \Gls{Jeannie} is annoyed by the
threat posed to her authority by \Gls{Tiff}, and refuses to let anyone in the clan go to her help,
even to warn her about the danger posed by the \Gls{Hiver}.

\subsubsection{\Gls{Tiff} watches \Gls{Tick} perform a ritual out of fear that they are being
    watched}
\Gls{Tiff} gets some food at a small town called Twoshirts, which happens to be much larger than the
sheep-rearing village she grew up in. She purchases some souvenirs and postcards to send home,
while noticing how troubled \Gls{Tick} looks. She sees the witch take out some scraps of cloth and
string to perform a ritual, intending to find out what unseen entity is stalking them.

\subsubsection{\Gls{Tiff} narrowly escapes her mind being invaded by the \Gls{Hiver}}
An immense pressure on \Gls{Tiff}'s mind is suddenly stopped by the arrival of the stagecoach that
is supposed to take them on the rest of their journey. \Gls{Tick} remains nervous while putting
away her tools, in time for the passengers to disembark for their lunch break, and asks \Gls{Tiff}
to remain vigilant as they take a detour to the nearby woods.

\subsubsection{\Gls{Tiff} learns about magic detection from \Gls{Tick}}
The animals near the rest stop in Twoshirts are later found scared out of their wits, and the
coach driver notices the faint sound of swarming flies when he comes back to his carriage after his
meal. \Gls{Tick} tells \Gls{Tiff} that her equipment was designed to detect outbursts of magic, and
that she must have done something wrong to make it fall to pieces at the inn.

\subsubsection{\Gls{Tiff} is attacked by the \Gls{Hiver} yet again}
\Gls{Tiff} spirit-walks in order to eavesdrop on \Gls{Tick}, as she talks to \Gls{Level} when she
lands in the forest to take the little girl along to her cottage. All of a sudden, the two senior
witches are alarmed by sensing some magical presence, and ask \Gls{Tiff} to group up with them.
She ends her spirit-walk and runs up to them, just as the headache comes back again with force. The
two witches make another magic detector, forcing the \Gls{Hiver} to withdraw yet again.

\subsubsection{\Gls{Level} takes \Gls{Tiff} back to her cottage by broomstick}
\Gls{Tick} asks \Gls{Tiff} not to be so inquisitive about \Gls{Level}'s supposed invisible twin,
as the two of them take flight on her stealth broomstick. \Gls{Tiff} is terrified of the height,
as \Gls{Level} does a circuit of the area in order to give the young girl a view of her village.
\Gls{Level} flies close to the ground when \Gls{Tiff} tells her that she forgot the insulated pants,
and shows off the full power of her broomstick on the way to her cottage.

\subsubsection{\Gls{Tiff} is alarmed by the helpful spirit living in \Gls{Level}'s house}
\Gls{Tiff} notices the freshly baked bread and pot of stew in \Gls{Level}'s kitchen as she receives
a tour of the cottage. She is then shown to her bedroom, which is very fancy by the standards of her
farmstead back home. After finishing up her meal, she is shocked to see a disembodied force take her
bowl and tray away from her room, even being so kind as to bolt the bedroom door after.

\subsubsection{\Gls{Tiff} tries to make sense of \Gls{Level}'s haunted house}
\Gls{Tiff} wakes up the next day to find all of her possessions carefully packed into her trunk,
and wonders if the spirit is obsessed with restoring order wherever it can. She unwraps
\Gls{Roland}'s gift, and finds a silver necklace made in the shape of the horse carved into the
village's chalk cliffs. When she spirit-walks for a bit to examine herself in the absence of a
mirror, the \Gls{Hiver} senses her, and starts to home in on her location.

\subsubsection{\Gls{Tiff} learns about the secret of \Gls{Level}'s two bodies}
\Gls{Tiff} wakes up the next day to see circus posters lining the walls of \Gls{Level}'s home,
complete with a telepathic twin act listed at the bottom. Once in the kitchen, she sees two
identical bodies, both of whom introduce themselves as \Gls{Level}. \Gls{Level} says that she was
initially mistaken by her parents for a pair of twins, and shunned as a demon shortly after.

\subsubsection{\Gls{Level} explains her daily chores to \Gls{Tiff}}
\Gls{Level} shows \Gls{Tiff} around her farm, complete with a flock of goats and a set of beehives.
\Gls{Tiff} learns about the superstitions surrounding beekeeping, and wonders if it might be
possible to listen to the bees as they talked to each other. \Gls{Level} also mentions \Gls{Oswald},
the inverse poltergeist who had helped \Gls{Tiff} with her dishes at night.

\subsubsection{\Gls{Level} shows off her special herbs and roots to \Gls{Tiff}}
\Gls{Level} shows \Gls{Tiff} her garden of magical herbs, and reveals that many of them have
evolved usage instructions written on their roots in small lettering, as a means of indicating their
use to humans. At the Unseen University Library, an exhibit about the \Gls{Hiver} states its likely
origins, and the failed attempts to kill it through the ages. It shows a senior professor who
unsealed the \Gls{Hiver}, after ignoring the warnings on the bottle, and got his brain hijacked as
a result.

\subsubsection{\Gls{Jeannie} allows \Gls{RobA} to travel to the mountains to defend \Gls{Tiff}}
\Gls{Jeannie} senses the despondency in \Gls{RobA}'s mind, as he sits on top of the colony mound,
thinking about the threat to \Gls{Tiff}'s life from the \Gls{Hiver} pursuing her. She sets aside
her concerns for \Gls{RobA}, and asks him to take some Feegles along to the mountains, to ensure
\Gls{Tiff} returns safely to the village after her training.

\subsection{}
\subsubsection{\Gls{RobA} discusses various means of traveling to \Gls{Tiff}'s location}
\Gls{RobA} enlists some of his closest friends for the rescue mission, and asks the other Feegles
to brawl, so that he can select the last few still standing. \Gls{Bigchin} asks him how they are
going to cover the immense distance to \Gls{Tiff}, and rules out riding with \Gls{Hamish}. He
recalls his time as a bagpiper in \Gls{Jeannie}'s old home, and sings a song about some Feegles
using a scarecrow to smuggle themselves out of a predicament undetected.

\subsubsection{\Gls{Tiff} goes round with \Gls{Level} on her medical duties}
\Gls{Tiff} accompanies \Gls{Level} on her rounds through the village, helping people with their
medical needs. She notices how the villagers try to pay her in supplies as soon as they have any
goods available to spare. She also notices how \Gls{Level} redistributes the supplies to the
poor and destitute villagers, acting as a sort of indirect charity.

\subsubsection{\Gls{Level} shows \Gls{Tiff} the house of a demented old man on her rounds}
\Gls{Level} is convinced that \Gls{GAch} was a witch, regardless of how she was referred to by the
villagers. \Gls{Tiff} dreads visiting \Gls{Weavall}, an old man in his nineties who is close to
death, and obsessed with spending his fortune on a grand funeral. \Gls{Tiff} is appalled to learn
that \Gls{Weavall} has lost both of his children already, and has gone demented with age,
believing that they are coming to take care of him. \Gls{Level} tells her that this is the best she
can do for old people with no families to look after them, and firmly denies taking orders from
\Gls{GWea}.

\subsubsection{\Gls{RobA} and his squad of Feegles commandeer the goods wagon to Twoshirts}
\Gls{RobA} commandeers the rest of his squad into the clothing of an old bearded man, and hires
the local wagon for travel up to the town of Twoshirts. The Feegles dig up some of the gold coins
in the grave next to their colony to entice the driver into doing their bidding. Meanwhile,
\Gls{Level} demonstrates the art of making a magic detector again as \Gls{Tiff} watches on
flummoxed. \Gls{Level} insists that there are no explicit instruction to be found, and that she will
have to learn to rely on her instincts to make a detector of her own.

\subsubsection{\Gls{Level} introduces \Gls{Petulia} to \Gls{Tiff}}
\Gls{Level} greets \Gls{Petulia}, a fellow trainee witch in the area, when she drops by with an
invitation to the next witches' meetup. \Gls{Tiff} realizes she could do with some friends her age,
and agrees to go along, in spite of having none of the fancy ornaments or dress that \Gls{Petulia}
expects her to wear. Meanwhile, the Feegles thrust a bag of gold coins into the hands of the
carriage driver at Twoshirts, making him abandon his regular passengers and speed along with the
one customer.

\subsubsection{\Gls{Tiff} meets \Gls{Anna} and the other trainee witches at one of their rituals}
\Gls{Petulia} explains to \Gls{Tiff} that the regular meetings are the idea of \Gls{Anna}, the
oldest apprentice witch in the neighbourhood, as they walk through the dense forest. Once they reach
a ruined hut, they find a clearing with a small bonfire, and hear \Gls{Anna} scolding one of her
students for burning the tip of her hat by accident. \Gls{Anna} introduces herself as a trainee
working with \Gls{Earwig}, and goes on to point out the other students gathered at the bonfire.

\subsubsection{\Gls{Anna} rambles about \Gls{Earwig}'s movement to modernize witchcraft}
\Gls{Anna} laughs off the idea that \Gls{Tiff} banished the \Gls{QueenF} from her home village when
she was just nine years old, and starts an elaborate ritual involving several other girls following
her instructions. \Gls{Anna} insists on adopting \Gls{Earwig}'s modern approach to witchcraft, as
outlined in the big tome she reads from. She insists on embracing a hierarchy and modern dress code,
just like the wizards.

\subsubsection{\Gls{Anna} and the other girls laugh at \Gls{Tiff}'s imaginary hat}
\Gls{Anna} taunts \Gls{Tiff} on her lack of talent for the coming Witch Trials, where witches from
lands far away would gather for a fair, along with a talent show that \Gls{GWea} would invariably
win every year. \Gls{Tiff} makes the mistake of telling the girls about the virtual witch's hat that
\Gls{GWea} had gifted her, and is laughed all the way out of the meeting. She returns to
\Gls{Level}'s cottage, and sobs out of homesickness.

\subsubsection{\Gls{Tiff} performs a spirit-walk and gets her body hijacked by the \Gls{Hiver}}
\Gls{Tiff} decides to perform a spirit-walk to check if she can see the invisible hat for herself,
as a thunderstorm picks up outside. She lights a candle, and is pleased to see the blurry outline
of the hat on her own head, but is horrified when her body is taken over by something other force,
that stops her from ending the spirit-walk.

\subsubsection{\Gls{Tiff} wakes up with the \Gls{Hiver} infecting her brain}
\Gls{Jeannie} performs a ritual in her colony's main hall to link up with the racial memory of the
Feegles, and realizes that \Gls{Tiff}'s body has been taken over. \Gls{Tiff} wakes up in the
morning, failing to notice how the \Gls{Hiver} is affecting her subconsciously. She spots
\Gls{Level} cleaning up the mess in the garden, and mumbling something about \Gls{Oswald} having
vanished in the thunderstorm.

\subsubsection{\Gls{Tiff} struggles to realize that her mind has been hijacked}
\Gls{Tiff} goes to the goat shed, and finds the animals cowering in fear. She milks them without
facing any of the usual belligerence, and finds that someone has scribbled the words `Help Me' on
the slate used to tally the goat's milk. She fails to notice the abrupt change in her ambitiousness,
and insults \Gls{Petulia} when the fat young girl comes to check in on her after the fiasco at the
bonfire.

\subsubsection{\Gls{Tiff} accompanies \Gls{Level} to the village, and hallucinates the \Gls{Hiver}'s
    memories}
\Gls{Tiff} hears a second voice in her mind, and almost mentions it to \Gls{Level} when asked why
she was so rude to \Gls{Petulia}. \Gls{Tiff} feels a subconscious revulsion to cheese-making,
believing she is meant for greater things, and tags along as \Gls{Level} goes on her daily medical
rounds. \Gls{Tiff} suddenly starts to hallucinate the \Gls{Hiver}'s past memories of inhabiting
wild animals, causing \Gls{Level} to take her back to the cottage.

\subsubsection{\Gls{Level} watches \Gls{Tiff} ramble about the strict norms against using
    everyday magic}
\Gls{Level} is flustered by her magic detectors going up in flames, and realizes that \Gls{Tiff} is
suffering from an outburst of magical talent. \Gls{Tiff} shows off her ability to perform magic,
and asks why the witches must spend so much of their lives trying to do their tasks the mundane way.
She overcomes her fear of flying, and gets on the training broomstick used by \Gls{Level}, just
as the Feegles reach the garden.

\subsubsection{\Gls{RobA} and his squad talk to \Gls{Level} about \Gls{Tiff}'s childhood}
\Gls{RobA} laments to his fellow Feegles that they are just too late, and points out that part of
\Gls{Tiff}'s mind is still resisting the \Gls{Hiver}. \Gls{Level} manages to entice the Feegles to
come out of hiding using one of her old bottles of whiskey, and learns from them about the little
girl's feats of magical prowess in the village.

\subsubsection{\Gls{Wullie} talks about watching \Gls{Tiff} spirit-walk, giving \Gls{Level} the
    final piece of the puzzle}
\Gls{Bigchin} talks about the myths surrounding the \Gls{Hiver}, and lets slip the fact that it
can never be killed. \Gls{Level} wonders what latent power it must have detected in \Gls{Tiff}'s
mind, given how she struggled to perform even the simplest witchcraft. \Gls{Wullie} talks about the
times when \Gls{Tiff} would sit very still with her eyes closed, and of how they could hear her
voice coming from somewhere else. \Gls{Level} realizes that \Gls{Tiff} has the rare gift of
spirit-walking, and works out how the \Gls{Hiver} must have found its way into her mind.

\subsubsection{\Gls{Tiff} bullies \Gls{Anna} at \Gls{Earwig}'s mansion}
\Gls{Tiff} lands on \Gls{Earwig}'s well manicured lawn, and asks to come in to see \Gls{Anna}. She
takes note of how formally \Gls{Earwig} dresses in her own home, and of how deliberate she is when
it comes to advertising her status as the town's witch. The \Gls{Hiver} shows off its power to
\Gls{Anna}, and asks for help in acquiring modern witch's clothing in exchange for being friends
with the most powerful trainee witch in the land.

\subsubsection{\Gls{Tiff} tries to cut a favourable deal with \Gls{Zakzak} for his merchandise}
\Gls{Tiff} is taken to \Gls{Zakzak}'s shop for witches, and observes the large number of used
magic detectors hanging from the ceiling. She plays with a valuable crystal ball, and drops it on
the floor, only for \Gls{Zakzak} to be surprised when she holds it in her hands again, without a
single scratch on its surface. She plays around with one of the fancy wands on display, and asks
\Gls{Zakzak} for a deep discount in exchange for advertising his products at the Witch Trials.

\subsubsection{\Gls{Tiff} turns \Gls{Brian} the wizard into a frog}
\Gls{Zakzak} asks his assistant \Gls{Brian}, a wizard from Unseen University, to deal with the
unruly customers. \Gls{Tiff} turns him into a frog when he starts to fumble with his words, as
\Gls{Zakzak} looks on horrified. The ripple effects of this act of high magic go out far into the
world, hitting \Gls{GWea} when she is out spirit-walking amongst a hive of bees. \Gls{GWea} worries
that \Gls{Tiff} has learned to spirit-walk, and has gotten into trouble for using it without any
safeguards.

\subsection{}
\subsubsection{\Gls{Tiff} threatens \Gls{Zakzak} with violence, unless he becomes her ally}
\Gls{Zakzak} pleads with \Gls{Tiff} to turn \Gls{Brian} back to human form, and is horrified to
see the rest of the boy's body mass floating in the air like a blood-coloured balloon. \Gls{Anna}
almost faints out of fear, and is horrified when \Gls{Tiff} calmly asks \Gls{Zakzak} to offer her
a deep discount, while reversing the spell on \Gls{Brian}. She reminds him that his wands might be
simple curios, but the power within her is deadly serious.

\subsubsection{\Gls{RobA} and the Feegles try to explain their plan to \Gls{Level}}
\Gls{RobA} is tongue-tied when \Gls{Level} asks him how he plans to get rid of the \Gls{Hiver}, and
\Gls{Bigchin} reminds her that the Feegles can invade her dreams using their fairy powers. She
is appalled by the idea of grown men peeking into \Gls{Tiff}'s mind, and is further horrified when
\Gls{Wullie} lets slip the fact that they read her sealed diary regularly.

\subsubsection{\Gls{Level} greets \Gls{Tiff} when she comes back from the boutique}
\Gls{Level} gets the Feegles to take a bath, just as \Gls{Tiff} returns from her shopping trip,
wearing fancy robes and jewelry. \Gls{Level} pretends not to notice the change in her behavior, and
sends one of her bodies to \Gls{Weavall}'s home in the village, to check if \Gls{Tiff} has stolen
his box of coins to pay for the merchandise.

\subsubsection{\Gls{Tiff} kills one of the physical bodies of \Gls{Level}}
\Gls{Tiff} manages to banish the \Gls{Hiver} temporarily by chanting the spell that initiates her
spirit-walks. The \Gls{Hiver} is angry at this sudden display of insubordination, and kills one of
\Gls{Level}'s bodies, when she tries to confront \Gls{Tiff}. The other body of \Gls{Level} passes
out from the trauma, and the Feegles decide to move it somewhere the \Gls{Hiver} cannot track it
down.

\subsubsection{\Gls{Level} passes out as the Feegles prepare to infiltrate \Gls{Tiff}'s mind}
\Gls{Level} is propped up next to \Gls{Tiff} in her room, and manages to mumble some first aid
instructions for the Feegles to perform before passing out. \Gls{Wullie} asks how they are going to
invade her mind, and \Gls{RobA} points out the necklace gifted by \Gls{Roland}, and proposes using
\Gls{Tiff}'s strong feelings for him as a means of getting in. Once inside, they notice her mind
is a model of the hills surrounding her village, but missing any evidence of life.

\subsubsection{\Gls{RobA} and his squad try to make sense of \Gls{Tiff}'s mindscape}
\Gls{RobA} notices the dark starless sky, with just the sun at its zenith, as the rest of them
spread out in search of \Gls{Tiff}'s original mind trying desperately to fight back against the
\Gls{Hiver}'s control. \Gls{Bigchin} leads the Feegles to the hill with \Gls{GAch}'s cottage, and
is convinced that the sun in the sky is a representation of \Gls{Tiff}'s fight against the
\Gls{Hiver}.

\subsubsection{\Gls{RobA} thinks of a method to defeat the \Gls{Hiver} within \Gls{Tiff}'s mind}
\Gls{Wullie} believes that the place they are in is the last bastion of \Gls{Tiff}'s mind as it
resists the \Gls{Hiver}'s control, leading \Gls{RobA} to realize that the \Gls{Hiver} will remain
content with keeping the host mind in a perpetual state of house arrest. He decides to drag the
\Gls{Hiver} to the safe place, where \Gls{Tiff} might be able to defeat it.

\subsubsection{\Gls{RobA} asks \Gls{Wullie} to fetch the items that represent \Gls{GAch}'s smell}
\Gls{RobA} watches some words in chalk appear on the walls of \Gls{GAch}'s hut, and figures out that
the list of items will remind the \Gls{Hiver} of the safe haven, since they represent the scent of
\Gls{GAch}. \Gls{RobA} sends \Gls{Wullie} to fetch the items and make sure the body of \Gls{Tiff}
smells those things, in the hopes that the \Gls{Hiver} will be drawn to the safe haven in her mind.

\subsubsection{\Gls{Wullie} leads a group of Feegles back to the shepherding village}
\Gls{Wullie} takes some Feegles along, and gets \Gls{Hamish} to pilot \Gls{Level}'s broomstick, as
the rest of them cling to its rear end. Meanwhile, \Gls{RobA} notices the \Gls{Hiver} trying to
sprout some trees within the grassy meadow to try and block out the sunlight. \Gls{Bigchin}
welcomes \Gls{Wullie} and his squad as they return from \Gls{Tiff}'s village a short while later
with the objects, and asks them not to drink any of the turpentine as they pour it out next to
\Gls{Tiff}'s nose.

\subsubsection{\Gls{RobA} and the Feegles keep the \Gls{Hiver} distracted as \Gls{Tiff}'s mental
    image wakes up}
\Gls{RobA} greets the \Gls{Hiver} when it materializes inside \Gls{GAch}'s hut within the mind of
\Gls{Tiff}. The Feegles attack it, and force it to desperately shapeshift in order to try and
defend itself. After a while, the land wakes up, having taken the form of \Gls{Tiff}, and grabs
the hiver in its fist. \Gls{RobA} believes that \Gls{Tiff}'s mind will now be able to eject the
\Gls{Hiver} for good, and gives the order to retreat.

\subsubsection{\Gls{GWea} helps \Gls{Tiff} recover full control of her mind after the \Gls{Hiver}
    is banished}
\Gls{Tiff} feels someone trying to shake some sense into her after she wakes up groggy, with the
\Gls{Hiver}'s past memories still jostling for control in her mind. The mysterious voice tries to
get her to recall her real name in the Feegle tongue, and to assert its dominance over the other
identities now fighting for control of her body. \Gls{Tiff} recognizes the voice as \Gls{GWea}, and
gradually manages to shut out the other voices in her head, knowing that they will eventually fade
away.

\subsubsection{\Gls{GWea} is impressed by \Gls{Level} using her phantom body to make tea}
\Gls{GWea} and \Gls{Tiff} notice \Gls{Level} making tea with two extra invisible arms, as if her
brain has not yet come to terms with the loss of her second body. When \Gls{Level} lets go of the
sugar bowl after seeing it suspended in the air unsupported, \Gls{GWea} makes her close her eyes
and convince her brain that the disembodied hands are real. \Gls{Level} manages to do tasks in the
kitchen using her phantom body, but remains skeptical whether she can maintain the delusion
long-term.

\subsubsection{\Gls{Level} takes a day off, as \Gls{GWea} substitutes for her}
\Gls{Level} lists the medical visits that are scheduled for the day, as \Gls{GWea} asks her to take
the day off. \Gls{Tiff} dreads the return to her old life as \Gls{Level}'s apprentice, and listens
to \Gls{GWea} talk about how the villagers did not respect \Gls{Level} as much as they should.
\Gls{Tiff} struggles to justify her actions while under the \Gls{Hiver}'s possession, and \Gls{GWea}
correctly guesses that part of \Gls{Tiff}'s mind is still with the \Gls{Hiver}.

\subsubsection{\Gls{GWea} warns \Gls{Tiff} about being under-prepared for the \Gls{Hiver}'s return}
\Gls{GWea} appeals to the anger inside \Gls{Tiff}, and tells her that she needs to be prepared for
the \Gls{Hiver} when it regains its strength and tries to possess her mind once again. \Gls{Tiff}
dreads returning to medical duty in the village, but is forced to by \Gls{GWea} in order to rebuild
her sense of identity and routine.

\subsubsection{\Gls{Tiff} watches \Gls{GWea} lie about medicine and pathology}
\Gls{Tiff} is amused to see \Gls{GWea} resorting to superstitious explanations, when the villagers
refuse to listen to reasoning. \Gls{GWea} justifies her actions by saying that they will be thankful
for the material results, even if the underlying logic is full of lies. \Gls{Tiff} senses the
\Gls{Hiver} loitering in the forests outside the village, and wonders what opportunity will tempt
it into attempting a possession.

\subsubsection{\Gls{Tiff} listens to \Gls{Weavall}'s plan to marry the widow next door}
\Gls{Tiff} tells \Gls{Weavall} about stealing his savings under the \Gls{Hiver}'s influence, and is
surprised to find his chest refilled with the gold coins from the Feegle colony. \Gls{Weavall}
realizes the money is more than enough to pay for his funeral, and asks \Gls{Tiff} to help him
arrange a wedding with the widow next door who is caring for him.

\subsubsection{\Gls{Tiff} travels up the mountain trail with \Gls{GWea}, hoping to catch the
    \Gls{Hiver}}
\Gls{Tiff} wipes off her tears as \Gls{GWea} reminds her that she cannot hope to face the
\Gls{Hiver} alone, and tells her to thank the Feegles for their help with the gold coins. \Gls{Tiff}
is convinced that \Gls{GWea} has a plan for the \Gls{Hiver} that involves using her as bait, as she
walks along the mountain trail away from the village. They make camp at an isolated clearing filled
with huge boulders, and wait for the \Gls{Hiver} to catch up.

\subsubsection{\Gls{Tiff} and \Gls{GWea} are joined on the mountain by \Gls{Petulia}}
\Gls{Tiff} munches on the food packed by \Gls{Level}, as \Gls{GWea} settles down to sleep at dusk.
She eventually falls asleep, and wakes up to see an eagle sitting next to \Gls{GWea}, who has the
card on her chest that says she isn't dead. \Gls{Tiff} shakes \Gls{GWea} awake, and offers her some
tea to get the taste of raw rabbit out of her mind. \Gls{Petulia} arrives a short while later, as
\Gls{Tiff} thinks about how the piece of her mind inside the \Gls{Hiver} must be advising it.

\subsubsection{\Gls{Tiff} learns about the Witch Trials coming up soon}
\Gls{Tiff} recalls the coming Witch Trials when \Gls{Petulia} asks \Gls{GWea} if she plans to
attend, and is humbled by the idea that \Gls{Petulia} rushed to help them in spite of knowing that
some treacherous evil spirit was lingering nearby. She is glad to see \Gls{Petulia} talk about
meeting the Feegles in \Gls{Level}'s garden, and is reassured by the news of \Gls{Level} gaining
full use of her phantom body.

\subsection{}
\subsubsection{\Gls{GWea} leads \Gls{Tiff} to the Witch Trials}
\Gls{Tiff} notices \Gls{GWea} start to run out of breath as they trek through the mountains to the
Witch Trials. She tries to figure out why the \Gls{Hiver} is keeping its distance, and struggles
to quiet the memories of a powerful wizard who was one of its past victims. \Gls{GWea} pushes past
the line at the ticket counter, and gives the man two imaginary coins as a show of magic.

\subsubsection{\Gls{Tiff} is left alone at the fairgrounds by \Gls{GWea}}
\Gls{Tiff} notices the merchandise being sold in stalls all around the fair, with \Gls{Zakzak}
having the biggest tent of the lot. She turns around to see \Gls{GWea} missing, and is struck with
a sudden fear of being alone in the massive crowd of witches. The wizard's memory tells her that
the \Gls{Hiver} is notorious for fixating on its target once it starts hunting, even if more
attractive options show themselves later.

\subsubsection{\Gls{Tiff} struggles to outsmart the \Gls{Hiver}}
\Gls{Tiff} spots the \Gls{Hiver}'s aura creeping through the lunch tables, and desperately thinks
about the third wish granted by a genie in stories, and finds \Gls{GWea} preparing to face her if
she loses her mind to the \Gls{Hiver}. \Gls{RobA} parachutes down from \Gls{Hamish}'s bird, in time
to help \Gls{Tiff} craft her magic detector.

\subsubsection{\Gls{Tiff} receives the \Gls{Hiver}'s death wish, and opens a portal to \Gls{Death}'s
    realm}
\Gls{Tiff} works out the logic behind the \Gls{Hiver}'s evil actions, since they are simply the
desires that people keep hidden away inside their minds. The \Gls{Hiver} asks \Gls{Tiff} to help it
die, and is shocked when she is able to open a portal to \Gls{Death}'s pocket dimension. \Gls{RobA}
remains skeptical about the \Gls{Hiver}'s intentions, but \Gls{Tiff} reassures him that a piece of
her own mind is stuck inside it, and can guarantee its sincerity.

\subsubsection{\Gls{Tiff} learns from \Gls{Death} that she is stuck in his realm}
\Gls{Tiff} convinces the \Gls{Hiver} to cross the desert of black sand in \Gls{Death}'s realm in
order to find an afterlife, and is glad to see it go. She shuts down her second sight out of
tiredness, and goes to sleep just as \Gls{Death} appears next to her, closing the portal back to the
Disc. \Gls{Death} tells her that the only exit he knows of is across the black desert, and is only
for the use of dead people.

\subsubsection{\Gls{GWea} gets \Gls{Tiff} and \Gls{RobA} back from \Gls{Death}'s realm}
\Gls{GWea} manages to make an unstable portal into \Gls{Death}'s realm and rescues \Gls{Tiff},
who wakes up a few hours later with \Gls{GWea}'s old hat on her head. The other trainees marvel at
her magical prowess, with \Gls{Anna} still afraid of the show of power at \Gls{Zakzak}'s shop.
\Gls{Tiff} is surprised to learn that \Gls{GWea} is busy socializing with the other senior witches
in their private tent, and tries to make amends for spooking \Gls{Anna} when she was under the
\Gls{Hiver}'s control.

\subsubsection{\Gls{Petulia} finds evidence to support \Gls{Tiff}'s stories about traveling to
    \Gls{Death}'s realm}
\Gls{Petulia} recognizes the sand that pours out of \Gls{Tiff}'s boots when she takes them off, as
\Gls{Anna} tries to brush off the supernatural events being described. \Gls{Petulia} talks about
the black desert of the afterlife that is the secret duty of every witch, when an old person is
having trouble finding the means to die.

\subsubsection{\Gls{Tiff} chooses not to present her feats of magic at the Witch Trials}
\Gls{Tiff} refuses to talk about her antics at the Witch Trials, as the others go on stage to
show off their feats of magic. She recalls \Gls{GAch}'s position as the unofficial judge at the
shepherding contests, and of how young shepherds valued her approval above any material prize. She
sees \Gls{GWea} staring at her, as if daring her to step onto the stage, and refuses to challenge
the senior witch out of respect for her position.

\subsubsection{\Gls{Tiff} visits \Gls{GWea} in her cottage to return her hat}
\Gls{Level}'s phantom body takes \Gls{Tiff} to \Gls{GWea}'s cottage, so that the little girl can
return the hat, and ask if the events in \Gls{Death}'s realm really happened. \Gls{GWea} is
reassured by \Gls{Tiff}'s decision to give her hat back, and points out th need for some occasional
grandstanding, so that the rural peasants will be reminded of the value witches have in society.

\subsubsection{\Gls{Tiff} returns home on break and puts her veterinary skills to good use}
\Gls{Tiff} goes back to her village for the lambing season, and is glad to see the villagers accept
her status as a witch. She hopes to get rid of the stigma surrounding witches in her part of the
Disc, and pays her respects to \Gls{GAch} at her ruined cottage on the hill, surrounded by the
Feegles from \Gls{Jeannie}'s colony.