\section{Carpe Jugulum}


\subsection{}
\subsubsection{\Gls{IgorV} waits for his master's family to return from their hunt}
The six-inch tall species of gnome called Nac-mac-Feegle assemble an army to invade Lancre, as a
mysterious shadowy figure swoops down from the sky to observe their assembled forces. Some distance
away, a black carriage drawn by black horses grinds to a halt at the top of a mountain path, as the
driver waits for a vampire family to return from their nightly hunting trip.

\subsubsection{\Gls{Ogg} and \Gls{Agnes} look at the invitation to some fancy ceremony}
\Gls{Ogg} has her best formal clothes prepared for a fancy invitation that she received a short
while ago. The shadowy figure rests for a moment on a tree outside her cottage, before flying off.
Meanwhile, \Gls{Agnes} also leaves her house after looking at the fancy invitation card, while
thinking of how the two senior witches would remain miffed at \Gls{Magrat} for choosing to retire
from witchcraft.

\subsubsection{\Gls{Casan} witnesses some vampires kill a bandit on the highway to Lancre}
\Gls{GWea} finds a young man running up to her cottage to ask for her help in attending to a
baby's delivery gone wrong. Meanwhile, \Gls{Hodges} is intrigued by his brood of falcons staring
up into the sky through the roofs of their stables. Meanwhile, \Gls{Casan} has taken up the life
of a highwayman, and prepares to waylay a black carriage. A different bandit accosts them first,
and \Gls{Casan} is horrified to see the occupants drag him into the carriage and toss him out after
draining all of his blood.

\subsubsection{The vampire family prepare to set foot into Lancre}
At a vantage point overlooking Lancre valley, the family of vampires surveys the kingdom, with
the father \Gls{Magpyr} and his wife \Gls{Countess} declaring that \Gls{GWea} will soon become their
ally. Their daughter \Gls{Lacci} asks why they cannot simply kill all the powerful entities within
the kingdom and seize control by force.

\subsubsection{\Gls{Agnes} tells \Gls{Ogg} the news about the new priest}
The highwayman's soul is reaped by \Gls{Death}, as some flying monster starts to burn through the
window slats in the falcon stables. Meanwhile, \Gls{Agnes} meets up with \Gls{Ogg} at the palace
courtyard in Lancre town, and asks her why \Gls{GWea} seems so busy after the birth of
\Gls{Magrat}'s child. She tells \Gls{Ogg} that a replacement priest from the Omnian church is to
officiate the naming ceremony, since the scheduled one broke both legs in a donkey accident.

\subsubsection{\Gls{Oats} prepares to put his best foot forward as the representative of Omnianism}
\Gls{Oats} offers a sermon to the townsfolk of Lancre, even though no one shows up to his makeshift
tent. He thinks about \Gls{Bru}'s teachings, which stress on the importance of making a good
impression of Omnianism when traveling to lands that have never been exposed to it. Meanwhile,
\Gls{GWea} goes to the small mountainside village of Slice, where the midwife tells her that the
expecting mother is in dire straits.

\subsubsection{\Gls{GWea} saves a mother's life in Slice, when the delivery becomes too risky}
\Gls{GWea} tells the midwife to keep the father occupied with some tea, and tries to attend to the
mother. \Gls{Death} shows up at the barn, to ask \Gls{GWea} if she knows which of the two lives
will end. \Gls{GWea} tries to save the young mother, and watches \Gls{Death} reap the soul of the
unborn child. She asks the midwife to get the mother ready for wet nurse duties in the Lancre
palace, as a means of distracting her from the trauma of miscarriage.

\subsubsection{\Gls{Ogg} asks \Gls{Agnes} to keep an eye out for \Gls{Oats}}
\Gls{Ogg} frets about the Omnian priest, and asks \Gls{Agnes} to search for him, lest he start
evangelizing to the gullible townsfolk of Lancre. She asks \Gls{Shawn} if he sent an invitation to
\Gls{GWea}, and wonders why she hasn't gotten to the palace yet. \Gls{Agnes} watches \Gls{Hodges}
make it to the party in his ceremonial outfit, and spots \Gls{Oats} in the distance, being given a
wide berth by all the other guests.

\subsubsection{\Gls{Magpyr} and his family enter Lancre through the bridge}
\Gls{Shawn} informs \Gls{Agnes} that she is being summoned by Queen \Gls{Magrat}, leading her to
abandon her surveillance of \Gls{Oats}. Meanwhile, \Gls{IgorV} plays along with the troll guarding
the rimward entrance to Lancre, and asks \Gls{Magpyr} to give him a piece of paper for stamping.
The troll seems happy to stamp the gilded invitation card, and lets them pass.

\subsubsection{\Gls{Agnes} listens to \Gls{Magrat} talk about her time as a junior witch}
\Gls{GWea} flies to the castle after resolving the miscarriage in Slice, and notices a mist rolling
into the valley from the direction of Uberwald. Meanwhile, \Gls{Magrat} tells \Gls{Agnes} that
she misses the respect that she used to get as a witch, and is tired of the rigidity of life as a
Queen. She fondly recalls the brow-beating she had to endure at the hands of \Gls{GWea} and
\Gls{Ogg}, something \Gls{Agnes} finds very relatable.

\subsubsection{\Gls{VerSec} outlines his ambitious foreign policy doctrine to \Gls{Ogg}}
\Gls{Agnes} helps \Gls{Magrat} with her dress, and thinks about how futile \Gls{VerSec}'s
attempts to modernize the country were turning out to be. Meanwhile, \Gls{Ogg} tries to argue to
\Gls{VerSec} that the Omnians are a dangerous religion with their history of public witch trials,
and asks him to banish \Gls{Oats} from Lancre. \Gls{VerSec} reminds her of the increasing
globalization on the Disc, and believes that Omnia might become a valuable ally in the future.

\subsubsection{\Gls{Ogg} is chosen to substitute for \Gls{GWea} as the child's godmother}
\Gls{Ogg} and \Gls{Agnes} watch the royal procession reach the great hall where the guests are
arranged on either side of a red carpet. \Gls{VerSec} grows impatient waiting for \Gls{GWea} to make
her last-minute entrance, and \Gls{Millie} is forced to ask \Gls{Ogg} if she can stand in as
godmother to the child.

\subsubsection{\Gls{GWea} waits at home instead of hurrying to the castle for the naming ceremony}
\Gls{GWea} refuses to go to the castle, recalling that her defiance directly led to her saving the
life of the miscarrying mother in Slice. \Gls{Ogg} threatens \Gls{Oats} with violence unless he
sticks to his ordained role for the night, as \Gls{Agnes} notices how young he looks underneath
the fancy black robes and hat.

\subsubsection{\Gls{Oats} screws up the naming of \Gls{Magrat}'s daughter}
\Gls{Oats} messes up the baby's name, and gives it an unfortunate middle name when he reads out
\Gls{Magrat}'s warning to mind the spelling. \Gls{GWea} lays down in her cottage, and thinks about
how some important decision had been made in the town without consulting her. She recalls all the
crimes that she had to adjudicate, using her witchcraft to look for guilt inside the minds of the
accused parties.

\subsubsection{\Gls{Agnes} meets \Gls{Vlad} and is impressed by his beauty}
\Gls{Vlad} bumps into \Gls{Agnes} as she excuses herself from \Gls{Oats}, who is busy having a
panic attack because of the mix-up with the baby's name. \Gls{Agnes} marvels at \Gls{Vlad}'s
style and foreign demeanour, just as \Gls{Shawn} comes up to her and tells her that she is needed
in the front yard. \Gls{Ogg} points out the vampiric coat of arms on the black carriage at the
palace gates, and wonders if they have been invited by \Gls{VerSec} as part of his new foreign
policy.

\subsubsection{\Gls{Ogg} learns about the vampire family at the palace from \Gls{IgorV}}
\Gls{Ogg} gets \Gls{IgorV} to talk about his old master, and listens to him moan about how the new
ones have no sense of tradition when it comes to architecture or fashion. \Gls{Agnes} is shocked
to know that there are vampires in the palace, as \Gls{Ogg} reminds her that they have been invited
formally by \Gls{VerSec}.

\subsubsection{\Gls{Vlad} erases \Gls{Ogg} and \Gls{Agnes}'s memories after telling them about
    the bandit he killed}
\Gls{Vlad} runs into \Gls{Ogg} and \Gls{Agnes} at the kitchens, and casually lets slip the fact
that he killed a bandit on the way to the town. \Gls{Ogg} immediately starts to look for \Gls{Shawn}
in order to punish them, and the vampire uses his mind-control powers to erase their memories of the
last few minutes. He then invites the two of them to the main hall, where \Gls{VerSec} is
entertaining the higher nobility.

\subsubsection{\Gls{Ogg} is horrified by how easily the vampires brainwash \Gls{VerSec}}
\Gls{Ogg} hurries off to find \Gls{GWea} when she sees \Gls{Magpyr} making small talk with
\Gls{VerSec}, and \Gls{Agnes} notices how accepting she is of the fact that they plan to move into
Lancre castle in order to take over the kingdom. \Gls{VerSec} seems to be regretting his invitation,
when \Gls{Countess} lets slip the fact that they cannot enter places without one, even as the
vampiric charm seems to wash away his worry.

\subsubsection{\Gls{Vlad} fails to bring \Gls{Perdita} under his thrall}
\Gls{Vlad} is perplexed by his vampiric charm failing to work on \Gls{Agnes}, as her inner self
\Gls{Perdita} is magically protected from the mind-control. \Gls{Agnes} excuses herself and
decides to seek out \Gls{Ogg}, so that they can return to her cottage. \Gls{Ogg} seems on edge about
some unknown danger lurking in the town, and \Gls{Agnes}'s own hand scrawls the word `Vampire'
into her wall, acting completely outside her conscious control.

\subsubsection{\Gls{Perdita} emerges from \Gls{Agnes}'s mind for the first time}
\Gls{Perdita} hurriedly drinks some alcohol offered by \Gls{Ogg}, and takes full control over
\Gls{Agnes}. Meanwhile, \Gls{Hodges} finds a small flame burning in the stables that is not hot to
the touch, and does not frighten the birds. He believes that some strange bird migrating over the
kingdom has dropped into his falcon stables, and checks in the ancient falconer's logbook for
matching entries.

\subsubsection{\Gls{Perdita} fills in \Gls{Ogg} and \Gls{Agnes} on the happenings at the palace}
\Gls{Agnes} takes back control of her body a while later, and reassures \Gls{Ogg} that \Gls{Perdita}
is simply that part of her mind which is responsible for the forbidden thoughts. \Gls{Ogg} remains
cautious, but is intrigued when \Gls{Perdita} narrates the conversations they had with \Gls{IgorV}
and \Gls{Vlad} at the palace. \Gls{Ogg} is amused to learn that she cannot recall any of the actual
words spoken by the vampires, and \Gls{Perdita} warns her that mustering men to throw them out will
not work.

\subsubsection{\Gls{Hodges} works out which mysterious bird broke into his stables}
\Gls{Perdita} compares \Gls{GWea} to the vampires, when \Gls{Ogg} believes that they will need her
help in defeating the mind-control. \Gls{Ogg} slaps her reflexively, and asks her to come along to
the palace to try and alert the townsfolk. Meanwhile, \Gls{Hodges} realizes that a phoenix has laid
its egg in the falcon stables, and given up its life in order to ensure the hatching of the chick.

\subsubsection{\Gls{Vlad} speaks highly of his father's reformist ideas for Lancre}
\Gls{Ogg} is smitten by the vampires when she takes \Gls{Agnes} and \Gls{Jason} with her to the
private chamber where \Gls{VerSec} is entertaining them. \Gls{Perdita} manages to resist
\Gls{Vlad}'s charm, and he picks up on the fact that there is some part of \Gls{Agnes}'s mind that
is immune to his control. He reads her thoughts, and starts gloating about the radical changes that
will be coming to Lancre once the vampires sink their teeth into the kingdom.

\subsubsection{\Gls{Perdita} fights off \Gls{Vlad}'s attempt to drink her blood}
\Gls{VerSec} sweats as he tries unsuccessfully to resist the vampire charm, as \Gls{Lacci} plays the
grand piano on her mother's insistence. \Gls{Perdita} is able to notice the fact that she is playing
terribly, even as the others politely applaud her performance. \Gls{Perdita} manages to take
control of \Gls{Agnes} and kick him aside when he tries to grab her. The \Gls{Countess} starts to
list some popular weapons supposedly useful against vampires, when she desperately tries to think
of some means to stop them.

\subsubsection{\Gls{Magpyr} asks \Gls{Agnes} to talk to \Gls{GWea} about the vampires}
\Gls{Magpyr} taunts \Gls{Agnes} when she points out how powerful \Gls{GWea} will be, and lets her
go fetch the old witch from her cottage. He is confident that the witches of Lancre can either be
subdued or turned into allies, and asks \Gls{Agnes} to return quickly.

\subsection{}
\subsubsection{\Gls{Ogg} and \Gls{Agnes} find \Gls{GWea}'s cottage empty}
\Gls{Hodges} sets out into the forest with a wide variety of lures and foods to try and bait the
newborn phoenix. \Gls{Ogg} and \Gls{Agnes} reach \Gls{GWea}'s cottage, and find that she has left
a few hours before sunrise, with the cutlery all polished up. \Gls{Ogg} finds \Gls{GWea}'s box of
personal items missing, and is worried about what threat she must have sensed.

\subsubsection{\Gls{Ogg} realizes why \Gls{GWea} refused to attend the naming ceremony}
\Gls{Perdita} points out to \Gls{Agnes} that all the cutlery has been arranged in sets of three on
the dining table, as \Gls{Ogg} confirms that the clock has come to a stop at three minutes past
three. \Gls{Agnes} watches three magpies land on a nearby tree, and wonders what cryptic message
\Gls{GWea} is trying to convey. \Gls{Ogg} works out something related to \Gls{GWea} not lighting
her fireplace and not being at the birth of \Gls{Magrat}'s daughter.

\subsubsection{\Gls{Ogg} presents a theory why \Gls{GWea} abandoned her cottage}
\Gls{GWea} makes it to the foothills on the borders of Lancre, and looks back for a second at the
mist enveloping the valley. She continues her trek further uphill, and reaches the snow line.
Meanwhile, \Gls{Ogg} speculates that \Gls{GWea} has left Lancre because she feels it already has a
set of three witches, with \Gls{Magrat} being promoted to the role of mother, and \Gls{Agnes} being
the new maiden.

\subsubsection{\Gls{Magpyr} sets out his grand plan to adopt human culture as the rulers of Lancre}
\Gls{Agnes} speculates that \Gls{GWea} somehow knows that the baby has been named after her, and
believes it makes her presence in Lancre redundant. A magpie steals one of the shiny spoons from
the table, and gets away before \Gls{Ogg} can throw her hat at it. Meanwhile, \Gls{Magpyr} taunts
\Gls{Lacci} about her hippie vampire trends, such as bright clothes and mundane human names. He
demonstrates how \Gls{Vlad} is gradually overcoming his fear of sacred symbols, and reminds her that
they will slowly acclimatize to human traditions.

\subsubsection{The vampires plan to feed on \Gls{VerSec}, and avoid the baby for the near future}
\Gls{Lacci} suggests getting rid of \Gls{IgorV}, given how he hands on to traditional vampire
aesthetics and culture. \Gls{Magpyr} agrees with her plan to have him tortured to death in the
palace cellars, and sends for \Gls{VerSec} so that they can draw some royal blood for breakfast.
Meanwhile, \Gls{Agnes} uses her broomstick to fly high into the branches of a tree, and finds
\Gls{GWea}'s invitation in a magpie nest.

\subsubsection{\Gls{Oats} talks about his visit to check up on \Gls{GWea}}
\Gls{Oats} finds \Gls{Agnes} and \Gls{Ogg}, while looking for \Gls{GWea} in her cottage. \Gls{Ogg}
remains wary of him, and tells him that he can come back later since \Gls{GWea} is out at the
moment. \Gls{Agnes} decides to walk the priest back to town, seeing how uncomfortable he is with
the rural landscape. On the way back, she notices how boring he is, and wonders if this is a
deliberate affect meant to hide some ulterior motive.

\subsubsection{\Gls{Oats} and \Gls{Agnes} find out \Gls{GWea}'s last known location}
\Gls{Oats} casually lets slip the fact that the vampires did not affect his mind beyond a small
migraine, when they were chatting openly at the party about their blood-drinking habits. \Gls{Agnes}
spots \Gls{Hodges} calling out to the baby phoenix, and learns from him that \Gls{GWea} was last
seen climbing the mountains at the borders of Lancre. She decides to head back to \Gls{Ogg}'s house
to convey the news.

\subsubsection{\Gls{GWea} conducts some experiments in the high mountains outside Lancre}
\Gls{GWea} blindfolds herself, and crosses a small stream using a makeshift bridge made of some
logs. She falls down midway, and believes that something is tampering with Lancre outside of her
knowledge. Meanwhile, \Gls{Ogg} recruits \Gls{Oats} to go along with \Gls{Agnes} to the palace and
rescue \Gls{Magrat} so that they can use her power to scry \Gls{GWea}'s location. \Gls{Ogg} is
intrigued to see \Gls{Oats} mention how fussy vampires tend to be about things being in their place.

\subsubsection{\Gls{Agnes} and \Gls{Oats} use the empty coffins to sneak into the palace}
\Gls{Agnes} and \Gls{Oats} sneak into the castle by climbing into the back of the last carriage in
a long line being driven into the palace grounds. She notices how pacified the drivers look, and
wonders if they have been permanently charmed by the vampires to act as blood bags. A group of
mercenaries dressed in the colors of the vampire family crest lead the procession. \Gls{Oats} finds
some coffins hidden in straw underneath him, and opens them to check if they are empty.

\subsubsection{\Gls{Oats} knocks out \Gls{IgorV} before he can provide any helpful advice}
\Gls{Agnes} senses the coffins being taken to the cellars, and hears \Gls{IgorV} complaining about
his masters. He believes her to be an undercover assassin when he finds her inside the coffin, and
starts helpfully listing all the methods that will not work against the Magpyrs. \Gls{Oats}
knocks \Gls{IgorV} out with a coffin plank, and realizes too late that he is merely a servant.
\Gls{Agnes} marches into the kitchen, and finds the head cook going about her duties with a blissful
look on her face and a bandage on her neck.

\subsubsection{\Gls{Oats} and \Gls{Agnes} help \Gls{Magrat} pack up her belongings}
\Gls{Oats} fills some water from the kitchen, and blesses it to try and defeat the vampires, as
\Gls{Agnes} tries to think of a path to \Gls{Magrat}'s room. Once there, she convinces \Gls{Magrat}
to come help \Gls{Ogg} by talking about the grave danger that \Gls{GWea} has put herself in.
\Gls{Magrat} asks \Gls{Oats} to pick up the baby's toys and diapers, as \Gls{Agnes} makes a sling
to carry it.

\subsubsection{\Gls{Magpyr} thinks about the falcons in the palace interfering with his magpies}
\Gls{Magpyr} reads the minds of his pet magpies, as they hover near the castle's tower, with
their minds full of the sights and sounds of the day. He wonders where \Gls{GWea} has gone off to,
and reminds himself that \Gls{Hodges} will eventually have to be eliminated since the falcons preyed
on his pet magpies.

\subsubsection{\Gls{Magrat} convinces the other witches to reach \Gls{GWea} on foot}
The three witches manage to catch a brief glimpse of \Gls{GWea} in the crystal ball, and
\Gls{Magrat} immediately wishes to track her down in person. \Gls{Ogg} reminds them that the
mountain lands are soaked in magic, and that their broomsticks cannot fly properly. \Gls{Oats}
offers to mind the baby, but \Gls{Ogg} is convinced that it is better if \Gls{Magrat} takes it along
in the makeshift sling.

\subsubsection{\Gls{Hodges} finds the baby phoenix trying to find the right form for itself}
\Gls{Hodges} runs into the phoenix on his way back to the castle, and finds it repeatedly bursting
into flames as it tries to remodel itself like one species after another. Meanwhile, \Gls{Magpyr}
tells his wife that \Gls{GWea} has disappeared after he encouraged the self-doubt in her mind using
his charm. He reminds her that witches will soon go extinct along with all the other esoteric
extra-human species.

\subsubsection{\Gls{Ogg} and the witches reach the deep gorge inside the pocket dimension}
\Gls{Ogg} is relieved to know that the baby is fast aslepp, as she prepares to lead the witches
through the pocket dimension made by the tectonic plates colliding in the mountains. \Gls{Perdita}
wonders if \Gls{GWea} is trying to spy on them through the baby's mind, as they come to a deep
gorge being spanned by a rickety bridge. \Gls{Perdita} points out that it is all an illusion, and
that the bridge is a plan spanning a small stream a foot underneath it.

\subsubsection{\Gls{Agnes} surrenders to \Gls{Perdita} to avoid falling into the deep gorge}
\Gls{Agnes} decides to listen to \Gls{Perdita} and jumps onto the bridge. Halfway through, it rocks
precariously, causing her to tip over the edge, and hang on with her hands. \Gls{Magrat} recommends
\Gls{Perdita} to take control of \Gls{Agnes} and let go of the bridge, so that she can fall down
into the small stream a few feet below. \Gls{Perdita} does a handstand on the edge of the bridge,
noticing how little \Gls{Agnes} uses her own muscles.

\subsubsection{The three witches pass through \Gls{GWea}'s defenses and find her in a cave}
Once they cross the bridge, \Gls{Ogg} points out an ancient rock formation that looks like a
hunchbacked old woman with a witch's nose. \Gls{Ogg} guesses that the place is reacting to
\Gls{GWea}'s thoughts, and uses the baby as a shield from the other obstacles in their way.
Eventually, they reach a sandy cavern, where \Gls{GWea} is lying down holding a signboard asking
them to leave her alone.

\subsubsection{\Gls{Ogg} listens to \Gls{GWea}'s despondent mumbling about the vampires}
\Gls{GWea} remains defiant about helping the kingdom repulse the vampires, and reminds the three
witches that they can deal with the problems on their own. \Gls{Ogg} and \Gls{Magrat} consider this
tone of voice to be odd, and decide to go back to her tent to check up on her. \Gls{GWea} tells
\Gls{Ogg} that she has no hope of defeating the vampires, since they have superior mind-control. She
believes that the best she can do is hide out in the pocket dimension where the magpies cannot find
her.

\subsubsection{\Gls{Ogg} asks \Gls{Agnes} to try and ingratiate herself with \Gls{Vlad}}
\Gls{Magrat} is appalled by \Gls{Ogg}'s idea of sending \Gls{Agnes} into the castle to court
\Gls{Vlad}, and potentially turn him into an asset against the much more powerful \Gls{Magpyr}.
\Gls{Agnes} is horrified at the suggestion of using her womanly wiles against \Gls{Vlad}, who seems
to be equal parts amused and intrigued by her mind.

\subsubsection{\Gls{Ogg} asks \Gls{Magrat} to make a deal with the Feegles}
One of the Nac-mac-Feegles sneaks into \Gls{Ogg}'s cottage, and she catches him in time to stop him
from toppling her bottle of liquor. She offers him a small glass, and listens to his tale of the
vampires driving the pixies out of Uberwald, along with the other races deemed too strange to exist.
She lets the rest of the Feegles have full use of her liquor cabinet, and asks \Gls{Magrat} to give
them ownership of the northern island in Lancre, so that they will join the fight against the
vampires.

\subsubsection{\Gls{Agnes} is forced to go in through the kitchen in order to let the others in}
\Gls{Ogg} calls on \Gls{Jason} to organize a rioting mob at the gates of the palace, and reminds
him to set up some food for the rioters, who are usually made up of the extended Ogg family with
their friends. \Gls{Ogg} finds \Gls{Hodges} outside the main castle, and learns that the vampires
are in the kitchen. \Gls{Agnes} volunteers to go in to unlock the side entrance so that the rest of
them can sneak in.

\subsection{}
\subsubsection{\Gls{Vlad} finds \Gls{Agnes} being harassed by two of the vampire servants}
\Gls{Agnes} is accosted by two vampires, who get knocked out by \Gls{Vlad} when they taunt her.
He tells her that they are distant relatives who have sworn allegiance to \Gls{Magpyr}, and offers
to lead her to the long gallery. He points out some family portraits, including an uncle who
operated an inn out of the family castle, and a distant ancestor who looks much like an overgrown
mutant bird.

\subsubsection{\Gls{Vlad} shows \Gls{Agnes} around the castle, and points out his family portraits}
\Gls{Vlad} tells \Gls{Agnes} that \Gls{Magpyr} is visionary in his ideas of exposure therapy and
tight family bonding. He tells her that old-fashioned vampires would not have bothered to strike
such a gracious pact with the humans they ruled over, and brushes off the holy water she pours on
him. He chides \Gls{IgorV} for trying to enforce the traditional vampire ambience, and tells him
to go away.

\subsubsection{\Gls{Agnes} lets \Gls{Ogg} into the castle as the mob starts their riot}
\Gls{Agnes} excuses herself when \Gls{Magpyr} shows up to take \Gls{Vlad} to the front gates and
show him the mob. She unlocks the side door, and is surprised to see \Gls{Ogg} take a swig of her
brandy so that she can face the vampires without falling to their charm. Meanwhile, \Gls{Oats} looks
at the scattered notes on vampire hunting from his time in theological college, and wonders if there
might have been more useful tomes on the subject in the Citadel's library.

\subsubsection{\Gls{Magpyr} deals with the rioting mob at the castle gates}
\Gls{Magpyr} tells the mob gathered outside that they have done an admirable job gathering in front
of the castle, and gives them an hour to disperse before his soldiers take up positions. He shuts
the gates and starts to tell \Gls{Vlad} how he has short-circuited the mob's goals, just as
\Gls{Ogg} shows up at the steps leading to the palace with the other two witches, drunk and ready
to face him.

\subsubsection{\Gls{Magpyr} expects \Gls{Oats} to try and stop him using his Omnian prayers}
\Gls{Magpyr} summons his weather-manipulating magic to levitate the three witches, and takes them
into the castle, where \Gls{Oats} steps out with his holy book to try and stop the vampires.
\Gls{Magpyr} calmly tosses the book away and shocks \Gls{Oats} by stating that he helped write the
verses that could supposedly weaken vampires. \Gls{GWea} shows up, drenched in the rain, just as
\Gls{Magpyr} swats \Gls{Oats} aside like a fly.

\subsubsection{\Gls{Magpyr} decides to turn \Gls{GWea} into a vampire servant}
\Gls{GWea} tries to intimidate \Gls{Magpyr} using her powers of mind-jumping, but he remains
unimpressed. She then tries to penetrate his mind, and almost succeeds. \Gls{Magpyr} is alarmed by
her power-level, as \Gls{Agnes} notices how weary \Gls{GWea} looks. \Gls{Magpyr} shrugs off the
rest of \Gls{GWea}'s mental assaults, and levitates her to a table, intending to turn her into a
subservient vampire.

\subsubsection{\Gls{Ogg} and \Gls{Magrat} run away from the great hall to protect their minds}
\Gls{Ogg} senses \Gls{GWea} sending her mind away into some other body, and decides to retreat into
the kitchen with \Gls{Magrat} so that the vampires cannot read her mind. \Gls{Vlad} advances towards
\Gls{Agnes} when she uses her enchanted voice to scream at a high pitch, and is knocked down by
\Gls{Perdita}'s elbow.

\subsubsection{\Gls{Magpyr} drinks \Gls{GWea}'s blood and throws out her body afterward}
\Gls{Magpyr} knocks \Gls{GWea} out, and prepares to suck her blood, after pushing \Gls{Oats} into
\Gls{Agnes}'s arms. Once outside the castle doors, \Gls{Agnes} is intrigued by \Gls{Oats}'
immunity to the mind-control, and wonders if \Gls{GWea} might really have sent her mind into the
baby. \Gls{Oats} thinks about going back in, just as \Gls{GWea}'s body is thrown out into the
courtyard with bite marks on her neck. \Gls{Agnes} decides to drag her to the stables nearby, hoping
to find shelter and avoid questions about the wounds.

\subsubsection{\Gls{VerSec} is kidnapped by the Feegles}
The Feegles break into \Gls{VerSec}'s private bedroom, and knock out the two guards set to watch
over him. \Gls{VerSec} fails to come out of his happy vampire-induced haze, as he is carried up
and out of the castle through a window. Meanwhile, \Gls{Agnes} asks \Gls{Hodges} to make space in
his bedroom for \Gls{GWea}, and tells \Gls{Oats} that she might just be able to resist the vampiric
poison in her blood.

\subsubsection{\Gls{Ogg} and \Gls{Magrat} find \Gls{IgorV} in the stables}
\Gls{Ogg} refers to \Gls{Oats}' document on vampire pacification when one of the servant vampires
stops her from leaving through the kitchen door. \Gls{Magrat} asks \Gls{Ogg} to sneak into the
falcon stables so that they can change the baby's diapers, and goes to the weak candlelight for
vision. \Gls{IgorV} stumbles into them as they try to unlock his carriage, and offers to help them
on his way out of Lancre.

\subsubsection{\Gls{GWea} asks \Gls{Oats} to drag her into the armory}
\Gls{GWea} wakes up in \Gls{Hodges}' bedroom all of a sudden, and shrugs off the bindings that
\Gls{Agnes} had tied to her arms and legs as a precaution. \Gls{Oats} helps \Gls{GWea} get up,
noticing how fevered she feels, and catches her mumbling the word `iron'. \Gls{Agnes} realizes the
armory is nearby, and asks \Gls{Oats} to help take \Gls{GWea} next door.

\subsubsection{\Gls{GWea} conveys her plan before the vampirism takes over her body}
\Gls{GWea} asks \Gls{Oats} to ready a sharp axe, as well a hammer and stake to impale her once she
loses control of her body and reanimates as a vampire. She asks \Gls{Agnes} to rejoin the other
two witches in case her gambit fails, and falls unconscious on the large anvil. \Gls{Oats} hastily
polishes a nearby axe on the grindstone, just as \Gls{Hodges} peers in offering a cup of tea.

\subsubsection{\Gls{VerSec} is taken into an underground tunnel network by the Feegles}
The Feegles transport \Gls{VerSec} to a riverbank at the edge of the fields outside Lancre town,
and hide him in some rabbit tunnels. \Gls{Agnes} runs out into the pounding rain and spots the
Magpyr family's carriage leaving through the gates. She wonders if \Gls{Ogg} might be on it
alongside \Gls{IgorV}, just as \Gls{Vlad} grips her firmly in his hands.

\subsubsection{\Gls{Vlad} jumps into the Lancre river with \Gls{Agnes}}
\Gls{Vlad} jumps into the Lancre gorge with \Gls{Agnes} clutched in his arms, as he talks about the
utility of turning people into simple-minded servants, instead of killing them outright. Meanwhile,
\Gls{GWea} faces the dark side of her own mind inside her head, as \Gls{Death} stands by looking
amused. She realizes that \Gls{Magpyr} is using the dark side to distract her, and decides to
dismiss the idea of pursuing greater power at the cost of her morality.

\subsubsection{\Gls{GWea} wakes up from her near-death experience}
\Gls{GWea} wakes up in her body, while hearing the two halves of \Gls{Oats}' mind chanting the
Omnian hymns out of habit. Meanwhile, \Gls{Ogg} decides to go towards the next town in Uberwald,
since the roads leading every other way are flooded in the rain. \Gls{Vlad} toys with \Gls{Agnes}
by using his levitation magic to take her high above the Disc and letting her fall to the ground.
He stops her mid-fall, just as \Gls{Lacci} finds them, and tells them that the two witches are
headed for their old castle in Uberwald.

\subsubsection{The Feegles lift the vampiric charm off of \Gls{VerSec}}
\Gls{VerSec} is propped up against the wall in an underground chamber full of Feegles. The leader
points a crossbow at him, and shoots it next to his ear after performing some ritual at a miniature
bonfire. He realizes that the Feegles have gotten rid of the vampiric influence in his mind, and
starts to feel the mental fog lift. The translating Feegle introduces himself as the spokesman for
their leader \Gls{Aggie}, and asks \Gls{VerSec} to sign a lengthy document as thanks for rescuing
him from the castle.

\subsubsection{\Gls{GWea} asks \Gls{Oats} to get her some tea}
\Gls{GWea} asks \Gls{Oats} to fetch some tea and biscuits for her from \Gls{Hodges}, and reminds
him that the supposed witch-trials held by the Omnians only caught innocent women. Further doubts
crop up in \Gls{Oats}' mind when he recalls \Gls{Magpyr} talking about authoring the Omnian texts,
as \Gls{Hodges} walks in with the phoenix egg-shells he found earlier.

\subsubsection{\Gls{GWea} guesses that the baby phoenix is disguised as a falcon}
\Gls{GWea} spots different patterns among the eggshells, and asks \Gls{Hodges} to tally up the
falcons in his stables. He returns with news that there is one more bird than in his books, and
\Gls{GWea} asks him to check their species, confident that the baby phoenix can shapeshift as a form
of self-defense.

\subsubsection{\Gls{GWea} decides to pursue \Gls{Ogg} through the Uberwald route}
\Gls{GWea} asks \Gls{Hodges} to put a hood over the baby phoenix, and he agrees readily out of a
desire to get it out of his stables. She decides to go back to the palace with the phoenix, only
for \Gls{Oats} to point out that the Magpyr carriage was seen leaving the palace, with the two
witches riding in it. \Gls{GWea} guesses correctly that \Gls{Ogg} must be going to Uberwald, and
asks for \Gls{Oats} to bring his mule so that she can chase after them.

\subsubsection{\Gls{Oats} takes \Gls{GWea} along on his mule}
\Gls{Oats} helps \Gls{GWea} through the muddy yard, taking care to help her maintain her charade of
strength in front of the assembled townsfolk. She decides to let him help her, after making a show
of helping him instead. \Gls{GWea} falls off the mule because of her weakened legs, and \Gls{Oats}
decides to strap her down behind him. The phoenix manages to fly perfectly in the dark night, in
spite of the hood covering its head, and perches on \Gls{GWea}'s arm as they head out.

\subsubsection{The Feegles help \Gls{VerSec} combat the fatigue caused by his blood-loss}
\Gls{Ogg} does her best to reassure \Gls{Magrat} that her husband is safe with the Feegles, and
that the potential threats in Uberwald will be within their power to handle. Meanwhile, \Gls{Aggie}
has a herbal brew brought to \Gls{VerSec} to help him recover his strength. \Gls{VerSec} worries
about the violence he will have to oversee in retaking his castle, and is falsely reassured by the
herbs supposedly in the broth.

\subsubsection{\Gls{Vlad} decides to show off his father's work in the town of Escrow}
On their way to Uberwald, \Gls{Vlad} decides to make a stop at the pacified town of Escrow, while
pointing out how instructive it will be for \Gls{Agnes} to see the future of Lancre. \Gls{Perdita}
starts to point out how attractive \Gls{Vlad} is becoming, while noticing something is off about him
compared to the other vampires.

\subsubsection{\Gls{Oats} sets fire to his Book of Om as \Gls{GWea} grows cold in the rain}
\Gls{Oats} spends the mule-ride arguing theology with \Gls{GWea}, until he notices her loosening
her grip on his shoulder and slide off her seat. He finds her pulse weakening, and desperately looks
for some wood so that he can give her some heat. Unable to find any twigs or lichen that might
catch fire, \Gls{Oats} is forced to burn his Book of Om, to warm up \Gls{GWea}.

\subsubsection{\Gls{IgorV} falls for the enchanted road leading to Magpyr castle}
\Gls{IgorV} tells \Gls{Ogg} that the roads leading into Uberwald have been enchanted to always
point to the Magpyr castle, just as they go over a nasty trench and lose the two back wheels.
\Gls{Magrat} asks him to bundle up the baby's toys, as they hear a werewolf howling in the darkness,
with \Gls{Ogg} eager to get indoors within the safety of the castle's thick walls.

\subsubsection{\Gls{IgorV} lets the witches into the Magpyr castle}
\Gls{IgorV} tells \Gls{Ogg} that he plans to pack up his belongings and leave the Magpyrs as soon
as he gets to their castle. \Gls{Magrat} notices how much he is smitten with \Gls{Ogg} because of
her sharp words, just as he returns from the castle with news that only the servants are in. His
pet dog \Gls{Scraps} greets him at the castle gates, and the witches take not of how the dog seems
put together from spare parts, just like its master.

\subsubsection{\Gls{IgorV} leads the way into the castle's crypts}
\Gls{IgorV} leads the witches to his chamber in the crypt, and shows them the extensive
vampire-killing tools that the old master had collected. \Gls{Ogg} surmises that he preferred for
the locals to put him out of action temporarily, so that he might come back a few years later and
stave off any permanent threat to his position in the kingdom. \Gls{Magrat} takes note of a heavily
bolted door that \Gls{IgorV} claims is unimportant, as \Gls{Ogg} inspects the library of holy
symbols beside the tank of holy water.

\subsection{}
\subsubsection{\Gls{VerSec} and the Feegles set off to the castle to reclaim it}
\Gls{Ogg} sets about gathering tools to fight off the vampires, with \Gls{Magrat} confident that the
vampires will be able to track them down. Meanwhile, the Feegles give \Gls{VerSec} a large dose of
their herbal cocktail, driving him into a battle frenzy. He cuts his way out of an underground
tunnel with an ancient bronze sword pilfered from a village chieftain's burial mound. The Feegles
set off after him, when they are reminded of their pact with \Gls{Ogg}.

\subsubsection{\Gls{IgorV} talks about the grand pipe organ as \Gls{Ogg} watches in fascination}
\Gls{IgorV} shows off his old master's pipe organ in the basement, and points out the reinforced
doors designed to hold off rioting mobs. \Gls{Vlad} points out the fancy architecture in the town
of Escrow as he lands there with \Gls{Agnes}, followed by \Gls{Lacci} and one of her friends.
Meanwhile, \Gls{GWea} wakes up from her stupor, and is glad to see a bonfire warming her up. She
asks \Gls{Oats} to find her a walking stick, so that they can march on to Uberwald without waiting
for the rain to abate.

\subsubsection{\Gls{Agnes} watches a disease grip the vampires as they assemble in Escrow}
\Gls{Agnes} watches in horror as \Gls{Magpyr} gets the villagers lined up for the bimonthly
feeding lottery. He gleefully states that there are a lot of children up for grabs this month, as
the lesser vampires form a cordon around the villagers. \Gls{Lacci} confronts her father about
his dictatorial control over the family, and \Gls{Vlad} pipes up about his reservations regarding
Lancre. All of a sudden, they start clutching their throats and collapsing one by one, with
\Gls{Magpyr} looking to blame \Gls{Agnes} for the contagion.

\subsubsection{\Gls{Agnes} incites the villagers of Escrow to rise up against the Magpyrs}
\Gls{Agnes} manages to hit back at \Gls{Lacci} when she pounces for the kill. Sensing the weakness
in the vampires, the village rises to riot against them, forcing them to try and rise into the air
with their last remaining bit of magic. Meanwhile, \Gls{GWea} asks \Gls{Oats} if he heard her
mumbling in her sleep while at the armory. He says yes, and is surprised when she asks him to forget
the episode.

\subsubsection{\Gls{GWea} talks about religion and its use as a tool of social cohesion}
\Gls{GWea} takes a liking to \Gls{Oats}, while remaining skeptical of his evangelism. She correctly
predicts that any ancient miracle will have become twisted in its retelling over the centuries,
causing sects to keep splitting into sub-sects until nothing remained that resembled the original
teachings. She collapses yet again on the trek downhill to Uberwald, causing \Gls{Oats} to carry
her on his shoulders.

\subsubsection{\Gls{Agnes} wakes up with the vampiric urge trying to rise inside her}
\Gls{Agnes} stops the villagers from executing her, just as she fights off the subconscious urge
to become a vampire and wakes up. The villagers point to the bite marks on her neck, and she brushes
it off by stating that \Gls{Vlad} tried to convert her but missed in the darkness. \Gls{Piotr}, one
of the villagers, tells her that they managed to kill two of the clan, but the others fled. He
speculates that they will have to walk to their castle, and reach it before sunrise.

\subsubsection{\Gls{VerSec} launches the counterattack against the Magpyr mercenaries}
\Gls{Piotr} tells \Gls{Agnes} that the villagers plan to pursue the vampires, taking the shortcut
through the werewolf infested woods which is too dangerous for the vampires themselves. Meanwhile,
\Gls{Jason} and the villagers watch in awe as \Gls{VerSec} rushes the castle with the army of
Feegles behind him. \Gls{Shawn} decides to take the gatekeeping troll with him to try and sneak in
through the privy, as \Gls{Jason} tends to his wounded shoulder.

\subsubsection{\Gls{Shawn} flushes the mercenaries out of the castle}
\Gls{Shawn} has the troll open the door to the privy tower, and shoots a flaming arrow into it to
trigger a massive explosion that smokes out the soldiers hunkered down inside. He uses his
prototype Lancrastian Army Knife to kill one of the mercenaries running out in a daze, as
\Gls{VerSec} gets to work dealing with the rest of them.

\subsubsection{\Gls{Magpyr} and his clan limp away to their castle, unable to fly}
\Gls{Agnes} walks with the villagers of Escrow as they set out to cull the fleeing vampires.
\Gls{Perdita} points out that \Gls{Vlad}'s bite may not have affected her body, but definitely
left a mark on her mind. Meanwhile, \Gls{Magpyr} touches the wounds on his neck from the mayor
of Escrow trying to strangle him, and is shocked by how weak he felt at the time. The family
start to discuss where \Gls{GWea} might have hidden herself, and rule out some possibilites.

\subsubsection{\Gls{Magpyr} and his clan reach the entrance to their castle}
At the drawbridge leading to their castle, the \Gls{Magpyr} clan get hit with some bottles of
holy water thrown by \Gls{IgorV}. One of the lesser vampires burn up, and \Gls{Magpyr} is alarmed
when a single drop hitting his skin leaves a small burn. He believes that the tools against vampires
work only based on their own psychological weaknesses, and asks the others to keep faith in his
positive thinking.

\subsubsection{\Gls{Greebo} kills one of the lesser vampires when his sleep is interrupted}
The \Gls{Countess} asks the rest of the clan to prepare for a full morning's rest within the castle,
as \Gls{Magpyr} is hit by the strange thirst for tea. He wonders if \Gls{GWea} is hiding inside
his own mind, as he summons some lightning bolts to blow away the outer gate. Once inside, the
rest of the vampires head for the palace, while one of them goes to the cellars to sleep. He
fails to notice \Gls{Greebo} curled up inside his coffin, and is murdered for his mistake.

\subsubsection{\Gls{Oats} and \Gls{GWea} reach the gates of the Magpyr castle}
\Gls{Oats} watches the baby phoenix swoop away towards the castle with its body sustaining a weak
flame. He runs after it, carrying \Gls{GWea} on his shoulders, and finally reaches the outskirts
of the Magpyr castle. \Gls{GWea} wakes up, mumbling some of the phrases uttered by \Gls{Magpyr}
when he announced his plan to his family, as \Gls{Oats} gets angry at her apparent lack of
gratitude. \Gls{GWea} has him knock on the ruined gates, so that the vampires can let them in.

\subsubsection{\Gls{Oats} and \Gls{GWea} watch the baby phoenix save \Gls{Ogg} on a tower}
\Gls{Ogg} baits two lesser vampires into following her up some stairs to a tower, where \Gls{IgorV}
kills them using wooden stakes. Some more vampires try and surround them on the battlements, but
are burned by the phoenix when it summons a huge spectral version of itself. \Gls{GWea} points out
to \Gls{Oats} that the baby phoenix on her arm must be the male, and shows him how the two of them
are not being burned by its flame, which supposedly only affects evil.

\subsubsection{\Gls{Magpyr} and his family slowly lose control of their civilized minds}
\Gls{Magpyr} is forced to slap some sense into \Gls{Lacci}, as the family hunkers down in another
tower, while waiting for their underlings to clear out the rest of the castle. The natural sense
of paranoia and distrust among vampires starts to creep back in, with \Gls{Lacci} horrified by
the holy symbols that she sees all around her. She blames \Gls{Magpyr} for giving them the
knowledge about the hundreds of holy symbols, as \Gls{Countess} insists that everyone calm down
with a cup of tea.

\subsubsection{\Gls{Agnes} and the villagers reach the castle}
\Gls{Piotr} helps \Gls{Agnes} wake up when she collapses on the way to the castle. Meanwhile,
\Gls{GWea} and \Gls{Oats} meet \Gls{Ogg} coming down from the tower, as \Gls{IgorV} informs them
of \Gls{Magrat} keeping the baby safe in the crypt. Meanwhile, \Gls{Magrat} traps the \Gls{Countess}
in a jar full of lemons, when she tries to enter the crypt in her mist form. The \Gls{Magpyr}
realizes that \Gls{Magrat} cannot be reasoned with, and slams the door open using brute force.

\subsubsection{\Gls{Magpyr} kidnaps \Gls{Magrat} and the baby}
\Gls{IgorV} arrives at the crypt a few minutes later, and finds \Gls{Scraps} lying dead at the
ruined door. \Gls{Ogg} asks him where the Magpyrs might have taken \Gls{Magrat} and the baby,
as \Gls{Agnes} points out the possibility that they might stay back for a showdown with \Gls{GWea}.
\Gls{IgorV} points out that the heavily bolted door leading down into the secret tunnel is still
closed, and agrees with \Gls{Ogg}.

\subsubsection{\Gls{IgorV} wakes up his old master, tired of \Gls{Magpyr}'s antics}
Angry at the death of \Gls{Scraps}, \Gls{IgorV} reanimates his old master up using a drop of his
blood. He curses \Gls{Magpyr} for his lack of manners, and is appalled by the kidnapping of the
baby. Meanwhile, \Gls{GWea} and \Gls{Ogg} manage to find \Gls{Magpyr} and his family in the
crypt next to the grand pipe organ, as the villagers remain afraid of confronting them directly.

\subsubsection{\Gls{GWea} warns the vampires about their minds being compromised}
\Gls{Magpyr} holds \Gls{Magrat} and the baby hostage, as \Gls{Ogg} tries to argue with him.
\Gls{GWea} walks in with a cup of tea, and notices the vampires eyeing it hungrily. She tells them
that they cannot harm the baby even if they try, and that they will not run away from her until
the situation is resolved. \Gls{Lacci} tries to hit the baby, and is alarmed when her hand disobeys
her all on its own.

\subsubsection{\Gls{RedEM} joins the rest of the family in the crypt}
\Gls{RedEM} morphs from his mist form back to humanoid form in the room, with the villagers
recognizing him as the old vampire from the stories told by their grandparents. He holds \Gls{Vlad}
and \Gls{Lacci} in his hands with little effort, as \Gls{Magpyr} decides to walk out of the
castle with his hostages. \Gls{GWea} reminds him that by drinking her blood, he has imbibed her
values, and cannot harm innocents anymore.

\subsubsection{\Gls{Oats} stops \Gls{Magpyr} using an axe as a religious symbol}
\Gls{Oats} stops \Gls{Magpyr} at the crypt's entrance by holding up an axe, and using it as a
holy symbol instead of a weapon. \Gls{GWea} calls the villagers to cut off \Gls{Magpyr}'s head and
confine him to a grave for fifty years, so that he can think about his crimes. \Gls{RedEM}
recalls \Gls{GWea}'s grandmother, and claims that she had visited the Magpyr castle long ago.

\subsubsection{\Gls{RedEM} vanishes with \Gls{Vlad} and \Gls{Lacci}, to spare them the long rest
    in the crypts}
\Gls{RedEM} promises to teach \Gls{Vlad} and \Gls{Lacci} the traditional ways of vampirism, and
takes them away after transforming into a swarm of magpies. \Gls{Magrat} thanks \Gls{Oats} for
saving her and the baby, as \Gls{VerSec} arrives at the Magpyr castle followed by some villagers
from Lancre, as well as the Feegles.

\subsubsection{\Gls{Oats} decides to leave Lancre for Uberwald after a last sermon}
\Gls{GWea} is pleased to learn that \Gls{Oats} has overcome his fixation with Omnianism, as
\Gls{Jason} repairs the Magpyr carriage to take the royal family back to Lancre. \Gls{Ogg} arranges
a last sermon for \Gls{Oats}, by gathering most of Lancre in front of his tent, including the
royal family. \Gls{Oats} decides to head on to Uberwald, and gratefully accepts \Gls{VerSec}'s
gift of a new amulet, made in the likeness of a double-headed axe.

\subsubsection{\Gls{Agnes} gives \Gls{Oats} a parting gift}
\Gls{Agnes} gives \Gls{Oats} some medication for his acne, and tells him that \Gls{GWea} is doing
just fine in her cottage. She thanks him for helping her cross the treacherous mountain path to
Uberwald, and fights against \Gls{Perdita}, who wishes for him to stay in Lancre. \Gls{Death}
allows \Gls{Scraps} to go back from the afterlife, when \Gls{IgorV} uses a lightning strike to
reanimate its corpse.