\section{The Colour of Magic}


\subsection{}
\subsubsection{The first expedition under the rim of the Discworld is successful}
Zoologists from the kingdom of Krull are lowered past the rim of the world's edge, to investigate
the nature of the \Gls{Atuin}, the cosmic turtle, and the four elephants riding it, who bear
Discworld on their shoulders. The two prevalent hypotheses about the purpose of \Gls{Atuin} are the
Steady Gait (Steady state) and the Big Mating (Big Bang).

\subsubsection{\Gls{Bravd} and \Gls{Wsl} spot a pair of riders fleeing Ankh-Morpork}
\Gls{Wsl} and \Gls{Bravd} watch the burning city of Ankh-Morpork from a nearby hill, scanning for
anyone who might be fleeing the city through its gates. \Gls{Bravd}'s attempts to waylay a
wealthy-looking man coming out of the city is thwarted when he gets recognized. \Gls{Wsl} emerges
from his hiding place, identifying the escapee as \Gls{Rince}, a poor wizard.

\subsubsection{\Gls{Rince} talks about the sentient chest}
\Gls{Rince} tells \Gls{Wsl} that his companion \Gls{Twofl} had originally set fire to the city,
using the fact that he was a lightning rod for bad luck. He runs back to get \Gls{Twofl}, who is
knocked out by his horse, and shows them the sentient chest that walks along with him. \Gls{Wsl}
is unimpressed by \Gls{Rince}'s claims of strange magic from the chest compelling him to help
\Gls{Twofl}, as \Gls{Bravd} offers some food and drink.

\subsubsection{\Gls{Twofl} arrives at the Ankh-Morpork by ship}
\Gls{Wsl} notices the river Ankh being forcefully diverted into the burning city to flood it,
quenching the fire and ruining everything left in it that was not flammable. A few days earlier,
\Gls{Twofl} arrives by ship at the city, with the sentient chest in tow. He uses a phrasebook to
try and find accommodation, causing a spectacle with his casual splurging of gold coins.

\subsubsection{\Gls{Hugh} leads \Gls{Twofl} to the Broken Drum}
\Gls{Hugh}, a beggar on the harbour with a preternatural sense for gold, accosts \Gls{Twofl} and
promises to take him to a nearby tavern. He is terrified by the sentient chest walking along behind
\Gls{Twofl}, as he leads the newcomer to the Broken Drum, a nearby inn. Elsewhere in the city,
underworld boss \Gls{Ymor} speculates that the newcomer is a spy or a merchant, as he thinks about
the gold that might be swindled from him.

\subsubsection{\Gls{Twofl} tries to pay for room and board with gold coins}
\Gls{Withel}, a thief in the employ of \Gls{Ymor}, informs him that the ship captain had taken on
\Gls{Twofl} as a trader, with a raven informing him of \Gls{Hugh} leading the newcomer to
\Gls{Broad}'s tavern. At the broken drum, \Gls{Hugh} holds up three fingers to indicate the cost
of board being three copper pieces. \Gls{Twofl} misunderstands, placing three fat gold coins on the
bar.

\subsubsection{\Gls{Rince} recognizes the value of the sentient chest}
\Gls{Broad} tries to mime food and drink, as \Gls{Rince} identifies the sapient pearwood that the
chest is made of, from a dark corner of the tavern. The wizard, who is a graduate of Unseen
University, and was dishonourably discharged some time ago, uses his proficiency with languages to
try and talk to \Gls{Twofl}.

\subsubsection{\Gls{Twofl} talks to \Gls{Rince} about meeting some adventurers}
\Gls{Broad} hastily tells \Gls{Rince} that his own boarding and meals will be free if he helps
scam the foreigner. For his part \Gls{Rince} reminds \Gls{Twofl} that he would be killed very soon
by the many gangs converging on the Inn, using the Torb language. \Gls{Twofl} introduces himself,
excited to visit one of the famed taverns of Ankh-Morpork, and wishes to meet some adventurers
frequenting such establishments.

\subsubsection{\Gls{Broad} verifies the gold content of \Gls{Twofl}'s coins}
\Gls{Twofl} explains that he is from the port city of Bes Pelargic in the Agatean Empire.
\Gls{Rince} is shocked to meet someone from the Counterweight Continent. Meanwhile, \Gls{Broad}
learns from an alchemist that \Gls{Twofl}'s gold coin is pure, unlike those of Ankh-Morpork, causing
him to hurry back to the tavern. The alchemist sends a message to someone by homing rat, as a
nearby fortune-teller happens to scry the burning of the city.

\subsubsection{\Gls{Twofl} explains his reasons for visiting the city}
\Gls{Twofl} talks about the drudgery of his life as a clerk in Bes Pelargic, and of how he had
decided to see the world for himself. \Gls{Rince} reminds him that the currency he has will pay for
much more in Ankh-Morpork, and that he has massively overpaid the innkeeper. \Gls{Twofl} insists on
paying \Gls{Rince} in advance, for his help as a guide, and drops a few gold coins in his hands.

\subsubsection{\Gls{Rince} is brought to stand before the \Gls{Patri} of Ankh-Morpork}
\Gls{Rince} is captured and brought to the \Gls{Patri}'s palace in Ankh-Morpork, where he is accused
of trying to buy the horse using bad currency. \Gls{Rince} tries to argue that solid gold is a valid
medium of exchange, but grows quiet when he realizes the \Gls{Patri} is merely trying to get him to
become the foreigner's companion.

\subsubsection{\Gls{Patri} asks \Gls{Rince} to act as a tour guide for \Gls{Twofl}}
The \Gls{Patri} talks about the wealth and hostility of the Agatean Empire, and of how the visitor
was likely undercover to survey the Circle Sea's many city-states. He asks \Gls{Rince} to guide
the foreigner, ensuring he returns home with a positive impression of Ankh-Morpork, thus making
trade-deals more feasible between the two empires.

\subsubsection{\Gls{Rince} reaches \Gls{Twofl} at the tavern}
\Gls{Rince} returns to the Broken Drum, to find a massive brawl in the main floor, with bodies
littering the ground. He manages to sneak up the stairs to the lodgings, and finds \Gls{Twofl}
fast asleep in his room. He is tempted to reach into the pearwood \Gls{Lugg} for the bag of gold,
as \Gls{Twofl} wakes up, oblivious to the bloodbath that had just taken place downstairs.

\subsubsection{\Gls{Rince} is horrified by \Gls{Twofl}'s desire to meet the barbarian heroes}
\Gls{Rince} thinks about the barbarian heroes from the frozen hubland wastes, and tries to explain
the grim reality of their questing around Ankh-Morpork. \Gls{Twofl} is insistent on meeting some of
the famous heroes like \Gls{Bravd} and \Gls{Hrun}, just as a Sergeant of the City Watch arrives at
the tavern. \Gls{Rince} notices the survivors being given plenty of time to escape, with the city
guardsmen cleaning up the bodies afterward.

\subsubsection{\Gls{Rince} escorts \Gls{Twofl} away from the Broken Drum}
\Gls{Rince} lies about the corpses in the tavern being minor heroes, causing \Gls{Twofl} to pull out
his iconograph (polaroid), and ask the city watch to pose for a picture. \Gls{Rince} explains to the
terrified guards that the box contains a demon that draws pictures, and marvels at the little piece
of glass with his picture on it. During lunch, \Gls{Twofl} explains that he is an risk assessor for
an insurance firm, leaving \Gls{Rince} flummoxed.

\subsubsection{\Gls{Rince} escapes from \Gls{Withel} using the \Gls{Lugg} as a distraction}
After a day out taking pictures of the city's sights, \Gls{Rince} is alarmed by the imp within
the iconograph poking its head out the side to warn him that there was no ink remaining. He finds
\Gls{Twofl} missing, and is held up by \Gls{Withel} at knife-point. When he runs into the riverbank,
desperate to get away from \Gls{Withel}, the single spell burrowed in his memory tries to show
itself.

\subsubsection{\Gls{Rince} is joined by the \Gls{Lugg} at the banks of the Ankh river}
\Gls{Rince} is surprised to see the \Gls{Lugg} catch up to him, speculating that he is now its
master in the absence of \Gls{Twofl}. He decides to wait for dusk, and to swim out through the
Ankh river gate, hoping that the \Gls{Lugg} is buoyant enough to bear his weight. He feels guilty
about leaving \Gls{Twofl} to his fate, before the idea of living a wealthy life in some faraway
kingdom entrances him.

\subsubsection{\Gls{Patri} receives a second message from the Golden Empire's \Gls{GViz}}
The \Gls{Patri} asks one of his veteran diplomats to explain why a second message had arrived by
albatross from the Golden Empire, asking \Gls{Twofl} to be executed. The diplomat states that the
first message from the \Gls{Empe} had asked for the visitor to be protected, whereas the second one
was from the \Gls{GViz}, who might dread the idea of someone bringing back stories of a free
society flourishing elsewhere.

\subsubsection{\Gls{Rince} talks to the imp in the iconograph}
The \Gls{Patri} asks for the president \Gls{Zlorf} of the Assassins' Guild to be tasked with
eliminating the foreigner. Meanwhile, \Gls{Rince} tries to argue with the imp in the iconograph
about the alternative to magic that \Gls{Twofl} had said was prevalent in his homeland (science).
The imp reminds him that the \Gls{Lugg} contains a reserve of food and drink, bringing him relief
from the hunger that had begun to creep up on him.

\subsubsection{\Gls{Twofl} is held by \Gls{Ymor} at teh Broken Drum}
\Gls{Rince} uses gold coins to lure a thug keeping standing watch outside \Gls{Ymor}'s hideout, and
learns from him that \Gls{Twofl} is being held captive at \Gls{Broad}'s tavern. Meanwhile, at the
Broken Drum, \Gls{Ymor} watches with amusement as \Gls{Twofl} explains insurance to \Gls{Broad},
even getting him to agree to a policy premium.

\subsubsection{\Gls{Ymor} meets \Gls{Zlorf} and then \Gls{Rerpf}}
\Gls{Zlorf} barges into the Broken Drum, asking to kill the tourist, only for \Gls{Ymor} to remind
him that he was surrounded by even more thugs. He asks \Gls{Zlorf} to sit down, only for \Gls{Rerpf}
to enter the tavern behind him, flanked by several armed trolls. He introduces himself as the
representative of the recently formed Guild of Merchants, here to protect the foreigner, who was
valuable to the tourism industry.

\subsubsection{\Gls{Rince} talks to \Gls{Death}, as it stalks the streets of Ankh-Morpork}
\Gls{Rince} runs into \Gls{Death} on his way through the city's markets, and is alarmed to learn
that his own demise was scheduled for later that day, in some far off place. \Gls{Death}, as a
spirit visible only to the fine-tuned senses of a wizard, tells him that the prediction system had
gone haywire recently, as he runs away horrified.

\subsubsection{\Gls{Rince} and \Gls{Twofl} reunite in the tavern}
\Gls{Rince} throws bags of gold through the windows of the Broken Drum, to distract from the
\Gls{Lugg} preparing to break down the door in a charge. Once inside, \Gls{Twofl} cuts down the
hanging light, from a rafter on the ceiling. The people in the tavern are horrified by the
\Gls{Lugg}, and run for the exit in the absolute darkness. Meanwhile, \Gls{Broad} works in the
basement, preparing for a great fire to consume his inn, to claim the insurance policy.

\subsubsection{\Gls{Rince} defeats \Gls{Withel} using \Gls{Twofl} as a distraction}
\Gls{Death} itself gives \Gls{Broad} the tinder necessary to start the fire, as \Gls{Withel}
challenges \Gls{Rince} to a duel outside the inn. \Gls{Rince} stays alive out of sheer luck, as
\Gls{Twofl} shows up to distract the thief. \Gls{Rince} knocks out \Gls{Withel} in the split-
second of confusion, as the inn explodes in a firestorm that spreads through the street.

\subsubsection{\Gls{Twofl} and \Gls{Rince} buy horses to escape the flaming city}
\Gls{Twofl} tells \Gls{Rince} that he had insured the Broken Drum for two hundred gold coins, making
\Gls{Rince} realize that the proprietor had probably destroyed his own inn to cash out on the
policy. He finds some horses to escape the city, and is amused to see \Gls{Twofl} incapable of
riding one. Meanwhile, the \Gls{Lugg} emerges from the Ankh river some distance form the city, and
immediately sets off towards its master.

\subsubsection{\Gls{Wsl} and \Gls{Bravd} prepare to raid Ankh-Morpork for abandoned riches}
The \Gls{Wsl} finishes listening to \Gls{Rince}'s story, and prepares to raid the burnt-out city
for possessions left behind by its fleeing inhabitants. He reveals the tourist's pocket-watch, that
he had stolen on the way out, only to be bitten by the imp inside it that kept the time on an
abacus. He smashes the watch on the ground, banishing the imp to its home-realm, as \Gls{Bravd}
reminds him of the riches waiting for them in the ruined city.

\subsection{}
\subsubsection{The Discworld gods play their latest game with in their abode}
At Dunmanifestin, the home of the Discworld Gods, a game-board resembling a miniature disc is laid
out, with pieces representing its many heroes. After most players cash out of the game, or go
bankrupt, \Gls{Lady} takes out two pieces resembling \Gls{Rince} and \Gls{Twofl}, to set them on
the board as her newest pawns.

\subsubsection{\Gls{Rince} and \Gls{Twofl} flee Ankh-Morpork on horseback}
\Gls{Rince} and \Gls{Twofl} ride through the mountain trail to Chirm, with \Gls{Twofl} exasperated
by the claims that some system more logical than the magic of Discworld had to exist somewhere.
\Gls{Rince} hears the faint noise of bones clattering, as if dies were being rolled, and is alarmed
to find no one next to them.

\subsubsection{\Gls{Rince} and \Gls{Twofl} face a troll on the road to Chirm}
An angry troll appears on the road in front of \Gls{Rince}, seemingly teleported there from its
home in a faraway land. It charges them, with \Gls{Rince} missing his thrown short-sword. The
sword rebounds from a boulder on the side of the road, and impales the troll's neck, killing it.
Wounds from the troll's claws scatter \Gls{Rince} and \Gls{Twofl}'s horses, making them gallop in
opposite directions offroad.

\subsubsection{\Gls{Twofl} finds a statue pointing him to the temple of \Gls{Belsh}}
\Gls{Twofl} thinks about the jungle predators that his horse had disturbed in its mad dash away
from the troll, as he spots a stone carving with strange runes etched into it. The message bypasses
his cognition, directly informing him that the temple of \Gls{Belsh} was nearby. He decides to find
shelter in the temple, and follows a dirt track, hoping to escape the wolves in pursuit.

\subsubsection{\Gls{Lady} and \Gls{Fate} continue their game in the abode of the Gods}
\Gls{Rince}, hanging desperately from the collapsing branch of a tree, watches a hornet's nest get
blown into the pack of hungry wolves waiting for him down below. Meanwhile, at the game board in
Dunmanifestin, \Gls{Fate} and \Gls{Lady} are the last two players left, with \Gls{Fate} taking out
an icon representing an ancient eldritch monster. \Gls{Lady} reaffirms her ability to match his
bet, and asks him to keep playing.

\subsubsection{\Gls{Rince} is saved by \Gls{Druell}}
\Gls{Rince} is rescued by the dryad of the tree, who introduces herself as \Gls{Druell}. She tells
him that his friend is entering a temple of \Gls{Belsh} nearby, bringing back memories of his time
in the Unseen University's library, and of how he had read the Octavo, the forbidden spellbook that
was kept chained in a magic-insulated room.

\subsubsection{\Gls{Rince} is held captive by the dryads, who plan to kill him}
\Gls{Rince} realizes he has been captured by the tree, when some male dryads arrive to stop him
from leaving. \Gls{Druell} tells him that he will have the privilege of watching his friend suffer
\Gls{Belsh}'s cruelty, before he is killed for the crime of injuring the tree. As he is escorted
through the tree, \Gls{Rince} realizes the dryads are like insects in a hive, and is reminded of
the fact they should be extinct by now.

\subsubsection{\Gls{Rince} tries and fails to escape the tree}
The dryads summon a magical hologram of the temple of \Gls{Belsh}, showing a large horse tethered
near its entrance. \Gls{Druell} laughs at the fact that someone other than \Gls{Twofl} is also
in the temple, with the male dryads watching the proceedings carefully. \Gls{Rince} uses the
distraction to try and escape, but is encircled by the guards. He asks \Gls{Druell} to peer into
his mind to see the one spell he knows, making her recoil in horror at its power.

\subsubsection{\Gls{Hrun} and \Gls{Twofl} navigate the temple of \Gls{Belsh}}
\Gls{Rince} runs through the center of the ritual circle sustained by the female dryads meditating
in harmony, causing it to collapse. Meanwhile, \Gls{Hrun} silently walks through the dark corridors
of the temple, in pursuit of the \Gls{Lugg}, having spotted the bags of gold inside it. \Gls{Twofl}
asks the imp in his iconograph why it is so unnerved, just as \Gls{Rince} appears out of a portal,
gradually growing to his full size.

\subsubsection{\Gls{Rince} and \Gls{Twofl} reunite within the temple}
\Gls{Rince} begs \Gls{Twofl} not to utter the forbidden number (eight), as he realizes he is in some
underground chamber of the temple. He recounts the laws around the storage of  powerful magical
tomes, and of how he had been expelled from the Unseen University once the spell from the Octavo
had vanished from the page and lodged itself in his mind.

\subsubsection{\Gls{Twofl} and \Gls{Rince} run into \Gls{Hrun}}
At a central chamber, \Gls{Twofl} prepares to take some pictures of a central dais with a stone slab
on it, as \Gls{Hrun} walks in, pointing to the \Gls{Lugg}. \Gls{Rince} reminds him not to utter the
forbidden number, only for his sentient sword \Gls{Kring} to say it nonchalantly. As \Gls{Belsh}
sends out tentacles from the pit in the center of the chamber to drag them in, \Gls{Rince} uses the
pink lizards in \Gls{Twofl}'s box to make a bright flash, blinding the monster.

\subsubsection{\Gls{Hrun} decides to pursue \Gls{Belsh} through the pit in the chamber}
\Gls{Belsh} lets go of the intruders and slithers back into its pit, leaving \Gls{Rince} to study
the magic salamanders in \Gls{Twofl}'s box. They had fed on the dense octarine radiation within the
temple and excreted it at the opportune moment, blinding \Gls{Belsh}, and forcing him to retreat.
\Gls{Hrun} recovers, and immediately starts dislodging the stone slab protecting the \Gls{Belsh}'s
pit, convinced there is treasure buried underneath.

\subsubsection{\Gls{Rince} and the adventurers make it out on \Gls{Hrun}'s warhorse}
\Gls{Rince} realizes that the magical gale blowing into the pit, was the accumulated effect of
Time on the temple, kept away so far by the intimidating presence of \Gls{Belsh}. The roof of the
chamber starts to sag, sending inlaid octagonal stones falling down. \Gls{Hrun} summons his massive
warhorse, which carries them out of the temple just as it collapses into ruin, with Time making
amends for centuries of inaction.

\subsubsection{\Gls{Rince} and \Gls{Twofl} consider the idea of hiring \Gls{Hrun} as protection}
Outside the temple, \Gls{Hrun} kills a bear for food, with \Gls{Twofl} sorting through the
silver statues plundered from the temple. \Gls{Rince} pre-empts his idea of traveling in the
company of \Gls{Hrun}, by reminding him that the barbarian would likely rob them, and leave them to
the jungle predators. \Gls{Rince} realizes that \Gls{Hrun} could be lured into protecting them,
by appealing to his sense of vanity.

\subsubsection{\Gls{Rince} uses the iconograph to pay for \Gls{Hrun}'s services}
\Gls{Hrun} insists on more attempts at posing, delighted by the pictures \Gls{Rince} takes of him
standing victorious over slain brigands and monsters. At Dunmanifestin, \Gls{Fate} resigns from the
game, pushing his soul-chips across the game board to \Gls{Lady}. Meanwhile, \Gls{Death} watches
\Gls{Rince} ride off from the ruined temple, annoyed by his repeated escape from his scheduled
demise.

\subsection{}
\subsubsection{\Gls{Rince} realizes the party is in a strong magical field}
At a small cave along a road, \Gls{Rince} suspects the presence of a strong magical field, and asks
\Gls{Hrun} to toss a coin. The wars between the First Men and the Discworld Gods had been so
destructive that the High Old Ones had exterminated the former, and confined the latter to a remote
hideout. \Gls{Rince} suggests backtracking through the magical radiation field, and using the coins
to check if they are safe.

\subsubsection{\Gls{Liessa} intends to capture the riders intruding in her realm}
\Gls{Liessa} observes \Gls{Rince}'s party through a scrying glass, taking great interest in the
sapient pearwood. Her father, a powerful wizard suspended in purgatory for the last few months, asks
her to pursue them before they escape her zone of influence. He secretly hopes that she will get
killed, as payback for her mortally wounding him.

\subsubsection{\Gls{Liessa} and her dragons catch up to \Gls{Hrun}'s party}
\Gls{Liessa} goes to the dragon roost in the hollow interior of Wyrmberg, the inverted mountain that
was her hideout. She thinks about the ease with which she could rule over Wyrmberg if she had a
dim-witted brute as her mate, and sets her eyes on capturing \Gls{Hrun}. \Gls{Rince} and his party
are chased by the dragons, with only \Gls{Rince} making it to the cover a dense canopy.

\subsubsection{\Gls{Rince} is compelled by \Gls{Kring} to try and rescue his companions}
\Gls{Rince} wakes up from his concussion, and manages to evade the gaze of a dragon perched on a
high branch, as he runs away. Eventually, he finds \Gls{Kring} lodged in the branches of a tree,
asking him to turn around and rescue the others. He decides to retrieve the magical sword, and head
back to town to sell it. \Gls{Kring} however, compels him to rescue the others, by hijacking the
sword arm and setting it to his throat.

\subsubsection{\Gls{Rince} forces a dragon-rider to take him to Wyrmberg}
\Gls{Kisdra}, the lone dragon-rider left to hunt down \Gls{Rince}, is subdued when \Gls{Kring} uses
its skills to disarm him, and hold him hostage. \Gls{Rince} asks to be taken to Wyrmberg so that he
might rescue his friends, and is horrified to learn that the only entrance is through the dragon
caves high up along its face.

\subsubsection{\Gls{Rince} arrives at the dragon perch within Wyrmberg}
\Gls{Rince} notices the strong magical fields surrounding Wyrmberg, and notices the dragon grow
less transparent as it approaches the mountain. As the dragon perches on its huge ring inside the
hollow central chamber of Wyrmberg, \Gls{Rince} notices other dragon-riders converging on him with
crossbows armed. \Gls{Kring} advises him to attack them head-on, and sends waves of pain through
his hands when he considers surrender.

\subsubsection{\Gls{Rince} miraculously escapes \Gls{Death} using bullet time}
\Gls{Liort}, a dragonlord, challenges \Gls{Rince} to mortal combat, believing him to be a hero.
\Gls{Kisdra} helps \Gls{Rince} don a harness and boots, and teaches him how to navigate the ceiling
using the system of hooks and rings. As \Gls{Liort} prepares to deliver a killing blow, \Gls{Rince}
enters bullet-time, ducking under \Gls{Death}'s swinging scythe, and alarming \Gls{Liort} with his
superhuman speed.

\subsubsection{\Gls{Twofl} and \Gls{Hrun} investigate their jail cell}
\Gls{Rince} hangs on desperately from \Gls{Liort}'s hand, as both of the rings suspending him
give way, and lets go when the other dragon-riders aim their crossbows at him. Meanwhile, \Gls{Hrun}
and \Gls{Twofl} argue about the translucent dragons being the real thing, as they inspect the
treasure in the rooms adjoining their cell.

\subsubsection{\Gls{Liessa} convinces \Gls{Hrun} to perform some feats for her}
\Gls{Liessa} walks in with some crossbowmen, and stabs the sleeping \Gls{Hrun}, and is satisfied
when he reflexively stops her. When he wakes up, she tells him that there are more tests he needs
to pass, in order to win a valuable reward. \Gls{Twofl} is escorted to an adjacent cell, as
\Gls{Liessa} gives \Gls{Hrun} the task of killing her two brothers, to put her in line for the
throne of Wyrmberg.

\subsubsection{\Gls{Twofl} and his dragon reach the throne room of Wyrmberg}
\Gls{Hrun} is pleased by the prospect of winning \Gls{Liessa}'s hand and the treasures heaped in
Wyrmberg, as \Gls{Twofl} notices a dragon occupying most of his cell. It tells him that his own
imagination summoned it into existence, and melts the metal door on his orders. He navigates the
dusty corridors of Wyrmberg, noticing the dragon-sized harnesses rotting along the walls. Finally,
he comes across a set of massive double doors, opening to the slightest touch.

\subsubsection{\Gls{Twofl} talks to \Gls{Greicha} in the throne room}
In the throne room, the wizened old corpse on the chair introduces himself as \Gls{Greicha}, a
First Human now locked in purgatory, free of the constraints of time. He tells \Gls{Twofl} that he
also has the Power (of imagination ?), enabling him to summon true dragons by imagining them in
great detail, while in a place impregnated with a strong magical field.

\subsubsection{\Gls{Greicha} explains his predicament to \Gls{Twofl}}
\Gls{Greicha} bemoans his daughter's lack of imagination, leading to her dragons being weak and
translucent, and reveals that succession in his family required the elimination of all competing
claimants. He tells \Gls{Twofl} that the same route used by \Gls{Liessa} will lead to \Gls{Rince},
who is in danger of being killed by \Gls{Liort}.

\subsubsection{\Gls{Twofl} saves \Gls{Rince} in the roosting chamber}
\Gls{Twofl} and his dragon arrive at the roosting chamber, in time to catch \Gls{Twofl} as he
falls from the ceiling. \Gls{Rince} almost finishes uttering the forbidden spell sealed in his mind,
as he is caught by \Gls{Twofl}, getting knocked out in the process.

\subsubsection{\Gls{Hrun} defeats \Gls{Liessa}'s brothers}
On top of the Wyrmberg, \Gls{Liort} and his brother \Gls{Liart} mount their dragons to face
\Gls{Hrun}, who \Gls{Liessa} chooses as her champion. \Gls{Hrun} manages to knock out both brothers,
making their dragons vanish. \Gls{Liessa} informs him that the dragons are imaginary, (Imagined
Dragons), and reminds him that there is one final test remaining.

\subsubsection{\Gls{Hrun} is rescued by \Gls{Twofl}'s dragon}
\Gls{Twofl} asks his dragon to fly to \Gls{Hrun}'s rescue, as \Gls{Rince} tries to deal with his
fear of heights. The dragon snatches \Gls{Hrun} in its claws, causing \Gls{Liessa} to furiously
summon her own golden dragon and gives chase (Freud comes up with his theory of girls subconsciously
sexualizing horse-riding). \Gls{Death} uses the commotion to snatch \Gls{Greicha}'s soul, ending
his self-imposed purgatory.

\subsubsection{\Gls{Twofl} and \Gls{Rince} shift into the real world}
\Gls{Twofl} passes out from the thinning air when his dragon flies high up, causing all of them
to fall. \Gls{Hrun} is caught by \Gls{Liessa}'s dragon, with \Gls{Death} appearing beside
\Gls{Rince} to taunt him once again. He crosses realities with \Gls{Twofl}, and is now a doctor on
an airplane helping defuse a bomb.

\subsubsection{\Gls{Rince} and \Gls{Twofl} are dragged back into their original reality}
When the \Gls{Lugg} crashes into the airplane, causing a large hole in it, \Gls{Twofl} and
\Gls{Rince} are banished back to their original reality by the multiverse trying to correct itself.
They fall into the Circle sea, having been displaced many miles during their reality shift.

\subsection{}
\subsubsection{\Gls{Archast} kills \Gls{GSDact} after he finishes building the bronze submersible}
In the secretive rimward kingdom of Krull, \Gls{Archast} supervises the completion of their latest
submersible, designed by \Gls{GSDact}, the greatest craftsman in all Discworld. \Gls{Archast}
patiently listens to his tales of losing parts of his body after completing each of his contracts,
and finally kills him, to prevent the possibility of an equally impressive piece of art ever being
recreated.

\subsubsection{\Gls{Rince} and \Gls{Twofl} accidentally get swept to a Rimfall}
\Gls{Rince} and \Gls{Twofl} try desperately to keep their ship afloat, after escaping some slavers,
and notice a current dragging them into the Rimfall on the outer rim of Discworld. As their ship
approaches the Rimfall, \Gls{Rince} rescues a frog struggling against the current, and shoves it
into an inside pocket. \Gls{Twofl} sees no point in worrying about their impending deaths, as
something metallic hits their hull, causing \Gls{Rince} to nearly drown.

\subsubsection{\Gls{Twofl} and \Gls{Rince} are rescued by \Gls{Tethis}}
The captain of the slaver ship that had fished out \Gls{Rince} and \Gls{Twofl} prepares his raft,
as the bloodbath wrought by the \Gls{Lugg} forces him to abandon his own ship. Meanwhile,
\Gls{Twofl} helps \Gls{Rince} get up, and tells him that a sea troll named \Gls{Tethis} had rescued
them, and that they were currently tethered to the Circumference, a system of ropes and pulleys
just inside the rim of Discworld.

\subsubsection{\Gls{Tethis} rows his boat to his home at the edge of the rim}
\Gls{Rince} notices a small island at the rim, with the troll's shack being built on it. He also
sees the system of ropes and bells attached to it, resembling a spiderweb, as the boat slides into
a makeshift jetty. He dares to look at the troll, and is pleased to find a humanoid shape made
entirely out of water, instead of the horribly disfigured monster he had imagined.

\subsubsection{\Gls{Twofl} learns about the Circumference}
\Gls{Twofl} recognizes the green drink offered by \Gls{Tethis}, as Ghlen Livid (GlenLivet whiskey),
a distilled fermented drink from his homeland. \Gls{Tethis} then talks about the Circumference being
a net constructed by the Krull, spanning the entirety of the rim of Discworld, and of how he had
been enslaved by them when he tried to sail into the Rimfall.

\subsubsection{\Gls{Tethis} talks about his journey to Discworld from his home of Bathys}
\Gls{Tethis} suspends \Gls{Rince} over the rimward edge of his island, allowing the wizard to
see the elephants and \Gls{Atuin} holding up the Disc. He talks about his own cowardice when it came
to jumping off the edge, and possibly returning to his home world of Bathys. He explains his journey
through the void between worlds, given how his body was capable of withstanding the cold, unlike
humans.

\subsubsection{\Gls{Rince} and \Gls{Twofl} learn about their imminent capture by the Krull}
\Gls{Rince} tries and fails to injure \Gls{Tethis} with a sword he finds in the boxes strewn around
the shack, with the troll reminding them of the moon's tides affecting its size throughout the day.
A message arrives by bell from the slavers of Krull, declaring that \Gls{Rince} and \Gls{Twofl}
were to be collected immediately by flyer, instaed of the usual salvage fleet that would visit the
island periodically.

\subsubsection{\Gls{Rince} and \Gls{Twofl} are forced on board the Krull flyer}
A Krull flyer arrives at the island, piloted by a squad of hydrophobe mages. \Gls{Rince} marvels
at the magical resources needed to construct such a vessel, as he is forced to climb aboard it, and
fasten himself to one of the rings on its floor. Some ferocious sea monster speeds towards
\Gls{Tethis}, as the Krull vessel lifts off, to return to the capital.

\subsubsection{The \Gls{Lugg} manages to escape the sinking of the pirate ship}
The \Gls{Lugg} sinks along with the pirate ship, and is swallowed by a sea monster in the depths of
Gorunna Trench. Later, the monster washes ashore dead on a small rimward island, and a straight line
of destructive force travels towards the rim, cutting through many other atolls.

\subsubsection{\Gls{Rince} and \Gls{Twofl} are taken to the city of Krull}
\Gls{Rince} is stunned into silence, by the wizard holding the wand of Negativity over him, as he
sees the hand shaking in fear. The witch introduces herself as \Gls{Marchesa}, and reveals that they
are not slaves, but ritual sacrifices. When he reaches the capital city of Krull, \Gls{Rince}
and \Gls{Twofl} are led into a richly appointed room, with a seafood feast laid out on a grand table
for them.

\subsubsection{\Gls{Garha} explains the ritual sacrifice in store for \Gls{Rince} and \Gls{Twofl}}
\Gls{Garha}, the Krull Guestmaster, introduces himself to \Gls{Rince}, explaining the delicacies
laid out on the dining table in front of them. He reveals that the sacrifice is due for the next
morning, and leaves them sealed in the guest chamber, to get ready for the ritual. Meanwhile,
the \Gls{Lugg} surfaces at the rim, and makes its way along the rope lines of the Circumference,
crashing through any islands along the way.

\subsubsection{\Gls{Rince} learns about the Krull expedition past the rim}
\Gls{Rince} takes the frog out of his robes, and sees it enshrouded in a tornado of magical
radiation. The magical field dissipates, to reveal the same frog, with \Gls{Lady} standing by its
side. She tells them that the Krullians intend to lower a submersible past the rim of Discworld, to
investigate \Gls{Atuin}. She tells them that \Gls{Fate} has been conspiring against them, demanding
that they be sacrificed to ensure the safety of the expedition.

\subsubsection{\Gls{Garha}'s own bottle knocks him out when his spell wears off}
The frog telepathically tells \Gls{Rince} to prepare for \Gls{Garha}, just as \Gls{Lady} vanishes,
and guards enter their room to escort them out. The bottle that \Gls{Rince} had thrown earlier at
the Guestmaster out of anger, now resumes its normal trajectory after the time-spell slowing it
down wears off, and knocks \Gls{Garha} out, allowing the two prisoners to escape.

\subsubsection{\Gls{Fate} is exasperated by \Gls{Death}'s ambivalence regarding \Gls{Rince}'s
    demise}
\Gls{Twofl} and \Gls{Rince} escape some hydrophobe wizards by pushing them into a pool, and make it
to the safety of a planetarium. Meanwhile, \Gls{Fate} viists \Gls{Death} in his hideout, and
insists that \Gls{Rince} and \Gls{Twofl} were certain to be claimed in the coming Krull sacrifice.
\Gls{Death} reminds him that he had bigger business to attend to, than chase after these two souls
that repeatedly eluded his grasp.

\subsubsection{\Gls{Twofl} and \Gls{Rince} take the place of the chelonauts}
\Gls{Twofl} suggests volunteering as the chelonauts, when he spots the two spacesuits hanging in
one corner of the planetarium, just as the two original astronauts step into the room, having
finished their bath. \Gls{Rince} is annoyed by the fact that he cannot make sense of their language,
They knock out the two youths, and prepare to come out of the room, wearing the suits.

\subsubsection{\Gls{Archast} notices something odd with one of the chelonauts}
At the launch site, \Gls{Archast} is furious when told of the escape of the two prisoners, and
brushes off some news from the harbour, about a monster ravaging the docked ships (\Gls{Lugg}).
As the chelonauts are escorted into the arena set up for the citizens to witness the launch,
the \Gls{Archast} grows suspicious of \Gls{Rince}'s gait, and starts to prepare a levitation
Curse.

\subsubsection{\Gls{Twofl} and \Gls{Rince} are reunited with the \Gls{Lugg}}
The \Gls{Archast} is interrupted by the \Gls{Lugg} breaking into the launchpad, forcing him and his
underlings to fire all of their offensive magic at it. The confluence of magic makes a positive
feedback loop with the ambient magical field, causing a huge explosion that sends the mages
running. A while later, after the \Gls{Lugg} spits out \Gls{Tethis} at its master's feet, some
soldiers try to retake control of the arena.

\subsubsection{\Gls{Rince} and his party board the submsersible}
\Gls{Rince} wonders how the \Gls{Lugg} manages to swallow so many people, while keeping its master's
belongings completely isolated from the bloody aftermath. \Gls{Twofl} and \Gls{Tethis} manage to
undo the hatch leading into the ship, just as soldiers start to climb the ladder leading to it.
\Gls{Rince} hastily descends the ship's interior, just as an automated mechanism sets the ship in
motion along the rail designed to launch it over the Discworld's rim.

\subsubsection{\Gls{Rince} escapes \Gls{Death}'s apprentice}
\Gls{Rince} gets caught in a tree growing off the edge of the Rim, and is visited by \Gls{Death}'s
apprentice. The little demon tells him that \Gls{Death} cannot come in person because of a plague
in progress elsewhere, and is dismayed when \Gls{Rince} loses his grip on the branch, to fall into
the void of space.