\section{Darwin's Watch}


\subsection{}
\subsubsection{\Gls{Rince} talks about history going wrong in Roundworld yet again}
\Gls{Rince} tells the council of wizards that the progress of humanity on Roundworld has gone wrong
yet again, and takes them to the corridor outside his office, where the globe is kept. \Gls{Ridcu}
observes an ice age covering the planet, as \Gls{Stibb} receives a report from \Gls{Hex} pointing
out where and when the timeline diverged on Roundworld from the good ending where humans get off
the planet to avoid the apocalypse.

\subsubsection{\Gls{Stibb} learns about the catastrophic book authored by \Gls{CDar}}
\Gls{Stibb} points out nineteenth-century England under Queen Victoria as the likely cause of the
timeline worsening, with the wizards quickly losing interest when he starts to talk about his
multiverse theory. The next morning, \Gls{Stibb} learns from \Gls{Hex} that \Gls{CDar} has grown up
to be a creationist, and authored the seminal book on young-earth creationism that stifles any
inquiry into the question of evolution.

\subsubsection{\Gls{Stibb} outlines his proposal for the cause of the Roundworld timeline
    diverging}
\Gls{Ridcu} patiently listens to \Gls{Stibb} describe the two diametrically opposite books written
by \Gls{CDar} in the two possible timelines. \Gls{Stibb} then states that creationism was overturned
too late in the bad timeline for humanity to escape the apocalypse, since creationism became
established dogma for many centuries after \Gls{CDar}'s death.

\subsubsection{\Gls{Stibb} talks about the influence of \Gls{CDar} on Roundworld science}
The \Gls{Libra} notices a picture of \Gls{CDar} on the front cover of his book, and takes note of
the uncanny resemblance he bears to \Gls{Ridcu}. Meanwhile, \Gls{Stibb} tries to explain how the
publishing of \Gls{CDar}'s creationist book led to the hegemony of creationism for many decades,
and thwarted the timely progress of science on the Roundworld, dooming them to extinction with the
next Ice Age.

\subsubsection{\Gls{Hex} reveals the precarious nature of \Gls{CDar}'s expedition and resulting
    epiphany}
\Gls{Hex} is alarmed by the revelation that \Gls{CDar} only wrote his book on natural selection in
one of the infinite timelines within Roundworld. It performs some more calculations and detects
some meddling by a hostile force seeking to prune the possible timelines where the correct book is
written, and implores the wizards to intervene in \Gls{CDar}'s life to help him.

\subsubsection{\Gls{Ridcu} gets his council ready for the trip into Roundworld}
\Gls{Ridcu} gets the \Gls{Libra} to wear a wig and false beard in order to fit into Victorian
society, as the rest of the council look through some costume suggestions printed by \Gls{Hex}.
\Gls{Stibb} states that there are about ten crucial points in \Gls{CDar}'s life where the wizards
will have to interfere to ensure the correct outcome, as \Gls{Hex} prepares a portal to take them
into Roundworld London.

\subsubsection{\Gls{Stibb} goes through his checklist of interventions needed to guarantee
    \Gls{CDar}'s place in the voyage}
\Gls{Stibb} goes to the mansion of an aristocrat and asks the cook to get rid of some spoiled fish.
He tells the wizards that the aristocrat will meet \Gls{CDar}'s uncle the next day, and give him the
idea of sending the young boy on a long voyage to make a man out of him. \Gls{Stibb} next makes sure
that the man in consideration for \Gls{CDar}'s spot on the voyage to the Galapagos islands declines
the offer, by telling his wife some horror stories about monsters in the open seas.

\subsection{}
\subsubsection{The wizards get back to the Disc to think about what force is counteracting them}
\Gls{Hex} warns the wizards that their attempts to safeguard the timeline are being countered by
some other malicious force, who has managed to undo the very existence of \Gls{CDar} as a
naturalist. Back at the University, \Gls{Rince} speculates that the force opposing them is so afraid
of \Gls{CDar} writing his book on evolution, that it is conspiring to make sure the voyage never
starts.

\subsubsection{\Gls{Stibb} draws a visual map of the various timelines awaiting \Gls{CDar}}
\Gls{Stibb} asks \Gls{Hex} to turn up the magical reactor to dangerous levels, so that it can run a
simulation of the multiverse with respect to \Gls{CDar}'s voyage. He has the faculty assemble in the
Great Hall, where he points out the vital points at which they would have to intervene in the voyage
to make sure \Gls{CDar} draws the right conclusions and observes the right geological evidence.

\subsubsection{\Gls{Stibb} talks to \Gls{Ridcu} about the rise of creationism}
\Gls{Stibb} rejects the \Gls{Dean}'s idea of kidnapping \Gls{CDar} and bringing him to the Disc, so
that they can give him a copy of the book on natural selection. \Gls{Stibb} talks about the
timelines in which \Gls{CDar} wrote his book on intelligent design, and how the clergy immediately
pounced on the happy compromise between natural selection, by adding on the caveat that the Creator
had given his creations some room to improve themselves over the course of their existence.

\subsubsection{\Gls{Stibb} is flummoxed by the underlying mechanism of genetic inheritance}
\Gls{Stibb} continues to have trouble with the means by which organisms pass on their
character to their offspring, which is a crucial prerequisite for natural selection. \Gls{Ridcu}
realizes how seductive the idea of intelligent design seems to someone from the Discworld, which
has its own \Gls{EGod}.

\subsection{}
\subsubsection{\Gls{Rince} accomplishes the first of his interventions, and notices the meddling
    of an Auditor}
As \Gls{Rince} watches the extended staff of the University being portaled into Roundworld by
\Gls{Hex} to resolve the obstacles in \Gls{CDar}'s path, he realizes that the most dangerous
interventions have been saved for himself. The \Gls{Lugg} joins him as he steps into the portal,
and lands on a ship moving gently through the open seas of Roundworld. He spots the faint outline of
an Auditor in the air as he unloads the ship's cannon, before jumping overboard and returning to the
Disc.

\subsubsection{\Gls{Rince} distracts an Auditor when it stops him leaving the Ronudworld}
\Gls{Rince} diverts a cloud of wasps from stinging \Gls{CDar} to death on a beach, and leaves behind
a note with the incantation to be used to travel back to the Disc. \Gls{CDar} reads the note and
is whisked off the Roundworld, just as some Auditors confront \Gls{Rince} about his meddling.
The \Gls{Lugg} sneaks up on the Auditor and swallows it, giving \Gls{Rince} the time to run from
other Auditors who were trying to merge their power to project enough force on the material plane of
Roundworld.

\subsubsection{\Gls{CDar} arrives next to \Gls{Rince} at the fountain of Unseen University}
\Gls{Rince} runs into \Gls{CDar} in the fountain outside the Great Hall of Unseen University, and
mistakes him for one of the faculty returning from their interventions in Roundworld. \Gls{CDar} is
horrified to see the \Gls{Lugg} shuffling away on its many feet, as \Gls{Rince} believes him to be
suffering from temporary amnesia from the shock of inter-dimensional travel. \Gls{Rince} starts to
notice the resemblance of young \Gls{CDar} to the image on the famous book, and drags him into the
Great Hall to meet \Gls{Ridcu}.

\subsubsection{\Gls{Ridcu} believes the \Gls{EGod} has entered Roundworld}
\Gls{CDar} tries to make sense of the magic on display in the Great Hall, and talks about an earlier
dream, where the \Gls{EGod} came to him and showed him the miracle of intelligent design.
\Gls{Ridcu} puts \Gls{CDar} in magical stasis, and asks \Gls{Stibb} to think of some way they can
flush the \Gls{EGod} out of Roundworld, before returning \Gls{CDar} to the island he came from.

\subsubsection{\Gls{Ridcu} and the council travel to Mono Island to chase away some Auditors}
\Gls{Ridcu} and the wizards portal themselves to the office of the young \Gls{CDar} on the night
that the portal to Mono Island opens in a dark corner. They use the opportunity to sneak into the
\Gls{EGod}'s island home, and deal with the Auditors assembling on the island by shooting chocolate
at them using some slings. \Gls{Ridcu} believes that the \Gls{EGod} will not visit \Gls{CDar} to
deliver his sermon on intelligent design, saving them the labour of weeding out those ideas from
the scientist's brain later.

\subsubsection{\Gls{Stibb} and \Gls{CDar} travel to Mono Island}
\Gls{Stibb} takes \Gls{CDar} to Mono Island on \Gls{Ridcu}'s orders, to meet with the \Gls{EGod} and
learn about his true nature. Once on the island, \Gls{CDar} is flabbergasted by the absurd
inventions of the \Gls{EGod}, including a tortoise on wheels and a tree that grows pencils instead
of fruit. The \Gls{EGod} greets them on the way to his mountain abode, and \Gls{CDar} recognizes the
figure as the one from his dreams.

\subsubsection{\Gls{CDar} rationalizes the wizards as constructs of his own mind trying to help
    him work through the scientific conundrum facing him}
\Gls{CDar} is horrified by the half-finished animals in the workshops of the \Gls{EGod}, and asks
to be taken back home. \Gls{Hex} retrieves \Gls{CDar} and \Gls{Stibb} to the Great Hall, where
\Gls{Ridcu} wishes to have his memory wiped before returning him to Roundworld. The wizards show
\Gls{CDar} a glimpse of the Museum of Natural History that is opened a few decades after his death
in London, and reinforce his belief that they are figments of his psyche trying to guide him to a
scientific conclusion within his dreams.