\section{Equal Rites}


\subsection{}
\subsubsection{\Gls{Billet} wishes to pass on his powers to a newborn before he dies}
A wizard named \Gls{Billet} seeks out \Gls{Gordo} the blacksmith the remote village of Bad Ass,
high up in the mountains, and asks him if he is the youngest of eight siblings, and is about to have
an eighth child of his own. The blacksmith dismisses the villagers crowding his workshop for the
warmth, and asks \Gls{Billet} if he is here to pass on his powers to the unborn son, who is highly
likely to have magical talents.

\subsubsection{\Gls{Billet} unwittingly transfers his magical powers to a baby girl}
The blacksmith tells \Gls{Billet} that his wife is in labour with the eighth child, and learns that
\Gls{Billet} has mere minutes left to live. \Gls{Billet} has the baby hold his magic staff, over
the midwife's feeble attempts to stop him. The blacksmith discovers too late that the child is a
girl, and the wizard flops over dead with \Gls{Death} waiting for his soul.

\subsubsection{\Gls{GWea} fails to destroy \Gls{Billet}'s magic staff}
\Gls{Billet} asks \Gls{Death} if he can reverse his ritual from the afterlife, after realizing his
error. The blacksmith is despondent at the idea of raising a female wizard, as \Gls{GWea} asks him
to burn the magic staff. After her attempts to hack it with an axe almost lead to \Gls{Gordo} losing
his ear, he asks her to hold off for the moment.

\subsubsection{\Gls{Eskar} grows up with her many brothers without any magic manifesting}
A few years pass, and the little baby named \Gls{Eskar} grows up without any visible signs of
magical talent, with \Gls{GWea} keeping a close eye on her. During a particularly cold winter,
\Gls{Gordo} loses his temper and hits \Gls{Eskar} out of annoyance, and faces immediate retaliation
from \Gls{Billet}'s magic staff, even though no one else sees this happen.

\subsubsection{\Gls{Eskar} reaches \Gls{GWea}'s cottage with her brothers}
\Gls{Eskar}'s mother asks her to go investigate \Gls{GWea}'s cottage, along with her brothers
\Gls{Cern} and \Gls{Gulta}. The two brothers find \Gls{Eskar} sulking in the apple tree planted over
the corpse of \Gls{Billet}, and set off from the village towards \Gls{GWea}'s hut. At the cottage,
\Gls{Eskar} decides to look in the privy for a spare key, and finds it without much trouble.

\subsubsection{\Gls{Cern} and \Gls{Gulta} decide to look for help}
\Gls{Cern} finds \Gls{GWea} lying in her bedroom on the upper floor of the cottage, and wonders if
she is dead. \Gls{Eskar} volunteers to stay back while the other two fetch some help, when they
appear terrified of defending a possible corpse from the demons that come to claim fresh souls.
\Gls{GWea}'s pet crow tries to enter the bedroom through the open window, and is shooed away by
\Gls{Cern}.

\subsubsection{\Gls{Eskar} mistakes \Gls{GWea}'s crow for a demon, and flees into the wilderness}
\Gls{Eskar} mistakes the crow for a monster trying to gain entry into the cottage through the
windows, and is terrified when the candles go out after sunset. She runs out of the cottage, and
into the snow-storm, desperate to get away from the supposed demon, just as the crow manages to
drop in through the chimney. \Gls{GWea} jumps back into her own body from that of her pet crow,
and realizes that a pack of wolves is converging on \Gls{Eskar}'s location.

\subsubsection{\Gls{Billet}'s magic staff protects \Gls{Eskar} from the pack of hungry wolves}
The cat in \Gls{Gordo}'s forge notices \Gls{Billet}'s staff take off after \Gls{Gordo} leaves with
his sons. When \Gls{GWea} reaches the clearing where the wolves have \Gls{Eskar} surrounded, she
notices the staff kick a few of them to death, and send the others running. \Gls{GWea} decides to
hide the entire affair from \Gls{Gordo}, who is waiting for her at the cottage with his sons,
surprised that she is not dead.

\subsubsection{\Gls{GWea} decides to help \Gls{Eskar} recover with one of her sleeping potions}
\Gls{GWea} struggles to light the fireplace in her cottage, and \Gls{Eskar} asks her about using
magic to light it instead. \Gls{GWea} tries to argue that her magic only extends to living things
with minds that can be manipulated, and warns \Gls{Eskar} about the unintended side-effects of
magic. Later in the night, \Gls{GWea} puts \Gls{Eskar} to sleep in her bedroom, and decides to
shift into an owl to go talk to \Gls{Billet}.

\subsubsection{\Gls{GWea} consults with \Gls{Billet} about \Gls{Eskar}'s future}
\Gls{GWea} flies to the apple tree growing on \Gls{Billet}'s corpse, and talks to his spirit
telepathically after landing on it. \Gls{Billet} suggests sending \Gls{Eskar} to Unseen University
and \Gls{GWea} disagrees, considering it impossible for a girl to pick up magic the way the Wizards
practiced it. She returns to the cottage, intent on helping \Gls{Eskar} gain control over her
violent outbursts of magic.

\subsubsection{\Gls{GWea} realizes that \Gls{Billet}'s staff is trying to protect \Gls{Eskar}}
\Gls{GWea} finds \Gls{Billet}'s staff waiting for her in the cottage, and tosses it into the
fireplace, only to be alarmed by \Gls{Eskar}'s cries of pain from upstairs. She hastily puts out
the fire, and goes to the bedroom to console \Gls{Eskar}, who is deliriously mumbling something
about fire and heat. The next morning, \Gls{Eskar} wakes up with no memories of the past day,
and explores \Gls{GWea}'s cottage for the first time.

\subsubsection{\Gls{GWea} convinces \Gls{Gordo} to let \Gls{Eskar} become her student}
\Gls{GWea} hides away the magic staff, and asks \Gls{Eskar} if she wouls like to learn witch magic.
\Gls{Eskar} is afraid of her father rejecting the idea, and \Gls{GWea} immediately goes to the
smithy to confront him. He fails to make sense of her warnings about the nature of wizard magic,
and finally agrees when he realizes the social status that would come from having a young healer and
chemist in the family.

\subsubsection{\Gls{GWea} starts to teach \Gls{Eskar} the tricks of the trade}
\Gls{GWea} spends the next few months teaching basic medicine to \Gls{Eskar}, and looks furtively
at the hidden staff when the little girl is exasperated by the wait for real magic. \Gls{Eskar}
realizes to her horror, that a large part of \Gls{GWea}'s power is the gimmick of her costume, and
the placebo effect engendered by her elaborate rituals when administering medicines.

\subsubsection{\Gls{GWea} fails to stop \Gls{Eskar} from mind-controlling an eagle}
\Gls{GWea} is impressed by how intuitively \Gls{Eskar} is able to jump into an eagle's mind, and
tries to show her the process of returning to her own body. Once \Gls{Eskar} guides the eagle
directly above their location on the ground, she ignores \Gls{GWea}'s advice against taking over
the animal's mind fully, and reaches out for complete control. \Gls{GWea} realizes too late that
\Gls{Eskar} has flown away, and takes the girl's body back to her cottage.

\subsubsection{\Gls{GWea} tries to find \Gls{Eskar}'s location}
\Gls{GWea} waits an entire day for \Gls{Eskar} to return to her cottage, and realizes that she is
likely losing control of her mind. Meanwhile, \Gls{Eskar} finds the eagle's mind slowly starting to
assert dominance, and finds it difficult to remind herself that she is a separate entity invading
it. \Gls{GWea} sets the bees in her beehives to scout for \Gls{Eskar}, and they return a few hours
later with no sightings of the eagle.

\subsubsection{\Gls{GWea} uses \Gls{Billet}'s staff to track down \Gls{Eskar}'s location}
\Gls{GWea} pleads with \Gls{Billet}'s magic staff to track down \Gls{Eskar}'s mind, and reluctantly
boards it, when it levitates to broomstick height. It takes her far into the snowy mountains, where
\Gls{Eskar}'s eagle is huddled in a cave, hiding from the cold. \Gls{GWea} bundles the eagle up
in a robe, and has the staff fly her back to the cottage, where she fails to find any sign of human
intelligence in the bird.

\subsection{}
\subsubsection{\Gls{GWea} rescues \Gls{Eskar} from the eagle's mind}
\Gls{GWea} lets the staff vent some power into her, and enters the mind of the eagle in order to
extricate \Gls{Eskar}. She works overnight and slowly manages to unravel the child's mind, and
notices \Gls{Eskar} sleeping in the bed with her mind back in its original body. When \Gls{Eskar}
wakes up, \Gls{GWea} chastises her for taking control of the eagle's body without realizing the
long-term consequences for her own mind. \Gls{Eskar} talks about dark shapes in her dreams, and
\Gls{GWea} brushes it off as figments of her imagination.

\subsubsection{\Gls{GWea} forces \Gls{Eskar} to demonstrate the magic hidden inside her}
\Gls{GWea} gives \Gls{Eskar} the magic staff, and narrates the circumstances of her birth. She
then reminds her that no woman has ever been admitted to Unseen University and trained to become a
wizard. \Gls{GWea} asks \Gls{Eskar} to light the fireplace using magic, and is surprised when the
fireball conjured by the little girl melts through the iron grill, and sinks into the ground.

\subsubsection{\Gls{Eskar} turns \Gls{Gulta} into a pig when he annoys her}
\Gls{GWea} posts a letter to Unseen University, asking them to take on \Gls{Eskar} as a student,
while asking the girl to consider traveling to Ankh-Morpork to learn how to control the terrible
power inside of her. \Gls{Eskar} turns \Gls{Gulta} into a pig, when he taunts her about the new
magic staff, and her inability to control the magic inside of her. \Gls{GWea} rushes out with
\Gls{Gordo} and his wife, when \Gls{Cern} screams in terror, and is annoyed when \Gls{Eskar} refuses
to reverse her spell.

\subsubsection{\Gls{GWea} and \Gls{Eskar} go to the nearby town}
\Gls{GWea} sets out on a cart to the nearby town, unsure of where Unseen University is located.
\Gls{Gordo} gives her a small sum of cash to see \Gls{Eskar} safely to the University, after being
impressed by the ease with which she polymorphed her brother. At the town square, \Gls{GWea} is
overwhelmed by the crowds in the market, and strolls around with \Gls{Eskar} until she spots a
witch selling herbal medicine.

\subsubsection{\Gls{Hilta} talks about the great distance to Unseen University}
\Gls{GWea} recognizes the other witch as \Gls{Hilta}, and starts gossiping about life in the remote
villages, while \Gls{Eskar} explores the strange medicines lining her stall. Eventually, \Gls{Hilta}
reveals to \Gls{GWea} that Ankh-Morpork is many weeks away by carriage, and asks them to stay the
night in her house, so that they can travel by day.

\subsubsection{\Gls{Eskar} converts a tavern's supply of liquor into milk}
\Gls{Eskar} gets lost in the thronging crowds, as \Gls{Hilta} and \Gls{GWea} head out, and
eventually finds a well-lit tavern to keep herself safe. She subconsciously converts the beer in
the tavern into goat's milk, and asks him to pour her a glass. The innkeeper \Gls{Skiller} is
alarmed by the power on display, and notices the rest of his clientele walk out in fear. He asks
\Gls{Eskar} to undo her spell, and is surprised when she tells him she didn't perform any magic to
begin with.

\subsubsection{\Gls{Eskar} turns the milk in the tavern back into high-grade liquor}
\Gls{Eskar} tries to recall \Gls{GWea}'s distillation process, and applies it to the milk using
her magical powers, to convert it into high-grade brandy. The innkeeper is stunned by the sheer
value of his store of alcohol, and invites \Gls{Eskar} to sleep the night in his finest bedroom.
Meanwhile, \Gls{Hilta} and \Gls{GWea} try to search for \Gls{Eskar}, unable to track down her mind
amidst the people crowding the market.

\subsubsection{\Gls{GWea} decides to wait for \Gls{Eskar} to catch up to them}
\Gls{GWea} recalls the magic staff's innate ability to sense danger and defend \Gls{Eskar}, leading
her to believe that the girl would find \Gls{Hilta}'s cottage eventually. She asks \Gls{Hilta} to
stop the search, and head home for the night to wait for \Gls{Eskar}. \Gls{Skiller} tries to sneak
into \Gls{Eskar}'s room to steal the staff, and it bites his hands reflexively. \Gls{Eskar}
pushes him out of the room, and breaks out of the tavern using the high window.

\subsubsection{\Gls{Eskar} accidentally becomes a stowaway on a cargo boat}
\Gls{Eskar} finds a cargo boat in the town's harbour, and goes to sleep on a heap of wool. In the
morning, she wakes up to find the boat drifting downriver with a group of other cargo boats, and
realizes she has left the town behind. The boat's owner wakes her up, and offers her some food after
realizing that she is not a threat. \Gls{GWea} figures out that \Gls{Eskar} has stowed away on one
of the boats, and heads back to \Gls{Hilta}'s house to track her using the crystal ball.

\subsubsection{\Gls{Hilta} and \Gls{GWea} see the cargo fleet in their crystal ball}
\Gls{Hilta} realizes that the crystal ball is responding well to \Gls{GWea}'s scrying, and peers
into it. She sees a bird's eye view of the Ankh river, along with the cargo fleet on which
\Gls{Eskar} is likely heading down-river. \Gls{GWea} realizes that the sparkling snowy particles are
the latent magic in the atmosphere being gathered by the magic staff, which will eventually feed
the power into \Gls{Eskar}.

\subsubsection{\Gls{Eskar} helps \Gls{Amsch} from a merchant intending to cheat him}
\Gls{Eskar} accompanies \Gls{Amsch} on his trade visits on one of the riverside settlements, and
spots a merchant trying to trade the wool for sophisticated fake gemstones. \Gls{Amsch} catches
the merchant fidgeting when \Gls{Eskar} points out the fakes, and wrangles a better deal from him.
He then takes the fakes to a local jeweller, who confirms \Gls{Eskar}'s claim.

\subsubsection{\Gls{Eskar} decides to stop traveling with the cargo fleet}
\Gls{Amsch} is impressed by \Gls{Eskar}'s instincts for identifying gemstones, leading her to
realize that questions about magic would soon be raised. She decides to stop traveling with the
cargo fleet, and bends reality in order to make the staff appear in her hands. The consequences
of this shifting of reality start to ripple out from her location, and \Gls{Eskar} nonchalantly
wanders through the central market square with the staff disguised as a broomstick.

\subsection{}
\subsubsection{\Gls{Eskar} watches \Gls{Gander} hire \Gls{Treatle} and his apprentice}
\Gls{Eskar} asks some local merchants about the trade routes leading out of the town, and realizes
that one of the caravans is supposed to head for Ankh-Morpork. She spots the leader of the caravan
\Gls{Gander} negotiating a deal with the wizard \Gls{Treatle} to act as their security escort.
\Gls{Gander} decides to include the wizard's young apprentice \Gls{Simon}, after pitying the boy's
speech impediment and general lack of guile.

\subsubsection{\Gls{GWea} asks some dwarves to help repair the broomstick gifted by \Gls{Hilta}}
\Gls{Gander} is alarmed to see \Gls{Eskar} walk away in the direction of Ankh-Morpork after he
refuses to take her on his caravan, and calls out to her. Meanwhile, \Gls{GWea} falls into a bear
trap dug by some dwarves, and is forced to wait all night for them to come dig her out. She
threatens them with curses unless they help patch up \Gls{Hilta}'s broomstick, which is the only
hope she has of catching up with \Gls{Eskar}.

\subsubsection{\Gls{Gander} is intrigued by a mysterious force defending his camp from a gnoll
    attack at night}
\Gls{Gander} is shocked to find a sneak attack by some gnolls repulsed by some mysterious force that
killed several of them before the sound of their retreat wakes up the campers. \Gls{Eskar} talks to
\Gls{Simon}, who is tasked with driving \Gls{Treatle}'s wagon while the wizard sleeps through the
morning. She has no idea about her staff having defended her against the gnolls, and learns that
\Gls{Simon} has been scouted by the wizard as a promising young talent for the University.

\subsubsection{\Gls{Treatle} insults \Gls{Eskar} by pointing out the University's boys only policy}
\Gls{Treatle} is shocked by the nine year-old girl asking him about the uses of Wizard magic, and
politely dismisses her idea that women can also become wizards. \Gls{Eskar} runs away from the
caravan after grabbing her staff, angry at \Gls{Treatle}'s dismissal of witchcraft, and his
sheer confidence in declaring her unfit for the University. She falls asleep in the hot sun, while
thinking of becoming both a wizard and witch.

\subsubsection{\Gls{Eskar} dreams about a locked castle that she cannot get into}
In her dreams, \Gls{Eskar} prepares to be invaded by the creatures from the Dungeon Dimensions yet
again, and wanders over to a large black castle, to find its gates locked shut. She dumps the power
stored in her staff at the gate, only to see it absorb the energy with ease. As she wakes up, she
hears a voice laughing from a room high up in the castle.

\subsubsection{\Gls{Eskar} burns the field of shrubs around her as a result of her dream}
\Gls{Eskar} wakes up at midnight, to find \Gls{GWea} tending to her, having sensed the firestorm
unleashed as a by-product of her dreams. \Gls{Eskar} is horrified to find the surrounding vegetation
burnt to ashes, and decides to seek out the University anyway, hoping to learn some way to
control the power growing inside her.

\subsubsection{\Gls{GWea} is shocked to see \Gls{Eskar} speeding up the old broomstick}
\Gls{GWea} tells \Gls{Eskar} that her broomstick will only work at night, as they notice it losing
altitude with the coming of dawn. \Gls{Eskar}'s fear of crashing into the ground makes her
subconsciously pump magic into the faltering broomstick, speeding it up well past the approaching
rim of sunlight. \Gls{GWea} asks \Gls{Eskar} to stop supercharging the broomstick once they get
ahead of the sunlight, and slows it down until they glide over the city of Ankh-Morpork.

\subsubsection{\Gls{GWea} leads \Gls{Eskar} to the Unseen University gates}
\Gls{GWea} lands in the poorest-looking district of the city, confident that her talents would be in
high demand there. A few days later, she is happy to be a well-respected member of the Shades, and
decides to take \Gls{Eskar} to the University. They find the gates firmly shut, and \Gls{Treatle}
comes along in his wagon after a while, amused at the sight of \Gls{Eskar}. He decides to take her
into the University to meet the Inner Council, with \Gls{GWea} deciding to go back to her makeshift
shop-font.

\subsubsection{\Gls{Eskar} goes to the admissions process with \Gls{Treatle} and \Gls{Simon}}
\Gls{Eskar} finds \Gls{Simon} in the back of the wagon, busy making notes from a thick book filled
written in a strange script. He asks her if she can read, and is shocked when she says no.
\Gls{Treatle} leads the two of them into the University, and takes them to the Great Hall, where
admissions are in progress for young boys who have completed their apprenticeships with senior
wizards. Archchancellor \Gls{Cutangle} wanders over to \Gls{Treatle}, and congratulates \Gls{Simon}
on his good work.

\subsubsection{\Gls{Simon} performs some rudimentary magic for \Gls{Cutangle}'s amusement}
\Gls{Simon} performs some impressive magic, with only \Gls{Eskar} noticing the creatures from the
Dungeon Dimensions as they try to cross into the Disc. She stops his illusion, and \Gls{Cutangle} is
pleased with the demonstration. He admits \Gls{Simon} to the University, and is annoyed when
\Gls{Eskar} asks to become a wizard. She is flustered by his dismissal, and starts to prepare a
fireball aimed at the statue of the University's founder \Gls{Albert}.

\subsubsection{\Gls{GWea} finds the mind of the Unseen University's stone foundations}
\Gls{GWea} goes to the University's staff entrance, to find \Gls{Whitlow} commandeering the laundry
staff. She is mistaken for a witch bearing news of her four dead husbands from the afterlife, and
escorted to the private office, where \Gls{Whitlow} tries to puff up her own skills in clairvoyance.
\Gls{GWea} makes a show of divining \Gls{Whitlow}'s future in some tea leaves, and accidentally runs
into the semi-sentient mind of the University itself.

\subsubsection{\Gls{Whitlow} receives a badly imagined reading of her future from \Gls{GWea}}
\Gls{Whitlow} is annoyed by \Gls{GWea}'s trance, as she is busy observing \Gls{Eskar} through the
mind of the University. She hurriedly returns to her own body, and asks \Gls{Whitlow} to hire the
next young girl who will come to her seeking a job. \Gls{Whitlow} is intrigued by the demand, but
\Gls{GWea} manages to placate her by saying that the young girl holds the key to her divinations
coming true.

\subsubsection{\Gls{GWea} distracts \Gls{Eskar} from her humiliation by outlining her new plan}
\Gls{GWea} returns to the front gate of the University, just in time to see \Gls{Eskar} run out in
tears, dismayed at her magic failing her in the Great Hall. She tells the little girl that there is
an alternate way into the University that requires no lessons or public humiliation. \Gls{Eskar} is
immediately interested, and takes up the maid's position under \Gls{Whitlow}.

\subsubsection{\Gls{Eskar} spots \Gls{Simon} giving a lecture on his theory of magic}
\Gls{Eskar} lets her staff take care of her sweeping duties by itself, and wanders into the
classrooms upstairs. She finds most of them unremarkable, with the lectures consisting solely of
words that go over her head. On one occasion, she stumbles into an empty classroom with \Gls{Simon}
giving a talk about theoretical magic to a group of senior wizards. She fails to understand most of
his jargon, but manages to agree with his idea of many parallel worlds, all existing at the same
time in order to allow all possible outcomes to happen.

\subsubsection{\Gls{Eskar} is surprised by \Gls{GWea} adapting well to life in the city}
\Gls{Eskar} spots \Gls{GWea} one day on her way back from a divination session with \Gls{Whitlow},
and is shocked to learn how well her business has been doing. \Gls{GWea} talks about taking on
another apprentice to help with brewing potions, leaving \Gls{Eskar} aghast at the prospect of being
replaced. She decides to learn how to read, and forces \Gls{Whitlow} to give her an assignment
sweeping the Library.

\subsection{}
\subsubsection{\Gls{Eskar} runs into \Gls{Simon} at the University Library}
\Gls{Eskar} offers some bananas to the \Gls{Libra} as a distraction, and wanders into the aisles of
the Library, marveling at the sheer number of books on the shelves. She notices the chains
weighing down some of the tomes, and runs into \Gls{Simon}, who points out the difficulty in
learning to read such complex magical words. He talks about a wizard who lost control of his mind
reading an ancient magical tome, and got absorbed into it, in the form of scribbles on the margins.

\subsubsection{\Gls{Eskar} and \Gls{Simon} see the Dungeon Dimension trying to leak into their
    realm}
\Gls{Eskar} spots the creatures from the Dungeon Dimensions in the periphery of her vision, aiming
to use the high concentration of magic in the Library to try and tear through the fabric between
realms. The staff knocks out \Gls{Simon} to put an end to the terror of the creatures, with several
tomes breaking out of their restraints in an effort to get away from them. The \Gls{Libra} takes
\Gls{Eskar} away from \Gls{Simon}'s body, with the girl believing she has killed him.

\subsubsection{\Gls{Eskar} and \Gls{GWea} inspect the unconscious \Gls{Simon}}
A few days later, \Gls{Eskar} manages to sneak into the hospital ward with \Gls{GWea} disguised as
nurses, to see \Gls{Cutangle} and \Gls{Treatle} mourning the possible loss of a bright mind.
\Gls{GWea} inspects \Gls{Simon}'s body, and concludes that his mind is wandering someplace else.
She chastises \Gls{Eskar} for throwing the magic staff into the Ankh river after it knocked
\Gls{Simon} out to stop the attempted invasion by the Dungeon creatures.

\subsubsection{\Gls{GWea} confronts \Gls{Cutangle} as the students watch on fascinated}
\Gls{GWea} barges into the Dinner Hall, completely disregarding the rule against ladies entering,
and deals swiftly with the guards who try to drag her away. She approaches the high table, intent
on asking \Gls{Cutangle} to undertake an expedition into the Dungeon Dimensions to try and retrieve
what remains of \Gls{Simon}'s mind.

\subsubsection{\Gls{Eskar}'s mind leaves her body for the Dungeon Dimensions when she tries to
    save \Gls{Simon}}
\Gls{Cutangle} tries to use his magic to assault \Gls{GWea}, and \Gls{Eskar} struggles to keep track
of their shifting forms. \Gls{Eskar} notices the Dungeon Dimension trying to break through again,
and tries to stop the fight. When \Gls{GWea}'s body pushes her back using magical fire, she runs
to \Gls{Simon}'s room, anxious to stop his body being possessed by a Dungeon creature. She uses
the mind of the building to force the door open against the Dungeon forces, and enters it. A while
later, the other students find her slumped on the floor, fast asleep just like \Gls{Simon}.

\subsubsection{\Gls{Eskar} finds \Gls{Simon} playing with models of many worlds}
\Gls{Eskar} wanders through the Dungeon Dimensions, until she finds the cold sandy beach from her
dreams, and spots \Gls{Simon} meditating in a ritual circle surrounded by the Creatures. She sees
geometric solids lying next to him, and recalls \Gls{GWea}'s dismissal of wizardry as the pursuit
of fancy mathematical shapes. She grabs a pyramid bearing a miniature model of the Discworld inside
it, and wonders how to return to her home realm, just as \Gls{Simon} wakes from his trance, and
speaks to her with the voice of the Creatures.

\subsubsection{\Gls{Cutangle} ends the duel with \Gls{GWea}, and rushes to \Gls{Simon}'s bed}
The Creatures take hold of \Gls{Simon}, and ask \Gls{Eskar} to give them the simulation of the
Discworld in the glass pyramid in exchange for the boy's life. Meanwhile, \Gls{Cutangle} ends his
duel with \Gls{GWea}, in awe of her stamina and worried about his impending loss if the fight were
to keep going. The two of them are led to \Gls{Simon}'s body, now being looked at by several doctors
and wizards.

\subsubsection{\Gls{Cutangle} and \Gls{GWea} set out to find \Gls{Billet}'s staff}
\Gls{Cutangle} shares his high-grade tobacco with \Gls{GWea}, and listens to the tale of her
magical inheritance. The two of them decide to look for \Gls{Billet}'s magical staff in the Ankh
river, confident that the wizards will not be able to retrieve the two minds on their own. They
find a boat in the University's jetty, and set out on the flooded Ankh river, with a rainstorm
pouring down on them.

\subsubsection{\Gls{Cutangle} and \Gls{GWea} cross the frozen sea in search of the staff}
\Gls{Cutangle} remains pessimistic about finding the staff, believing must have washed away too far
downstream. As they reach the bay, the water starts to freeze over, with the rain turning into
snowfall. \Gls{Cutangle} believes that the frigid temperatures of the Dungeon Dimensions are leaking
into the staff, which is chilling everything in its vicinity. The two of them recall their
childhood in the mountain villages, and \Gls{GWea} is surprised to know that \Gls{Cutangle} grew up
very close to her own home.

\subsubsection{\Gls{Cutangle} and \Gls{GWea} fly back to the University on the magic staff}
\Gls{Cutangle} admits he threw away the letters written by \Gls{GWea} to ask for \Gls{Eskar}'s
admission, as they find the staff floating just under the surface of the ocean. \Gls{Cutangle} uses
the last of his power to levitate it up to them, and watches \Gls{GWea} chastise it for abandoning
\Gls{Eskar} in her time of need. She then makes the staff resist the outflow of coldness, and
uses it to fly back to the University, with \Gls{Cutangle} tagging along terrified of the speed.

\subsubsection{\Gls{Treatle} watches \Gls{Cutangle} return by broomstick with \Gls{GWea}}
\Gls{Treatle} guides the students in saving the priceless portraits hanging in the University's
Great Hall, as it starts to flood with the waters of the Ankh. He wonders if the witch's lifestyle
might have been better, as the rest of the faculty argue about the best spell to fix the large hole
in the roof. \Gls{Cutangle} and \Gls{GWea} arrive by broomstick, and trudge off to the library,
where everyone is seeking shelter.

\subsubsection{\Gls{Cutangle} is forced to reckon with the ban on allowing female wizards}
\Gls{Cutangle} lays the staff next to the sleeping body of \Gls{Eskar}, and \Gls{GWea} reminds him
that he will need to declare the girl a wizard for her to be able to use its power. \Gls{Cutangle}
thinks about going down in history as the first Archchancellor ordain a female wizard, and decides
it would not be so bad after all.

\subsubsection{\Gls{Eskar} shows \Gls{Simon} the way to repulse the Creatures}
Inside the Dungeon Dimensions, \Gls{Eskar} manages to conjure the staff in its ethereal form, and
works out a way to weaken the Creatures. She hands the staff over to \Gls{Simon}, and asks him to
suppress the magic inside him. She reasons that the Creatures feed off of magic, and that any
attempt to use magic offensively would only make them stronger.

\subsubsection{\Gls{Eskar} and \Gls{Simon} return to their bodies}
\Gls{Simon} manages to use the staff to find a way back into the real world, and arrives along with
\Gls{Eskar} into the bodies lying in the Library's reading room. The staff dumps all of its power
into the surrounding city in a flash of octarine, and goes inert. \Gls{Cutangle} picks it up, and
notices the absence of shifting runes on it, as \Gls{GWea} welcomes \Gls{Eskar} back with her
wizard hat.

\subsubsection{\Gls{Cutangle} offers \Gls{GWea} a faculty position at the University}
\Gls{Cutangle} offers \Gls{GWea} a teaching position at the University, and offers her the chance
to commute from her mountain home to the city using a modern broomstick. He also promises to admit
some girls in a pilot program to reform the University's archaic laws, and hopes to see her more
often.