\section{(Faust) Eric}


\subsection{}
\subsubsection{\Gls{Death} senses someone in an alternate dimension running past his cottage}
In his realm, \Gls{Death} is disturbed from his beekeeping routine, by a strong gust of air blowing
through his cottage, and the faint sounds of someone running away from trouble. Meanwhile, the
\Gls{Libra} is startled in his makeshift hammock withing the ice chamber of the Library, as a
disembodied voice runs past him, to disappear into the walls.

\subsubsection{The disembodied voice runs through many places in Ankh-Morpork}
As the sun sets on a blistering summer day in Ankh-Morpork, more citizens hear the disembodied voice
run past them, and notice the magical after-effects left in its wake. The new Archchancellor of
Unseen University meets with his inner council at night, and decides not to take the haunting
seriously. The council members decide to let him rest for the night, and prepare to summon
\Gls{Death} for answers.

\subsubsection{\Gls{Death} tells the inner council of wizards that the ghostly voice is \Gls{Rince}}
The inner council of the University summon \Gls{Death}, who tells them that \Gls{Rince} is trying
to escape the Dungeon Dimensions, and is the cause of the voices they hear. The council members,
anxious that he might refute their alibis during the reign of the sourceror \Gls{Coin}, try to
brush off the escape as near impossible.

\subsubsection{\Gls{Rince} is summoned into the Discworld by a ritual}
\Gls{Rince} escapes the Dungeon Dimensions, as someone summons him to the Discworld using the ritual
used to conjure and bind demons to one's will. He tries to argue that he is human, and cannot be
banished back to the Dungeon Dimensions, but the summoner is adamant about the three wishes he
is now contractually obligated to receive.

\subsubsection{\Gls{Rince} realizes that \Gls{Eric} is a child pretending to be a wizened old man}
\Gls{Rince} learns that he is in Pseudopolis, and that \Gls{Eric} has summoned him by accident,
while looking for a demon that grants wishes. \Gls{Rince} recognizes the demonologist as a little
boy wearing an old man's disguise, just as his mother calls out from downstairs for dinner. After
\Gls{Eric} goes downstairs, leaving \Gls{Rince} confined to his room, the stuffed parrot speaks up,
revealing that \Gls{Eric}'s grandfather had been a prodigious demonologist long ago.

\subsubsection{\Gls{Rince} learns about the rules of demonology}
The \Gls{Parrot} reminds \Gls{Rince} that the rules binding demons would apply to him since he
emerged onto the Discworld using a demonic portal. \Gls{Rince} gets electrocuted by magic when he
tries to escape through a window, and settles down to wait for \Gls{Eric}'s return. Meanwhile, in
the city of Pandemonium, at the center of the Demon realm, Demon King \Gls{Astf} receives the news
that someone else went through \Gls{Eric}'s portal, causing it to close automatically.

\subsubsection{\Gls{Astf} determines the identity of the interloper}
\Gls{Astf} learns that \Gls{Eric}, a self-centered savant he had long hoped to seduce into the
demon world, using \Gls{Vassen} as his messenger, had successfully summoned someone else using his
ritual. In his private chamber, \Gls{Astf} uses his CCTV mirror to watch the events in \Gls{Eric}'s
room, and learns that the interloper's name is \Gls{Rince}. He bemoans the lack of a formal census
in the Demon world, so that he might cross-verify \Gls{Rince}'s identity.

\subsubsection{\Gls{Rince} is reunited with the \Gls{Lugg} in \Gls{Eric}'s room}
When the \Gls{Lugg} materializes in \Gls{Eric}'s room, the boy loses interest in setting \Gls{Rince}
free, and goes back to his earlier demands of world domination. \Gls{Rince} is shocked to find that
he can summon a miniature model of the Disc with a snap of his fingers, and is annoyed to see
\Gls{Eric} demand tribute from the kingdoms of the Disc.

\subsubsection{\Gls{Rince} teleports \Gls{Eric} and the party to Klatch}
\Gls{Rince} next teleports himself and \Gls{Eric} into the dense jungles of Klatch, where they
trek for a while, until they find some buildings of the Tezuman kingdom. \Gls{Rince} is surprised
when the Tezuman warriors bow down to \Gls{Eric}, as the \Gls{Parrot} expresses its satisfaction at
his demonic capabilities.

\subsubsection{\Gls{Eric} is celebrated by the Tezumen with a grand festival in his name}
The Tezumen procession brings \Gls{Eric} and \Gls{Rince} to one of the stone pyramids, with the
common-folk throwing coins and flowers at them, as if to celebrate a hero. \Gls{Rince} spots the
treasure chests lined up at the entrance to the pyramid, where Tezuman royalty await their arrival.
He starts to believe that he is indeed capable of granting \Gls{Eric}'s wishes, after all the time
spent in the Dungeon Dimensions.

\subsection{}
\subsubsection{\Gls{Rince} runs into a prisoner condemned to death as a human sacrifice}
\Gls{Rince} wanders away from the festivities, and finds a hollow pyramid, holding a large statue
of \Gls{Quezo}, the patron God of the Tezuman kingdom. A voice from underground begs him to be set
free, and tells him that it is scheduled to be flayed alive as a sacrifice to \Gls{Quezo}. The
\Gls{Parrot}, riding \Gls{Rince}'s shoulder, agrees with the idea to rescue the prisoner, even as
\Gls{Rince} is not sure about escaping the city with him.

\subsubsection{\Gls{Astf} makes \Gls{Quezo} repent for his mistakes}
\Gls{Astf} asks \Gls{Quezo} to be brough to him, and berates him for infesting the minds of the
Tezumen priests with a religion based on human sacrifice. He bemoans the belligerence seeping into
Tezuman culture, making them enter pointless feuds with every neighbouring kingdom in the jungles of
Klatch. He asks \Gls{Quezo} to manifest physically in the Tezuman capital, and tell them to pivot
their civilization to a path of progress.

\subsubsection{\Gls{Rince} reads the hieroglyphs predicting his death in the pyramid}
The prisoner in the pyramid introduces himself as \Gls{Ponce}, and asks \Gls{Rince} to study the
hieroglyps lining its inner walls. \Gls{Rince} spots the likenesses of \Gls{Eric} and himself, both
being subjected to ritualized torture, and decides to run from the city. He emerges from the
pyramid's back door, and is surrounded by Tezuman soldiers pointing crude spears at hibernation

\subsubsection{\Gls{Quezo} is accidentally killed by the \Gls{Lugg}}.
\Gls{Rince}, \Gls{Ponce} and \Gls{Eric} are all bound at the top of the flattened pyramid, ready to
be offered to \Gls{Quezo} as sacrifice. The \Gls{Lugg} bulldozes its way through the jungle, heading
for \Gls{Rince}, just as \Gls{Quezo} chooses to manifest at the ritual site. Being a six inch tall
imp, \Gls{Quezo} gets bulldozed by the \Gls{Lugg} as it runs over him, leading to the Tezumen
placing it at the center of their faith, and freeing the prisoners condemned to death.

\subsubsection{\Gls{Rince} and his companions leave the Tezuman kingdom}
\Gls{Rince} gifts the \Gls{Parrot} to \Gls{Ponce}, calling it a valuable asset in his search for
the Fonutain of Youth, as they exit the Tezuman city and make it to the cover of the jungle.
Meanwhile, the priestly class of Tezuma decide to replace \Gls{Quezo} with a new God, instead of
letting the absurdity of their religious rituals become common knowledge.

\subsubsection{\Gls{Rince} teleports himself and \Gls{Eric} into a huge wooden horse}
\Gls{Astf} is relieved by \Gls{Quezo} being condemned to several centuries of hell before his next
rebirth, and gets to work on his CCTV mirror, examining recent events. When \Gls{Rince} snaps his
fingers to grant \Gls{Eric}'s second wish, to get the most beautiful woman in the world, they are
transported into a huge wooden horse, and captured the moment they use a rope ladder to descend to
the ground.

\subsubsection{\Gls{Eric} and \Gls{Rince} are trapped in Tsort during the war for \Gls{Elenor}}
\Gls{Eric} realizes that he has been transported to Tsort thousands of years ago, during the war
to retrieve \Gls{Elenor}, famed to be the most beautiful woman in the realm. The guard captain
leaves them imprisoned in a room, and leaves with his men to investigate a disturbance at the city
gates. The \Gls{Lugg} smashes the city gates, and eats a squad of soldiers sent out to open it,
as \Gls{Rince} convinces the soldier guarding them to join his comrades in their valiant defense of
the city.

\subsubsection{\Gls{Rince} initiates the battle for \Gls{Elenor}}
\Gls{Rince} and \Gls{Eric}, running through the streets of the city, find an abandoned gate.
\Gls{Rince} unlocks it, hoping to find a way out, and accidentally lets in the sieging army instead.
He is exasperated by \Gls{Eric}'s single-mindedness in meeting \Gls{Elenor}, completely oblivious
to the bloody battle that is imminent.

\subsection{}
\subsubsection{\Gls{Rince} watches the fight happen in parallel to civilian life in the city}
As the battle between the Ephebians and Tsortians rages on in the streets, civilian life continues
unperturbed. In a bar, \Gls{Rince} learns that a civilian is being hunted for the crime of letting
the invaders in through the city gates, and is relieved when there is no description out for the
fugitive. A Tsortian soldier finds him in the bar, and takes him into custody.

\subsubsection{\Gls{Rince} and \Gls{Eric} meet the Ephebian general}
At the Ephebian command post, one of the generals casually feeds the \Gls{Lugg} some bread, as
\Gls{Rince} and \Gls{Eric} are escorted in. The other nobles choose to ignore them, as the general
asks \Gls{Rince} where he is from. \Gls{Rince} is surprised to see no surprise on the general's face
when he reveals that he is from the future, and that the \Gls{Lugg} is bound to him by magic.

\subsubsection{\Gls{Rince}, \Gls{Eric} and the \Gls{Lugg} follow \Gls{Laveo} through tunnel}
\Gls{Laveo}, the captain who was the brain behind the wooden horse, invites \Gls{Rince} and
\Gls{Eric} to an expedition into the Tsortian citadel, by way of a secret underground tunnel their
spies had discovered. The squad accompanying them praise \Gls{Laveo} for eschewing the pomp and show
attached to traditional military strategy, in favour of getting results by any means necessary.

\subsubsection{\Gls{Eric} sees how different \Gls{Elenor} is from the historical descriptions}
Inside the citadel, \Gls{Laveo} emerges into a secret chamber, where \Gls{Elenor} is cowering in
fear, with several children clinging to her. \Gls{Eric} recalls the legends of \Gls{Laveo}, hailed
as a hero in the Classics, and asks \Gls{Rince} if they should warn him of the misfortunes waiting
for him in the future. He is then dismayed to see \Gls{Elenor} not match the descriptions from the
history books, as the Ephebian sergeant explains literary metaphor.

\subsubsection{\Gls{Elenor} wishes to stay back in Tsort with the King}
\Gls{Elenor} tells \Gls{Laveo} that she has grown to like the Tsortian King, and that she does not
care to leave her life behind to return to Ephebe. \Gls{Laveo} laments the years he has wasted
sieging Tsort, and wonders if his soldiers will burn the city down, when they hear the news of their
campaign being futile.

\subsubsection{\Gls{Laveo} bids farewell to \Gls{Rince}}
The \Gls{Lugg} rescues the civilians stuck inside the palace, as the city is burned down, with the
two armies declaring a truce. \Gls{Laveo} asks \Gls{Rince} if he will make it home in one piece,
and \Gls{Rince} decides not to tell him about the tribulations he is to face along the way. After
\Gls{Laveo} sets sail on his ship, \Gls{Eric} speculates that he is \Gls{Rince}'s distant ancestor.

\subsubsection{\Gls{Rince} ends up in outer space with \Gls{Eric}}
Meanwhile, \Gls{Astf}, from his realm outside space and time, notices that \Gls{Eric} is becoming
more personable, and thinks about some means of breaking the boy's heart. \Gls{Rince} snaps his
fingers again, teleporting himself and \Gls{Eric} to the vacuum of space. \Gls{Astf} loses track
of the two of them, and guesses they have to be in one of two possible places he cannot observe in
his CCTV mirror.

\subsubsection{\Gls{Astf} talks to \Gls{Death} at the end of the Universe}
A mysterious man accosts \Gls{Rince}, offering him some food, as \Gls{Eric} notices the absence of
stars, and of any physical sensation in his body. The man tells them that they are in the time
before creation, even before light is summoned into existence. Meanwhile, \Gls{Astf} runs into
\Gls{Death} at the end of the Universe, and learns that \Gls{Rince} is a mere human, accidentally
trapped in the Dungeon Dimensions.

\subsubsection{\Gls{Rince} sees the \Gls{Creat} bring the Discworld into existence}
\Gls{Death} is pleased to see the cycle of the Universe start again, when a paperclip and a button
pop into existence from nothingness. At the start of the universe, \Gls{Rince} learns that the
little man is a \Gls{Creat}, tasked with the job of designing and creating universes. The man asks
them to remain silent, as the universe starts to take shape from raw matter and energy.

\subsubsection{\Gls{Rince} and \Gls{Eric} are left at the beginning of the Discworld}
The Discworld's gravity starts to pull \Gls{Rince} and \Gls{Eric}, with the creator struggling to
think of a way to save them. Eventually, he tinkers with their positions and velocities to leave
them on a beach, before vanishing. \Gls{Rince} realizes that \Gls{Eric}'s third wish of living
forever has been interpreted to mean a life that stretches the entire timespan of the Discworld. He
is alarmed by the prospect of hanging around in the Disc for millennia before life evolves, and
sentience finally emerges.

\subsubsection{\Gls{Rince} and \Gls{Eric} accidentally end up at the gates of Hell}
\Gls{Rince} thinks about getting \Gls{Eric} to draw a magic circle to take them back to the present,
and tosses his half-eaten sandwich on the beach. \Gls{Astf} materializes some time later to find
his quarry gone, and notices the bacteria in the sandwich kickstarting life on the Disc.
\Gls{Eric}'s portal takes the two of them to the gates of Hell, where an abomination welcomes them
by reciting a customer-service script.

\subsubsection{\Gls{Rince} hoodwinks \Gls{Urgle}}
The demon, who has a badge identifying him as \Gls{Urgle}, the guardian of the Gates of Hell,
bemoans the changes instituted by his new master, including a change in decor, and the dispassionate
tone adopted in welcoming new entrants. \Gls{Rince} commiserates with the demon at the gate,
who despises the changes being pushed on the workers, and manages to march into Hell, before
\Gls{Urgle} can fully process the fact that the two newcomers are not dead.

\subsubsection{\Gls{Rince} and \Gls{Eric} explore the revamped depths of Hell}
Inside Hell, \Gls{Rince} finds the demons subjecting souls to eternal boredom, designed to numb
their minds in a way that physical torture never could. \Gls{Rince} thinks back to his own life,
and of how he valued boredom, simply becuase it meant he was out of trouble. They hear \Gls{Astf}
roaring in anger, and decide to run, until they bump into \Gls{Ponce} and the \Gls{Parrot}.

\subsubsection{\Gls{Astf} gets his underlings to search for \Gls{Rince} and \Gls{Eric}}
\Gls{Astf} asks his vassals to hunt down the intruders, alarmed at the prospect of live humans
making it to Hell. \Gls{Vassen} reminds him that it is demonic culture to foment rebellion and
mutiny against any authority figures, as he reluctantly complies with the orders. \Gls{Urgle} is
condemned to disassembly in the lowers circle of Hell for his crime of letting \Gls{Rince} in.

\subsubsection{\Gls{Rince} reunites with \Gls{Ponce} and the \Gls{Parrot}}
\Gls{Rince} learns that \Gls{Ponce} died from drinking the water at the fountain of youth, since he
did not boil it first to make it safe. He is pleased to see the \Gls{Parrot} also condemned to Hell,
as he leads the party away from the demons trying to hunt them down. Meanwhile, the gates of Hell
open up to allow the \Gls{Lugg} to pass through, seeing the certainty with which they were about to
be torn down if it was forced to charge in.

\subsubsection{\Gls{Rince} learns from \Gls{Laveo} that a staircase leads out of Hell}
\Gls{Rince} then finds \Gls{Laveo}, who points out a staircase leading out of Hell at the opposite
end of the circle of Hades. The \Gls{Lugg} gets on the infinite treadmill that \Gls{Rince} and his
party are on, and runs so fast that it breaks off its handles, and starts to roll through Hades
like a bulldozer, crushing any demons caught in its path.

\subsubsection{\Gls{Vassen} plans to undo the changes wrought by \Gls{Astf}}
\Gls{Vassen} convinces the other senior demons to buy into his plan to usurp \Gls{Astf}'s throne,
as he thinks back to how useful \Gls{Rince} has been as a distraction. He laughs at \Gls{Rince}'s
naivete in believing that he had granted \Gls{Eric}'s three wishes using some magic of his own, and
is satisfied with his own plan to use \Gls{Rince} as an unwilling puppet.

\subsubsection{\Gls{Astf} accepts a promotion to an emeritus position with no impact on Hell}
When \Gls{Astf} captures \Gls{Rince} and \Gls{Eric}, he finds the great hall decorated in his
honour, with \Gls{Vassen} waiting to inform him of his promotion. He is overjoyed at the idea of
spending the next few eons drawing up elaborate plans for the demon world, and does not realize that
he is being trapped in a never-ending treadmill designed to keep him busy forever. As the demons
celebrate the return to the old ways of Hell, \Gls{Rince} decides to make a run for it.

\subsubsection{\Gls{Rince} and \Gls{Eric} emerge into the Discworld from Hell}
\Gls{Vassen} decides to let \Gls{Rince} and \Gls{Eric} escape, in exchange for their help in
ousting \Gls{Astf}. Meanwhile, the demons of hell are happy to get back to the old ways of torture
and eternal pain, leaving \Gls{Astf} stuck in his chamber of eternal paperwork, delighted to start
the greatest task of organization in the universe.