\section{Feet of Clay}


\subsection{}
\subsubsection{A golem is sold to a factory owner in Ankh-Morpork for dirt cheap prices}
A mysterious golem sells one of its newer model brethren to a factory owner, one misty night in
Ankh-Morpork. It seems eager to make the sale, by aggressively lowering the price till the factory
owner finds the deal irresistible, and donates the money to a nearby beggar afterward.

\subsubsection{\Gls{Tubel} bleeds out on the floor of his church}
Father \Gls{Tubel} lays dying in his church, with a precious book torn in half laying in front of
him. A mysterious figure walks in to watch him bleed out, as it picks up the papers strewn all
over the floor.

\subsubsection{\Gls{Vimes} goes to meet the novice assassin who missed the latest attempt on his
    life}
\Gls{Vimes} shaves his stubble in the morning, just as another assassination attempt against him
fails. He manages to duck out of the way of a crossbow bolt, that shatters his mirror, and asks
\Gls{Willi} to send a message to the Assassins' Guild about the latest failure. He goes to the
dragon pen, where the novice assassin is caught between the dragons on his way out.

\subsubsection{\Gls{Vimes} allows the assassin who failed to kill him to run away}
\Gls{Vimes} gives the novice a fair chance to escape the swamp dragons, and sees him run straight
into the estate pond, desperate to put out the fires in his clothing. \Gls{Willi} reminds him about
his engagements for the day, and hands him the expensive crossbow that his wife \Gls{Ramkin} gifted
him at their wedding.

\subsubsection{\Gls{Carrot} and \Gls{Angua} observe a heist in progress}
\Gls{Carrot} writes home about the expansion of the City Watch, including the undercover division
that \Gls{Vimes} has newly instituted. He stakes out a nearby cafe, where the owner \Gls{Gimlet}
is eager to serve him all the food he needs. \Gls{Angua}, morphed into her hound form, sits by his
side, carefully observing the heist underway at a nearby bakery.

\subsubsection{\Gls{Hopkin} is bludgeoned to death using some dwarf bread}
\Gls{Hopkin}, a master baker and curator of the Dwarf Bread Museum, tries to argue with \Gls{Death}
about the nature of his murder. He is beaten to death with a loaf of dwarf bread, and refuses to
recognize the reality of his death, until his spirit gradually begins to fade away from Discworld.

\subsubsection{\Gls{Vimes} talks to \Gls{CheeryL} at the Alchemists' Guild}
\Gls{Vimes} reaches the main Watch House at Pseudopolis Yard, and learns from \Gls{Colon} that a
strange murder has been reported by Constable \Gls{Visit}, at the house of some priest. He proceeds
to his office, where a dwarf named \Gls{CheeryL} greets him with news about the Alchemists' Guild.
He tells \Gls{Vimes} that his failed experiment blew up the Guild Council, making him lose his
membership.

\subsubsection{\Gls{CheeryL} joins the Watch as the first forensic officer}
\Gls{CheeryL} is intrigued to see no hint of laughter at the mention of his name, as \Gls{Detri}
arrives with news of a drug dealer being killed by some unnamed troll Watchman. \Gls{Vimes}
realizes that \Gls{Detri} broke the rules of policing to kill the troll drug dealer, and lets it
go for the good of the city. \Gls{CheeryL} is assigned to the forensic division as a Sergeant, and
sent to train under \Gls{Detri} for a month.

\subsubsection{\Gls{Detri} introduces the Watch House to \Gls{CheeryL}}
\Gls{Detri} shows \Gls{CheeryL} around the Watch House, and shows him a toilet in disuse, that is
to be the alchemy station. He talks about an addictive drug doing the rounds in the troll enclave,
and of the special mission given to him to track down its source within the city. Meanwhile,
\Gls{Carrot} and \Gls{Angua} apprehend the gang of three trying to make their getaway from the
bakery.

\subsubsection{The factory owner who purchased the golem fears for his life}
The factory owner who bought the new golem, visits some other person, talking about it escaping his
compound and possibly murdering \Gls{Tubel}. The other man reminds him that the golem is making him
a handsome profit, and asks him to look the other way with regard to the drugs being cooked in his
premises.

\subsubsection{\Gls{Vimes} goes to the Heralds' office regarding his coat of arms}
\Gls{Vimes} arrives at the Herald shop, and finds a menagerie of exotic animals inside, being made
to pose for one of the workers to paint on canvas. He finds another man, with arms full of scrolls,
and tells him that his wife \Gls{Ramkin} had made the appointment. He rejects the idea of using
weasels for his coat of arms, just as a new undead man walks into the Heralds' office.

\subsubsection{\Gls{Carrot} gets \Gls{Ironc} to pay his taxes}
\Gls{Carrot} negotiates with the three thieves, getting them to drop their weapons, just as
\Gls{Ironc}, the owner of the bakery, storms out of his shop with some heavily armed dwarves.
\Gls{Carrot} asks the dwarves to escort the burglars to the Thieves' Guild, for the crime of robbing
without a license. \Gls{Ironc} is crushed by the prospect of \Gls{Carrot} visiting him later, with
income tax forms meant to entitle him to the Watch's continued protection.

\subsubsection{\Gls{Vimes} meets the vampire \Gls{DragonK}}
Inside the Heralds' office, the undead voice asks \Gls{Vimes} to enter the sanctum, and identifies
itself as \Gls{DragonK}, a vampire several centuries old. \Gls{DragonK} talks about \Gls{Stonef},
a direct ancestor to \Gls{Vimes}, executing the last king of Ankh-Morpork in public, and thereby
disqualifying any successor from holding a family crest.

\subsubsection{\Gls{DragonK} talks about the royal heritage of \Gls{Nobby}}
\Gls{DragonK} explains that the Heralds have become nothing more than fiction authors, for
businessmen fancying themselves a coat of arms and a heraldic slogan, to try and make secure their
place amongst the real aristocrats. He is alarmed to hear that \Gls{Nobby} is a royal scion, and
that he is eligible for the title of the Earl of Ankh, provided he can prove his lineage.

\subsubsection{\Gls{Carrot} and \Gls{Angua} find the corpse of \Gls{Hopkin}}
\Gls{Carrot} takes \Gls{Angua} to the Dwarf Bread Museum, to show her a piece of historically
important bread that was used in an old battle between the trolls and dwarves. \Gls{Angua} smells
fresh blood, and finds the curator \Gls{Hopkin} murdered in his office, with the loaf lying beside
him.

\subsubsection{\Gls{DragonK} looks at the documents outlining the lineage of \Gls{Carrot}}
\Gls{DragonK} takes out a tome with the family trees of \Gls{Carrot} and \Gls{Angua} drawn in
detail. He then sets it aside, to look at a second tome with the partially filled family tree of
\Gls{Nobby}. He muses on the unpredictability of human minds, and of how small nudges often led to
a different man being crowned king.

\subsubsection{\Gls{Vimes} and \Gls{Detri} survey the scene of \Gls{Tubel}'s death}
\Gls{Vimes} visits the home of \Gls{Tubel} with \Gls{Detri}, and learns from \Gls{Visit} that the
corpse had a scroll of paper stuck in its mouth, with scribbles in some obscure Klatchian script.
He finds some white clay next to the corpse, and on the window sill leading to a steep drop onto the
river Ankh. \Gls{CheeryL} arrives with his alchemist kit, and is flummoxed when \Gls{Vimes} leaves
without telling him what to look for at the crime scene.

\subsubsection{\Gls{Angua} finds the smell of clay in the \Gls{Hopkin}'s oven}
\Gls{Angua} morphs into a wolf to check the scents lingering in the museum, and reports no living
things visiting the place in the last few days. When she morphs back, she spots an oven in the back
room, from which a strong smell of clay seems to dominate the other scents.

\subsubsection{\Gls{CheeryL} examines the scene of \Gls{Tubel}'s murder for material evidence}
\Gls{Vimes} is late for his meeting with \Gls{Vetina} at the palace, as he fumbles with the personal
assistant Imp gifted to him by \Gls{Ramkin}, as an upgrade to his humble notebook. Meanwhile,
\Gls{CheeryL} gets the imp in his iconograph to paint a picture of \Gls{Tubel}'s open eye, focusing
on his pupil. He surveys the corpse for fragments of evidence, and collects the wax under its
fingertips, just in time for another constable to summon him to the palace.

\subsubsection{\Gls{Vimes} finds \Gls{Vetina} close to unconsiousness at the palace}
\Gls{Vimes} finds \Gls{Vetina} struggling to remain seated on his chair, with his skin pallid as if
poisoned. He lays the patrician down on his bed, and calls for \Gls{Colon} to come to the palace
with his uniform and service weapons. \Gls{Colon} asks if \Gls{Vetina} is dead, as he sets about
enforcing a cordon around the palace to keep curious citizens from wandering in.

\subsubsection{\Gls{Vimes} tries to take charge of the palace security}
\Gls{Vimes} recalls the hostility for \Gls{Vetina} in the minds of every Guild, including the
Doctors, and asks for the pre-eminent veterinarian \Gls{Doughn} to be brought in to treat him. A
while later, \Gls{Vimes} comes down to the great hall, and is beset by Guildmasters pestering him
for the latest news on \Gls{Vetina}'s health.

\subsubsection{\Gls{Vimes} tells the city council that \Gls{Vetina} is ill}
\Gls{Vimes} tells the Guildmasters gathered in the great hall, that they cannot see \Gls{Vetina}
in his chamber, on the orders of \Gls{Doughn}, who is busy examining him. \Gls{Colon} reminds him
that \Gls{Nobby} is still on leave, on the excuse of family business, and that \Gls{Angua} has the
day off with \Gls{Carrot}.

\subsubsection{\Gls{CheeryL} suspects arsenic poisoning in \Gls{Vetina}'s room}
\Gls{Doughn} decides to make one of his horse medications for \Gls{Vetina}, and leaves the palace.
\Gls{CheeryL} arrives some time later, and guesses that the poison might have been arsenic. He
suspects the carpet and bedsheets of being dosed with trace quantities of the poison, and asks for
fresh replacements to be brought into \Gls{Vetina}'s chamber.

\subsubsection{\Gls{Colon} suggests the idea of a deputy Patrician for the time being}
\Gls{Colon} tries to suggest to \Gls{Vimes} that he take up the position of Patrician, at least
temporarily until \Gls{Vetina} recovers. \Gls{Vimes} is horrified to bear the brunt of every single
Guildmaster in the city, eager to make sure no rival guild gained the slightest advantage in the
balance of power. \Gls{Colon} then tells him that \Gls{Nobby} is back, and on his way to the palace.

\subsection{}
\subsubsection{\Gls{Vimes} learns about \Gls{Nobby} playing a role in the civil war re-enactment}
\Gls{Vimes} thinks about the persistence of social hierarchies as ideas within Ankh-Morpork, long
after the monarchy was torn down. \Gls{Nobby} walks in, expecting to be chastised, and is
surprised when \Gls{Vimes} talks about his bloodline. \Gls{Nobby} reveals his role in the coming
centenary celebrations as the King in the re-enactment of \Gls{Stonef} and his civil war.

\subsubsection{\Gls{Vimes} thinks about possible enemies of \Gls{Vetina}}
\Gls{Nobby} shows the faded gold ring his father left him, prompting \Gls{Vimes} to tell him about
the Heralds' office, and of how he should also pay them a visit. After \Gls{Nobby} leaves,
\Gls{Vimes} thinks about the few people in the city who might profit directly from the death of
\Gls{Vetina}, and realizes that he is near the top of the list, along with \Gls{Carrot}.

\subsubsection{\Gls{Vimes} gives new orders to \Gls{CheeryL}, \Gls{Angua} and \Gls{Carrot}}
\Gls{Vimes} lets \Gls{CheeryL} enter the Oblong office next, and learns about the murder of
Father \Gls{Tubel}. He sees the two dots glowing red in the zoomed iconograph of the priest's eyes,
as \Gls{CheeryL} talks about the folk myth about the last thing a dead man sees being imprinted
on his eyes. A while later, \Gls{Angua} and \Gls{Carrot} also arrive with news of \Gls{Hopkin}'s
murder. \Gls{Vimes} sends \Gls{Carrot} away to the Watch headquarters to keep him away from the
palace, in case \Gls{Vetina}'s condition worsens.

\subsubsection{\Gls{Angua} talks to \Gls{CheeryL} about the choices available to female dwarves}
\Gls{Angua} works out the fact that \Gls{CheeryL} is a female dwarf, and asks her why she chooses to
keep her gender private. \Gls{CheeryL} replies that she is not interested in the stereotypical
jobs open to male dwarves, and was originally interested in being a seamstress. \Gls{Angua} sniffs
one of the evidence envelopes from \Gls{Tubel}'s home, sensing a match to the clay she found on
the floor of the Dwarf Bread Museum.

\subsubsection{\Gls{Nobby} is given an expensive gift by the Heralds once they verify his heritage}
\Gls{Nobby} shows up at the Heralds' office, and is let in reluctantly. Once they figure out his
true heritage, they offer him a fancy pair of boots, and lament his lowly station in the Watch as
he walks away unsteadily. \Gls{Angua} and \Gls{CheeryL} travel to the pottery shop run by
\Gls{Igneous}, notorious fence and smuggler in the troll underworld.

\subsubsection{\Gls{Igneous} examines the clay sample shown by \Gls{Angua}}
\Gls{Igneous} examines the clay sample brought by \Gls{Angua}, and informs her that it is the kind
of low quality recycled pottery-mulch, that is abundantly available in any workshop. \Gls{Igneous}
then tells them about the increased security in his warehouse, after a large consignment of the
cheap clay was stolen a few months ago.

\subsubsection{\Gls{Angua} takes \Gls{CheeryL} to a shady underworld bar}
\Gls{Angua} speculates that the suspect tried to use the bakery in the Dwarf Bread Museum to bake
the stolen clay, and \Gls{CheeryL} immediately points out the fact that such an oven would not
have yielded good results. She takes \Gls{CheeryL} to a seedy black-market tavern, where the barman
\Gls{Igor} is exasperated by her questions.

\subsubsection{\Gls{Angua} visits \Gls{Igor}'s bar for the supernatural with \Gls{CheeryL}}
\Gls{Angua} tells \Gls{CheeryL} that \Gls{Igor}'s bar is a hangout for nonhumans to come be
themselves for a while, away from the prying eyes of the human citizens and their bigotry.
\Gls{CheeryL} is relieved not to be at a dwarf tavern, as \Gls{Angua} describes the next target for
her inquiry. On their way out of the tavern, \Gls{CheeryL} recounts the werewolves of Uberwald
terrorizing her dwarf clan, and eating one of her cousins.

\subsubsection{\Gls{Vimes} learns about the writing on the scroll of paper stuffed into
    \Gls{Tubel}'s mouth}
\Gls{Vimes} sees \Gls{Visit} arguing about religion with someone in the office, and asks him for
the translation of the glyphs in \Gls{Tubel}'s mouth. \Gls{Visit} says they are commandments handed
down from some forgotten God, to the people he fashioned out of clay, asking them not to kill, not
to be lazy and so on.

\subsubsection{\Gls{Angua} and \Gls{CheeryL} visit \Gls{GSock}'s butcher shop}
\Gls{Vimes} stops \Gls{Visit} when he starts taking out the latest pamphlets about his evangelical
faith, and asks him to go inform \Gls{Carrot} about his findings. At \Gls{GSock}'s butcher shop,
\Gls{Angua} tries to resist the smell of fresh meat, as \Gls{CheeryL} shows her badge, hoping to
be taken seriously as a member of the Watch.

\subsubsection{\Gls{Angua} and \Gls{CheeryL} interrogate \Gls{Dorfl}}
\Gls{Angua} sniffs some rat meat, and comments on it, as \Gls{GSock} is busy setting up his sausage
production line. She asks to speak with the golem \Gls{Dorfl}, employed in his abattoir. The golem
tells by writing on its slate, that it was working continuously for the past few days in the
slaughterhouse, and expresses sorrow at the death of \Gls{Tubel}. \Gls{CheeryL} likens the use of
golems to slavery, and is horrified at how easily \Gls{Angua} rationalizes it as a complex machine.

\subsubsection{\Gls{Dorfl} asks for time off for a religious ritual}
\Gls{GSock} is exasperated to see \Gls{Dorfl} ask for time off, and recalls the previous owner
telling him about the periodic breaks they needed to visit their temple, and renew the instructions
in their head that animated them. He lets it go, while asking it to return as soon as possible to
the slaughterhouse. Meanwhile, the conspirators who poisoned \Gls{Vetina} sit at a table and discuss
the value of lowering the dosage so that the Patrician is only incapacitated.

\subsubsection{\Gls{Vimes} tells \Gls{Vetina} about the special cordon set in place for his safety}
\Gls{Vimes} walks into \Gls{Vetina}'s chamber, to find him sitting up, complaining about a dull
ache in his toes. He points out the dwarf and troll Watchmen set to special duty around his room,
as well as Constable \Gls{Downs}, a gargoyle tasked with watching over the window facing out towards
the city. \Gls{Vetina} dismisses him, eager to get back to his paperwork, and \Gls{Vimes} sets out
into the city, as the fog rolls in.

\subsubsection{\Gls{Nobby} tells \Gls{Colon} about his heritage}
\Gls{Nobby} returns to the Watch House, lamenting the news about his elevation to the Earl of
Ankh, while having no material inheritance attached to the title. \Gls{Colon} consoles him, when he
learns that only \Gls{Vimes} is aware of this fact, as \Gls{Dorfl} lumbers into the Watch House.
Using its slate, it declares itself the murderer of \Gls{Tubel}, and asks to be arrested.

\subsubsection{\Gls{Vimes} chases after a golem in the foggy streets of the city}
\Gls{Vimes} spots an extra statue lining the bridge that he usually crosses on his way back to the
Watch House from the palace, and reacts too late to stop the golem from knocking him down and
running away into the foggy night. Meanwhile, \Gls{Carrot} looks after the administrative drudgery
of the Watch. He looks at \Gls{CheeryL}'s iconograph of \Gls{Tubel}'s eyes, just as \Gls{Colon}
walks into his office with news of \Gls{Dorfl}'s surrender.

\subsubsection{\Gls{Vimes} loses the suspect in the dark alleyways of the city}
\Gls{Vetina} gets to work on writing his book, as he takes note of the guards doing the rounds
outside his room, headed by \Gls{Detri}. Meanwhile, \Gls{Vimes} realizes he has misjudged the
suspect, as he makes a wrong turn through the foggy streets, stumbling into an open sewer.

\subsubsection{\Gls{Carrot} works out the fact that \Gls{Dorfl} is covering for someone else}
\Gls{Carrot} realizes that \Gls{Nobby} is trying to pin every single open case on \Gls{Dorfl}, and
feeds it a lie about the murder weapon used to kill \Gls{Hopkin}. He quickly realizes that the
golem has been programmed to take the fall for every one of the mysterious murders, and snatches its
scroll out of its head, just as it becomes belligerent.

\subsubsection{\Gls{Vimes} finds a mysterious wooden mannequin}
\Gls{Vimes} finds a wooden mannequin hanging from the old public execution site of Ankh-Morpork.
He turns away to look at the other alleyways leading to the square, and finds the mannequin in a
nearby gutter, free from the chains that suspended it on its gibbet.

\subsubsection{\Gls{Carrot} makes sense of \Gls{Dorfl} visiting the dying \Gls{Tubel}}
\Gls{Carrot} realizes that the scroll inside \Gls{Dorfl}'s head is an exact copy of the one stuffed
into \Gls{Tubel}'s mouth. He works out that \Gls{Dorfl} happened upon the priest as he was bleeding
out, and tried to save him the only way it knew how. \Gls{Vimes} returns to the Watch House, as
\Gls{Colon} tries to come to terms with the idea of disbelieving someone who confessed to a crime
out of their own volition.

\subsubsection{\Gls{Carrot} tries to argue against \Gls{Dorfl} being the murderer}
\Gls{Carrot} tells \Gls{Vimes} about the white clay that was found in both of the crime scenes, and
wonders if \Gls{Dorfl} was following another golem around, one which possibly found a way to
bypass its scroll and harm humans. \Gls{Vimes} meanwhile, is lost in thoughts about the way people
treat golems, and of how the instinctive fear of their emtpy eye sockets and mechanical movement
is so universal among all humans.

\subsubsection{\Gls{Angua} stumbles upon the secret council of free-thinking golems}
In her wolf form, \Gls{Angua} follows the scent of \Gls{Dorfl}, and finds an underground cellar,
with evidence of a council of golems. She finds one of twelve matchsticks on the ground broken in
half, and speculates that \Gls{Dorfl} had been selected by the council to turn itself in to the
Watch. She is alarmed by the words scrawled all over the cellar walls, and believes that a furious
argument must have been underway between the golems.

\subsubsection{\Gls{Angua} talks to \Gls{Vimes} and \Gls{Carrot} about the golem council}
\Gls{Angua} reports back to \Gls{Vimes} about the secret meeting of the golems in the cellar, and
wonders how many of them must be toiling away in the city, away from the eyes of the common-folk.
\Gls{Vimes} is alarmed by the prospect of golems plotting against their human masters, and wishes
for a hearty meal to make up for his light breakfast.

\subsection{}
\subsubsection{\Gls{Colon} and \Gls{Nobby} drink the night away at the Mended Drum}
\Gls{Colon} is alarmed by the increasingly drunk \Gls{Nobby} trying to make sense of his new title,
and the lack of any associated inheritance to go with it. Eventually, as the regulars at the Mended
Drum threaten a bar-fight, he defuses the tension by offering a round of drinks for everyone at the
tavern to celebrate \Gls{Nobby}'s elevation to earldom.

\subsubsection{\Gls{Vimes} tries to wile away the mornings at the Bucket}
\Gls{Vimes} nurses a lemonade at the Bucket, a bar adopted by the Watch as their unofficial hangout.
The same group of thieves that tried to rob \Gls{Ironc} barge into the tavern, and threaten the
barman with violence lest he hand over all his money. One of the thieves takes \Gls{Angua} hostage,
as the lot of them start to exit the tavern, as they realize its clientele is heavily armed.

\subsubsection{\Gls{Carrot} asks \Gls{Angua} not to kill any of the burglars}
\Gls{Carrot} reminds \Gls{Angua} not to take any lives, as she morphs into a werewolf, and
incapacitates the three burglars. \Gls{Vimes} struggles to continue his alcohol abstinence, as he
reminds \Gls{Carrot} that all the injuries sustained by the thieves can be written off as the
side effects of resisting arrest.

\subsubsection{\Gls{Colon} pays a heavy price for defusing the bar-fight}
\Gls{Colon} notices the denizens of the Mended Drum start to collapse in a drunken torpor, as the
barman presents him with the final bill. He is shocked by the tally, and reluctantly gives pays the
amount when the barman threatens to break his bones. He uses the Night Watch's food budget pilfered
from the headquarters to foot the bill.

\subsubsection{\Gls{CheeryL} informs \Gls{Vimes} of her forensic tests}
\Gls{CheeryL} accidentally includes the grease taken from the fingernails of \Gls{Tubel} in her
tests for arsenic along with the food from the palace, and finds a positive result. She tells
\Gls{Vimes} about the strange results, and talks about the match between \Gls{Dorfl}'s outer coating
and the white clay sample common to both crime scenes.

\subsubsection{\Gls{FORon} and \Gls{Gaspode} lead their retinue of beggars down the riverside}
\Gls{Downs} watches \Gls{FORon} and his band of ostracized beggars walk through the foggy night onto
a bridge, with the sentient dog \Gls{Gaspode} leading them. They spot a white golem trying to bash
its own head, as it staggers from one building to the next, and wonder if it was the same golem
they saw the night of \Gls{Tubel}'s murder.

\subsubsection{A golem kills itself at one of Ankh-Morpork's biggest foundries}
A golem commits suicide in the city's biggest foundry, after returning from its latest day's leave
for religious rituals. The owner of the foundry wonders if golems can commit suicide, as he looks
at the last message it wrote on its slate, and finds a statement of remorse for some heinous crime.

\subsubsection{\Gls{Colon} and \Gls{Nobby} wake up from their binge}
\Gls{Colon} and \Gls{Nobby} wake up from their drunken stupor in the gutters next to the Mended
Drum, and hear a loud animal sound in through the foggy night. They decide to return to the Watch
House to report the incident, and to avoid having to face whatever monstrosity was making the sound.
\Gls{Dorfl} recognizes the howling as the sound of a fellow golem, and repeats its commandments in
its head out of instinct.

\subsubsection{\Gls{Vimes} attends to \Gls{Vetina} at the palace}
\Gls{Vimes} is woken up at his home by \Gls{Visit} early in the morning, with news of \Gls{Vetina}'s
health declining. He hurries to the palace, and asks for everyone who came and went from the palace
to be lined up in the Great Hall for questioning. Meanwhile, he examines the book and ink-pot that
\Gls{Vetina} had been using just before he collapsed, and asks \Gls{CheeryL} to rotate the bedroom
he slept in at random.

\subsubsection{\Gls{Vimes} talks to \Gls{Drumk} about \Gls{Vetina}'s personal diary}
\Gls{Vimes} learns that one of the maids serving \Gls{Vetina} hurriedly left the palace on some
family business, and asks \Gls{Detri} to track her down. He then asks \Gls{Drumk}, the patrician's
newly appointed secretary, about \Gls{Vetina}'s personal diary. Meanwhile, \Gls{Carrot} and
\Gls{Angua} investigate the fourth golem suicide after their secret council, and confiscate the
slates with their last messages.

\subsubsection{\Gls{Detri} tells \Gls{Vimes} about the maid attending a funeral at her home}
\Gls{Detri} returns with news of a funeral in progress at the maid's home, with \Gls{Vimes}
realizing that it is the same street in the Shades that he grew up in. He decides to drop by later,
and notices \Gls{CheeryL} wearing some lipstick and jewelry, supposedly a gift from \Gls{Angua}.
Meanwhile, \Gls{RPalm}, the master of the Seamstress Guild, holds a meeting with the other
Guildmasters, talking about the attempt on \Gls{Vetina}'s life.

\subsubsection{\Gls{Slant} brings up the idea of restoring a monarch to the throne}
As the topic veers inevitably to the next Patrician of the city, the Guildmasters go quiet thinking
about the problems that might come with accepting the position. \Gls{Slant}, Master of the Lawyers'
Guild, starts to ramble about the need for a monarchy, and of how the institution brought stability
to kingdoms such as Klatch.

\subsubsection{The Guildmasters come to a decision about propping up \Gls{Nobby} as king}
Realizing the value of a puppet monarch, \Gls{Downey} states the rumours linking \Gls{Nobby}, a
lowly Corporal in the City Watch, to the last known Earl of Ankh. \Gls{QMolly} of the Beggars' Guild
recalls how dim-witted he seemed, and the other Guildmasters immediately start to see the value in
propping him up as the monarch.

\subsubsection{\Gls{Vimes} watches two bodies being mourned in Cockbill Street}
\Gls{Vimes} strolls by Cockbill Street, where he was born, and notices how little it has changed
over the decades. He arrives just in time for two coffins to be brought out of the home that
\Gls{Detri} had marked, and the procession to begin. Meanwhile, \Gls{Carrot} and \Gls{Angua} see
some dwarves protesting outside \Gls{Gimlet}'s cafe, accusing him of adulterating their rat meat
with pork and beef.

\subsubsection{\Gls{Carrot} starts his investigation of the food poisoning in \Gls{Gimlet}'s cafe}
\Gls{Carrot} breaks up the fight inside the cafe, and asks \Gls{Gimlet} about the claims of food
poisoning. \Gls{Gimlet} in turn, tells them that he had sourced his rats from \Gls{WMArthur}, same
as always, and that this had been the first time that his food had poisoned the patrons in many
years.

\subsubsection{\Gls{Vimes} asks the maid about the deaths of her family}
\Gls{Vimes} corners the mourning maid after the burial of her aged grandmother, and young brother.
She confesses to nicking some fancy food from the palace pantry, prompting \Gls{Vimes} to conclude
that the food might have been poisoned with \Gls{Vetina} in mind. Meanwhile, \Gls{Carrot} finds out
that \Gls{WMArthur}'s rats had ingested arsenic before they were cooked, pointing at a possible link
to the attempt on \Gls{Vetina}'s life.

\subsubsection{\Gls{WMArthur} deals with meddling from the Rat Catchers' Guild}
\Gls{WMArthur}, a rat-sized humanoid, gathers up the last of his current batch of rats, as he
updates the prices on his signboard advertising a vermin extermination business. He beats up some
enforcers from the Rat Catchers' Guild, sent to punish him for plying his trade without a guild
license. A while later, \Gls{Colon} and \Gls{Nobby} arrive at his shop, to talk about the
arsenic-laden rats sold to \Gls{Gimlet}.

\subsubsection{\Gls{WMArthur} denies any knowledge of the arsenic in \Gls{Gimlet}'s rat consignment}
\Gls{WMArthur} insists that he never uses poison to catch rats, and that he discourages all of his
customers from putting out poison-traps of their own. He also denies catching the palace rats, which
were well-fed, and made up \Gls{Vetina}'s spy network. \Gls{Nobby} shows \Gls{Colon} his invite to
an aristocrat party, and is delighted to know that some aging noble might want to marry their
daughter off to him.

\subsubsection{\Gls{Carrot} talks to \Gls{Vimes} about loose ends in their security}
\Gls{Carrot} reports to \Gls{Vimes} in the palace, and is shocked to find him bristling with anger,
at the deaths of the two innocent bystanders on Cockbill Street. \Gls{Vimes} goes through the
Patrician's daily meal regimen, and decides to stake out the mechanical elevator that carries his
meals up from the kitchen to his room. He is convinced that someone is accessing the elevator shaft
to poison the food after it has left the kitchen.

\subsubsection{\Gls{Vimes} takes care of the food prepared in the palace kitchens}
\Gls{Vimes} has a dwarf board up the unused openings along the elevator shaft, and presents
\Gls{Vetina} with pizza from a dubious dwarf eatery near the palace. \Gls{Vetina} eats as much of
the pizza as he dares to, and is amused by how meticulous \Gls{Vimes} has been in ruling out
various sources of the poisoning.

\subsubsection{\Gls{Carrot} tries to wring some information out of \Gls{Dorfl}}
\Gls{Carrot} puts \Gls{Dorfl}'s scroll back in its head, and asks it about the golem that is
responsible for the murders. \Gls{Dorfl} tells him that it can feel the other golems in the secret
council all having killed themselves, and refuses to betray the golem who went rogue. \Gls{Carrot}
reminds it that a pogrom is underway against any golems in the city, and asks it to return to its
workplace.

\subsubsection{\Gls{Carrot} is disgusted by \Gls{CheeryL}'s makeup and skimpy clothing}
\Gls{Carrot} is alarmed by \Gls{CheeryL}'s desire to express her femininity, and considers it a
deep taboo in dwarf culture. \Gls{Angua} reminds him that the melting pot of Ankh-Morpork might
simply have influenced her into wearing skirts and putting on makeup, taking after her human
counterparts.

\subsubsection{\Gls{Nobby} turns up with the invitation to \Gls{LSelach}'s party}
\Gls{Nobby} shows up at \Gls{LSelach}'s manor for the party, with a letter from \Gls{Vetina}
certifying that he is human. The guard salutes him the moment he shows the letter from \Gls{DragonK}
verifying his lordship, and wishes him the best for his first showing amongst the aristocracy.
Meanwhile, \Gls{Vimes} decides to investigate the wallpaper on the sixth floor of the palace, which
was the Patrician's personal living space.

\subsection{}
\subsubsection{\Gls{Nobby} attends the party thrown by \Gls{LSelach}}
\Gls{LSelach} welcomes \Gls{Nobby} to the party, and quickly adapts to his pedestrian tastes in
alcohol. The rest of the aristocrats also play along, silencing any among them who tried to point
out how plebian he looked. Meanwhile, \Gls{FORon} warns \Gls{Vimes} cryptically about some danger
to his life, as he rambles on about \Gls{QMolly} excommunicating him from the Beggars' Guild.

\subsubsection{\Gls{Vimes} summarizes the facts surrounding the golem murders}
\Gls{Vimes} writes down all the clues he has found this far in his notebook, and tries to make a
connection between the golem council and some sort of attempt to forge a new golem using their own
body parts and \Gls{Hopkin}'s oven. He then notices an expensive bottle of whiskey in his drawer
that he cannot recall ever purchasing.

\subsubsection{\Gls{Colon} is kidnapped by \Gls{DragonK} and the other monarchists}
\Gls{Colon} wakes up groggy in a cellar, and realizes he has been kidnapped. He struggles to sit up,
taking note of how he has been tied up, and catches voices from the other side of the door.
\Gls{DragonK} seems to be asking someone else to take care of \Gls{Angua}, and states that
\Gls{Vimes} has already been dealt with.

\subsubsection{\Gls{WMArthur} rescues \Gls{Colon} from his kidnappers}
\Gls{WMArthur} swims up an underground stream on his boat, and happens to pass right under
\Gls{Colon}'s cell. He manages to climb up the small trapdoor and cut open the ropes binding
\Gls{Colon}, just as a golem with eyes glowing red walks in through the door. He manages to break
through the decaying wood floor, and land on the stream, rich with the waste of the cattle pens.
\Gls{Colon} then manages to swim through the drain, struggling not to breathe in the methane
emanating from it.

\subsubsection{\Gls{Nobby} becomes the life of \Gls{LSelach}'s party}
As \Gls{Nobby} entertains the guests with his lewd jokes, and insists on everyone else drinking his
cheap beer, the monarchists gather in the next room, eager to discuss his viability as a puppet
king. They believe that \Gls{DragonK} has found them an excellent candidate, and believe that his
earldom is a fiction thought up by the Master Herald.

\subsubsection{\Gls{Carrot} tries to liberate \Gls{Dorfl} from slavery}
\Gls{Carrot} and \Gls{Angua} follow \Gls{Dorfl}'s scent to a dead end alleyway, where a mob is
trying to break the golem to pieces, with huge hammers. \Gls{Carrot} disperses the crowd, and takes
\Gls{Dorfl} back to its former master \Gls{GSock}. \Gls{Carrot} buys the rights to \Gls{Dorfl}
from the butcher, and puts the receipt inside the golem's head.

\subsubsection{\Gls{Dorfl} accepts his freedom, and walks away from \Gls{Carrot}}
\Gls{Dorfl} reboots when the receipt showing its freedom is put inside its head, and walks away
after spending some time lying on the ground. \Gls{Angua} is annoyed at how easily the city
accepts golems, but not werewolves and other non-humans like her. Meanwhile, someone drags
\Gls{Nobby} away from the party to a smoking room, eager to tell him about the plan to prop him up
as the new king.

\subsubsection{\Gls{Colon} is chased by the handsome golem, as he flees with \Gls{WMArthur}}
\Gls{Colon} is alarmed to see the handsome golem from earlier still in pursuit, and starts to run
away with \Gls{WMArthur}. The golem manages to grab \Gls{Colon}'s foot as he leaps past a collapsing
flight of stairs onto the roof of a building. Meanwhile, \Gls{Nobby} suggests \Gls{Carrot}'s name
out of instinct, when the monarchists at the party suggest the need for a king to replace the
ailing Patrician.

\subsubsection{\Gls{Carrot} enters the office of \Gls{Vimes} along with some Guildmasters}
\Gls{Carrot} sees some Guildmasters waiting for him at the Watch House, intent on inspecting
\Gls{Vimes}' office. \Gls{Carrot} tells them that he will have to accompany them to ensure no
wrongdoing, and finds \Gls{Vimes} passed out next to an empty bottle of liquor. When \Gls{Downey}
proceeds to open the bottom drawer of his table, \Gls{Vimes} pins him to the ground, seemingly sober
and alert.

\subsubsection{\Gls{Vimes} outwits the Guildlmasters, intent on framing him for the murders}
\Gls{Vimes} accuses \Gls{Downey} and the Guildmasters of trying to frame him, using the bottle of
liquor and a bag of arsenic powder planted in his office as circumstantial evidence. After the
Guildmasters leave the Watch House in all haste, having realized that their plan had been spoiled,
\Gls{Vimes} talks to \Gls{Carrot} about the child golem that had probably gone mad.

\subsubsection{\Gls{CheeryL} and \Gls{Carrot} notice \Gls{Vimes} working out the mystery}
\Gls{CheeryL} chimes in with news of golems being employed in the arsenic mining operations around
the city, leading \Gls{Vimes} to have an epiphany about the means by which \Gls{Vetina} had been
poisoned. Meanwhile, \Gls{Colon} is relieved to find the golem falling to the ground as his boot
comes off his foot. \Gls{WMArthur} informs him that it is slowly reassembling its shattered body,
making him worry for his life even more.

\subsubsection{\Gls{Dorfl} breaks free of its programming}
\Gls{Dorfl} has a fever dream where the idea of freedom battles with its innate programming
requiring a master to obey. Finally, it manages to realize the value of independence, and scratches
the words ``No Master'' into the walls of the cellar where the council of golems had argued a few
days ago.

\subsubsection{\Gls{Nobby} rejects the monarchists when they try to suggest his ascension to the
    throne}
\Gls{Nobby} is horrified by the idea of becoming king himself, even as the monarchists try to
persuade him with the lavish lifestyle and idle luxury that would entail. He dreads facing
\Gls{Vimes}, who is deathly opposed to the idea of monarchy, and jumps out of an open window to flee
the destiny being thrust upon him.

\subsubsection{\Gls{Vimes} realizes the Patrician has been inhaling poison through the candle fumes}
At the palace kitchen, \Gls{Vimes} asks the maids about the candles used in \Gls{Vetina}'s room,
and works out that the poison has been administered through the wicks. The maid confirms that she
pilfered some half-used candles to use in her home, as the housekeeper remarks on the new supplier
they have secured for the high-quality candles exclusively used for the Patrician's living quarters.

\subsubsection{\Gls{WMArthur} and \Gls{Colon} try to stay ahead of the handsome golem}
\Gls{WMArthur} tells \Gls{Colon} that the handsome golem has managed to screw its limbs back on, and
is walking into the building, hoping to climb the stairs from the inside. \Gls{Colon} manages to
swing himself onto a drainpipe, just as the golem reaches the terrace, and tries to punch him.
\Gls{WMArthur} falls off the roof, trusting in his size to shield him from damage, as \Gls{Colon}
realizes the drainpipe is coming loose from the top end.

\subsubsection{\Gls{Dorfl} emancipates the animals in \Gls{GSock}'s slaughterhouse}
\Gls{Dorfl} walks into \Gls{GSock}'s slaughterhouse, and sets all the animals free, while fending
off his employees with ease. It finally smashes an egg into \Gls{GSock}'s face, and walks out of the
warehouse, writing the words `No Master' on the notice board.

\subsubsection{\Gls{Colon} is cornered by some angry animals}
\Gls{Colon} loses grip on the drainpipe, and falls to the ground, only to be cushioned by the
animals liberated by \Gls{Dorfl}. He quickly notices the disquiet and annoyance in the herds, and
sees some bulls striding up to him belligerently. \Gls{Vimes} along with his men, finds some more
victims of \Gls{Dorfl}'s violence, as the butchers talk about the havoc it wreaked in their shops.

\subsubsection{\Gls{WMArthur} helps \Gls{Colon} get off the aging bull}
\Gls{Colon} rides past on a bull, desperately hanging on for his life, as \Gls{Vimes} looks on with
amusement. Some time later, \Gls{WMArthur} manages to tame the bull by leaping onto its head and
pulling on its hair, allowing \Gls{Colon} to slide off its back. \Gls{Vimes} helps him up, just as
a factory owner asks for his help in dealing with \Gls{Dorfl}.

\subsubsection{\Gls{Vimes} sides with \Gls{Dorfl} against the sweatshop owner}
\Gls{Vimes} threatens the sweatshop owner with violence, when he notices \Gls{Dorfl}'s handiwork
inside the place. The other golems working the factory's treadmill stare at the message scrwaled
by \Gls{Dorfl} on the wall, exhorting them to throw off their yokes. \Gls{Vimes}, angry at the
bigorty against the golems, asks \Gls{Colon} to include more undead in the City Watch.

\subsubsection{\Gls{Nobby} escapes from \Gls{LSelach}'s manor}
\Gls{Nobby} runs away from the aristocrat district, horrified at the prospect of volunteering for
the position of king. He recalls all the times in his life that volunteering had backfired, as he
runs into the Judas goat from \Gls{GSock}'s factory, now milling in the streets.

\subsubsection{\Gls{Carrot} and \Gls{Angua} confront \Gls{Carry} in his candle factory}
\Gls{Carrot} and \Gls{Angua} leave \Gls{CheeryL} in the street, and enter the candleworks owned
by \Gls{Carry}. The proprietor faces them with a loaded crossbow, claiming innocence about the
golem's actions. He tells them that it has been working at maximum speed, wandering off into the
city when he ran out of raw material to feed it.

\subsubsection{\Gls{Angua} is almost killed by \Gls{Carry}'s silver tipped crossbow bolt}
\Gls{Angua} smells the scent of a vampire in \Gls{Carry}'s warehouse, and asks him about the
arsenic in the wicks. He says that a vampire had fed him that idea as a means of incapacitating
\Gls{Vetina}, before he fires the crossbow and runs away. \Gls{Carrot} recognizes the silver tip
on the bolt, and pushes \Gls{Angua} out of the way, taking the bold in his palm.

\subsubsection{\Gls{Dorfl} is killed by the handsome golem}
\Gls{Dorfl} arrives to wrestle with the handsome golem, as and eventually has its scroll pulled
out of its head. \Gls{Carrot} is horrified at \Gls{Dorfl} being murdered, and asks \Gls{Angua} for
help distracting it. \Gls{CheeryL}'s feeble attacks with an axe are batted aside by the handsome
golem, as it tries to screw one of its legs back on.

\subsubsection{\Gls{Vimes} corners \Gls{Carry}, who is then mysteriously killed}
\Gls{Vimes} watches \Gls{Carry} fleeing his warehouse, and runs after him. He hears \Gls{Carry} try
to bargain with him, and asks \Gls{Detri} to cut off the exit at the other end of the alley. A
while, later he walks into the alley, to find \Gls{Carry} lying dead on the ground, his neck snapped
clean. He wonders how someone might have got in and out of the alleyway without accessing either of
its two ends.

\subsubsection{\Gls{Vimes} watches \Gls{Dorfl} kill the handsome golem}
\Gls{Vimes} arrives with \Gls{Detri} and \Gls{Colon} to \Gls{Carry}'s warehouse, just as \Gls{Dorfl}
comes alive in an attempt to stop the handsome golem from killing \Gls{Carrot}. \Gls{Vimes} is
alarmed to see \Gls{Dorfl} animated without any scroll in its head, as it smashes the handsome
golem's face, scattering the many scrolls that were stuffed inside it.

\subsubsection{\Gls{Vimes} asks \Gls{Carrot} to reassemble \Gls{Dorfl}}
\Gls{Vimes} orders \Gls{Carrot} to put \Gls{Dorfl} back together, as it scrawls some words on his
notebook, indicating that it has agency beyond the scroll inserted into its skull. He then notices
\Gls{CheeryL} hanging on for dear life above a vat of bubbling wax. \Gls{Angua} is forced to morph
into wolf form so that she can jump high enough to save her. She is annoyed when \Gls{CheeryL}'s
silver chainmail burns her mouth, as she lands on the ground and morphs back to human form.

\subsubsection{\Gls{Igneous} is compelled to reassemble \Gls{Dorfl}}
\Gls{Carrot} and \Gls{Detri} take the remains of \Gls{Dorfl} to \Gls{Igneous}, and ask him to put
the golem back together using the well-equipped furnace in his foundry. \Gls{Igneous} is skeptical
of the golem having any life without a priest to put a sanctified scroll in its head, but gets to
work when \Gls{Detri} threatens to unmask his smuggling operation.

\subsubsection{\Gls{Vimes} talks to \Gls{DragonK} in his chamber}
\Gls{Vimes} wakes up the next morning, trying to make sense of his notes about the crimes. He
finally works out the connection to the Heralds' office, and gets \Gls{Dorfl} from its overnight
bake in the furnace. He then confronts \Gls{DragonK} in his chamber, accusing him of poisoning the
Patrician, and causing two other deaths by negligence. He then realizes that \Gls{Nobby} was being
propped up as an Earl based on evidence concocted by the vampire, as an alternative to \Gls{Carrot}
ascending the throne.

\subsubsection{\Gls{Vimes} has \Gls{Dorfl} arrest \Gls{DragonK} for his crimes}
\Gls{Vimes} notices \Gls{DragonK} trying to morph into his bat form, and reminds him that he had
taken the precaution to soak the candles in holy water to suppress his powers. \Gls{Dorfl} steps
out of the shadows to pin down the weakened \Gls{DragonK}, while revealing his new sense of morality
that stops him from committing murder.

\subsubsection{\Gls{Vimes} faces \Gls{Vetina} at the palace}
\Gls{Vimes} realizes that \Gls{Vetina} will probably be forced to let \Gls{DragonK} walk free, since
the political landscape of the city required that he exist. Later, he visits the recovered
\Gls{Vetina} at the palace, and is pleased to learn that the entire city council is upset at the
chaos that his investiagation has caused. \Gls{Vetina} lauds him for taming the Guildmasters,
and promises him a pay raise for his troubles.

\subsubsection{\Gls{Vetina} reveals his knowledge of how he was being poisoned}
After \Gls{Vimes} leaves, \Gls{Vetina} asks his secreteray \Gls{Drumk} to dispose of a poisoned
candle, which has been cut off unburned. He reveals that he had worked out the source of the poison
early on, and was merely humouring \Gls{Vimes} and his investigative mind. He also secretly
supports \Gls{Vimes} in his crusade against the churches declaring \Gls{Dorfl} to be an abomination,
and asking for his disassembly.

\subsubsection{\Gls{Vimes} takes \Gls{Dorfl} out for a stroll through the city}
\Gls{Vimes} sets off on patrol with the newly sworn \Gls{Dorfl} at his side. Meanwhile, \Gls{Colon}
is relieved to be back on desk duty, and asks \Gls{Nobby} if he regrets losing his title.
\Gls{Nobby} declares the aristocrat life boring, privately thinking about all the family heirlooms
that he did not reveal to \Gls{DragonK}.

\subsubsection{\Gls{Dorfl} valiantly declares his atheism}
\Gls{Dorfl} is happy to be posted at the palace, where he can argue theology with the evangelical
Constable \Gls{Visit}. He is accosted by some priests who declare his existence a blasphemy, and
ask him if he believes in any Gods. A lightning bolt smites \Gls{Dorfl} when he says no, melting
his armour but leaving his clay body unscathed. \Gls{Vimes} realizes that the priests will be busy
arguing amongst themselves, trying to bend \Gls{Dorfl} to their own ways of worship.

\subsubsection{\Gls{Angua} almost walks out on \Gls{Carrot} and the city of Ankh-Morpork}
\Gls{Angua}, set on leaving the city and rejecting \Gls{Carrot}'s proposal, finishes packing up her
belongings, as she hands over the excess clothing to \Gls{CheeryL}. On her way out, she changes her
mind when \Gls{Carrot} asks her to help refurbish the Dwarf Bread Museum, eager to attract the
dwarves in the city using the appeal of historical artifacts.