\section{The Fifth Elephant}


\subsection{}
\subsubsection{\Gls{Colon} abuses his position as traffic policeman to get a free lunch}
As \Gls{Colon} is busy installing a new speed trap on a busy intersection, per \Gls{Vetina}'s new
traffic rules, he is interrupted by \Gls{AJolson}. The chef asks him to come to his shop, and shows
him the wheel clamp on a supply cart. \Gls{Colon} signals for the traffic police trolls working in
his department to come undo the clamps, when \Gls{AJolson} arranges for a free lunch.

\subsubsection{\Gls{Vimes} and \Gls{Carrot} help keep the peace in Ankh-Morpork}
\Gls{Vimes} supervises a fire extinguishing operation at the Fools' Guild, as \Gls{Carrot} reminds
him of the resistance to a formal fire service being established in the city. They receive a message
about a riot in the dwarf district, and find the likely origin to be an argument within
\Gls{Gimlet}'s cafe.

\subsubsection{\Gls{Vimes} and \Gls{Carrot} receive updates from \Gls{Vetina}}
\Gls{Vimes} and \Gls{Carrot} proceed to the palace, where \Gls{Vetina} tells them about the traffic
police inflating the number of infractions artificially, and asks them to investigate a flyer
about animal rights. He then talks about the town of Bong in Uberwald, where the new Low King is to
be crowned in a grand ceremony attended by envoys from every nearby nation.

\subsubsection{\Gls{Vimes} receives a new mission from \Gls{Vetina}}
\Gls{Vimes} is dismayed to learn that he has to travel to Uberwald as the duke of Ankh-Morpork, in
the hopes of securing favourable trade deals with the wealthy fiefdom of Bonk. \Gls{Vetina} suggests
he take some of the watchmen hailing from Uberwald with him, as a royal retinue, and leave the
actual negotiations to his clerks who will man the embassy.

\subsubsection{\Gls{Vimes} decides to learn the basics of dwarf history and culture}
\Gls{Vimes} is disheartened by his ignorance of dwarf culture, as \Gls{Carrot} decides to take him
to the Dwarf Museum for a quick refresher. \Gls{Vetina} tells him that he already has \Gls{Ramkin}
on board with his plan, since she is alarmed by how much her husband is overworking himself,
running around the city.

\subsubsection{\Gls{Angua} and \Gls{Nobby} interrogate a petty thief in the Shades}
In the Shades district, \Gls{Nobby} and \Gls{Angua} set a trap for \Gls{Duncan}, who falls for it,
and immediately starts talking about how was behind every great robbery in the city. \Gls{Angua}
is distracted by the smell of someone dangerous, as \Gls{Nobby} decides to return to the Watch
House with the tipoffs extracted from \Gls{Duncan}.

\subsubsection{\Gls{Carrot} explains the dilemma faced by the electors for the Low King}
\Gls{Carrot} explains to \Gls{Vimes} that the largest dwarf enclave outside of Uberwald is now
Ankh-Morpork itself, and that the election process for the new Low King is being held up by the
city dwarves. He says that the dwarves of Uberwald refuse to recognize the voice of others who
moved away from their ancestral lands, and this is leading to heated disputes among the electoral
college.

\subsubsection{A fugitive tries to escape werewolves chasing him in Uberwald}
\Gls{Carrot} explains that the orthodox dwarves are angry that their candidate is at risk of losing
to the progressive \Gls{RhysR}, who has the support of the dwarves in Ankh-Morpork. Meanwhile,
a fugitive on the run from some werewolves manages to evade them until he reaches the docks, and
manages to get on an abandoned boat. He then turns around to see some of them lying in wait in the
nearby bushes.

\subsubsection{\Gls{Margo} considers the remote possibility of having to face \Gls{Vimes}}
\Gls{Margo}, a vampire noble in Uberwald, thinks about the representative likely to be sent by
\Gls{Vetina} to the conclave at Bonk. She tells her butler \Gls{Igor} to send a message to their
spy in Ankh-Morpork, to gather information about \Gls{Vimes}, whose name sticks out like a sore
thumb in the book listing all the aristocrats in the city.

\subsubsection{\Gls{Vimes} talks to his wife aboue the coming trip to Uberwald}
\Gls{Vimes} is busy wondering what hidden reason \Gls{Vetina} is sending him to Bonk, as
\Gls{Ramkin} expresses the need to represent the best of Ankh-Morpork. \Gls{Ramkin} remarks on
\Gls{Angua}'s mother \Gls{Seraf} being her old schoolmate, and wife of the current ruler of
Uberwald. \Gls{Carrot} arrives at \Gls{Ramkin}'s manor with news of the Dwarf Bread Museum being
robbed, and the replica throne gone missing.

\subsubsection{\Gls{Vimes} learns about the two main factions of dwarves}
\Gls{Vimes} listens to \Gls{CheeryL} fill him in on the details of the robbery, and the lack of any
forensic evidence left behind at the Museum. He thinks about the clumsiness with which the glass
case housing the artifact was broken, and believes some deeper conspiracy is afoot. He then learns
about how the dwarves of Uberwald differ from the ones who adopted \Gls{Carrot}, and of the
increasing number of orthodox dwarves moving into the city.

\subsubsection{\Gls{Margo} is happy to have guessed who the envoy from Ankh-Morpork will be}
\Gls{Vimes} talks to \Gls{Detri} about the need for tact when facing the orthodox dwarves of
Uberwald, and the troll reassures him of his newfound sense of diplomacy. Meanwhile, \Gls{Igor}
informs \Gls{Margo} that her hunch about \Gls{Vimes} is indeed true, and tells her that the news
has spread to the other factions as well.

\subsubsection{\Gls{Wolfg} listens to his parents argue about \Gls{Vimes}}
At the Uberwald werewolf manor, \Gls{Wolfg} sees his mother, the baroness, argue with his father
about the insult to their honour in appointing \Gls{Vimes} as the envoy. He suggests helping the
official entourage reach the town of Bonk in all safety, so that the plan hatched by \Gls{RhysR}
might be put in motion.

\subsubsection{\Gls{Vimes} learns about the killing of \Gls{WallaS}}
\Gls{Vimes} welcomes \Gls{Vetina}'s diplomat \Gls{Inigo}, as he prepares to set out for Uberwald,
with his wife and the three watchmen hailing from there. He visits the Watch House one last time,
and finds \Gls{Carrot} reading a report on the murder of \Gls{WallaS}. \Gls{Carrot} tells him that
no guild has taken responsibility for the murder, and \Gls{Vimes} realizes that the dead man was a
valuable rubber manufacturer for the city.

\subsubsection{\Gls{Vetina} talks to \Gls{LeoQ} about cryptography}
\Gls{Vetina} visits \Gls{LeoQ}'s hidden workshop, where the latest code-breaking machine is ready,
and capable of breaking all of the coded messages arriving from Uberwald on the semaphore towers.
He then asks for a new cipher to be made for his own messages, knowing that it has to be breakable
by someone intelligent enough, so that he might mislead the other party into believing they had
the upper hand.

\subsubsection{\Gls{Vimes} learns about the geography of Uberwald}
\Gls{Vimes} reads the notes prepared by \Gls{Inigo} on the carriage to Uberwald, and learns of the
storied fat deposits underground, considered the best animal fat on the Disc. He reads about the
fifth elephant featuring in all the local mythologies, and is amused by the ban on silver mining
put in place many decades ago. He wonders what other natural resources the envoys might have their
eyes on as they converge for the coronation.

\subsection{}
\subsubsection{\Gls{Shoe} inspects \Gls{WallaS}'s rubber factory with \Gls{BSwires}}
Constables \Gls{Shoe} and \Gls{BSwires} investigate the death of \Gls{WallaS}, and find his corpse
sheathed in a rubber casing in the basement. The troll foreman tells them that he was distracted by
competitors popping up in the city, selling gimmicky replicas of his products, and that he had been
busy worrying about a large order coming up.

\subsubsection{\Gls{Carrot} receives a private message from \Gls{Angua}}
\Gls{Carrot} receives a personal message by pigeon from \Gls{Angua}, and sends a response with the
same bird. \Gls{Visit}, who is in charge of maintaining the pigeon nests, is happy to see the
pneumatic tube system set up to replace the simple act of shouting messages across buildings in the
Watch Headquarters.

\subsubsection{\Gls{Carrot} quits his job to pursue \Gls{Angua} in Uberwald}
When \Gls{Carrot} presents his resignation to \Gls{Vetina}, in order to go to Uberwald, the
Patrician correctly deduces that \Gls{Angua} has been summoned there by her family, and that
\Gls{Carrot} is intent on finding her. He tells \Gls{Carrot} where to start his search, and keeps
the offer of resuming his duties open should he return to the city.

\subsubsection{\Gls{Colon} is promoted to Captain in the absence of \Gls{Carrot}}
\Gls{Vetina} tells his secretary \Gls{Drumk} to prepare a promotion letter for \Gls{Colon}, as
\Gls{Carrot} seeks out \Gls{Gaspode} in his quest to follow \Gls{Angua}'s trail. \Gls{Nobby}
congratulates \Gls{Colon} on his promotion to Captain, when his suggestion about rejecting the offer
is met with fear.

\subsubsection{\Gls{Colon} and \Gls{Nobby} investigate \Gls{WallaS}}
\Gls{Colon} and \Gls{Nobby} inspect \Gls{WallaS} in his basement, as \Gls{Shoe} comments on the
similar smell reported by \Gls{CheeryL} at the Dwarf Bread Museum. \Gls{Colon} immediately dismisses
the idea that someone might want to make a copy of the replica throne stolen from the museum, since
it would not fool a single dwarf.

\subsubsection{\Gls{Carrot} learns of the second werewolf accompanying \Gls{Angua}}
\Gls{Gaspode} leads \Gls{Carrot} to a pond outaside the city, from which two werewolf scents emerge,
headed straight to the mountains. He tells \Gls{Carrot} that \Gls{Angua} is probably in the company
of a male werewolf, as \Gls{Carrot} mounts his horse, carrying \Gls{Gaspode} with him.

\subsubsection{\Gls{Colon} thinks about the power in his hands as Captain}
At the Watch House, \Gls{Colon}'s power goes to his head, as he orders fancy cutlery to be bought
for his daily tea, and decides to make some radical changes to the City Watch. \Gls{Vimes} climbs
onto the roof of his carriage, to secretly give \Gls{CheeryL} a coded request to be sent back
home at the next semaphore tower. He wishes to conduct a background check on \Gls{Inigo}, not
satisfied with the cover story supplied by \Gls{Vetina}.

\subsubsection{\Gls{Visit} delivers the message from \Gls{Vimes} to \Gls{Colon}}
\Gls{Visit} delivers the coded message meant for \Gls{Carrot} to the new Captain \Gls{Colon}.
He sees \Gls{Colon} struggling with the paperwork, and decides wisely not to laugh at him.
\Gls{Colon} meanwhile, begins to work out the value of the officer class, in keeping the ugly
business of paperwork away from the foot-soldiers of the Watch.

\subsubsection{\Gls{AStrong} gets to work on the background check ordered by \Gls{Vimes}}
\Gls{AStrong} reports on the stolen replica of the dwarf artifact left lying on the streets, and
is fed up with \Gls{Colon}'s antics. The other dwarves fondly recall \Gls{Vimes} and the help he
gave them during the race riots long ago, as \Gls{Nobby} tries to defend \Gls{Colon}'s integrity.
\Gls{Nobby} us blindsided when \Gls{Colon} calls him into his office, only to promote someone else
to Sergeant.

\subsubsection{\Gls{Carrot} and \Gls{Gaspode} find a farm where \Gls{Angua} stole some chickens}
\Gls{Carrot} and \Gls{Gaspode} happen upon a farm where some chickens are missing, with some coins
mysteriously left behind by the culprits as payment. He believes it to be \Gls{Angua}'s doing, and
asks the farmer to prepare some chickens for him and \Gls{Gaspode}. A while later, \Gls{Gaspode}
wakes him up when another man arrives with news for the farmer about a wolf being caught by some
trappers nearby.

\subsubsection{\Gls{Vetina} tries to rein in \Gls{Colon}}
At the Patrician's office, \Gls{Vetina} tries discreetly to remind \Gls{Colon} that he is
overstepping his bounds as Acting Captain, and asks him to speed up the investigation into
\Gls{WallaS}. Afterward, \Gls{Colon} mistakes \Gls{Vetina}'s decorum for approval, and believes he
has is getting into the groove of leading the City Watch.

\subsubsection{\Gls{Carrot} rescues a trapped wolf in exchange for news about \Gls{Angua}}
\Gls{Carrot} reaches the town where the captured wolf is set to be executed, and \Gls{Gaspode}
tells it that it can walk away with its life, in exchange for news about the werewolves who passed
through. At night-time, \Gls{Vimes} receives the response from \Gls{AStrong}, confirming his
suspicions about \Gls{Inigo}, and informing him of the murder of \Gls{WallaS}.

\subsubsection{\Gls{Inigo} asks \Gls{Vimes} to hurry onward through a mountain pass}
\Gls{Inigo} insists that the caravan skip that night's rest, and ride through a dangerous mountain
pass as fast as possible. \Gls{Vimes} asks for the servants to stay back, and make the trip after
sunrise, as \Gls{Ramkin} insists on accompanying him. Meanwhile, \Gls{Gaspode} manages to extract
information from the rescued wolf about \Gls{Angua} and another werewolf accompanying her, before
\Gls{Carrot} sets it free.

\subsubsection{\Gls{Vimes} prepares to fend off some bandits with his Watchmen}
\Gls{Vimes} informs the watchmen that they might be facing an ambush by bandits, as a snowstorm
picks up speed, and they arrive at the mountain pass. He picks the lock on \Gls{Inigo}'s suitcase,
and is dismayed to find an assassin's weapon hidden inside, confirming his suspicions that the
diplomat is not who \Gls{Vetina} said he is.

\subsubsection{\Gls{Angua} finds \Gls{Carrot} and \Gls{Gaspode} in the alpine forests}
\Gls{Carrot} decides to sleep through the snowstorm, just as \Gls{Angua} catches up to them along
with a large pack of wolves. \Gls{Gaspode} is relieved to recognize her wolf form, since he had
been unable to wake \Gls{Carrot} up from his slumber.

\subsubsection{\Gls{Vimes} talks to \Gls{Inigo} about the Assassins' Guild}
\Gls{Vimes} manages to outwit the bandits attempting to take him hostage, and tells the Watchmen
to continue through the pass, without waiting for \Gls{Inigo}. \Gls{Ramkin} heads into the next
tavern to relieve herself, as \Gls{Vimes} confronts \Gls{Inigo} about his true identity. \Gls{Inigo}
claims to be a scholarship student at the Assassins' Guild, tasked with keeping \Gls{Vimes} safe.

\subsubsection{\Gls{Angua} tells \Gls{Carrot} about her old friend \Gls{Gavin}}
\Gls{Carrot} is woken up by \Gls{Gaspode}, and learns from \Gls{Angua} that the wolf accompanying
her is an old friend named \Gls{Gavin}, who had rescued her from a trap many years ago. He is
shocked to learn that \Gls{Gavin} is just a wolf, and had braved the journey into Ankh-Morpork to
warn her of her family's wrongdoing.

\subsubsection{\Gls{Vimes} finds out about a second ambush by bandits in the night}
The next morning, \Gls{Vimes} learns that several dead bodies have been found close to the tavern,
and asks \Gls{Inigo} if he killed them. \Gls{Inigo} states that a second ambush was attempted at
night, and that some of the bandits got away in the confusion.

\subsubsection{\Gls{Inigo} deals with a dwarf checkpoint in the mountain road}
As \Gls{Vimes} and his retinue ride deeper into the mountains, a company of dwarf soldiers stop
them, and demand they identify themselves. \Gls{Inigo} speaks fluent dwarfish with the leader, and
shows them some documents bearing the seal of Ankh-Morpork, and gets them to stand aside. He then
congratulates \Gls{Vimes} on appearing stupid with his broken Dwarfish, and mentions that he is
adapting well to the role of a diplomat.

\subsubsection{\Gls{Angua} finds a sled for \Gls{Carrot}, who is too weak to run}
\Gls{Angua} trots off with some wolves to find a sled to haul \Gls{Carrot} through the snow, since
he is too weak and too hungry to run along with them. \Gls{Gaspode} wonders if \Gls{Carrot} starved
himself intentionally to force \Gls{Angua} to rescue him, thus revealing her position.

\subsection{}
\subsubsection{\Gls{Colon} learns about the Watchmen unionizing}
\Gls{Colon} is embarrassed to find out that he burned the paperwork containing the monthly wage
release forms for the remaining Watchmen. \Gls{Nobby} then informs him that he is the Guildmaster
of the newly formed Guild of Watchmen, and that everyone \Gls{Colon} had dismissed has registered
with him. \Gls{Nobby} tells him that he is putting the entire City Watch on strike, and that he will
wait for him at their coppers' bar.

\subsubsection{\Gls{Vimes} challenges the guards at the city gates of Bonk}
At the gates of Bonk, \Gls{Vimes} is stopped by some guards, who ask to search his coach and inspect
his papers. He refuses, hoping that the diplomatic weight of his position will cow the guards into
standing down. After some heated argument with \Gls{Inigo}, who acts as interpreter, the guards
let them in.

\subsubsection{\Gls{Vimes} secures the right to entry for \Gls{Detri}}
\Gls{Vimes} notices more guards stopping \Gls{Detri}, and asking him for written permission from his
envoy to enter the city. \Gls{Vimes} turns his carriage around, and threatens to leave the city,
until the leader of the guardsmen issues an order waiving the requirement. \Gls{Vimes} tells
\Gls{Inigo} that all of the weapons on the guardsmen are exports of the dwarf armorers in
Ankh-Morpork, and that trade is a powerful foundation for diplomatic power.

\subsubsection{\Gls{Angua} talks about her brother \Gls{Wolfg}, and his plans for gaining power}
\Gls{Inigo} then comments on the news about the dwarf throne going missing, and is surprised when
\Gls{Vimes} seems to know about this already. Meanwhile, \Gls{Gaspode} watches \Gls{Angua} talk
to \Gls{Carrot} about her brother \Gls{Wolfg}, who was planning to exploit the division among the
dwarves to amass more power for their house. She comments on how he had killed one of their sisters
and driven away a brother, for not inheriting the ability to shapeshift.

\subsubsection{\Gls{Vimes} and \Gls{Ramkin} inspect their makeshift embassy}
\Gls{Vimes} and \Gls{Ramkin} are welcomed by \Gls{Igor} at the building set aside for the makeshift
embassy. They find the building stuffed full of taxidermied heads, and believe the former occupant
to be a prolific hunter. \Gls{Detri} walks in, and finds a troll head mounted on the wall, with
\Gls{Vimes} quick to notice his discomfort. He asks \Gls{Igor} to get rid of all the mounted heads,
and throw them in the river if needed.

\subsubsection{\Gls{Igor} talks about the disappearance of \Gls{WSleeps}, their former consul}
\Gls{Igor} tells \Gls{Vimes} that \Gls{WSleeps}, the acting consul of Ankh-Morpork, had vanished a
few weeks ago, and that some of his personal items were also missing. \Gls{Inigo} tries to make
sense of the news, as \Gls{Vimes} is lost in thought about the Dwarf artifact being stolen.

\subsubsection{\Gls{Inigo} talks about the history of Uberwald}
The next morning, \Gls{Inigo} informs \Gls{Vimes} of a formal meeting with Lady \Gls{Margo}, the
leader of the vampire faction in Uberwald. He talks about the history of the vampires and werewolves
coming to an uneasy truce with the newly risen dwarves, and of how the city of Bonk was little more
than a glorified meeting hall for the various clan leaders.

\subsubsection{\Gls{Vimes} heads to the dwarf caversn with \Gls{CheeryL} and \Gls{Tantony}}
\Gls{Vimes} decides to take \Gls{CheeryL} and the captain of the Bonk city guard \Gls{Tantony}, to
the formal meeting with \Gls{Margo}. Meanwhile, \Gls{Inigo} decides to ask around the city about
\Gls{WSleeps}, afraid that he might have been executed on the suspicion of being a spy.
\Gls{CheeryL} guides \Gls{Vimes} through a dwarf checkpoint leading to an underground room, which
eventually takes them via elevator to a cavern deep underground.

\subsubsection{\Gls{Vimes} meets with \Gls{Dee} inside Shmaltzberg}
\Gls{Vimes} is greeted by \Gls{Dee}, the sheriff of Shmaltzberg, which is the underground fat
deposit said to originate from the mythical fifth elephant crashing into the Disc long ago. He
examines the papers presented by \Gls{Vimes}, and tells him that there is no need to meet the king
in person. \Gls{Vimes} notices the commotion building in the cavern, and wonders if some kind of
riot or crisis is happening just out of earshot.

\subsubsection{\Gls{Vimes} catches \Gls{Dee} off-guard with the theft of the Dwarf Throne}
\Gls{Dee} is quick to dismiss the allegation that the Dwarf Throne has been stolen, and tries to
reassure \Gls{Vimes} that it is being kept under strict observation. The leader of the orthodox
dwarves \Gls{AlbreA} walks in, and is horrified by \Gls{CheeryL}'s expression of femininity.
\Gls{Vimes} asks \Gls{Dee} to make sure no further derogatory words are used in the presence of his
staff, and is hurriedly taken to another room to meet the king.

\subsubsection{\Gls{RhysR} talks to \Gls{Vimes} about the brain-drain to Ankh-Morpork}
In his throne room, King \Gls{RhysR} talks about the racism he faced in Ankh-Morpork long ago, and
asks \Gls{Vimes} why dwarves still find it more attractive than their traditional homelands as a
place to settle down and earn a living. \Gls{Vimes} is flummoxed, and tries to argue that the
personal rights guaranteed in the city might be the reason why dwarves sing about Uberwald every
night in the bars, but never go back to visit.

\subsubsection{\Gls{Vimes} heads to \Gls{Margo}'s manor}
\Gls{CheeryL} talks about the split in dwarf society caused by the scientific advancements
originating from Ankh-Morpork, and of how the Shmaltzberg dwarves insisted on following the old
ways, even at increased risk to their lives. They head to \Gls{Margo}'s manor, which looks like a
poorly designed castle, meant more for show than actual defense.

\subsubsection{\Gls{Vimes} talks to \Gls{Margo} about the dwarf civil war}
Inside the manor, \Gls{Margo} welcomes \Gls{Vimes}, and talks about the coming civil war among the
dwarves, triggered by the loss of their ancestral Throne. After a while, \Gls{CheeryL} informs him
about the last civil war that had broken out fifty years ago, and had been conducted completely
underground, in the dwarf mines of Uberwald. They return to the carriage, where \Gls{Tantony} is
happy to wait, terrified of walking into the vampire's presence.

\subsubsection{\Gls{Vimes} meets with \Gls{Seraf} at their castle}
\Gls{Vimes} meets \Gls{Seraf}, and immediately sees the resemblance to \Gls{Angua}. Her husband
walks in a while later, surrounded by the family dogs, all jostling for attention. He notices one of
the wolves looking at him with a judgemental look, and sees \Gls{Seraf} wince when he mentions
\Gls{Vetina}'s name.

\subsubsection{\Gls{Vimes} thinks about the differences between \Gls{Angua} and her parents}
After the meeting \Gls{Vimes} talks to \Gls{CheeryL} about the taxidermied heads that had been
hastily removed from \Gls{Seraf}'s walls, and wonders if \Gls{Angua} has been excommunicated.
Back at the embassy, \Gls{Detri} welcomes then with news of \Gls{Igor} being hurt, as \Gls{Vimes}
carefully unloads the hand that had been given to them by the werewolves' butler.

\subsubsection{\Gls{Vimes} decides to ride to the semaphore tower near Bonk}
\Gls{Vimes} sees the goods wagon ransacked, as \Gls{Detri} talks about nothing missing from inside
it, per the list of goods kept by \Gls{Ramkin}. He decides to take \Gls{Ramkin} along for a ride
into the mountains, and sorts through the invitations to various events piled up on his desk. He
rides with \Gls{Igor} to the nearest semaphore tower, and notices something wrong with it.

\subsubsection{\Gls{Vimes} finds \Gls{Inigo} at the defunct semaphore tower near Bonk}
\Gls{Vimes} pulls out his hidden sword, and nudges the door into the tower, which is left unlocked.
He finds \Gls{Inigo} inside the main signaling room, with the crew seemingly vanished. \Gls{Inigo}
claims that someone had forced the crew to leave, taking advantage of a lapse in security protocol,
and then smashed the signaling machines at the top of the tower. He promises to send out the
emergency flare that \Gls{Vimes} finds under a bed, and asks him to return to the embassy.

\subsubsection{\Gls{Vimes} finds the spy's secret room within the Embassy building}
\Gls{Nobby} prepares to picket the Watch House using the ideas supplied by \Gls{Shoe}, from his
time as a protestor for Undead Rights. \Gls{Vimes} accidentally finds a way to open the secret room
found by \Gls{Ramkin}, when measuring the area of their rooms in the embassy. Inside, he finds
detailed reports kept by a spy, including news the coming werewolf uprising led by \Gls{Wolfg}, in
the aftermath of the dwarf Throne being stolen.

\subsubsection{\Gls{Vimes} sees a secret tunnel hidden in the embassy}
\Gls{Vimes} then notices a stairway leading to a hidden underground tunnel, that enables discreet
access to and from the embassy, as well as a miniature iconograph for taking pictures without
anyone noticing. Meanwhile, \Gls{Inigo} gets ambushed by someone in the tower, just after he sends
the signal flare up to inform any nearby towers about the emergency.

\subsubsection{\Gls{Dee} agrees to let \Gls{Vimes} and \Gls{CheeryL} inspect the Throne's safe-room}
At the great hall of Shmaltzberg, \Gls{Vimes} leaves \Gls{Ramkin} and \Gls{Detri} to mingle with
the guests, and drags \Gls{CheeryL} along to the safe-room from which the Dwarf Throne has been
stolen. \Gls{Dee} gives in to his accusations of the Throne being necessary for the coronation, and
leads him to the safe-room.

\subsubsection{\Gls{Dee} shows \Gls{Vimes} the ransom note, and the political nature of the theft}
At the safe-room, \Gls{Dee} explains the elaborate security systems, that make it impossible for
someone to leave with the Throne, unless they can fly. \Gls{Dee} suggests outsourcing the
investigation to \Gls{Vimes}, since any questions coming from the dwarf ruling class would trigger
hysteria in Uberwald. He also shows \Gls{Vimes} a ransom note, asking for \Gls{RhysR} to abdicate
his claim to the throne in exchange for the return of the artifact.

\subsection{}
\subsubsection{\Gls{Vimes} talks to \Gls{Dee} about some preliminary ideas regarding the theft}
\Gls{Dee} leaves \Gls{Vimes} and \Gls{CheeryL} in the safe-room, and is shocked when \Gls{Vimes}
clears the security system using his added height. After the opera ends, \Gls{Vimes} introduces
himself to \Gls{Wolfg}, noticing the flashy new symbol sewn into his robes. He then finds \Gls{Dee},
and asks to set up an interrogation for the guards who were on duty at the safe-room. He believes
that the thief might have used the changing of shifts at the safe-room to steal the artifact.

\subsubsection{\Gls{Vimes} saves \Gls{RhysR} from a falling chandelier full of hot wax}
\Gls{Vimes} sees \Gls{Detri} trying his best to mingle with the other cultural attaches, and is
forced by \Gls{Ramkin} to attend the formal dinner, where he will be introduced to the Low King
\Gls{RhysR}. \Gls{Vimes} notices the chandelier set above \Gls{RhysR} start to fall, and dives to
save him. In the process he is knocked out by some blunt hits to his armour.

\subsubsection{\Gls{Vimes} receives a visit from \Gls{Dee}}
\Gls{Vimes} wakes up in a dark prison cell lined in stone, and notices all his armour and weapons
stripped from him. Some time later, \Gls{Dee} arrives to inform him that some dwarves suspect his
agent \Gls{Inigo} of letting loose the chandelier which fell on the Low King, and that the
assassin's corpse had been found next to the mechanism.

\subsubsection{\Gls{Dee} informs \Gls{Vimes} about the charges levelled against him}
\Gls{Dee} also tells him that \Gls{Ramkin} and the rest of his retinue are under house arrest at
the embassy. He then talks about the ancient taboo against touching the Low King, and of how
saving him from an assassination attempt was not likely to be a mitigating circumstance in dwarf
law. \Gls{Vimes} notices the miniature crossbow belonging to \Gls{Inigo} hidden in side one of the
pillows in his cell.

\subsubsection{\Gls{Vimes} escapes his cell using a matchstick to blind the guards}
When the prison guards outside his cell open the door for his next meal, \Gls{Vimes} uses one of
his matchsticks to blind them, and chooses to knock them out. He believes that whoever put the
crossbow in his room expected him to use it to murder the guards. He sneaks out of the cell, and
finds a spiral staircase made of old wooden planks, climbing up from a mineshaft. He slips midway
through his climb, as the wood crumbles with age, and holds on for dear life.

\subsubsection{\Gls{Vimes} trudges through the snowy forest and falls asleep}
\Gls{Vimes} is rescued by \Gls{Margo}, who abandons him in a snowstorm at the top of the mineshaft.
She tells him that he is a few miles away from Bonk, and that she cannot be seen interfering in
dwarf affairs any further. \Gls{Vimes} crawls through the forest, and eventually finds a cave to
protect him from the wind and snow, where he falls asleep.

\subsubsection{\Gls{Vimes} is surrounded by \Gls{Wolfg} and his lackeys}
\Gls{Vimes} wakes up, and continues his trek downhill, until he finds some hot springs, where he
relieves his muscles. \Gls{Wolfg} and his gang emerge from the bushes, to surround him, and reveal
plan to trigger a civil war amongst the dwarves. \Gls{Vimes} suggests that \Gls{Dee} had also wanted
the war, but was superseded by \Gls{Wolfg}'s plan to replace the stolen Throne with the rubber
replica made in \Gls{WallaS}'s rubber factory.

\subsubsection{\Gls{Vimes} runs away from \Gls{Wolfg}, after being given a head start}
\Gls{Vimes} is forced to accept the offer of a pursuit by the werewolves, in keeping with their
tradition of giving their targets a head start before starting the hunt. He runs away from the
hot springs, in the direction of Bonk as indicated by \Gls{Wolfg}. Meanwhile, \Gls{Vetina} is pleased
to see the strike in progress, and congratulates \Gls{Nobby} on his organizational skills.

\subsubsection{\Gls{Vimes} finds an orchard and a farmhouse outside Bonk}
\Gls{Vimes} runs into a barn in the outskirts of Bonk, as the three sisters inside reminisce about
better days spent in the city. Meanwhile, \Gls{Angua} detects the news of the hunt in progress when
\Gls{Wolfg}'s pack howls, and tells \Gls{Carrot} that she intends to put a stop to the vile
practice of playing with people's lives.

\subsubsection{\Gls{Vimes} escapes \Gls{Wolfg} and his pack by luring them into the barn}
\Gls{Vimes} uses his aristocratic credentials to persuade the three ladies into helping clothe and
arm him. He looks out of the barn's attic, and finds a boat anchored to a jetty nearby, indicating
a river. He manages to outwit the wolves, and get to the boat to row it downriver. The werewolves
catch up to him eventually, and go away before telling him that the river is coming to a waterfall.

\subsubsection{\Gls{Vimes} lands at the bottom of the waterfall, and knocks out some werewolves}
\Gls{Vimes} sees \Gls{Death} materialize in front of him, claiming that he had entered a situation
that could possibly kill him. At the bottom of the waterfall, \Gls{Vimes} manages to drown two of
the werewolves when they chase him into the river, and crawls onto the shore. He notices the
semaphore tower nearby, and works out the distance to Bonk in his mind.

\subsubsection{\Gls{Vimes} is rescued by \Gls{Gavin} and his pack}
\Gls{Vimes} is chased to the top of a pine tree, and manages to force one of the werewolves to fall
when it climbs up after him. A while later, \Gls{Gavin}'s pack chases the werewolves away, and
\Gls{Carrot} helps him settle down next to a campfire. After being relieved from the cold and
hunger, \Gls{Vimes} learns from \Gls{Angua} that her brother is intent on expanding their family's
power, using the dwarf civil war as a smokescreen.

\subsubsection{\Gls{Angua} talks to \Gls{Vimes} about her brother's ambitions}
\Gls{Angua} tells \Gls{Vimes} that \Gls{Wolfg} always preferred to let his targets get close to
the finish line, in order to savour the hope in their eyes draining away at the last moment.
\Gls{Vimes} is carried by sleigh to the city, and starts to piece together the fact that the Dwarf
Throne might not have been stolen at all.

\subsubsection{\Gls{Vimes} travels to the semaphore tower on his way to Bonk}
\Gls{Vimes} stops at the semaphore tower to gather up the personal belongings of the crew, who had
been mercilessly slaughtered by \Gls{Wolfg}, after being chased down in the forest. Meanwhile,
\Gls{Colon} thinks about the prospect of facing \Gls{Vimes} and his wrath when he returned from the
trip to Uberwald.

\subsubsection{\Gls{Vimes} enters the embassy through the secret tunnel}
\Gls{Angua} manages to persuade the guard at the Bonk city gates into letting them in. Meanwhile,
\Gls{Tantony} positions men inside the embassy, suspicious of the orders to kill \Gls{Vimes} on
sight, that had been given to the dwarves in Bonk. \Gls{Vimes} manages to enter the embassy using
the tunnel, and threatens \Gls{Tantony} with prosecution since he is on embassy soil. \Gls{Tantony}
gives him the keys to the cells underground, and informs him that \Gls{Ramkin} is at the werewolf
manor to meet her friend \Gls{Seraf}.

\subsubsection{\Gls{Ramkin} prepares to escape the bedroom where \Gls{Seraf} locks her up}
\Gls{Ramkin} realizes that \Gls{Seraf} has never given up her racist opinions about the non-humans,
and prepares to go to bed after dinner. She hears the door to the bedroom being locked shut, and
takes note of the heavy iron bars lining the windows. She uses the bedsheets to make a rope, and
plans to lower herself to ground level from the window, after dismantling the bars.

\subsubsection{\Gls{Vimes} watches \Gls{Angua} confront her family}
\Gls{Vimes} orders \Gls{Detri} to blow up the door to the werewolf manor, and prepares to storm it
with the watchmen by his side. At the castle, \Gls{Vimes} is relieved to find \Gls{Ramkin} in the
courtyard, with an iron bar in her hands. They confront \Gls{Seraf} and \Gls{Wolfg}, until
\Gls{Angua} decides to turn around and walk away, paying no heed to her mother's accusations of
being a race traitor for liking \Gls{Carrot}

\subsubsection{\Gls{Tantony} confronts \Gls{Seraf} at her manor}
Outside the werewolf manor, \Gls{Tantony} walks up with the Bonk Watch, to level charges against
\Gls{Seraf} for the conspiracy against the dwarves. \Gls{Wolfg} leaps at him mid-sentence, forcing
\Gls{Detri} to fire his crossbow again. \Gls{Gavin} and \Gls{Wolfg} fall down the bridge into the
river below, after \Gls{Carrot} is knocked out in his attempt to restrain \Gls{Wolfg}. \Gls{Vimes}
accuses \Gls{Seraf} of having the copy of the Dwarf Throne in her manor, and asks \Gls{Detri} to
retrieve her butler.

\subsubsection{\Gls{Gaspode} finds \Gls{Gavin} dead after falling from the bridge to \Gls{Seraf}'s
    manor}
\Gls{Gaspode} recovers from the fall to find \Gls{Death} tending to \Gls{Gavin}'s body, and howls
the news out to the forest for his pack to receive. Meanwhile, \Gls{Vimes} asks \Gls{Igor} to tend
to the wounds of \Gls{Tantony} and \Gls{Carrot}, as \Gls{Angua} forces her mother to give her the
replica Dwarf Throne.

\subsubsection{\Gls{Vimes} and his party reach the embassy at Bonk}
\Gls{Vimes} is relieved to see the semaphore tower repaired, when the crew send up a green flare of
confirmation. He watches \Gls{Carrot} slowly wake up on the sleigh as they march back to Bonk, and
chastises him for going easy on \Gls{Wolfg}. \Gls{Vimes} surrenders himself to the chief of the
dwarves guarding the embassy, and asks to be taken to the Low King.

\subsubsection{\Gls{Vimes} manages to get the dwarves in Bonk to take him to the Low King}
\Gls{Vimes} lies to the dwarves about the green signal flares, claiming that they indicate the
news of his arrest being relayed to Ankh-Morpork. He asks the dwarves to take him to the Low King,
and avoid the blame of triggering a war with Ankh-Morpork, just as \Gls{Ramkin} finishes singing
one of the dwarf operas which talks about legal precedent for their request.

\subsubsection{\Gls{Vimes} watches \Gls{AlbreA} verify the authenticity of the Throne}
\Gls{Vimes} is taken to \Gls{RhysR}'s chamber, in spite of \Gls{Dee}'s accusations against
\Gls{Vimes}. Once inside, \Gls{Dee} claims that the Throne held by \Gls{Vimes} is a copy forged in
Ankh-Morpork, and is relieved to see the Low King ask for an appraisal by \Gls{AlbreA}. \Gls{AlbreA}
makes an elaborate show of inspecting the Throne, before declaring it authentic.

\subsection{}
\subsubsection{\Gls{Dee} comes out as female, after expressing annoyance at the freedom that
    the dwarves in Ankh-Morpork enjoyed}
After \Gls{RhysR} forces \Gls{Dee} to confess to collaborating with the werewolves, and
participating in the conspiracy to forge a copy of the Throne, she comes out as female, to the
shock of everyone present. \Gls{CheeryL} decides to help \Gls{Dee} deal with her femininity, and
leads her away from the throne room.

\subsubsection{\Gls{RhysR} reveals the true nature of the Dwarf Throne}
\Gls{RhysR} then reveals to \Gls{Vimes} that the Dwarf Throne was replaced every century, and was
not a long-lived artifact as believed by the common dwarves. \Gls{AlbreA} is also aware of this
truth, since he is from an aristocratic family. He talks about the nature of dwarf bread, and the
need to replace the old Throne with a newly baked one every few centuries, and maintain the facade
of an indestructible ancient artifact.

\subsubsection{\Gls{Vimes} sees \Gls{Ramkin} negotiate a trade agreement with the Low King}
\Gls{Vimes} feels sleep overcome him, as \Gls{RhysR} asks him what the city of Ankh-Morpork wants
from the dwarves. \Gls{Ramkin} steps in to negotiate a trade deal for the fat mined from
Shmaltzberg, and drives a hard bargain until \Gls{RhysR} relents to her terms. The next day,
\Gls{Vimes} wakes up to see the finalized trade deal delivered to the embassy, along with a polite
request to evacuate Bonk.

\subsubsection{\Gls{Vimes} invites one of the Igors to Ankh-Morpork, impressed by the surgical
    talent}
\Gls{Vimes} is impressed by \Gls{Igor}'s surgical talent in stitching up \Gls{Tantony}'s lacerated
chest, and \Gls{Carrot}'s broken arm. When asked if he would like to move to Ankh-Morpork,
\Gls{Igor} is overjoyed to recommend his cousin for the position, given how plentiful corpses were
in the shadier districts of the city.

\subsubsection{\Gls{Vimes} learns that \Gls{Ramkin} is pregnant}
\Gls{Ramkin} tells \Gls{Vimes} that she is pregnant, just as \Gls{Wolfg} busts his way into the
embassy, taking out \Gls{Igor} in his rage. He then heads for \Gls{Carrot}'s room, and \Gls{Angua}
stops him, using his inability to hold a steadily morphed shape to try and best him. Meanwhile,
\Gls{Vimes} hears \Gls{Igor}'s dying words, asking to put his corpse on ice so that his organs might
be transplanted where needed by the other butlers.

\subsubsection{\Gls{Vimes} sets out in pursuit of \Gls{Wolfg}}
\Gls{Vimes} realizes that he has the jurisdiction to go after \Gls{Wolfg}, since he has committed
a crime on embassy grounds. He promises \Gls{Ramkin} that he will try to minimize any collateral
damage, as he sets off after \Gls{Wolfg}, who has fled the embassy in his weakened state. He
pursues \Gls{Wolfg}'s trail of carnage through the town, until he finds \Gls{Tantony} herding the
coronation attendees along with his guardsmen.

\subsubsection{\Gls{Vimes} kills \Gls{Wolfg} with a signal flare}
\Gls{Vimes} asks \Gls{Tantony} to let him chase after \Gls{Wolfg}, and finally catches up to him
at the central square. He drops his crossbow, and takes out a signal flare from the semaphore tower,
and fires it at the werewolf. \Gls{Wolfg} notices how slow the projectile is traveling, and
instinctively catches it in his mouth, as if to taunt \Gls{Vimes}. It then explodes, killing
\Gls{Wolfg}, and \Gls{Tantony} arrives to help \Gls{Vimes} deal with the legal aftermath.

\subsubsection{\Gls{Margo} talks to \Gls{Vimes} about the balance of power in Uberwald}
\Gls{Vimes} is escorted back to the embassy by \Gls{Margo} on her carriage. He suspects that she
helped \Gls{Wolfg} recover, and egged him on to confront \Gls{Angua} at the embassy as soon as
possible. She also talks about her time with \Gls{Vetina}, as \Gls{Vimes} thinks about the danger
of waiting interminable for \Gls{Wolfg} to show up in pursuit of \Gls{Angua}, if he had not received
any help from \Gls{Margo}.

\subsubsection{\Gls{Carrot} and \Gls{Angua} bury \Gls{Gavin}'s corpse, and make peace with his pack}
\Gls{Vimes} attends the coronation, and watches the assembled dwarves sigh in awe as the Throne is
carted out in front of \Gls{RhysR}. Meanwhile, \Gls{Carrot} manages to assert his dominance over
\Gls{Gavin}'s pack when he goes to to bury the corpse with \Gls{Angua}. He reassures her that if
she becomes mentally unstable in the future like her brother, he will come after her with
overwhelming force, to make sure she does not hurt anyone else.

\subsubsection{\Gls{RhysR} gives \Gls{Vimes} and his party some gifts}
After the coronation, \Gls{RhysR} invites \Gls{Vimes} and his retinue to the throne, and offers them
favours. He gifts \Gls{Ramkin} with a silver ring, to mark the occasion of the silver mines being
reopened after many decades. He then asks \Gls{CheeryL} about where she gets her dresses made,
hinting at the fact that he might be a closet female. \Gls{Vimes} is shocked, even as the Low King
gives him a ceremonial axe to maintain as a family heirloom.

\subsubsection{\Gls{Igor} gets his son appointed to \Gls{Vimes}' City Watch}
\Gls{Igor} brings one of his sons to the embassy, hoping for employment in the Ankh-Morpork City
Watch. \Gls{Vimes} is happy to take him on, desperate for the surgical know-how, and chooses to
overlook the breeding experiments jumping around in his trunk. He asks \Gls{Carrot} to go ahead with
\Gls{Angua} and the others, and asks for a message to be sent to the city, informing them that
\Gls{Vimes} and \Gls{Ramkin} would stay in Uberwald for a while longer.

\subsubsection{\Gls{Gaspode} decides to return to Ankh-Morpork, having had enough of Uberwald}
\Gls{Gaspode} hitches a ride on one of the transport barges heading from the Uberwald mountains to
Ankh-Morpork. Meanwhile, \Gls{Carrot} arrives at the Watch House and takes charge of the City
Watch. He laments his decision to leave the City Watch floundering and chase after \Gls{Angua}, and
asks \Gls{Colon} to return to his old position.