\section{Going Postal}


\subsection{}
\subsubsection{\Gls{Moist} tries and fails to escape his jail cell on death row}
A semaphore tower maintenance goes wrong, when a worker loses grip of his rope at the top of the
tower and falls to his death. A month later, \Gls{Moist} waits to be hanged, for crimes committed
under the false name of \Gls{Alfred}. He digs a stone out of the wall, and is dismayed to find the
warden \Gls{Wilkin} looking at him from the other side. The warden tells him that all prisoners were
to be given the illusion of hope per \Gls{Vetina}'s orders, and asks him about where he buried his
treasure.

\subsubsection{\Gls{Trooper} tries to get the hanging to proceed on schedule}
Later in the day, \Gls{Moist} is taken to the hanging platform, where the executioner \Gls{Trooper}
greets him, and asks him to sign the rope so he might sell it to some antique collectors.
\Gls{Trooper} points out the various newspapers in attendance at his hanging, as \Gls{Moist} notices
\Gls{Vetina}'s carriage pull up behind the crowd. He notices \Gls{Vetina}'s clerk fight his way
through the crowd, only to ask why the hanging is being delayed.

\subsubsection{\Gls{Moist} is made an offer he cannot refuse}
\Gls{Moist} is hanged, and wakes up groggily in \Gls{Vetina}'s office a while later. He realizes
that \Gls{Vetina} had arranged for \Gls{Trooper} to apply enough force with the rope only to cause
unconsciousness, and offers him the job of Postmaster General, in exchange for \Gls{Alfred} to be
declared dead throughout the Disc. \Gls{Moist} works out that he has no way to run without being
hunted down, and reluctantly accepts the position.

\subsubsection{\Gls{Vetina} asks \Gls{Moist} to report to his new job at the Main Post Office}
\Gls{Vetina} asks \Gls{Moist} to go to the Head Post Office to report for his new job, and tells him
that a parole officer will be waiting there to keep eyes on him. \Gls{Moist} decides to make a run
for it, and purchases a horse to ride out of the city. He looks at his emergency conman kit,
consisting of some authentic and replica diamonds, as he uses them to scam a greedy onlooker at the
next town. He then thinks about the misleading map that would lead \Gls{Wilkin} on a wild goose
chase, and reminds himself that his buried treasure is waiting to be reclaimed.

\subsubsection{\Gls{Moist} tries to outrun whoever is out to apprehend him}
\Gls{Moist} prepares to make a hasty exit by jumping out of his window at an inn, and is vindicated
when someone barges in through his door at night. The water meant to cushion his fall is missing,
and \Gls{Moist} twists his ankle falling down. He limps to his horse at the stables, and finds its
legs chained when he tries to mount it.

\subsubsection{\Gls{Moist} is dragged back to Ankh-Morpork by \Gls{Pump}}
\Gls{Moist} is dismayed to find that his parole officer is a golem, as his attempts to escape end
with the loss of his makeshift crutch. The golem carries him and his horse back to Ankh-Morpork,
where \Gls{Vetina} greets him once again. \Gls{Vetina} tells \Gls{Moist} that the golem is named
\Gls{Pump}, and the public will be told that it is acting as its bodyguard. \Gls{Vetina} reminds
him that a golem can walk non-stop to the ends of the Disc, making desertion impossible.

\subsubsection{\Gls{Moist} steps into the long-disused Post Office with \Gls{Pump}}
\Gls{Moist} thinks about his ankle, and decides to play along for a while, in order to let himself
gain strength and to come up with an escape plan. At the Post Office, \Gls{Moist} notices the
big motto in front with letters peeling off, and finds a warning pasted on the front door,
denying any inquiries about \Gls{Cake}.

\subsubsection{\Gls{Moist} meets \Gls{Groat} at the Post Office}
\Gls{Moist} learns that the Post Office has been shuttered for twenty years, and finds a mass of
pigeons nesting in the main hall. He notices the overwhelming graffiti on every surface, as an old
man in a ridiculous toupee limps in, introducing himself as Junior Postman \Gls{Groat}. \Gls{Moist}
is glad to learn that he can ask \Gls{Pump} to perform chores, as \Gls{Groat} warns them about the
weakened floorboards.

\subsubsection{\Gls{Moist} meets the other members of the Post Office}
\Gls{Groat} leads \Gls{Moist} to the staff locker room in the basement, which is divided into two
halves by a line extending up the walls and to the ceiling. \Gls{Groat} introduces \Gls{Stanley},
an Apprentice Postman, and the editor of the city's magazine for pin collectors. The elderly cat
inhabiting the post office then walks by, and \Gls{Groat} tells \Gls{Moist} that it is named
\Gls{Tiddl}. \Gls{Moist} is alarmed to see \Gls{Groat}'s natural medicine, including many mild
poisons and dubious home remedies.

\subsubsection{\Gls{Groat} shows \Gls{Moist} the piles of undelivered letters in the building}
\Gls{Pump} digs into the pigeon droppings, and finds a thick layer of letters coating the floor.
\Gls{Groat} stops his fond recollections of the glory days of the Postal Service, and shows the
undelivered mail crammed into every room except the basement itself. \Gls{Groat} claims that this
bypasses the cardinal sin of tampering with mail by destroying it, since a delay was more
justifiable under the old rules.

\subsubsection{\Gls{Moist} ends his day sleeping in his office surrounded by dead letters}
\Gls{Moist} believes that \Gls{Groat}'s story about under-staffing and budget cuts is hiding some
crucial detail, and loses his opportunity to pry further. \Gls{Pump} arrives to escort him to his
office, which is also jammed full of dead letters. \Gls{Pump} explains to him that he was a slave
in an underground mine for two centuries before being liberated by the Golem Rights Movement. As
he settles down to sleep, \Gls{Moist} asks \Gls{Pump} to clear the way to his attached residence
for his next task.

\subsubsection{\Gls{Groat} and \Gls{Stanley} read from the Book of Regulations at night}
\Gls{Groat} and \Gls{Stanley} complete their daily ritual of refilling the ink pots in the sorting
hall, and take some time to look at the God of Post in a weathered tome on the desk. \Gls{Stanley}
complains about voices in the night whispering to him in his dreams, and \Gls{Groat} reminds him
that following the Post Office Regulations would be the surest way to avoid trouble.

\subsubsection{\Gls{Moist} comes up with a plan to win over \Gls{Stanley}}
\Gls{Moist} steps out into the city, when \Gls{Pump} tells him that he can be tracked at all times
by golem magic. \Gls{Moist} heads to a pin shop, and notices the customers obsessing over the
collection of rare pins, and the various books on pin culture. He purchases the amateur magazine
published by \Gls{Stanley}, to the disgust of the store owner.

\subsubsection{\Gls{Moist} buys a rare pin that might capture \Gls{Stanley}'s fancy}
\Gls{Moist} returns to the shop, where the owner \Gls{DaveB} is surprised to see him ask about
specialty pins that might be too valuable to display out front. He purchases one of the rare pins,
as well as several bags containing lucky draws pins, based on what he read in the magazine. As he
steps out of the store, he spots the address on a dead letter, holding the positive reply to a
proposal.

\subsubsection{\Gls{Moist} delivers the reply to \Gls{Parker}'s love letter many decades later}
\Gls{Moist} asks if \Gls{Parker} still lives at the address on the letter, and is pleased to learn
that the family is running a greengrocer's shop, now headed by his son. The son is intrigued to see
the letter dated forty years prior, and calls for \Gls{Parker} to come see it. \Gls{Moist} wonders
how many lives have been affected by the Post Office holding up letters, and returns home for the
day.

\subsubsection{\Gls{Groat} gets his monthly rent from the men on the terrace}
\Gls{Groat} makes the difficult climb to the terrace of the Post Office, to get the rent from the
messenger pigeon business that he has rented the space to. He spots them tinkering with some
clockwork mechanism, and wonders where the pigeons are. They tell him that they are working on a
speedier alternative to the semaphore network, and give him the measly rent money while asking him
how long the new postmaster was going to last.

\subsubsection{\Gls{Moist} talks to \Gls{Adora} about the survivability of golems}
\Gls{Moist} next heads to a run-down neighbourhood and finds the store with Golems for rent or sale.
Inside, he finds the owner \Gls{Adora} cleaning up the broken glass from the latest round of
vandalism. He asks her about the sturdiness of golems, and learns that she is helping them organize
into a self-sustaining trust, that buys them out of their own slave-labor contracts. She hands him
a pamphlet containing the core of golem philosophy, and tells him that the last postmaster was
killed just a few weeks ago.

\subsubsection{\Gls{Vetina} is worried about the semaphore network being interfered with}
In his office, \Gls{Vetina} reads some reports about interruptions in the semaphore network, as
\Gls{Drumk} comes in with the latest results from their surveillance. \Gls{Vetina} asks him to keep
listening, convinced that some actionable evidence will come to light soon. The representatives of
the Grand Trunk Clacks company are then shown into the room with the Lawyer \Gls{Slant} representing
them.

\subsection{}
\subsubsection{\Gls{Vetina} talks to \Gls{Slant} and the owners of the Grand Trunk Company}
\Gls{Slant} introduces the backers of the Grand Trunk network, with \Gls{Stow} and \Gls{Horse} being
the bank representatives funding the company. \Gls{Vetina} takes note of \Gls{Horse}'s insistence
that there was a strict Code of Conduct against people on the managing boards of competing companies
using privileged information. He reminds them of the recent death of \Gls{Dearh}, and wonders if
the rumours of murder might have truth to them.

\subsubsection{\Gls{Vetina} summarizes the recent events surrounding the Grand Trunk Compnay}
\Gls{Vetina} talks about a hostile takeover of the Grand Trunk Company by the investors in front
of him, and the subsequent breakdown in the quality of service, with the banishment of all the
engineers who invented it in the first place. \Gls{Gilt} chimes in with the idea of a free market
being important to the city, and tells \Gls{Vetina} that the customers always have the option of
getting their information by horse instead.

\subsubsection{\Gls{Gilt} and \Gls{Horse} make fun of \Gls{Vetina}'s attempt to bring the Post
    Office back into relevance}
\Gls{Vetina} wonders if the recent accidents are related to the Grand Trunk Company hampering any
efforts at a crowd-funded competitor being set up, as \Gls{Horse} and \Gls{Gilt} remind him of his
folly in reopening the Post Office. They recall the bureaucratic bloat that it had become in its
final days, as \Gls{Vetina} expresses his faith in \Gls{Moist}'s ability to modernize it.

\subsubsection{\Gls{Moist} learns about the rapid deaths of his predecessors at the Post Office}
\Gls{Vetina} asks \Gls{Drumk} to set a spy on \Gls{Horse}, believing him to be the most jittery and
nervous member of the conspiracy. Meanwhile, \Gls{Groat} talks about the string of postmasters dying
in the last few weeks, and causally lets slip the fact that the City Watch has a werewolf on duty.
\Gls{Moist} realizes that it is going to be even easier for them to track him, and tries desperately
to believe that he won't be the next postmaster to die on the job.

\subsubsection{\Gls{Moist} decides to look into the sealed room at the Post Office}
\Gls{Moist} realizes that a room where one of his predecessors died to some industrial accident is
locked away, with the City Watch in possession of the key. He placates \Gls{Stanley}'s PTSD by
giving him the antique pin he had purchased earlier, and is happy to see the boy examining it with
great interest. He then asks \Gls{Groat} to find a crowbar and come with him to the sealed room.

\subsubsection{\Gls{Moist} recovers the letters stolen from the motto of the Post Office}
\Gls{Moist} notices that a barbershop for ladies has stolen the letters from the Post Office motto,
and takes \Gls{Groat} along with him to confront them. \Gls{Groat} is incensed by the theft, and
\Gls{Moist} asks \Gls{Pump} to restrain the old man while he talks to the shop owner. The owner is
fooled into thinking that \Gls{Moist} was sent by \Gls{Vetina} with a negotiated settlement, that
would involve a fine and the return of the stolen letters.

\subsubsection{\Gls{Moist} is invited to \Gls{Parker}'s wedding}
\Gls{Moist} asks \Gls{Groat} to hire the workmen needed to restore the motto, and shows him the
gold paid by the shop owner as penalty for his theft. The crew finish installing the stolen letters,
just as \Gls{Parker} shows up with his son, thanking \Gls{Moist} for reuniting him with his
long-lost love. He insists on having \Gls{Moist} be the guest of honor at the wedding, as a woman
from the gathering crowd mumbles something about the Post Office being cursed.

\subsubsection{\Gls{Moist} sees a murderous trance come over \Gls{Stanley} when he manhandles
    \Gls{Groat}}
\Gls{Moist} takes \Gls{Groat} inside the Post Office, and offers him the promotion that he so
desperately wants, in exchange for the information that he is concealing. \Gls{Stanley} enters one
of his trances, and threatens \Gls{Moist} with death unless he lets \Gls{Groat} go. \Gls{Moist}
distracts him once again with a replica pin, and asks \Gls{Pump} if he can order him to sabotage his
own body.

\subsubsection{\Gls{Moist} tries to order \Gls{Pump} to sabotage itself}
\Gls{Pump} reminds \Gls{Moist} that he must let go of any intent to escape his sentence, and plays
back a voice recording of \Gls{Vetina}, which states that he cannot ask \Gls{Pump} to harm himself.
\Gls{Moist} is horrified to see \Gls{Pump} recite the full list of his crimes, and then tell him
how many deaths he caused indirectly by bankrupting people on the brink.

\subsubsection{\Gls{Alice} asks \Gls{Grandad} about the repeated messages naming \Gls{Dearh}}
\Gls{Alice}, a child learning the semaphore operation at the tower next to Bonk, finds an
unauthorized maintenance message coming over the network, without any encryption. She works
alongside \Gls{Roger}, a younger boy just starting to learn the trade, and \Gls{Grandad}, the
master of the tower licensed by the company. \Gls{Grandad} explains that the name of \Gls{Dearh}
is kept circulating in the tower network by the linesmen, as a tribute to his life spent on the
towers.

\subsubsection{\Gls{Horse} goes to \Gls{Gilt}'s manor to discuss his next move}
\Gls{Stanley} is busy arranging his pin collection, as \Gls{Groat} mumbles about testing the
new Postmaster's worthiness. Meanwhile, \Gls{Horse} enters \Gls{Gilt}'s house, and finds the
portraits of his newly appointed ancestors in the waiting room. He thinks about the novelty of using
the newfound bounty to purchase a pedigree, complete with long line of ancestors, manor house, and
\Gls{IgorG}.

\subsubsection{\Gls{Horse} talks about being tailed and hiding their financial fraud}
\Gls{Horse} recalls how suddenly \Gls{Gilt} had turned up in Ankh-Morpork, and the way his parties
had allayed any suspicion about his past among the citizens of high society. He finds \Gls{Alph},
the pet cockatoo repeating some lines in a closed cage, just as \Gls{Gilt} arrives from his ongoing
party, and reassures him that Sergeant \Gls{Colon} is not a spy to be worried about.

\subsubsection{\Gls{Horse} talks about the petty scams being run by their co-owners}
\Gls{Horse} is dismayed by the revenue officers checking in on the Grand Trunk Company's books,
and worries that they will find out they bought the company with its own money. \Gls{Gilt} reminds
him that fiat currency is a deception by its very definition, and bemoans the naked market
manipulation being done by their partner \Gls{Greeny} in Lancre.

\subsubsection{\Gls{Horse} is escorted home by \Gls{IgorG}, after he hands over the incriminating
    ledger to \Gls{Gilt}}
\Gls{Horse} gives \Gls{Gilt} the ledger containing all of their fraudulent transactions, as he gets
drunk on the brandy from the party. \Gls{Gilt} is privately appalled at the idea of recording their
crimes, and is relieved to have the evidence in his possession. He asks \Gls{IgorG} to deliver
\Gls{Horse} to his home, and asks for \Gls{Gryle} to be summoned.

\subsubsection{\Gls{Moist} decides to investigate the semaphore tower on the Post Office roof}
\Gls{Moist} watches the fleet of Postal coaches operating from the back of the Post Office, now
converted to ferry passengers instead of mail. He notices the semaphore tower installed on the
roof of the Post Office, and notices someone ducking in when he spots them operating it. He wonders
if the space has been rented out to a local semaphore company, and decides to climb the old
staircase leading to the higher floors.

\subsubsection{\Gls{Moist} hallucinates a vision of the Post Office in its heyday}
\Gls{Moist} climbs the precarious stairs to reach the fifth and topmost floor, noticing the
corridors jammed with letters come undone in a landslide below him. He then realizes that he is
seeing a vision of the Post Office in its heyday superimposed over the present ruins, and even
hears faint murmurs of the employees hard at work.

\subsubsection{\Gls{Moist} feels a ghost walk through him at the fifth floor of the Post Office}
\Gls{Moist} sees the Postmaster General in the past walk into the sorting hall, and command the
delivery of the mail for the day, as if he were a general signaling the start of a march. He is
then nauseated by a ghost walking straight through him, and realizes that one of his predecessors
found this experience so disorienting that he stepped onto a nonexistent balcony, and plunged to
his death.

\subsubsection{\Gls{Moist} is rescued from a massive pile-up of letters by \Gls{Pump}}
\Gls{Moist} gets caught in an avalanche of letters, and is buried under a huge heap. He sees the
words in those dead letters start to appear across his vision, and believes them to be alive, just
as \Gls{Pump} digs him out of the deep pile. \Gls{Moist} is afraid of the letters haunting the
building, until \Gls{Pump} reminds him that he is technically just some pottery with added magic.
\Gls{Stanley} walks into the office to tell \Gls{Moist} that a group of men want to see the new
Postmaster.

\subsubsection{\Gls{Moist} is blindfolded and subjected to a hazing}
\Gls{Stanley} tells \Gls{Moist} to remain calm, as the gathered men pull a hood over his head, and
lead him down the front stairs of the Post Office. He hears them talk about some sort of test, and
works out that they must be a secret society within the Post Office, intent on hazing the newcomer.
The three men take him to the sorting hall, where he recognizes \Gls{Groat}'s voice talking to
someone called the \Gls{Master}.

\subsection{}
\subsubsection{\Gls{Groat} and the postmen subject \Gls{Moist} to the final test}
\Gls{Groat} gives \Gls{Moist} the hints he needs to complete the various tasks set forth by the
\Gls{Master}, as part of inducting him into the Post Office. For the final test, \Gls{Moist} notices
the postmen flee the room after releasing some Uberwaldian dogs, to test him. He recognizes them
as being breeds from his ancestral homelands, and uses the old tongue to give them the command to
sit down.

\subsubsection{\Gls{Moist} sees the postmen of the secret society in the light}
\Gls{Moist} is happy to see that the postmen in mysterious robes have finally accepted him as their
Postmaster, as \Gls{Pump} walks in through the front door. \Gls{Moist} notices \Gls{HarryK}'s men
waiting with cages for the dogs, and works out that they were guard dogs rented out by the postmen
for the ritual. The \Gls{Master} tries to tell \Gls{Groat} that the semaphore network was the
death-knell for the Post Office, and his belief in a messiah that would revitalize the place was
wishful thinking.

\subsubsection{\Gls{Moist} is accepted by the dead letters as the new Postmaster General}
\Gls{Pump} walks in with a box holding the ceremonial helmet and boots of the Postmaster General,
as \Gls{Moist} tells \Gls{Groat} that he had caused a major shifting of the debris last night.
\Gls{Groat} is relieved that the box holding the uniform has finally been found, as more letters
start to fall from the higher floors. In the darkness, \Gls{Moist} sees the letters beg him to
restore the Post Office to its former glory, and to deliver them unto their intended recipients.

\subsubsection{\Gls{Moist} dons his new outfit as Postmaster General}
The next day, \Gls{Pump} wakes \Gls{Moist} up, and helps him recollect the oath he had taken in
a trance, to restore the Post Office, and install the statue of the Messenger God in the sorting
hall. He then shows the suit of imitation gold made by one of his fellow golems, and \Gls{Moist}
is pleased to see how conspicuous it will make him look in the city streets.

\subsubsection{\Gls{Groat} shows \Gls{Moist} the magical letter sorting machine}
\Gls{Moist} sends the retired postmen volunteering for the secret society into the city, with a load
of forty-year-old letters to deliver. He asks \Gls{Groat} to take him to the sealed underground
chamber, and is shown the magical sorting machine, which began to spit out letters from other
alternate timelines, or from different points of time. \Gls{Groat} explains that the most of the
letters clogging up the Post Office were not the ones brought in for sorting, and were instead the
magical ones spit out by the sorting machine.

\subsubsection{\Gls{Moist} comes up with one-time-use stamps for an inter-city postal service}
\Gls{Moist} decides to use one-time stamps, and asks \Gls{Groat} to summon a salesman from the
fancy print shop that catered to the banks in the city. He decides to revive the inter-city mail
service first, taking advantage of the decline in the semaphore service, and decides to lower prices
temporarily to draw in customers.

\subsubsection{\Gls{Moist} wishes to hire some golems as postmen, and goes to \Gls{Adora}'s shop}
\Gls{Moist} realizes he needs to expand his fleet, and heads to \Gls{Adora}'s shop, where she offers
him four golems for hire. She tells him that \Gls{Angha} is the only one that is capable of speech
at the moment, and asks him to wait while she brings them out of the cellar. He learns that all
working golems, including \Gls{Pump}, had one day off every week, to further their liberation
movement and to remind themselves that they were not mere tools.

\subsubsection{\Gls{Stanley} seeds the idea of stamps as currency in \Gls{Moist}'s mind}
\Gls{Stanley} makes an offhand remark about the new stamps being a form of fiat currency if they
were impossible to forge, and \Gls{Moist} sees the nucleus of a new scam forming in his mind. He
makes some prototype designs for the new stamps, as \Gls{Angha} recounts his past as a messenger for
civilizations many thousands of years ago. \Gls{Groat} is delighted to have such an ancient being
joining their secret society, and welcomes him as Extraordinarily Senior Postman.

\subsubsection{\Gls{Moist} rents out the first set of golem postmen}
\Gls{Moist} asks \Gls{Adora} out for dinner, and is dismayed to realize that she sees right through
his charade of sincerity and goodwill. She promises to come back with the rest of the golems in
her roster, as \Gls{Stanley} finishes painting the postman golems with the traditional blue and
gold of the Post Office.

\subsubsection{\Gls{Moist} steals some stamp paper from \Gls{Spools}, as he places his first order}
At the specialty print shop of Mr. \Gls{Spools}, \Gls{Moist} explains his requirements for the
stamps, and shows them the perforated paper made by \Gls{Stanley} to hold his pin collection, as a
blueprint for the sheets of stamps that can be easily torn off one at a time. \Gls{Spools} is
amused by \Gls{Moist}'s insistence on speed over precision, and agrees to print up a batch of
low-denomination stamps the next day. \Gls{Moist} swipes some sheets of the special stamp paper off
\Gls{Spools}' desk, when they are all busy marveling at the prototype stamps.

\subsubsection{\Gls{Sacha} interviews \Gls{Moist} about the delivery of the dead letters}
Back at the Post Office, \Gls{Moist} stashes the stolen stamp paper, and is ushered to the lobby,
where \Gls{Sacha} is waiting to interview him. \Gls{Groat} tells him that a long-delayed will was
delivered today, leading to a fight between two siblings over a stolen inheritance. \Gls{Sacha}
asks him if he is going to deliver all of the backlogged letters, and he reminds her of \Gls{Parker}
marrying his old lover as a result of the letters.

\subsubsection{\Gls{Moist} tries to retake control of the interview from \Gls{Sacha}}
\Gls{Moist} shows \Gls{Sacha} his prototype stamps, and tells her that the semaphore system has
become so impersonal, expensive and unreliable, that an opportunity is now open for the Post Office
to be revived. He diverts her idea of including his picture on the front page of the Times, with
a lofty speech about establishing a Postal Service that would deliver to all throughout the
continent, and shows her the new letters that people have been handing to the postmen.

\subsubsection{\Gls{Moist} reassures \Gls{Sacha} that he has the best interests of the Post Office
    at heart}
\Gls{Moist} brushes off the idea of any danger to his life, when \Gls{Sacha} points out the four
other postmasters who had died in the last few months. He learns that Professor \Gls{Pelc} at the
Unseen University has written a book on the sentience of messages trapped in large numbers in one
place, and wishes \Gls{Sacha} the best of luck with the photo spread of golems painted in Post
Office colors.

\subsubsection{\Gls{Moist} finds \Gls{Pelc} at the University}
\Gls{Moist} goes to the University Library, and is beckoned into a seat strapped to some sort of
magical contraption. The machine whirs and squeaks, with \Gls{Moist} feeling the sensation of being
slapped with a fish, and is pleased to find \Gls{Pelc} looking at him beside the \Gls{Libra} as he
is being unstrapped.

\subsubsection{\Gls{Pelc} reassures \Gls{Moist} about the effects of undelivered letters}
\Gls{Pelc} quickly catches on to \Gls{Moist}'s worries about the hallucinations, and explains that
the strange phenomena are the words trying to influence any minds in their vicinity into delivering
them to their recipients. To find out where the fancy chandeliers in the Post Office ended up,
\Gls{Pelc} takes \Gls{Moist} to his predecessor's storage room, where many senior faculty choose to
be confined to a pocket dimension with time dilation.

\subsubsection{\Gls{Moist} goes to the Palace when he is summoned by \Gls{Vetina}}
\Gls{Moist} learns that even delivering some of the backlogged letters will cause a sharp decrease
in the hallucinations, goes to bed only to be haunted by the voices of old wizards with their
non-stop chattering. He is woken up by \Gls{Pump}, who informs him of the huge crowd at the front
door, and taken to the Palace by the hidden exit at the stables.

\subsubsection{\Gls{Vetina} congratulates \Gls{Moist} on his first few successes as Postmaster}
\Gls{Drumk} shows \Gls{Moist} the cartoon on the front-page, making fun of the stamp bearing
\Gls{Vetina}'s face, as he is summoned into the central office. \Gls{Vetina} then shows him the
Grand Trunk semaphore towers lying in disrepair, and the queue forming outside the Post Office in
response to the unfulfilled demand for inter-city mail. He congratulates \Gls{Moist} on the stamp
system, as \Gls{Drumk} informs him of the tragic demise of \Gls{Horse}.

\subsubsection{\Gls{Moist} decides to make the first mail delivery to Sto Lat}
\Gls{Moist} spots \Gls{Spools} waiting at the front door of the Post Office with the first delivery
of stamps, and decides to undercut the semaphore prices to attract customers. He asks \Gls{Stanley}
to fetch Mr. \Gls{Hobson}, owner of the city's largest horse rental service, and asks \Gls{Groat} to
be acting Postmaster as he takes the first mail delivery to Sto Lat by himself. \Gls{Drumk} pushes
his way through the crowd to hand him an envelope bearing \Gls{Vetina}'s stamp, to be delivered to
the mayor of Sto Lat.

\subsubsection{\Gls{Moist} prepares to deliver mail to Sto Lat by horse}
\Gls{Moist} watches \Gls{Hobson} arrive with news of a special horse ready for his ride to Sto Lat.
He decides to take up \Gls{Hobson} on his boast, and asks for the saddle to be removed, in order to
lighten the burden on the horse. \Gls{Hobson} is horrified by the idea of \Gls{Moist} riding such
an unruly horse, and begs to offer a better-behaved alternative.

\subsubsection{\Gls{Moist} leaves on horseback for Sto Lat}
As \Gls{Moist} mounts \Gls{Boris} the horse with his bag of mail, \Gls{Sacha} asks him if he intends
to deliver the semaphore messages as well. \Gls{Moist} answers diplomatically, wishing the semaphore
company the best of luck in their repair work, and is happy to see \Gls{Adora} in the background
watching the show. \Gls{Boris} is released from his tethers, and rides out of the city, with
\Gls{Moist} trying his best to hang on.

\subsubsection{\Gls{Moist} makes it to Sto Lat with the first express mail delivery}
\Gls{Moist} spots a heavily damaged semaphore tower a third of the way to Sto Lat, and wonders if
even longer journeys could be viable using the passenger wagons currently running from the Post
Office stables. He finally arrives at the town hall of Sto Lat, and asks for a cold bath as
\Gls{Boris} settles down at a watering hole for horses. He tells the mayor to fill his return bag
with mail for Ankh-Morpork, and is surprised to see the undelivered semaphore messages also being
included in the mail.

\subsection{}
\subsubsection{\Gls{Moist} makes the return journey to Ankh-Morpork, on a replacement horse}
The mayor of Sto Lat wishes for a set of stamps bearing the face of the local sovereign, and
\Gls{Moist} realizes that vanity stamps are a potential gold mine. He returns to Sto Lat on a
replacement horse, after the mayor tells him that he will have \Gls{Boris} confined for later
delivery. \Gls{Groat} welcomes him at the Post Office, and shows him the greatly expanded operation
in the main hall, including deliveries to cities further off.

\subsubsection{\Gls{Moist} sees the repercussions of his latest interview with \Gls{Sacha}}
\Gls{Moist} asks \Gls{Groat} to look into the wagons as a means of delivering mail to faraway
cities overnight, and asks for someone else to take over the express run to Sto Lat. He is
flummoxed by Ms. \Gls{Macca} asking for one of the golems to be given a female name and attire, so
that it might clean out the women's bathroom with no breach of decorum. \Gls{Moist} hastily concedes
her demands, and looks at the special edition of the Times, carrying a photo of him riding
\Gls{Boris} out of the city.

\subsubsection{\Gls{Moist} makes further plans to expand the Post Office}
\Gls{Moist} decides to impersonate \Gls{Gilt} in a letter to the manager of a fancy restaurant, so
that he can have dinner there with \Gls{Adora}. He finishes the forged letter, and hands it off to
\Gls{Stanley}, after elevating him to the farcical position of Chief of Stamps. \Gls{Groat} comes
in with an anonymous letter warning of the breakdown of the semaphore line to Pseudopolis to happen
some time the next morning.

\subsubsection{\Gls{Gilt} asks \Gls{Gryle} to dispose of \Gls{Moist}}
\Gls{Gryle}, the hitman under retained by \Gls{Gilt}, is told that \Gls{Moist} is becoming a
nuisance. \Gls{Gryle} asks for a payment in gold, and states that encrypted wire transfer using
the semaphore network can no longer be trusted. \Gls{Gilt} tells him that the gold will require a
few days to be ready, and suggests that the dead letters in the post office are conveniently
flammable.

\subsubsection{\Gls{Moist} negotiates with \Gls{HarryU} and \Gls{JimU} about the mail coaches}
\Gls{Moist} goes to the makeshift office set up by \Gls{HarryU} and \Gls{JimU}, the operators of the
mail coach service headquartered in the Post Office stable. He intimidates them by making
\Gls{Gladys} take wheels off the carriages, when they do not respond to polite requests. He gets
them to cooperate by reminding them of the foul play that the Grand Trunk Company will engage in,
and reminds them that a lot of extra revenue was on the table if they took the mailbags on the trips
along with the usual load of passengers.

\subsubsection{\Gls{JimU} and \Gls{HarryU} talk about the exploitative practices of the Grand Trunk
    Company}
\Gls{JimU} mentions in passing that the Grand Trunk Company has been losing too many maintenance
workers of late, always in the hour before dawn when the daily repair jobs took place. \Gls{JimU}
talks about the rumours of a semaphore tower sending out a message long after all of its workers
were killed performing maintenance, as \Gls{Moist} insists on running a service to Pseudopolis that
night. After \Gls{Moist} leaves in a hurry to keep his dinner date, the brothers wonder if the
semaphore line to Pseudopolis is due to break down.

\subsubsection{\Gls{Moist} meets up with \Gls{Adora} at the Mended Drum}
\Gls{Moist} goes to the Mended Drum, and steps past the mobs planning out the strategy for their
next bar fight. He finds \Gls{Adora} seated at the back, and tells her that he has a reservation
for the most exclusive restaurant in the city. She is impressed, and immediately asks him who he
had to con in order to acquire the table.

\subsubsection{\Gls{Adora} talks about her father and brother, victims of \Gls{Gilt}'s takeover}
\Gls{Adora} talks about her father founding the Grand Trunk Company along with a bunch of talented
engineers, and of how \Gls{Gilt} had performed a hostile takeover using his influence over the
banking system. She talks about her father going catatonic at the loss of his life savings, and the
suspicious death of her brother \Gls{Dearh}.

\subsubsection{\Gls{Stanley} faces \Gls{Gryle} after the Post Office is set ablaze}
At the Post Office basement, \Gls{Stanley}'s inspection of the faulty prototype stamps is
interrupted by a strange voice in the dark, that seems to be disembodied. He notices a half-eaten
pigeon land next to the door, as \Gls{Gryle} spreads lamp oil over the heaps of letters.
\Gls{Stanley} runs into the Great Hall to find the fire spreading through the letters, and sees
\Gls{Gryle} swooping towards him, with \Gls{Groat} lying curled up in the path of the flames.

\subsubsection{\Gls{Moist} meets \Gls{Gilt} in the expensive restaurant}
\Gls{Moist} sees \Gls{Gilt} walk into the restaurant after he is seated with \Gls{Adora}, and asks
her to loosen her grip on the dining knife. To his shock, \Gls{Gilt} walks over to their table, and
thanks him for delivering backlogged semaphore messages. \Gls{Moist} sees a fellow conman in
\Gls{Gilt}'s eyes, and sees a moment of shock in his face when they shake hands. A while later,
the words trapped in the Post Office send a vision of burning letters to \Gls{Moist}, causing him
to run out in search of the fire service.

\subsubsection{\Gls{Moist} reaches the Post Office as the fire starts to spread}
\Gls{Moist} reaches the front door of the Post Office with \Gls{Adora}, and notices that the fire
has not spread to the inhabited half yet. He runs into the basement, to find \Gls{Stanley} calmly
organizing the box of stamps, as well as the cash register. \Gls{Moist} notices \Gls{Groat} lying
unconscious on a nearby bed, as \Gls{Stanley} talks about defending himself against a vampire
that attacked him in the Main Hall.

\subsubsection{\Gls{Moist} rescues \Gls{Groat} and \Gls{Stanley} from the burning Post Office}
\Gls{Moist} asks \Gls{Adora} to take \Gls{Groat} to the Hospital, and insists that the puncture
wounds are the results of a beam with nails falling on top of him. \Gls{Adora} plays along for the
moment, and is shocked to see him preparing to go into the building to look for\Gls{Tiddl}. He
spots \Gls{Tiddl} and follows it to the cellars, where it crouches underneath the sorting machine.

\subsubsection{\Gls{Moist} throws \Gls{Gryle} into the sorting machine}
\Gls{Moist} realizes that the wooken chair he is holding for self-defense isn't going to be much
use when \Gls{Gryle} sneaks up on him from behind. As \Gls{Gryle} fights off the food poisoning and
smoke-induced disorientation, \Gls{Moist} presents him with an easy stationary target. \Gls{Gryle}
pounces, only to be tackled by a shoulder charge, and pushed into the multidimensional core of the
sorting machine, which melts him into soup.

\subsubsection{\Gls{Moist} comes out of the building as the golems extinguish the fire}
\Gls{Moist} grabs \Gls{Tiddl} and prepares to exit the Post Office with his golden suit. \Gls{Pump}
and the other golems manage to clear a way out for \Gls{Moist}, with \Gls{Angha} losing his life in
the process. He is welcomed by \Gls{Death} to an afterlife that has no orders to follow, and is
finally at peace.

\subsubsection{\Gls{Moist} gives the City Watch a story about the fire being accidental}
A spell of heavy rain puts the fire to rest, as \Gls{Carrot} and \Gls{Angua} arrive at the Post
Office to interview \Gls{Moist}. He decides to call the flying monster a freak pigeon, and blames
the fire on an unfortunate accident. He realizes that voicing his suspicions about \Gls{Gilt} will
only lead to more trouble with the reconstruction efforts, and notices \Gls{Angua} wing at him in
werewolf form as she leaves.

\subsubsection{\Gls{Moist} comes up with a new scam involving the city's temples}
As he looks at the steaming rubble around the Post Office, \Gls{Moist} has an idea about using
religion to collect the money needed for repairs, and even hit back at \Gls{Gilt}'s company
eventually. He asks \Gls{Adora} to adopt a stage name, and suggests the name \Gls{Spike}, as some
musicians respond to his call for ambient music. After dancing for a while with \Gls{Adora},
\Gls{Moist} goes to the nearest major temple, with a letter addressed to \Gls{Offler}.

\subsubsection{\Gls{Moist} prays for cash at some temples in Ankh-Morpork}
\Gls{Moist} asks the night-shift priest for the well-being of \Gls{Groat}, who is undergoing
treatment at the Hospital, and then makes a prayer for a large sum of cash. He repeats the same
routine at a few more temples, and returns to the Post Office, where \Gls{Aggy} is surprised to
learn that the place will open for business in spite of the fire.

\subsubsection{\Gls{Moist} waits for the semaphore to Pseudopolis to break down, per the tipoff}
\Gls{Moist} tells \Gls{JimU} to be ready with the Pseudopolis carriage, and remains confident that
he will have a bag full of mail for delivery a few hours after opening time. Later in the morning,
\Gls{Macca} runs into the Post Office, and despairs at the loss of her dream job. \Gls{Moist}
reassures her about the money needed for rebuilding being a few days' business away, as \Gls{Aggy}
walks in with confirmation of the semaphore breaking down.

\subsection{}
\subsubsection{\Gls{Moist} declares a deep discount for mail to Pseudopolis}
\Gls{Moist} makes a bold declaration to the masses gathered in front of the Post Office, telling
them that the price of mail delivery would be deeply discounted for the morning. \Gls{Stanley}
tells him that people have started to send stamps to themselves as a hobby, and \Gls{Moist} starts
to work out the royalty payments that will come from partnering with \Gls{Spools}.

\subsubsection{\Gls{Moist} is taken to the Palace for a surprise meeting with \Gls{Vetina}}
\Gls{Moist} is taken to \Gls{Vetina}'s office and asked about the events of the day, involving
a sudden epiphany about the location of buried treasure. \Gls{Moist} claims that divine intervention
provided him the location, and conceals the fact that the chest was simply the nest egg he had
refused to divulge to his jailers. \Gls{Vetina} suggests that \Gls{Moist} pay a percentage of the
find to the local temples, in order to placate the priests, and use the rest for the public good.

\subsubsection{\Gls{Moist} goes to the hospital to see \Gls{Groat} being treated}
\Gls{Moist} is saddened to learn that all of the recovered treasure will have to be spent for the
Post Office repairs, as \Gls{Vetina} talks about the priests who are overjoyed at their gods
seemingly granting a miracle. \Gls{Moist} then heads to the Hospital, where \Gls{Groat} is angry
at the nurses for bathing him, and getting rid of his home remedies. \Gls{Moist} meets with
\Gls{Lawn}, who is impressed by \Gls{Groat}'s resilience, and is desperate to discharge him as soon
as possible, to save the nursing staff's sanity.

\subsubsection{\Gls{Pony} answers the inquiries about the time needed to restore the Grand Trunk
    towers}
In \Gls{Gilt}'s meeting room, \Gls{Greeny} point out the prescience of \Gls{Moist}'s discount mail
services, that always seem to be ready in times of semaphore breakdown. He suggests increasing the
repair budget, as \Gls{Pony}, the chief engineer of the Grand Trunk Company reminds them of the
insufficient manpower. \Gls{Stow} asks him about the estimated time needed for repairs, and is
shocked to learn that nine months of complete shutdown is the smallest amount of time needed.

\subsubsection{\Gls{Pony} is sent away while \Gls{Gilt} asks his board members for more funds}
\Gls{Pony} reminds the board about their downsizing spree, and of how the craftsmen would never
come back for increased wages, out of sheer pride. \Gls{Gilt} sends \Gls{Pony} away, and talks to
the rest of the board, fully aware of the fraudulent ways in which they raised the cash needed to
become investors. He reveals the presence of \Gls{Horse}'s ledger, secreted away in some vault, and
asks them to secure another round of funding by embezzling the money from their banks.

\subsubsection{\Gls{Gilt} asks \Gls{Pony} to come up with a stop-gap solution for the next year}
The board members are persuaded to provide twice the amount budgeted by \Gls{Pony}, as \Gls{Gilt}
makes a spirited speech outlining their mission to revitalize the semaphore network. After the
investors leave, \Gls{Gilt} invites \Gls{Pony} back in, and tells him that the board can only
provide a third of the budget he estimated. He offers \Gls{Pony} a small pay raise, and asks him to
provide a band-aid solution that can last them a year, before breaking down.

\subsubsection{\Gls{Gilt} starts questioning his own sanity}
\Gls{Gilt} asks \Gls{IgorG} if he is insane to offer the greedy young men a chance to throw their
money away in one scheme after another. \Gls{IgorG} thinks about making his escape in time,
believing that \Gls{Gilt} is reaching the natural end of his lifespan as a fraudster. Meanwhile,
\Gls{Moist} oversees the rebuilding efforts all through the night, starting with the surveyors
taking measurements.

\subsubsection{\Gls{Adora} and \Gls{Moist} collect the prayers from the citizens}
\Gls{Adora} helps \Gls{Moist} sort through the letters addressed to him, asking for desperate
prayers to be delivered to the various gods in the city. She asks him to take the letters to the
appropriate temples, and fulfil the promise of the stamp system. \Gls{Groat} walks in with a copy
of the times, bearing \Gls{Gilt}'s new mission on the front page.

\subsubsection{\Gls{Moist} reads the puff piece by \Gls{Gilt} praising the Grand Trunk repair plan}
\Gls{Moist} reads the front-page piece by \Gls{Gilt}, and realizes that the Grand Trunk Company has
become too big to fail. He works out that \Gls{Gilt} will force more rounds of funding until the
underlying system is close to collapse, and then buy it at bargain prices using another shell
company. \Gls{Moist} learns that \Gls{Adora} lost her job at a bank, for letting some of his
forged money orders through. He decides to go the Times office, and stop the press with a front-page
story of his own.

\subsubsection{\Gls{Moist} faces \Gls{Vetina} after issuing a preposterous challenge to the
    Grand Trunk Company}
\Gls{Moist} is woken up at noon by \Gls{Vetina}, who asks him what plan he had in mind when
issuing the front-page challenge to the Grand Trunk Company. The Times had printed the challenge as
a test of speed in carrying a secret message to Genua, a city two months away by coach, but only
a few hours away by semaphore.

\subsubsection{\Gls{Moist} learns about the betting pool in his favour for the race to Genua}
\Gls{Moist} decides to set off on the race to Genua the next night, and asks \Gls{JimU} to arrange
the best horses possible at every leg of the ride until Bonk. \Gls{Stanley} shows off the latest
novelty stamps to \Gls{Moist}, and tells him that he is participating in the betting pool, where the
bookies are offering the Postal Service better odds. He calls for \Gls{Groat}, who is managing the
pot, and asks him how they have so much faith in the Post.

\subsubsection{\Gls{Gilt} and \Gls{Pony} tell the board of investors about their plan for the race
    to Genua}
\Gls{Groat} remains optimistic about \Gls{Moist}'s abilities, and fully believes that the treasure
chest was divine intervention. Meanwhile, \Gls{Gilt} reassures his board of investors that
\Gls{Moist} has no plan to back up his challenge, and suggests they shore up the semaphore line to
Genua just to be safe. \Gls{Pony} explains the safety measures that will be in place when the race
starts, and \Gls{Gilt} assures the board that the chief engineer has the situation under control.

\subsubsection{\Gls{Moist} reveals his past to \Gls{Adora}, including the faked hanging}
\Gls{Pony} mentions in passing that some students at the University have found a way to construct
messages that harm the tower equipment in the process of transmission, just by virtue of their
content. Meanwhile, \Gls{Moist} takes \Gls{Adora} to a cafe, and tells her about his past as a
con-man, and reminds her that he has no plan for the race. She suggests cryptically that he go to
the Post Office roof and offer a sincere prayer.

\subsubsection{\Gls{Moist} goes to the roof of the Post Office}
\Gls{Macca} expresses some doubts about hiring dwarf postmen, and \Gls{Moist} quickly reminds her
that some tolerance in the short term will mean more control for her in the design of the new Post
Office Building. She salivates at the power on offer, and relents, to go help \Gls{Groat} in the
hiring process. At dusk, \Gls{Moist} climbs up to the roof, and sees the central semaphore tower
busy at work, receiving messages from all around the city.

\subsubsection{\Gls{Moist} talks to the three semaphore hackers}
\Gls{Moist} kneels down in prayer, and sees three figures approach him, calling themselves friends
of \Gls{Adora}, who were tenants living on the roof before the fire. \Gls{Moist} quickly works out
that the three of them are the rogue signalers who sent him the tipoffs about semaphore towers
breaking down. The three of them explain to \Gls{Moist} that they were able to send their own
messages through the semaphore network using some exploits, which have now been rectified by
\Gls{Pony}.

\subsubsection{\Gls{Moist} comes up with a plan to sabotage the Grand Trunk Network}
The three hackers tell \Gls{Moist} that they were friends of \Gls{Dearh} and were working on the
improved semaphore system to replace the Grand Trunk, before his suspicious death. The four of them
decide to work on a prototype message that can destroy every tower it passes through, provided they
can get it onto the network using the correct encryption.

\subsection{}
\subsubsection{\Gls{Moist} escorts the hackers to the ruined stone tower on the path to Sto Lat}
\Gls{Moist} takes the three hackers to the abandoned stone tower halfway to Sto Lat, and lets them
set up an impromptu semaphore station on top. They tell him that the stone tower was rejected as
the a semaphore station earlier because of the residual magic in it from a wizarding war a long time
ago.

\subsubsection{\Gls{Ridcu} decides on the message to be used for the race to Genua}
\Gls{Stibb} shows off \Gls{Hex}'s new real-time phasing spell, as he plays billiars on \Gls{Ridcu}'s
cluttered table. \Gls{Ridcu} decides to have the racers send the contents of a magical textbook to
Genua, where \Gls{Devious} is performing studies as a transfer student. \Gls{Ridcu} asks for
\Gls{Devious} to be contacted immediately, before the race is set to start.

\subsubsection{\Gls{Moist} has a dream about the hackers successfully taking down the semaphore
    towers}
The hackers start to take down towers on the network using a malicious message, designed to harm the
equipment in a way that would require several days to repair. The layoffs mean that the towers
don't have maintenance men on hand to identify and strip such messages from the stream. \Gls{Moist}
wakes up at noon, realizing that what he saw was just a dream, and believes that real life will not
be so rosy. \Gls{Pump} tells him that they race will start in front of the University.

\subsubsection{\Gls{Moist} pores over the ledgers kept by \Gls{Adora}'s father}
\Gls{Moist} has an epiphany about how he can ruin \Gls{Gilt}'s reputation and rob him of his
social status. He goes to \Gls{Adora}'s house and asks to see the paperwork kept by her father, from
the time of the hostile takeover by \Gls{Gilt}. He returns to the Post Office in the evening with
some scribbled notes, and spots \Gls{SaneA} asking for a small delay in the race. He tells
\Gls{Moist} that they need an hour of darkness to ensure they are not spotted on the stone tower,
as they work their hack.

\subsubsection{\Gls{Moist} makes a show of letting the semaphore have a hour's lead to encode the
    textbook}
At the University entrance, \Gls{Ridcu} chastises \Gls{Moist} for being late, and hands him the
textbook that is to be sent to Genua. \Gls{Moist} tears off a few chapters from the textbook
containing fancy diagrams, and makes a grand gesture of offering the semaphore a head start of one
hour. \Gls{Pony} is flustered by the idea of coding and decoding the elaborate diagrams, even
though the subsequent transmission will be very fast. Meanwhile, \Gls{IgorS} writes a note for
\Gls{Gilt} and deserts his job at the manor.

\subsubsection{\Gls{Gilt} and \Gls{Moist} ask for each other's backup plans to be removed from play}
\Gls{Gilt} walks over from his carriage, and asks \Gls{Moist} to start his journey immediately.
\Gls{Moist} notices \Gls{Sacha} waiting with her notepad, and remains diplomatic in his response.
\Gls{Gilt} asks \Gls{Ridcu} to have the painted broomstick on \Gls{JimU}'s cart removed, when
\Gls{Moist} claims it is a backup in case the roads prove too dangerous in the mountains.
\Gls{Moist} is happy to see his misdirection pay off, and asks for the backup horses at each
semaphore tower removed in the spirit of fair play.

\subsubsection{\Gls{Moist} forces \Gls{Gilt} to enter a substantial cash bet for the race to Genua}
\Gls{Ridcu} agrees to both requests as the referee, and tells \Gls{Moist} in private that he is
aware of the broomstick being a phony. \Gls{Moist} decides to unsettle \Gls{Gilt} further, and
suggests a personal bet cash bet between the two of them. He notices \Gls{Gilt}'s signs of breakdown
as he tries to politely rise to the challenge.

\subsubsection{\Gls{Moist} asks to be dropped off at the stone tower where the hackers are set up}
\Gls{Moist} asks \Gls{JimU} to drop him off at the stone tower midway to Sto Lat, and is reassured
by the mercenaries hiding inside the undercarriage. He tells \Gls{JimU} that the part of the book
he tore off to give to \Gls{Pony} contained all the color diagrams, which were the most difficult to
encode.

\subsubsection{\Gls{Moist} cancels the malicious message at the last minute}
At the top of the stone tower, \Gls{Moist} notices the makeshift semaphore tower being set up, and
learns from \Gls{Unde} that \Gls{Gilt} has sent a warning to all towers to convey the coming message
faithfully or lose their jobs. \Gls{Moist} then tells the hackers not to send their malicious
message through the network, since he has a plan to seize the company from \Gls{Gilt} while keeping
the towers intact.

\subsubsection{\Gls{Moist} makes up a new message to be sent through the semaphore network}
\Gls{Moist} dictates a new message which he is confident will bring down \Gls{Gilt}, as the hackers
set about obscuring the real semaphore tower in the city, and impersonating it using their own
makeshift setup. \Gls{Unde} is impressed by the message, and hopes that the men in the towers will
faithfully pass it along even after reading the contents.

\subsubsection{\Gls{Ridcu} talks to \Gls{Devious} in Genua about the message that reached him}
\Gls{Ridcu} talks to \Gls{Devious} through the University's largest looking-glass, now placed in
the Banquet Hall for the guests to see. \Gls{Devious} prepares to read the message that reached him
via semaphore, and warns \Gls{Ridcu} that is probably not the original message he set out to
transmit. \Gls{Ridcu} overrules his fears, and \Gls{Devious} reads a list of crimes committed by
the investors of the Grand Trunk Company, seemingly unearthed by the dead tower engineers.

\subsubsection{\Gls{Devious} reads out the message accusing the Grand Trunk board of high crimes}
\Gls{Ridcu} overrules the investors' attempts to stop \Gls{Devious} from finishing his message, and
asks him to continue. He reassures the investors that \Gls{Devious} has no cause to cheat, and asks
him again if the message is exactly what was handed over to him by the semaphore operator.
\Gls{Devious} agrees, and is persuaded by the prospect of promotion to continue with his speech.

\subsubsection{\Gls{Vetina} declares an impending investigation of the Grand Trunk Company's
    finances}
\Gls{Vetina} asks \Gls{Stow} and \Gls{Greeny} to keep quiet, and assures them that the allegations
will be looked into with all haste, if only to prove them wrong. Meanwhile, \Gls{Moist} notices that
\Gls{Gilt} has left the Great Hall, and watches \Gls{Vimes} send some Watchmen away, seemingly in
search of him.

\subsubsection{\Gls{Alice} sees \Gls{Grandad} get back to work after sending the ghost message
    onward}
\Gls{Alice} watches \Gls{Grandad} and the rest of the crew pick up their equipment and get back to
work, convinced that the message that just came through was indeed sent by the spirits of dead
semaphore engineers. \Gls{Grandad} is confident that \Gls{Gilt} will shortly be losing control of
the company, and exhorts his men to get back to work.

\subsubsection{\Gls{Vetina} places the board of investors under arrest}
\Gls{Vetina} asks \Gls{Pony} to take a tour of the towers, and retrieve the backup copy of the
messages originating from each of them. \Gls{Pony} readily accepts the demand, sensing the
opportunity to be away from the city for a few months. \Gls{Vetina} then asks \Gls{Vimes} to
detain the board of investors, and sends a summons to \Gls{Slant}, who is likely to offer them
legal advice.

\subsubsection{\Gls{Vetina} congratulates \Gls{Moist} on the malicious message to Genua}
\Gls{Vetina} offers \Gls{Moist} a ride to the Post Office, and asks him if \Gls{Pony} is likely to
conclude that the malicious message came from human intervention. \Gls{Moist} says no, and is
surprised when \Gls{Vetina} asks him to oversee the semaphore system in addition to the Post Office.
\Gls{Moist} reminds him that \Gls{Adora} and her family were the original owners, and should have a
bigger say in the new administration of the semaphore network. As he is dropped off, \Gls{Moist}
realizes that \Gls{Vetina} is aware of his fake semaphore setup in the stone tower.

\subsubsection{\Gls{Moist} receives \Gls{Alph} at the Post Office, as \Gls{Pump} says goodbye}
\Gls{Moist} reaches the Post Office, and realizes that winning the race to Genua will only mean that
his life will be consumed by administrative tasks day after day. He notices \Gls{Drumk} reprogram
\Gls{Pump}, and realizes that he is being sent after \Gls{Gilt}. \Gls{Pump} bids him goodbye, and
\Gls{Groat} arrives with a package containing \Gls{Alph}. \Gls{Moist} realizes that this is
\Gls{Gilt}'s parting gift, and looks forward to a stable life in the city.

\subsubsection{\Gls{Vetina} watches the Association of Bankers bail out one of their own}
At the palace, \Gls{Vetina}'s accountants lay bare the scam perpetrated by \Gls{Gilt} using the
notes prepared by \Gls{Moist}, as well as \Gls{Horse}'s ledger. The bank that had been swindled
by the Grand Trunk investors gets a bailout from the other banks, and continues to operate in the
short term. The association of bankers also place a hit on \Gls{Gilt} with \Gls{Downey} at the
Assassins' Guild, intending to rid themselves of the menace once and for all.

\subsubsection{\Gls{Vetina} offers \Gls{Gilt} a second chance, just like \Gls{Moist}}
\Gls{Vetina} has \Gls{Gilt} dragged back to Ankh-Morpork by \Gls{Pump}, and offers him the same
deal that he did to \Gls{Moist}. \Gls{Gilt} decides to take his chances with the Assassins' Guild,
and rejects the offer. \Gls{Drumk} arrives with news of the semaphore network resuming operation,
even as the renovations are in progress.