\section{Hogfather}


\subsection{}
\subsubsection{\Gls{Susan} deals with her new job as a governess}
At the Unseen University, \Gls{Ridcu} insists on breaking down a sealed door, with an ominous label
warning otherwise, to create a private bathroom for himself. Meanwhile, \Gls{Susan} takes up a job
as a babysitter, in spite of her inherited position as the duchess of Sto Helit. On the insistence
of \Gls{Twyla}, one of the children in her care, she goes to the basement of the manor and deals
with a furry monster using a red-hot poker.

\subsubsection{\Gls{Downey} is offered a preposterous contract by an Auditor}
An Auditor appears inside the office of \Gls{Downey}, the Master of the Assassins' Guild, offering a
valuable contract to have someone removed. \Gls{Downey} is alarmed when the ghost-like entity states
that the payment has already been transported to the guild vaults, and asks the treasurer
\Gls{Winvoe} to check.

\subsubsection{\Gls{Downey} takes on the contract to eliminate the Hogfather}
\Gls{Winvoe} confirms that the bounty has been deposited in advance, causing \Gls{Downey} to enquire
about the target. He is taken aback when the Auditor asks for the removal of the Hogfather, a
mythical figure whose whereabouts are unknown. He decides to ask \Gls{Teatime}, a controversial
member of their Guild, known for his lack of elegance, and sadistic tendencies, for help.

\subsubsection{\Gls{Teatime} talks about his rudimentary plan to kill the Hogfather}
\Gls{Teatime} shocks \Gls{Downey} by stating that he has already spent time formulating a plan to
kill mythical figures as a mental exercise, and asks for access to some obscure books in the Guild
Library. \Gls{Teatime} tells \Gls{Downey} that he will keep his plan secret, leaving the Master
content with his choice of agent.

\subsubsection{\Gls{Susan} is forced to confront the question of the Hogfather}
\Gls{Susan} finds herself a natural at the job of governess, and gets the two children in her care
to read complex books, in the vein of her own school curriculum. One night, as she finishes telling
them their bedtime story and tucking them into bed, \Gls{Twyla} comments on the rumours in the
playgroud that the Hogfather is not real, with her brother \Gls{Gawain} listening eagerly for
\Gls{Susan}'s explanation.

\subsubsection{\Gls{Teatime} meets with some independent thugs for help with his newest job}
\Gls{Peachy}, \Gls{Catse}, \Gls{Chick} and \Gls{Banjo} wait in a dingy tavern for \Gls{Teatime} to
show up with the details of the latest contract. \Gls{DaveL}, a medium, talks about how prompt
\Gls{Teatime} was in paying his contractors, when the rest of them bemoan the falling standards
within the Assassins' Guild. A short while later, \Gls{Teatime} sneaks in as a waiter, startling
the thugs with the efficacy of his disguise.

\subsubsection{\Gls{Teatime} remains vague about the target of their coming heist}
\Gls{Teatime} waits for the final member of their group to join them, as a student from the Unseen
University walks into the tavern in his robes. \Gls{Teatime} introduces him as \Gls{Sideney}, a
wizard saddled with gambling debt. He then talks cryptically about the hideout that they are going
to infiltrate, and reminds them of famed underworld locksmith \Gls{Brown}, who is set to join them.

\subsubsection{\Gls{Death} senses something wrong with the Discworld}
\Gls{Teatime} hits \Gls{Banjo} in the face, after making fun of his dim-witted nature, much to the
annoyance of his brother \Gls{DaveL}. Meanwhile, \Gls{Death} senses some problem with the laws of
the Disc, regarding the cycle of life. He returns abruptly from harvesting the soul of some
thermophilic lifeforms at the bottom of the ocean to investigate.

\subsubsection{\Gls{Teatime} and his group set off on their job}
\Gls{Teatime} hijacks a wagon driver by threatening him with a knife to his back, and takes the
group to the Unseen University. \Gls{Brown} joins them on the way, casually walking away from a
bank job, as the City Watch chase some other robbers who made the mistake of running. \Gls{Teatime}
then asks to be taken to the old refuse pit next to the University.

\subsubsection{\Gls{Teatime} kills the wagon driver after being shown the secret of the portal}
\Gls{Teatime} asks the wagon driver about the secret entrance next to the University, and kills him
after learning that it requires some tobacco to be thrown at an unsuspecting path of wall. The
Auditors, who inspect the wagon driver's corpse, marvel at \Gls{Teatime}'s ingenuity, before
dispersing in time for \Gls{Death} to come harvest the newly liberated soul.

\subsubsection{The \Gls{DRat} inspects an offering laid out for the Hogfather}
The \Gls{DRat} harvests the soul of a rat that gets trapped by a piece of pork, and notices a
letter written to the Hogfather by a child eagerly awaiting gifts in exchange for her good
behaviour. It eats some of the ritual food left out for the Hogfather, and hides when a rotund
figure in a red coat drops into the hall via the chimney.

\subsubsection{The \Gls{DRat} watches \Gls{Death} do the duties of the Hogfather}
The \Gls{DRat} follows the figure up to the roof after watching it stuff some presents into a
stocking, as requested by a child in its letter. After watching the supposed Hogfather leave in
his magical sleigh pulled by pigs, the \Gls{DRat} climbs down to the garden, where \Gls{Quoth}
is waiting for it. It tries to tell the raven that \Gls{Death} had taken over the duties of the
Hogfather, an idea that \Gls{Quoth} does not take seriously.

\subsubsection{\Gls{Susan} dismisses the \Gls{DRat} when it tries to warn her about \Gls{Death}}
\Gls{Susan} gets a drink at the Biers, where \Gls{Igor} notices someone arriving by the sunroof
built into the ceiling. \Gls{Susan} is alarmed to see the \Gls{DRat} after two whole years of
normalcy, and asks it to leave her alone, when it tries to tell her about \Gls{Death} taking on
the role of the Hogfather.

\subsubsection{\Gls{Albert} helps \Gls{Death} discharge his new duties as the Hogfather}
The night before Hogswatch, \Gls{Ridcu} inspects his newly installed private bathroom, as \Gls{Modo}
puts the finishing touches on the plumbing. Meanwhile, \Gls{Albert} helps \Gls{Death} navigate to
the next child's home, and sorts out the presents to be stuffed into his stockings. \Gls{Death} is
perplexed at the how prevalent the idea of the Hogfather being fake is getting, and wonders how
children are judged to be worthy of presents.

\subsubsection{\Gls{Susan} listens to the \Gls{DRat} warn her about \Gls{Death} delivering presents}
\Gls{Susan} attends to a bogeyman who threatens to scare \Gls{Twyla} at bedtime, and comes back
to the room with the Hogswatch tree. She finds the \Gls{DRat} and \Gls{Quoth} waiting for her,
trying to warn her about the possibility of confronting her grandfather at night. Meanwhile, several
other supernatural get on with their assigned role for Hogswatch night.

\subsection{}
\subsubsection{\Gls{Teatime} and his crew secure a tower in the spirit world}
\Gls{Teatime} kills the last of the guards hiding inside a mysterious tower in the spirit realm,
as the rest of his crew secure the insides. \Gls{Sideney} is intrigued by the unreal architecture
of the spiral staircase winding its way up the tower, and compares it to the University. Meanwhile,
\Gls{Susan} is alarmed to learn that the real Hogfather is dead, and that \Gls{Death} has been
asked to fill in for Hogswatch day.

\subsubsection{\Gls{Death} reveals the special time dilation to \Gls{Susan} for Hogswatch night}
The mysterious gnome runs into another Hogswatch myth, busy drawing patterns in frost on the
windows of the city. \Gls{Death} explains to \Gls{Susan} that the world has been put in a state of
special time dilation, for him to be able to deliver all the Hogswatch presents. \Gls{Susan}
realizes that this is why \Gls{Albert} is able to come to the Disc, in spite of having mere seconds
left in his hourglass.

\subsubsection{\Gls{Susan} goes against \Gls{Death}'s advice not to investigate the Hogfather's
    disappearance}
After leaving \Gls{Susan}, \Gls{Death} hints to \Gls{Albert} that he asked \Gls{Susan} not to
investigate his new predicament, precisely to goad her into doing so. \Gls{Susan} is annoyed by the
lack of information regarding the Hogfather, and stops time to go out and summon \Gls{Binky}. She
decides to fly off to \Gls{Death}'s House, the \Gls{DRat} and \Gls{Quoth} close behind.

\subsubsection{\Gls{Susan} visits the hall of Hourglasses reserved for the Gods}
In \Gls{Death}'s House, \Gls{Susan} notices an army of pet cats, and proceeds to the Hourglass room.
She spots a hidden chamber along the wall, and opens it to see another room filled with spectral
hourglasses labeled with the names of Gods. She steps on a shattered hourglass, and is horrified to
see half of the label spell out the Hogfather.

\subsubsection{\Gls{Ridcu} uses the bathroom that had been kept sealed at the University}
\Gls{Ridcu} refuses to listen to his council, when they remind him that the private bathroom must
have been sealed for good reason. He uses the bathroom's various settings, and finds all of them to
be enjoyable, except for one that mimics a geyser, spraying a jet of hot water vertically.
\Gls{Modo} shuts off the water supply, when he hears \Gls{Ridcu} stop singing, and helps him come
out of the bathroom.

\subsubsection{\Gls{Ridcu} is visited by the \Gls{VerruG}}
\Gls{Ridcu} is attacked by a gnome responsible for giving people verrucas. He knocks the gnome down,
and opens his bag before it can explain its purpose to him. Meanwhile, \Gls{Albert} insists on
doing a meet and greet with some children, in order to restore the rapidly failing belief in the
Hogfather's existence. \Gls{Ridcu} decides to help the \Gls{VerruG} resolve his predicament, when
it states that the responsibility was simply thrust upon it out of nowhere.

\subsubsection{\Gls{VCrum} watches \Gls{Death} arrive at his store with his sleigh}
\Gls{VCrum}, the manager of a local toy store, puts the finishing touches on his Hogswatch
display, complete with sleigh, stuffed pigs, and tree. As he is inspecting the long line of children
eager to meet the Hogfather, he feels a reality shift, resulting in \Gls{Death}'s sleigh taking the
place of the one he had set up.

\subsubsection{\Gls{VCrum} is surprised to see someone new take over the role of the Hogfather}
\Gls{VCrum} is surprised to see the assembled kids gravitate to the newly arrived hogs, and the
morbid-looking sleigh, even as the parents try to drag them away from the store. \Gls{Death} has
taken the place of the old man who was signed on to be the Hogfather, and asks a little girl what
presents she wants.

\subsubsection{\Gls{Death} joins his first meet-and-greet at a toy store for kids}
The little girl in \Gls{Death}'s lap recites an impressive list of toys, and \Gls{Death} immediately
pulls out a sack containing all of them. \Gls{VCrum} is alarmed at the idea that the toys are being
given away for free, before he realizes that they are not from his stock of merchandise.

\subsubsection{\Gls{Ridcu} asks \Gls{Stibb} to look into the \Gls{VerruG}}
\Gls{Ridcu} walks into \Gls{Stibb}' lab at the High Energy Magic Building, and sees the \Gls{Bursar}
testing out \Gls{Hex}'s new voice input system. He is amused to see the \Gls{Bursar} struggle to
communicate with the machine, and asks \Gls{Stibb} to investigate the sudden appearance of the
\Gls{VerruG}.

\subsubsection{\Gls{Death} faces a cynical child who does not believe in the Hogfather}
\Gls{Death} is amused by a the next child who sits on his knee, when it declares that Hogswatch is
nothing more than a cash-grab, and that the Hogfather is a lie. \Gls{Albert} is surprised by how
patient \Gls{Death} is with the boy, and is amused to learn that all the boy's presents have been
magically replaced.

\subsubsection{\Gls{Susan} tries to read the Hogfather's biography}
\Gls{Susan} tries to find the biography of the Hogfather in \Gls{Death}'s Library, and learns from
\Gls{Quoth} that he did not occupy the same role thousands of years ago. She realizes that Gods were
happy to adapt to changing times, in order to remain relevant in the minds of believers, and stay
alive. The \Gls{DRat} suggests they go to the Castle of Bones, which is supposed to handle all the
letters written by children to the Hogfather.

\subsubsection{\Gls{Chick} and \Gls{DaveL} wonder about the true target of their heist}
At the mysterious tower, \Gls{Chick} and \Gls{DaveL} talk about the mysterious locked room that
\Gls{Teatime} is trying to open, with the help of \Gls{Sideney}'s magic. They realize they are
trapped in the alternate world, with no way of getting back to the Disc without help from
\Gls{Teatime}.

\subsubsection{\Gls{Death} fulfills an impractical wish from a little girl}
\Gls{Death} makes a pony appear in the high-rise apartment of the next girl to sit on his lap at the
toy store, according to her wishes. He laughs it off as a joke when the girl's mother warns her
about the impracticality of such a gift. \Gls{Albert} realizes that these extraordinary acts of
magic are meant to build faith in the Hogfather among the children of the Disc.

\subsubsection{\Gls{Susan} investigates the abandoned Castle of Bones}
\Gls{Susan} reaches the Castle of Bones, and finds it deserted. She notices lots of cigarette ashes
strewn about, and realizes that \Gls{Albert} must have visited the place earlier. She marvels at
the impressive structure made of ice, as the \Gls{DRat} tries to tell her that the resident God's
absence might collapse the pillars soon.

\subsubsection{\Gls{Susan} rescues a young boy from the Castle of Bones}
\Gls{Susan} finds a boy in white robes buried in the rubble of the Castle, and drags him out as it
starts to collapse. An imp keeps hitting the boy with a small hammer on the back of his head, and
tells \Gls{Susan} that it is part of his curse when she asks it to stop.

\subsection{}
\subsubsection{\Gls{Susan} notices the change of reality when the Castle of Bones comes down}
After the Castle of Bones collapses to a massive heap of snow, the young boy tells \Gls{Susan} that
he is named \Gls{Bili}, and that he woke up one day as the God of Hangovers. She notices the ruins
rapidly disappear, leaving a snowy plateau as if to suggest that the Hogfather's home had never been
there to begin with.

\subsubsection{\Gls{Nobby} and \Gls{Visit} come to the aid of \Gls{VCrum}}
\Gls{Nobby} and \Gls{Visit} respond to \Gls{VCrum}'s call for help, and ask him what crime they
can charge the fake Hogfather with. \Gls{VCrum} realizes that the merchandise being given away is
not his own, and that arresting the Hogfather upstairs would be bad publicity for the shop.
\Gls{Nobby} sees the large mob in front of the Hogfather, and recalls the empty stockings that made
up his childhood.

\subsubsection{\Gls{Susan} asks \Gls{Ridcu} to cure \Gls{Bili} of his hangover}
\Gls{Susan} brings \Gls{Bili} to the Unseen University, where \Gls{Ridcu} and \Gls{Indef} are
overseeing the preparations for the Hogswatchnight feast. She asks \Gls{Ridcu} to help \Gls{Bili}
clear his perpetual hangover, so that she can interrogate him about current events. The inner
council proceed to suggest their hangover cures, and \Gls{Ridcu} decides to give \Gls{Bili} a mix
of all the recipes.

\subsubsection{\Gls{Death} gives \Gls{Nobby} a valuable present}
\Gls{Death} finds great joy in seeing the children's faces light up when he tells them they have
earned their Hogswatch presents. Meanwhile, \Gls{Ridcu} adds his ancestral recipe for gunpowder
sauce to the hangover cure, making a potion of pure sobriety. Meanwhile, \Gls{Nobby} sits on
\Gls{Death}'s lap, and lets his inner child take over. He is rewarded with a deluxe crossbow, and
decides to let go of his initial plan to arrest the Hogfather.

\subsubsection{\Gls{Bili} drinks the potion of pure sobriety}
\Gls{Bili} is cured of his hangover, and immediately asks for the crystal ball to be brought
forward, so that he might see the effects of the potion on the God of Wine, who is relaxing in
Dunmanifestin. He is glad to see the cause-and-effect chain reverse, as the God of Wine starts
vomiting his last meal.

\subsubsection{\Gls{Susan} asks \Gls{Bili} for help tracking down \Gls{Death}}
\Gls{Susan} stops \Gls{Bili} from enjoying his newfound sobriety by getting drunk, and works out
that the special magical field of Hogwatch is bringing Gods into existence by the power of wishful
thinking. The council of wizards run to the laundry, to find out whether a fairy has been stealing
their socks.

\subsubsection{\Gls{Death} rescues a little girl freezing to death in the streets}
\Gls{Death} is angered to see \Gls{Albert} hand him an hourglass when he asks what the next child
wants for Hogswatch. Meanwhile, \Gls{Susan} tries to explain to \Gls{Bili} that she is \Gls{Death}'s
granddaughter, and asks for help tracking him down. \Gls{Death} saves the little girl from freezing
to death on Hogswatchnight, and hands her to \Gls{Nobby} for safekeeping. \Gls{Nobby} recognizes
\Gls{Death} from his antimemetic field, and escorts the girl back to the Watch House for dinner.

\subsubsection{\Gls{Ridcu} brings the inner council to \Gls{Hex}}
\Gls{Ridcu} and the inner council arrive at \Gls{Stibb}'s lab, and notice \Gls{Hex} malfunctioning.
\Gls{Ridcu} types in the name of the pills used by the \Gls{Bursar} to alleviate his insanity, and
is shocked to see the machine act normal after accepting his input. It tells the council that
newer mythical creatures are no less absurd than the established ones, leaving \Gls{Ridcu} to ponder
over some theories brewing in his mind.

\subsubsection{\Gls{Susan} talks to \Gls{Bili} about her heritage}
\Gls{Susan} realizes that \Gls{Bili} materialized in the Castle of Bones because he was being
substituted for the Hogfather, who was vanishing from the Disc. \Gls{Albert} argues with \Gls{Death}
about his newfound crusade to spread goodwill by performing miracles as the Hogfather. \Gls{Susan}
feels the role of grim reaper being thrust upon her, and realizes that \Gls{Death} is shirking his
duties once again.

\subsubsection{\Gls{Susan} talks to \Gls{Quoth} about the tooth fairies}
Another God materializes on the table of the feast hall at the University, causing chaos.
\Gls{Quoth} and the \Gls{DRat} sneak into the hall, and ask \Gls{Susan} about her premonition
involving rows of teeth. \Gls{Bili} wonders where the tooth fairies might be depositing the teeth
they harvest, leading them all to think deeply about possible answers.

\subsubsection{\Gls{Death} harvests the soul of a man lying dead on the University terrace}
\Gls{Ridcu} and the council retire to their meeting hall, to discuss the possible reasons why old
Gods were coming back to life, in addition to new ones materializing just because someone thought
of them. Meanwhile, \Gls{Death} harvests the soul of a man lying dead on the roof of the University,
whose spirit mumbles something about teeth.

\subsubsection{\Gls{Susan} goes after the local tooth fairy}
\Gls{Susan} asks \Gls{Igor} for the whereabouts of the tooth fairy named \Gls{Violet} who frequents
his bar, and is forced to use \Gls{Death}'s voice to get him to comply. Meanwhile, the \Gls{DRat}
distracts him from \Gls{Quoth}, who is trying to eat a pickled eff off the shelf, since it resembles
an eyeball.

\subsubsection{\Gls{Susan} investigates \Gls{Violet}'s home}
Inside \Gls{Violet}'s home, \Gls{Susan} spots the list of names given to the fairy for harvesting
teeth, and notices the name of a hardened criminal on it. She also notices the lack of any tallies
for the last few days, just as the bulk tooth collection agent shows up looking for \Gls{Violet}.
\Gls{Susan} asks him about the teeth, and realizes that he knows nothing more than the delivery
cart that comes by weekly to take the bags of teeth from him.

\subsubsection{\Gls{Death} stops a minor King from humiliating a poor peasant in the name of
    charity}
\Gls{Death} stops a king in some remote hill kingdom from giving a poor peasant a grand Hogswatch
feast, and gives him the food he fondly remembers from his childhood instead. The peasant is
thankful for the meal, and \Gls{Death} feels happy to see people look forward to his arrival, when
he is substituting for the Hogfather.

\subsubsection{\Gls{Susan} tries to track down \Gls{Banjo} at the Young Men's Hostel}
\Gls{Susan} finds the local Young Men's Hostel, where she spots the room of \Gls{Banjo} empty, with
signs of recent habitation. She recalls his name as the last one on \Gls{Violet}'s list, and sees a
curious silver coin lying next to his bed.

\subsection{}
\subsubsection{\Gls{Susan} reads the biography of \Gls{Violet}}
\Gls{Susan} reads \Gls{Violet}'s biography in the Library of \Gls{Death}, and finds that the latest
entry talks about her being held captive in a surreal pocket dimension, where the design reminds her
of \Gls{Death}'s own House. Meanwhile, \Gls{Albert} tries to tell \Gls{Death} that he cannot give
poor children all the presents they wish for, without upsetting the natural state of wealth
inequality on the Disc.

\subsubsection{\Gls{Hex} puts forward its hypothesis about the vanishing of the Hogfather}
\Gls{Hex} speculates that some major God is no longer being believed in, and the excess belief is
being filled up by the other old Gods materializing. \Gls{Ridcu} wonders if the Hogfather is the
God being erased, as his council start arguing about their Hogswatch traditions. The \Gls{Dean}
lets slip something about the \Gls{CheerF}, and she materializes in front of them, as a primary
school teacher intent on forcing smiles out of her entire classroom.

\subsubsection{\Gls{Ridcu} and \Gls{Stibb} hope to catch the Hogfather delivering presents for the
    \Gls{Libra}}
The inner council feel bad about their unshakable gloom in the face of the \Gls{CheerF}, and
\Gls{Ridcu} asks \Gls{Stibb} about sending a letter to the Hogfather. \Gls{Stibb} suggests waiting
for him to visit the University, considering some senior wizards might still be hanging stockings
out for him. They head to the Library, and camp outside the \Gls{Libra}'s bed, where he has gone to
sleep early on Hogswatchnight.

\subsubsection{The troupe of beggars in Ankh-Morpork receives a surprise gift from \Gls{Death}}
The champion caroling troupe in Ankh-Morpork encounter the some beggars singing their own tune,
and banging pots in the hopes of getting paid to stop. A while later, \Gls{Death} drops a care
package next to the beggars, containing all the food they need for a handsome feast. Meanwhile,
\Gls{Stibb} decides to hang up one of his own socks, asking for electricity in a hastily written
note to the Hogfather.

\subsubsection{\Gls{Albert} finds out about \Gls{Death} swindling some food from a restaurant}
\Gls{Albert} is alarmed to see the ideas of wealth redistribution taking shape in \Gls{Death}'s
mind. Meanwhile, \Gls{Susan} lands on the pocket dimension that looks like a child's painting of
a field and river. She walks to the house in the distance, which looks like the standard house
painted by every child in the Disc.

\subsubsection{\Gls{Teatime} talks about something more valuable than money in the Tooth Fairy
    tower}
The high-end restaurant is forced to make up a menu around old muddy boots, when \Gls{Death} takes
all of its food and leaves the boots as compensation. At the strange white tower, \Gls{DaveL} and
the other thugs investigate a safe-room containing deeds to properties owned by the Tooth Fairy,
as \Gls{Teatime} walks in, talking about some other greater treasure hidden in the tower.

\subsubsection{\Gls{Ridcu} asks \Gls{Death} about his new duties as the Hogfather}
\Gls{Ridcu} immediately sees through \Gls{Death}'s disguise when he comes down the Library's
chimney, and asks what happened to the original Hogfather. Meanwhile, \Gls{Teatime} has \Gls{Banjo}
push \Gls{Brown} off the spiral staircase when he says he cannot open the locks to the treasure
room. \Gls{DaveL} and the others watch his corpse tumble past them, and decide to investigate.

\subsubsection{\Gls{Susan} finds the pile of teeth designed for a powerful ritual}
\Gls{Susan} reaches the entrance to the Tooth Fairy's tower along with \Gls{Bili}, and finds a large
heap of children's teeth arranged in a ritual circle at the ground level. She sees the body of
\Gls{Brown} come tumbling down a spiral staircase, and runs to check if he is still alive.
Meanwhile, \Gls{Chick} runs to \Gls{Teatime} to inform him of the intruders, as \Gls{Susan} tries to
make sense of the symbols surrounding the pile of teeth.

\subsubsection{\Gls{Susan} realizes that the children of the Disc are being manipulated}
\Gls{Peachy} tries to describe his childhood fears of a bogeyman hiding in his cupboard, as the
thugs reach the bottom floor, and find \Gls{Brown}'s body missing. They spot the intruders climbing
another spiral staircase, and decide to surround them. Meanwhile, \Gls{Susan} runs into one of the
tooth storage rooms, and spots the teeth missing from their rightful shelves. She works out that
they are being used to influence the minds of the children, using ancient blood magic.

\subsubsection{\Gls{Susan} rescues \Gls{Violet} from her chains}
In a nearby room, \Gls{Susan} follows the sound of \Gls{Violet}'s shouting, and finds her chained
to a shelf. \Gls{Violet} is thankful to be rescued, and narrates the tale of her kidnapping, before
\Gls{Bili} is smitten by her vow of sobriety. \Gls{Catse} is taken by a shadow monster that flows
through the corridors of the tower without any physical body. \Gls{DaveL} draws his sword when he
finds his comrade's boots left in the passage he was investigating.

\subsubsection{\Gls{Chick} is eaten by the sinister cupboard from his childhood}
\Gls{Peachy} threatens \Gls{Susan} and the others with a crossbow, but runs away when his own
childhood nightmare materializes at the top of the stairs. \Gls{Bili} and \Gls{Violet} are stopped
by \Gls{Chick} on their way down to the tower's exit. He is swallowed up by the nightmare cupboard
from his childhood, and \Gls{Bili} finds only his boots left when he opens the doors to it a while
later.

\subsection{}
\subsubsection{\Gls{Death} explains his mission to \Gls{Ridcu}}
\Gls{Death} explains to \Gls{Ridcu} that the Auditors are out to abolish any superstitious beliefs
in the Disc, starting with the biggest one of them all. He is annoyed to see them go so far as to
employ humans to do their dirty work for them, and warns \Gls{Ridcu} of the need to reignite belief
in the Hogfather before the night is up.

\subsubsection{\Gls{Ridcu} finds the corpse of \Gls{Chick} in the \Gls{Bursar}'s room}
\Gls{Ridcu} runs to the \Gls{Bursar}'s chamber, to see him terrified by a corpse that fell out of
his cupboard. He is surprised to find its pockets stuffed full of teeth, and senses that it must
have got there by magical means. \Gls{Stibb} asks for the corpse to be taken to \Gls{Hex} for
further analysis, and is alarmed to see \Gls{Death} take offense at the mention of a thinking
machine.

\subsubsection{\Gls{Death} asks \Gls{Hex} to believe in the Hogfather to further his mission}
\Gls{Death} goes to \Gls{Hex}'s chamber and asks to be left alone with it. He asks it to believe in
the Hogfather, and is alarmed when it starts writing a letter to him with a list of complicated
trinkets for presents.

\subsubsection{\Gls{Susan} is captured by \Gls{Teatime}}
\Gls{Susan} is captured by \Gls{Teatime} as she tries to sneak up on him, while \Gls{Sideney} is
busy breaking picking the last few magical locks guarding the treasure room. \Gls{Teatime} asks him
to leave the tower, as he tells \Gls{Susan} about his time at the Assassins' Guild learning about
her noble heritage.

\subsubsection{\Gls{Susan} neutralizes \Gls{Banjo} and \Gls{DaveL} by recalling their mother}
\Gls{Susan} makes an educated guess about \Gls{Teatime}'s childhood, when the other children must
have sensed his sociopathy and refused to play with him. Meanwhile, the monster of childhood fear
lurking in the tower takes the form of \Gls{DaveL}'s mother, and terrifies the two brothers to the
point of losing consciousness. \Gls{Susan} tries to use the distraction to attack \Gls{Teatime},
but is too slow for his reflexes.

\subsubsection{\Gls{Susan} watches \Gls{Teatime} vanish from the Tooth Fairy's tower}
\Gls{Susan} correctly works out that \Gls{Death}'s magical sword would not work in the Tooth Fairy's
tower, since the idea of death did not exist in a world that worked on children's logic. When
\Gls{Teatime} fails to kill her using the sword, she tips him over the railing of the spiral
staircase, and watches him disappear when he falls to the ground. She then tells \Gls{Banjo} that
his brother must have gone to a better place, and asks him to get rid of the ritual circle of teeth.

\subsubsection{\Gls{Susan} forces the \Gls{OBogey} to show its true form}
Inside the treasure room, \Gls{Susan} finds an old lady in a bed, pretending to be a grandmother.
She works out that the illusion is an attempt by a bogeyman to appeal to any fears she might have,
and forces it to reveal its true form. The bogeyman identifies itself as the \Gls{OBogey}, and tells
her that the advancement of civilization forced it to take up a new job, as the Tooth Fairy, who
guarded children by keeping their teeth safe.

\subsubsection{\Gls{Susan} puts \Gls{Banjo} in charge of the Tooth Fairy's tower}
\Gls{Susan} watches the \Gls{OBogey} vanish, as it complains about the inability to die in the
tower, and appoints \Gls{Banjo} as the replacement Tooth Fairy. She leaves \Gls{Violet} and
\Gls{Bili} to assist him, and finds \Gls{Binky} for the trip back to the Disc. \Gls{Death} finds her
midway through her ride, and asks her to rescue the Hogfather so that he can take over his old duty.

\subsubsection{\Gls{Teatime} returns to the Disc at the Unseen University's dining hall}
The Auditors resort to desperate measures when their plan to use \Gls{Teatime} fails. \Gls{Wrangle}
decides to charm the \Gls{CheerF}, and almost succeeds but for Cupid failing to land his shot on
her through the magically barred windows. At the feast, \Gls{Teatime} materializes on the table,
knocking down all the food. He recovers his senses and runs off with \Gls{Death}'s sword before
\Gls{Ridcu} can interrogate him.

\subsubsection{\Gls{Susan} saves the Hogfather from the Auditors on the Disc}
\Gls{Susan} guides a magical board by climbing on its back as \Gls{Death} warns her of the Auditors
chasing it as ethereal wolves. \Gls{Susan} manages to jump a large chasm between two plateaus,
and sends one of the Auditors crashing to the ground when it tries to follow. \Gls{Death} corners
the other Auditors when they give up on the chase, and warns them about breaking the rules of the
Disc by meddling directly in its affairs.

\subsubsection{\Gls{Death} and \Gls{Susan} watch the Hogfather resume his duties}
\Gls{Death} explains to \Gls{Susan} that the human society depends on people believing in abstract
ideas like justice and mercy. This starts with children being taught to believe in little lies such
as the Tooth Fairy and the Hogfather. \Gls{Death} arrives with \Gls{Susan} at the home where she
works as a babysitter in time for the children to start opening their presents.

\subsubsection{\Gls{Teatime} is killed by \Gls{Susan}'s poker as \Gls{Twyla} and \Gls{Gawain} watch}
\Gls{Teatime} takes \Gls{Susan} hostage using \Gls{Death}'s sword when she goes to the kitchen, and
asks for the children to be summoned. When he tries to kill \Gls{Death} using the magical sword,
\Gls{Susan} throws her poker through \Gls{Death} to kill him. \Gls{Death} pauses time to thank her
for her role in rescuing the Hogfather, and leaves with \Gls{Teatime}'s corpse to spare the two
children's innocence.

\subsubsection{\Gls{Death} buys a present for \Gls{Albert} from the past}
\Gls{Death} travels back in time to \Gls{Albert}'s childhood, and buys the expensive toy horse that
he fondly remembers staring at. \Gls{Ridcu} finds a dangerous mechanism in the newly renovated
bathroom that links to the Grand Organ of the University, and has it sealed again. \Gls{Stibb} is
alarmed by the sentimentality of \Gls{Hex}, as it seems to become more and more human.