\section{I Shall Wear Midnight}


\subsection{}
\subsubsection{\Gls{Tiff} walks through the annual fair next to her village}
\Gls{Tiff} walks through the Chalk's annual fair at the end of summer, and sees the young boys of
the village hoping desperately to attract the attention of some of the girls from neighbouring
villages. She thinks about her unofficial training period at \Gls{Ogg}'s cottage in Lancre town,
and of how witches seldom got married considering the size of their workload.

\subsubsection{\Gls{Tiff} faces some difficult questions from young girls at the fair}
\Gls{Tiff} thinks about the tedious process of fighting back against the stigma that witches
faced in her part of the hills, and wonders if she can call the witches of Lancre for help without
taking a hit to her reputation. Some younger girls ask her if she has found a lover herself, and
\Gls{Tiff} avoids answering them by pointing out the start of the downhill cheese-rolling
contest.

\subsubsection{\Gls{Tiff} receives some relationship advice from \Gls{Jeannie}}
\Gls{Tiff} spots \Gls{Horace} lining up with the other wheels of cheese, and wonders if the Feegles
are at the fair, secretly watching over her. \Gls{RobA} finds her at the fair, and asks her if she
is getting along well. He then conveys the message from \Gls{Jeannie} asking her to remain
optimistic even if the relationship with \Gls{Roland} has fallen apart, and vanishes before she can
get angry.

\subsubsection{\Gls{Tiff} meets \Gls{Roland} in her capacity as the village medic}
\Gls{Tiff} performs some first aid at the bottom of the hill after the cheese rolling, and sees
\Gls{Roland} arrive by carriage along with his lover \Gls{Leti}, who happens to be a noble-born
girl. \Gls{Roland} asks her about the severity of the injuries, and remains formal in his language
in front of the villagers. She flies to her cottage at dusk, as the last of the fairground
entertainers disassemble their tents.

\subsubsection{\Gls{Tiff} helos \Gls{Petty} avoid mob justice after he beats his daughter, causing
    a miscarriage}
\Gls{Tiff} responds to a call from her father, asking to help the village drunk \Gls{Petty} evade
mob justice, after he causes his teenage daughter to miscarry by beating her. \Gls{Tiff} drags him
out of his bedroom, and tries to get him to flee the village. \Gls{Petty} eventually decides to run
from the mob when \Gls{Tiff} transfers the pain from his daughter into his body. Her father comes to
check in on her in the barn, where the girl is asleep next to the miscarried foetus. He asks her why
she chooses to care for the destitute villagers, and talks about how glamourous his opinion of
witchcraft had originally been.

\subsubsection{\Gls{Tiff} talks to her father about her career choice}
\Gls{Tiff} tells her father some stories about destitute old people who had been left dead on their
beds for months by villagers who never bothered to check up on them, and reminds him that she finds
fulfillment in helping those who have no one else to take care of them. She then asks him to find
some rope so that she can take \Gls{Petty}'s daughter on her broomstick to a senior witch for
further medical attention, after burying the aborted foetus in the forest away from the village.

\subsubsection{\Gls{Tiff} asks the Feegles to take \Gls{APetty} to they colony}
\Gls{Tiff} asks her father to clean out the old barn that now lies unused, and is happy to learn
that he plans to take in \Gls{MPetty} and her daughter, who don't have anyone else left. She then
senses the Feegles peering down at her from the wooden beams above, and asks them to show
themselves. She gets them to haul \Gls{APetty} to their newly renovated colony, now boasting a
much larger underground cavern with a wide entrance that \Gls{Tiff} can descend comfortably.

\subsubsection{\Gls{Jeannie} insists on \Gls{Tiff} getting a good night's sleep in the colony}
\Gls{Jeannie} greets \Gls{Tiff} in her private chamber, and asks for a hot meal to be brought to
her. She warns \Gls{Tiff} that the premonitions coming to her in her sleep are strange, and that she
cannot work out the nature of the danger that is coming. \Gls{Tiff} falls asleep out of exhaustion,
and \Gls{Jeannie} lets her rest in the cavern, before returning to \Gls{RobA} and the others in the
colony, who are busy with their sparring.

\subsubsection{\Gls{Tiff} sees a strange omen on her way to bury the foetus}
\Gls{Tiff} wakes up before dawn the next day, and hears \Gls{APetty} laughing at the Feegles trying
to entertain her. \Gls{Jeannie} informs her that her fairy magic has wiped the girl's painful
memories, and that she will have a few nightmares until the last remnants fade away. \Gls{Tiff}
sets off to bury the foetus, and spots an old woman hiding in the bushes. This woman fades away
into smoke, and all that is left is a hare that bursts into flames for a moment, before running
away.

\subsubsection{\Gls{Tiff} buries the foetus next to the grave of a destitute old woman}
\Gls{Tiff} flies to the Petty household, and finds \Gls{Petty} hanging in the barn, next to
\Gls{APetty}'s aborted foetus. She watches \Gls{RobA} cut the rope after noticing some evidence of
life still remaining in his body. She lets \Gls{RobA} deal with the noose, and vows to help
\Gls{Petty} now that he has demonstrated some remorse for the miscarriage he caused. She flies to
the old cottage of the woman who had been falsely prosecuted for \Gls{Roland}'s disappearance, and
buries the foetus next to her grave.

\subsubsection{\Gls{Tiff} talks to her father about the danger in reuniting \Gls{Petty} with his
    wife}
\Gls{Tiff} goes home with \Gls{APetty}, and talks to her father about finding the body of
\Gls{Petty} in a near-death state in his barn. Her father in turn tells her that \Gls{MPetty}
returned to her husband out of a sense of misplaced loyalty, and promises to keep watch on the
family to spare her the trouble.

\subsubsection{\Gls{Tiff} talks to the \Gls{Baron} about her service to the village}
\Gls{Tiff} takes away the \Gls{Baron}'s pain after sending the nurse \Gls{Spruce} away, and is
surprised to see him want to sit up to talk. He asks her to be a good advisor to \Gls{Roland} after
he passes on, and recalls \Gls{GAch} fondly when she acted as a balance to his own judgment. He
commends her for her selfless service to the village, and reminds her that the fear of witches has
not totally vanished from the psyche of the villgers.

\subsubsection{\Gls{Tiff} hears the \Gls{Baron} recite an old poem when she shows him a trick}
The \Gls{Baron} asks \Gls{Tiff} to take a bag of gold coins as payment for rescuing his son from
the fairy realm, and tells her that the bag is worth a fortune when exchanged for present-day
dollars. She shows off her heat transfer skill by holding one of her hands over the fireplace and
letting the heat turn a bucket of water into steam. The \Gls{Baron} is impressed by her trick, and
recites an old poem about how witches could be recognized by their ability to play with fire.

\subsubsection{The \Gls{Baron} dies after recalling a fond childhood memory}
The \Gls{Baron} recalls seeing a hare as a child run into a forest fire, and come out unscathed.
\Gls{Spruce} enters the room, and calls for the guards when she sees the steam rising from the
bucket, next to the weakened \Gls{Baron}. The \Gls{Baron} then dies after pointing out the painting
he had made as a child of the burning forest, and of how his father had kept it as a prized
possession in the family strongbox.

\subsubsection{\Gls{Spruce} accuses \Gls{Tiff} of stealing from the dying \Gls{Baron}}
\Gls{Spruce} drags the guards into the \Gls{Baron}'s chamber, and accuses \Gls{Tiff} of killing him
in order to get her hands on his strongbox. Sergeant \Gls{Brian} is annoyed by the nurse's wild
speculation, and listens to \Gls{Tiff} talk about the coins that the \Gls{Baron} gave her for her
service. She asks the palace staff to get the place clean for the ascension of \Gls{Roland} to the
title of Lord, and tells \Gls{Brian} that she will go find him in the nearby town.

\subsubsection{\Gls{Tiff} scolds \Gls{Spruce} for slacking at the castle}
\Gls{Tiff} insults \Gls{Spruce} when she refuses to participate in the castle's cleanup, and notices
how her white coat never gets dirty. She recalls how \Gls{Roland} has a high opinion of her, along
with her new religion, as the new guard \Gls{Preston} tells her that the \Gls{Baron}'s corpse is
in the crypt, ready for her to perform the last rites.

\subsubsection{\Gls{Tiff} talks to \Gls{Toad} about \Gls{APetty}'s supernatural abilities}
\Gls{Tiff} goes to the Feegle colony to inform \Gls{Jeannie} about the death of the \Gls{Baron}. She
spots \Gls{APetty} playing above the mound, and tells her to go down the rabbit hole to call for
\Gls{Jeannie}. Meanwhile, the \Gls{Toad} tells her that \Gls{APetty} seems to have an unusual
aptitude for language, and notices her talking fluently to \Gls{Jeannie} in the original Feegle
language. \Gls{Tiff} also recalls how the chickens in their farm had followed \Gls{APetty} in a neat
line when she was asked to feed them.

\subsubsection{\Gls{Jeannie} talks to \Gls{Tiff} about the promise shown by \Gls{APetty}}
\Gls{Jeannie} oversees the Feegles marking their snails with a clan brand, and is confident that
the clan will soon be famous for the snails they breed. She asks \Gls{Tiff} to get \Gls{APetty}
apprenticed someone who can put her linguistic genius to good use. She congratulates \Gls{Tiff} on
dealing with the \Gls{Baron} on his deathbed, and is surprised when \Gls{Tiff} asks the Feegles to
help her track down \Gls{Roland}.

\subsubsection{\Gls{Tiff} cleans up \Gls{MPetty}'s kitchen, against her will}
\Gls{Tiff} visits the Petty household, and finds \Gls{MPetty} in the dilapidated kitchen, crying
about her husband's supposed innocence. \Gls{Tiff} gets the Feegles to clean up the place, and
realizes too late that her very presence in the house is likely to upset \Gls{Petty} when he wakes
from his drunken stupor.

\subsubsection{\Gls{Tiff} listens to her mother talk about witches being slandered in the village}
\Gls{Tiff} returns home to see \Gls{Went} being cleaned up after getting into a fight with a
neighbour who had been accusing \Gls{Tiff} of being an evil witch. Her mother tells her that the
sentiment in the village was slowly turning against her, in spite of her years of selfless medical
service to the people.

\subsubsection{\Gls{Tiff} helps a coachman with his bad joints}
\Gls{Tiff} is forced to crash into a fast-moving mail coach when \Gls{Wullie} sets fire to her
brromstick. The coachman is annoyed to have his paint scratched, but cheers up when he sees
the pointy hat on \Gls{Tiff}'s head. He drops the valuable disco ball made of glass when he inspects
it for damage, and screams in pain from his dislocated vertebra. Meanwhile, \Gls{APetty} sits in on
\Gls{Jeannie}'s divination ritual, and effortlessly completes the cryptic premonition, stating that
\Gls{Tiff} will meet a man with no eyes.

\subsubsection{\Gls{Tiff} faces an angry spirit accusing her of being an evil witch}
\Gls{Tiff} is interrupted by a spirit wearing filthy black robes, that asks her to stop whatever
black magic she is doing. The Feegles try to fight him, but pass right through him when they
pounce. The man vanishes right as \Gls{Tiff} notices the absence of any shadow cast by his body, and
the presence of two holes in his head where the eyes should be. \Gls{Carpet} notices none of this,
and gets up with his vertebra back in place, to his great relief.

\subsubsection{\Gls{Carpet} gives \Gls{Tiff} a free ride to Ankh-Morpork}
\Gls{Carpet} notices the disco ball being whole again, and \Gls{RobA} quielty whispers to \Gls{Tiff}
that he used Feegle magic to reverse the shattering of the ball. \Gls{Carpet} gladly offers her a
ride to Ankh-Morpork now that he is not liable for the disco ball, and asks her to take off the
pointy hat in view of the libel being spread against witches in the plains. \Gls{Carpet} drops her
off at the gates of Ankh-Morpork, and promises to consider her one of the good witches.

\subsubsection{\Gls{Tiff} meets \Gls{MProust} at the joke shop}
\Gls{Tiff} goes to the joke shop to find out if a dwarf can repair her damaged broomstick, and the
boy at the counter recognizes her as a real witch. He calls out to his mother in the basement, who
comes up to ask her if she can prove the fact that she is a witch. She introduces herself as
\Gls{MProust}, and asks \Gls{Tiff} to take off the hat as they walk through the city to the dwarf
workshop.

\subsubsection{\Gls{Tiff} listens to \Gls{Proust} talk about the source of her power}
\Gls{Tiff} realizes that \Gls{Proust}'s face is authentic, and that the evil witch masks being sold
by the joke shop are replicas of her actual face, complete with hooked nose and hairy warts. She
talks about the power in the city's cobblestones, and the layers of buried remains that make up its
foundations, as \Gls{Tiff} considers the possibility that \Gls{Proust} is abusing her gifts.

\subsubsection{\Gls{Proust} takes \Gls{Tiff} to the dwarf workshop to get her broom repaired}
The dwarves in the broom workshop become alert when \Gls{Tiff} mentions the Feegles tampering wtih
her broomstick. She tells them that they are friendly with her and out running an errand for her
at the moment. \Gls{Proust} tries to point out how eligible a bachelor her son is, and quickly sees
the disinterest in \Gls{Tiff}'s face.

\subsection{}
\subsubsection{\Gls{Tiff} }
\Gls{Tiff} and \Gls{Proust} go to a bar where the Feegles are making a commotion, and find
\Gls{WMArthur} being brought in by the city watch to knock them out. \Gls{Tiff} watches in amazement
as the imp drags out the Feegles one by one, as \Gls{Carrot} escorts \Gls{Roland} out of the
trashed building. \Gls{Tiff} spots \Gls{Leti} and her mother coming out with boxes full of fancy
clothes, and is forced to tell \Gls{Roland} in public about the death of his father.

\subsubsection{\Gls{Carrot} leads \Gls{Tiff} and the Feegles to the watch house}
\Gls{Roland} screams at \Gls{Tiff} for her inability to keep the \Gls{Baron} arrive, and she senses
the presence of the man with no eyes once again. \Gls{Carrot} places her under arrest for letting
the Feegles loose within the city, and asks \Gls{Proust} to hold her broomstick for safekeeping. On
the way to the watch house, \Gls{Carrot} talks about some other incidents of witch hunting out in
the countryside.

\subsubsection{\Gls{Proust} starts to talk about the old witch hunts across the Disc}
In the underground jail, \Gls{Proust} slaps \Gls{Tiff} when she starts to moan the loss of
\Gls{Roland}'s goodwill, and wonders what the mysterious spirit must have been. \Gls{Proust} recalls
other times in the past when witches were persecuted, and asks \Gls{Tiff} if she performed any
strong ritual recently, that might have attracted the spirit's attention.

\subsubsection{\Gls{Proust} talks about the city watch's relationship with witches}
\Gls{Proust} speculates that \Gls{Tiff} banishing the \Gls{Wint} triggered the rise of the
mysterious spirit, and this is why it is hunting her down specifically. She believes that the spirit
is also responsible for the hostility she just showed to \Gls{Tiff}, and reminds her that the city
watch turns a blind eye to witches in the city, expecting them to keep a low profile in turn.

\subsubsection{The Feegles make peace with \Gls{WMArthur}}
The Feegles sneak out of the holding cells, and travel to the ruined tavern, where they knock out
\Gls{Nobbs}, who is standing guard. Inside, \Gls{WMArthur} confronts them, and tells the story of
being adopted by gnomes in the mountains, since he had been found as an orphan. \Gls{RobA} tells him
that he must be some sort of Feegle, and proudly declares their duty to make trouble. Meanwhile,
\Gls{Proust} receives two trays with meals and a bottle of wine, much to \Gls{Tiff}'s surprise.

\subsubsection{\Gls{Haddock} sets \Gls{Tiff} and \Gls{Proust} free the next morning}
\Gls{Haddock} brings \Gls{Tiff} breakfast the next morning, and tells her that she is being set
free with a warning. The Feegles seem to have spent all night putting the tavern back together,
only to its orientation wrong. \Gls{Tiff} suspects Feegle magic when \Gls{Haddock} talks about how
the renovated tavern has become an attraction overnight, as she pushes through the crowd gathered
outside it.

\subsubsection{\Gls{Tiff} is rescued from a hostile mob by \Gls{Eskar}}
\Gls{Tiff} watches \Gls{Vimes} oversee the crowd control at the renovated tavern, and spots the
unsaid words that \Gls{Proust} had told her about coming from his mind. \Gls{Proust} enquies about
\Gls{SamJ}, and \Gls{Vimes} is immediately reminded of the remedy that he had asked her about
earlier. All of a sudden, the mysterious spirit walks through the crowd, turning them against her.
She is rescued by a mysterious witch who teleports her underground, and leads her to an abandoned
cottage abutting Unseen University's garbage dump.

\subsubsection{\Gls{Eskar} talks about the \Gls{CMan} and his incessant quest to kill witches}
The mysterious old woman introduces herself as \Gls{Eskar}, and talks about the death of an ancient
witch-finder, now nicknamed the \Gls{CMan} after he has risen as a spirit. She then talks about
\Gls{Tiff} kissing the \Gls{Wint}, and therefore becoming the \Gls{CMan}'s primary target for
possession.

\subsubsection{\Gls{Eskar} asks \Gls{Tiff} to stay alert when evading the \Gls{CMan}}
\Gls{Eskar} offers some cryptic hints about her time travel, and asks \Gls{Tiff} to flee when her
magic detector reacts to the \Gls{CMan}. She asks \Gls{Tiff} to keep in mind the fact that the
\Gls{CMan} might possess someone close to her, and to watch out for an opportunity to help herself.
The Feegles manage to navigate the garbage dump and find \Gls{Tiff}, just as she prepares to leave
the cottage through a tunnel.

\subsubsection{\Gls{Tiff} reaches her village by broomstick, and notices \Gls{WMArthur} joining
    the Feegles}
\Gls{Tiff} escapes from the city on her broomstick, as \Gls{Proust} runs away from the hostile mob.
She manages to outwit two of the men who manage to keep up with her, and wonders how many ugly
old women will get mistaken for witches by the end of the day. \Gls{Tiff} is shocked to see
\Gls{WMArthur} tag along with the Feegles, and is amazed by his appreciation for the fine arts.
When she lands in her village, she finds \Gls{Brian} and his men surrounding the Feegle colony with
shovels.

\subsubsection{\Gls{Brian} tells \Gls{Tiff} that \Gls{Roland} has ordered \Gls{APetty} tracked
    down}
\Gls{Tiff} manages to hold the Feegles at bay, and takes \Gls{Brian} aside to ask why he has come
to their colony. \Gls{Brian} tells her that \Gls{Roland} has ordered the colony destroyed as his
first act after ascending to the title of Baron. \Gls{Tiff} asks the guards to drop their weapons
and leave, while thinking about the rumours being spread about how she has swayed the mind of
young \Gls{APetty}.

\subsubsection{\Gls{Tiff} takes \Gls{APetty} to \Gls{Roland}'s castle}
\Gls{Tiff} convinces \Gls{APetty} to come see \Gls{Roland} and tell him that she is safe with the
Feegles, even if she has no interest in returning to her parents. \Gls{Jeannie} warns her that
\Gls{APetty} is extremely gifted with linguistic acumen, and warns her to keep the child safe from
\Gls{Roland} and his family. At the castle, \Gls{Tiff} notices the preparations for a funeral
followed shortly by \Gls{Roland}'s wedding, and walks past the staff too busy to pay attention to
her.

\subsubsection{\Gls{Roland} repeats the accusations against \Gls{Tiff} half-heartedly}
\Gls{Roland} talks about all the accusation being leveled on \Gls{Tiff} by \Gls{MPetty} and
\Gls{Spruce}, while struggling to fight through the memory-wiping magic of \Gls{Jeannie} when
\Gls{Tiff} tries to remind him of his time in the fairy realm. She tells him that a part of him is
aware of her innocence, and asks \Gls{APetty} to state her happiness in being away from her parents.

\subsubsection{\Gls{Tiff} visits the castle and spots the \Gls{DucheK} bullying the servants}
\Gls{Tiff} asks \Gls{APetty} the next morning if she remembers her miscarriage, and is glad to know
that \Gls{Jeannie}'s memory-wiping has done its job. At the castle, \Gls{Tiff} uses her camouflage
to eavesdrop on the \Gls{DucheK}, only to find her scolding \Gls{Leti} about keeping the servants
on a short leash. \Gls{Tiff} thinks about her parents arguing long ago about seizing power from the
\Gls{Baron}, and gets noticed by the \Gls{DucheK}.

\subsubsection{\Gls{Preston} defends \Gls{Tiff} using habeas corpus}
\Gls{Preston} responds to the \Gls{DucheK}'s request for a guard, and refuses her order to jail
\Gls{Tiff} in the dungeon. He reminds her that \Gls{Tiff} has not broken any laws, and uses the
exact same logic when she threatens to sack him. The \Gls{DucheK} leaves in a huff, and \Gls{Tiff}
is amazed by \Gls{Preston}'s literacy. She finds out that he had been taught to read at an early
age, and had been dismissed as an acolyte from the Church of Om for asking too many questions.

\subsubsection{\Gls{Tiff} listens to the castle cook repeat the rumours about her being spread by
    \Gls{Spruce}}
\Gls{Tiff} runs to the kitchen, where the cook has had an accident, and is clearly too drunk to be
working next to hot stoves. She hears the cook rant about her grand plan to punish \Gls{Roland} by
killing the \Gls{Baron}, and spirit-walks in an attempt to sniff out the \Gls{CMan}'s influence.
She finds no trace, and realizes that the cook is simply overwhelmed by her family life falling
apart, in addition to \Gls{Spruce} spreading rumours about her.

\subsubsection{\Gls{Tiff} is put under house arrest at the castle}
\Gls{Tiff} faces \Gls{Roland} and the \Gls{DucheK} in the main office, and refuses to take the
blame for the death of the drunk cook. She walks out of the office past the guards as they
suddenly collapse, and rests next to the main fireplace. \Gls{RobA} tells her that he is still angry
at them for trying to harm his colony, and vanishes as soon as \Gls{Brian} arrives with an official
order confining \Gls{Tiff} to the castle and its grounds. He confiscates her broom, surprised that
she accepts the arrest without any protest.

\subsubsection{\Gls{Tiff} locks herself in the castle's dungeon}
\Gls{Tiff} locks herself in the dungeon, which has now fallen into disuse except for a goat shed
inside it. \Gls{Roland} visits her after a while with the \Gls{DucheK}, and tells her that he only
wants her under observation till the wedding is over. The \Gls{DucheK} insults \Gls{Roland}'s
mother for her proletarian hobbies, and \Gls{Roland} finally stands up for himself by overriding
her orders to the guards.

\subsubsection{\Gls{Tiff} works out a deal with \Gls{Brian} giving her access to the village at
    night}
\Gls{Tiff} notices the words crowding \Gls{Letitia}'s mind, and realizes that she is an unwilling
participant in the \Gls{DucheK}'s schemes. After the others leave, \Gls{Tiff} reminds \Gls{Brian}
that she needs to be out and about every night to help the infirm in the village, including his
own mother. \Gls{Brian} decides to accept her plan to escape the cell each night, and return by
morning to save him any trouble from the \Gls{DucheK}.

\subsubsection{\Gls{Tiff} confronts \Gls{Leti} about her innate magical ability}
\Gls{Tiff} sneaks out of the dungeon using her broomstick, and flies to the top floor, where she
hears \Gls{Leti} sobbing in her room. She manages to use the guard's meal break to get into
\Gls{Leti}'s room, and learns that the girl has some innate aptitude for magic. \Gls{Leti} tells
her that her life circumstances prevented her from becoming a witch, and is amazed by the broomstick
when \Gls{Tiff} takes her out of the castle for privacy.

\subsubsection{\Gls{Tiff} witnesses \Gls{Leti} perform magic casually}
\Gls{Tiff} realizes that \Gls{Leti} performed some bogus spell meant to get \Gls{Roland} to hate
her, out of simple jealousy. \Gls{Tiff} clears up the fact that she and \Gls{Roland} have no
interest in each other anymore, and is glad to see the relief in \Gls{Leti}'s face. She is alarmed
when \Gls{Leti} picks up a broken branch and waves it around as if it were a fancy wand, only to
leave a trail of sparks.

\subsection{}
\subsubsection{\Gls{Leti} takes \Gls{Tiff} to her home}
\Gls{Tiff} learns that \Gls{Leti} has left her voodoo doll at her family home, and offers to fly
her there. \Gls{Leti} is glad to be given the opportunity to reverse the spell she put on
\Gls{Tiff}, and asks to ride in front. At the Keepsake mansion, \Gls{Tiff} spots some ghosts
haunting the corridors, as \Gls{Leti} points out how most of the buildings are now a care home for
the old and infirm.

\subsubsection{\Gls{Tiff} finds the book written by the \Gls{CMan} in \Gls{Leti}'s home library}
\Gls{Tiff} realizes that \Gls{Leti} has stumbled upon the basic tenets of witchcraft all by herself,
and wonders how excited \Gls{Tick} would be to meet her. \Gls{Tiff} feels the stink of the
\Gls{CMan} coming from the library in \Gls{Leti}'s room, and notices the large book on the table
that \Gls{Eskar} had talked about. The huge leather-bound tome starts to jump around, trying to
shake off \Gls{Tiff}, who wants to burn it in an attempt to get the \Gls{CMan} off her trail.

\subsubsection{\Gls{Tiff} is overwhelmed by \Gls{Leti}'s gift of a valuable tome}
\Gls{Tiff} tries to explain to \Gls{Leti} that the \Gls{CMan}'s book on burning witches acts as a
portal to facilitate his travel, and is surprised when \Gls{Leti} gifts her an ancient tome on
pocket dimensions as an apology. \Gls{Leti} suggests leaving through the back entrance as the
watchman starts his rounds, as \Gls{Tiff} wonders why the voodoo doll simply has the word `witch'
written on it instead of her name specifically.

\subsubsection{\Gls{Tiff} takes \Gls{Preston} along to cool down the \Gls{Baron} in the crypt}
\Gls{Tiff} asks \Gls{Leti} to tell \Gls{Roland} about the voodoo spell she performed, as they fly
back to his castle before dawn. She visits the \Gls{Baron}, who is in the crypt awaiting his
funeral, and asks \Gls{Preston} to watch her perform the heat transfer spell to keep the body cold.
\Gls{Preston} talks about the medicinal skills passed on to him by his grandmother, and bemoans the
lack of gold needed to get apprenticed to a doctor.

\subsubsection{\Gls{Roland} listens to \Gls{Tiff} accidentally express her interest in marrying
    him}
\Gls{Roland} apologizes to \Gls{Tiff} in his office, and speculates that \Gls{Leti} might not have
told him the whole story about her voodoo magic. She reminds him that \Gls{Magrat} is openly a witch
while being the Queen of Lancre, and gets him thinking about \Gls{Leti}'s desire to get trained as a
witch herself. She blurts out the idea that she would be happy to marry him, and \Gls{Roland} is
forced to hastily reaffirm his love for \Gls{Leti}.

\subsubsection{\Gls{Leti} asks \Gls{Tiff} for help with her duties as \Gls{Roland}'s wife}
\Gls{Leti} calls \Gls{Tiff} to her room, and asks her about what her duties would be during the
honeymoon. \Gls{Tiff} attempts an explanation, and notices the \Gls{CMan} staring at her through
the full-length mirror in the room. She tries her best to tune out his voice, but is forced to
listen to him talk about tracking her down and getting her burnt on the stake for being a witch.

\subsubsection{\Gls{Tiff} reads the book on portals, while thinking about the \Gls{CMan}}
\Gls{Tiff} is busy fussing over her wedding dress, and points out the smell of the \Gls{CMan},
without actually being able to see or hear him. \Gls{Tiff} refuses the offer of being a bridesmaid,
and quickly returns to the dungeon so that the \Gls{CMan} cannot get any further hints about her
location. She reads the book on pocket dimensions gifted to her by \Gls{Leti}, and notices the
Feegles crawl into the dungeon led by \Gls{WMArthur}.

\subsubsection{\Gls{Tiff} notices the \Gls{CMan} trying to track her down through the castle's
    tapestries}
\Gls{Tiff} asks the Feegles when they have last killed a human in a fight, and prompts serious
discussion among them. She promises \Gls{WMArthur} that their colony will be left alone, and is
surprised to see him resign from the Ankh-Morpork city watch to be with his own kind. She then goes
to the main fireplace, and sees the \Gls{CMan} running towards her through the tapestry depicting
an ancient battle.

\subsubsection{\Gls{Eskar} offers \Gls{Tiff} some timely advice}
\Gls{Eskar} transports \Gls{Tiff} to a pocket dimension and tells her that the other witches will
kill her without a second thought if she gets possessed by the \Gls{CMan}. \Gls{Tiff} returns to
real time, and waves a burning log threateningly at the \Gls{CMan}, convinced that he is still
afraid of fire. He retreats, just as \Gls{Preston} calls out to her about her lack of sleep the past
few days.

\subsubsection{\Gls{Proust} figures out that the \Gls{CMan} has found a suitable host}
\Gls{Proust} is summoned to the city prison, where the guards point out an escaped prisoner, who
was set to be hanged within a week. She takes one look at the superhuman feats of strength involved
in the escape, and hurries back to the joke shop to get her broomstick, so that she can warn
\Gls{Tiff} about the \Gls{CMan} having found a host to possess.

\subsubsection{\Gls{Tiff} thinks about the dying \Gls{Baron}'s painting from his childhood}
\Gls{Tiff} sleeps in one of the guest bedrooms, and sees the hare again in her dreams. \Gls{Preston}
wakes her up on the day of the funeral, and spots \Gls{GWea} arriving with \Gls{Magrat} and other
senior witches from Lancre. She talks to the Omnian Pastor who is about to oversee the rituals, and
is satisfied with the proceedings. She recalls the painting that the dying \Gls{Baron} had talked
about, and asks \Gls{Brian} if he had found a leather folder in the \Gls{Baron}'s office.
\Gls{Brian} says no, leading \Gls{Tiff} to conclude that \Gls{Spruce} must have stolen the folder on
her way out.

\subsubsection{\Gls{Ogg} helps the funeral attendees get into the wedding state of mind}
\Gls{Ogg} and \Gls{GWea} greet \Gls{Tiff}, and tell her indirectly that she is expected to deal with
the \Gls{CMan} on her own. \Gls{Tiff} asks \Gls{GWea} for tips, given that she had to deal with
the same problem many decades ago, and receives a cryptic reply about trusting herself. \Gls{Ogg}
takes note of how much \Gls{Tiff} seems to like \Gls{Preston}, and gets the funeral to sing along
to a happy song to lift the mood of the gathering.

\subsubsection{\Gls{Proust} talks about the origins of the \Gls{DucheK} in Ankh-Morpork}
\Gls{Proust} arrives by broomstick at the roof of the castle, with \Gls{Preston} helping open a
trapdoor that lets them climb down into the \Gls{DucheK}'s guest bedroom. \Gls{Tiff} listens to
\Gls{Proust} talk about finding a working broomstick and being forced to bring two other witches
along on her quest to warn her of the \Gls{CMan}. \Gls{Proust} speculates that the \Gls{DucheK} used
to be a dancer in Ankh-Morpork, and cooked up the story about her family perishing in a fire to
make a clean slate after marrying into the Keepsake family.

\subsubsection{\Gls{Tiff} figures out that the \Gls{DucheK} is desperately trying to keep her
    cover story from being blown}
In the main hall, \Gls{Tiff} is surprised to see \Gls{Proust} and \Gls{GWea} recognize each other by
name, and notices the \Gls{DucheK} sobbing in a corner. She finds the \Gls{DucheK} apologetic about
her past actions, and realizes that \Gls{Proust} has cut a deal with her in exchange for not
revealing her past as a dancer in the city. \Gls{GWea} accosts her and tells her that the witches
are prepared to kill her if she lets the \Gls{CMan} into her mind, and wishes her the best for the
next day.

\subsubsection{\Gls{Tiff} agrees to help \Gls{Preston} look for \Gls{Roland}}
\Gls{Tiff} visits the \Gls{Baron} in the crypt, and wonders what weapons she has to use against
the \Gls{CMan}. Back at the castle, she finds \Gls{Preston} needing her help tracking down
\Gls{Roland}, who has been trapped in a pigsty on the eve of his wedding, as per tradition. She
asks \Gls{RobA} not to interfere in her fight with the \Gls{CMan}, so that her reputation among the
gathered witches will not take a hit, and sets off to find her broomstick.

\subsubsection{\Gls{Tiff} finds \Gls{Roland} just as the \Gls{CMan} tracks her down}
\Gls{Tiff} finds \Gls{Roland} crawling out of the pigsty as she lands next to it, having flown all
the way to the edge of her steading. She finds \Gls{Leti} running to her, just as the \Gls{CMan}
telepathically taunts her. \Gls{Tiff} drags \Gls{Roland} and \Gls{Leti} with her, and runs across
the field with the \Gls{CMan} in hot pursuit, just as \Gls{Preston} prepares to set fire to it from
the far edge.

\subsubsection{\Gls{Tiff} escapes from the \Gls{CMan} using his deep-seated fear of fire}
\Gls{Tiff} jumps through the approaching wall of burning stubble quickly, and manages to get away
with minor burns. The mud from the pigsty protects \Gls{Roland} from getting injured, and \Gls{Leti}
gets away with damage to her lacy dress. \Gls{Tiff} then goes back to see the \Gls{CMan} slowly
fade away as his host body dies to the fire, being too afraid to leap past it. She banishes the
spirit, and returns to \Gls{Leti} to tell her that jumping past fire is an ancient wedding custom.

\subsubsection{\Gls{Tiff} asks \Gls{Roland} for some reforms in the village}
\Gls{Tiff} asks \Gls{Roland} to set up a school for the children of the village, using the renovated
barn next to her farm. She also asks for \Gls{Preston} to act as teacher for a while, so that he
can earn the gold needed to pay for apprenticeship as a doctor. \Gls{Roland} grants her the
requests, just as \Gls{Preston} hands over the gold recovered from \Gls{Spruce}, who had spent only
a small part of it in a neighbouring town. She also secures land ownership for the Feegles, and gets
them recognized as fellow inhabitants of the village.

\subsubsection{\Gls{Tiff} goes to the next village fair with \Gls{Preston}}
\Gls{Tiff} is grabbed by \Gls{Eskar} in her pocket dimension again, and meets her future self. She
realizes that the witch who peered at her from the shadows occasionally was her older self, with
some assistance from \Gls{Eskar} in the mystical arts of time travel. A months later, \Gls{Tiff}
attends the next village fair with \Gls{Preston}, and is gifted a beautiful black cloak by
\Gls{APetty}'s husband, who has finished training as a tailor.