\section{Interesting Times}


\subsection{}
\subsubsection{\Gls{Fate} starts a new board game on \Gls{Lady}'s request}
At the game board in Dunmanifestin, \Gls{Lady} challenges \Gls{Fate} to a game of Kingdoms, to be
played using the five factions vying for control of the Counterweight Continent. \Gls{Fate} accepts
her request, while forbidding the use of dice to play the turns.

\subsubsection{\Gls{Vetina} shows \Gls{Ridcu} the messenger albatross from the Agatean Empire}
\Gls{Vetina}, now Patrician of Ankh-Morpork, thinks about the uneasy truce between the bureaucracy,
and the wizards of Unseen University, now headed by Archchancellor \Gls{Ridcu}. On one of his social
visits, \Gls{Ridcu} is amused to see the \Gls{Patri} lead him through his garden, and into the
oversized coop for his messenger pigeons. He is alarmed to see a messenger albatross from the
Agatean Empire, as \Gls{Vetina} reminds him of the need for secrecy.

\subsubsection{\Gls{Vetina} asks \Gls{Ridcu} to find a great wizard for the Agatean empire}
The \Gls{Patri} decodes the Agatean pictograms in the message, asking for the Great Wizard to be
sent there as soon as possible. He asks \Gls{Ridcu} to find a scapegoat on whom they can pin this
responsibility, and he immediately starts to think about his rival, the \Gls{Dean} of the
University. Meanwhile, a shark converging on \Gls{Rince} as he lounges on seawater, is alarmed by
the \Gls{Lugg} appearing behind it.

\subsubsection{\Gls{Ridcu} talks to his inner council}
\Gls{Ridcu} summons the inner council and tells them about the Agatean empire's request, only to
see the \Gls{Libra} run out of the room as if to warn someone. He turns to the \Gls{Dean}, trying
to appeal to his ego and declaring him the greatest wizard in the room. \Gls{Stibb}, a budding
mathematician and inventor, tries to reassure everyone that his computing machine can perform the
calculations needed to teleport to the other side of the Disc, just as the \Gls{Libra} runs in with
\Gls{Rince}'s old pointy hat.

\subsubsection{\Gls{Rince} is forcibly teleported by \Gls{Stibb} to the Unseen University}
The inner council bickers about \Gls{Rince}, and their whereabouts during the reign of the
Sourceror, as \Gls{Ridcu} loses his temper, and calls them to order. \Gls{Stibb} rudely interrupts
\Gls{Rince}'s encounter with some Amazonian tribeswomen on a deserted island, and drags him back
to the inner council's chamber using the calculations supplied by his computer, named \Gls{Hex}.

\subsubsection{\Gls{Rince} indulges in some greasy junk food outside the University}
\Gls{Rince} runs into the market outside the University, and gorges on some junk food, having
developed a craving for it in his time on the deserted island. He is slapped by an old man, but
seems to be lost in the deliciousness of the snacks, much to the amusement of \Gls{Ridcu} and his
inner council. \Gls{Rince} comes to his senses as the \Gls{Libra} hands him his old hat.

\subsubsection{\Gls{Hong} speaks to his spy \Gls{TFHerb} about the summons for \Gls{Rince}}
\Gls{Hong}, newly ascended to the Lordship of one of the ruling families of the Counterweight
Continent, thinks about the recent assassination of his father, as he receives the news of his
albatross successfully flying away to the Circle Sea. The spy named \Gls{TFHerb} tells \Gls{Hong}
that the Great Wizard is famously incompetent, and will lead to the fizzling out of the Red
Revolution slowly taking root among the proletariat.

\subsubsection{\Gls{Rince} realizes he is being coerced into undertaking a dangerous mission}
Once he is awake, \Gls{Rince} is threatened by \Gls{Ridcu} with prosecution for impersonating a
wizard, and subtly corners him into taking on the quest outlined by \Gls{Vetina}. Meanwhile,
\Gls{Stibb} thinks about the self-assembling pieces of his computer \Gls{Hex}, as he receives a
spell in response to his latest enquiry. He thanks it, before going back to \Gls{Ridcu} thinking
about the absurdity of emergent intelligence.

\subsubsection{\Gls{Rince} prepares for his mission to the Agatean Empire}
\Gls{Rince} sees his shabby room preserved in its entirety, as he puts on his old robe, and sends
off the \Gls{Lugg} to stock up on potatoes from the underground kitchen. \Gls{Ridcu} finds him
midway through his preparations, and commends him on his eagerness to perform the act of great
service to wizardkind. \Gls{Rince} looks forward to the dullness and boredom supposedly available
in plenty inside the Agatean Empire.

\subsection{}
\subsubsection{\Gls{Stibb} gets the council to agree to his plan}
As the Red Army holds another secret meeting, with the mole \Gls{TFHerb} in attendance, they learn
that the Great Wizard is coming to the Agatean Empire to help their movement. Meanwhile, \Gls{Stibb}
successfully persuades the inner council and \Gls{Rince} to undertake the journey to the Agatean
Empire using the teleportation spell computed by \Gls{Hex}.

\subsubsection{\Gls{Stibb} sends \Gls{Rince} on his way using \Gls{Hex} and its computations}
\Gls{Stibb} starts to explain the issues with traditional traveling spells, as \Gls{Rince} listens
with growing horror. The other members of the council grow impatient with his mathematical lecture,
and ask him to get on with the spell-casting. \Gls{Rince} travels through the Discworld as he is
exchanged for an Agatean cannon, shaped to resemble a dog's mouth.

\subsubsection{\Gls{Rince} arrives in the Agatean Empire}
\Gls{Stibb} extinguishes the cannon's burning fuse, as \Gls{Ridcu} investigates the large ball
lodged inside its barrel, oblivious to the danger of a cannonball exploding in his face. He knocks
over some prison guards in the Agatean Empire, as he arrives in a snow-covered hillside holding a
long chain of manacled prisoners.

\subsubsection{\Gls{Rince} reunites with \Gls{Cohen}}
\Gls{Rince} recognizes \Gls{Cohen} among the prisoners, by his diamond dentures, and is relieved to
know that the prison guards will be dispatched by the legendary hero. \Gls{Cohen} then frees the
other prisoners chained to him, and asks them to run to safety. \Gls{Cohen} realizes that the slaves
he just freed had never experienced freedom in their lives, and were looking to him for orders. He
commands them to follow on foot, as he finds horses for himself and \Gls{Rince}.

\subsubsection{\Gls{Hong} learns of the arrival of the Great Wizard}
\Gls{Rince} learns of the siege underway in the capital city of HungHung, with the death of the
Emperor, and the resultant politicking between the five ruling families. Meanwhile, \Gls{Hong}
receives news from a messenger that \Gls{Rince} has arrived, and seemingly magicked away one of the
prototype cannons. He casually beheads the girl sent to serve him his tea, and searches her robes
for the poison meant to kill him.

\subsubsection{\Gls{Cohen} talks about the dictatorial ruling class of the Agatean Empire}
\Gls{Cohen} explains to \Gls{Rince} that the Agatean Empire runs on a tyrannical ruling class
treating the common-folk like slaves, depriving them of even the most basic human rights. He
believes that the isolationism and traditionalism in the Empire have convinced the people that the
governance they are experiencing is normal, and an improvement over the other kingdoms of the Disc.

\subsubsection{\Gls{Cohen} reaches his hideout in the mountains}
\Gls{Cohen} tries to dismiss the freed slaves following him, and is exasperated by their desperate
need for orders from an authority figure. He threatens them with death unless they go back to their
village, and is glad to see them shamble away. \Gls{Cohen} then leads \Gls{Rince} to his mountain
hideout, while talking about something worse than whips used to break the spirits of the peasants.

\subsubsection{\Gls{Hong} meets with the other lords to talk about the Red Army}
\Gls{Hong} envies the simplicity of the writing system in Ankh-Morpork, as the eunuch recording his
meeting with the lords of the other ruling families struggles with his calligraphic decorations.
He tells the gathered lords a Great Wizard has arrived from Ankh-Morpork to assist the Red Army in
their plot to assassinate the Emperor. The other lords are shocked by the news, and quickly recite
their own efforts to quell the revolution growing in their lands.

\subsubsection{\Gls{Hong} reassures the other lords about the quelling of the Red Revolution}
\Gls{Tang} claims not to have any knowledge of the foreigner's arrival, as \Gls{Hong} speculates
about the possibility that someone in a position of power is assissting the Red Army. \Gls{Hong}
dismisses the nobles, and retires to his private chamber, where he dreams of conquering
Ankh-Morpork, to taste its riches, and experience the efficiency of free-market enterprise.

\subsubsection{\Gls{Cohen} and the Silver Horder terrify \Gls{Rince}}
\Gls{Cohen} introduces \Gls{Rince} to the Silver Horde, his handpicked squad of old barbarian
heroes, all over the age of eighty, as \Gls{Rince} muses on the propsect of facing entire armies in
Hunghung. \Gls{Cohen} explains that the Red Revolution will give them the cover they need to sneak
into the capital city and steal something of great value, as he dismisses \Gls{Rince}'s concerns
about the Horde's age.

\subsubsection{\Gls{Rince} talks to \Gls{Saveloy} about the situation in Hunghung}
\Gls{Rince} walks up to a slim old man busy reading a book, who introduces himself as \Gls{Saveloy},
a geography teacher who decided to take up the barbarian lifestyle after retirement. He talks about
the ongoing cold-war in Hunghung, and is nonplussed by \Gls{Rince}'s insistence on riding away to
the coastline, to find a ship back to the Circle Sea.

\subsubsection{\Gls{Rince} is appalled by the state of the Agatean peasants}
\Gls{Rince} rides through a farming village, and is shocked to see the peasants toil away at their
fields, trying not to notice the strange man on horseback. He uses his broken Agatean to ask one
of the farmers for some food, and is shocked to see them run away in terror when he offers his horse
as payment.

\subsubsection{\Gls{Rince} reads \Gls{Twofl}'s book about Ankh-Morpork}
\Gls{Rince} reads the book lent to him by \Gls{Saveloy}, talking about an Agatean traveler
experiencing the city of Ankh-Morpork (\Gls{Twofl} ?), and is intrigued by mentions of a Great
Wizard in the scibblings. He fails to hear someone sneaking up on the peasant track behind him, and
gets knocked out. Meanwhile, the \Gls{Lugg} materializes in the mountains of the Agatean empire, and
starts to make sense of \Gls{Rince}'s position.

\subsubsection{\Gls{Rince} is sent to the Emperor's palace as a slave}
\Gls{Rince} is accosted by a minor noble in a palanquin, as his guards hold take him into custody
for stealing a horse. The noble issues a formal punishment of slavery in the royal palace, and
simultaneously talks to him in Morporkian, about a false story concocted to justify his presence in
the Agatean Empire without any identifying papers. \Gls{Rince} fails to recognize the nobleman as a
leader of the Read Army, intent on sneaking the prophesized leader in the Emperor's palace.

\subsubsection{\Gls{Rince} reaches a tavern in the Agatean countryside}
\Gls{Rince} runs away from the guards, and hides in a nearby village, pretending to be the officer
administering an examination for the position of sewage hauler. Eventually, \Gls{Rince} hears the
guards wander off, and walks to an Inn some distance away from the village. The landlord loudly
proclaims his refusal to serve any Red Army rebels, while giving him free bowl of soup upon seeing
the revolutionary book hidden in his robes.

\subsubsection{\Gls{Rince} recognizes \Gls{Twofl} as the author of the revolutionary book}
\Gls{Rince} peruses \Gls{Twofl}'s book of travels, and realizes that his descriptions of a free
country across the seas, has accidentally sparked a revolution within the Agatean peasants, who were
used to centuries of regimented chattel slavery. The landlord knocks \Gls{Rince} out, presumably to
take him to the Red Army hideout, as an impromptu drama troupe puts on a play in the tavern.

\subsubsection{\Gls{Rince} is kidnapped by the theatre actors}
\Gls{Cohen} almost entertains doubts about his Plan to storm the capital, as he asks \Gls{Saveloy}
about the secret route through the mountains. Meanwhile, \Gls{Rince} realizes he is being kidnapped
with a sack over his head, as a young girl talks to him from the front of the carriage. She is
skeptical about his claims of being the Great Wizard mentioned in \Gls{Twofl}'s book, even as he
tries desperately to defend his supposed feats of magic.

\subsubsection{\Gls{PrettyB} warns \Gls{Rince} about his value as a symbol of hope for the Red Army}
The woman holding \Gls{Rince} hostage reaveals herself as \Gls{PrettyB}, part of a traveling
troupe of artists, and instigators of the Red Revolution. She tells \Gls{Rince} that he his life was
in great danger if he turned out to be a phony wizard, and weakened the revolution by showing his
true nature.

\subsubsection{\Gls{Saveloy} thinks about breaching the Forbidden City within Hunghung}
\Gls{Saveloy} studies the geography surrounding the city of Hunghung, speculating that the Forbidden
City must have a secret water supply tunnel, which could be their means of breaking and entering.
\Gls{Cohen} fails utterly to grasp the intricacies of the plan, nodding along as if he has a rough
idea of \Gls{Saveloy}'s direction of inquiry.

\subsection{}
\subsubsection{\Gls{PrettyB} warns \Gls{Rince} to act the part of the Great Wizard}
\Gls{PrettyB} supervises \Gls{Rince} being deposited in an abandoned barn outside Hunghung, as two
other members of the Red Army greet him, identifying themselves as \Gls{LotusB} and \Gls{ThreeYO}.
\Gls{PrettyB} talks about the legend of a Great Wizard who had led another revolution thousands of
years ago, and warns him that he has inadvertently been trapped in the same role.

\subsubsection{\Gls{Rince} gets cornered by some city guards in Hunghung}
\Gls{Rince} manages to run away from the Red Army hideout, and emerges onto a bustling street market
in Hunghung. He elbows his way through the crowds, until he finds an empty square. Guards step out
of the trees around it, surrounding him, and ask him to bow down for the crime of tresspassing on
Imperial land. He realizes that they are ill-equipped to chase him, since they expect absolute
obedience from any peasant.

\subsubsection{\Gls{Cohen} allows himself to get captured by the city guards}
With the help of \Gls{Saveloy}'s rigorous training, \Gls{Cohen} and the Silver Horde manage to
submit to the city guardsmen examining their papers at the gates of Hunghung. They are dragged off
to the jailhouse nearby, where \Gls{Cohen} slits the guard captain's throat. The other soldiers,
confused about the chain of command, bow down expecting new orders from \Gls{Cohen}, as
\Gls{Saveloy} reminds him about the need to treat unarmed prisoners humanely.

\subsubsection{\Gls{Rince} talks to \Gls{Dibha} about trade opportunities in Ankh-Morpork}
\Gls{Rince} runs into street food vendor who reminds him of another in the square outside the
Unseen University. The vendor, named \Gls{Dibha}, starts to explain paper money, making \Gls{Rince}
recognize the counterfeiting opportunities to be had in exchanging them for the gold coins that were
the base currency. He sees a Red Army youth being dragged through the streets for the crime of
putting up posters, and learns that the likely punishment is getting is limbs chopped off.

\subsubsection{\Gls{Saveloy} tries to get the Silver Horde to play by the rules of civilization}
\Gls{Saveloy} is dismayed to see \Gls{Cohen} almost complete a transaction with a fruit merchant in
the markets of Hunghung, before he loses patience and knocks him out. \Gls{Saveloy} tries to get
\Gls{Caleb} to purchase a duck from a woman in the market, and is pleased to see him resisting
his barbarian instincts when talking to her.

\subsubsection{\Gls{PrettyB} forces \Gls{Rince} to rescue \Gls{ThreeYO}}
\Gls{TFHerb} and \Gls{LotusB} talk about \Gls{Rince} being the Great Wizard, and of the stories
written by \Gls{Twofl} in his book detailing his magical prowess. \Gls{TFHerb} remains skeptical of
the claims in the book, until \Gls{PrettyB} corners \Gls{Rince} into mounting an expedition into
the dungeons beneath the Forbidden City, in the hopes of rescuing \Gls{ThreeYO}.

\subsubsection{\Gls{Rince} is coerced into mounting a rescue operation for \Gls{ThreeYO}}
\Gls{Rince} is alarmed to find children surrounding him in the musty cellar, describing themselves
as the Hunghung cadre of the Red Army. He resolves to play along with \Gls{PrettyB}'s plan, and
make a run for it at the first opportunity that presented itself. Meanwhile, the \Gls{Lugg} breaks
into an enclosure for other sentient pearwood trunks, and beats up some other chests seeking to
bully one of their own.

\subsubsection{\Gls{Saveloy} thinks about his plan to penetrate the Forbidden City}
\Gls{Saveloy} works out the finer details of the plan to use fireworks purchased from the market,
as the Silver Horde enjoy their first taste of civilization. Meanwhile, \Gls{PrettyB} pulls
\Gls{Rince} to the side, and tells him that she immediately recognized him as an unskilled, but
extremely lucky wizard, from her readings of \Gls{Twofl}'s book.

\subsubsection{\Gls{TLWang} hears the barbarians in the water pipes underneath the Forbidden City}
\Gls{TLWang}, newly appointed assistant to the \Gls{Empe}, bemoans the descent of the Agatean
Empire, into a land of inequality, decadence, authoritarianism, and martial law. He hears some
sounds coming from under the grounds of the palace, when out for a stroll, and follows them across
the garden.

\subsubsection{\Gls{Saveloy} uses his knowledge of the water supply system to infiltrate the
    Forbidden City}
\Gls{Saveloy} tries to explain to the Silver Horde that the fireworks are rigged to blow a hole in
the Forbidden City's outer wall, as a distraction meant to enable their infiltration. Meanwhile,
\Gls{Rince} is egged on by \Gls{TFHerb} at the walls of the Forbidden city, prompting him to think
that \Gls{TFHerb} is a double agent sent by the Empire to ensure the failure of the Red Revolution.

\subsubsection{\Gls{Rince} pretends to be responsible for \Gls{Saveloy}'s explosion}
\Gls{Rince} is surprised to see \Gls{Saveloy}'s fireworks punch a hole in the wall of the Forbidden
City, flattening all the Red Army members gathered around him to witness his magic. A while later,
some city guards capture \Gls{Rince}, and send him to the \Gls{Empe}'s jail, as the Red Army
cadre start to recover from the shockwave of the blast.

\subsubsection{\Gls{Saveloy} gets the Silver Horde to don their eunuch disguises}
Once inside the water supply room of the Forbidden city, \Gls{Saveloy} asks the barbarians to put
on the eunuch costumes they had purchased earlier. \Gls{OldVin} worries about the songs that will
be sung about their cowardly approach to the mission, until \Gls{Cohen} reminds him of the fact
that minstrels can be bribed.

\subsubsection{\Gls{Hong} deals with the latest threat to his life}
\Gls{Hong} kills an elite assassin sent to kill him, while distracted by the imperfections in his
latest sword, fresh from the forge. He sends new orders via messenger to a guard captain in the
city, while distracted by the sloppiness of the latest attempt at his life. Meanwhile, \Gls{Rince}
is brought to the \Gls{Empe}'s court, where he is alarmed to see a frail old man, confined to an
ornate bed.

\subsubsection{\Gls{Rince} faces the Agatean \Gls{Empe} in his throne room}
\Gls{Hong} arrives at the throne room, in time for the \Gls{Empe} to declare his liking for
\Gls{Rince}, and his intention to keep the foreigner around as a funny pet. The \Gls{Empe} dismisses
his courtiers, and retires for the night, after ordering \Gls{Rince} to be confined to the special
dungeon. \Gls{Rince} is alarmed by the sly wink \Gls{Hong} gives him, as the \Gls{Empe} sentences
a courtier to death for some perceived insult.

\subsubsection{\Gls{Saveloy} and the barbarians hide in plain sight}
\Gls{Hong}, now the \Gls{GViz} of the Agatean Empire, thinks about his efforts to make the Red Army
appear stronger than it was, including the gift of the Great Wizard. He eagerly anticipates the
Red Army's eventual slaughter, and the counter-revolution that he would ignite in the aftermath.
Meanwhile, \Gls{Saveloy} leads the Silver Horde through the corridors of the Forbidden City, in the
guise of eunuchs carrying paperwork to some office.

\subsubsection{\Gls{Rince} is reunited with \Gls{Twofl} in the Forbidden City's prison}
Inside his prison cell, \Gls{Rince} is alarmed to hear \Gls{Twofl}'s muffled voice from the cell
next to his. He manages to push a brick free and learns that \Gls{Twofl} is likely stuck in jail
because of errors in paperwork. \Gls{Twofl} innocently states that he only meant his book as a form
of light entertainment, and not a document that might foment a revolution.

\subsubsection{\Gls{Saveloy} finds a tax-collector inside the Forbidden City's offices}
\Gls{Saveloy} and the horde walk into an important-looking office within the Forbidden City, to find
a tax-collector inside, lost in his paperwork. The official, who identifies himself as \Gls{SixBW},
quickly realizes that the old men are not eunuchs, and quite happy to kill him should he call for
the guards. \Gls{Saveloy} forces \Gls{SixBW} to show them around the Forbidden City complex, as the
barbarians resist the urge to cut his head off.

\subsection{}
\subsubsection{\Gls{Twofl} and \Gls{Rince} spend time in the prison}
\Gls{Twofl} spends the night remembering his time in Ankh-Morpork, as \Gls{Rince} tries desperately
to make a dent in the stone blocks making up the jail cell. In the morning, they hear a scream in
the distance, which \Gls{Twofl} believes is the sign that the \Gls{Empe} has woken up. Someone stabs
the guard outside \Gls{Rince}'s cage, and uses his keyring to unlock the cell. \Gls{Rince} uses the
opportunity to free the other prisoners.

\subsubsection{\Gls{Rince} frees the Red Army in the Forbidden City's prison}
\Gls{Rince} is shocked to discover that \Gls{PrettyB} and \Gls{LotusB} are \Gls{Twofl}'s daughters.
He frees the rest of the Red Army children, and comments on the curious absence of \Gls{TFHerb}.
He sees \Gls{PrettyB} coming to the same realization as him, that \Gls{TFHerb} is probably a double
agent, sent to monitor the Revolution and ensure its failure.

\subsubsection{\Gls{SixBW} is amazed to see the invaders take on the ninjas of the Agatean Empire}
\Gls{SixBW} takes advantage of the barbarians being lost, to lead them to the ninja training
grounds. A group of ninjas surround them, with \Gls{SixBW} asking the invaders to surrender, or
face the finest warriors in the kingdom. He watches the barbarians casually face down the ninjas,
as \Gls{Saveloy} explains the lifetime of experience they have staying alive while being
outnumbered.

\subsubsection{\Gls{SixBW} wishes to join \Gls{Cohen}'s troop}
\Gls{Truckle} holds a sword at \Gls{Saveloy}'s throat when the teacher reveals the true meaning of
their disguises. \Gls{Cohen} gets him to back down, by reminding his fellow barbarian that the
mission merely required them to pretend to be harmless old eunuchs to hide in plain sight.
\Gls{Saveloy} is happy to see \Gls{SixBW} mulling over the idea of joining their group as an
accountant, and is shocked to see the stagnation of technology in the Empire.

\subsubsection{\Gls{Rince} explains the futility of a violent rebellion}
\Gls{Rince} tries to persudae the Red Army that the night's events were very suspicious, as they
find all the prison guards dead, with a map leading to the Emperor's chamber conveniently lying
beside one of the soldiers. He asks the children to go back to the safety of the prison, intending
to run away from the Forbidden City, but is cornered by \Gls{PrettyB} into investigating the
palace.

\subsubsection{\Gls{SixBW} understands \Gls{Cohen}'s plan}
\Gls{SixBW} tries to explain the idea of taxation to the Horde, who fail to see the point of taking
only a fraction of the money from a merchant, and letting him live afterward. \Gls{Saveloy} keeps
saying no to all of his guesses regarding the tresure they were planning to steal, until
\Gls{SixBW} works out their intentino to kidnap the \Gls{Empe}.

\subsubsection{\Gls{PrettyB} and \Gls{Rince} reach the \Gls{Empe}'s chamber}
\Gls{PrettyB} refuses to heed \Gls{Rince}'s warnings about the Red Army being set up for the
\Gls{Empe}'s murder, and guides him deeper into the residential area of the Forbidden City. They
eventually come to the Emperor's chamber, to find him lying very still in his ornate bed. The
guards turn on \Gls{Rince}, framing him for the death of the \Gls{Empe}, causing him to flee the
chamber.

\subsubsection{\Gls{SixBW} watches \Gls{Cohen} take over the Agatean throne}
\Gls{PrettyB} considers the idea that \Gls{TFHerb} is a double agent meant to guide the Revolution,
and to provide his master the excuse for a counter-revolutionary tightening of laws. \Gls{SixBW}
watches \Gls{Cohen} walk up to the empty throne and sit on it, realizing that the current \Gls{Empe}
led a reclusive life, with only a handful of people even knowing what he looked like. \Gls{Saveloy}
promises to elevate him to the highest position in the civil service, and asks him to gather all
those who know the \Gls{Empe}'s face for disposal.

\subsubsection{\Gls{TFHerb}'s plan to use the Red Army as a scapegoat fails}
\Gls{Rince} stumbles into the sumo wrestler quarters, and convinces them into ganging up on the
palace guards. Meanwhile, \Gls{Hong} receives news of the Red Army not showing themselves at the
\Gls{Empe}'s chamber, to act as scapegoats for his murder. He orders \Gls{TFHerb} to be imprisoned,
pending execution. Meanwhile, \Gls{Cohen} witnesses the handful of courtiers assembled in front of
him, asking them if they had any problems accepting him as their new ruler.

\subsubsection{\Gls{Cohen} kills the old \Gls{Empe}'s chamberlain for rejecting his claim to the
    throne}
\Gls{Rince} runs into the laundry hall, and realizes that a sudden change of disguise might throw
off the guards chasing him, and allow him to blend into the bureaucrats milling about in the
Forbidden City. The head chamberlain raises his voice against \Gls{Cohen} and is swiftly killed,
as the rest of the Silver Horde deal with the \Gls{Empe}'s elite guards. The other courtiers pledge
their allegiance to \Gls{Cohen}, in the hopes of maintaining their decadent lifestyle under the new
regime.

\subsubsection{\Gls{Rince} outsmarts the guards chasing him}
\Gls{Rince} pretends to be a servant in the laundry hall, and touches his wizard hat daintily, to
make a show of falling down, bent over in great pain. The guards pursuing him take the hint, and
run away from the cursed hat, only for \Gls{Rince} to get whipped by the chief laundryman, in
response for shirking his duties for the day.

\subsubsection{\Gls{Hong} poisons the food meant for \Gls{Cohen}}
\Gls{Hong} walks in on the courtiers trying to get the kitchen staff to prepare food for their
new \Gls{Empe}, and decides to poison the meat right in front of them. The courtiers make no attempt
to stop this subterfuge, believing that their lives would remain the same regardless of who sits on
the throne. \Gls{Rince}, in the disguise of a kitchen servant, wheels the tray of food from the
kitchen to the throne room.

\subsubsection{\Gls{Rince} saves \Gls{Cohen} from the poisoned food}
\Gls{Rince} warns \Gls{Cohen} about the poisoned food, causing him to summon two shifty looking
courtiers, to taste the food. One of them dies in a small explosion, and \Gls{Cohen} orders the
other to be imprisoned. Meanwhile, \Gls{Saveloy} goes off on a rant about the Silver Horde having
wasted their lives looting and pillaging, and of how the reformation of the Agatean Empire was a
unique opportunity for them to leave their mark on world history.

\subsubsection{\Gls{Rince} reminds himself of the Red Army still stuck in prison}
\Gls{Rince} asks for the Red Army still stuck in the prison to be rescued, and \Gls{Cohen} sends one
of his friends to oversee their safe transfer to the throne room. Meanwhile, the newly ascended
Chamberlain warns \Gls{Cohen} about \Gls{Hong}'s scheming, and the possibility of the warlords
forming an alliance to march on Hunghung. \Gls{Hong} and some other generals enter the throne room,
to parley with \Gls{Cohen}.

\subsubsection{\Gls{Cohen} parleys with \Gls{Hong}}
\Gls{Cohen} rejects \Gls{Hong}'s offer of surrender, and carefully avoids any mention of the true
size of his invading force. \Gls{Rince} tries to scare the other warlords with the rumours of
invisible ghosts being led by the barbarian generals, but \Gls{Hong} refuses to fall for the bait.
\Gls{Saveloy} believes that no more assassination attempts will happen, now that war has been
formally declared.

\subsubsection{\Gls{Rince} hopes to use misinformation and rumours to break the enemy camp's spirit}
\Gls{Rince} uses \Gls{Dibha} to spread rumours about the coming army of invisible vampire ghosts
through the enemy camp, believing that centuries of propaganda about the lands outside the Agatean
Empire might prove useful in winning the war against \Gls{Hong}. \Gls{Rince} sets the children of
the Red Army loose within the enemy camp, spreading rumours about the invisible ghost army that
may or may not be marching to devour them.

\subsubsection{\Gls{Rince} finds \Gls{Death} and \Gls{War} at \Gls{Hong}'s army camp}
\Gls{Rince} runs into \Gls{Death} and \Gls{War} surveying \Gls{Hong}'s encamped army, and is
surprised to learn that even \Gls{Death} does not know the outcome of the coming battle. He returns
to the safety of the palace, leaving \Gls{Death} and \Gls{War} to set up their picnic, invisible to
everyone else.

\subsubsection{\Gls{Hong} decides to take morale for granted}
\Gls{Hong} asks his diviner to give a false prediction saying they would win the coming battle with
overwhelming advantage, as the gathered warlords express their doubts about the invading army of
vampire ghosts. \Gls{Hong} orders the circulation of new rumours stating that the Agatean ancestors
were also rising as a ghost army to counter the enemeies, believing that the common soldiers would
remain unfazed by ghosts on both sides.

\subsubsection{\Gls{Stibb} sets his computer to finding \Gls{Rince}'s position}
\Gls{Hong} takes out his secret outfit, that makes him look like a minor noble of Ankh-Morpork, and
anticipates the opportunity to wear it as the ruler of the city. Meanwhile, \Gls{Hex} is put to task
finding the location of \Gls{Rince}, at the behest of the inner council, who want to retrieve him
so they can send back the huge Agatean cannon that they inadvertently received during the
teleportation process.

\subsubsection{\Gls{Cohen} and the barbarians prepare for the battle at dawn}
\Gls{Cohen} and the Silver Horde discuss their chances in the coming fight, and reject
\Gls{Saveloy}'s offer of a tactical retreat. \Gls{Saveloy} eventually realizes that death in the
field of battle is preferable to life as a school teacher, and pledges to fight beside \Gls{Cohen},
in spite of having no knowledge about war.

\subsubsection{\Gls{Rince} is reunited with the \Gls{Lugg}}
\Gls{Rince} repeatedly tells the Red Army that there are no Great Wizards ready to perform feats of
magic to solve their problems, and that the barbarians are foolish for taking on astronomical odds
on the battlefield. He decides to desert the city, and is joined by the \Gls{Lugg} and its mate.

\subsubsection{\Gls{Cohen} parleys with \Gls{Hong}}
\Gls{Cohen} parleys with \Gls{Hong} before the battle, causing \Gls{Saveloy} some amusement as he
asks for the Agateans to surrender and avoid unnecessary death. Afterward, \Gls{Truckle} speculates
that the enemy warlords might want them alive, making it easier for them to slaughter the enemy
troops.

\subsubsection{\Gls{Rince} gets to the top of the small hill outside Hunghung}
\Gls{Rince} talks to a farmer next to the circular hill outside Hunghung, and learns that he has no
conception of the impending change in rulership, given how much his life is confined to his
farmland. He walks to the small hill, to find a rusty building in ruins. He takes no notice of the
sapient pears growing in large numbers at its base, and climbs the hill, as a thunderstorm gathers
over Hunghung.

\subsubsection{\Gls{Hong} decides to take charge of the battle}
\Gls{Hong} is incensed by the warlords hesitating to charge the barbarians head on, and of the
reports of increasing desertion among their armies. He decides to lead the charge himself, and
dismisses the new rumours stating that the barbarians are the Indestructible Great Sages from some
distant land.

\subsubsection{\Gls{Rince} falls into the cavern underneath the hill}
\Gls{Rince} holds on to a rotting log, as the ground beneath him starts to give way, indicating an
uncertain fall in the darkness. He spots a small yellow butterfly landing on his hat and shoos it
away. As self defense, the butterfly of chaos summons a miniature thunderstorm to haunt \Gls{Rince},
and causes the log holding him up to collapse.

\subsubsection{\Gls{Rince} navigates through the dark cave}
\Gls{Rince} spots a large warrior staring at him when he lights a match to dispel the darkness
inside the cave. Meanwhile, \Gls{Cohen} notices the strange yellow cloud approaching from the
horizon, and marvels at the swarm of butterflies as they approach the hill outside Hunghung.
\Gls{Rince} stumbles around in the dark cave, and pulls a lever he finds, believeing it could not
possibly be a trap.

\subsubsection{\Gls{Cohen} and the horde face off against \Gls{Hong}'s elite warriors}
\Gls{Cohen} and the Silver Horde charge into the Agatean army, who refuse to engage them out of
fear for the closing thunderstorm. The storm induced by the swarm of chaos butterflies starts to
send lightning down into the massed ranks of the Agatean army, forcing them to back off. \Gls{Hong}
arrives with his samurai warriors, only to see the barbarians cut them down as \Gls{Cohen}
distracts them with a party trick.

\subsubsection{\Gls{Rince} dons the magical armour of \Gls{OSMirr}}
\Gls{Rince} sees some magical globes suspended from the ceiling absorb the lightning from the storm,
and illuminate the cavern. He notices a large pool of mercury, with an ornate gold sarcophagus on
its edge, bearing the inscription \Gls{OSMirr}, the founding Agatean Emperor. He dons the magical
armour and stands up, noticing the Red terracotta Army wake up from their magical slumber.

\subsubsection{\Gls{Hex} outputs the spell to retrieve \Gls{Rince}}
\Gls{Stibb}'s request for the spell to retrieve \Gls{Rince} goes wrong, when a butterfly of chaos
lands on \Gls{Hex}, disturbing one of its computational ants with a drop of nectar. He believes that
naming the machine, might have induced some unintentional sentience in it, as his assisstant informs
him of \Gls{Hex} providing answers for questions he had not asked it yet.

\subsubsection{\Gls{Cohen} and the Silver Horde are saved by the Red terracotta Army}
\Gls{Rince} tests out the controls in the magical gloves, allowing him to control the Red Army, and
is pleased that they are on his side. Meanwhile, the Red terracotta Army rise from the ground to
march on the Agatean army, scattering the five warlords into chaos and mutual suspicion. \Gls{Cohen}
and the barbarians decide to return to the palace, believing \Gls{Hong} is also headed there. The
gathering clouds burst, making the battlefield muddy, and making it even more difficult for the
five Agatean clans to distinguish each other's uniforms.

\subsubsection{\Gls{Cohen} officially becomes the Agatean Emperor}
\Gls{Cohen} walks into Hunghung through the gates, with some Red Army golems acting as an honor
guard. He asks \Gls{Saveloy} to make a proclamation ending chattel slavery, and giving a fair share
of the profits to the peasants. \Gls{Cohen} sits down on the Agatean throne, with \Gls{SixBW}
announcing to the court that he has been accepted as the reincarnation of \Gls{OSMirr}. Meanwhile,
\Gls{Rince} tries to use the terracotta golems to scribble on the city walls that he needs help
taking off the magical armour.

\subsubsection{\Gls{Twofl} works out \Gls{Rince}'s desperate attempt to ask for help}
\Gls{Saveloy} is dismayed to learn that there can be no empire without a cleansing of the old guard,
and is amused by a terracotta golem walking into the throne room and doing charades. \Gls{Twofl}
recognizes \Gls{Rince} trying to send a message, and rescues him from the mudslide in the tomb of
\Gls{OSMirr}. He tells \Gls{Rince} that \Gls{Cohen} has offered him the position of Chief Wizard,
given how he reanimated the terracotta army to turn the tides of battle.

\subsubsection{\Gls{Rince} is paraded in front of \Gls{Cohen} by \Gls{Hong}}
\Gls{Hong} kidnaps \Gls{Rince} as he walks back to the palace with \Gls{Twofl}, and tells him that
will be publicly executed to send a message to the people about the false myth of the Great Wizard.
\Gls{Hong} holds \Gls{Rince} hostage as \Gls{Cohen} comes out of the palace to face him, just as
\Gls{Stibb} casts his teleportation spell, making \Gls{Rince} vanish into thin air.

\subsubsection{\Gls{Twofl} decides to confront \Gls{Hong} for the murder of his wife}
\Gls{Twofl} tells his daughters that \Gls{Hong}'s men had killed their mother many years ago in some
minor scuffle, and declares his vengeance. As \Gls{Hong} draws his sword, amused at the clerk's
inability to handle his own blade, the ornate cannon arrives at \Gls{Rince}'s position, with its
fuse lit, and blows him to pieces when it fires.

\subsubsection{\Gls{Stibb} realizes that his teleportation spell has misfired}
\Gls{Twofl} sees the \Gls{Lugg} arrive with its mate and their children, as \Gls{Cohen} appoints him
Grand Vizier. He is eager to take on his new role in the court, as a valkyrie takes \Gls{Saveloy}
towards a barbarian conception of heaven. Meanwhile, \Gls{Stibb} realizes that his spell has gone
wrong, leading to a three way substitution, with \Gls{Rince} being teleported to the unknown
continent of XXXX, and a strange beast sent to the Unseen University in his place.

\subsubsection{\Gls{Rince} ends up in XXXX as a result of \Gls{Hex} botching its calculations}
The inner council discourage \Gls{Stibb} from searching for \Gls{Rince} again, and trying to
retrieve him, afraid of what strange object might fly into them next time. Meanwhile, \Gls{Rince}
is shaken awake in XXXX by some tribal men wearing loincloths and pointing spears at thim. They
give him a boomerang, which he throws away with all the force he can muster, tired of going on any
more adventures.