\section{Jingo}


\subsection{}
\subsubsection{\Gls{SolidJ} notices his usual fishing spots being empty}
At the middle of the Circle Sea, between the cities of Ankh-Morpork and Al Khali, the fisherman
\Gls{SolidJ} despairs at the absence of any valuable squid at the usual spawning grounds. He spots
a fisherman from Klatch rowing furiously to his spot, and asks his son \Gls{LesJ} to man the sails,
so he can prepare to fight.

\subsubsection{The two fishermen explore the rising city with their sons}
\Gls{LesJ} points out the giant city rising up from the Circle Sea, prompting \Gls{SolidJ} to
row away as fast as he can toward the coast of Ankh-Morpork. The two pairs of fishermen realize
that the city is rising too fast to row away from, and decide to explore it on foot, hauling their
boats over their heads.

\subsubsection{\Gls{Vimes} pays attention to the speakers in Sator Square}
Meanwhile, a small harbour wave lashes the coast of Ankh-Morpork as a result of the rising city,
raising no eyebrows whatsoever. \Gls{Vimes} is busy observing the evangelists plying their trade at
the City Square next to the University, and notices some xenophobic orator capturing the attention
of the crowds.

\subsubsection{\Gls{Vimes} shooes away an orator stoking hatred against Klatch}
\Gls{Vimes} confronts the trader lamenting his loss of precious cargo to Klatchian pirates, and
identifies him as \Gls{Jenkins}, whose cargo is fish organs and offal. \Gls{Jenkins} is flustered
by \Gls{Vimes} making holes in his accusations, and hastily leaves the podium, making the crowd lose
interest.

\subsubsection{\Gls{Vimes} listens to people claiming Leshp for Ankh-Morpork}
\Gls{Vimes} hears more criers shouting about the newly risen continent of Leshp, and of how Klatch
was intruding in land that rightfully belonged to Ankh-Morpork. \Gls{Detri} reminds him that he can
sense a tide of jingoism building slowly within the city, as a messenger pigeon arrives from the
Patrician.

\subsubsection{\Gls{Vetina} struggles to deal with the xenophobia in the city council}
\Gls{Vetina} listens avidly to his city council trying to prove their superiority in comparison
to Klatch, and remains unsatisifed by their empty boasts. \Gls{Slant} starts to talk about the
centuries old documents in the city vaults that prove Ankh-Morpork's claim on Leshp, and wonders
if the Klatchians are out to steal the territory from under their noses.

\subsubsection{\Gls{Vimes} asks his officers to gather for a debriefing}
\Gls{Vimes} walks into the Great Hall to drag \Gls{Vetina} out of the meeting, and asks
\Gls{CheeryL} to send pigeons asking his officers to assemble for a meeting. He notices more
citizens than usual in front of the palace, waiting expectantly for some sort of declaration.

\subsubsection{\Gls{Vetina} dismisses the city council's suggestions about a standing army}
\Gls{Vetina} explains to the city council that Ankh-Morpork does not have a standing army, and
has no likely allies amongst its neighbouring states. The last wars had been waged many centuries
ago, and resentment was still flaring bright in the minds of the other city-states. When the
council suggests hiring mercenaries, \Gls{Vetina} reads out the taxes owed by the Guilds, and asks
\Gls{Vimes} to set up a special unit to recoup the back-taxes owed to the city treasury.

\subsubsection{\Gls{Vimes} is alarmed to learn that a highly ranked Klatchian envoy is visiting}
\Gls{Vimes} scoffs at the nobility suggesting they use their private wealth to raise their own
regiments, but \Gls{Vetina} is forced to accept the idea, given the state of his own coffers. He
talks about Prince \Gls{Khufu} of Klatch arriving as an envoy to Ankh-Morpork, and asks \Gls{Vimes}
to lead the procession at the University that will receive him.

\subsubsection{\Gls{Vimes} is asked to lead the reception for the Klatchian prince}
\Gls{Vimes} is shocked to learn that \Gls{Vetina} asked his wife \Gls{Ramkin} to get him ready
for the banquet at the University. He dreads having to secure the streets from the citizens seeking
to throw eggs onto the Klatchian dignitary, as \Gls{Vetina} warns him about the xenophobic sentiment
on the rise.

\subsubsection{\Gls{Carrot} helps reform the child gangs of Ankh-Morpork}
\Gls{Carrot} tries to get the child gangs to participate in some youth sports, as Constable
\Gls{Shoe} informs him of a hostage situation requiring his attention. \Gls{Carrot} asks the two
child gangs to be on their best behaviour, till their next community outreach event.

\subsubsection{\Gls{Nobby} and \Gls{Colon} discuss the contrast between the Klatchains and
    themselves}
\Gls{Nobby} and \Gls{Colon} relax at the city harbour, talking about the relative superiority of
their own civilization to that of Klatch. \Gls{Nobby} fails to see how they are any better than the
their neighbours, but chooses to defer to \Gls{Colon}'s authority on the subject anyway.

\subsubsection{\Gls{Carrot} deals with \Gls{Angua} being taken hostage by some amateur thieves}
\Gls{Carrot} asks the thieves at the diamond shop to come out with their hands in the air, as
\Gls{Angua}, who had been taken hostage, morphs into wolf form to growl at them inside the shop's
safe-room. After the thieves confess to all the allegations leveled at them by \Gls{Shoe}, he
arrests them and escorts them to the Watch House.

\subsubsection{\Gls{Vimes} prepares to address the full strength of the City Watch}
\Gls{Vimes} is shocked to see the strength of the City Watch, as they assemble for the briefing.
\Gls{Carrot} points out that he had signed all of their appointment orders when he hastily
stamped all of the paperwork piled up on his desk. He is alarmed to find the zombie \Gls{Shoe} and
the gnome \Gls{BSwires} among the newly sworn Constables, and thinks back to the early days of the
Watch.

\subsubsection{\Gls{Vimes} aborts his speech about law and order halfway through}
\Gls{Vimes} struggles to get his point about policing across, and chooses to abort his tirade about
the difference between Watchmen and soldiers. He warns the hall about the rise of xenophobic
sentiment within the city, and orders them to stake out the procession path that the Klatchian
envoy is to ride on the next morning.

\subsubsection{\Gls{OssieB} takes up position on a rooftop with his bow}
\Gls{OssieB} thinks about his time spent at the archery range, as his landlady Mrs. \Gls{Spent}
harangues him about last month's rent. He braves the heavy rain, as he climbs a high roof in the
middle of the night with his bow, to wait for his target. Meanwhile, \Gls{Nobby} talks about his
bad luck when it comes to relationships, leading \Gls{Angua} to chuckle internally at his naivete.

\subsubsection{\Gls{Vimes} and \Gls{Carrot} stop a Klatchian shop being firebombed}
\Gls{Vimes} sees \Gls{Carrot} join him on his night-time stroll through the streets, and runs to the
site of a horrified scream echoing through the city. He puts out a small fire in a shop, and
sees \Gls{Carrot} speak in broken Klatchian to the shop's owner, Mr. \Gls{Goriff}. The owner tells
them that some men threw the bottle of flammable oil into their shop's windoe, before running off
into the night.

\subsubsection{\Gls{Vimes} goes back to the Watch House}
\Gls{Vimes} asks \Gls{Carrot} to stay at the shop, and returns to the Watch House to send someone
else over. Meanwhile, the two groups of fishermen anchored next to Leshp come to blows when the
heavy rain and turbulent sea threatens to destroy their boats. \Gls{Vimes} is woken up in the
morning by his butlet \Gls{Willi}, who hands him the ceremonial uniform, and talks about enlisting
in one of the noble regiments.

\subsection{}
\subsubsection{\Gls{Vimes} attends the banquet for the Klatchian envoys}
\Gls{Vimes} spots the food that \Gls{Goriff} has sent over as thanks for their help at night, and
chastises \Gls{Colon} in private when he uses a derogatory term to refer to the Klatchians. At the
University's Great Hall, \Gls{Ramkin} asks him to be on his best behaviour before she mingles with
the crowd. As \Gls{Vimes} thinks back to the last banquet he had escaped, using the excuse of a
hostage negotiation, he is accosted by Archchancellor \Gls{Ridcu}.

\subsubsection{\Gls{Vimes} meets Prince \Gls{Khufu} and his bodyguard}
\Gls{Ridcu} introduces Prince \Gls{Khufu} to \Gls{Vimes}, and realizes that he is talking to a
seasoned diplomat. Before he can ask about the grizzled veteran by the Prince's side with a big
sword on his back, \Gls{Ridcu} gives the call for the procession to start, and tells \Gls{Vimes}
that he is to lead it.

\subsubsection{\Gls{Vimes} spots someone atop a disused building}
\Gls{Vimes}, delirious from the sleep deprivation, lets his mind enter auto-pilot, and starts to
toss his ceremonial baton in the air. The procession slows down to laugh at him, and \Gls{Carrot}
notices him suddenly become alert as he notices someone on a rooftop. \Gls{Angua} follows him after
morphing into her wolf form, and finds someone dead at the base of the ruined building.

\subsubsection{\Gls{Vimes} faces an inquiry from \Gls{Vetina} and the city council}
\Gls{Vimes} is intrigued to find the same scent lingering around the corpse, that had emanated
from \Gls{Khufu}'s bodyguard. \Gls{Vimes} and \Gls{Carrot} report to the Patrician's office later,
to find the city council pestering them with questions about the bowman who had fired an arrow at
\Gls{Khufu}. \Gls{Vimes} fends off the questions, until \Gls{Vetina} asks for the rest of them to
leave the room, and works out the fact that he is hiding some facts.

\subsubsection{\Gls{Vetina} asks \Gls{Vimes} about the lone bowman}
\Gls{Vimes} admits to the presence of some co-conspirator that has not been identified yet, when
\Gls{Vetina} asks him how the assassin might have barricaded himself in the ruined building.
\Gls{Vetina} indirectly asks \Gls{Vimes} to close the case of the bowman as a lone actor who was
harbouring some deep-seated xenophobia, and pay no attention to the possibiility of a wider
conspiracy.

\subsubsection{\Gls{Vetina} looks at \Gls{LeoQ}'s latest military prototypes}
\Gls{Vetina} then visits \Gls{LeoQ}, who is confined to a well-equipped dungeon, that has been
turned into a workshop. He looks at the latest sketches of siege weapons, as he describes the
pressure now facing Prince \Gls{Cadram}, the younger and less experienced heir to the Klatchian
throne.

\subsubsection{\Gls{Vimes} starts to notice irregularities with the lone bowman theory}
\Gls{Vimes} believes that the half-chewed clove is evidence of \Gls{SevenOA}, the bodyguard of the
prince \Gls{Khufu} at the scene of the lone gunman's death. \Gls{Angua} tells him that she lost
the trail of the clove in the city's spice market, and \Gls{Carrot} remarks on the mismatch
between the bow's draw strength and the bowman's weak arms.

\subsubsection{\Gls{Vimes} asks \Gls{Carrot} and \Gls{Angua} to shadow the official investigation}
\Gls{Vimes} is pleased to see \Gls{Downs} arrive with a fancy arrow found halfway to the city
Square, and notices the iconograph showing a different arrow sticking out of the prince's back, as
if shot from the direction opposite to the dead bowman. He sets \Gls{Angua} and \Gls{Carrot} on
the task of shadowing \Gls{Colon} as he is led on a wild goose chase by the conspirators.

\subsubsection{\Gls{Nobby} and \Gls{Colon} investigate \Gls{OssieB}'s apartment}
\Gls{Nobby} and \Gls{Colon} show up at \Gls{Spent}'s house, posing as tenants looking for a room.
Once she sees their willingness to pay rent in advance, she shows then \Gls{OssieB}'s room, where
\Gls{Colon} asks for some time to look around. He finds a stash of Klatchian silver coins and some
archery magazines under the bed, and dismisses \Gls{Nobby}'s misgivings about how badly hidden the
clues are.

\subsubsection{\Gls{Colon} and \Gls{Nobby} write a formal report for \Gls{Vimes}}
\Gls{Colon} notices some sand on the apartment floor, as \Gls{Nobby} points out the glass being
smashed on one of the window panes. He sees an easy path out onto the rooftops from the window, and
prepares to write a report summarizing the evidence. \Gls{Vimes} is amused by the racist stereotypes
in the report, as he reads it in \Gls{Ramkin}'s manor. \Gls{Ramkin} is annoyed at him for
overworking himself, but lets him leave when \Gls{CheeryL} runs in with news of a murder.

\subsubsection{\Gls{Carrot} and \Gls{Angua} go to the University incognito}
\Gls{Carrot} and \Gls{Angua} try to recreate \Gls{Khufu}'s position at the city square, and work
out that he was likely shot at from the University. The \Gls{Libra} welcomes them, and happily
allows then access to the vantage point from which the prince might have been shot. \Gls{Angua}
is relieved to see an abandoned storeroom with no air currents to disturb the scents.

\subsubsection{\Gls{Carrot} suspects \Gls{SnowyS} of being the true bowman}
\Gls{Angua} works out the presence of someone next to the storeroom's window, and describes the
details of the scent to \Gls{Carrot}. He believes it might have been \Gls{SnowyS}, a well-known
mercenary thug, and sets off to ask around in the underworld about where he was last seen in
Ankh-Morpork.

\subsubsection{\Gls{Detri} stops a race riot at \Gls{Goriff}'s shop}
\Gls{SnowyS} is flummoxed as \Gls{Death} welcomes him to an afterlife with no dandruff, as he
watches his expensive shampoo bottle spill all over his decapitated corpse. Meanwhile, \Gls{Vimes}
runs to \Gls{Goriff}'s shop, where a mob has gathered to answer a murder by one of his children.
\Gls{Detri} uses brute force to quell the belligerent mob, just as \Gls{Vimes} gets there to stop
him using any lethal force.

\subsubsection{\Gls{Vimes} asks \Gls{Goriff} to proceed to the Watch House}
\Gls{Vimes} asks \Gls{Goriff} to evacuate his shop, and spend the night at the Watch House with
his family. He writes a message on the front door stating that the place is under observation, and
thinks about the Riot Act that \Gls{Detri} had almost invoked when trying to disperse the crowd.
\Gls{CheeryL} then runs in with news of the Klatchian embassy being set of fire.

\subsubsection{\Gls{Carrot} and \Gls{Angua} find actual clues in \Gls{OssieB}'s room}
\Gls{Carrot} and \Gls{Angua} investigate \Gls{OssieB}'s room, and find some cloves in the floor,
leading \Gls{Angua} to assume that \Gls{SevenOA} had visited the room a day after the supposed
bowman's death. \Gls{Carrot} also thinks about the impracticality of paying a local killed in
Klatchian coins, which would be difficult to spend or exchange.

\subsubsection{\Gls{Vimes} barges into the Klatchian embassy to try and rescue the people inside}
\Gls{Vimes} approaches the flaming embassy, and knocks out the two Klatchian guards trying to
obstruct his entry. Once inside, a mysterious figure helps him wrap a cloth around his nose and
mouth, and helps him onto the roof, where he can see people stuck inside the smoke-filled rooms.
He decides to wrap his scarf around a chimney and swing into a window to try and smash it open.

\subsubsection{\Gls{Carrot} and \Gls{Angua} inspect the site of \Gls{SnowyS}' murder}
\Gls{Carrot} interrogates a gnoll on the streets about the last known hideout of \Gls{SnowyS}, and
proceeds with \Gls{Angua} to check it out. Inside, \Gls{Angua} smells the same shampoo as in the
University storeroom, and is horrified by the smell of fresh blood. \Gls{Carrot} goes into the
room alone, to document the decapitated corpse, as \Gls{Angua} tells him that her werewolf instincts
are going mad at the scent of blood.

\subsubsection{\Gls{Vimes} narrates his escape from the burning embassy}
\Gls{Vimes} recounts the burning room he had entered through the window, to find a woman begging
for help. He had thrown her out for \Gls{Detri} to catch, and eventually been carried out by
\Gls{Dorfl}, who was immune to the fire. \Gls{Carrot} and \Gls{Angua} arrive to ask him to clock out
and relax at home, and are dismayed to see him proceed to the Watch House, to fill in some reports.
\Gls{Vimes} is exasperated by the stranger who helped him and then vanished without a trace.

\subsubsection{\Gls{Vimes} allows the \Gls{Goriff} family to leave his custody}
\Gls{Vimes} is exasperated by a Klatchian community leader \Gls{Wazir}, the release of \Gls{Goriff}
and his family. He and asks \Gls{Detri} to show them the way out and later learns that \Gls{Goriff}
had punched \Gls{Wazir} because of some religious fight between their two sects. He then looks at
\Gls{SnowyS}' notebook, which has had the first few pages torn off, as if to avoid the writing
being deciphered by the impression underneath.

\subsection{}
\subsubsection{\Gls{Vimes} learns about \Gls{Vetina} temporarily ceding poewr to the nobles}
\Gls{Nobby} visits \Gls{Cake}, a renowned fortune-teller, and asks her to read his future. She tells
him that she can see many young women pleased to be in his presence, and privately looks at a more
detailed divination. He is then summoned to the palace, where \Gls{LRust} tells him that
\Gls{Vetina} has stepped down for the duration of the emergency, and granted power to the council of
aristocrats.

\subsubsection{\Gls{Vimes} resigns as Commander of the City Watch}
\Gls{Vimes} is asked to resign, and surrender the City Watch to the city council. \Gls{Colon} and
\Gls{Carrot} both reject the offer to be the temporary Commander of the Watch, recognizing the kind
of racial violence they will be asked to engage in. The Klatchian ambassador walks in, and announces
the coming war between their two nations, over the occupation of Leshp. \Gls{Vimes} decides to go
back home, after surrendering his badge and is pleased to see \Gls{Colon} and \Gls{Carrot} take his
side.

\subsubsection{The City Watch take the day off, to observe the mustering of their army}
The Watchmen observe the noble regiments marching through the city the next morning, with
\Gls{Colon} reliving his time in the Pseudopolis military. \Gls{Nobby} recalls his own time in the
army, mainly as a scavenger of the dead and a grave robber. Meanwhile, \Gls{Vimes} wakes up, and
sees \Gls{Ramkin} handing him his shaving razor, impressed by his heroism at the Klatchian embassy.

\subsubsection{\Gls{Vimes} spots \Gls{SevenOA} board a ship out of Ankh-Morpork}
\Gls{Vimes} finds the sealed letter from \Gls{Vetina} to be completely blank, and realizes that he
has the power to raise his own regiment, as a nobleman. \Gls{Carrot} and \Gls{Angua} help
\Gls{Goriff} board a ship out to Klatch along with his family, as they spot \Gls{SevenOA} arrive at
the docks. \Gls{Carrot} is sad to see a suspect get away, and is stopped by \Gls{Angua} from
pursuing him.

\subsubsection{\Gls{Angua} infiltrates \Gls{SevenOA}'s ship to Klatch}
\Gls{Angua} decides to infiltrate the Klatchian ship in her wolf form, confident that there are no
werewolves in Klatch, and no possibility of her being found out. Meanwhile, \Gls{Nobby} and
\Gls{Colon} discuss the race realism starting to take hold in Ankh-Morpork as they stroll through
the city. \Gls{Colon} concedes \Gls{Nobby}'s point that most the racist ideas are baseless and
nothing more than fear-mongering.

\subsubsection{\Gls{LeoQ} holds \Gls{Colon} and \Gls{Nobby} hostage}
\Gls{LeoQ} arrests \Gls{Colon} and \Gls{Nobby} using one of his fancy rocket launchers, and asks
them to step into a dark alley per the order of \Gls{LRust}. Meanwhile, \Gls{Vimes} starts his
recruitment parade right outside the palace, where \Gls{LRust} is busy discussing his invasion plans
with his Lieutenant \Gls{Hornett}.

\subsubsection{\Gls{LRust} is flummoxed by \Gls{Vimes} raising his own private army}
\Gls{LRust} tries to talk \Gls{Vimes} out of massing his own regiment, but is forced to back down
when \Gls{Vimes} pulls out the scrolls from \Gls{Ramkin}'s library enshrining his duties as a
knight. \Gls{LRust} gives up, and walks back to the palace in annoyance, as \Gls{Vimes} asks
\Gls{Detri} for a list of volunteers who have signed up.

\subsubsection{\Gls{LeoQ} gets \Gls{Colon} and \Gls{Nobby} to sign up for an undercover mission}
\Gls{LeoQ} tells \Gls{Nobby} and \Gls{Colon} that \Gls{Vetina} has asked for them to be brought to
the docks discreetly, for some secret mission requiring their special talents. \Gls{Nobby} is
immediately suspicious, believing that no one in their right minds would consider him fit for any
mission of importance.

\subsubsection{\Gls{Vimes} learns of \Gls{Nobby} and \Gls{Colon}'s undercover operation}
\Gls{Vimes} is shocked to see his organizer predict appointments in the future that he has no
knowledge of, and is shocked to find \Gls{CheeryL} arrive with a message from \Gls{Colon} stating
his participation in \Gls{Vetina}'s secret mission. He is alarmed by the organizer demon's newfound
powers of divination, just as it informs him of an upcoming meeting with \Gls{Carrot}.

\subsubsection{\Gls{Vetina} watches }
\Gls{Vetina} stops \Gls{Nobby} and \Gls{Colon} from running away, when they realize that they have
to set sail on board \Gls{LeoQ}'s prototype submarine with him. He asks them to strap in, and
launches it from a hidden dockyard, hoping to use dolphin propulsion once out in the open seas.
Meanwhile, \Gls{Angua} is found out by \Gls{SevenOA}, as he lures her into his cabin, and chains her
with a silver collar.

\subsubsection{\Gls{Vimes} decides to help in the rescue of \Gls{Angua}}
\Gls{Vimes} is amazed to see \Gls{Carrot} barge into his office just as his organizer predicted,
and elects to follow him in pursuit of \Gls{Angua}. He happens to pick up the organizer from an
alternate timeline where he chooses to stay back in defense of the city. \Gls{LRust} learns from a
beggar that \Gls{Vimes} and his coterie were hastily headed to the docks, after a short meeting
with \Gls{Carrot}.

\subsubsection{\Gls{Vimes} commandeers a smuggler's ship for the rescue operation}
\Gls{Vimes} arrives at the docks, and finds \Gls{Jenkins} busy smuggling weapons to the enemy for a
high price. He coerces the sailor to lend him the ship, and unpack the weapons for their use.
Meanwhile, \Gls{LRust} is annoyed by the possibility of the Klatchians defeating \Gls{Vimes} and
his small force, before a proper invasion is underway.

\subsubsection{\Gls{Cadram} is told that a lone ship has set sail from Ankh-Morpork}
Prince \Gls{Cadram} learns from his General \Gls{Ashal} that a single ship has departed the docks
of Ankh-Morpork, possibly as a scouting party for the coming invasion. He then asks about news of
his brother \Gls{Khufu}, who has been missing since the night of the Klatchian embassy fire.

\subsubsection{\Gls{Vetina} and \Gls{LeoQ} reveal their destination}
\Gls{Vetina}, who is also on-board the submarine, asks \Gls{Nobby} to stop pedaling once they
reach the open seas. \Gls{LeoQ} tells them that the drill head at the front is for attaching the
submarine to a ship's hull, and be carried along to Leshp. He is horrified by \Gls{Nobby}'s
suggestion that the drill could be used to sink enemy ships by overdoing the hull penetration.

\subsubsection{\Gls{Vimes} tries to catch up to the Klatchian ship}
\Gls{Vimes} orders the contraband thrown overboard, when \Gls{Carrot} points out how slow they are
in comparison to \Gls{SevenOA}'s Klatchian vessel. \Gls{Jenkins} is horrified to see valuable
merchandise go to waste, as \Gls{Vimes} opens his organizer, looking for the next appointment.
Meanwhile, \Gls{Angua} is intrigued to hear familiar voices through the pointy end of \Gls{LeoQ}'s
drill, as it buries itself into the ship's lower deck.

\subsubsection{\Gls{SevenOA} is alarmed by \Gls{Jenkins}' ship pursuing him}
\Gls{SevenOA} learns from his crew that their ship is weighed down, and that a mysterious sea
monster seems to be following them. He refuses to believe in the crew's superstitions, and is
instead more focused on the Morporkian ship following them in the distance. \Gls{LeoQ} tries out a
game of Scrabble with the submarine crew, as \Gls{Vetina} comes to the conclusion that Leshp must be
close by.

\subsubsection{\Gls{Vimes} thinks about boarding \Gls{SevenOA}'s ship}
\Gls{Vetina} asks for the drill head to be detached from the ship, so that they can pedal their way
to Leshp under cover of darkness. Meanwhile, \Gls{Vimes} frets about the distance to the Klatchian
ship, as \Gls{Carrot} gets some sleep in preparation for the boarding. \Gls{Jenkins} reminds him
that all the grapnels and swords have been thrown overboard in their hurry to lighten the ship's
load.

\subsubsection{\Gls{Jenkins} spots a magical sea-storm attacking his ship}
\Gls{Jenkins} notices a magical storm building up above the two ships, and asks desperately for the
sails to be lowered. Meanwhile, \Gls{SevenOA} is relieved to see his crew calm down, as they try
desperately to fix the sails that someone else had cut mysteriously in the darkness of the night.
\Gls{SevenOA} works out the magical nature of the sea-storm, just as \Gls{Jenkins} asks \Gls{Vimes}
to brace for rough seas.

\subsubsection{\Gls{Angua} manages to escape \Gls{SevenOA}'s ship}
The Watchmen struggle to stay sane on the ship's lower decks, as \Gls{Carrot} sleeps through the
storm. \Gls{SevenOA} is ambushed by \Gls{Angua}, who has managed to remove her silver collar. She
escapes through a nearby cabin, where she spots \Gls{Khufu} in a weakened state lying on one of the
beds. \Gls{SevenOA} lets her go, declaring to his crew that the intruder was unlikely to make it
out alive in the stormy sea.

\subsubsection{\Gls{LeoQ} nears the coast of Leshp with his periscope}
\Gls{LeoQ} tries out his new periscope to better scout the seas near Leshp, and decides to head in
the approximate direction. Once close to the island, he surfaces, and runs into \Gls{SolidJ}, who is
busy trying to snatch more of the island from Klatchian occupiers.

\subsection{}
\subsubsection{\Gls{SevenOA} abandons ship with \Gls{Khufu}}
\Gls{Vimes} gives a pep talk to his crew after the magical storm blows over, and is amused to see
\Gls{Visit} calling it a divine blessing, in accordance with many stories from his scriptures.
\Gls{SevenOA} takes the unconscious \Gls{Khufu} with him on the lifeboat, and asks the ship's
captain to withhold this information from the commander of Fort Gebra. As the crew is busy looking
at \Gls{SevenOA}'s fellow tribesmen welcoming him, \Gls{Angua} silently leaps into the sea.

\subsubsection{\Gls{Vimes} forces \Gls{Jenkins} to land on the Gebra coast}
\Gls{Vimes} asks \Gls{Jenkins} to take his ship straight to the coast of Gebra, as they spot
\Gls{SevenOA} climbing the dunes with someone on his shoulders. \Gls{Jenkins} warns him of the
dangerous currents and the hostile tribesmen, but is overruled by \Gls{Vimes}. Meanwhile,
\Gls{Vetina} asks \Gls{LeoQ} to finish his survey of the undersea volcano, and proceed to the
underside of Leshp.

\subsubsection{\Gls{Vimes} heads inland at the Gebra coast, and gets ambushed}
\Gls{Vimes} decides not to linger on the beach, and head inland into the desert. \Gls{Jenkins},
saddened by the loss of his dear ship as it beaches unceremoniously on the Gebra coast, decides not
to warn the Watchmen about their fresh water stores, and lets them walk inland to their deaths.
As \Gls{Detri} struggles with the heat slowing down his brain, the watchmen walk into an ambush by
the tribesmen, lying in wait under the sand.

\subsubsection{\Gls{LesJ} is disheartened by his father's insistence on claiming Leshp}
\Gls{SolidJ} is annoyed by his son's idea of trading their rainwater supply for the bread and meat
that the Klatchian settlers had a monopoly on. \Gls{LesJ}, who is not interested in continuing the
family trade of fishing, starts to take note of the bizarre architecture on the island, and believes
some sinister force might be lying in wait for anyone foolish enough to stake their claim to Leshp.

\subsubsection{\Gls{LeoQ}  studies the underside of Leshp, which is a gas bubble}
\Gls{LeoQ} surfaces the submarine underneath Leshp, and \Gls{Nobby} uses the periscope to see the
surface. He is shocked to find a large cavern, bubbling with gas and stray bolts of lightning.
\Gls{LeoQ} speculates that Leshp is supported by porous rock, which is generating a large gas bubble
holding it afloat.

\subsubsection{\Gls{Vimes} gets knocked out in the D'reg ambush}
\Gls{Vimes} manages to get the chieftain of the tribesmen in a stranglehold, and is surprised to see
the others disobey \Gls{Carrot}'s request to back off. A while later, \Gls{Vimes} wakes up slightly
concussed, to find that \Gls{Carrot} and the others are wearing desert robes. He learns that the
D'reg tribesmen have decided to hold them hostage instead of outright killing them.

\subsubsection{\Gls{Jabbar} talks about \Gls{Cadram}'s attempt at unifying Klatch}
\Gls{Jabbar} says that Prince \Gls{Cadram} in Al-Khali is intent on organizing the outlying tribes
into a cohesive fighting force, to take on the Morporkians. He says that the tribes have no interest
in paying tribute, or supplying men for the pointless war for control of Leshp, and that they are
happy to lead simple lives as brigands and pirates.

\subsubsection{\Gls{LeoQ} guides the submarine to Al-Khali}
\Gls{LeoQ} manages to hitch a ride on another fishing boat, to reach the harbour of Al-Khali.
\Gls{Vetina} suggests blending in with the myriad ambassadors and mercenaries thronging the city,
to answer the call to arms by \Gls{Cadram}. He is impressed by the size of the assembled fleet, as
\Gls{Colon} explains how Klatch punishes spies to \Gls{Nobby}.

\subsubsection{\Gls{Angua} joins \Gls{Jabbar}'s camp, after clawing her way through enemy soldiers}
At night, \Gls{Angua} enters \Gls{Jabbar}'s camp at full speed, having bitten some of the Al-Khali
forces sent to round up the D'regs. After morphing back to human form, she tells \Gls{Vimes} that
they are heavily outnumbered, and that it would be best to ambush them before dawn. \Gls{Jabbar}
is horrified by the dishonourable tactics under consideration, and insists on waiting for dawn and
a suicidal charge.

\subsubsection{\Gls{Colon} and \Gls{Nobby} prepare to infiltrate Al-Khali}
\Gls{Colon} and \Gls{Nobby} disembark at the Al-Khali harbour, as \Gls{Vetina} waits for them in
the submarine. They set off to find clothing that might help them fit in, believing their mission
is of grave importance in averting the war. Meanwhile, \Gls{Vimes} prepares for a guerilla ambush
under cover of darkness, after learning that the enemy forces are scattered in small squads with no
co-ordination.

\subsubsection{\Gls{Vimes} runs into \Gls{Goriff}'s son among the Klatchian soldiers}
\Gls{Vimes} ambushes a Klatchian soldier, only to find that it is \Gls{Goriff}'s son, who claims to
be sent out to D'reg lands against his will. He asks the boy to surrender, and join the watchmen as
a hostage of the D'regs. Meanwhile, \Gls{Colon} and \Gls{Nobby} manage to get some local clothing,
and are chased to the docks by Klatchian watchmen, who mistake them for soldiers shirking their
duty.

\subsubsection{\Gls{Nobby} and \Gls{Colon} learn about their eventual target}
\Gls{Nobby} and \Gls{Colon} get back to the submarine, and narrate their brief adventure to
\Gls{Vetina}, as they empty the contents of the travel pack they stole. \Gls{Vetina} figures out
that the travel pack belonged to a dance troupe, and asks \Gls{Colon} to wear the skimpy clothing
meant for the female dancer. He tells them that \Gls{LeoQ} has engineered a gift that might end
the war when they deliver it into the hands of the Klatchian high command.

\subsubsection{\Gls{Vimes} gets the Klatchian force to surrender to the D'regs}
The Klatchian soldiers look to their commander when the D'reg camp fail to charge them at dawn,
until he finally relents, and asks his sergeant to lead a small force into the camp. When they are
surrounded by D'reg warriors, and asked by \Gls{Carrot} to surrender peacefully, the Klatchian
commander readily agrees, happy to escape D'reg lands with his life.

\subsubsection{\Gls{Vimes} works out the likely plan of \Gls{SevenOA}}
\Gls{Vimes} is horrified to see \Gls{Carrot} stripping the Klatchian soldiers of their weapons and
armour. He tells \Gls{Carrot} that it is futile to stay on with \Gls{Jabbar}'s tribe and try to
fight against the Klatchian unification force. \Gls{Vimes} believes that \Gls{SevenOA} wants them
alive and out of the way as he fulfils some secret mission, and asks \Gls{Jabbar} to reveal his
location.

\subsubsection{\Gls{Vetina} performs for the guardsmen in Al-Khali, to maintain his cover}
In the streets of Al-Khali, \Gls{Colon} and \Gls{Nobby} are accosted by some guardsmen, who demand
to see their tricks. \Gls{Vetina} saves them by performing some acts of juggling and then using
his sleight of hand to amuse the gathering crowd. He gets them to disperse, and the two watchmen
with him to a nearby bar.

\subsubsection{\Gls{Nobby} is forced to separate from \Gls{Vetina} and \Gls{Colon}}
\Gls{Nobby} is denied entry into a nearby tavern because of his female disguise, and forced to
wander off alone into the city, looking for information on the mustering of Prince \Gls{Cadram}'s
forces. Meanwhile, \Gls{Vetina} and \Gls{Colon} get to work mingling with the tavern regulars,
trying to catch the latest news and rumours floating around.

\subsubsection{\Gls{Nobby} and \Gls{Colon} try to learn about the army's location}
\Gls{Nobby} is accosted by a group of Klatchian women, lamenting their husbands running off to the
war in Gebra. He fumbles his way through the conversation, recalling how much the \Gls{Cake} had
tried to hide her laughter when telling his fortune. Meanwhile, the group at the tavern entertaining
\Gls{Colon} quickly realize he is a spy pretending to be from Ankh-Morpork.

\subsubsection{\Gls{Vetina} steals a flying carpet from the Al-Khali watchmen}
\Gls{Nobby} threatens the guards with kisses, when they hesitate to rescue his new donkey from the
top of a narrow tower. \Gls{Vetina} convinces them to bring out one of their flying carpets, now
kept under lock and key because of the war, and manages to steal it when the crowd is distracted by
one of his tricks.

\subsubsection{\Gls{Vimes} meets with \Gls{SevenOA} in his hideout}
\Gls{Vimes} is blindfolded and carried on camel to the secret hideout of \Gls{SevenOA}, where
\Gls{Jabbar} abandons him and returns in all haste. A while later, as \Gls{Vimes} explores the
ruins of what must have been an ancient city established by some Morporkian general, he is accosted
by \Gls{SevenOA}.

\subsubsection{\Gls{Vetina} manoeuvres the flying carpet to Gebra}
\Gls{Vetina} is pleased to learn that the army has moved to Gebra, and diverts the flying carpet to
the city. \Gls{Nobby} hangs on for dear life, as his fear of heights returns in full force.
Meanwhile, \Gls{SevenOA} reveals the true intent behind the clumsily placed clues in \Gls{OssieB}'s
house. \Gls{Vimes} was meant to arrive at the conclusion that some Morporkian had attempted to
murder \Gls{Khufu}, and make it look like a Klatchian did it.

\subsubsection{\Gls{Vimes} decides to stop the war between Klatch and Ankh-Morpork}
\Gls{Vimes} is saddened to know that \Gls{Cadram}, \Gls{Khufu}'s own brother, had ordered the hit.
\Gls{SevenOA} insists that the fire at the embassy was planned, and that he has coded messages
bearing \Gls{Cadram}'s seal to prove his claims. \Gls{Vimes} realizes that \Gls{Cadram} wants the
war as an excuse to unify the tribes of Klatch, and considers the thousands of lives at stake on
both sides.

\subsubsection{\Gls{Willi} and his men run into \Gls{Vimes} and \Gls{SevenOA}}
\Gls{Vimes} and \Gls{SevenOA} are ambushed by \Gls{Willi} and his regiment, who are on the way back
from a foraging mission, and taking refuge in the ruined city. After killing two of the ambushers,
\Gls{Vimes} finally manages to identify himself to \Gls{Willi}, and gets him to call off his men.

\subsubsection{\Gls{LRust} fails to see the danger in his position against the Klatchians}
\Gls{LRust} surveys his forces as they assemble outside Al-Khali, with the opposing armies also
getting in formation. \Gls{Hornett} muses on the probability of their own army beating the
well-trained Klatchian defenders, and longs for his life as a surveyor before the war. Meanwhile,
\Gls{Carrot} manages to muster the remaining Klatchian ambushers, as well as the D'reg into a
makeshift army, meant to prevent the coming war.

\subsection{}
\subsubsection{\Gls{Cadram} is persuaded to parley with \Gls{LRust} before their battle}
\Gls{Cadram} sets off along with his general \Gls{Ashal}, to the parley with \Gls{LRust} on the
eve of their first pitched battle. He is amused by how small the Morporkian forces are, and learns
that they hold racist beliefs in the cowardice of the Klatchian men when it comes to warfare on the
open field.

\subsubsection{\Gls{Cadram} meets with \Gls{LRust} before the battle}
\Gls{Cadram} recalls reading a book on imperialism written by a Morporkian general who had
previously conquered a fair fraction of modern-day Klatch. At the parley tent between the two
armies, \Gls{Cadram} amuses himself at the cost of \Gls{LRust}, until he notices a column of
mounted men riding towards them in the distance, waving the white flag of surrender. \Gls{Cadram}
and \Gls{LRust} order their own men to send scouting parties to investigate.

\subsubsection{\Gls{Vimes} and \Gls{SevenOA} reach the parley tent}
\Gls{Vimes} runs away from the D'regs as the two scouting parties converge on them, and makes it
to the parley tent along with the rest of the Watchmen. \Gls{SevenOA} orders his tribesmen to hold
the two sets of bodyguards at bay, as he approaches \Gls{Cadram}, blaming him for the kidnapping of
Prince \Gls{Khufu}.

\subsubsection{\Gls{Vimes} contemplates the alternate future where he does not pursue \Gls{Angua}}
\Gls{Vimes} orders \Gls{Carrot} to arrest both armies, as \Gls{LRust} and \Gls{Cadram} agree to
stand down for the moment. Inside his tent, he receives news about the deaths of his men in the
defense of Ankh-Morpork, as the organizer demon from an alternate future announces his appointments
for the day. Just as he is about to shoot \Gls{Cadram} in honour of \Gls{Stonef}, \Gls{Vetina}
arrives and disarms his crossbow.

\subsubsection{\Gls{Vetina} proposes a surrender negotiation on the island of Leshp}
\Gls{Vetina} hands \Gls{Cadram} the surrender document drafted by \Gls{LeoQ}, giving up all claims
on Leshp, as well as juicy trade deals for goods exclusive to Ankh-Morpork. \Gls{Vimes} tries to
tell \Gls{Vetina} that the city cannot possibly fulfill all the lofty demands outlined in the
document, and is asked to step aside so that negotiations can continue on the island of Leshp.

\subsubsection{\Gls{Vimes} bids goodbye to \Gls{SevenOA}}
\Gls{SevenOA} takes his leave of \Gls{Vimes}, claiming that he will be safe from \Gls{Cadram}'s
men in the desert. \Gls{Carrot}'s game of football between the two armies is in full swing, with
\Gls{SevenOA} remarking on how effective he is at inspiring men to follow him. A while later,
\Gls{LRust} comes out of the parley tent after arguing about the terms of the pact, and yells at
\Gls{Vimes} for snatching away his chance at glorious battle.

\subsubsection{\Gls{Vimes} sets sail using \Gls{Jenkins}' ship}
\Gls{Carrot} reports on the progress of the football match, as \Gls{Colon} notices the outlying
Klatchian fiefdoms withdrawing from the battlefield. A while later, \Gls{Vetina} commandeers the
submarine, with \Gls{Nobby} and \Gls{Colon} joining him after their souvenir shopping spree.
Meanwhile, \Gls{Vimes} struggles to sleep aboard \Gls{Jenkins}' ship, as the watchmen discuss his
possible ouster after the deal is signed.

\subsubsection{\Gls{Vetina} is apprehended according to the wishes of the city council}
\Gls{Vetina} arrives by submarine shortly after \Gls{Vimes} docks in Ankh-Morpork, and asks him
to execute the arrest warrant signed by most of the Guildmasters. \Gls{Carrot} insists on the
document being legally binding, and reminds \Gls{Vimes} that no one should be above the law, not
even the Patrician. He reluctantly handcuffs \Gls{Vetina}, and walks him to the palace.

\subsubsection{\Gls{Vetina} stands before the city council for the surrender of Leshp}
The organizer demon's soul is collected by \Gls{Death} at the outskirts of Gebra. Meanwhile,
\Gls{Vimes} is alarmed by the crowds thronging the Great Hall, expecting \Gls{Vetina} to be
sentenced to death for his treason. \Gls{Vimes} informs \Gls{LRust} that Leshp has disappeared,
and the \Gls{Dean} of Unseen University corroborates his claims using a crystal ball.

\subsubsection{\Gls{Slant} fails to build a case for \Gls{Vetina}'s execution}
\Gls{Slant} tries desperately to find a crime that \Gls{Vetina} can be charged with, now that
Leshp no longer remains as a victory for the Klatchians. \Gls{LRust} is reminded of how easily
the Klatchian military disposes of leaders that fail them, and worries about \Gls{Cadram}.
Meanwhile, \Gls{Ramkin} welcomes \Gls{Vimes} back, and asks to accompany him when \Gls{Vetina}
summons him to the palace.

\subsubsection{\Gls{Vetina} tells \Gls{Vimes} about the reward due to \Gls{Nobby} and \Gls{Colon}}
\Gls{Vetina} tells \Gls{Vimes} that a new traffic police division is to be set up, allowing
\Gls{Colon} and \Gls{Nobby} to make a livelihood stopping rule-breakers, and stay away from violent
crime in the process. He then offers \Gls{Vimes} the title of Duke, making him react with anger at
the continued bribing. \Gls{Vimes} is forced to reconsider when \Gls{Vetina} makes him the offer of
rewriting \Gls{Stonef}'s role in the city's history.

\subsubsection{\Gls{Vimes} is enticed by the creation of a statue to \Gls{Stonef}}
\Gls{Vimes} quickly realizes that he can only become a Duke when the city has a monarch, and
settles for a statue of \Gls{Stonef} being erected outside the palace. He then struggles with the
idea of bargaining with the lives of men, as \Gls{Vetina} reminds him of the horrors of all-out war.

\subsubsection{\Gls{Colon} and \Gls{Nobby} reconsider their biases against Klatchian culture}
\Gls{Colon} and \Gls{Nobby} stroll through the city, with some food handed to them by \Gls{Goriff}.
They reconsider their racist beliefs about the Klatchians as they reach the docks, and decide to
head to a different tavern. At the procession marking his ascent to Dukedom, \Gls{Vimes} once again
gets distracted by a thief robbing an old woman, and runs after him, throwing away his ceremonial
robes.