\section{Judgment Day}


\subsection{}
\subsubsection{\Gls{MDaw} is transported to the Disc from Roundworld}
A librarian from England named \Gls{MDaw} gets transported to Unseen University in a magical
accident, with \Gls{Ridcu} trying his best to placate the woman's fears. He hands \Gls{MDaw} off
to \Gls{Whitlow} when she faints, and goes with the \Gls{Libra} to \Gls{Stibb}, who is desperately
trying to make sense of the unplanned link between Roundworld and the Disc.

\subsubsection{\Gls{Ridcu} decides to burden the \Gls{Dean} with investigating the magic leaking
    into Roundworld}
\Gls{Ridcu} decides to send \Gls{Rince} along to Roundworld with the \Gls{Dean}, in order to
check for side effects of the teleportation of \Gls{MDaw}. \Gls{Ridcu} is pleased to have the
\Gls{Dean} take the fall for the accident, since he had kick-started the Roundworld's Big Bang by
poling his fingers into the magical globe enclosing it.

\subsection{}
\subsubsection{\Gls{MDaw} follows \Gls{Ridcu} around as he collects the Roundworld from
    \Gls{Rince}}
\Gls{MDaw} is taken to a garden the next morning, where \Gls{Ridcu} patiently spends the day
explaining the Roundworld experiment to her, and tells her that they can return her to her timeline
after they solve the problem being caused by the latest big experiment in the High Energy Magic
Building. \Gls{MDaw} follows \Gls{Ridcu} as he retrieves the Roundworld globe from \Gls{Rince} and
brings it to his own office for a demonstration.

\subsubsection{\Gls{Ridcu} and \Gls{MDaw} talk about Flat Earthers on Roundworld}
\Gls{Ridcu} learns about the Omnians issuing a fatwa on the wizards for ownership of the Roundworld
globe, since it aligns with their religious beliefs about the Discworld being round. \Gls{MDaw}
talks about Flat Earthers in Roundworld, who happen to be the counterparts of the Omnians on the
Disc. \Gls{Stibb} reports that the issues preventing teleportation into Roundworld have been
resolved, as \Gls{Ridcu} tries to suppress his anger toward the Omnians.

\subsubsection{\Gls{MDaw} meets the \Gls{Libra} while waiting for the trial to start}
\Gls{Ridcu} offers to send \Gls{MDaw} back home, but she insists on watching the trial that is to
take place for the ownership of Roundworld. \Gls{Stibb} walks in with some arguments prepared by
\Gls{Slant}, who is to be their lawyer for the case, against a collective of religious
fundamentalists led by the Omnian Church. \Gls{MDaw} receives a tour of the University Library,
and is happy to meet the \Gls{Libra} in person, having heard stories of banana peels turning up in
libraries all over Roundworld.

\subsubsection{\Gls{Rince} and the \Gls{Dean} carouse through Roundworld, admiring the sights}
\Gls{Rince} lands in modern day London with the \Gls{Dean}, and wonders how his meddling in the
Roundworld cosmos led to the life in all its complexity over the many billions of years that the
toy universe has been allowed to exist. \Gls{Rince} remains pessimistic about the decline of human
civilization, boosted by the stranglehold that religion still has over society.

\subsubsection{\Gls{Vetina} tries to pin \Gls{Stack} down as a Moon-landing denier}
In the Great Hall of his palace, \Gls{Vetina} initiates the trial by asking Reverend \Gls{Stack} of
the Omnian Church to make his opening arguments. \Gls{Vetina} is forced to ask if \Gls{Stack} denies
the mission to Discworld's moon that took \Gls{LeoQ} and three other chelonauts over the rim of the
Disc, and brought back soil samples from the Moon.

\subsubsection{\Gls{MDaw} speaks up against \Gls{Ridcu}'s advice}
The \Gls{Dean} reports to \Gls{Ridcu} about his latest sojourn through Roundworld, when the trial is
adjourned for lunch. \Gls{MDaw} thinks about her religious father, and of how his faith in his
God had been strengthened after the untimely death of her mother. As \Gls{Stibb} explains the
creation of Roundworld to the audience, after placing the snow-globe onto \Gls{Vetina}'s desk,
\Gls{MDaw} loses her self-control and talks about the wasteful wars brought on by religion.

\subsubsection{\Gls{Gom} chimes in with a full rejection of the Omnian beliefs about the Disc
    being round}
\Gls{Gom} materializes in the Great Hall when \Gls{Oats} comes in to deliver his testimony, and
tells \Gls{Stibb} that there has been cross-pollination of religious myths between Roundworld and
the Disc. \Gls{Stibb} realizes that the Omnian belief in the Discworld being round is a consequence
of Roundworld astronomy leaking into the distant past. Bandits break into the room and run away with
Roundworld, and \Gls{MDaw} gives chase, fully aware that the globe might break if dropped on the
ground.

\subsubsection{\Gls{Sally} and \Gls{Angua} help \Gls{MDaw} fend off the bandit trying to knife her}
\Gls{Sally} and \Gls{Angua} stop the bandit when he tries to attack \Gls{MDaw} with a knife, after
throwing Roundworld at her to disorient her. \Gls{MDaw} manages to catch Roundworld, and proceeds
to the University where \Gls{Stibb} is ready to send her back to her home, at the precise moment
when she was suddenly teleported to the Disc.