\section{The Last Continent}


\subsection{}
\subsubsection{The \Gls{Libra} suffers from a magical shape-shifting illness in the Unseen
    University}
The inner council of Unseen University watch over the \Gls{Libra}, as he struggles with a magical
disease that makes him morph unpredictably into a variety of objects. \Gls{Stibb} tries to explain
to \Gls{Ridcu} that the \Gls{Libra} is highly vulnerable to the illness, since he has already been
morphed from a human to an orangutan. They lose hope in the \Gls{Libra}'s recovery, and wander off
to let him rest.

\subsubsection{\Gls{Stibb} works on his unseen books initiative using \Gls{Hex}}
A miner in some mine discovers a box shaped opal deposit deep underground, and is shocked when
little feet drop out from its bottom surface and start to wriggle their toes. Meanwhile, \Gls{Stibb}
gets to work reading pages from unwritten books, by exploiting the time delay between trying
something impossible, and the universe moving its causality particles to make the newly tried thing
extremely difficult.

\subsubsection{\Gls{Ridcu} happens upon \Gls{Stibb} and his book of micromanagement}
\Gls{Ridcu} gets to work implementing his new leadership program, and starts to take a keen interest
in the daily lives of the inner council, leaving them irritated at the intrusion. \Gls{Stibb} is
woken up one night by a commotion at the library entrance, and learns that the books have barred
entry to all wizards, with the \Gls{Libra} no longer there to placate them.

\subsubsection{The inner council realize they have no way of knowing the \Gls{Libra}'s name}
The \Gls{Dean} suggests using some magic to heal the \Gls{Libra}'s illness, but \Gls{Runes} points
out the need to know his real name before trying anything. \Gls{Ridcu} is dismayed to learn that no
one knows the \Gls{Libra}'s name, and that he has torn out any reference to it in order to stop the
others from turning him back into a human.

\subsubsection{\Gls{Ridcu} and the inner council decide to try and locate \Gls{Rince}}
The \Gls{Libra} approaches the library entrance, and suddenly morphs into a tome with a furry
leather cover. \Gls{Stibb} points out that the illness is making him morph into objects as a crude
form of camouflage, as \Gls{Indef} remembers the time when \Gls{Rince} had been assisstant librarian
and was likely to know his real name.

\subsubsection{The inner council of wizards search the chambers of the geography professor}
Realizing that \Gls{Rince} is stuck on the mythical continent of XXXX, \Gls{Ridcu} leads the inner
council through the University's endless corridors, until they arrive at a geography professor's
room. The council barge into the professor's room, and notice sounds of water splashing from the
attached bathroom. After spending some time persuing through his books for mentions of XXXX, they
decide to open the bathroom, and find a portal to some tropical beach.

\subsubsection{\Gls{Rince} stumbles his way through the arid desert of XXXX}
\Gls{Rince} eats some insects salvaged from a water-hole, as the dry desert drains his energy day
after day. He is puzzled by the small indigenous tribes acting hostile the moment he starts to make
polite conversation by talking about the weather, as a mysterious spirit keeps an eye on him from a
nearby water-hole. \Gls{Rince} fails to notice the spirit keeping him alive and hydrated by ensuring
he always ends the day next to a water source, as he fills in the latest entry in his journal.

\subsubsection{\Gls{Rince} sleeps on the deserts of XXXX}
As \Gls{Rince} settles down to sleep, the land itself animates, to go check on the mine where the
opal encrusted \Gls{Lugg} had been unearthed, and starts to form some patterns on a rock next to
\Gls{Rince}. Meanwhile, the miners hastily climb out of the mining shaft, with the \Gls{Lugg}
following them soon after.

\subsubsection{\Gls{Death} is amused by the sheer danger in the biosphere of Terror Incognita}
\Gls{Death} asks his model of the Disc to zoom in on \Gls{Rince}, and is amused to see him stuck on
the forbidding continent of Terror Incognita. His butler \Gls{Albert} describes it as a hot, arid
land surrounded by a permanent anti-cyclone, thus guaranteeing zero precipitation. \Gls{Death}
walks into his library, and is buried under an avalanche of books in response to his request for
the dangers of Terror Incognita. He then asks for the list of harmless creatures and receives a
single piece of paper with some sheep drawn on it.

\subsubsection{\Gls{Ridcu} observes the portal to the beach}
\Gls{Stibb} is amazed at the two way wormhole created by the professor of geography, allowing him
to get his suntan on the beach leading out of his chamber. He immediately starts to think about
perpetual motion machines that might be built using a pair of such portals, as the others in the
council debate the idea of exploring the beach directly.

\subsubsection{\Gls{Ridcu} leads the inner council into the geography professor's beach}
\Gls{Ridcu}'s inner angler is roused by \Gls{Indef} describing the varied fish and sharks inhabiting
the rimward seas, as the rest of them prepare to spend some time on the beach, hoping to improve the
\Gls{Libra}'s condition. \Gls{Ridcu} insists that they are not using the beach as a vacation, as
they come up with flimsy excuses to research the fauna and the natives in the unknown coastline.

\subsubsection{\Gls{Rince} spots a tribal warrior watching him sleep}
\Gls{Rince} wakes up to see a heavily armed tribal warrior observing him, and walking away into the
desert the moment he tries to make conversation. Later, a disembodied voice casts a spell on him,
after telling him that he will be able to find food underneath some nearby shrubbery. The shapes on
the rock made by the sentient desert spirits fade away, as \Gls{Rince} eats the chicken sandwich
buried under the shrubs.

\subsubsection{\Gls{Rince} becomes the unwitting pawn of a trickser spirit of Terror Incognita}
On the other side of the rock, the trickster spirit appears on the desert in his own dimension,
and asks his pet bird to guide \Gls{Rince} to the object he was interested in stealing. He tells
the bird that a hero is necessary, since he cannot be accused of interfering directly in the
Discworld's affairs.

\subsubsection{The \Gls{Libra} watches his colleagues enjoy their time on the beach}
The \Gls{Libra}, now restored to his ape form by the lush vegetation of the beach, looks at the
plants and birds surrounding him, and feels uneasy about the whole thing. He notices the portal
through which they had originally come to the beach, now propped open by \Gls{Ridcu} using a wooden
plank with a warning written on it.

\subsubsection{\Gls{Whitlow} strands the inner council on the tropical beach}
\Gls{Rince} sees a kangaroo hop up to him, and start to talk about some important mission that he
was needed for. He pre-empts it, by running away, and falls into a dark pit, as it keeps up with him
using its powerful legs. Meanwhile, the head housekeeper of the university, \Gls{Whitlow}, shows up
at the window shaped portal to the beach, and tries to climb through. When the wizards ask her for
some food, she returns with a large tray and accidentally closes the portal by knocking over
\Gls{Ridcu}'s plank.

\subsection{}
\subsubsection{\Gls{Rince} and \Gls{Scrappy} look at the underground cave}
In the waterhole, \Gls{Rince} notices the absence of any flies, and sees a small lake underground,
together with the collapsed remains of a tunnel network. \Gls{Scrappy} points out a cave painting
resembling a group of University wizards, and tells him that it wasn't there a week ago. \Gls{Rince}
realizes he has been receiving help from an unknown source with his uncanny luck in finding food
under rocks, and water sources every night.

\subsubsection{\Gls{Ridcu} realizes the extent of the trouble they are in}
\Gls{Ridcu} gets to work fishing for dinner, as the rest of the wizards try to forage for food and
fresh water. \Gls{Whitlow}, convinced that the council is pulling a harmless prank on her, starts to
get anxious about returning to the university. Meanwhile,

\subsubsection{\Gls{Scrappy} talks about the trouble in the last continent}
\Gls{Scrappy} tries to tell \Gls{Rince} that Terror Incongnita was the last continent to be
designed, and had different rules of space and time. \Gls{Rince} fails to make sense of the assetion
that his arrival on the continent had changed history thousands of years ago, leading to trouble in
the present. \Gls{Scrappy} then tells him that it is his mission to integrate the continent into the
rest of Discworld by righting the wrongs.

\subsubsection{The inner council find some strange food in the forest}
\Gls{Indef} arrives from the nearby forest with some nuts and berries, including a curious looking
cigarette. \Gls{Ridcu} is desperate to find the bush where the cigarettes grow, and immediately
lights one up, to relieve his nicotine itch. The rest of the council are surprised to see fruits
having baked confections stuffed inside them, as the others notice the \Gls{Bursar} gorging on the
nuts.

\subsubsection{\Gls{Scrappy} talks about rescuing the last continent}
\Gls{Scrappy} tells \Gls{Rince} that he as already saved the continent, just that the jumbled nature
of time makes it so that he must be egged on to do it again to complete the causal loop. \Gls{Rince}
is annoyed at the tedium of a trek through the dangerous desert, and learns that his mission will
have succeeded when the continent receives rainfall again.

\subsubsection{\Gls{Rince} decides to run away from the underground oasis}
\Gls{Scrappy} explains that someone had come along and added the last continent as a sneaky extra
after the \Gls{Creat} had initially designed the Discworld. \Gls{Rince} pretends to sleep as night
falls, and waits till \Gls{Scrappy} leaves him alone to run away from the underground cave. A
drawing of \Gls{Scrappy} fades away at a nearby rock, satisfied that \Gls{Rince} has inadvertently
embarked on the mission.

\subsubsection{The inner council scavenge a meal for the night}
\Gls{Whitlow} eats at a makeshift table made out of wood, as the rest of the wizards dine on the
local enchanted flora at a campfire. They notice the empty pair of boots, seemingly belonging to
the geography professor, and surmise that the desserts are an after-effect of his magic. Meanwhile,
the \Gls{Libra} notices something important about the island, but sneezes and turns into a giant
conch before he can inform the council.

\subsubsection{\Gls{Stibb} argues with \Gls{Ridcu} about evolution}
\Gls{Stibb} realizes that the \Gls{Libra} had been trying to point out the fact that there was
only one of each kind of tree or fish, and that there was not time for evolution to take its course
naturally. All of a sudden, an alligator-like creature emerges from the forest, and charges at the
wizards. \Gls{Ridcu} and the rest prepare their magic, even as \Gls{Stibb} questions the ethics of
killing an endangered animal.

\subsubsection{\Gls{Rince} meets up with the dwarf named \Gls{Mad}}
The monster turns into a chicken after undergoing rapid changes in its shape, and \Gls{Ridcu}
decides to cook it using the fireball he had charged up. Meanwhile, \Gls{Rince} runs into an armored
cart being pulled by a team of horses, and gets captured by the dwarf riding it. The dwarf calls
himself \Gls{Mad}, and asks \Gls{Rince} to hold off some pirates pursuing him with a crossbow.

\subsubsection{\Gls{Mad} and \Gls{Rince} flee the desert pirates}
\Gls{Mad} tells \Gls{Rince} that he has been journeying through the roads of Terror Incognita for
many years, and warns him of the emu-riding gangs giving chase. \Gls{Rince} is almost killed by
the gang's arrows, as \Gls{Mad} prepares the supercharger for his carriage. Another pirate on a
camel falls off his mount all of a sudden, causing a pile up that destroys all of the pirate wagons.

\subsubsection{\Gls{Rince} learns about the vagaries of life in the XXXX desert}
\Gls{Rince} and \Gls{Mad} inspect the wreckage of the pile-up, with the camel grazing nearby.
\Gls{Mad} inspects and discards several shoddy weapons used by the pirates, and asks \Gls{Rince}
to take the bale of hay to his cart, recognizing it as quality feed for his horses. \Gls{Rince}
finds the pirate's corpse, and notices a large spider hidden in his robes, as he retrieves his
hat.

\subsubsection{\Gls{Stibb} is frustrated by the old heads in the inner council}
\Gls{Stibb} tries and fails to get the council to take him seriously, as his hypotheses about
evolution are dismissed without a second thought. He asks the \Gls{Libra} if he has noticed the
absence of any flotsam in the driftwood they found, and is dismayed when the \Gls{Libra} morphs
into a furry red penguin. The wizards retire for the night, after constructing a hut for
\Gls{Whitlow}, and \Gls{Stibb} is left to stand guard.

\subsubsection{\Gls{Rince} talks about precipitation with \Gls{Mad}}
\Gls{Rince} asks \Gls{Mad} about his early life, and learns that the dwarf migrated to the mainland
of XXXX from the nearby island city of Nothingfjord, after their voyage was hit by a sea-storm.
\Gls{Mad} is incredulous at \Gls{Rince}'s suggestion that rainfall is real, and that water falls
from the sky. He insists that water belongs deep underground, and asks how something as heavy as
water rises so high in the first place.

\subsubsection{\Gls{Stibb} tells the inner council that they are stuck in the distant past}
\Gls{Stibb} works out the fact that the portal has taken them many millennia in the past, from the
change in the night sky, and tries to tell the rest of the wizards that they could end up changing
the future unintentionally. \Gls{Ridcu} remains obtuse when presented with the idea of accidentally
killing his own ancestor, and thus erasing his own existence.

\subsubsection{\Gls{Ridcu} and \Gls{Stibb} argue about the nature of predestination}
\Gls{Ridcu} comes up with the idea of determinism, and tells \Gls{Stibb} that they cannot actually
do anything to change history, since that would mean they could not come back to the past to make
that change in the first place. He tells the other wizards not to worry about affecting the future,
as \Gls{Stibb} conceals his anger at the cavalier attitude of the Archchancellor.

\subsubsection{The \Gls{EGod} decides to hasten the wizards' escape from his island}
The \Gls{EGod} ponders the idea of shooing away the intruders on his island, as he congratulates
himself on the rapid evolution of his custom-designed cigarette bush. He gets back to work
designing more bizarre plants, in his temple on the mountain deep inland. Meanwhile, \Gls{Mad} leads
\Gls{Rince} to the largest settlement in XXXX, which turns out to be a small street and a single
run-down tavern.

\subsubsection{\Gls{Dean} and the other wizards are alarmed by the trees showing up around them}
The \Gls{Dean} and the other council members talk about their failure to find a library on the
island to help them learn how to build a boat, as \Gls{Ridcu} gets to work exercising first thing
in the morning. \Gls{Indef} makes note of the bizarre flora that \Gls{Stibb} has found for
breakfast, and wishes to get off the island as soon as possible.

\subsubsection{\Gls{Dongo} talks to \Gls{Rince} about the local liquor}
The half-crocodile barman, \Gls{Dongo}, tells \Gls{Rince} that they have some quality beer, as he
notices the other half-animal denizens of the tavern. A while later, \Gls{Mad} enters the bar to
ask another customer to put down \Gls{Rince}, and takes out his crossbow to prepare for the
inevitable bar-fight.

\subsubsection{The \Gls{Bursar} finds a strange log throbbing with fluid}
The \Gls{Bursar}, tired of \Gls{Ridcu}'s enforced morale-building exercises, temporarily shakes
out of his insanity, to stomp on some ants that might be lead to \Gls{Ridcu} never existing. He
follows a long stem lying on the ground, that sounds like a pipe with liquid flowing through it.
Meanwhile, \Gls{Ridcu} is happy to see the rest of the wizards find a log suitable for building a
raft.

\subsubsection{\Gls{Rince} wakes up from a night of heavy drinking}
\Gls{Rince} wakes up the next day hungover, and tries to recall the details of \Gls{Mad} fighting
some animals at the tavern. \Gls{Scrappy} tells him that his mission is still waiting, as he notices
more etching representing the council of wizards on a makeshift toilet behind the bar. He decides to
head to the town of Bugarup, believing it might have a port, and some ships to take him home.

\subsection{}
\subsubsection{\Gls{Ridcu} and the wizards find the boat made of pumpkin}
The \Gls{Bursar} tries to explain to \Gls{Ridcu} that he has found a ship floating along the
coast, complete with sails, and a mermaid-shaped figurehead. \Gls{Wrangler} is flustered by
\Gls{Whitlow}'s sarong, as she asks them for directions to a pool inland. Meanwhile, the wizards
inspect the pumpkin-ship, with \Gls{Ridcu} voting for an immediate escape from the island.

\subsubsection{\Gls{EGod} talks to the inner council of wizards}
The \Gls{EGod} materializes as a three-foot tall old man in white robes, and tries to threaten
the wizards with dire consequences, unless they flee his island. \Gls{Ridcu} refuses to take him
seriously, as he narrates his tale of despair and hopelessness, bemoaning the spread of organized
religion. He had decided to leave his dwindling group of followers and come back to the small
island, to put his practice of gene splicing and evolution to work designing a better world.

\subsubsection{\Gls{Ridcu} and the other wizards prepare to leave the island}
\Gls{Ridcu} suggests that there might be multiple Gods of evolution, and that the best among them
might eventually win, leading to the \Gls{EGod} vanishing. \Gls{Stibb} realizes that he might have
hit upon the idea of natural selection by competition, as the final puzzle piece to his idea of
evolution. \Gls{Stibb} is dismayed at the eagerness of the other wizards to set sail immediately,
ignoring the island's potential as a research subject.

\subsubsection{\Gls{Rince} wakes up from his drinking binge}
\Gls{Rince} tries to recall the events of last night, as he wakes up from his blackout. \Gls{Dongo}
tells him that he had placed an outrageous wager last night in a sheep shearing face-off against a
local champion, after blowing all the money \Gls{Mad} had given him in betting on coin tosses.
He notices the poster with \Gls{Scrappy} changing in place, with the kangaroo vanishing, and
eventually reappearing facing the opposite direction.

\subsubsection{\Gls{Rince} goes to the sheep pen to make good on his bet}
The \Gls{Lugg} walks along a desert track, unsure of where to go in search of its owner, and is
picked up by a purple carriage, bearing the name Desert Princess. Meanwhile, \Gls{Rince} makes a
mess of his first sheep, making the assembled shearers suspect his ability to win the challenge.
\Gls{Daggy}, the head shearer, tells him that the challenge is simply one of speed, and backs off
as a huge ram paces towards them from the pen.

\subsubsection{\Gls{Scrappy} helps \Gls{Rince} win his shearing challenge}
\Gls{Scrappy} whispers to \Gls{Rince} that the sheep will be enchanted into cutting their fur
automatically on his shears, and disappears into the barn's rear wall. \Gls{Rince} wins the
challenge, and the sheares tell him that they do not have the money yet. He rejects the reward, and
asks for the fastest way to Bugarup. Terrified of his magic, the shearers give him their only horse,
named \Gls{Snowy} and point him in the direction of the coastal city.

\subsubsection{\Gls{Ridcu} inspects the melon-boat as the others load supplies}
One of the shearers asks \Gls{Daggy} if he has indeed owned \Gls{Snowy} for many years, and if his
story of winning it off someone in a bet is a false memory. He tries to think through the fog in
his mind, and gives up, accepting whatever he had just said as the truth. Meanwhile, \Gls{Ridcu}
learns of \Gls{Stibb} wandering off into the island, and decides to look for him. He believes that
\Gls{Stibb} is miffed at their decision to leave the island, instead of probing its secrets further.

\subsubsection{\Gls{Rince} helps some sheep with groundwater}
\Gls{Rince} comes across a broken-down windmill, and finds a herd of thirsty sheep looking at him
for water. He decides to dig into the ground, and finds a dwindling reservoir. He manages to carry
some of the groundwater to a trough for the sheep, and notices \Gls{Snowy} unperturbed by all the
commotion. A while later, he comes across a well-worn trader track, and spots a group of horsemen
chasing some wild horses through the desert cliffs.

\subsubsection{\Gls{Snowy} accidentally corners the herd of wild horses}
\Gls{Snowy} reaches a steep canyon, and walks down the wall nonchalantly, before scaling the
opposite wall with equal ease. \Gls{Rince} hangs on desperately, recalling \Gls{Daggy}'s words about
the breed being selected for its sure-footedness, as \Gls{Snowy} walks upside down onto an overhang.
Eventually, \Gls{Snowy} manages to engineer a small rockslide to trap the wild horses in a narrow
canyon, just as the herders catch up. They marvel at \Gls{Snowy}'s skills, and offer to buy the
horse off \Gls{Rince}.

\subsubsection{\Gls{Rince} sets off to Bugarup with help from \Gls{Remorse} and \Gls{Clancy}}
\Gls{Remorse}, the lead shepherd, tells \Gls{Rince} that Bugarup is a dangerous place, as his
underling \Gls{Clancy} talks about rangers in the desert who might help him on the way. \Gls{Rince}
refuses their offer of hospitality, and is grateful for the bag of rations they give him, along with
some cash for herding the wild horses. He sets off in the direction of Bugarup, leaving the
horsemen to discuss the fine art of metaphor as an adjective.

\subsubsection{\Gls{Stibb} talks to the \Gls{EGod} in his mountain abode}
\Gls{Stibb} walks into the workshop of the \Gls{EGod} at the top of his mountain, and notices an
elephant being assembled. He points out the futility of wheels on the elephant, leading the
\Gls{EGod} to design another beetle to deal with his despondence. \Gls{Stibb} realizes that the
\Gls{EGod} has not worked out reproduction, and is designing the next iteration of each creature by
hand, making whatever improvements he deems necessary.

\subsubsection{\Gls{Ridcu} and \Gls{Whitlow} talk to the \Gls{EGod}}
\Gls{Ridcu} and the other wizards walk into the workshop, just as \Gls{Stibb} tries to explain
reproduction to the \Gls{EGod}, and makes him realize that a lot of his workload might be dealt with
if his creations could make copies of themselves. \Gls{Whitlow} walks in to explain reproduction to
the \Gls{EGod}, satisfying his curiosity, and convincing him to let the wizards leave his cave.
\Gls{Stibb} chooses to stay on as the god's assistant, as \Gls{Ridcu} and the inner council take
their leave.

\subsubsection{\Gls{Ridcu} and the council return to the melon-ship}
On their way back to the melon-ship, the wizards discuss the idea of sexual selection, and wonder
how the \Gls{EGod} will work with the idea of attractive traits in different species. \Gls{Ridcu}
is glad that a wizard from the Unseen University will contribute to the design of all life on the
island, as he leads the rest of them down the mountain.

\subsubsection{\Gls{Rince} invents vegemite and gets caught by rangers}
\Gls{Rince} dumps his supply of beer into a cooking pot filled with vegetables, and passes out from
exhaustion as it stews overnight. The next morning, he finds some sheep wandering into his camp,
hungry for food, and looks at the brown sludge left in the pot (vegemite). He digs another hole in
search of groundwater, and finds himself surrounded by armoured horsemen pointing crossbows at
him.

\subsubsection{\Gls{Stibb} is happy to participate in the design of intelligent life}
\Gls{Stibb} is happy to learn that the \Gls{EGod} is working on a fancy project, involving an
adaptable and resourceful life-form that is not confined to one habitat, or to one food source. He
eagerly walks into the hidden chamber with the \Gls{EGod}, expecting to find some sort of prototype
human, and is shocked to see a cockroach.

\subsubsection{\Gls{Stibb} reunites with the inner council of wizards}
The wizards on board the melon-ship fall over each other in their attempts to serve \Gls{Whitlow},
as \Gls{Ridcu} notices the \Gls{Libra} turn into a deck chair when he boards the ship. After a
while, \Gls{Stibb} swims out to the ship, horrified by the cockroach that the \Gls{EGod} had
claimed as his masterpiece.

\subsubsection{\Gls{Rince} is captured pending execution}
\Gls{Rince} learns from the jailer that he is to be hanged the next morning for the crime of
sheep-stealing, and is amused to find the sheep in the same jail cell. One of the song-writers
prepares a song to memorialize him for his crimes, and lets slip the fact that another prisoner had
managed to break out of the same jail cell multiple times. \Gls{Death} materialized in front of
him a while later, and tells him that he is due to escape his hanging, before vanishing through a
wall.

\subsubsection{\Gls{Rince} escapes the jail cell after \Gls{Death} tells him that he will live}
\Gls{Rince} sees a message scribbled on the jail cells's ceiling, telling him to undo the hinges to
the cell door. He decides to try lifting the heavy door off its hinges, hoping to put them back in
place after he slips out. After \Gls{Rince} leaves the jail cell in Bugarup city, the sheep in his
cell dissolves into the wall, becoming a painting of \Gls{Scrappy} before fading away.

\subsubsection{\Gls{Ridcu} talks to \Gls{Stibb} about the side effects of strong magical fields}
\Gls{Stibb} notices the perpetual storm-front encircling XXXX, and wonders if the intense magical
field is going to affect the wizards. He starts to grow irritable, and the \Gls{Dean} becomes
civil, causing \Gls{Ridcu} to suspect the handiwork of the magical field. The ship hits the
storm-front, just as \Gls{Ridcu} sees the excessive magic in the air surrounding them.

\subsection{}
\subsubsection{\Gls{Rince} talks to \Gls{FGDibb} outside the prison}
Out in an alley beside the prison, \Gls{Rince} runs into \Gls{FGDibb}, yet another member of the
expansive Dibbler diaspora, and immediately starts to see through his sales pitch. He decides to
buy one of \Gls{FGDibb}'s meat pies, and is spotted by a patrolling guardsman as he is distracted
by the pie's flavour.

\subsubsection{\Gls{Rince} manages to evade the pursuing guardsmen}
\Gls{Rince} finds the opera house of Bugarup next to the harbour, and enters it, afraid of the
heavy footsteps closing in from the city center. The chef at the opera house mistakes him for a
substitute cook, and tasks him with designing a gimmick dessert for the prima donna in their next
big show.

\subsubsection{\Gls{Whitlow} and the wizards lose their ship in the rough seas}
A fight breaks out on the melon-ship, as it breaches through the storm-front, and comes in view of
the XXXX coast. \Gls{Whitlow} decides to let the wizards float along on the pumpkin seeds, and
swims for the shore, disregarding the warnings about sharks. Meanwhile, \Gls{Ridcu} gets into an
argument with the \Gls{Dean} and the \Gls{Indef} about who fired the magic that breached the ship's
hull, as \Gls{Stibb} spots the sharks also heading for the shore.

\subsubsection{\Gls{Rince} notices some guardsmen passing by the opera house}
\Gls{Rince} hides in the depths of the kitchen, as the guardsmen come searching through the street,
as the head chef \Gls{Ron} tells them about the night's show reaching half-time. \Gls{Charley}, the
cook originally in charge of making dessert, comes up with some suggestions for peach and ice cream,
which \Gls{Rince} agrees to.

\subsubsection{\Gls{Rince} learns of the bizarre traditions of XXXX}
\Gls{Rince} invents a new dessert, just in time for the jailer to barge into the kitchen, and
threaten \Gls{Rince} with dire consequences once he gets caught. He is amused to hear that the
guards will give him a ten second head start, so that the ballads singing of his last stand can be
suitably heroic. \Gls{Rince} decides to defy their traditions of a fight to the death, and runs for
the safety of the harbour.

\subsubsection{\Gls{Rince} runs into \Gls{Letitia} in the grand carnival of Bugarup}
\Gls{Scrappy} appears in front of \Gls{Rince} to remind him that a legend was steadily being
built up around his exploits, and that he was close to becoming the hero that the continent needed.
He then runs into a carnival, where \Gls{Letitia}, one of the carnival float managers, takes him
on board her carriage.

\subsubsection{\Gls{Rince} is reunited with the \Gls{Lugg}}
\Gls{Rince} sees the crowds gathering around the carnival procession, and hopes that the city
watch will find it difficult to track him down. Someone in the crowds recognizes him from his
wizard's hat, and he is forced to bid goodbye to \Gls{Letitia}, and jump off the carriage. He runs
into a dead end alleyway, with some guardsmen who recognize him, just as the \Gls{Lugg}, now wearing
hundreds of heels on its feet, lands next to him from \Gls{Letitia}'s wagon.

\subsubsection{\Gls{Stibb} and the wizards reach the shores of XXXX}
The wizards crash into the beach, after being sucked into an undersea current that spits them out
close to the shore. Meanwhile, the \Gls{Bursar} elegantly surfs a wave using his melon-seed, and
lands on his feet, before wandering off inland. \Gls{Ridcu} accidentally melts a rock when he tries
to demonstrate a small fireball to lift the spirits of his council. \Gls{Stibb} reminds him of the
intense magical field pervading the continent, and of how the place still had no vegetation.

\subsubsection{\Gls{Stibb} is shown a glimpse of his mortality}
\Gls{Stibb} morphs into an old man under the influece of the magical instability, just as the other
wizards morph into children. A while later, as they manage to regain control of their minds, and
morph back to their old forms, \Gls{Stibb} comments on the physical weakness he felt as an old man,
and immediately sets about finding the \Gls{Creat} in charge of designing the place.

\subsubsection{The \Gls{Bursar} finds a \Gls{Creat} making life on the continent}
\Gls{Whitlow} joins the wizards with the \Gls{Libra} in her arms, now morphed into a baby orangutan.
\Gls{Ridcu} warns her to loosen her clothing as her own temporal instability resolves, returning her
to her original age. Meanwhile, the \Gls{Bursar} wanders into a forest, where an old black man
draws on a cliff wall, using simple white paint, and creates new life from the very lines of his
artwork.

\subsubsection{\Gls{Rince} learns about \Gls{Neilette}'s past}
\Gls{Rince} finds \Gls{Neilette} hiding inside the \Gls{Lugg}, after it beats up the guardsmen in
the alley. She talks about her brother coming out as a transgender woman, and their father disowning
him for it. She then mentions the beer factory that had failed, leaving the family destitute, and
forcing her to find work in \Gls{Darleen}'s troupe.

\subsubsection{\Gls{Rince} escapes the brewery as it collapses in a fiery ruin}
\Gls{Rince} sees another earthquake start to collapse the brewery, and hides inside the \Gls{Lugg}
with \Gls{Neilette}. A while later, as the city watch try to put out the burning brewery and find
the water pumps running dry, \Gls{Rince} asks \Gls{Neilette} if there is a University for wizards in
the city. She says yes, before mumbling about how useless they are, and agrees to help him find
the place.

\subsubsection{\Gls{Rince} sneaks into the University of Bugarup}
\Gls{Ridcu} and the council find the \Gls{Bursar} and the old man painting the animals, and get to
work drawing a duck. They accidentally design the duck-billed platypus, as they revise each other's
drawings, adding their own touches to the figure. Meanwhile, \Gls{Rince} finds a secret side
entrance into the University of Bugarup, and walks in, to find the inner council mistaking him for
a demon. They ask him about the water table receding, and are shocked when he mentions the idea of
rainfall.

\subsubsection{\Gls{Rince} marvels at the magical tower of the Bugarup University}
\Gls{Rince} learns of the failed attempts at summoning clouds, and tells the Archchancellor that
his university's tower is very small. Miffed by the insult, the Archchancellor takes him to the
top of the tower, which turns out to be a hundred times higher than it looks from the outside.
Meanwhile, \Gls{Stibb} helps the \Gls{Libra} untangle himself from a string toy, as he plays with
the other objects in his leather sack.

\subsubsection{\Gls{Rince} meets his distant cousin \Gls{BillR}}
\Gls{Stibb} notices the \Gls{Creat} draw the council of wizards using his enchanted white paint, as
the rainfall stops and night falls on the land. Meanwhile, the Archchancellor of Bugarup University,
named \Gls{BillR}, offers some beer to help \Gls{Rince} unwind, and is dismayed to hear more talk
of precipitation. He decides to take \Gls{Rince} to the abandoned brewery, to investigate the
drawing of the council of wizards.

\subsubsection{\Gls{Rince} descends into the cellars under the brewery}
\Gls{Rince} climbs down into the brewery's cellar, now drunk on beer, and is happy to see the
\Gls{Lugg} join him. \Gls{BillR} and his council descend shortly after, with some meat pies from
\Gls{FGDibb} per \Gls{Rince}'s request. \Gls{Rince} keeps himself in a constant state of tipsiness,
which allows him to think clearly about the cave system underneath the city.

\subsubsection{\Gls{Rince} pulls the inner council into the present using the magical paint}
\Gls{Rince} guesses that the cave system just appeared beneath the city because of some abrupt
change in the timeline, and probably wasn't present when the brewery was built. He decides to paint
an impression of the Unseen University's inner council on the enchanted rock at the center of the
cave, and drags them into the present using its magic. The lot of them hastily flee the cave as it
closes in on itself, having been erased from the past.

\subsubsection{\Gls{Rince} talks to the \Gls{Libra} about his yo-yo}
\Gls{Ridcu} tries to impress \Gls{BillR} with his knowledge of rain-making spells, as they sit
around in the central chamber of Bugarup University, discussing possible means of getting off the
continent. At the top of the University's tower, \Gls{Rince} plays with the \Gls{Libra}'s yo-yo,
and notices it spin on its own at the slightest bit of effort. He sniffs the smell of rain when he
spins it, and decides to heave it around in big circles.

\subsubsection{\Gls{Rince} destroys the magical storm-front preventing rainclouds in XXXX}
The magical air currents created by the yo-yo nullify the storm-front circling the continent, and
enable the rain-bearing clouds to finally float over the landmass. Meanwhile, \Gls{Clancy} and
\Gls{Remorse} tend to the wild horses, slowly dying of thirst, and are shocked to see rainclouds
floating over them, starting to drizzle rain.

\subsubsection{\Gls{Rince} and the \Gls{Libra} escape the University's tower burning down}
At Bugarup University, \Gls{Rince} and the \Gls{Libra} almost get burnt up when a massive lightning
discharge hits the metal tower, but manage to get away from the rubble at the last moment. The
sudden rain brings in permanent ecological change to XXXX, as the city of Bugarup hails the wizards
as their saviors.

\subsubsection{\Gls{Rince} departs to Ankh-Morpork along with the wizards}
\Gls{Rince} says goodbye to all of his friends from the last few months, and climbs aboard the
ship waiting to take them home. Meanwhile, a tribal elder throws his ancestral boomerang into the
sky, prompting the gathered rainclouds to disperse all over the continent. His grandson is happy to
have witnessed the Wet, finally realizing why a word for the smell of rain had been passed down
through the generations.