\section{The Last Hero}


\subsection{}
\subsubsection{\Gls{Vetina} listens to \Gls{Ridcu} and \Gls{Stibb} explain their new contraption}
\Gls{Vetina} receives a letter by albatross, and hurries to Unseen University so that he can ask
the wizards for help. They set up a looking glass that is capable of scrying any place on the Disc,
and \Gls{Stibb} explains how difficult it is to get the device to focus on a given point in
spacetime. \Gls{Ridcu} advises \Gls{Vetina} not to ask about scrying the future, since the act of
observation would eliminate all possible alternate futures.

\subsubsection{\Gls{Vetina} wishes to track the location of \Gls{Cohen}}
\Gls{Vetina} asks to home in on \Gls{Cohen}, claiming that he has received news of the horde
heading for Cori Celesti. \Gls{Stibb} is disappointed that there is no personal belonging of
\Gls{Cohen}'s that they can use to tune the looking glass to his location, while \Gls{Vetina} talks
about returning what the first hero had stolen from the Gods.

\subsubsection{\Gls{Vetina} explains the desperate request from the Agatean Empire}
The council of Guildmasters gather in Unseen University, and listen to \Gls{Vetina} repeat the
message from the Agatean Empire. They fear that \Gls{Cohen} has given up his position on the
Agatean throne, and gathered his horde of old heroes to take some destructive weapon to
Dunmanifestin, threatening the end of the world.

\subsubsection{\Gls{Stibb} talks about how vital magic is to life on the Disc}
\Gls{Ridcu} states that all magic stops working close to Cori Celesti, as \Gls{Slant} recalls the
stories of fire being stolen from the Gods, as the first recorded act of heroism on the Disc.
\Gls{Vetina} states that \Gls{Cohen} has some powerful explosives that will disable all magic on
the Disc for a few years if detonated in Dunmanifestin, and \Gls{Stibb} explains how life itself
will come to an end mere minutes after such an explosion.

\subsubsection{The Silver Horde discuss their progress on \Gls{Cohen}'s final mission}
\Gls{BWill}, \Gls{MHam} and \Gls{Truckle} discuss the ugly death of one of their fellow barbarian
heroes, as they make camp on the foothills of Cori Celesti. They pass some food along to a poet
from the Agatean court, who has been dragged along by \Gls{Cohen} for some reason, and wonder where
he has gone off to. Meanwhile, \Gls{Rince} fills in \Gls{Vetina} on his adventures in the Agatean
Empire, and explains that the Silver Horde had all the wealth they could hope for as rulers of the
Empire.

\subsubsection{\Gls{Vetina} enlists \Gls{LeoQ} to help chase down the Silver Horde}
\Gls{Vetina} goes to \Gls{LeoQ}'s secret workshop in the palace, and is surprised to find him ready
with a solution to his problem of beating the Silver Horde to Cori Celesti. \Gls{LeoQ} asks for
hundreds of swamp dragons to be corralled, as well as an army of craftsmen to build the blueprints
he is sketching.

\subsubsection{\Gls{Cohen} tries to get the bard to record their adventure in a saga}
The rest of the barbarians find \Gls{Cohen} meditating next to the burial mound of some ancient
hero, and inform him that the bard they brought along seems to be uninterested in chronicling
their last great adventure. \Gls{Cohen} decides to knock some sense into the bard, and tells the
others that he does not expect them to make it out of Cori Celesti alive.

\subsubsection{\Gls{LeoQ} talks about his plan to send a small crew flying into Cori Celesti}
\Gls{LeoQ} outlines his idea to use the elephants under the Disc as a gravitational slingshot to
get his device to emerge from the opposite end of the Disc and fly straight into Cori Celesti. He
asks for the wizards to supply a magical wind to get his aircraft off the edge of the Disc, while
the \Gls{Dean} remains skeptical about the engineering behind the contraption.

\subsubsection{\Gls{Vetina} helps assemble a crew for \Gls{LeoQ} to fly with}
\Gls{Vetina} sets up a committee to decide who will accompany \Gls{LeoQ} on his flying machine, and
is surprised to see \Gls{Carrot} volunteer. \Gls{Rince} runs into the room, refusing to come along
before anyone even asks him to. \Gls{Ridcu} immediately reminds everyone of the prior contact
\Gls{Rince} has had with the Horde, and of how they would be likely to listen to him. \Gls{Vetina}
decides to add \Gls{Rince} to the list of passengers on the flying machine, even as \Gls{Rince}
realizes he could never wriggle out of the responsibility.

\subsubsection{\Gls{Cohen} shows the bard the bounty he will receive for writing a poem about the
    Silver Horde's last adventure}
A mysterious female barbarian deals with some bandits who try to waylay her as she lights a fire to
keep warn in the snowy weather. Meanwhile, \Gls{Cohen} entices the bard with a payout of precious
gems if he writes the saga of their heroic deaths. \Gls{Vetina} supervises the fleet of ships
bearing \Gls{LeoQ}'s makeshift workshop, as they prepare to set sail for to the Disc's rim.

\subsubsection{\Gls{Cohen} muses on the unfair deaths of his comrades over the years}
\Gls{Cohen} talks about growing old, and of how the Gods denied his fellow barbarians the heroic
afterlife they were supposed to get. He wishes to take revenge by blowing up Dunmanifestin in a
grand suicide pact with the Gods, just as some trolls ambush the Silver Horde. Meanwhile, a
freak accident on the barge breaks the looking glass that \Gls{Ridcu} had commissioned to follow
the progress of \Gls{LeoQ}'s flying machine.

\subsubsection{\Gls{Cohen} invites \Gls{EHar} and his henchmen along for the mission}
\Gls{EHar} embraces \Gls{Cohen} as a long-lost friend, and talks about how the business of being
a villain has changed, with the advent of modern systems of government across the Disc. He asks
the Dark Lord to join the Horde along with his henchmen, since there seems to be no place left in
the modern Disc for either of them.

\subsubsection{\Gls{Hughnon} tries to herd the clergymen in the Temple of Small Gods}
\Gls{Vetina} wonders how the swamp dragons will power the flight of \Gls{LeoQ}'s machine, as he
inspects the cages on a different ship accompanying the fleet at a distance. Meanwhile,
\Gls{Hughnon} addresses a gathering of clergymen from the major religions of the Disc, and is
dismayed to see some of them welcoming the apocalypse.

\subsubsection{\Gls{Death} observes the hourglass of \Gls{Atuin}}
\Gls{EHar} helps \Gls{BWill} drag the wheelchair of \Gls{MHam} through the snowy paths, as
\Gls{Cohen} scouts the cave network up ahead. Meanwhile, \Gls{Albert} tries to explain the idea of
multiverses to \Gls{Death}, who is busy trying to make sense of the cat in a box experiment. He
pulls out the hourglass of \Gls{Atuin}, and senses trouble for the Disc in its entirety.

\subsubsection{\Gls{Cohen} finds the handiwork of the female barbarian}
\Gls{Cohen} and the barbarians come across the bandits killed by the mysterious old woman, and
wonder who used knitting yarn as a weapon of self-defense. Meanwhile, \Gls{Carrot} sews some
patches for \Gls{Rince} and \Gls{LeoQ}, bearing the symbol of the new space mission. \Gls{Rince}
wonders if the Silver Horde were so addicted to conflict that they could not remain sated by the
wealthy lifestyle they enjoyed in the Agatean palace for very long.

\subsubsection{The Silver Horde work their way through the traps on the way to Dunmanifestin}
The Silver Horde make it out of the gauntlet of deadly traps on the path to Cori Celesti, with the
minstrel traumatised by the number of times he almost died to one of the surprise traps. \Gls{EHar}
seems proud of his henchmen for trying their best to navigate the traps, even though they all died
along the way. Meanwhile, \Gls{LeoQ} perfects his special recipe that makes the swamp dragons
breathe fire without risking an explosion in their digestive systems.

\subsubsection{\Gls{Cohen} and the crew link up with \Gls{Vena} in a cave}
Following the scent of fish stew, the Silver Horde find \Gls{Vena} in a cave, and are surprised to
hear her recite the same story about an ancient scroll pointing the way to Cori Celesti, supposedly
the site of some buried treasure. The bard realizes that some supernatural entity has handed the
same instructions to \Gls{EHar}, \Gls{Cohen} and \Gls{Vena}, possibly to draw them into a fight to
the death.

\subsection{}
\subsubsection{The barbarians begin their climb up the central spire of Cori Celesti}
\Gls{Nuggan} tells the rest of the gods that the bard is close to uncovering their interference, and
tells \Gls{Offler} that he comes from the Borogravian religion. \Gls{Offler} asks him not to smite
the poor bard, and continues the game by rolling the dice. The barbarians begin their climb up the
central spire of Cori Celesti, which is magically able to bend gravity to act as a floor. \Gls{EHar}
has some trouble ignoring the actual ground rapidly receding behind him, as \Gls{Cohen} looks out
at the panorama, remarking that his adventures have taken him all through the Disc.

\subsubsection{\Gls{LeoQ} prepares the take-off platform for his flying machine}
\Gls{LeoQ} shows the wizards a new schematic to solve the issue of the Krullian trawlers at the
Rim that will prevent their ships from sailing over the edge of the Disc. Meanwhile, \Gls{Stibb}
tells \Gls{Rince} that it will be his responsibility to feed the third stage of swamp dragon
boosters the special feed formulated by \Gls{LeoQ}, once they are in microgravity.

\subsubsection{\Gls{LeoQ} guides his flying machine off the Disc's Rim}
\Gls{Vetina} gives a speech just before take-off, as \Gls{Stibb} asks the three chelonauts to pose
for a commemorative iconograph. The flying machine successfully takes off, powered by the breath
of a hundred swamp dragons, and goes over the rim. \Gls{LeoQ} tests out the control surfaces, as
\Gls{Carrot} manages to speak to \Gls{Stibb} through a piece of his shattered looking glass.

\subsubsection{\Gls{Carrot} finds the \Gls{Libra} stowed away on the ship}
The second stage boost is completed successfully, and \Gls{LeoQ} jettisons the second set of
swamp dragons, hoping that they can fly up to the Disc. \Gls{Rince} is alarmed by the microgravity,
and rushes to the bathroom to throw up, shortly followed by \Gls{Carrot}. \Gls{LeoQ} realizes that
they are using up air faster than expected, and \Gls{Carrot} searches the ship for a stowaway.
\Gls{Rince} contacts \Gls{Stibb} again, and reports that the \Gls{Libra} has joined them as a fourth
passenger.

\subsubsection{\Gls{Vetina} learns about the flying machine losing air and fuel too quickly}
As \Gls{Vena} prepares the next meal for the horde, \Gls{Cohen} talks to the bard about replacing
his lute. The bard recalls the legends of \Gls{Mazda} stealing fire from the Gods and getting
chained to a rock for all time, and having his organs picked at by crows every day. Meanwhile,
\Gls{Vetina} asks \Gls{Stibb} if the \Gls{Libra} cannot be jettisoned to save air and fuel, only to
be quieted down by the wizards. He starts to wonder if \Gls{Stibb} can transfer air from the
University to the ship using magic.

\subsubsection{\Gls{Cohen} gets the bard working on his poem again}
\Gls{Cohen} listens the tale of a great conqueror settling down to rule his vast empire on the Disc,
only for his heirs to lose all the power squabbling amongst themselves. He wishes all of his
children the best, and asks the bard to embellish as much as necessary when writing their saga.
Meanwhile, \Gls{Rince} notices a written message in the looking glass, as the rest of the crew
consider opening the doors to jettison some of their cargo.

\subsubsection{\Gls{Stibb} helps \Gls{LeoQ} perform an impromptu Moon landing}
\Gls{Stibb} suggests using some of their dragons for a boost into the Moon's orbit, and \Gls{LeoQ}
performs the necessary steering to get them on approach to the Moon. \Gls{Rince} wonders how they
will stay on the Moon, given its weak gravity, and hopes to refill their supply of if they manage to
land. \Gls{Carrot} reports to the wizards that they have landed on the Moon, and that something
ate his Ankh-Morpork flag shortly after he planted it on the ground.

\subsubsection{The four chelonauts appreciate the Moon's ecosystem}
\Gls{Rince} notices the dragons on the Moon, which look like ancestors of the swamp dragons on the
Disc. He takes note of the silvery vegetation dotting the Moon's surface, as \Gls{Carrot} points
out the loss of their dragon-fodder meant to help them perform their re-entry into the Disc. The
Moon rises over the Disc's plane after a few hours, with the chelonauts too stunned by the view to
speak.

\subsubsection{\Gls{Rince} and the other chelonauts overload the swamp dragons with fuel}
None of the chelonauts realize how energy-dense the Moon-plants are, and feed their swamp dragons
far more than the safe limit. One of them explodes when it burps involuntarily, rocking the ship
with the shockwave. Meanwhile, \Gls{EHar} despairs at the lack of planning from any of the heroes,
and suggests disguising \Gls{Cohen} as a new God when they try to enter Dunmanifestin.

\subsubsection{\Gls{Rince} desperately tries to stop the ship burning down from the swamp dragons
    breathing white fire}
\Gls{Rince} is the only person left conscious on the ship after the dragons breathe pure white
fire, causing it to accelerate so hard that it knocks out the rest of the crew. He pulls one of the
levers next to his seat, hoping that it will jettison the swamp dragons that will soon set fire to
the rest of the wooden structure if they keep firing any longer.

\subsubsection{\Gls{Cohen} works out that \Gls{EHar} is about to betray the Silver Horde}
\Gls{Cohen} works out that \Gls{EHar} has betrayed them when he refuses to accompany the heroes
into Dunmanifestin, after spending a lot of time coming up with false identities for each of them.
The barbarians are satisfied with playing the role of small Gods, even as \Gls{Io} plays his game of
dice with the rest of the pantheon in the Grand Hall of the Gods. \Gls{Fate} suggests humoring the
barbarians by playing along for a while, as \Gls{Lady} makes her move in secret.

\subsubsection{\Gls{Vetina} helps \Gls{Rince} engage the autopilot, as \Gls{LeoQ} remains
    unconscious}
\Gls{Vetina} works out which lever on the ship corresponds to the autopilot, and asks \Gls{Rince} to
pull the corresponding lever, as \Gls{Stibb} pores over the schematics trying to work out how to
manually steer it instead. Meanwhile, \Gls{Cohen} is proud of \Gls{EHar} for trying his best to
fulfil his role as the villain, and asks him to stay back and escort the bard to safety. The bard
refuses to turn back, and asks to accompany the heroes into Dunmanifestin, so that he can watch the
end of their adventure first-hand.

\subsubsection{\Gls{Fate} challenges \Gls{Cohen} to perform a mathematically impossible feat}
\Gls{Cohen} and the barbarians are welcomed by the Gods of Dunmanifestin, and ushered into the
Main Hall to participate in the dice game. \Gls{Fate} asks \Gls{Cohen} to throw a seven using a
seemingly normal die, and is shocked when \Gls{Cohen} cuts the die using a single stroke of his
sword, with the two halves adding up to seven. Meanwhile, \Gls{Rince} and the \Gls{Libra} manage
to get the flying machine on approach to Dunmanifestin, and use its gravity distorting field to
fly straight into the main gate.

\subsubsection{\Gls{Cohen} and the heroes confront the Gods}
The bard tries to assault \Gls{Nuggan} for the draconian dietary restrictions he had to face growing
up, and \Gls{Cohen} restrains him. He tells the Gods that the explosion is meant to signal to the
mortals on the Disc that they can throw away the yoke of religion, more than causing direct harm to
the Gods. \Gls{Carrot} and \Gls{Rince} manage to convince \Gls{Cohen} not to blow up Cori Celesti,
and the barbarians decide to descend the mountain just in time for the fuse on their bomb to finish
burning.

\subsubsection{\Gls{Cohen} and the heroes sacrifice their lives to save the Disc}
\Gls{Vena} and the bard, who stayed back in Dunmanifestin, comment on the bravery of the heroes
as they watch the explosion at ground level send its shockwaves up the mountain. The Gods curse
\Gls{LeoQ} with painting the ceiling of the Temple in Ankh-Morpork as punishment for daring to
invent powered flight. \Gls{Rince} asks the Gods to repair the machine so that it can fly them back
home as in its last flight.

\subsubsection{\Gls{Cohen} and the heroes reject the afterlife offered by the valkyries}
\Gls{EHar} helps the bard descend the mountain, and is surprised to see him throw away the gemstones
that \Gls{Cohen} had given him as payment for his poetry. The heroes waylay the group of valkyries
who descend to the site of the explosion to take them to the afterlife, and use the horses to
travel to parallel worlds, eager for adventure. \Gls{Vena} notices \Gls{Death} arriving to harvest
some souls, and is surprised to see him offer no explanation about the deaths of the heroes.

\subsubsection{\Gls{Mazda} is freed from his eternal punishment by \Gls{Cohen}}
The heroes liberate \Gls{Mazda} from his divine imprisonment, and continue on as spirits to other
worlds. \Gls{LeoQ} finishes his painting in the Temple of Small Gods in a few weeks, surprising
the priesthood with the grandiosity of his imagination. \Gls{Rince} notices the people of the city
scuttle the flying machine for spare parts the moment it lands on the Ankh river, and is not
surprised by the lack of praise for his successful mission saving the world.