\section{The Light Fantastic}


\subsection{}
\subsubsection{\Gls{GalderW} and his chain of command witness the Octavo produce its own magic}
\Gls{GalderW}, the Chancellor of Unseen University is summoned to the room holding the Octavo, as
the tome starts radiating raw magic, in response to \Gls{Rince} plunging to his death past the rim
of Discworld. The tome releases a giant ball of raw magic, that transmutes everything in its path,
as it rises through the underground levels to hover in the central hall of the university.

\subsubsection{\Gls{GalderW} reaches the top of a tower to observe the Discworld's rim}
\Gls{GalderW} and the wizards see the ball of raw magic resolve into a miniature model of the
Discworld, and head up to the University's terrace, to observe the model of Dunmanifestin. He
levitates himself up the Tower of Art, and observes a new dawn arise over Discworld, complete
with the shadow of Cori Celesti falling over the city.

\subsubsection{\Gls{Rince} is saved by the Spell of Change triggered by the Octavo}
\Gls{GalderW}'s second-in-command, \Gls{Trymon}, notices the miniature model of the Discworld expand
to life-size, and identifies it as a spell of change. The two of them notice no visible changes
around them, as it fades away with the coming of dawn. The spell moves \Gls{Rince} to a tall tree,
leading to a nasty fall into some pine needles. He is surprised when the tree replies to him, but
walks away after declaring its life boring.

\subsubsection{\Gls{Twofl} and the \Gls{Lugg} reunite with \Gls{Rince}}
\Gls{Twofl} and the \Gls{Lugg} also appear magically somewhere on the Disc, and manage to find
\Gls{Rince} wandering through the forest of talking trees. \Gls{Rince} tries to impress \Gls{Twofl}
with his knowledge of botany, as they struggle to find something edible in the vegetation. He is
alarmed at the small doors and windows in its cap, as \Gls{Twofl} tries to speculate why he
considers it inedible.

\subsubsection{\Gls{GalderW} and his inner council summon \Gls{Death} to interrogate him}
At the Unseen University, \Gls{GalderW} talks to the assembled council of eight powerful wizards,
about their inability to learn the reason behind the Spell of Change. They decide to summon
\Gls{Death}, and ask him about the events of that morning. \Gls{Death} tells them that the Octavo
had interfered in \Gls{Rince}'s death, in an effort to keep all of its spells intact.

\subsubsection{\Gls{Trymon} decides to beat \Gls{GalderW} and his council to the Library}
\Gls{Death} casually lets slip a prophecy that outlines the destruction of Discworld, unless all
eight Forbidden Spells are uttered in sequence sometime in the next two months. Meanwhile,
\Gls{Trymon} hurries to the Library, having observed the meeting of the inner council from a hidden
vantage point. He gives the head librarian, now morphed into an orangutan, some bananas in exchange
for a book about the Pyramids of Tsort.

\subsubsection{\Gls{Twofl} and \Gls{Rince} agree to follow \Gls{Swires} the gnome}
In the forest of Skund, \Gls{Twofl} and \Gls{Rince} argue about the identity of a small man living
in a mushroom cap, as \Gls{Twofl} narrates the fairy tale descriptions he had read as a child.
The gnome catches up to them, introduces itself as \Gls{Swires}, and points them to a nearby cottage
with food and shelter for full-sized humans. It turns out to be a gingerbread house belonging to a
long-dead witch.

\subsubsection{\Gls{Trymon} gets to work researching the Pyramids of Tsort}
Meanwhile, \Gls{Trymon} is busy trying to decipher the tome describing the construction of the Tsort
pyramids. A mysterious wizard with few teeth sits in a campfire along with some hubland barbarians,
and talks about the finer things in life.

\subsubsection{\Gls{GalderW} talks about the Spell burrowed in \Gls{Rince}'s mind}
\Gls{GalderW} receives \Gls{Trymon} in his workshop, and claims to know a better way to recapture
the spell hidden in \Gls{Rince}'s mind than mere brute force. \Gls{Trymon} is intrigued to learn
that the Great Spells will simply jump to another mind when their current owner dies, as
\Gls{GalderW} sends a homing arrow to kill \Gls{Rince}.

\subsubsection{\Gls{Trymon} tries and fails to kill \Gls{GalderW} to get the Great Spell}
\Gls{Trymon} tries to kill \Gls{GalderW} by throwing a kitchen knife at him, only for some defensive
spell to divert it harmlessly to the door. \Gls{Trymon} covets the Great Spell in \Gls{Rince}'s
mind, after reading about the rewards reserved for the person who recited all eight of them in the
Pyramid of Tsort.

\subsubsection{\Gls{Twofl} wishes to buy out the gingrebread house}
\Gls{Twofl} is interested in purchasing the gingerbread house of the old witch \Gls{Whitlow} to
turn it into a tourist attraction. Against \Gls{Rince}'s wishes, \Gls{Swires} arranges for the
forest council to sell it to \Gls{Twofl}, who believes he can pack it inside the pocket dimension
of the \Gls{Lugg}

\subsubsection{\Gls{Greyha} attempts to build a fortified room to keep \Gls{Death} at bay}
At the Unseen University, \Gls{Greyha}, one of \Gls{GalderW}'s fellow council members, and the
oldest wizard in the university, prepares a protective den meant to keep \Gls{Death} from getting
at him. The elaborate rituals fail, as \Gls{Death} simply enters the room through an airhole.

\subsubsection{\Gls{Twofl} and \Gls{Rince} escape the cottage on a flying broomstick}
A squad of junior wizards find the gingerbread cottage, and break in, just as \Gls{Twofl} and
\Gls{Rince} hide inside a small cupboard. As more young wizards converge on the cottage, and
get distracted by bumping off the other squads, \Gls{Twofl} finds a flying broomstick in the
cupboard. \Gls{Rince} drives it out of the cottage with \Gls{Twofl} riding pillion, just as
\Gls{GalderW}'s enchanted arrow zips into the building, and hits the \Gls{Lugg}.

\subsection{}
\subsubsection{\Gls{Rince} and \Gls{Twofl} notice the coming end of Discworld}
\Gls{Rince} and \Gls{Twofl} break through the thick layer of clouds covering the Disc, and notice
all the stars vanishing from the sky, with only one red dot approaching them in the distance.
\Gls{Rince} points the broomstick down, overcome with terror at the prospect of Discworld being
annihilated.

\subsubsection{\Gls{GalderW} finds the \Gls{Lugg} answering his spell of Recall}
In \Gls{GalderW}'s workshop, he completes the spell recalling his homing arrow, only for the
\Gls{Lugg} to land on him. Meanwhile, \Gls{Trymon}, who had been pushed back by a shockwave from
the spell, decides not to investigate whether the \Gls{Lugg} has eaten his master, and runs out of
the room.

\subsubsection{\Gls{Twofl} and \Gls{Rince} crash into \Gls{Belafon}'s flying rock}
\Gls{Twofl} and \Gls{Rince} crash into a rock flying high in the sky on their way down to the
ground, and find it being piloted by a young druid named \Gls{Belafon}. He claims to be delivering
a replacement stone for some time-measurement device (Stonehenge) in the mountains, and subscribes
to the druid system of magic based on persuasion and charm. \Gls{Rince} warns \Gls{Twofl} not to
insist on the utility of an almanac in telling the time, as opposed to the druid system of sun
shadows.

\subsubsection{\Gls{Belafon} lands his rock at the site of the Druid stonehenge}
At the University, \Gls{Trymon} is relieved to hear that the \Gls{Lugg} has left the premises, and
walked into the city. Meanwhile, \Gls{Rince} and \Gls{Twofl} land at the site of the Stonehenge,
to see the druids arguing about how it was already suffering inaccuracies in predicting the
sunrise. \Gls{Rince} is suddenly forced into sleep by the Great Spells, who talk to him about his
role in averting the coming calamity.

\subsection{}
\subsubsection{\Gls{Trymon} asks the Chief Astrologer of the University to read \Gls{Rince}'s
    horoscope}
At the observatory of the Unseen University, \Gls{Trymon} talks to the Chief Astrologer about the
prospect of the red dot in the sky being a massive star that might burn Discworld long before a
direct collision, and suggests the use of \Gls{Rince}'s horoscope to divine his current location.
The Astrologer reads the horoscope, which offers no specific information, except a warning about
druids.

\subsubsection{\Gls{Rince} tries to tell \Gls{Twofl} about the reality of priesthood}
\Gls{Twofl} is convinced that priests all over the world are men of poverty, chastity and discipline
the way they are in his homeland. \Gls{Rince} tries to explain that priests in his home deal in
ritual sacrifices, often involving the killing of innocent victims, all in the name of perpetuating
their religion. He sees the druids prepare for their festival by escorting a maiden in white to
the central ritual altar.

\subsubsection{\Gls{Rince} rescues \Gls{Twofl} with the help of heroic old man}
The old man, acclaimed as one of the greatest heroes of Discworld, breaks into the ritual circle,
just as \Gls{Twofl} tries to argue against the practice of human sacrifice. He starts to slaughter
the druids, allowing \Gls{Rince} to rescue the girl in white robes, as well as \Gls{Twofl}. He
notices the girl complain about her missed opportunity to reach heaven, as \Gls{Twofl} is grazed by
a druid's sickle.

\subsubsection{\Gls{Cohen} is rushed away from the commotion at the Stonehenge}
The old man, who reveals himself to be \Gls{Cohen} the Barbarian, takes a look at \Gls{Twofl},
and declares him mentally absent. \Gls{Rince} worries about the possibility of retrieving his mind,
as \Gls{Bethan}, the maiden in white robes, helps apply ointments on \Gls{Cohen}'s arthritic knees.
\Gls{Rince} notices the large white warhorse, matching his grandfather's descriptions of
\Gls{Cohen} and his majestic steed.

\subsubsection{\Gls{Rince} and the party are led to a necromancer of the stepp tribes}
Meanwhile, the \Gls{Lugg} barrels through a squad of wizards sent by \Gls{Trymon} to track
\Gls{Rince}, leaving them horrified by the prospect of facing a powerful necromancer. \Gls{Cohen}
leads the party to a chieftain of the steppe tribes, where an old woman tries to cast some Caroc
cards to divine \Gls{Twofl}'s location. \Gls{Rince} is made to drink a potion that sends him on a
spirit-walk, with only the old woman able to see his spirit rising from the tent.

\subsection{}
\subsubsection{\Gls{Trymon} takes charge of the council meeting at the University}
At the University's council hall, the six remaining old wizards worry about the threat presented by
\Gls{Trymon}, just as he walks into the room, distributing agenda sheets for the meeting.
\Gls{JigladW}, one of the original council members, is exasperated by his disregard for the archaic
ways of conducting University business, as they start to describe their failed attempts at tracking
down \Gls{Rince}.

\subsubsection{\Gls{Trymon} tells the council about the hero sent to track down \Gls{Rince}}
\Gls{Trymon} reveals to the council that he has sent a tracker to hunt down \Gls{Rince}, leading to
an argument breaking out about the need to hire heroes to do the work of wizrds. \Gls{Trymon}
reminds them that \Gls{Rince} is somehow able to evade magical detection, necessitating these
desperate measures.

\subsubsection{\Gls{Rince} travels to the house of \Gls{Death} as a spirit}
\Gls{Herrena}, the rare female hero of any renown in Discworld, rides with a posse of hired swords
to the Trollbone mountains, at the behest of \Gls{Trymon}. Meanwhile, \Gls{Rince} spirit-walks into
the realm of \Gls{Death}, where he finds his cottage. He sneaks into the cottage, to find an ornate
double staircase with a grandfather clock in between. The \Gls{Lugg}, which is waiting for him in
the garden next to the cottage, follows him inside.

\subsubsection{\Gls{Rince} finds \Gls{Twofl} inside \Gls{Death}'s cottage}
Inside the main hall of \Gls{Death}'s cottage, a woman takes hold of \Gls{Rince}'s hand, and guides
him into a room, surprised to finally have a living guest. She leads him to a study room, where he
overhears \Gls{Twofl} excitedly explaining the rules of a card game to \Gls{Death} and his horsemen.
She introduces herself as \Gls{Ysabell}, the adopted daughter of \Gls{Death}.

\subsubsection{\Gls{Ysabell} wishes to keep \Gls{Twofl} and \Gls{Rince} in the underworld}
\Gls{Twofl} gives \Gls{Death} a rulebook for his nations's version of Bridge, and is hastily
escorted out by \Gls{Rince}, as the gods are busy arguing the finer details of the card game.
\Gls{Ysabell} stops them from leaving, intending to cut their lifelines with her scythe. The
\Gls{Lugg} stops her by biting down on the blade, allowing \Gls{Rince} to run away with an
unconscious \Gls{Twofl} on his shoulder.

\subsubsection{\Gls{Rince} and \Gls{Twofl} escape the underworld}
The \Gls{Lugg} jumps off the platform holding \Gls{Death}'s house, into the gigantic funnel where
the souls of the dead were being sent. \Gls{Rince} also jumps off, when he notices the two lifelines
falling into the abyss below. \Gls{Death} and his horsemen arrive shortly after, and decide not to
pursue \Gls{Rince}, still being enchanted by the allure of Bridge.

\subsubsection{\Gls{Rince} is dragged once again into the Octavo by the Great Spells}
\Gls{Rince} finds himself inside the Octavo once again, where the Great Spells reveal the true
purpose of his existence. He was to prevent the wizards from uttering all eight Spells at the same
time, by keeping himself out of their clutches for as long as he could. Suddenly, \Gls{Rince}'s
homesickness grips his mind, and drags him back to his body, causing him to wake up from his
spirit-walk inside the chieftain's tent.

\subsubsection{\Gls{Rince} and the party set off for the Smarl river}
\Gls{Rince} eagerly looks at the pictures produced by \Gls{Twofl}'s iconograph, while asking the
painting imp what it saw in the underworld. \Gls{Cohen} and the party set out for Ankh-Morpork,
hoping to ride to the Smarl river and hire a boat to the Circle Sea. \Gls{Cohen} is amused by
\Gls{Twofl}'s star-struck babbling, and lets him recount the greatest tales from his childhood about
the most famous hero of the Disc.

\subsubsection{\Gls{Cohen} makes the party pitch camp for the night}
\Gls{Cohen} suspects the party has entered troll country, as \Gls{Rince} reluctantly sets out to
find herbs and roots for the next meal. \Gls{Cohen} is deeply suspicious of \Gls{Twofl}'s belief
that the wizard is well-versed in botany, as \Gls{Rince} receives some help from a disembodied
voice in the jungle. Hoping that it is not a troll, \Gls{Rince} sees the sun set, and is reminded of
the stories of trolls turning to stone when exposed to sunlight.

\subsubsection{\Gls{Cohen} is shocked to learn about dentures}
Back at camp, \Gls{Cohen} despairs at the loss of his teeth, and of how no one takes him seriously
anymore when they see his gummy smile. In response, \Gls{Twofl} takes out his own teeth, which are
a complete set of dentures, and offers a backup set to \Gls{Cohen}, who is left stunned by the
idea of removable teeth.

\subsubsection{\Gls{Rince} runs into a troll family in the forest}
In the forest, a family of trolls, introduce themselves to \Gls{Rince}, talking about some ancient
prophecy that mentioned him saving the Disc from the red star. He asks them for help making some
soup, with the head of the family, \Gls{Kwartz} being underwhelmed by how their prophecy was
being fulfilled. They return to \Gls{Cohen}'s camp, to find it deserted, with a blood trail and
several hoof-prints riding away from it.

\subsubsection{\Gls{Herrena} captures \Gls{Rince}'s companions}
\Gls{Herrena} leads her mercenaries to a small hill, with the three captives in tow. The \Gls{Lugg}
is also bound and dragged along, as she looks at some troll caves to make camp for the night. She
asks \Gls{Gancia}, the leader of the hired thugs from Ankh-Morpork, to set up camp, while thinking
about the two men and the box that matched \Gls{Trymon}'s description.

\subsection{}
\subsubsection{\Gls{Twofl} tries to ask politely to be released}
\Gls{Kwartz} tells \Gls{Rince} that the fire lit in front of the mountain cave, is unlikely to
deter his grandfather, since he is the mountain itself. He also explains that normal-sized trolls
might keep away from fires because of the adverse effects on their brain. Meanwhile, \Gls{Twofl}
notices the teeth, tonsils and cheeks within \Gls{OldG}'s mouth, and asks \Gls{Herrena} to let them
out.

\subsubsection{\Gls{Herrena} orders her men to open the \Gls{Lugg} by force}
\Gls{Herrena} decides to disregard \Gls{Trymon}'s orders not to touch the chest, and asks
\Gls{Gancia} to force it open. \Gls{Twofl} tries to tell him that the chest opens only when it feels
in the mood, as the rest of the mercenaries notice someone approaching the cave from lower ground.
\Gls{OldG} moves his mouth, leading to everyone inside losing their footing.

\subsubsection{\Gls{Twofl} and the prisoners are set free by the last remaining mercenary}
As \Gls{OldG} tries slowly to stand up, waking from a centuries-long slumber,
\Gls{Herrena} and the mercenaries jump out of its mouth, leaving \Gls{Gancia} and \Gls{Weems} alone
with the prisoners. \Gls{Gancia} gets eaten by the \Gls{Lugg} when he tries to retrieve some gold
inside it, and \Gls{Weems} hastily unties the prisoners before leaping out of the rising cave mouth.

\subsubsection{\Gls{Rince} sees his friends on top of \Gls{OldG}}
With sunrise, the trolls helping \Gls{Rince} as well as \Gls{OldG} all turn to stone, with the
mercenaries having fled the scene. \Gls{Rince} notices \Gls{Twofl} and the \Gls{Lugg} high up in
\Gls{OldG}'s mouth, trying to find a way down to the ground.

\subsubsection{\Gls{Cohen} decides to square off against the \Gls{Lugg}}
\Gls{Cohen} tries to fight the \Gls{Lugg} with his bare hands, rambling about the gold he had seen
in it, and of how it had swallowed \Gls{Gancia}, never to be seen again. \Gls{Twofl} calls off his
pet, while reminiscing about the vanishing shop he had purchased it from when preparing for his
travels. \Gls{Rince} takes him aside, and recommends separating from the others, to improve their
chances of survival.

\subsubsection{\Gls{Herrena} takes \Gls{Rince} and \Gls{Twofl} to the Smarl river}
\Gls{Herrena} ambushes \Gls{Twofl} and \Gls{Rince} along with her men, while warning the \Gls{Lugg}
to stay away from her camp. The \Gls{Lugg} chooses to follow them on their ride to the Smarl river,
triggering paranoia and fear in \Gls{Weems}, much to \Gls{Rince}'s amusement. Eventually, they
reach the river crossing, and strike the gong for the winch-operated ferry. \Gls{Twofl} laughs
through his gag as he recognizes \Gls{Cohen} rowing the ferry.

\subsubsection{\Gls{Herrena} is ambushed by \Gls{Cohen} and the \Gls{Lugg}}
\Gls{Herrena} asks her men to seize the ferryman, growing suspicious of his voice, as \Gls{Cohen}
takes off his robe, and fights the mercenaries. The \Gls{Lugg} terrifies \Gls{Weems} by emerging
from the river, as \Gls{Rince} escapes his captor's grip, and runs into the bushes. A while later,
\Gls{Herrena} is knocked out by a log thrown by \Gls{Bethan}, and the rest of the mercenaries
scatter in the absence of their leader.

\subsubsection{\Gls{Cohen} leads the party to a nearby town}
\Gls{Cohen} and \Gls{Bethan} announce their desire to get married, and lead the group to a nearby
town hoping to find a priest who might officiate the ceremony. \Gls{Rince} tries and fails to warn
\Gls{Cohen} about the age-gap between himself and \Gls{Bethan}, before giving up and tagging along.
In the city, they notice the people evacuating to the mountains, with rumours about the red star's
arrival spreading like wildfire.

\subsubsection{\Gls{Rince} is surrounded by doomsday cultists}
\Gls{Rince} notices huge red stars painted on the temples in the city, as well as the foreheads of
the people left in it. As a doomsday preacher starts his speech, \Gls{Death} appears next to
\Gls{Rince} to bemoan the formation of cults. The mob starts to corner \Gls{Rince}, accusing him of
being a wizard, and revealing that they had killed all of the city's wizards a few days ago.

\subsubsection{\Gls{Rince} is dragged away from the temples by \Gls{Twofl} and \Gls{Bethan}}
The Great Spell within \Gls{Rince}'s mind emerges, to incinerate one of the cultists, leaving him
in a state of shock at casting his first ever spell. \Gls{Bethan} and \Gls{Twofl} try to run off
with \Gls{Rince} into the city's alleyways, only to be trapped in a dead end, with a mob of
cultists closing in. \Gls{Twofl} notices the vanishing shop appear in the brick wall where the
dead end was, causing the cultists to run away.

\subsubsection{\Gls{Cohen} gets new dentures made at a goldsmith's shop}
\Gls{Cohen} is busy with a dwarven goldsmith, trying to get some dentures made from the diamong
tooth that the \Gls{Lugg} had broken when coming out of \Gls{OldG}'s mouth. A group of cultists try
to intimidate the dwarf, claiming that the Red Star might spare the Discworld if they eliminated all
magical races. \Gls{Cohen} deals with the cultists, while the dwarf packs up his valuables and
readies to flee the town.

\subsubsection{\Gls{Cohen} and \Gls{Lackjaw} reunite with the \Gls{Lugg}}
\Gls{Cohen} runs away from more cultists, wondering why they burned all the magical books, instead
of using the pages judiciously as fuel during the winter. Eventually he runs into a dead end with
\Gls{Lackjaw}, the dwarven goldsmith, and finds the \Gls{Lugg} staring intently at a brick wall.
\Gls{Lackjaw} believes \Gls{Cohen} is going insane, as the old man talks to the \Gls{Lugg}, only
to see it run into the brick wall, causing it to collapse.

\subsubsection{\Gls{Rince} wakes up inside the wandering shop}
\Gls{Twofl} is taken by a cigarette holder in the dusty shelves of the wandering shop, as the
\Gls{Shopk} emerges from a counter, to berate him for fiddling with the goods. Meanwhile,
\Gls{Rince} slowly wakes up from his haze, angry that the Great Spell had stopped him from
memorizing other spells, and experiencing the pleasure of exercising magic.

\subsubsection{\Gls{Rince} asks the \Gls{Shopk} to let them out in Ankh-Morpork}
\Gls{Bethan} intimidates the \Gls{Shopk} into getting some water for \Gls{Rince}, as he bemoans the
spread of the red star cult across Discworld. The \Gls{Shopk} prepares to send \Gls{Rince} and his
companions back to Ankh-Morpork, as \Gls{Atuin} fights the influence of the red star, in its swim
through space.

\subsubsection{\Gls{Twofl} listens to the \Gls{Shopk} narrate his sad tale}
At his miniature model of the universe, the \Gls{Shopk} talks to \Gls{Twofl} about insulting a
wizard long ago, and being cursed to wander in the shop forever, traveling the multiverse with no
way to settle down, except to run into the same wizard again and give him what he was in search of.
\Gls{Twofl} commiserates with him, as he thinks back to the different shop from which he had
purchased the \Gls{Lugg}

\subsubsection{\Gls{Twofl} and his party land in Ankh-Morpork}
The \Gls{Shopk} hands \Gls{Twofl} his fancy cigarette holder, as he kicks them out onto an empty
street in Ankh-Morpork, before running back into his shop and vanishing. \Gls{Twofl} tries to
explain to \Gls{Bethan} that \Gls{Rince} not being afraid of the approaching red star must mean it
does not pose the slightest threat, as she grumbles about \Gls{Cohen}. They get swept away by a
procession of cultists marching through the city.

\subsubsection{\Gls{Trymon} initiates the ritual to open the Octavo}
Beneath the Unseen University, \Gls{Trymon} leads the inner council to the lead-lined chamber
holding the Octavo, as they prepare to open it using \Gls{GalderW}'s invocation. Outside its main
gate, the cultists demand that the wizards commit mass suicide, to rid the world of the approaching
red star, as \Gls{Rince} guides his party to a secret entrance in a narrow alleyway.

\subsection{}
\subsubsection{\Gls{Trymon} steals the Octavo from the council of Wizards}
\Gls{Trymon} locks the others in the council within the lead chamber, as he runs out with the
Octavo. He tries to ignore the mind-tricks being played by the book, and marches to his room in the
main level. Meanwhile, \Gls{Rince} hears the main gate being torn down by the cultists, and decides
to head for the safety of the underground cellars.

\subsubsection{\Gls{Rince} manages to rescue the council of Wizards from the Octavo's chamber}
\Gls{Rince} investigates the banging downstairs, and runs into the council of Wizards locked in
the lead-lined chamber underground. He uses the Great Spell's residual power to open the magical
lock, and \Gls{JigladW} comes out bemoaning the theft of the Octavo by \Gls{Trymon}. They run into
the Great Hall, to find the Dungeon Dimensions bleeding into the terrace of the Tower of Art, and
believe that \Gls{Trymon} has started to memorize the Great Spells one by one.

\subsubsection{\Gls{Rince} and \Gls{Twofl} march off into the Tower of Art}
\Gls{Rince} watches \Gls{Twofl} disappear into the tower's base, and decides against his better
judgment to follow him. \Gls{Bethan} scolds the council into helping them, even as they feel their
magic weaken with the closing of the red star. Eventually they catch up to \Gls{Twofl} and
\Gls{Rince} half-way up the spiral staircase, as the empty Octavo falls down on them.

\subsubsection{\Gls{Rince} confronts \Gls{Trymon} at the top of the Tower of Art}
\Gls{Rince} reaches the top of the tower, only to find the council of wizards standing very still
around \Gls{Trymon}, who is unchanged, except for his eyes being hollow pits through which a strange
force seems to be leaking. \Gls{Trymon} declares himself the elected leader of all eight Orders,
and threatens \Gls{Rince} with death, unless he surrenders the Great Spell in his mind.

\subsubsection{\Gls{Rince} defeats \Gls{Trymon} using brute force}
\Gls{Rince} fights \Gls{Trymon} with just his fists and knees, and is transported to an arena in
the Dungeon Dimension, where \Gls{Trymon} presents in his beastly form. \Gls{Rince} gains the upper
hand by tearing open a weak point in the monstrous exoskeleton of \Gls{Trymon}, bringing the two of
them back to Discworld, and resuming time. \Gls{Trymon}'s body falls into the spiral staircase, and
is destroyed, leading to the seven Great Spells in his mind returning to the Octavo.

\subsubsection{\Gls{Cohen} rescues \Gls{Rince} and \Gls{Twofl} at the top of the tower}
\Gls{Cohen} saves \Gls{Rince} from falling down the tower's staircase, and immediately gets to work
cutting the rings out of the stone statues that the council of wizards had been reduced to.
\Gls{Rince} forces the Great Spell to evacuate his head, and return to the Octavo, before starting
the ritual of reading out all eight spells.

\subsubsection{\Gls{Bethan} spots the problem with \Gls{Rince}'s ritual}
An audience of cultists and citizens gather to see \Gls{Rince} pronounce the eight Great Spells,
only for an anticlimactic end to the ritual. \Gls{Bethan} spots a possible mistake in the
pronunciation of the esoteric languages within the book, and asks him to try again. \Gls{Twofl}
accidentally provides the correct pronunciation, making the Octavo buzz with power, and fly off into
the sky.

\subsection{}
\subsubsection{The Octavo is swallowed by the \Gls{Lugg}}
The Octavo wisely chooses to be swallowed by the \Gls{Lugg} as it comes back down from the sky,
after triggering the hatching of baby Discworlds, filling \Gls{Atuin}'s mind with joy at the
completion of its reproductive cycle. The red star and the baby turtles orbiting it drift away,
with \Gls{Twofl} deciding to head back home to the Agateam Empire.

\subsubsection{\Gls{Rince} prepares to re-enroll at the Unseen University}
\Gls{Twofl} gifts the \Gls{Lugg} to \Gls{Rince} after emptying it of all his possessions, and gives
a bag of gold as a wedding gift for \Gls{Cohen} and \Gls{Bethan}. \Gls{Rince} tries to dismiss the
\Gls{Lugg}, before realizing it was incapable of existing without a master. He reluctantly asks it
to follow him into the University, as he prepares to re-enroll, his mind now free from the clutches
of the Great Spell.