\section{Lords and Ladies}


\subsection{}
\subsubsection{\Gls{GWea} talks to a strange woman in a red dress as a child}
Thousands of years ago, a meteor shower brings ferromagnetic metal to the Discworld, and immediately
captures the attention of the dwarves. Fifty years ago, a young \Gls{GWea} runs to an ancient
stonehenge, where she spots a woman in a red dress who appears to be an experienced witch. She
taunts the woman's inability to come out of the stone circle, and talks about how she is going to
grow up to be a powerful witch herself.

\subsubsection{\Gls{GWea} refuses the offer made by the \Gls{QueenF} as a child}
As a child, \Gls{GWea} hesitates when the old witch asks her to step into the stone circle, being
enticed with the promise of great magical power. In the present, the woman in red, looks from a
high vantage point at the same stone circle, as her two companions ask her about the persistent
threat of the witches. \Gls{QueenF} reassures them that the witches are too easy to manipulate now,
and asks to be left alone so that she can deal with them.

\subsubsection{\Gls{Jason} fits new horseshoes for \Gls{Binky}, using the recycled metal from her
    old ones}
\Gls{Jason} recalls his father's words about having to fit new horseshoes for a mysterious customer
who would want absolute secrecy, and insist that he wear a blindfold during the process. On a
cold stormy night, \Gls{Jason} senses the arrival of this customer again (\Gls{Death}), and fits
new horseshoes using the melted remains of the old ones, which he has been warned never to mix with
mundane iron.

\subsubsection{\Gls{Jason} is reminded of his deal with \Gls{Death} made by blacksmiths}
Overcome by curiosity, \Gls{Jason} asks \Gls{Death} what he will see if he takes off the blindfold.
\Gls{Death} warns him not to, and reminds him of the bargain which guarantees that he will remain
the most well-respected blacksmith in Lancre in exchange for his unquestioning obedience. In the
magic-soaked highlands of Lancre, a cornfield is mysteriously distubed by some magical force that
arranges the corn into a ritual circle.

\subsubsection{The three witches return to Lancre after their adventures in Genua}
\Gls{GWea} returns to her cottage from the excursion to Quirm, and realizes that she has been gone
for the whole of winter. She gets to work cleaning up her kitchen, and thinks about her childhood as
she rests for a while. \Gls{Ogg} inspects her daughters-in-law as they continue their household
chores, and looks forward to greeting \Gls{Jason}'s child.

\subsubsection{\Gls{Magrat} talks to \Gls{VerSec} about their coming wedding}
\Gls{Magrat} goes to the palace, hoping to ask \Gls{VerSec} about their engagement, and possible
marriage. She finds him busy planning some agricultural reforms, and is surprised when he lists out
the elaborate arrangements for their wedding ceremony, including a town fair and a special play
written by \Gls{Hwel}. Part of \Gls{Magrat}'s mind is annoyed by the idea that he did not bother to
consult her, while most of her mind is busy imagining life as a queen.

\subsubsection{The three witches notice the crop circles all over Lancre}
\Gls{VerSec} shows \Gls{Magrat} the repurposed royal gardens, where the crops suddenly assemble
themselves into a circle, causing the pollinating bees to flee in terror. The three witches meet
at their usual spot in the meadows north of Lancre town, and talk about the spontaneous crop circles
that seem to be showing up all over the place. \Gls{Magrat} is annoyed when the \Gls{GWea} and
\Gls{Ogg} remain vague about the threat posed by the crop circles. She reminds them that they will
have to give her more respect when she becomes their queen.

\subsubsection{\Gls{GWea} and \Gls{Ogg} decide to investigate the stonehenge}
After \Gls{GWea} goads \Gls{Magrat} into abandoning the new mission in favour of her duties as
queen-to-be, \Gls{Ogg} calls for a quick trip to the old stonehenge in the high mountains, in order
to check on the magic seals. A hunter chases a stag into the stonehenge, and is killed when
some projectile shoots out of it, impaling him to a tree. \Gls{Death} explains that the entity that
just killed him is not extinct, and has just come out of hiding.

\subsubsection{\Gls{Ogg} and \Gls{GWea} investigate the stonehenge}
\Gls{Magrat} prepares to move into Lancre Castle, and gets rid of the worthless trinkets in her
cottage by throwing them into the Lancre river. Meanwhile, in the fairy dimension, the \Gls{QueenF}
receives a report that her pet has stepped into the Disc when the stag ran into the stonehenge's
ritual circle. \Gls{Ogg} and \Gls{GWea} hack their way through the undergrowth surrounding the
henge, and find the corpse of the hunter.

\subsubsection{\Gls{GWea} and \Gls{Ogg} observe the lethal injuries inflicted on the hunter}
At the Unseen University, Archchancellor \Gls{Ridcu} wakes up with a circular bald spot on his head,
and asks the \Gls{Bursar} if he has noticed this happening to any of the other faculty. At the
stonehenge, \Gls{GWea} checks that the slabs still have some magnetic power left, as \Gls{Ogg}
prepares to drag the hunter's corpse back to the village.

\subsubsection{\Gls{Ridcu} decides to attend the wedding of \Gls{VerSec}}
\Gls{Ridcu} receives the invitation to \Gls{VerSec}'s wedding, and is goaded by the rest of his
inner council to take \Gls{Stibb} along with him. He decides to also invite the \Gls{Libra} as a
third guest in order to project a sense of wizardly authority at the wedding, and refuses to listen
to \Gls{Stibb} trying to explain the increasing occurrence of crop circles.

\subsubsection{\Gls{Magrat} gets a glimpse of the royal lifestyle}
The next day, \Gls{Magrat} wakes up in the palace, to see \Gls{Millie}, one of her childhood
acquaintances, arrive with the wedding dress. She is alarmed by the incessant bowing and deferential
language being used to address her, and is flummoxed by the instructions attached to the
multi-layered gown. She slowly realizes that her life as a queen will be highly regimented, and
will involve a strict dress code.

\subsubsection{\Gls{GWea} tries to use her bee swarms to surveil the stonehenge}
\Gls{GWea} decides to perform the difficult task of shifting into a swarm of bees, in order to
see what intelligence they might have gathered about the land surrounding the stonehenge. Meanwhile,
\Gls{Ogg} goes to \Gls{Jason}'s armory, and asks him if anything strange has happened during the
trip to Quirm.

\subsubsection{\Gls{Ogg} tells \Gls{Jason} about the threat within the stonehenge}
\Gls{Jason} tells \Gls{Ogg} that some girls from the neighbouring village led by \Gls{Diaman} had
gone to the stonehenge to try out some elementary witchcraft. \Gls{Ogg} explains that the stonehenge
is made out of meteorite iron, and is meant to act as a fence stopping some other-worldly entities
from invading the Disc. She calls the invaders the Lords and Ladies, and decides to tell \Gls{Jason}
what they truly are, in the safety of the forge.

\subsubsection{\Gls{Ogg} and \Gls{GWea} try to track the escaped elvish creature}
\Gls{Ridcu} struggles to get the price of travel to Lancre down to a manageable amount, as
\Gls{Stibb} hits upon the idea of declaring the \Gls{Libra} a pet. At \Gls{GWea}'s cottage,
\Gls{Ogg} reports the activities of \Gls{Diaman} and her coterie. The unicorn, which escaped the
elven dimension and killed the hunter, watches \Gls{Ogg} and \Gls{GWea} stroll through the dense
vegetation trying to track it down.

\subsubsection{\Gls{Perdita} watches \Gls{Diaman} perform a simple act of witchcraft}
\Gls{Perdita} watches \Gls{Diaman}, fresh from her schooling in Sto Helit, lead the coven of young
girls in their first divination ritual. She makes a show of picking out ornate cards from a deck,
and shows the first one bearing a picture of the moon. \Gls{Ogg} and \Gls{GWea} break into the
cottage, only for \Gls{Diaman} to call them out for being simple tricksters who preyed on the minds
gullible townfolk. \Gls{Ogg} realizes that \Gls{GWea} is up against someone just like her own child
self.

\subsubsection{\Gls{GWea} challenges \Gls{Diaman} to a public face-off in Lancre town}
\Gls{GWea} invites \Gls{Diaman} to a public show of talent the next day at noon, and realizes on her
way out that the young girl is clearly behind the elven crop circles gaining strength. On their
way back, \Gls{Ogg} wonders if \Gls{Diaman} really is strong enough to take them on, with \Gls{GWea}
privately thinking about putting an end to the elven threat before her appointed time of death.

\subsubsection{\Gls{GWea} starts to draft her will, sensing her imminent death}
Back at her cottage, \Gls{GWea} continues drafting her will, with the sense that she only has a
few days left to live. The unicorn from the elven dimension comes to her garden, and she spooks it
with an iron poker. She tells it to run along and inform the \Gls{QueenF} that iron is widespread
in Lancre.

\subsubsection{\Gls{Ogg} receives the details of the challenge from \Gls{Perdita}}
The next day, \Gls{GWea} comes to the town square, and \Gls{Ogg} immediately notices the fact that
she has not had any food or sleep all night. \Gls{GWea} says that she went up to the stonehenge to
try and weaken the portal from the elven dimension, as \Gls{Diaman} makes her grand entrance with
her posse. \Gls{Perdita} tells \Gls{Ogg} that the challenge is a simple staring contest, and is
alarmed when \Gls{Ogg} draws a simple circle using her boots to act as an arena.

\subsubsection{\Gls{Ogg} and \Gls{Magrat} engineer a sneaky win for \Gls{GWea} against \Gls{Diaman}}
\Gls{Ogg} sends one of her sick grandkids to \Gls{Diaman} in an attempt to unnerve them, as
\Gls{Perdita} strolls over to tell her that the challenge is not as simple as she expects.
\Gls{Magrat} runs to the town square in her royal outfit as soon as she hears news of the duel from
\Gls{Shawn}, and finds \Gls{Ogg} outside the huddle. \Gls{Ogg} and \Gls{Magrat} devise a way to end
the contest by sending a toddler into the circle, causing \Gls{GWea} to instinctively come to his
aid.

\subsubsection{\Gls{Ogg} mentions the wedding preparations to \Gls{Magrat}}
\Gls{Ogg} tells \Gls{Magrat} not to reveal how she enticed her grandson to interfere with the
contest, and remains vague about how \Gls{VerSec} had intimate knowledge of their trip to Quirm.
\Gls{Magrat} is exasperated by the play that is supposedly the highlight of their wedding, which is
to happen on Midsummer's Eve.

\subsection{}
\subsubsection{\Gls{Jason} and his troupe try to work out how to perform \Gls{Hwel}'s play}
\Gls{Jason} studies \Gls{Hwel}'s script for the wedding play, which features his friend \Gls{BCart}
as the Queen of the Fairies. The group try to make sense of the elaborate stage directions, and
wonder why they can't simply do the usual folk dances. On the slow and boring journey to Lancre,
\Gls{Ridcu} starts talking about his summer vacation in the mountain town, spent pursuing some girl
who turned him down for other life goals (\Gls{GWea} ?).

\subsubsection{\Gls{Ridcu} invites \Gls{Casan} on board his carriage}
\Gls{Ridcu} recalls a similar occurrence of crop circles all those years ago at Lancre, just as
their carriage is waylaid by some a single dwarf. He turns out to be \Gls{Casan}, who has been
waylaid himself on the way to the mountains. \Gls{Ridcu} invites him on their carriage out of sheer
boredom, and is happy to discover that \Gls{Casan} is a keen gambler.

\subsubsection{\Gls{Stibb} attempts an explanation of his multiverse hypothesis}
\Gls{Stibb} tries to explain his theory of parallel universes by stating that \Gls{Ridcu} probably
did marry the girl in Lancre in one of the other timelines where different decisions were made.
Meanwhile, the elven kingdom, which is a parasite universe trying to use the crop circles to keep
going.

\subsubsection{\Gls{Magrat} walks through the castle, and meets some of the senior staff}
\Gls{Magrat} sets about planning the remodeling of Lancre castle, and wonders why the remote
kingdom needs such a well-equipped fortification. She runs into the falconer \Gls{Hodges} in the
newly planted garden maze, and then goes to the Royal Beekeeper \Gls{Brooks} for a cup of tea.
Meanwhile, the unicorn from the elven dimension starts to go mad from the unfamiliar landscape and
disorientation caused by the passage of time.

\subsubsection{\Gls{GWea} feels false memories forming in her mind}
\Gls{Stibb} is able to detect some sort of alignment in the multiverse using his fine-tuned mind,
as the crop circles start to signal the opening of a substantial portal between worlds. Meanwhile,
\Gls{GWea} starts to have false memories show up in her head, of a life she never lived. She seals
a box full of letters after inspecting them (young \Gls{Ridcu} ?) as \Gls{Ogg} shows up at her
cottage with the young girls in tow.

\subsubsection{\Gls{GWea} sends away the little girls who want to be witches}
\Gls{GWea} asks the girls to return to \Gls{Diaman} after showing them how witchcraft is mostly
about practicality and simple psychology. \Gls{Ogg} is surprised to learn that \Gls{GWea} was not
chosen by a senior witch for training, and was largely self-taught. \Gls{Diaman} goes to the
stonehenge at midnight, unable to let go of the humiliation she suffered at the town square.
Meanwhile, \Gls{Ogg} settles down to sleep, recalling the stories of the elven invasion from
thousands of years ago.

\subsubsection{\Gls{GWea} tries to dissuage \Gls{Diaman} from accepting the offer made by the
    \Gls{QueenF}}
\Gls{GWea} waits for \Gls{Diaman} at the stonehenge, and correctly guesses that the little girl has
been offered the same deal that she was by the \Gls{QueenF}. When \Gls{Diaman} calls out the elves
by name, \Gls{GWea} is forced to slap her into silence, for fear of attracting the attention of the
elves, now trapped in their own dimension. \Gls{Diaman} rejects \Gls{GWea}'s advice to run away
from Lancre, and goes straight into the stonehenge portal.

\subsubsection{\Gls{GWea} and \Gls{Diaman} escape from the elven world with some injuries}
\Gls{GWea} is forced to follow \Gls{Diaman} into the elven world, where the \Gls{QueenF} is waiting
for them with some warriors. She asks for the two intruders to be killed, and \Gls{GWea} manages
to make a distraction that allows then to try and escape back through the portal. Just as \Gls{GWea}
seems overwhelmed, \Gls{Ogg} rescues her, and brings \Gls{Diaman} back to the Disc, noticing that
the girl has taken a poisoned arrow to her shoulder.

\subsubsection{\Gls{Ogg} and \Gls{GWea} are desperate to cure the poison in \Gls{Diaman}}
\Gls{Ogg} notices one of the elves has made it to the Disc, and decides to imprison him in the
palace dungeons, with the iron bars keeping him contained. Meanwhile, \Gls{GWea} thinks about how
they might cure the poison in \Gls{Diaman}'s body, and goes with \Gls{Ogg} to the castle, where
\Gls{Magrat} is having dinner with the \Gls{VerSec}.

\subsubsection{\Gls{Magrat} puts the medical skills inherited from \Gls{Whemper} to use}
\Gls{Magrat} takes a look at the sleeping form of \Gls{Diaman}, and is shocked by how politely
\Gls{GWea} asks her to think about a cure. \Gls{Magrat} asks \Gls{Shawn} to fetch the books from her
cottage, and sets about cleaning the wound with some mold and boiling water. \Gls{GWea} asks
\Gls{VerSec} to come down to the dungeons and take a look at the imprisoned elf.

\subsubsection{\Gls{Ridcu} turns the tables on the bandits ready to waylay him}
\Gls{Ridcu} turns the chief bandit into a pumpkin when their carriage gets waylaid, and has the
\Gls{Libra} go around extorting the rest of the gang for all their accumulated cash. He quickly
gets away with the carriage, and leaves the coachman behind along with \Gls{Casan}. Meanwhile,
\Gls{GWea} shows \Gls{VerSec} the elf, and points out how they can make themselves appear beautiful
to the native people of whatever world they invade.

\subsubsection{\Gls{GWea} becomes her alternate self for a short while in the dungeon}
For a moment, \Gls{GWea} becomes an alternate version of herself, and asks \Gls{VerSec} if her
children are safe. She snaps back to her true self after a few seconds, and plays off the
nonsensical question as sleep deprivation. \Gls{VerSec} is pleased to learn that the little girls
are not performing their ritual at the stonehenge any longer, and that the portal is unlikely to
be opened again.

\subsubsection{\Gls{GWea} and \Gls{Ogg} leave \Gls{Diaman} in \Gls{Magrat}'s care}
\Gls{GWea} asks \Gls{Magrat} to keep \Gls{Diaman} stable and under constant supervision.
\Gls{Magrat} reminds her that wedding guests will soon start arriving at the castle, and decides to
put \Gls{Diaman} in one of the guest bedrooms. \Gls{GWea} and \Gls{Ogg} leave the castle, while
remaining aware of the threat of \Gls{QueenF}, who can still penetrate the minds of other humans in
Lancre in order to entice them.

\subsubsection{\Gls{Jason}'s troupe of actors get drunk at the stonehenge and rant about village
    life}
\Gls{Jason} listens to his crew arguing about the difficult dialogue in the play, as they finish
one of their rehearsals in the forest, hoping to stay away from curious townsfolk. \Gls{Jason}
tries to dissuade the troupe from practicing next to the stonehenge, but is outvoted. After their
rehearsal, the troupe get drunk, and start to talk about their lives, inserting false memories into
the conversation with full conviction.

\subsubsection{\Gls{Jason} and his troupe accidentally get drunk and fall asleep at the stonehenge}
The troupe fall into a drunken stupor, even as \Gls{Jason} smells snow in midsummer, and wonders if
some sort of magic is transporting them to an alternate dimension. On the night before the wedding,
\Gls{Magrat} lays in bed thinking about how much more she was attracted to \Gls{VerSec} when he was
still a court jester. Meanwhile, \Gls{GWea} casts her mind out into the forest, and fails to notice
the men lying fast asleep at the stonehenge, since no animals dare tread near it.

\subsection{}
\subsubsection{The \Gls{Libra} deals with the troll guarding the entrance to Lancre bridge}
The \Gls{Libra} throws the official toll-troll off the bridge spanning the Lancre gorge, when he
makes the mistake of calling the orangutan a monkey. \Gls{Ridcu} fondly remembers his boyhood, when
the girl of his dreams had almost said yes to him while standing on the same bridge. \Gls{Stibb}
spots the troll wading to the shore with its club, and suggests traveling full speed ahead.

\subsubsection{\Gls{VerSec} realizes that his book request from Ankh-Morpork has been misunderstood}
Once in the city, \Gls{Shawn} comes by to pick up the mail bag from \Gls{Ridcu}, and is surprised
when the old man claims to know his late father. \Gls{VerSec} hurries to the coach, in order to
grab the book \Gls{Magrat} had ordered on marital life, and is surprised when it turns out to be a
book on martial arts. He immediately declares it a gift for \Gls{Shawn}, who is the chief of the
palace guard.

\subsubsection{\Gls{Jason} and his boys return from their night of drinking at the stonehenge}
\Gls{Jason} and his troupe wake up in the morning with agonizing hangovers, and manage to walk back
home with great effort. \Gls{Jason} is annoyed by his inability to remember the details of his
dreams at night, even though he can remember the fact that he spent the whole night dreaming.
Meanwhile, \Gls{GWea} returns home from her nightly wandering in the minds of forest animals, and
wonders why she now has false memories of being a married woman with children.

\subsubsection{\Gls{Magrat} does not believe in the threat of the elves}
\Gls{Magrat} wakes up on the day of her wedding, and feels unsure about becoming a queen. She
decides to go out incognito one last time in order to survey the festivities being set up in the
town square. As she walks past the room where \Gls{Diaman} is recovering, she asks \Gls{Shawn} why
there are iron bars placed around the little girl, who is still comatose. \Gls{Shawn} conveys the
instructions from \Gls{Ogg} regarding the iron and its ability to ward off elven mind-control, and
\Gls{Magrat} dismisses it as superstition.

\subsubsection{\Gls{Magrat} goes through \Gls{VerSec}'s possessions out of morbid curiosity}
\Gls{Magrat} goes to the royal bedroom, but finds it empty. She decides to investigate the room
anyway, and happens to find \Gls{VerSec}'s simple straw bed next to the unused royal mattress, and
looks inside the dressing table until she finds a piece of crumpled paper. \Gls{GWea} and \Gls{Ogg}
arrive at the palace courtyard, just as it starts to fill up with minor aristocrats from the
neighbouring kingdoms.

\subsubsection{\Gls{Ridcu} meets \Gls{GWea} at the Lancre castle}
\Gls{Casan} accosts \Gls{Ogg} and successfully charms her into a private dinner after the day's
festivities have concluded. \Gls{GWea} tries to keep \Gls{Ogg} focused on their mission for the
day, and points out the absence of \Gls{Magrat} when she spots the king mingling with the guests.
\Gls{Ridcu} greets \Gls{GWea} and teleports the two of them to the Lancre bridge, where he starts to
reminisce about their childhood.

\subsubsection{\Gls{GWea} understands the true meaning of the false memories in her mind}
\Gls{GWea} realizes that the false memories have simply been the lived experience of her alternate
selves, when she heares \Gls{Ridcu} describe the theory of multiverses proposed by \Gls{Stibb}. She
decides to hurry back to the castle, while reminding \Gls{Ridcu} that their life together might not
have been automatically happy. The elven unicorn bursts onto the road to obstruct their path back
to the town, as \Gls{GWea} vaguely senses the minds of her parallel selves.

\subsubsection{\Gls{Magrat} is angry at \Gls{VerSec} for some mysterious reason}
At the palace, \Gls{VerSec} waits anxiously outside \Gls{Magrat}'s room waiting for her to come to
the festivities. \Gls{Ogg} realizes that the bride is nervous about her future, and asks
\Gls{VerSec} to go on ahead without her. \Gls{Ogg} fails to convince \Gls{Magrat} to come out, and
decides to step into Lancre town. She is accosted once again by \Gls{Casan}, who takes her to the
fancy dinner he has arranged at one of the expensive taverns in town.

\subsubsection{The \Gls{Libra} notices some strange phenomena at the hill with the stonehenge}
\Gls{GWea} and \Gls{Ridcu} walk backward to the bridge, and jump off in an attempt to avoid the
unicorn. As the play gets underway, the \Gls{Libra} notices everyone else in the audience enter some
sort of trance, as the hill bearing the stonehenge begins to snow. Meanwhile, \Gls{Magrat} refuses
to forgive \Gls{Ogg} and \Gls{GWea} for their collusion with \Gls{VerSec} regarding the wedding
preparations.

\subsubsection{\Gls{Ogg} and \Gls{Casan} have their fancy dinner}
\Gls{Magrat} tries on the wedding dress in her room, and is enchanted by how well it fits her. She
vacillates about her plan to run away from Lancre, and wonders notices the unnatural cold creeping
into the palace. Meanwhile, \Gls{Casan} enjoys the dinner with \Gls{Ogg}, transfixed by her complete
disregard for the rules of fine dining.

\subsubsection{\Gls{GWea} and \Gls{Ridcu} evade the elven unicorn possessed by the \Gls{QueenF}}
\Gls{Brooks} notices his bees behaving very defensively, as he skips the wedding party in favour of
a wasp nest that he is cleaning out. \Gls{Ridcu} joins \Gls{GWea} downriver after escaping from the
unicorn, and takes off his hat to reveal the static electricity machine designed by \Gls{Stibb} as a
cure for his baldness. \Gls{Diaman} wakes up, now merely a spectator inside her own mind which has
been possessed by an elven power.

\subsubsection{\Gls{Shawn} finds \Gls{Diaman} in the dungeons having freed the captive elf}
\Gls{Shawn} goes to the dungeons on a hunch, and finds the door to the elf's cell open. He spots
\Gls{Diaman} and asks her to stand down. When she asks him to take off his iron armour and helmet,
he recalls \Gls{Ogg}'s words about the importance of iron, and runs back to the main hall.
Meanwhile, \Gls{GWea} gets lost in the forest leading to Lancre town, as \Gls{Ridcu} struggles to
keep up.

\subsubsection{\Gls{Magrat} finally learns about the elf in the dungeons}
\Gls{Magrat} hears the enchanting song of the elves, and is drawn to the dungeon entrance. She
runs into \Gls{Shawn} on his way out, and listens to him talk about the return of the elves. She
tries to shake him back to his senses, but realizes that this is yet another secret that \Gls{Ogg}
and \Gls{GWea} have kept from her. \Gls{Shawn} wonders why the guests haven't returned from the
festival yet, and decides to sneak out of the castle's back gate to investigate.

\subsubsection{\Gls{Magrat} runs from the elves sneaking into the castle}
\Gls{Magrat} realizes that she is alone in the castle, just as the elf tries to break into her room.
She decides to hide under the bed long enough for the elf to look for her in the latrine pit. She
hits it on the back of the head with a chair, and pushes it into the deep pit, full of the castle's
human excrement. \Gls{Magrat} decides to run away, and comes across a portrait of one of the
barbarian queens who founded Lancre.

\subsubsection{\Gls{Magrat} locks herself inside one of the castle's rooms}
Near the kitchens, \Gls{Magrat} spots \Gls{Greebo} and grabs hold of him on her way past. She senses
an elf ambush ahead when \Gls{Greebo} starts tensing up, and stabs through a doorway with a broken
chair leg, stabbing the waiting elf in the neck. She continues running, until she barricades herself
into a dark room with a set of candles in the shelves.

\subsubsection{\Gls{GWea} gives herself up to the \Gls{QueenF} in order to ensure \Gls{Ridcu}'s
    escape}
\Gls{GWea} realizes that the \Gls{QueenF} is forcing her to walk around in circles, as \Gls{Ridcu}
starts to fondly recall his childhood. She senses a few elves preparing to ambush them, and asks
\Gls{Ridcu} to use the last of his powers to teleport himself to the castle. Once he leaves, she
makes a show of surrendering to the elves, confident that they will want to keep her alive.

\subsubsection{\Gls{Magrat} hears the elves drag \Gls{Shawn} to the door as a bargaining chip}
\Gls{Magrat} explores the dark room, until she finds the armor of the old barbarian queen in the
midst of the rusted equipment. \Gls{Greebo} watches the spirit of the queen come over \Gls{Magrat}
as she dons the armor, just as \Gls{Shawn} is dragged to the armory's door by the elves. He asks
her to come out of the store-room, in order to stop the slow torture.

\subsubsection{\Gls{Magrat} takes out the elves after wearing the barbarian queen's armor}
\Gls{Magrat} comes out wearing her wedding dress, after taking out one of the elves with a crossbow
bolt through the keyhole. \Gls{Shawn} notices the armor beneath the \Gls{Magrat}'s dress, as she
takes out two of the other three elves alongside \Gls{Greebo}. She locks the sole remaining elf in
the armory surrounded by plenty of iron, and takes \Gls{Shawn} to the kitchen for some first aid.

\subsubsection{\Gls{Magrat} heads into town to investigate the elven invasion}
After \Gls{Magrat} stitches up \Gls{Diaman}'s stab wound in the kitchen, she hands some loaded
crossbows to \Gls{Shawn} and tells him to stand watch. She decides to head out into the city after
placating an elven warhorse and mounting it, with \Gls{Shawn} dumbfounded by her sudden courage.
Once at the town, she notices someone hastily shutting their doors after pinning a horseshoe to it.

\subsubsection{\Gls{Magrat} learns about the elves invading the play at the stonehenge}
\Gls{Magrat} convinces \Gls{Weaver} to let her in, and finds the entire famliy cowering under the
table, afraid of the terrible dark night and unnatural cold enveloping the town. She learns that
the elves invaded the play as it was happening near the stonehenge, and the crowd scattered out of
fear. She decides to go to the stonehenge in search of \Gls{VerSec}, and hopes the two other
witches are trying to beat back the elves.

\subsubsection{\Gls{Ogg} and \Gls{Casan} try to find some help}
\Gls{Jason} and the rest of his crew hide out in the bushes near the stonehenge, more afraid of
\Gls{GWea} than the elves. They try to dance and sing their way back to the village, as a group of
elves surround them, too distracted by the music to attack. Meanwhile, \Gls{Ogg} drags \Gls{Casan}
out of the tavern's attic, after the elves empty all the food and drink in the storerooms. She
decides to head back to her cottage to retrieve her broomstick, so that she can track down
\Gls{GWea}.

\subsubsection{\Gls{Ogg} and \Gls{Casan} fight off some elves as they travel to the burial mounds}
\Gls{Ogg} gets her broomstick from her cottage, after finding it trashed by the elves. She makes a
brief stop at \Gls{Jason}'s forge to pick up a crowbar, as \Gls{Casan} clings on desperately to the
broomstick, trying to deal with his fear of heights. They fend off some elves flying on their own
broomsticks, and reach the ancestral burial mounds. \Gls{Ogg} believes that the elves will not
follow them onto the ancestral land, out of some ancient fear.

\subsubsection{\Gls{Ogg} takes \Gls{Casan} to meet the \Gls{KingEl}}
\Gls{Ogg} asks \Gls{Casan} to open the entrance to the caves underneath the burial mound, and tells
him that the elves have a second home underneath that is never talked about. Once inside the cave
network, they walk past an army put to sleep by some wizard's enchantment, and reach the abode of
the \Gls{KingEl}. She asks him to sort out the \Gls{QueenF}, and reminds him that the elves will
never be able to rule the Disc again because of iron-age advancements.

\subsubsection{\Gls{Magrat} meets the \Gls{Libra} on the path to the stonehenge}
\Gls{Ogg} explains to \Gls{Casan} that the \Gls{KingEl} is simply waiting for the world to forget
about iron unlike the \Gls{QueenF}, who is more belligerent. Meanwhile, \Gls{Magrat}'s ride up the
forest path to the stonehenge is interrupted by some elves, who get knocked out by the \Gls{Libra}
when they turn their attention to her.

\subsubsection{\Gls{Magrat} listens to \Gls{Stibb} talk about the start of the elven invasion}
The \Gls{Libra} leads her off the road to \Gls{Stibb} and the \Gls{Bursar}, who are lightly injured
and propped up against some trees. She introduces herself as a minor noble come to Lancre as a
wedding guest, and learns from \Gls{Stibb} that the play opened up the portal to the elven realm,
allowing them to invade the festival.

\subsubsection{\Gls{Ogg} and \Gls{Casan} return to the castle}
\Gls{Magrat} decides to go on ahead to the stonehenge by herself, and \Gls{Stibb} feels obliged to
back her up after some time spent deliberating with the \Gls{Libra}. Meanwhile, \Gls{Ridcu} goes
over to \Gls{Shawn} at the castle's main hall after recovering his strength, while \Gls{Ogg} strolls
in from the terrace with \Gls{Casan}. She asks \Gls{Ogg} to put archers on the roof to watch for
elves trying to land on the roof, and learns that \Gls{Magrat} has gone out to face them on her own.

\subsubsection{\Gls{Magrat} reaches the stonehenge in pursuit of \Gls{VerSec}}
\Gls{Ogg} threatens the citizens seeking shelter in the castle with her wrath, unless they play
along with \Gls{Shawn}'s plan to organize a sortie into the forest. Meanwhile, \Gls{Magrat} makes
it to the hill with the stonehenge, and notices the elven encampment at the edge of the ritual
circle of stones.

\subsubsection{\Gls{GWea} is held captive by the \Gls{QueenF} in her makeshift royal tent}
\Gls{GWea} is questioned by the \Gls{QueenF}, and reminds her that humans have had many centuries
now to make the land their own. The \Gls{QueenF} remains confident that she can control
\Gls{VerSec}'s mind for long enough to marry him, and stake her claim over the Kingdom according to
some ancient rules of magic.

\subsubsection{The \Gls{QueenF} talks to \Gls{GWea} about her alternate lives}
The \Gls{QueenF} senses \Gls{Magrat} approaching, and tells \Gls{GWea} that the young woman seems
out of her depth with the weapons and armor that she can barely use. She then taunts \Gls{GWea} with
memories of her alternate selves that might have settled down with a man instead of remaining
celibate. \Gls{Magrat} receives help from the \Gls{Libra} and \Gls{Stibb}, who hide in the trees to
deal with elven archers taking aim at her.

\subsubsection{\Gls{Jason} and his army reach the elven encampment}
\Gls{Magrat}'s valiant last stand is interrupted by \Gls{Jason} and his makeshift army, who try to
assault the elves. The \Gls{QueenF} turns up her glamour, and gets the humans to back off, standing
transfixed by her beauty and dropping the weapons in their hands at the slightest suggestion.
\Gls{GWea} manages to taunt the \Gls{QueenF} by reminding her of the slow but inexorable advancement
of human technology, moves the \Gls{QueenF} to blind fury.

\subsubsection{\Gls{GWea} triggers a great swarm of bees with her mind-control}
\Gls{GWea} unleashes a wave of mind control that immobilizes the other elves, prompting the
\Gls{QueenF} to hit back with an even greater wave that kills most small animals for miles around.
The bees of Lancre pick up the disturbance, and start to swarm towards the stonehenge, as \Gls{GWea}
drops to her knees with a heavy migraine.

\subsubsection{\Gls{GWea} dies while empowering \Gls{Magrat} in the fight against the elves}
\Gls{GWea} shields \Gls{Magrat} temporarily from the mind-control of the \Gls{QueenF}, allowing her
to fight back. \Gls{Magrat} has the \Gls{QueenF} pinned under her with the rusty battleaxe ready
to strike, as the \Gls{KingEl} walks in to whisper some quiet words to his wife. After the people
come to their senses at dawn, \Gls{Ridcu} rushes to \Gls{GWea}'s body, and confirms her death.

\subsubsection{\Gls{GWea} leaves a note for \Gls{Ogg} asking to check back in with her corpse}
At \Gls{GWea}'s cottage, \Gls{Ogg} reads the letter addressed to her in the box containing her
will, and spots the piece of card inside that she uses while traveling through animal minds.
\Gls{Ogg} rushes back to the castle, believing that \Gls{GWea} was not fully confident she would die
on Midsummer's day.

\subsubsection{\Gls{GWea} returns to her body after inhabiting the mind of a bee swarm}
\Gls{Ogg} opens the castle windows, allowing the swarm of bees to descend on \Gls{Ogg}'s corpse,
which comes back to life when she jumps back into her own brain from that of the swarm. \Gls{Ogg}
is impressed by the feat of advanced witchcraft, as \Gls{GWea} asks about the wedding. \Gls{Magrat}
states that the kitchens is in a state of ruin, and most of the guests have run away, including
the priest.

\subsubsection{\Gls{GWea} controls the elven unicorn with her mind}
\Gls{Magrat} tries to plead with the head cook for an impromptu feast, while \Gls{GWea} asks
\Gls{Ridcu} to officiate the wedding in his capacity as senior wizard. \Gls{Ogg} and \Gls{GWea}
return from the wedding, and are waylaid in the forest path by the elven unicorn. \Gls{GWea} meets
its charge head on, and uses her mind-control to stop its charge. She controls it using a noose
made out of a single strand of hair, and leads it into town.

\subsubsection{\Gls{GWea} talks to \Gls{Ridcu} about their alternate lives}
\Gls{GWea} stands by her decision not to reveal the fact that the barbarian queen was a fiction made
up by one of the old kings of Lancre to give the kingdom some historical flair. She then takes
\Gls{Ridcu} to the bridge, and reminds him that in some alternate universe, the two of them did
indeed lead a happy life together.