\section{Making Money}


\subsection{}
\subsubsection{\Gls{Adora} leases a worthless piece of land from the Dwarf King}
\Gls{Adora} leases some land from \Gls{RhysR}, the Low King of the Dwarves for a substantial sum of
money. The dwarves are suspicious of her readiness, in spite of surveys reporting nothing of value
underground. She signs a contract stating that any dwarf artifacts, or objects of power are subject
to confiscation by the Dwarf King, even though no such object is expected to be found.

\subsubsection{A thief is found out in the process of sneaking into the Post Office}
A thief gets stuck climbing the wall of the Post Office Headquarters, and shouts to the carriage
drivers for help. They lower a rope from the roof, only to hear him use it to break into
\Gls{Moist}'s private room. The drivers run down in search of the thief, and are surprised to see
\Gls{Moist} stumble out of his room, offering a bounty for whoever apprehends the intruder.

\subsubsection{\Gls{Moist} reads the morning Times, with his face on the front page}
\Gls{Moist} is relieved that the drivers do not catch on to him being the intruder, and shuts the
door in an attempt to clean up the broken glass. \Gls{Gladys} arrives with the morning Times, and
he is dismayed to see his face on the front page, marking the grand reopening of the Post Office
alongside \Gls{Vetina}. Underneath the main story, he reads about another bank going under, and
the scheduled hanging of stamp forging maestro \Gls{Owls}.

\subsubsection{\Gls{Vetina} asks \Gls{Moist} nicely to take up a new mission}
\Gls{Vetina} summons \Gls{Moist} to the palace, and offers him a new job. \Gls{Moist} tries to say
that being Postmaster General is difficult enough, and chooses to walk out without further argument.
After he leaves, \Gls{Drumk} places his file on \Gls{Vetina}'s table, reminding him that a death
warrant was still out on his con-man persona, which could be used to force his co-operation.
\Gls{Vetina} chooses to use \Gls{Moist}'s psychology against him, and asks \Gls{Drumk} to bury the
file again.

\subsubsection{\Gls{Moist} is forced by his own boredom to entertain \Gls{Vetina}'s offer}
\Gls{Moist} thinks about how the Post Office has become a well-oiled machine, leaving him so
deprived of excitement that he resorted to scaling his own walls at night. \Gls{Gladys} informs
\Gls{Moist} that \Gls{Vetina}'s carriage is waiting outside the Post Office, and he tries his best
to ignore it while going about his morning routine. Finally, when the boredom of logistics and
administration overwhelms him, he steps out onto the street, and climbs into \Gls{Vetina}'s
carriage.

\subsubsection{\Gls{Vetina} explains the new job to \Gls{Moist}}
\Gls{Vetina} explains to \Gls{Moist} that the Post Office is now so trustworthy compared to the
city's banks, that the postage stamps have superseded minted currency as a store of value. He offers
\Gls{Moist} the job of managing the Royal Mint, as well as a position on the Royal Bank of
Ankh-Morpork, in order to bring it out of the gold reserve system into the modern world.

\subsubsection{\Gls{Vetina} takes \Gls{Moist} to the Royal Bank of Ankh-Morpork}
\Gls{Vetina} talks about the previous chairman of the Bank, who had died in his private apartment
with his mistress by his side. \Gls{Moist} learns that he had regularly had his mistress come to
his room, and that his wife Mrs \Gls{Lavish} insisted on avoiding the title of Lady. The two of them
walk into the bank, followed by \Gls{Drumk}, and \Gls{Vetina} tells \Gls{Moist} that no one but
the current manager of the Bank is aware of his offer.

\subsubsection{\Gls{Bent} is asked to show \Gls{Moist} around the Royal Bank}
\Gls{Vetina} guesses that \Gls{Moist} is covering up the fact that he misses \Gls{Adora}, and
promises him that whatever golem-rights issue she is out pursuing on dwarf lands must be very
important. \Gls{Bent}, the chief cashier, and a firm believer in the gold standard, greets
\Gls{Moist}, and congratulates him on the success of his penny stamps. \Gls{Bent} starts the tour of
the bank, with adjusting the main clock which seems to be running a few seconds slow every day.

\subsubsection{\Gls{Shady} explains the coin minting process to \Gls{Moist}}
\Gls{Bent} shows the gold vault to \Gls{Moist}, and expresses his disgust for the existing system
of coins, which represent a promise by the Royal Bank to be exchanged for a dollar's worth of gold.
\Gls{Moist} is then taken to the Royal Mint, where \Gls{Bent} introduces the hereditary foreman,
\Gls{Shady}. \Gls{Shady} talks about the extreme cost of minting the gold-alloy and silver-alloy
coins, and surprises \Gls{Moist} by revealing that the lower denominations are made by hand at the
homes of families, who have traditionally been performing the role for generations.

\subsubsection{\Gls{Moist} argues once again with \Gls{Bent} about the gold standard}
\Gls{Moist} asks about the security arrangements at the Mint, and \Gls{Bent} tells him that the
workers are probably pilfering a small fraction of what they manufacture daily. \Gls{Moist} asks
about the impracticality of coins costing more to mint than their face value, and is annoyed by
\Gls{Bent} bringing up the gold standard again.

\subsubsection{\Gls{Moist} meets \Gls{Lavish}, the current chairman of the Royal Bank}
\Gls{Moist} is taken to the office of the Royal Bank's chairman, where \Gls{Bent} knocks a secret
code on the door to enter. He notices an old woman disarm the crossbows pointed at the door, and
realizes that she is \Gls{Lavish}, and has been given the seat after her husband's death. Her pet
dog jumps into his lap eagerly, and she introduces him as \Gls{Fuss}.

\subsubsection{\Gls{Lavish} explains the crisis faced by the banking system}
\Gls{Lavish} recognizes \Gls{Moist} as a conman immediately, and tells him that he reminds her a lot
of her late husband. \Gls{Lavish} then talks about her own past as one of her husband's early
mistresses, and reminds him that trust in the banking system was most of its value to the city.
She tells him that bad decisions by her husband have led to a general loss of faith in the Bank,
with most people preferring to keep their money stashed at home.

\subsubsection{\Gls{Moist} learns that \Gls{Lavish} owns a majority of shares in the Royal Bank}
\Gls{Lavish} explains that her husband left her fifty percent of the shares to the bank when he
died, and the one percent owned by \Gls{Fuss} gave her the right to succeed him as chairman. Her
nurse comes in to stop her from consuming more alcohol, as \Gls{Bent} returns with \Gls{Fuss}.
\Gls{Lavish} asks \Gls{Bent} to take \Gls{Moist} to see \Gls{Hubert}, in order to gain a better
understanding of the banking system.

\subsubsection{\Gls{Moist} is given a tour of \Gls{Bent}'s arithmetic room}
\Gls{Moist} is taken to the counting room of the bank, where \Gls{Bent} oversees the human
calculators responsible for all the arithmetic performed at the bank. He religiously believes in
banning all mechanical devices for arithmetic, and prides himself on his ability to observe anyone
in the room from his revolving desk on the central dais.

\subsubsection{\Gls{Moist} sees \Gls{Hubert} show off his simulation machine}
\Gls{Bent} then takes \Gls{Moist} to the main cellar, which was designed by an ancient king in the
pattern of the temples of that time. \Gls{Moist} sees \Gls{Hubert}, a scientist fussing over an
elaborate glass contraption, meant to simulate the economy using the flow of colored water in its
tubes and vessels. \Gls{Hubert} shows a forecast of the current crisis, and \Gls{Moist} realizes
that an economic slowdown will result eventually in the collapse of businesses and large-scale
unemployment.

\subsubsection{\Gls{Bent} talks about the possible attempt to have \Gls{Lavish} institutionalized}
\Gls{Moist} correctly guesses that \Gls{Hubert} is related to \Gls{Lavish}, and \Gls{Bent} reveals
that he is her nephew. \Gls{Bent} shows off his prowess in arithmetic, and warns \Gls{Moist} about
the Lavish family, who are not used to losing control of their wealth. He speculates that
\Gls{Lavish} is being set up to be declared insane by her family, in order to wrest control of the
bank.

\subsection{}
\subsubsection{A conman is spotted running a color photograph scam at an amusement park}
A strange man in black runs a scam at a rural amusement park, promising families a color iconograph
to be posted to their address in exchange for a small advance payment. Some Watchmen posted nearby
take an interest in him when he carelessly tosses his camera in a deserted alley, and reads the
newspaper in his jacket.

\subsubsection{\Gls{Moist} tries to find out about the Lavishes operating in the city}
\Gls{Moist} returns to the Post Office, and looks up the Lavish family tree. He spots \Gls{Lavish}'s
stepson \Gls{Cosmo} and stepdaughter \Gls{Pucci} as the major players remaining in Ankh-Morpork,
with the rest having been sued out of existence, or migrated to far away cities. He reads a
semaphore message from \Gls{Adora} saying that she is coming back soon, and notices a report from
\Gls{Stanley} talking about the roaring success of the high-denomination stamps.

\subsubsection{\Gls{Vetina} makes a show of getting \Gls{Moist} to reaffirm his intention to
    remain at the Post Office}
\Gls{Vetina} comes to the Post Office with \Gls{Drumk}, and asks \Gls{Moist} about his opinion on
the Lavishes. \Gls{Moist} wishes to stay as far away from them as possible, and points out his
complete lack of financial knowledge. \Gls{Vetina} dictates a memorandum for him to sign, stating
his intention to remain the Postmaster General, and leaves promptly to hand it to the Times.

\subsubsection{\Gls{Lavish} dies at night, in her private chamber at the Royal Bank}
\Gls{Death} comes for \Gls{Lavish} at night, and she tells him that she finalized her will just in
time, with the full intention of annoying her stepchildren. The next day, \Gls{Moist} notices the
front-page piece mentioning his unwillingness to advise the Royal Bank, as well as a quashing of
the rumour that \Gls{Vetina} was interested in nationalizing it.

\subsubsection{\Gls{Moist} is afraid when \Gls{Slant} enters the Post Office with two Watchmen}
\Gls{Moist} receives a letter from \Gls{Gladys} threatening to expose his guilty secrets, and
suspects it to be a scam. A while later, \Gls{Stanley} informs him that a lawyer is waiting
downstairs, leading him to think reflexively about his escape plan. He sees \Gls{Slant} come up to
his office, alongside \Gls{Angua} and \Gls{Nobbs}. The lawyer tells him that \Gls{Lavish} has
left her dog \Gls{Fuss} to him, along with a massive collection of toys.

\subsubsection{\Gls{Slant} lays out the details of \Gls{Lavish}'s bequest to \Gls{Moist}}
\Gls{Slant} tells \Gls{Moist} that \Gls{Lavish} has left her shares in the Royal Bank to \Gls{Fuss}
as well, making it the de-facto chairman. \Gls{Moist} realizes that \Gls{Lavish} is giving him
ownership of the bank using the dog as a proxy. \Gls{Slant} reminds him that she dictated the will
to him just last night, in the presence of official witnesses. As he is leaving, \Gls{Slant} hands
over a personal letter from \Gls{Lavish} addressed to \Gls{Moist}.

\subsubsection{\Gls{Moist} realizes he has been manipulated into accepting the Bank job}
\Gls{Lavish} tells \Gls{Moist} to accept the job of shadow chairman at the Royal Bank, or be hunted
down by the Assassins' Guild, using the money she left as advance bounty at their Guild. He realizes
that \Gls{Vetina} simply outsourced the blackmail to \Gls{Lavish}, and is forced to take the job,
which comes with a handsome pay rise.

\subsubsection{\Gls{Moist} climbs into \Gls{Cosmo}'s carriage with \Gls{Fuss} by mistake}
\Gls{Moist} decides to leave the Post Office with \Gls{Fuss} to talk things over with \Gls{Vetina},
after seeing the Assassins' Guild fire a nonlethal arrow through his window to confirm the contract
on his life. He gets into the black carriage outside the Post Office, but finds \Gls{Cosmo}
waiting for him instead of \Gls{Vetina}.

\subsubsection{\Gls{Hereto} has a hitman kill the forger who made a replica of \Gls{Vetina}'s
    signet}
\Gls{Hereto} is forced to kill a forger for the replica of \Gls{Vetina}'s signet ring, when the
craftsman keeps haggling for a higher price, and threatens to tell on him unless he pays up.
Meanwhile, \Gls{Cosmo} offers a stamp paper promising a large payout in exchange for \Gls{Fuss},
only for \Gls{Moist} to point out that the salary for looking after the dog was already a bigger
sum.

\subsubsection{\Gls{Cosmo} drops \Gls{Moist} off next to the Palace}
\Gls{Cosmo} overcomes one of his involuntary eyebrow spasms, and threatens \Gls{Moist} with violence
unless he surrenders \Gls{Fuss}. He is dropped of at the palace, wondering how \Gls{Vetina} arranged
for the timely demise of \Gls{Lavish}, in a way that plunged him into all this trouble with the
stepchildren.

\subsubsection{\Gls{Vetina} talks to \Gls{Moist} about the city's dire need for funding}
At the palace, \Gls{Moist} notices \Gls{Vetina} excuse himself from a meeting with lots of
Guildmasters and engineers, only to deny any involvement in the death of \Gls{Lavish}. He reminds
\Gls{Moist} of his hanging and resurrection as a civil servant dedicated to the city's betterment,
and points out the money-hog that is the proposed Ankh-Morpork underground transit system, powered
by a dwarf artifact.

\subsubsection{\Gls{Moist} talks to \Gls{Sacha} about ending the gold standard}
\Gls{Moist} goes to the Royal Bank, taking note of yet another protest against the employment of
golems, and is welcomed in by \Gls{Bent}. He is told that a young woman is waiting for him in the
meeting room, and asked to sign the paperwork making him the de-facto chairman of the Bank. He
finds \Gls{Sacha} waiting for him, and lets go of his newfound sense of restraint when he starts to
talk about selling off the bank's gold reserve.

\subsubsection{\Gls{Moist} sees the private chef's daughter deliver \Gls{Fuss}'s breakfast}
\Gls{Moist} states that he is going to free up borrowing in order to stimulate the economy, using
money obtained by selling off the gold reserve to the dwarves. He remains vague when asked about
his life before becoming Postmaster, and watches the cook deliver \Gls{Fuss}'s meal. After
\Gls{Sacha} leaves, he goes to the kitchen, where the private chef \Gls{Aims} and his daughter
\Gls{Peggy} argue about the dog's lunch.

\subsubsection{\Gls{Moist} meets with the chefs in charge of \Gls{Fuss}'s meals}
\Gls{Moist} learns that \Gls{Aims} became an animal chef, because of his allergy to the word garlic
spoken out loud. \Gls{Peggy} tells him that he will recover from his PTSD in a minute when
\Gls{Moist} accidentally says the word, and gives him some dessert for \Gls{Fuss}. \Gls{Bent} comes
in with the key to the chairman's suite, where \Gls{Moist} is expected to sleep every night, as a
precondition of the \Gls{Lavish}'s bequest.

\subsubsection{\Gls{Moist} makes some prototype banknotes, following the idea of the promissory
    note}
\Gls{Moist} is impressed by his private suite, and learns that \Gls{Fuss} will stay there with him
every night. \Gls{Bent} informs him that \Gls{Lavish} has asked for her funeral to be held at the
lower-class temples, with only her family in attendance. \Gls{Moist} thinks hard about the idea of
fiat money, and decides to make some prototype bank-notes, bearing the \Gls{Fuss}'s paw-print next
to the written guarantee.

\subsubsection{\Gls{Cosmo} hands over the replica signet ring to \Gls{Cosmo}}
\Gls{Cosmo} inspects the replica signet ring delivered to him by his secretary \Gls{Hereto}, and
reminds him that sending Mr. \Gls{Cran} along to silence the craftsman was an unavoidable
inconvenience in his mission to imitate \Gls{Vetina}. \Gls{Hereto} tries to point out the fact
that the ring is too small for his overweight fingers, and \Gls{Cosmo} brushes off the blood supply
being cut off to his ring-finger.

\subsubsection{\Gls{Hereto} hopes that he can continue to fool \Gls{Cosmo} with \Gls{Vetina}'s
    alleged personal effects}
\Gls{Hereto} realizes that he has \Gls{Cosmo} successfully believing the ring to be genuine, with
the replica being switched for it at the palace. He realizes that \Gls{Cran} will be sent to hunt
him down, just like all the other loose ends, when \Gls{Cosmo} discovers the deception. He thinks
about the next item belonging to \Gls{Vetina} that might attract \Gls{Cosmo}'s attention, and win
him a similar bounty as the signet.

\subsubsection{\Gls{Adora} abruptly ends her digging expedition, as the dwarf observers try to fend
    off the boredom}
\Gls{Adora} finishes her work at the dig site all of a sudden, telling the dwarf observers that
any artifacts and coins dug up would be handed over to them. The golems in her employ leave along
with her, and the shaft dug into the ground collapses soon from a lack of support. Meanwhile,
\Gls{Cosmo} gathers the Lavvish family members after the funeral, and addresses them in the hopes of
reconciling the various claims for \Gls{Lavish}'s inheritance.

\subsubsection{\Gls{Cosmo} asks the extended family to say away from the \Gls{Fuss} problem}
\Gls{Cosmo} faces questions from a distant branch of the family, regarding \Gls{Moist} having
control of the Royal Bank by way of \Gls{Fuss}. He fends off the idea of poisoning the dog, and
asks them to let him deal with the issue of \Gls{Moist} on his own. Once he gets back home, he
decides to purchase \Gls{Bent}'s loyalty, and use him to influence the running of the bank under
the new chairman, believing that \Gls{Moist} will annoy him enough to make threats of violence
unnecessary.

\subsubsection{\Gls{Cosmo} thinks about the possible secrets about \Gls{Vetina} that \Gls{Moist}
    will know}
\Gls{Pucci} enters \Gls{Cosmo}'s dressing room, and sees him try on the tyrant's gloves and
hat. She warns him about his obsession with \Gls{Vetina}, and is amazed at how closely he has
studied \Gls{Vetina}'s daily schedule. He believes that \Gls{Moist}'s shady past is the secret to
gaining leverage over \Gls{Vetina}, and eventually usurping his position.

\subsection{}
\subsubsection{\Gls{Moist} does a test run of his new banknotes}
\Gls{Moist} goes to the joke shop owned by \Gls{Proust} and pays for his purchase using the new
banknote. He asks the rest of the shopkeepers to come gather around at closing time, and passes
more banknotes around for inspection. They agree with the general principle, but remain adamant that
the gold backing must remain at the bank, and that the notes should be more fancy.

\subsubsection{\Gls{Moist} almost falls into \Gls{Pucci}'s honeytrap}
\Gls{Moist} gets into a cab, only to find a scantily clad \Gls{Pucci} waiting for him inside. He
breaks out of the window, and runs away before the iconographer can take a picture of him for use in
her blackmail scheme. He wakes up the next day, and reads the front-page article in the Times about
his latest interview with \Gls{Sacha}. He absent-mindedly agrees to let \Gls{Gladys} give him a
massage, and gets some joints dislocated in the process.

\subsubsection{\Gls{Moist} decides to open up the bank to middle-income customers}
\Gls{Moist} is rescued by \Gls{Peggy} a while later, with \Gls{Gladys} looking sorry for the
damage she unwittingly caused. \Gls{Bent} walks in with news that a few people are lined up outside
the Royal Bank wanting to close their accounts, and \Gls{Moist} quickly asks him how many more are
waiting to open them. He decides to let people earn interest on much smaller deposits at the bank,
and accompanies \Gls{Bent} with his new hat, dusted with gold sprinkles.

\subsubsection{\Gls{Moist} makes the stamp collectors realize the value of his banknotes}
\Gls{Moist} makes an announcement to the gathered citizens that he will be offering them a small
interest on year-long deposits, and throws in a complimentary banknote as an account-opening bonus.
\Gls{Pucci} walks in, trying to debunk the value of the banknotes, and is angered by some astute
stamp collectors realizing the value of prototype banknotes. \Gls{Moist} seizes the opportunity to
auction off the banknotes for several times their face value, as \Gls{Pucci} hurries off in a huff.

\subsubsection{\Gls{Moist} issues his first business loan to \Gls{Dibbl}}
\Gls{Moist} watches the customers line up to open their accounts, and notices a preacher in a black
robe watching him intently in the background. He talks to \Gls{Bent} about opening up the loan
system, and notices the priest is suddenly gone. At the loan office, \Gls{Bent} is made to watch
as \Gls{Moist} issues a loan to \Gls{Dibbl} for the purchase of a larger wagon, with an attached
oven. Before \Gls{Bent} can object to the loan, \Gls{HarryK} walks in with two of his thugs.

\subsubsection{\Gls{Moist} gives his first large loan to \Gls{HarryK}}
\Gls{Moist} sees \Gls{HarryK} deposit a large sum into the bank, and immediately demand a loan for
twice the amount. \Gls{Bent} asks if he has any collateral, and is sent out of the room by
\Gls{Moist}, who wishes to lend to \Gls{HarryK} on the basis of his reputation. Afterward,
\Gls{Moist} receives the deeds to some of \Gls{HarryK}'s properties, and is relieved to have
something to placate \Gls{Bent}.

\subsubsection{\Gls{Moist} learns about the value of \Gls{Owls} in designing the new banknotes}
\Gls{Moist} visits \Gls{Spools} at his specialty printing shop, and is pleased to learn that a large
number of government orders have started pouring in, after their successful printing of the postage
stamps. \Gls{Spools} shows him some counterfeit stamps made by \Gls{Owls}, and believes he is the
right person to design the banknotes, given how his fakes contained more detail than the real stamps
themselves.

\subsubsection{\Gls{Cosmo} asks \Gls{Bent} to look for ways to oust \Gls{Moist}}
\Gls{Cosmo} visits \Gls{Bent} at his room in \Gls{Cake}'s lodging house, and asks him nicely to
consider non-violent options with regard to eliminating \Gls{Moist}. He makes a vague promise about
greater wealth in return, along with a possible share in the ownership of the Royal Bank.

\subsubsection{\Gls{Moist} breaks \Gls{Owls} out of death row}
\Gls{Moist} scales the walls of the prison using all the practice he had at the Post Office, and
impersonates a Watchman using the uniform stolen from the bank's locker room. He asks to transport
\Gls{Owls}, and notices that the warden on duty is \Gls{Belly}, a petty tyrant who hates
\Gls{Vimes}. He presents a correctly filled form that he stole from \Gls{Spools}, and \Gls{Belly}
brings \Gls{Owls} out without any shackles attached to his hands or ankles.

\subsubsection{\Gls{Owls} escapes from \Gls{Moist}'s hold, and runs off into the night}
\Gls{Owls} kicks \Gls{Moist} in the groin and runs off into the rainy night, as soon as he signs the
prisoner transfer form, relieving the warden of any responsibility for the prisoner. He returns to
the Bank after changing into his gold suit, and is pleased to see the guards let him in without any
fuss. Unable to sleep, he decides to sneak into the cellar, and asks \Gls{IgorC} if there is a
hidden entrance to the bank. \Gls{IgorC} tells him that there is only an exit that is left unguarded
since it only opens from the inside.

\subsubsection{\Gls{IgorC} accepts \Gls{Moist}'s request to give \Gls{Owls} a makeover}
\Gls{IgorC} shuts the door on \Gls{Moist} before explaining the secret door-knock that would
signal him to open the door later, and goes back to working on \Gls{Hubert}'s simulation machine.
He finds \Gls{Owls} at his last known location before being apprehended, and convinces him to come
to \Gls{Hubert}'s basement, where he can design banknotes for a living. Back at the basement,
\Gls{Moist} asks \Gls{IgorC} to give \Gls{Owls} a makeover, and agrees with the false name of
\Gls{Clamp}.

\subsubsection{\Gls{Vetina} talks to \Gls{Moist} about some curious deaths in the city}
\Gls{Moist} is dragged off the next morning to the palace, where \Gls{Vetina} tells him that
\Gls{Owls} was hanged as per schedule. \Gls{Moist} wonders if an impostor was hanged, with the
breakout being hushed up to avoid embarrassment. \Gls{Vetina} then shows his signet ring to
\Gls{Moist}, and tells him that the only known craftsman who worked on the magical alloy was found
murdered a few days ago. He then lists the other petty crimes and mysterious deaths perpetrated by
\Gls{Cosmo}, unsure of what the motive can be.

\subsubsection{\Gls{Vetina} asks \Gls{Moist} to lend the city the amount needed for the underground
    railway}
\Gls{Vetina} asks \Gls{Moist} to have the Royal Bank provide a large loan to the city, making him
run back to the cellar. He finds \Gls{Igor} finishing the electro-shock therapy on \Gls{Owls},
which supposedly sucked the old memories out of his brain and deposited them in a jar. \Gls{Clamp}
then shows off the finished one-dollar banknote, making \Gls{Moist} realize that higher
denominations would be needed desperately to service \Gls{Vetina}'s loans.

\subsubsection{\Gls{Moist} runs into his old partner in crime \Gls{Cribb}}
\Gls{Moist} insists that he has a better idea about running the bank than the other shareholders,
and asks \Gls{Bent} to accompany him to the Royal Mint, where \Gls{Spools} is setting up his new
printing press. \Gls{Moist} is accosted by his old partner in crime \Gls{Cribb}, now dressed as a
reformed thief who has found religion. \Gls{Moist} lets slip his name before \Gls{Cribb} reveals it,
and realizes that \Gls{Cribb} was likely the person behind the letter threatening to expose his
past.

\subsubsection{\Gls{Moist} gets \Gls{Shady} and the Mint workers to step aside for \Gls{Spools}}
\Gls{Moist} gets \Gls{Shady} and the mint workers to accept a promotion as inspectors and watchmen,
with fancy looking uniforms thrown in. Against \Gls{Bent}'s expectations, \Gls{Shady} consults with
his men for a while, and accepts the offer, after making sure that the craftsmen who made coins at
home would still have their jobs, even if they only made fancy commemorative coins. He is relieved
to find \Gls{Adora} back from her expedition, and curious why she asks him to accompany her to the
University.

\subsubsection{\Gls{Adora} leads \Gls{Moist} to the University to open the Cabinet of Curiosity}
\Gls{Adora} asks a wizard for the location of the Cabinet of Surprise, and is led to a secret
room by \Gls{Indef}. Inside, \Gls{Stibb} introduces the current iteration of the Cabinet as a
infinite fractal of cupboards, visualized by \Gls{Hex} as a large tree. \Gls{Adora} talks about
receiving a golem's foot from the Cabinet many years ago, and asks to see it once again.

\subsubsection{\Gls{Stibb} denies \Gls{Adora}'s request to take the golem's foot away}
\Gls{Stibb} has the Cabinet produce the ancient golem's foot as requested by \Gls{Adora}, as she
takes out a hay-wrapped package from her travel bag. She takes out an arm with the same inscriptions
as the leg, and attempts to confiscate it from the University in an attempt to put the golem
together and free it. \Gls{Stibb} refuses to let the artifact be taken away, and concedes
\Gls{Adora}'s request to talk to the spirit of \Gls{Flead}, using \Gls{Hix}'s necromantic methods.

\subsection{}
\subsubsection{\Gls{Bent} tells \Gls{Cosmo} about the visit from \Gls{Cribb}}
\Gls{Adora} tells \Gls{Moist} that her dig site found four golems buried so far deep, as to revise
existing estimates of when they were first made. The next day, \Gls{Moist} talks about \Gls{Gladys}
identifying as female, leading \Gls{Adora} to suspect that the girls at the Post Office were
giving her too many books on etiquette for women. Meanwhile, \Gls{Bent} is taken to \Gls{Cosmo}'s
manor, where he faithfully conveys the incident with \Gls{Cribb}.

\subsubsection{\Gls{Adora} talks about the solid gold golems found by the expedition}
After \Gls{Bent} leaves, \Gls{Cosmo} asks \Gls{Hereto} to try and track down \Gls{Cribb} using the
Beggars' Guild, and reminds him to continue bribing his way up the chain of command at the palace to
retrieve \Gls{Vetina}'s next personal belonging. On her way to the \Gls{Hix}'s office, \Gls{Adora}
explains to \Gls{Moist} that the four golems she had found were made of solid gold, and that the
others in the Golem Trust were sneaking them out to the city in violation of the contract signed
with the Dwarf King.

\subsubsection{\Gls{Hix} gets ready to communicate with \Gls{Flead}}
\Gls{Hix} points out the fancy props and ambience in his summoning room, as \Gls{Moist} realizes
that most of it is from the joke shop owned by the Clowns' Guild. \Gls{Hix} insists on putting on
a good show for \Gls{Flead}, who died many centuries ago, and is a traditionalist in these matters.
Meanwhile, \Gls{Bent} faces an inner struggle regarding the success of \Gls{Moist}'s new strategy,
and his own desire to prove himself to the Lavishes as an orphan who was given a second chance by
the late chairman.

\subsubsection{\Gls{Flead} receives the golem song transcript from \Gls{Adora} for deciphering}
\Gls{Flead} is immediately interested in the golem hand that \Gls{Adora} shows him, and asks if
more of the legendary golden golems have been found. She summarizes the results of her findings,
and hands him a transcript of the song that the buried golems were heard singing. \Gls{Flead} asks
for some time to decipher the language, and says something in the golem tongue that \Gls{Adora}
finds amusing.

\subsubsection{\Gls{Bent} makes his first ever mistake tallying figures in the bank's counting room}
\Gls{Drapes} is forced to return one of the calculation sheets marked by \Gls{Bent}, with a note
saying he made the mistake. The employees in the counting room brace for an outburst, since this is
the first time \Gls{Bent} has ever made a counting error in his career. Meanwhile, \Gls{Cribb}
reads all the back-issues of the Times at their office, realizing that a lifetime pension was on the
cards, if he could properly blackmail \Gls{Alfred}.

\subsubsection{\Gls{Moist} asks for \Gls{Clamp}'s mind to be restored to its original state}
\Gls{Alfred} is pleased to see the woman at the Times office, \Gls{Houser}, ask him to give a
lecture on theology to her support group. He starts to plan out his moves, and wonders why the
woman has changed her last name. Meanwhile, \Gls{Moist} returns to \Gls{Hubert}'s cellar, and
finds that \Gls{IgorC}'s treatment has robbed \Gls{Clamp} of his artistic abilities. He asks for the
procedure to be reversed, even as \Gls{IgorC} tries to point out how happy \Gls{Clamp} has become.

\subsubsection{\Gls{Drapes} enlists \Gls{Moist} in the search for \Gls{Bent}}
\Gls{Drapes} informs \Gls{Moist} of \Gls{Bent}'s mental breakdown, and asks him to go to his
residence to investigate. \Gls{Moist} realizes that the rest of his plans for the day will have to
wait, in order to keep up his image with the accountants as a benevolent boss. \Gls{IgorC} explains
to \Gls{Hubert} that he has sealed the simulation machine against any tinkering of parameters, and
this in turn has made it a voodoo doll that affects the city's economy if any changes happen to it.

\subsubsection{\Gls{Cosmo} wishes to have the walking stick of \Gls{Vetina}}
\Gls{Cosmo} learns about \Gls{Bent}'s breakdown, and asks \Gls{Hereto} to continue his quest to
acquire \Gls{Vetina}'s walking stick. He repeats the rumours about the stick concealing a sword that
had slain thousands of men, and is delighted to see \Gls{Hereto} agree with every detail.
\Gls{Hereto} asks for a large sum of gold in order to buy the silence of the palace staff, while
knowing that he is finishing up a cheap replica of the staff in his home.

\subsubsection{\Gls{Moist} and \Gls{Drapes} see \Gls{Bent}'s room at \Gls{Cake}'s house}
\Gls{Vetina} asks \Gls{Drumk} about \Gls{Bent}, once news of the mental breakdown reaches him.
\Gls{Drumk} says that there is no rap sheet on him, and reminds \Gls{Vetina} that he allegedly
arrived in the city as an orphan. Meanwhile, \Gls{Ludm} shows \Gls{Moist} and \Gls{Drapes} into the
room rented by \Gls{Bent}, and tells them that she does not have a key to his wardrobe. \Gls{Moist}
believes that \Gls{Bent} might be trying to hide the fact that he is a vampire, and learns that
\Gls{Cosmo} had paid him a visit recently.

\subsubsection{\Gls{Moist} tries to reassure the accountants in the absence of \Gls{Bent}}
\Gls{Moist} returns to the Royal Bank to have dinner with \Gls{Adora}, as the clerks wander about
the premises, lost without \Gls{Bent} at the helm. He tells them to head home for the night, and
promises to hold a meeting of the senior accountants the next morning to try and get their daily
schedule organized. \Gls{Adora} expresses interest in seeing \Gls{Clamp}'s work, and goes to the
cellar with \Gls{Moist}.

\subsubsection{\Gls{Adora} makes a small detour into \Gls{Hubert}'s cellar}
\Gls{Adora} sees \Gls{Hubert} tinkering with his simulation machine, and decides to return to the
chairman's suite immediately. \Gls{Moist} finds \Gls{Gladys} missing along with \Gls{Fuss}, and runs
downstairs to the kitchen to check. He finds \Gls{Peggy} bringing \Gls{Fuss} up from the storage
rooms, and \Gls{Gladys} helping \Gls{Aims} put the finishing touches on the fancy dinner.

\subsection{}
\subsubsection{\Gls{Adora} finds the journals of the old chairman}
\Gls{Cribb} is forced to step out onto the streets, when \Gls{Houser} closes the newspaper office
for the night, and runs into \Gls{Hereto}. Before the clerk can offer him a bargain, he asks to
be taken to \Gls{Cosmo}, who he believes is an ally against \Gls{Albert}. Meanwhile, \Gls{Adora}
finds a hidden compartment in the chairman's desk, that contains the key to one of the large
cupboards. Inside, \Gls{Moist} finds the journals kept by the chairman, and starts to look through
them for details on \Gls{Bent}'s early life.

\subsubsection{\Gls{Moist} decides to look inside the gold vault for \Gls{Bent}}
\Gls{IgorC} shows the compartment in the simulation machine that represents the bank's gold reserve,
and \Gls{Hubert} notices that it is empty. Meanwhile, \Gls{Moist} asks \Gls{Adora} if she can
hide her golden golems from the public eye, and hit upon the fact that \Gls{Bent} might have
hidden himself in the Royal Bank's gold reserve vault.

\subsubsection{\Gls{Moist} is told that the gold reserve in the vault has been stolen}
\Gls{Moist} asks \Gls{Gladys} to break into the gold vault from above, and drops in to find
\Gls{Bent} lying unconscious from oxygen deprivation. Two Watchmen on night-duty arrive in time to
spot him breaking into the vault, and ask him to explain why as soon as \Gls{Bent} is attended to.
A while later, \Gls{Carrot} comes along to interrogate \Gls{Moist} in his office, and tells him that
the werewolf in the Watch can confirm most of his story using \Gls{Fuss}'s testimony. He then
reveals that the gold reserve has vanished from the vault, leaving \Gls{Moist} the prime suspect.

\subsubsection{\Gls{Cribb} hands over a signed affidavit of his suspicions to \Gls{Cosmo}}
\Gls{Cribb} is appalled at the paltry sum offered by \Gls{Cosmo} in exchange for a signed affidavit
swearing that \Gls{Albert} and \Gls{Moist} are one and the same. \Gls{Hereto} is asked to lead
\Gls{Cribb} to a nice hotel for the night, with \Gls{Cosmo} promising a bigger payout if the
allegations are confirmed. \Gls{Hereto} decides to make a run for it after delivering the replica
of \Gls{Vetina}'s walking stick.

\subsubsection{\Gls{Moist} thinks about when the gold reserve was stolen}
\Gls{Flead} emerges as a specter in \Gls{Hix}'s summoning room, and tells him that he needs to
watch the golden golems being brought into the city. Meanwhile, \Gls{Moist} spends the night
thinking about when the gold reserve was swapped out for gold-painted lead ingots, and wonders if
the former chairman had spent it all on his lavish lifestyle. He is dismayed by \Gls{Adora} being
detained in jail overnight, for the attempted assault on \Gls{Detri}, and wanders into the cellar.

\subsubsection{\Gls{Moist} notices something off about \Gls{Hubert} and \Gls{IgorC}}
\Gls{Moist} asks \Gls{Hubert} if his machine is doing well, as \Gls{IgorC} brews a traditional
Uberwald drink for him. He detects something off in the way \Gls{IgorC} talks to \Gls{Hubert} about
the missing gold, and realizes he is not going to be let in on the secret. After the drink gets him
intoxicated, \Gls{Moist} returns to his office, waiting for the morning Times to print the news
about the gold, and lose him the job.

\subsubsection{\Gls{Cosmo} gleefully presents a search warrant to \Gls{Moist} for the vault}
The next morning, \Gls{Cosmo} knocks at the front door of the bank with a search warrant signed
by \Gls{Vimes}, who is also in attendance with his Watchmen. \Gls{Sacha} hands him the Times, where
the article covering the gold theft lacks any solid details, and asks him how he plans to stop the
bank run. \Gls{Moist} notices that the crowd gathering outside has not yet asked to withdraw their
money, even after knowing the bank has no gold to back it up.

\subsubsection{\Gls{HarryK} decides to use the crisis to deposit more money in the Royal Bank}
\Gls{HarryK} arrives with his retinue of bodyguards, and tells \Gls{Moist} that he is going to
deposit more money in the bank, in gold and silver coins. He tells \Gls{Moist} privately that the
Lavishes must be out to get him, and that he must have some secret plan to deal with the missing
gold. \Gls{Moist} tries to refuse the deposit, but relents when he works out the goodwill that it
would build with the assembled citizens.

\subsubsection{\Gls{Cosmo} tries to taunt \Gls{Moist} about the gold reserve costing him his job}
\Gls{Cosmo} and the group of auditors come out of the Bank, confirming the absence of the gold
reserve. \Gls{Vimes} stops any entry to the bank by creating a cordon of troll Watchmen, and
chastises \Gls{Cosmo} for trying to incite a bank run. \Gls{Adora} is escorted to the Bank by some
Watchmen, in time for a stampede running away from \Gls{Flead}, who is carried on a magical
trampoline by \Gls{Hix} and his assistants.

\subsubsection{\Gls{Flead} tells \Gls{Adora} about the coming army of golems}
\Gls{Flead} tells \Gls{Adora} that the inscriptions indicate the presence of four thousand golems
at the dig site, and not just four golems made of precious metals. \Gls{Moist} feels the ground
start to rumble, as the golems make landfall from the river Ankh. At an emergency council meeting
in the Great Hall of the palace, \Gls{Adora} tells \Gls{Vetina} that the army of golems have no
scroll in their head, and believes that their only orders are to protect the city.

\subsubsection{\Gls{Vetina} listens to \Gls{Hubert} argue against putting the golem army to work}
\Gls{Vetina} is dismayed by the other cities sending letters about the army of golems standing at
the city walls being an open declaration of war, as \Gls{Ridcu} tries his best to refute the idea.
\Gls{Hubert} shows up at the palace, desperate to explain the consequences of the golems being put
to work in the city. \Gls{Moist} pulls \Gls{Hix} to a private corridor, and asks him if he can
perform a ritual to implant the spirit of \Gls{Flead} inside the army of golems, against University
regulations.

\subsubsection{\Gls{Moist} initiates his plan to dispose of the golem army safely}
\Gls{Moist} pays off the Watchmen guarding the leader of the golem army, to get them to widen
their perimeter for \Gls{Hix}'s ritual. He persuades \Gls{Flead} to translate some command phrases
that might be used to control the golem army, in exchange for haunting the local strip club for
all eternity.

\subsubsection{\Gls{Moist} explains the new golem standard to \Gls{Sacha}}
\Gls{Moist} watches the crowd slowly arrive at the barren plain outside the city, as the golem
army prepares to bury itself underground. He reveals to \Gls{Sacha} that the golem army are the
new standard upon which the city's currency is to be based. \Gls{Sacha} notes that he is the only
person that knows how to command the golem army, and this automatically makes him the sole guarantor
of the city's financial system.

\subsubsection{\Gls{Moist} is taken into custody for the missing gold reserve}
\Gls{Vetina} arrives with some Watchmen, asking for \Gls{Moist} to be taken into custody, pending
the investigation into the missing gold reserve. \Gls{Cosmo} shows up looking smug, as \Gls{Moist}
asks for some of the golem horses to be handed over to the Post Office for use as couriers.
\Gls{Vetina} shocks \Gls{Cosmo} by ordering a detailed audit of the Royal Bank's ledgers, as he
takes \Gls{Fuss} along with him for safekeeping.

\subsubsection{\Gls{Hix} confines the spirit of \Gls{Flead} in a strip club}
\Gls{Hix} gets his students to play along in his plan to rid his department of \Gls{Flead}'s
annoying traditionalism, by confining his spirit to a strip club far from the University. The
students realize that co-operation will mean a big boost to their grades, and choose to set aside
the question of legality.

\subsubsection{\Gls{Pucci} spots the symptoms of \Gls{Cosmo}'s necrosis}
\Gls{Pucci} asks \Gls{Cosmo} about getting rid of \Gls{Bent}, since they now have \Gls{Cribb}
available for use as an informat. \Gls{Cosmo} tries to brush off her remarks about the smell of
dead flesh in his room, and his pale complexion. He remains careful about taking off the glove that
hides the decaying finger, caused by wearing the replica of \Gls{Vetina}'s ring. After \Gls{Pucci}
leaves, \Gls{Cosmo} asks \Gls{Cran} to take care of \Gls{Bent}, and wonders where \Gls{Hereto} has
gone off to.

\subsubsection{\Gls{Drapes} fills in \Gls{Bent} on the past few days when he was knocked out}
\Gls{Drapes} watches over \Gls{Bent} in his room, and informs him of the events of the last few
days when he wakes up. He opens his magically locked wardrobe, and transforms into some sort of
monster, just as \Gls{Cran} walks in to finish him off. The next day, \Gls{Moist} is escorted
ceremonially to the palace, where all the city's power-centers are gathered for the hearing.

\subsubsection{\Gls{Vetina} reveals the deal he made with \Gls{Moist} after the faked hanging}
\Gls{Vetina} asks for \Gls{Bent} to be brought to the inquiry, and \Gls{Vimes} returns with news
of people being found murdered in his residence, with \Gls{Bent} himself missing. The argument
continues with \Gls{Vetina} reading out the findings of his audit, and \Gls{Vetina} being forced
to reveal the hanging of \Gls{Albert}. \Gls{Cosmo} and \Gls{Cribb} realize that their chance of
blackmailing \Gls{Moist} is slipping by, as a clown walks in with custard pies that he throws at
every dignitary in the Great Hall.

\subsubsection{\Gls{Bent} makes a grand entrance as a clown}
\Gls{Moist} dives in front of \Gls{Vetina} to take the pie meant for his face, as \Gls{Drapes} walks
in holding the ledgers from \Gls{Bent}'s wardrobe. \Gls{Vetina} correctly identifies that the
clown is \Gls{Bent}'s alter ego, and asks \Gls{Whitef} to induct him into the Fools' Guild.
\Gls{Drumk} verifies that the new ledgers show the gold reserve having been sold by the Lavishes
long ago, and that the handwriting belongs to \Gls{Bent}, who recorded it in his own notebooks.

\subsubsection{\Gls{Moist} tries his best to get the delirious \Gls{Cosmo} to co-operate}
\Gls{Moist} tries to help \Gls{Cosmo} remain seated, and is alarmed to see the ailing man point a
sword at his neck. \Gls{Pucci} stands up, and tries to defend her father's pilfering of the gold
reserve, claiming that all of the extended family members had some share of it in the form of
jewelry. \Gls{Moist} decides to play into \Gls{Cosmo}'s delusions about being the Patrician, and
reveals the dead finger for everyone to see. He escorts \Gls{Cosmo} out into the sunlight, so that
the magical alloy in the ring might burn off the necrotic finger.

\subsubsection{\Gls{Vetina} takes \Gls{Moist} and \Gls{Adora} to the Fools' Guild}
\Gls{Vetina} shows up the next day, as \Gls{Moist} tries to wriggle out of revealing the secret of
the Golem Army at \Gls{Adora}'s insistence. He asks \Gls{Moist} to get in his carriage, and takes
him to the Fools' Guild to see \Gls{Bent}'s new life. At the Guild, \Gls{Whitef} reveals that
\Gls{Bent} was born to a famous clown, and could have been trained as one of the best in the world
if he had been brought to the guild as a child.

\subsubsection{\Gls{Vetina} figures out the secret to commanding the golem army}
\Gls{Moist} talks to \Gls{Bent} in private, and persuades him to come back as the bank's chief
cashier. He intends to launch his banknotes soon, and asks \Gls{Bent} to try and make peace with his
inner clown. \Gls{Vetina} then takes \Gls{Moist} and \Gls{Adora} to the palace, and correctly
guesses that the secret of the golem army is that the commands have to come from someone dressed in
gold.

\subsubsection{\Gls{Vetina} lets slip the fact that the secret of the golem army is known to
    every kingdom}
\Gls{Vetina} reveals that someone has sent the secret of the golem army to every kingdom in the
plains, and wonders if it was \Gls{Moist} who did it, as a means of preventing the army from being
used by any one kingdom against another. He then tells \Gls{Moist} that \Gls{Owls} has been granted
a second life inside the palace, leaving \Gls{Moist} to wonder if \Gls{Vetina} was as much a
conman as himself.

\subsubsection{\Gls{Cribb} tries and fails to extort \Gls{Moist} using \Gls{Adora} as a hostage}
\Gls{Cribb} attempts to hold up \Gls{Moist} by pointing a knife at \Gls{Adora}'s back, but is
betrayed by his own spring-loaded dentures exploding. \Gls{Carrot} scoops up \Gls{Cribb} to take
him to a hospital, as \Gls{Moist} decides to go to the temple and thank his new patron God.
\Gls{Vetina} asks \Gls{Drumk} about \Gls{Moist}'s next job once he inevitably gets bored with
minding the Royal Bank, and is amused when \Gls{Drumk} suggests the tax bureau.

\subsubsection{\Gls{Hubert} asks \Gls{IgorC} to return the stolen gold to the Bank vault}
\Gls{Bent} walks in with \Gls{Drapes} at opening time the next day, and tells the gathered staff
that he intends to marry her at the Fools' Guild. The staff celebrate, just as \Gls{Moist} returns
with the first batch of banknotes printed by \Gls{Spools} in the Mint next door. \Gls{Hubert} asks
\Gls{IgorC} to put the stolen gold reserve back into the vault in the simulation engine, since this
would be reflected in real life as well. \Gls{IgorC} complies, just as \Gls{Adora} and \Gls{Moist}
share a moment of intimacy in the empty vault.

\subsubsection{\Gls{Cosmo} is confined to an insane asylum, and \Gls{Flead} to a strip club}
\Gls{Cosmo} wakes up in an asylum for the insane, finding himself in a room filled with other
patients in white robes convinced they were the Patrician. He laughs at their delusion, believing
himself to be the real \Gls{Vetina}, as the nurses check in on him. Meanwhile, \Gls{Flead} uses his
powers as a spirit to rid the strip club of belligerent drunks, making the management thankful for
the smooth operation of the establishment.