\section{Maskerade}


\subsection{}
\subsubsection{\Gls{Ogg} and \Gls{GWea} struggle to stay cheerful after \Gls{Magrat} retires}
At a coven meeting in the high mountains, \Gls{Ogg} thinks about how the group has now lost
\Gls{Magrat}, who has become queen after marrying \Gls{VerSec} of Lancre. She hopes to find some
other junior witch to pick up the slack, and help restore \Gls{GWea} to her old self. Meanwhile,
\Gls{Goatb} picks up a faded manuscript for a cookbook in Ankh-Morpork, and asks for it to be
sent to the engravers' guild for reproduction, sensing the potential jackpot in selling copies of
it.

\subsubsection{\Gls{Perdita} signs up for the audition process at the Ankh-Morpork Opera House}
\Gls{Perdita} shows up to the Ankh-Morpork Opera house to answer a call for auditions, and is led
inside by \Gls{Walter}, the resident sweeper. At the audition room, she meets a man with a huge
moustache who hands her a clipboard. She chooses to adopt the fancy name instead of her birth
name when signing herself up for the audition process.

\subsubsection{\Gls{Perdita} wows the Opera House managers with her raw vocal talent}
\Gls{Ogg} rules out all the young girls in Lancre town except \Gls{Perdita}, as she thinks about
potential recruits to her coven of witches. Meanwhile, \Gls{Perdita} impresses the Opera House
managers with her vocal skills, even as she tells them that she has had no formal training.
Meanwhile, \Gls{GWea} grows tired of tending to sick villagers with her placebo potions and fancy
trinkets, while recalling the adventures she had outside Lancre.

\subsubsection{\Gls{Seldom} talks about admitting \Gls{Chris} to the Opera}
In his office, \Gls{Seldom}, the new owner of the Opera House, talks about \Gls{Chris}, one of the
new candidates, as \Gls{Salz} and \Gls{UShaf} try to remind him of her awful singing voice. He
asks \Gls{UShaf} if he can't bring her up to speed as chorus master with a few months' practice, and
keeps emphasizing her stage presence. \Gls{Seldom} then forces them to let her in, when he reveals
the loan that her father advanced for the purchase of the Opera House.

\subsubsection{\Gls{Chris} and \Gls{Perdita} both pass the audition process}
\Gls{Seldom} dismisses the idea of \Gls{Perdita} being a star in the Opera, even as the \Gls{UShaf}
points out her amazing vocal range. \Gls{Chris} meets \Gls{Perdita} some time later, and is glad to
know that they have been allotted the same room in the trainee lodgings. \Gls{Perdita} is alarmed
by how easily she is able to pass off \Gls{Ogg} as some renowned teacher who trained her in Lancre,
and proceeds to her room.

\subsubsection{\Gls{Ogg} learns about \Gls{Perdita}'s journey to Ankh-Morpork from the girl's
    mother}
\Gls{Ogg} visits \Gls{Perdita}'s mother, and is dismayed to learn that the young girl has gone to
Ankh-Morpork to seek her fortune as an opera singer. \Gls{Ogg} realizes that a tea-leaf divination
is expected of her, and prepares the empty cup of tea. She drops the cup out of shock when she sees
the pattern in it. At their room, \Gls{Perdita} spots the full length mirror built into the wall,
and finds the room very spartan otherwise.

\subsubsection{\Gls{Perdita} thinks about the witchcraft as a career choice}
\Gls{Perdita} thinks about her life as an overweight young girl in Lancre, and of how the people
around her tried very hard to talk about the importance of a good personality when addressing her.
She then thinks about the typical witch lifestyle, involving self-isolation and a deliberate sense
of mysticism to separate oneself from common-folk, and finds it at odds with her deep desire for
validation.

\subsubsection{\Gls{Ogg} and \Gls{GWea} realize that \Gls{Perdita}'s life is in danger}
\Gls{Ogg} hurries to \Gls{GWea}'s cottage and has her prepare some tea. \Gls{GWea} sees \Gls{Death}
in the tea leaves, when \Gls{Ogg} asks her to concentrate on \Gls{Perdita}, and is convinced to
help the little girl face whatever danger is coming. \Gls{Shawn} walks in with a big bag of mail,
with all the letters addressed to ``The Lancre Witch''.

\subsubsection{\Gls{GWea} plans to go to Ankh-Morpork to get \Gls{Ogg} the royalty she is owed}
\Gls{GWea} is firmly opposed to the idea of \Gls{Ogg} sending her recipes to Ankh-Morpork to have
them printed as a cookbook, until she learns about the monetary reward. She asks \Gls{Ogg} for some
paper, and starts to work out how much she is owed in royalties. \Gls{Ogg} is shocked by the royalty
amount, as \Gls{GWea} makes a plan to threaten \Gls{Goatb} in person. \Gls{GWea} also worried about
the hit to her reputation, if people mistook the author of the cookbook full of sexual innuendos to
mean herself.

\subsubsection{\Gls{Perdita} rushes to the pipe organ when she hears a commotion behind the stage}
\Gls{Chris} talks to \Gls{Perdita} about the famed \Gls{Ghost}, and of how a seat is kept reserved
for it in the expensive box seats meant for the wealthy. A while later, she hears a commotion at the
pipe organ behind the stage, and finds someone tangled up in the wires up above, with a bucket of
green paint toppled over on the floor.

\subsubsection{\Gls{Perdita} listens to murmurs about the reappearance of the \Gls{Ghost}}
The two witches manage to get the stage coach to Ankh-Morpork to stop using their magic, and bully
the coachman into giving them a free ride to the city. Meanwhile, \Gls{Pounder} tries to make a
show of describing the \Gls{Ghost}, as the man entangled above the pipe organ is gently lowered
down. \Gls{Perdita} breaks the spell by asking if the \Gls{Ghost} simply is a person with a mask
on that makes him look like a human skull with empty eye sockets.

\subsubsection{\Gls{Salz} monitors the incident with the organ pipe, and tries to restore order}
\Gls{Salz} then tries to get the gathered trainees back to their stations, and asks \Gls{Pounder}
to stop spreading rumours about the \Gls{Ghost}. Once he dismisses everyone else, \Gls{Salz} asks
\Gls{Chris} and \Gls{Perdita} to recall what they saw up above the pipe organ. \Gls{Perdita} fails
to repeat the fancy description of the \Gls{Ghost}, and \Gls{Salz} is happy to finally have one
other pragmatic person working in the Opera.

\subsubsection{\Gls{Ogg} and \Gls{GWea} make the best of their long journey by coach}
\Gls{Ogg} shows her fellow passengers her big sack of food for the long road trip, as \Gls{GWea}
observes the one fat man who did not wake up when the coach had a sudden stop at Lancre. \Gls{Ogg}
insists on stopping at Ohulan so that she can relieve herself, even as some passengers try to remind
her that the coach has not stop there.

\subsubsection{\Gls{Seldom} learns about the truth behind the \Gls{Ghost}}
\Gls{Seldom} goes over the accounts of the Opera House, and wonders how the previous owners maanged
to keep it working for so long. \Gls{Salz} comes in with \Gls{Andre}'s report about the organ pipe
being smashed beyond repair, and describes the full history of the \Gls{Ghost}. \Gls{Ogg} deals with
her emergency as \Gls{Death} reaps the soul of a swan nearby, after tricking it into singing its
last song.

\subsubsection{\Gls{Seldom} is horrified by the full extent of the Opera House's problems}
\Gls{Seldom} is shocked to learn that some unsolved murders in the Opera House have been attributed
to the \Gls{Ghost}, and shows him the turpentine soaked letter that is usually left at the scene of
the crimes. The letter is a written note where the \Gls{Ghost} laughs, leaving \Gls{Seldom} even
more convinced that it is a cover story for the real criminals. \Gls{Salz} shoots down
\Gls{Seldom}'s idea to involve the Watch, by pointing out that they would interfere with operations
and further tank revenue.

\subsection{}
\subsubsection{\Gls{GWea} sees \Gls{HenryS} receive a warm welcome at some small town}
The fat man in \Gls{GWea}'s carriage introduces himself as \Gls{HenryS}, a performer at the Opera.
At the next stop, the two witches are surprised to see people lined up outside the carriage,
waiting to see \Gls{HenryS}. \Gls{GWea} is surprised to see them shout the name of \Gls{Enrico},
and does not realize that it is his stage name.

\subsubsection{\Gls{Seldom} listens to \Gls{Salz} talk about the difficulty with running operas}
\Gls{Salz} lists the various bad omens and superstitions surrounding the opera, and tells
\Gls{Seldom} that he has no expectation of the Opera House ever being a profitable venture.
\Gls{Walter} comes in with two buckets of coal for \Gls{Seldom}'s office fireplace, and \Gls{Salz}
stares at the boy for a while, as \Gls{Seldom} recalls his old business in the cheese industry.

\subsubsection{\Gls{Ogg} and \Gls{GWea} realize that \Gls{HenryS} an accomplished singer}
\Gls{Greebo} breaks into the tavern's kitchen to eat some food, and subconsciously turns into his
human form when a cook walks in, trapping him in a corner. He runs out of the tavern into the
darkness, with some villagers following him. Meanwhile, \Gls{Ogg} and \Gls{GWea} listen to
\Gls{HenryS} take a bath in the room next to their own, and are intrigued by his proficient singing
in two different languages.

\subsubsection{\Gls{GWea} decides to help the innkeeper with his comatose child}
The innkeeper comes to \Gls{GWea} with his comatose child and asks her to use her witchcraft.
\Gls{Ogg} uses the opportunity to order a hearty meal for herself and stays in their upstairs room,
while \Gls{GWea} spends the night alone with the child in the cowshed, where one of the cows is
also on the verge of death.

\subsubsection{\Gls{GWea} successfully bargains with \Gls{Death} to save the innkeeper's child}
\Gls{Greebo} returns to \Gls{Ogg}'s room in his human form, and gradually reverts to his cat form
a few hours later. Meanwhile, \Gls{GWea} challenges \Gls{Death} to a hand of poker so that she can
force him to reap the cow's soul instead of the child. He plays along, and makes a show of losing
despite having a better hand. \Gls{GWea} helps \Gls{Death} overcome his aching arm using her
chiropractic adjustment, and reminds him that he can contact her for an appointment in the future.

\subsubsection{\Gls{Perdita} runs into \Gls{Andre} after the day's practice is over}
After watching the end of practice, \Gls{Perdita} climbs the stairs behind the stage to head to
her room. She is accosted by \Gls{Andre} with his beam lantern, and wonders how he managed to cover
the distance from the stage to the staircase so quick. She excuses herself, and finds \Gls{Chris}
in her room, afraid of some mirror that seemingly talked back to her.

\subsubsection{\Gls{Perdita} takes the place of \Gls{Chris} in her bed, and listens to the man in
    the mirror}
\Gls{Perdita} takes \Gls{Chris}'s place in her room, and keeps the lights off so that she can
impersonate her friend. The intruder's voice seems to come from the full-length mirror set into the
wall, and mistakes her for \Gls{Chris}. It tells her that it can empower her singing voice to
surpass even that of \Gls{Perdita}, and promises a demonstration the next day.

\subsubsection{\Gls{HenryS}'s manager insists on maintaining his fake identity}
The next day, \Gls{HenryS} is joined in the carriage by his manager, who insists that the fat man
is the famous singer \Gls{Enrico}, and cannot speak Morporkian. \Gls{GWea} nudges \Gls{Ogg} in the
ribs until she plays along, as they wait for the manager to return to his seat on the carriage roof.
\Gls{HenryS} pleads with them afterward to not blow his cover, and \Gls{Ogg} immediately asks him if
he is a fugitive on the run.

\subsubsection{\Gls{HenryS} gives \Gls{GWea} and \Gls{Ogg} tickets to the Opera House}
\Gls{HenryS} talks about his origins as a poor kid from Ankh-Morpork, and of how he had to come up
with the persona of \Gls{Enrico} so that he would get taken seriously by the opera industry. He
hands them two tickets to the Opera House in exchange for their silence, and falls back asleep.
\Gls{GWea} thinks back to her historical hatred of theater, and wonders if the stage at the opera
has a similar ability to attract magical phenomena.

\subsubsection{\Gls{Chris} talks to \Gls{Perdita} about the strange night-time singing}
\Gls{Chris} runs into \Gls{Perdita} at the mess hall during breakfast, and shows off the new dress
that some secret admirer left for her. \Gls{Perdita} claims not to have heard any faint singing
voice at night, as she struggles to fight off her drowsiness. \Gls{Chris} decides not to investigate
any further, and goes away with her tiny meal.

\subsubsection{\Gls{Pounder} suddenly vanishes from the empty stage when he whistles}
\Gls{Plinge} notices her son missing the next morning at his cleaning duties, and notices the
Opera House rat catcher \Gls{Pounder} stroll by the stage with a large sack. Before she can remind
him to stop whistling on stage, she sees him vanished, with his sack lying on one end of the stage.
\Gls{Pounder}'s meets the \Gls{DRat} after rising from his corpse as a soul, and realizes that he
is fated to reincarnate as a rat himself.

\subsubsection{\Gls{Seldom} tries to make sense of the seemingly accidental death of \Gls{Pounder}}
\Gls{Seldom} receives a letter form the \Gls{Ghost} asking for \Gls{Chris} to be given the lead
singing role in the coming performance. He then runs out to the stage, to find workers huddled
next to the counterweight sack that is lying on the stage, with the body of \Gls{Pounder} floating
high above with strangled to death by a noose. \Gls{Salz} shows \Gls{Seldom} another letter with
written laughter, and reminds him how unprofitable it will be to shut down operations to flush out
the troublemaker.

\subsubsection{\Gls{Seldom} starts to become paranoid about the \Gls{Ghost} striking again}
When \Gls{Seldom} looks at the heavy chandelier suspended over the stage, \Gls{Salz} reassures him
that the ropes are kept in a locked room, and offers to keep watch over it on performance days.
Meanwhile, \Gls{Ogg} and \Gls{GWea} arrive at Ankh-Morpork, and ask the stage coach agent how to
get to a share-house recommended by one of \Gls{Shawn}'s brothers.

\subsubsection{\Gls{Seldom} convinces \Gls{Perdita} to lend her voice to \Gls{Chris}}
In his office, \Gls{Seldom} tries to convince \Gls{Perdita} to stand directly behind \Gls{Chris}
during the night's performance, and sing the part for her. \Gls{Perdita} agrees reluctantly, and
leaves to learn the finer details from \Gls{Unde}. \Gls{Salz} remarks on how the Opera used to be
all about the singers, and how \Gls{Perdita} might have been a superstar a few decades ago, just
because of her voice.

\subsubsection{\Gls{GWea} returns to the whorehouse in Ankh-Morpork, much to \Gls{Ogg}'s surprise}
\Gls{Ogg} is surprised when \Gls{GWea} is welcomed by the whore-house, who remember her fondly from
her earlier visit. \Gls{Perdita} impresses \Gls{Unde} with her practice session, and \Gls{Andre} the
pianist takes her out of his office to congratulate her on a remarkable first attempt. He is shocked
when \Gls{Perdita} claims to have no knowledge of the original composer, singer or meaning of the
words, and offers to meet her after breakfast to help her go over the small mistakes in her tone.

\subsubsection{\Gls{Unde} is so impressed by \Gls{Perdita}'s performance that he decides to
    fight back against \Gls{Seldom}}
\Gls{Andre} hastily apologizes for spooking \Gls{Perdita} on the stairs at night, and laughs off the
idea that he might be the \Gls{Ghost}. \Gls{Unde} decides to argue against \Gls{Seldom}'s decision
to sideline \Gls{Perdita}, and makes a wrong turn on the way to his office. He ends up in the
orchestra's practice room behind the stage, and notices most of the instruments lying smashed on the
floor.

\subsubsection{The \Gls{Ghost} kills \Gls{Unde} in the orchestra practice room}
He is killed by the \Gls{Ghost} before he can recover from the shock, and sees the murdered drag his
own corpse into the shadows. \Gls{Death} shows up to reap his soul, and reminds \Gls{Unde} that the
investigation is best left to the living. \Gls{Unde} seems to recognize the \Gls{Ghost}. Meanwhile,
\Gls{Perdita} goes out into the city to get some herbs for a potion, and recognizes \Gls{GWea} from
afar on her way back. She recalls \Gls{Chris} asking to switch back to her original bedroom for the
night, as she runs back into the Opera House.

\subsubsection{\Gls{GWea} asks \Gls{Goatb} to pay royalties for \Gls{Ogg}'s cookbook}
\Gls{GWea} takes \Gls{Ogg} to the engraver's office in Ankh-Morpork, and asks to see the \Gls{Goatb}
about the new cookbook. He produces a picture of \Gls{Ogg} that is several decades younger, and
\Gls{GWea} insists that the witch next to her is the same person as the sketch he received in the
mail. \Gls{Goatb} rejects the idea of paying royalties to \Gls{Ogg}, when he notices that she is
far less interested than \Gls{GWea} in pressing the issue.

\subsubsection{\Gls{Seldom} surveys the damage to the orchestra equipment}
\Gls{Salz} and \Gls{Seldom} inspect the orchestra room, while noticing \Gls{Unde}'s broken
spectacles in the rubble. \Gls{Salz} points out another letter from the \Gls{Ghost}, while
\Gls{Seldom} thinks about the further expense in replacing the musical instruments. Meanwhile,
\Gls{GWea} and \Gls{Ogg} make their way to the Opera House, while thinking about how anxious
\Gls{Perdita} had looked to avoid them earlier.

\subsubsection{\Gls{Ogg} and \Gls{GWea} decide to watch the night's show at the Opera House}
\Gls{Walter} pays little attention to the two witches after asking them to step aside so that he can
glue some posters to the front walls for the coming night's show. \Gls{GWea} decides to go into the
Opera House to see the show, and exchanges the premium tickets gifted by \Gls{HenryS} for worse
ones farther from the stage.

\subsubsection{\Gls{Perdita} sings for \Gls{Chris} in the night's show}
\Gls{Perdita} hears \Gls{Salz} and \Gls{Seldom} talk about \Gls{Unde} having gone missing, as she
prepares backstage for the night's show to start. Once the show starts, \Gls{GWea} notices
\Gls{Chris} moving her lips at center-stage with \Gls{Perdita}'s voice booming out. \Gls{Ogg} also
notices one of the expensive boxes being covered with a curtain, as if someone inside requires
absolute privacy.

\subsubsection{\Gls{GWea} and \Gls{Ogg} run into \Gls{Plinge} at the box seats}
\Gls{GWea} casts her mind out to look for any superhuman entities in the Opera House, and senses
the impending death of one of the audience members seated right behind her. She runs out as
\Gls{Perdita}'s segment ends, with \Gls{Ogg} struggling to keep up, and descends the stairs to the
box seats. At the corridor leading to the boxes, they run into \Gls{Plinge}, who warns them about
opening the \Gls{Ghost}'s box.

\subsubsection{\Gls{GWea} helps \Gls{Plinge} home as \Gls{Ogg} takes her place at the Opera House}
\Gls{Ogg} stays behind to take on \Gls{Plinge}'s role of serving drinks to the premium box guests,
as \Gls{GWea} volunteers to take her home. \Gls{Plinge} keeps mumbling about the \Gls{Ghost} who
used to be a harmless good-luck charm for the performers, and bemoans the recent murders it has
committed.

\subsubsection{\Gls{Perdita} sees the corpse of \Gls{Unde} descend along with the counterweights}
\Gls{Perdita} goes backstage once her singing duties end with the interval call, and notices
the corpse of \Gls{Unde} descend from one of the ropes, instead of the usual counterweight.
\Gls{Ogg} arrives backstage using a service corridor, and notices the crowd around the corpse of
\Gls{Unde}. The stage manager offers a substantial bonus to the performers in exchange for their
continued work for the night, as \Gls{Ogg} notices \Gls{Walter} sobbing over the corpse.

\subsubsection{\Gls{Ogg} tries to console \Gls{Walter} after the death of \Gls{Unde}}
\Gls{Ogg} realizes that \Gls{Walter} is a simpleton, and tells him not to worry about his mother,
since she is being escorted by someone very powerful who will keep her safe. She asks him to take
the corpse of \Gls{Unde} aside for safekeeping, and sets off to find \Gls{Perdita}. A stage-hand
tells her to look in \Gls{Salz}'s office, as \Gls{Ogg} turns around to see \Gls{Walter} missing.

\subsubsection{\Gls{GWea} and \Gls{Plinge} are saved by a mysterious swordsman in black robes}
\Gls{GWea} and \Gls{Plinge} are accosted by some thieves in the darkness as they reach her house in
the Shades district. A mysterious figure with a sword leaps down from a roof and causes enough
confusion among the thieves to get most of them stabbing their own comrades. The stranger leaves
after calling \Gls{GWea} pretty, and she starts to fumble for her first aid kit so that she can stop
the thieves bleeding to death.

\subsubsection{\Gls{Ogg} observes \Gls{Seldom} in his office after \Gls{Unde}'s body is found}
\Gls{Ogg} walks into \Gls{Seldom}'s office, where \Gls{Chris} is lying on a couch after fainting at
the sight of \Gls{Unde}'s corpse. She introduces herself as \Gls{Plinge}'s substitute, and watches
\Gls{Seldom} ask \Gls{Perdita} for her support in propping up \Gls{Chris} using her voice. She
then decides to keep her cover by washing up the dirty dishes collected from the office, and is
warned by a stagehand not to whistle.

\subsubsection{\Gls{GWea} and \Gls{Ogg} watch the rest of the performance}
\Gls{GWea} returns to the Opera House as the second act starts. \Gls{Ogg} fills her in on the
discovery of \Gls{Unde}'s body, as \Gls{GWea} thinks about how the mysterious swordsman who saved
\Gls{Plinge} matches the description of the \Gls{Ghost}. After the show ends, \Gls{Ogg} and
\Gls{GWea} stay back to see \Gls{Walter} start his mopping duties, and spot \Gls{Greebo} begging
him for some milk. \Gls{GWea} feels sad about the meager existence that \Gls{Plinge} has to lead,
given the added stress of a simpleton like \Gls{Walter} to take care of.

\subsubsection{\Gls{Perdita} runs into \Gls{Walter} on stage after the show is wrapped up for the
    night}
\Gls{Perdita} agrees to go down to ground level and get some water, when \Gls{Chris} agrees to
drink the sleeping draught mixed with milk that she has prepared. When filling the jug, she hears a
perfect singing voice from the stage, and goes there to investigate. She runs into \Gls{Walter}
holding on to \Gls{Greebo} in the darkness of the main stage, and is surprised to hear him deny
hearing any voice in the night.

\subsubsection{\Gls{Perdita} impersonates \Gls{Chris} again, as the \Gls{Ghost} makes his next
    demand}
\Gls{Perdita} returns to \Gls{Chris}'s room, and finds a small package of rose stems among the many
bouquets delivered by \Gls{Walter} after the show. The stems glow in the dark, and show ethereal
flowers, as the voice of the \Gls{Ghost} asks her to take on another singing role in the next big
show. \Gls{Perdita} is reassured by the fact that \Gls{Ghost} still thinks it is talking to
\Gls{Chris}, and confirms that the singing voice she just heard on stage was its own.

\subsubsection{\Gls{GWea} and \Gls{Ogg} threaten \Gls{Goatb} at his office}
\Gls{GWea} and \Gls{Ogg} go to \Gls{Goatb}'s office at the engraver's workshop, after reminding the
guard troll that they know his family in the Lancre mountains. \Gls{Goatb} remains defiant about
the royalty owed to \Gls{Ogg}, and \Gls{GWea} threatens him with a dire prediction of her own as to
what will befall him within the next minute.

\subsubsection{\Gls{Seldom} discusses the \Gls{Ghost}'s next demand with \Gls{Salz}}
\Gls{Seldom} receives another letter from the \Gls{Ghost} asking for \Gls{Chris} to sing another
important role, along with critique of the previous night's show. \Gls{Salz} walks in with news
that \Gls{Vimes} is sending some men undercover for the next show, and that \Gls{Unde} had been
strangled to death well before he was hung up above the stage. \Gls{Seldom} thanks \Gls{Walter} for
topping up his fireplace again, and wonders if he knows something about the \Gls{Ghost}.

\subsection{}
\subsubsection{\Gls{GWea} decides to purchase the \Gls{Ghost}'s box seat using \Gls{Ogg}'s
    royalties}
\Gls{GWea} and \Gls{Ogg} walk out of \Gls{Goatb}'s office with their payout, as guests start to
arrive at the Opera House for the night's show. \Gls{GWea} decides to purchase the ticket to the
\Gls{Ghost}'s box seat to investigate the presence, as \Gls{Ogg} realizes that her nest-egg is
about to be spent the very day she earned it.

\subsubsection{\Gls{GWea} purchases an ostentatious dress for herself, in order to pass as a
    friend of \Gls{Enrico}}
\Gls{GWea} takes \Gls{Ogg} to an upscale dress shop, and pays cash outright to purchase one of the
dresses being designed for the Duchess of Quirm. Meanwhile, \Gls{Perdita} meets with \Gls{Andre} in
the mess hall, and learns that he used to teach singing to the children of the Klatchian monarch
a few months ago, when he left to join the Opera House. He gives her some old music sheets, and she
points out how \Gls{Walter}'s name shows up as a background singer in some of them.

\subsubsection{\Gls{Andre} talks to \Gls{Perdita} about the oddities of the Opera business}
\Gls{Andre} tells \Gls{Perdita} that \Gls{Walter}'s name is used as a stand-in for performers who do
not wish to have a certain song be in their record, and laughs when she asks if the janitor has any
real singing talent. She tells him that she has had help from a private teacher and keeps to herself
the fact that it is the \Gls{Ghost} who has been helping her practice after bedtime every night.
\Gls{Walter} is scolded by the head cook for a mess he causes in the kitchen by knocking over
some crockery.

\subsubsection{\Gls{Perdita} finds the secret tunnel hidden behind \Gls{Chris}'s full length mirror}
\Gls{GWea} gets a manicure and a full makeover before heading back to her share-house to change into
the elaborate dress. \Gls{Ogg} is annoyed that a third of their royalty payout has already been
spent on this charade, as \Gls{GWea} reminds her that all of this is necessary to hoodwink the
\Gls{Ghost}. Meanwhile, \Gls{Perdita} peeks into \Gls{Chris}'s room, and notices a switch in the
frame of the mirror that makes it swing out, exposing a secret corridor.

\subsubsection{\Gls{Ogg} tells \Gls{Seldom} that \Gls{GWea} is a wealthy partron of the arts}
\Gls{Seldom} informs \Gls{Salz} that the mysterious deaths have only hyped up the Opera House and
that their coming show is sold out. \Gls{Salz} is disgusted by the city's morbid interest in death
as a spectator sport, and goes to fetch \Gls{Enrico} for a chat before the night's big performance.
Meanwhile, \Gls{Ogg} comes into the office to point out \Gls{GWea}'s fancy carriage, and introduces
her as a wealthy patron of Opera who keeps a low profile.

\subsubsection{\Gls{GWea} makes her grand entrance at \Gls{Seldom}'s office}
\Gls{GWea} strides into \Gls{Seldom}'s office, and makes a show of being \Gls{Enrico}'s good
friend. \Gls{Enrico} tries to nonverbally plead with her to keep his identity a secret, and plays
along with her story. \Gls{Seldom} dismisses \Gls{Salz}'s questions about the provenance of
\Gls{GWea}, and asks \Gls{Ogg} to hurry to the kitchen to confirm if lunch is ready.

\subsubsection{\Gls{Ogg} sets about playing a prank on \Gls{GWea}}
\Gls{Ogg} tells the cook that she can make a last minute dessert for the special lunch, and asks
her to take care of the actual meal. She pulls out her cookbook, and gets to work making an
aphrodisiac pudding that might go well with her cover story to \Gls{Seldom} stating that \Gls{GWea}
used to be a famous courtesan. Meanwhile, \Gls{Perdita} continues down along the spiral staircase
that lies at the end of the sealed-off corridor behind \Gls{Chris}'s mirror.

\subsubsection{\Gls{Enrico} finally gets his hands on some traditional Ankh-Morpork food}
\Gls{Enrico} is overjoyed to see an opportunity to taste the cuisine of Ankh-Morpork, after all the
fancy meals where he has been forced to eat foreign food to go with his fake identity. \Gls{Ogg}
acts as the server in \Gls{Seldom}'s private dining room, as \Gls{GWea} gently broaches the subject
of the \Gls{Ghost}'s traditional empty Box-seat for her own use. \Gls{Salz} and \Gls{Seldom} go off
to a corner to argue about this grave violation of Opera House tradition, as \Gls{Ogg} bemoans the
loss of her entire nest egg.

\subsubsection{\Gls{Perdita} continues on her journey through the forgotten stairwell of the Opera
    House}
\Gls{Perdita} listens to the faint voices of others in the Opera House filtering into the spiral
staircase, as it reaches the underground levels and goes from wood to stone construction. The
staircase ends in a damp basement corridor, and \Gls{Perdita} goes into the darkness with a candle
she finds on a nearby shelf, along with a matchbox nearby.

\subsubsection{\Gls{GWea} has lunch with \Gls{Enrico} and the Opera House management}
\Gls{GWea} insists on the particular Box-seat reserved for the \Gls{Ghost}, and almost breaks
character when \Gls{Seldom} recommends taking a man in with her for safety. \Gls{Seldom} and
\Gls{Salz} excuse themselves from the dining room and \Gls{Enrico} goes to sleep, as \Gls{Ogg}
comes in with some cold water. \Gls{GWea} tells her that she had already taken preventative
measures against the enchanted recipe, and learns that \Gls{Greebo} has taken to following
\Gls{Walter} around all day.

\subsubsection{\Gls{Perdita} comes to the conclusion that \Gls{Walter} is the \Gls{Ghost}}
\Gls{Walter} rescues \Gls{Perdita} in the basement corridors when she gets lost, and tells her that
he has to take on \Gls{Pounder}'s duties after the rat-catcher's death. He tells her that he last
saw the \Gls{Ghost} in the ballet school, and states that it had run away. He leads her out onto
the surface through a trapdoor behind the stage, and walks away in a hurry. She goes to the ballet
school's main hall, and is shocked to see mirrors lining every wall.

\subsubsection{\Gls{Perdita} tells \Gls{Andre} about the evidence pointing to \Gls{Walter} being
    the \Gls{Ghost}}
\Gls{Perdita} goes to the pipe organ and sees the \Gls{Libra} helping \Gls{Andre} install some
spare parts. She pulls \Gls{Andre} aside and lists her suspicions about \Gls{Walter}, who
immediately points out that all her evidence is circumstantial. He returns to the pipe organ after
indulging her hypothesis for a few minutes, and tells her not to bother \Gls{Seldom} with these
findings.

\subsubsection{\Gls{Ogg} prepares for the night's show by purchasing a suit and hat for
    \Gls{Greebo}}
\Gls{Ogg} goes to a fancy tailor and gets a formal outfit for \Gls{Greebo}, who they plan to use
as their private security when entering the \Gls{Ghost}'s Box-seat for the show. She returns to the
Opera House, where \Gls{GWea} is waiting with news of the private party that is to take place before
the show starts.

\subsubsection{\Gls{Perdita} getes annoyed at \Gls{Chris} not taking her seriously}
\Gls{Perdita} blurts out her belief that \Gls{Walter} is the \Gls{Ghost} when \Gls{Chris} comes up
to her to show off her new dress. \Gls{Chris} dismisses her idea as too far-fetched, and
\Gls{Perdita} walks off in a huff to the scenery storage room. \Gls{Chris} follows her and tries to
defend herself, just as the \Gls{Ghost} walks into the deserted room behind them.

\subsubsection{\Gls{Perdita} sees the \Gls{Ghost} and \Gls{Walter} at different places within 
seconds}
\Gls{Chris} faints reflexively, and \Gls{Perdita} tries desperately to bargain with the \Gls{Ghost},
as it draws its sword concealed in the fancy cane. \Gls{Perdita} cry for help is answered by the 
sound of a bucket being dropped, which makes the \Gls{Ghost} hastily retreat through a side wall. 
\Gls{Walter} walks in a few seconds later, wearing a server's uniform, and brings in his mop to 
clean out a nearby privy.

\subsubsection{\Gls{Greebo} is forced to morph into human form and don the formal outfit}
A minor law clerk comes to the Opera House with his mother, using the two tickets he received as a 
bonus in \Gls{Slant}'s law firm. He struggles to get his mother in the right frame of mind for the 
opera, and reminds her that it is the polar opposite of the music she enjoys in the taverns. 
Meanwhile, \Gls{Ogg} and \Gls{GWea} get \Gls{Greebo} to morph into his human shape and put on the 
formal outfit that had been purchased for him.

\subsubsection{\Gls{Ogg} deals with the watchmen sent by \Gls{Vimes} to guard against the
\Gls{Ghost}}
\Gls{GWea} walks into the party with \Gls{Greebo}, and introduces him as a minor aristocrat to 
\Gls{Seldom}. \Gls{Ogg} serves some drinks as a waiter alongside \Gls{Walter}, and ensures there is 
a glass of milk for \Gls{Greebo}. She then spots some watchmen doing a horrible job of being 
undercover, and gives them some of her homemade apple cider to keep them out of action for the 
night.

\subsubsection{\Gls{Andre} forces the \Gls{Libra} to substitute for him as organist}
The law clerk's mother points out the huge chandelier suspended above their seats, and wonders what 
safety measures the Opera House takes to stop it from falling on the guests. The \Gls{Libra} 
wonders why \Gls{Andre} paid him a large bag of peanuts in exchange for taking over the organist 
duties for the night, and is further intrigued when \Gls{Andre} tells \Gls{Salz} that he was the 
one who insisted on playing.

\subsubsection{\Gls{GWea} notices a hidden entrance into the Box-seat usually reserved for the 
\Gls{Ghost}}
\Gls{Salz} recruits all the off-duty workers as lookouts for the \Gls{Ghost}, and tells them to 
report any sightings immediately, even at the cost of interrupting the show. \Gls{GWea} gets 
\Gls{Greebo} to sit down with his snacks in the \Gls{Ghost}'s Box-seat, and inspects it for any 
secret entrances that it might be using to come and go.

\subsubsection{\Gls{Ogg} follows \Gls{Plinge} as she hurries away to warn the \Gls{Ghost}}
\Gls{Ogg} breaks the news to \Gls{Plinge} that the \Gls{Ghost}'s Box-seat has been sold to a wealthy
guest for the evening. \Gls{Plinge} is alarmed, and tries to run away after smashing a wine bottle 
on \Gls{Ogg}'s head. The impact fails to knock \Gls{Ogg} out, and she runs along after \Gls{Plinge},
confident that the woman is hiding something about the \Gls{Ghost}'s identity.

\subsubsection{\Gls{Walter} becomes the \Gls{Ghost} as the Opera starts}
\Gls{Ogg} catches up with \Gls{Plinge} and detains her, as \Gls{Walter} ambles slowly to the 
Box-seats. She tells \Gls{Plinge} that \Gls{GWea} will try to protect her son from the murder 
accusations to the extent she can. \Gls{Walter} dons the mask just as he unlocks the door to the 
Box-seat, and is startled when \Gls{GWea} locks the door behind him. He clibms out of the Box-seat 
and heads for the balcony, when she reminds him of the long distance to the floor, and \Gls{Greebo}
prepares to follow him.

\subsubsection{The \Gls{Ghost} makes a last-ditch effort to escape \Gls{GWea}}
The audience watches with bated breath as the \Gls{Ghost} leaps onto the chandelier with
\Gls{Greebo} in hot pursuit. They believe this is part of the show, when the \Gls{Libra} starts to 
play a different tune on the organ pipes, to make up for the orchestra being stunned into silence.
A while later, \Gls{Ogg} reaches the main floor, to see \Gls{Salz} triumphantly holding up a piece 
of the \Gls{Ghost}'s skull mask, and declaring \Gls{Walter} the culprit. 

\subsubsection{\Gls{Salz} gets the Opera House staff to hunt down \Gls{Walter}}
\Gls{Ogg} is intrigued by someone else claiming that the \Gls{Ghost} was spotted on the terrace, 
and wonders if \Gls{Walter} is indeed the \Gls{Ghost}'s real identity. Meanwhile, \Gls{Perdita}
tries to tell the stage-hands that the \Gls{Ghost} is not \Gls{Walter}, and is surprised to see 
them ignore her.

\subsubsection{\Gls{Greebo} distracts the Opera House staff after putting on the \Gls{Ghost}'s mask}
\Gls{GWea} stops \Gls{Walter} at the rooftops and takes off his mask. She hands it to \Gls{Greebo},
and asks him to lead away the pursuers so that \Gls{Ogg} can take care of \Gls{Walter}. \Gls{Greebo}
dons the mask, and leaps down the back of the Opera House, using the piping and window sills for 
support. He runs away down the street and leaps into a waiting carriage, as he senses his original 
cat form trying to reassert itself.

\subsubsection{\Gls{Greebo} transforms back into a cat as the mob closes in on him}
The crowd eventually catch up to \Gls{Greebo}, and fail to notice him transform into a cat in the 
darkness. By the time they gang up on his position, they find some clothes and a mask, which makes 
them believe that the \Gls{Ghost} jumped into the Ankh river to escape. \Gls{Detri} and \Gls{Nobbs}
stay back to examine the torn clothes, as something resembling a bird snatches the \Gls{Ghost}'s 
mask from their hands before flying away into the darkness. 

\subsubsection{\Gls{Walter} shows \Gls{Ogg} the secret underground hideout of the \Gls{Ghost}}
\Gls{Walter} takes \Gls{Ogg} to an underground cellar through the disused spiral staircase, and 
shows her the room full of defective props with a table in the center. \Gls{Ogg} notices writing 
equipment at the table, and reads the titles of some of the half-completed scripts. Meanwhile, 
\Gls{GWea} finds \Gls{Perdita} amidst the commotion backstage, and asks her if she really wants to 
turn away from her future as a witch in Lancre.

\subsubsection{\Gls{Ogg} sees the \Gls{Ghost}'s storeroom after convincing \Gls{Walter} to lead 
her there}
\Gls{Ogg} convinces \Gls{Walter} to lead her to the \Gls{Ghost}'s store room, and spots the sacks 
of money hidden at the end of a long tunnel. She then sees the ethereal rose stems, and wonders how 
they are supposed to grow in the darkness. Meanwhile, \Gls{GWea} breaks into \Gls{Seldom}'s office, 
and finds many discrepancies in the account books, as if someone is trying to hide their 
embezzlement. \Gls{Perdita} warns her of someone approaching, and hides behind a curtain, as 
\Gls{GWea} goes to a dark corner.

\subsubsection{\Gls{Perdita} and \Gls{GWea} run into \Gls{Andre} inside \Gls{Seldom}'s office}
\Gls{Perdita} listens to someone enter \Gls{Seldom}'s office, and stop in their tracks. She decides 
to use the element of surprise and jumps out at the intruder, tacking them to the ground. A while 
later, \Gls{Andre} identifies himself as the intruder, and asks \Gls{Perdita} to let go. \Gls{GWea}
steps out of the shadows to ask him why he is sneaking around \Gls{Seldom}'s office, and \Gls{Andre}
tells them that he is an undercover watchman.

\subsubsection{\Gls{Ogg} interrupts someone tampering with the grand chandelier of the Opera House}
\Gls{Ogg} asks \Gls{Walter} to stay put in the \Gls{Ghost}'s storeroom, and goes to the chandelier's 
suspension point to check if it has been tampered with. She finds the thick cable partly torn, 
as a figure darts away into the shadows on hearing her approach. Meanwhile, \Gls{GWea} asks 
\Gls{Andre} to think about how the \Gls{Ghost}'s mask has become central to its identity, and
proposes the idea of multiple people donning it to give each other alibis.

\subsubsection{\Gls{Ogg} and \Gls{GWea} identify \Gls{Salz} as one of the \Gls{Ghost} impersonators}
\Gls{Ogg} works out that the masked man wearing the \Gls{Ghost}'s outfit is \Gls{Salz}, and chases 
him off the top levels to the ground. She drops a sack of counterweights on him just as he is 
about to descend through a trapdoor backstage, knocking him out. \Gls{GWea} and \Gls{Perdita} run 
backstage, just as \Gls{Ogg} meets up with them. She asks \Gls{Seldom} if he had seen \Gls{Salz}
recently, and makes a plan to find him among the masked performers on stage.

\subsubsection{\Gls{Ogg} and \Gls{GWea} lead the search to unmask \Gls{Salz}}
\Gls{Ogg} joins the line of ballerinas at the start of the third act, as \Gls{GWea} gets the 
\Gls{Libra} to take over the duties of the orchestra's conductor. \Gls{Perdita} tries to enlist 
\Gls{Chris}'s help in spreading around the orders that everyone was to unmask immediately, and not 
wait for the show to end. Meanwhile, \Gls{Enrico} staggers backstage and collapses next to 
\Gls{Seldom}, mumbling something about being bashed on the head.

\subsubsection{\Gls{Salz} is found out on stage after his disguise fails}
\Gls{Salz}, who has disguised himself as \Gls{Enrico} on stage, prepares for the duet featuring
himself and \Gls{Chris} to start. \Gls{Perdita} shouts at the top of her voice for the show to stop,
just as \Gls{Chris} takes position next to him and faces the audience. Meanwhile, \Gls{GWea} goes 
to the prop room underneath the stage, and gives \Gls{Walter} the mask of the \Gls{Ghost} so that 
he can rescue the show from its interruption.

\subsubsection{\Gls{Salz} seemingly defeats \Gls{Walter} on stage}
\Gls{Salz} holds \Gls{Perdita} hostage, and is forced to duel \Gls{Walter} when he jumps onto the 
stage wearing the \Gls{Ghost}'s mask. The duel ends swiftly since \Gls{Walter} only knows how to 
mock-fight with his sword, and \Gls{Salz} crumbles the mask in his hands. \Gls{GWea} forces
\Gls{Salz} to put on his reserve mask, and makes a show of handing \Gls{Walter} an invisible mask 
that \Gls{Perdita} has verified is a fine substitute for the real one. 

\subsubsection{\Gls{Salz} dies of a heart attack after his rant about the opera}
\Gls{Salz} rants about the opera and how it is a waste of musical talent, and dies of a panic attack 
when \Gls{Walter} almost hits him in the ribs with his sword. \Gls{Perdita} points out that 
\Gls{Salz} did not actually get injured, as \Gls{Seldom} asks \Gls{GWea} for the whereabouts of the 
embezzled cash.

\subsubsection{\Gls{Seldom} thinks about pivoting the Opera House into a simple music hall}
\Gls{GWea} suggests to \Gls{Seldom} that \Gls{Walter} be given the position held by \Gls{Salz}, 
and asks him to show the \Gls{Ghost}'s hidden cache of money in the underground cellars.
\Gls{HenryS} staggers on stage, and proudly declares that he is giving up the \Gls{Enrico} persona.
The law clerk's mother happens to be his long-lost sweetheart, and reunites with him as the audience 
cheer. \Gls{Ogg} and \Gls{GWea} convince \Gls{Perdita} to let out her own anger by singing a loud 
note, and her voice causes glass to break.

\subsubsection{\Gls{GWea} and \Gls{Ogg} prepare to leave Ankh-Morpork}
\Gls{GWea} and \Gls{Ogg} wait for the carriage next morning, and wonder if \Gls{Perdita} will be 
joining them on the trip back to Lancre. \Gls{Ogg} wonders how \Gls{Walter} figured out the secret 
of raising the ethereal roses, and how \Gls{GWea} caught \Gls{Salz}'s real sword by the blade using 
her bare hands.

\subsubsection{\Gls{GWea} returns to Lancre and takes \Gls{Perdita} under her wing}
\Gls{Greebo} jumps into the carriage at the last minute, and \Gls{GWea} gets back to her cottage to 
prepare for the sword cut in her palm. She lets the cut happen after assembling the bandages and 
ointment necessary to patch it up. \Gls{Perdita} returns to Lancre, and \Gls{GWea} is happy to offer 
her the job of junior witch, including the right to use \Gls{Magrat}'s old cottage.