\section{Men at Arms}


\subsection{}
\subsubsection{\Gls{Carrot} is promoted within the City Watch}
\Gls{Carrot}, now promoted to Corporal, writes a letter to his parents, informing them of the
aftermath of \Gls{Vimes} saving the city. He tells them that \Gls{Vimes} has elected to quit the
City Watch, to get married to \Gls{Ramkin}, and that the Watch is set to expand per the patrician's
orders.

\subsubsection{\Gls{Edward} completes the advanced course in assassination at the Guild}
\Gls{Edward}, son of a minor noble in Ankh-Morpork, buries his father using the little money left
to him, and enrolls for the advanced course in the Guild of Assassins, passing it with flying
colors. He spends too much time in the Guild Library, becoming well acquainted with every single
king and queen of the city, and is alarmed to find \Gls{Carrot} strolling past him one day, bearing
a strong resemblance to one of the long dead kings.

\subsubsection{\Gls{LRust} questions \Gls{Edward}'s plan to reinstate \Gls{Carrot} as the king}
After spending some time searching the ruins of the caravan where \Gls{Carrot} had been found by his
dwarven parents, \Gls{Edward} finds a signet ring, and shows it to some aristocrats assembled in
his home, along with portraits of past kings bearing a resemblance to \Gls{Carrot}. \Gls{LRust},
who has adapted better to the end of monarchy, asks \Gls{Edward} if the city requires a new king at
the moment.

\subsubsection{\Gls{Edward} tries and fails to enlist the other aristocrats to his cause}
\Gls{Edward}, seduced by the history books glorifying the monarchy of old, tries to tell the
gathered nobles that the power that used to belong to the noble houses, now belongs to the guilds,
populated by the common-folk and lowborn. \Gls{Edward} is exasperated to see them disagree with his
ideas, and take the pragmatic route ahead, by cooperating with \Gls{Vetina} and his reforms.

\subsubsection{\Gls{Vimes} is asked about his eventual successor as he prepares to resign}
\Gls{Edward} decides not to let the matter rest, as he falls asleep and has vivid dreams about
reestablishing the monarchy. Meanwhile, \Gls{Vimes} waits in \Gls{Vetina}'s chamber to tender his
resignation, and prepare for the leisurely life of a nobleman, married to \Gls{Ramkin}. He thinks
about promoting Sergeant \Gls{Colon} as his successor, and shivers at the thought.

\subsubsection{\Gls{Vimes} and \Gls{Vetina} talk about the Captaincy of the Night Watch}
\Gls{Colon} tries to teach the new recruits to salute, as he tries to hide his amusement at the
new policies requiring diversity in the force. Meanwhile, \Gls{Vetina} asks \Gls{Vimes} for his
opinion on elevating \Gls{Carrot} to the rank of Captain, keeping the knowledge of his royal
heritage to himself.

\subsubsection{\Gls{Carrot} trains the new female recruit \Gls{Angua}}
\Gls{Carrot} shows the new female recruit \Gls{Angua} around the city gates, and is alarmed to see
a shopkeeper chasing an unregistered thief. \Gls{Carrot} tells her about the new recruitment
policies, and is amused to see her annoyance at the blatant tokenism of Captain \Gls{Vimes}. They
use some shortcuts to catch the thief, and drag him to the Watch House, hoping to keep him safe from
the Thieves' Guild.

\subsubsection{\Gls{Vimes} visits \Gls{Ramkin} at her sanctuary for swamp dragons}
\Gls{Vimes} returns to the swamp dragon sanctuary now run by \Gls{Ramkin}, just in time to see a
sick dragon explode as its indigestion reaches a critical state. She tells him to prepare for the
elaborate reception the next night, where he would meet the aristocracy, and get to practice his
manners amongst her peers.

\subsubsection{\Gls{Carrot} insists on the new recruits taking an oath of office}
\Gls{Colon} supervises the new recruits, including the troll \Gls{Detri}, and a dwarf named
\Gls{Cuddy}, as \Gls{Carrot} tries to recall the oath of office he had read about in the rule-book
of Ankh-Morpork. The three recruits stumble through the oath, as \Gls{Colon} tells them that
\Gls{Vimes} is busy preparing for his retirement.

\subsubsection{\Gls{Colon} sends \Gls{Carrot} out to negotiate with the two contingents}
\Gls{Colon} tries not to use the usual slurs when describing the marches underway by both the
trolls and the dwarfs, who bear an ages-old vendetta towards each other. \Gls{Colon} decides to let
\Gls{Carrot} deal with the two contingents marching towards each other, as he tells \Gls{Angua}
about his irresistible charisma when it comes to conflict-resolution.

\subsubsection{\Gls{Carrot} manages to stop a race riot between the dwarves and the trolls}
\Gls{Carrot} manages to placate the troll and dwarf contingents, even as \Gls{Cuddy} gets into a
fight with \Gls{Detri}, eventually leading to them knocking each other out. \Gls{Carrot} gets the
two groups to put surrender their weapons and return home, as \Gls{Angua} wonders how he commands so
much respect from the citizens.

\subsubsection{\Gls{Vimes} is hit by the shockwave of a huge explosion}
\Gls{Vimes} visits \Gls{Ramkin}'s family lawyer, who is a vampire in their service for many
centuries, and learns of the full extent of her holdings. He is alarmed by the mention of
inheritance laws, and starts to think about the possibility of having children with \Gls{Ramkin},
as a massive explosion knocks out the windows of the Watch House, showering him in glass shards.

\subsubsection{\Gls{Angua} follows a mongrel at the Assassins' Guild House down an alley}
As \Gls{Vimes} tries to barge through the assassins guarding the entrance to their flaming Guild
House, \Gls{Angua} slinks away in pursuit of a mongrel watching them intently from a dark alley. The
dog tells her that it caught intelligence as a result of sleeping next to the High Energy Magic
building at the university one night, and reminds her that her scent still marks her as non-human.

\subsubsection{\Gls{Vimes} talks to \Gls{Cruces} about the accident at his Guild House}
The dog, introducing itself as \Gls{Gaspode}, demands some food in exchange for information.
Meanwhile, \Gls{Vimes} feels like the explosion is the tip of the iceberg, as the Master Assassin
\Gls{Cruces} emerges from the building. He shows \Gls{Cruces} a letter from \Gls{Ramkin}'s lawyer
stating that the Guild House was her ancestral property. Suppressing his annoyance, \Gls{Cruces}
simply blames fireworks misfiring for the massive hole in the wall of the Guild House.

\subsubsection{\Gls{Gaspode} reveals \Gls{Edward}'s plan to \Gls{Angua}}
\Gls{Gaspode} tells \Gls{Angua} that it had spotted someone use a swamp dragon's suicidal explosion
to blow a hole in the Assassins' Guild House, and sneak in dressed in their black robes, as if to
blend in with the other assassins in the confusion. Meanwhile, \Gls{Cruces} seems to convince
\Gls{Vimes} with his story about the fireworks malfunction, and insists that nothing has been stolen
from the Guild's storeroom.

\subsubsection{\Gls{Cruces} orders an exhaustive shakedown of every Guild member in the House}
In his chamber, \Gls{Cruces} tells his inner council to organize a search of all the valuables in
the Guild, as well as a roll-call to ensure that no one had gone in or out of the Guild House since
the explosion. He dreads having to inform \Gls{Vetina} about the incident, as he sets off to the
palace.

\subsubsection{\Gls{Vimes} points out the gaps in the excuse given by \Gls{Cruces}}
\Gls{Vimes} and the Watch return to their headquarters, as \Gls{Cuddy} remarks on the absence of
any sulphur smell. \Gls{Vimes} recalls the smell of swamp dragons, and believes that one of them
might have been used to breach the wall. \Gls{Angua}, who has now adopted \Gls{Gaspode}, agrees with
his theory, while passing off her confidence as woman's intuition.

\subsection{}

\subsubsection{\Gls{Vimes} and \Gls{Carrot} find evidence of the swamp dragon explosion}
\Gls{Vimes} sets off on patrol with \Gls{Carrot}, and rambles on about the end of the monarchy,
triggered by the erstwhile captain of the City Watch \Gls{Stonef}, dragging the king out to the
city square and having him executed. \Gls{Gaspode} catches up to them, and points out the burnt
collar lying on top of a gargoyle nearby. \Gls{Vimes} reads the name of the dragon that \Gls{Ramkin}
had asked him to find, and realizes that \Gls{Angua}'s guess is correct.

\subsubsection{\Gls{Cruces} meets with \Gls{Vetina} in the palace}
\Gls{Cruces} visits \Gls{Vetina} in the palace gardens, only to find that he already knows about the
missing artifact, which the last Master Assassin had been entrusted with. He asks \Gls{Vetina} to
call off \Gls{Vimes}, believing himself to be the person best suited to tracking down the intruder
and retrieving the missing item.

\subsubsection{\Gls{Edward} disposes of \Gls{BHam}'s corpse after he finishes the prototype gun}
The dwarven blacksmith \Gls{BHam} finishes designing \Gls{Edward}'s prototype revolver, and promptly
dies when it misfires. \Gls{Death} reminds him that he will be reincarnated in accordance with his
beliefs, as \Gls{Edward} drags his body away to be tossed into the Ankh river.

\subsubsection{\Gls{Colon} struggles with truncheon training for the new recruits}
\Gls{Colon} trains the recruits in the use of their official truncheon, and tries to tell
\Gls{Detri} that the suspect was supposed to be left capable of answering questions after being
apprehended. Meanwhile, \Gls{Vimes} asks \Gls{Ramkin} how the swamp dragon might have exploded at
the Assassins' Guild House, and she tells him about the mating rituals involving males posturing
against each other.

\subsubsection{\Gls{Carrot} and \Gls{Vimes} work out how the explosion was triggered}
When \Gls{Carrot}'s shiny armour provokes a male swamp dragon into rearing up its neck to breathe
fire, \Gls{Vimes} makes the connection that the arsonist likely used a mirror to make the other
swamp dragon explode, as it tried to compete against its own reflection. \Gls{Cuddy} takes offense
at \Gls{Colon}'s offhand racism, and destroys the archery dummy with his war-axe. \Gls{Angua}
suggests an evening out drinking to calm the others down, just as \Gls{Cuddy} recognizes the corpse
of \Gls{BHam} floating down the Ankh river.

\subsubsection{\Gls{Vimes} falls for \Gls{Vetina}'s game}
\Gls{Vimes} visits \Gls{Vetina}'s office with news of \Gls{BHam}'s body being fished out of the
river, only to be chastised for his inquisitiveness. \Gls{Vetina} asks him to lay off the Assassins'
Guild issue, and to hand over the search for \Gls{BHam}'s killer to Captain \Gls{Quirke} of the
Day Watch. \Gls{Vimes} storms off in a huff, leaving \Gls{Vetina} pleased at how easily his
reverse psychology works.

\subsubsection{\Gls{Carrot} and the other guards talk about the murder of \Gls{BHam}}
The Night Watch visit a police bar, and get some drinks for themselves, as well as \Gls{Gaspode},
who insists on following \Gls{Angua} around at all times. They talk about investigating the death of
\Gls{BHam}, as \Gls{Angua} tries to slink back home for the night. \Gls{Carrot} insists on
accompanying her, and makes small talk about why she joined the Watch. \Gls{Nobby} spots a card
stuck to his shoe, with some faded lettering written on it.

\subsubsection{\Gls{Angua} transforms into a werewolf, just as \Gls{Carrot} bids her goodnight}
\Gls{Angua} takes her leave of \Gls{Carrot}, rebuffing his attempts to spend time with her outside
of work. She makes it in time to a dark alley for the werewolf transformation to occur, and runs off
into the darkness. Meanwhile, \Gls{Vimes} struggles to get ready in time to face the banquet thrown
by \Gls{Ramkin} in honour of their wedding.

\subsubsection{\Gls{Gaspode} and \Gls{Angua} follow the scent trails at \Gls{BHam}'s workshop}
\Gls{Gaspode} accompanies \Gls{Angua}, as she decides to use her superhuman senses to sniff around
the workshop of \Gls{BHam}. \Gls{Gaspode} talks about \Gls{BigFido} and the Dogs' Guild, which
polices all activity related to stray dogs plying the city streets at night. They spot \Gls{Carrot}
strolling past, as he recognizes \Gls{Gaspode} while searching for a biscuit to offer them.

\subsubsection{\Gls{Vimes} tries to blend in with high society at the banquet}
\Gls{Vimes} joins in the conversation at the banquet, as the assembled aristocrats talk ill of the
troll and dwarf enclaves taking root in the city. \Gls{Ramkin} is annoyed by his excessive drinking,
just as \Gls{Carrot} barges in, with news of a recent crime. \Gls{Cruces}, who is among the nobles
invited to dinner, remains impassive as \Gls{Vimes} steps out of the manor to talk to \Gls{Carrot}.

\subsubsection{\Gls{Vimes} and \Gls{Carrot} head to \Gls{BHam}'s workshop}
\Gls{Ramkin} asks \Gls{Vimes} about his bad manners at the dinner-table, and he salvages it by
talking about the investigation into her swamp dragon that had exploded earlier. He decides to take
\Gls{Carrot} along with him to \Gls{BHam}'s workshop, hoping to poke around inside the place.

\subsubsection{\Gls{Vimes} finds some clues within \Gls{BHam}'s workshop}
After much negotiating, \Gls{Carrot} manages to persuade the dwarves into opening the workshop,
as \Gls{Vimes} looks around at the half-assembled weapons inside. \Gls{Carrot} spots a dent in the
wall, with cracks all around it, with \Gls{Vimes} commenting on the strong smell of fireworks.
\Gls{Vimes} pockets the lead disc buried deep inside the wall, a note with alchemist recipes, as
well as some strands of long red fiber stuck to the door.

\subsubsection{\Gls{Colon} sends \Gls{Detri} and \Gls{Cuddy} to the Alchemists' Guild}
\Gls{Carrot} leaves a note for \Gls{Colon} along with the corpse of \Gls{Beano} that \Gls{Vimes}
spots stuck to a bridge pillar across the Ankh. \Gls{Colon} is tasked with surrendering the corpse
to the Fools' Guild, and asking the Alchemists' Guild what recipes were scribbled on the paper.
He delegates the task to \Gls{Cuddy} and \Gls{Detri}, choosing not to visit the Alchemist Guild
House, which had a track record of exploding every month.

\subsubsection{\Gls{Silfish} talks about \Gls{LeoQ} being the author of the recipe sheet}
At the Alchemists' Guild, the secretary \Gls{Sendi} looks at the piece of paper in \Gls{Cuddy}'s
hands, as \Gls{Detri} follows the two of them into the Guild House. The chief alchemist
\Gls{Silfish}, busy with his alchemical ivory for billiard balls, immediately identifies the
recipes as the work of \Gls{LeoQ}, a famed polymath who was registered with many Guilds.

\subsection{}
\subsubsection{\Gls{Cuddy} learns about \Gls{LeoQ} from \Gls{Silfish}}
\Gls{Cuddy} is amused by the tales of \Gls{LeoQ}, and his proclivity for tinkering with mechanisms
far beyond the understanding of any other alchemists. They talk about leaving the magic to the
Wizards, and get back to their ivory experiments, as \Gls{Cuddy} tries to read the inscription
written in reverse on the sheet of paper.

\subsubsection{\Gls{Whitef} stonewalls \Gls{Colon}'s investigation into \Gls{Beano}'s murder}
At the Fools' Guild, the clown \Gls{Boffo} greets \Gls{Colon} and \Gls{Nobby}, and escorts them into
the central courtyard, where a funeral is being held for \Gls{Beano}. The Guild Master \Gls{Whitef}
joins them afterward, insisting on letting the Guild handle the investigation. \Gls{Boffo} recalls
\Gls{Beano} acting odd on the morning of his murder, as he takes the two of them to a side gate, on
\Gls{Whitef}'s orders.

\subsubsection{\Gls{Colon} finds something off about \Gls{Boffo}'s recounting of events}
\Gls{Colon} comments on the age of \Gls{Beano}'s corpse, and of how \Gls{Boffo} had claimed to see
him exit the Fools' Guild well after his supposed time of death. \Gls{Edward} decides to deal with
the meddling of \Gls{Vimes} by using his new revolver again, in spite of the trouble that might
follow.

\subsubsection{\Gls{Angua} agrees to go out with \Gls{Carrot} for lunch}
\Gls{Cake} asks \Gls{Angua} if she has morphed back to human form, as she enters her room, and
informs her about \Gls{Carrot} waiting at the front door. \Gls{Angua} dresses up, and decides to
accompany \Gls{Carrot} around the city for the afternoon, with \Gls{Gaspode} following along, trying
to hide its amusement at her being vegetarian.

\subsubsection{\Gls{Vimes} escapes an attempt on his life}
\Gls{Vimes} gets shot at by a mysterious man on the roof of the building across the street, as he
relaxes in his office at the Watch House. He manages to prop his helmet on a stick, and use it as a
decoy from behind a table, as he rushes out the rear entrance into the city streets. He believes
the weapon to be some sort of troll-sized crossbow designed to deliver small lumps of lead.

\subsubsection{\Gls{Vimes} investigates the opera roof from where he was shot at}
\Gls{Vimes} eventually reaches the roof of the opera house opposite the Watch headquarters, and
finds a clear line of sight into his office. He asks a stone gargoyle if it had seen anyone come up
to the roof, and it tells him that a stranger with a firework stick had been up there a while ago.
\Gls{Vimes} realizes that the weapon used to kill him was like a wizard's staff, but mechanical.

\subsubsection{\Gls{Carrot} and \Gls{Angua} happen upon another gunshot victim}
\Gls{Carrot} gives \Gls{Angua} a tour of the city at noon, and they eventually reach the Beggars'
Guild. When a beggar named \Gls{CMich} opens the door, \Gls{Angua} immediately smells fresh blood,
and insists \Gls{Carrot} investigate the commotion inside. \Gls{Carrot} uses some string to find
the line of sight through a window, and discovers that someone from the opera house roof must have
killed the beggar in the Guild House.

\subsubsection{\Gls{QMolly}'s maid is killed in her room, while trying on her ceremonial gown}
\Gls{QMolly}, the head of the Beggars' Guild, barges into the room, just as \Gls{Carrot} manages to
work out the motive for the murder. He surmises that the beggar who died was \Gls{QMolly}'s maid,
and was tempted into trying out one of the velvet gowns reserved for the Guildmaster. The gunman
had shot at the right dress in the right room, without bothering to check the identity of the
victim.

\subsubsection{\Gls{Cuddy} and \Gls{Detri} find a suspicious person running away from them}
\Gls{Cuddy} tries to teach \Gls{Detri} to count, when he realizes that their native system is binary
instead of decimal. Meanwhile, \Gls{Vimes} wakes up from an exhausted sleep, to find \Gls{Colon}
submitting a report of his findings at the Fools' Guild. A while later, \Gls{Vimes} orders a big
meal for himself at his regular restaurant. \Gls{Cuddy} and \Gls{Detri} spot someone running past
them and give chase out of instinct.

\subsubsection{\Gls{Vimes} tries to piece together the three murders}
\Gls{Vimes} reads the reports submitted by \Gls{Cuddy} and \Gls{Colon} over his meal, and tries to
make sense of the mysterious new weapon showing up in each of the three crimes. He realizes that the
Assassins' Guild might not like guns interfering with their livelihood, and might therefore keep
the diagrams of \Gls{LeoQ} under lock and key.

\subsubsection{\Gls{Cuddy} and \Gls{Detri} follow the suspect into a meat storage warehouse}
\Gls{Cuddy} hears the metallic sounds of a gun being cocked, and realizes they might have followed
the mysterious man into an ambush. \Gls{Detri} recalls a stick in the suspect's arms, as he chases
him into a dead end. They find the rear entrance to a pork storage facility, which is very cold
because of the intense magical field saturating the place.

\subsubsection{\Gls{Vimes} narrowly avoids being dismissed by \Gls{Vetina}}
The suspect fires the mysterious weapon, with all the projectiles hitting \Gls{Detri} in his armour.
He runs out of the warehouse in the confusion, shutting the door behind him. \Gls{Vimes} is summoned
by \Gls{Vetina} to his office, and warned once again not to involve himself in the recent murders.
\Gls{Vimes} pleads with \Gls{Vetina} not to have his badge taken away, and is told to surrender his
sword, and put the entire Night Watch on leave till his wedding.

\subsubsection{\Gls{Cuddy} sets off to find the keys to the pork warehouse}
\Gls{Detri} starts to think at an advanced level as his brain enters a superconducting state in the
extreme cold. He throws \Gls{Cuddy} out of a small window, after telling him to fetch \Gls{Vimes}
or \Gls{Carrot} once he got recovers at the Watch House. \Gls{Cuddy} lands on \Gls{Dibbl}'s cart
as he breaks the warehouse window on his arcing trajectory. \Gls{Dibbl} tells him that the Butchers'
Guild controls access to the pork warehouse.

\subsubsection{\Gls{Vetina} talks to \Gls{LeoQ} in the palace dungeon}
\Gls{Vetina} goes to the dungeon underneath the palace, where he is keeping \Gls{LeoQ} under house
arrest. He tells him that the gun blueprint has escaped into the city, with \Gls{LeoQ} reminding
him that the Assassins' Guild were supposed to destroy it. \Gls{LeoQ} laments his decision not to
destroy the prototype gun, and is surprised when \Gls{Vetina} tells him that the Night Watch is on
the case.

\subsubsection{\Gls{Vetina} tells \Gls{LeoQ} that the gun might be duplicated soon}
\Gls{Vetina} tells \Gls{LeoQ} that some enterprising minds in the city might be duplicating the
gun prototype quickly, once a model was available to work with. \Gls{LeoQ} talks about his grand
plan of powered flight, and remarks on the lack of a power source to turn the rotors fast enough.
Meanwhile, \Gls{Detri} works on number theory and calculus as the temperature drops close to the
point of killing him.

\subsubsection{\Gls{Cuddy} rescues \Gls{Detri} from the pork warehouse}
At the Butchers' Guild, \Gls{Cuddy} threatens the Guildmaster \Gls{GSock} with his war-axe, asking
for the key to the pork warehouse. \Gls{Cuddy} finds complex mathematics etched into the frost
lining the walls of the warehouse, as \Gls{Detri} is hauled out onto the street, where the heat
slows down his brain again.

\subsubsection{\Gls{Cuddy} seeks treatment for the gunshot wounds on \Gls{Detri}}
\Gls{Cuddy} takes \Gls{Detri} to the troll enclave, as he is warned about racial tensions flaring up
at the sight of a dwarf strutting through their streets. Meanwhile, \Gls{Carrot} and \Gls{Angua}
haul \Gls{Vimes} back to the Watch House, after the barkeeper tells them about \Gls{Vimes}
overdosing on alcohol.

\subsubsection{\Gls{Cuddy} and \Gls{Detri} try to escape the trolls and dwarves}
\Gls{Cuddy} and \Gls{Detri} are caught in a standoff between the trolls and a dwarf contingent led
by \Gls{BStrong}, claiming that \Gls{BHam} was murdered by another troll. They manage to escape the
race riot by fleeing down an alley, and are surprised to see both groups give chase. Meanwhile,
\Gls{Nobby} gets some Klatchian coffee to help sober up \Gls{Vimes}, who is blackout drunk.

\subsubsection{\Gls{Cuddy} and \Gls{Detri} trek through the old tunnels under the city}
\Gls{Angua} is surprised to see \Gls{Vimes} supporting the widows of the Night Watch, spending a
majority of his salary on keeping them afloat. \Gls{Cuddy} and \Gls{Detri} realize they are in
some tunnels deep within the city, after falling into a pit. They find inscriptions dating the
tunnels back many thousands of years ago, and find a fresh pair of footprints on the ground.

\subsubsection{\Gls{Cuddy} and \Gls{Detri} find something hidden by the suspect deep in the tunnels}
\Gls{Carrot} finds \Gls{Vimes} clutching his badge so hard that his hands it cuts through his palm.
Meanwhile, \Gls{Cuddy} and \Gls{Detri} find something left by the suspect at a dead end in the
tunnels, and decide to bring the others in to inspect it. They surmise that the lighter footsteps
leading away from the dead end should inevitably come to exit in the tunnel system.

\subsection{}
\subsubsection{\Gls{Vimes} learns about the murder being framed on \Gls{Coalf} the troll}
\Gls{Vimes} comes to his senses and learns that \Gls{Quirke} has closed the case by framing
\Gls{Coalf} for the murder of \Gls{BHam}. \Gls{Colon} echoes \Gls{Vetina}'s sentiment that
\Gls{Coalf} must be guilty of one crime or another, since he was a head enforcer for the troll
mafia.

\subsubsection{\Gls{Vimes} faces off against \Gls{Quirke} at the Watch House}
As \Gls{Vimes} expresses his disdain for \Gls{Vetina}'s idea of justice and policing, \Gls{Quirke}
barges into the Guard House, asking the Night Watch to surrender their service weapons, and
wondering if \Gls{Cuddy} and \Gls{Detri} are participating in the race riots brewing in the troll
enclave. Meanwhile, the two of them navigate the underground tunnels, finding a massive hall with
collapsed tunnels leading off from it.

\subsubsection{\Gls{Gaspode} persuades \Gls{Quirke} to leave the Watch House}
\Gls{Angua} notices \Gls{Gaspode} sneaking into the Watch House office, only to be kicked by
\Gls{Quirke}, and run yelping to her. \Gls{Gaspode} uses his powers of subliminal suggestion to
convince \Gls{Quirke} that he has haemorrhoids, causing him to hurry out of the Watch House with his
men, after reminding them that the Night Watch was likely to be dissolved in the near future.

\subsubsection{\Gls{Detri} and \Gls{Vimes} dig beneath the University Library}
\Gls{Detri} and \Gls{Vimes} dig their way out of the tunnel network, with the \Gls{Libra} amused
by their voices reaching him from underneath the University Library. Meanwhile, \Gls{Vimes} trudges
into \Gls{Ramkin}'s dragon-pen, declaring his intent to stand down from his duties for the last day
of his job.

\subsubsection{\Gls{Carrot} and the other Watchmen talk about the possibility of riots}
\Gls{Carrot} talks to \Gls{Nobby} about the increasing racial tensions in the city, with the Watch
being blamed for the death of \Gls{BHam}, and the subsequent arrest of \Gls{Coalf}. The \Gls{Libra}
drags \Gls{Cuddy} and \Gls{Detri} into the Watch House, angry at the desecration of his Library.
\Gls{Carrot} chooses to go with \Gls{Cuddy} and \Gls{Detri} to check out the corpse they found in
the tunnels.

\subsubsection{\Gls{Carrot} and the \Gls{Libra} also see the corpse of \Gls{Beano}}
\Gls{Carrot} is delighted to explore the tunnel system he had read of in the history books
describing in its age of kings. \Gls{Cuddy} and \Gls{Detri} eventually lead him to the corpse of
\Gls{Beano}, and decide to keep the discovery a secret from the other Watchmen. Once they return to
the Watch House, \Gls{Nobby} starts discussing the idea of kings and autocrats, as \Gls{Carrot}
reveals the pocket-watch he had purchased for \Gls{Vimes}' retirement.

\subsubsection{\Gls{Carrot} decides to help the Day Watch hunkered down in the palace}
A member of the Day Watch runs into the Watch House, to report the trolls sieging the palace,
protesting the release of \Gls{Coalf}. \Gls{Carrot} recalls the law that approves the formation of
voluntary militia in times of dire need, and asks the rest of the Night Watch to accompany him to
the palace.

\subsubsection{\Gls{Nobby} reveals his past as a corrupt quartermaster in Pseudopolis}
\Gls{Nobby} uses his experience as a quartermaster in Pseudopolis to con the Ankh-Morpork armourer
into letting them in for a surprise inspection. Once inside, he marvels at the esoteric weapons
confiscated from the various invaders, as \Gls{Carrot} politely asks the armourer to issue them some
weapons. \Gls{Detri} commandeers the two trolls working in the armoury to march with them to the
palace, after picking up a siege bow for himself.

\subsubsection{\Gls{Carrot} talks to \Gls{Whitef} about \Gls{Beano}'s exploits}
\Gls{Carrot} leads the militia to the Guild Houses, intending to ask \Gls{Whitef} at the Fools'
Guild about the circumstances of \Gls{Beano}'s death. \Gls{Whitef} falls for \Gls{Carrot}'s bluff
about orders from high up demanding the truth be squeezed out at any cost, and describes the hole in
the wall that connected their own Guild House to the Assassins' Guild next door.

\subsubsection{\Gls{Carrot} investigates the hole in \Gls{Beano}'s room}
\Gls{Carrot} sees the hole in \Gls{Beano}'s room, leading directly to the Assassins' Guild.
\Gls{Whitef} believes that \Gls{Beano} made the hole as an elaborate prank, and refutes the
possibility that someone from the other side might have dug it instead. \Gls{Carrot} starts to
suspect the Fools of lying, as he asks to be shown around their Guild museum.

\subsubsection{\Gls{Carrot} and \Gls{Angua} learn about the Clown etiquette}
\Gls{Carrot} gets the other Watchmen to repeat the lie that \Gls{Beano}'s death is a closed case,
reassuring \Gls{Whitef} that there is nothing wrong to with a guided tour of their museum. Inside
the Hall of Faces, \Gls{Boffo} tells him that a clown's face was his identity, and refuses to
entertain the idea that one clown might take on another's makeup, in violation of Guild rules.

\subsubsection{\Gls{Carrot} connects the dots between the mastermind and \Gls{Beano}}
\Gls{Carrot} works out the circumstances of \Gls{Beano}'s murder, believing that whoever was in the
Assassins' Guild next to \Gls{Beano}'s room probably befriended him in order to guarantee an escape
route after stealing the artifact. \Gls{Boffo} had simply assumed that the mastermind was
\Gls{Beano} upon seeing the makeup on his face, without realizing that an Assassin might have been
impersonating the dead clown.

\subsubsection{\Gls{Angua} decides to infiltrate the Assassins' Guild House in her animal form}
\Gls{Angua} takes her leave of \Gls{Carrot} just in time for the full moon to rise, and runs along
with \Gls{Gaspode} to the Assassins' Guild, now morphed into a werewolf. Meanwhile, \Gls{Edward}
gets to work casting the next set of bullets, as the gun starts to whisper to him in his
hallucinations. \Gls{Angua} blends in with the other pet dogs brought in by the Assassins as a
great commotion overwhelms their Guild House.

\subsubsection{\Gls{Angua} and \Gls{Gaspode} peer into \Gls{Edward}'s room in the Guild House}
\Gls{Angua} notices \Gls{Cruces} breaking open the sealed room connected to \Gls{Beano}'s, and
put a bounty on the rogue assassin's head, with his lieutenant Lord \Gls{Downey} marshalling the
search party. \Gls{Angua} looks at the room of \Gls{Edward} within the Guild House, now forced
open by the assassins, and catches the scent of the gun in the corridors. She returns with
\Gls{Gaspode} to the alley with her uniform, only to find it stolen.

\subsubsection{\Gls{Carrot} leads the militia to the palace, where \Gls{Coalf} is unjustly held}
\Gls{Carrot} and the militia reach the palace, to see a large protest happening outside of it. He
finds some dwarves and trolls, in an attempt to recruit them into his militia, using the tension
between the two factions to induce them into signing up. \Gls{Carrot} knocks out \Gls{Quirke} when
he comes out of the Day Watch headquarters to investigate, and asks the rest of his men to free
\Gls{Coalf}.

\subsubsection{\Gls{Angua} and \Gls{Gaspode} are detained by the Dogs' Guild}
\Gls{Detri} almost causes a race riot to break out with his offhand insult to the dwarves, but
the atmosphere remains calm under \Gls{Carrot}'s influence. Meanwhile, \Gls{Angua} and \Gls{Gaspode}
are captured by \Gls{BigFido}'s dogs as they stumble into the Shades district in pursuit of the
stolen uniform.

\subsubsection{\Gls{Carrot} gets \Gls{Coalf} to join the Night Watch to escape the wrath of the
    dwarves}
\Gls{Carrot} manages to bypass the rising tensions by enlisting \Gls{Coalf} into the Night Watch,
as the rest of the protesters disperse. \Gls{BStrong} asks \Gls{Carrot} to find the real culprit as
soon as possible, so that he has an answer to give the belligerents within the dwarf enclave.
\Gls{Colon} marvels at the gambit \Gls{Carrot} made in disposing of \Gls{Quirke}, and of trusting
in the authority of the Night Watch.

\subsubsection{\Gls{Angua} and \Gls{Gaspode} get away from the Dogs' Guild meeting}
\Gls{Angua} manages to sneak out of the Dogs' Guild after \Gls{BigFido} finishes his deranged speech
about the superiority of the canine race, and his dream of going back to the wolf-packs of a time
before humans had domesticated them. \Gls{Angua} decides to return to the Watch House, hoping to
find a some armour or spare clothing for herself before the night ends.

\subsubsection{\Gls{Angua} learns about the corpse of \Gls{Edward} from \Gls{Carrot}}
\Gls{Angua} finds new recruits volunteering for the expanded Night Watch, with \Gls{Colon} enlisting
them formally using his clipboard. She finds a blanket in \Gls{Carrot}'s room and rapes it on
herself, just as he gets back from the palace. She tells him about her findings in the Assassins'
Guild, and is alarmed when he reveals the corpse of \Gls{Edward} abandoned in the tunnel system.

\subsection{}
\subsubsection{\Gls{Carrot} kisses \Gls{Angua} at the suggestion of \Gls{Gaspode}}
\Gls{Carrot} is satisfied with his idea of using dwarf and troll militias to quell racial tensions
in the city, as \Gls{Gaspode} suggests kissing \Gls{Angua}. She kicks \Gls{Gaspode} out of the room,
realizing that she could save the revelation of her werewolf form for another day. Many hours later,
\Gls{Carrot} opens the window to let in moonlight onto the bed where \Gls{Angua} is still asleep,
as the mysterious gunman ascends the Tower of Art.

\subsubsection{\Gls{Carrot} is alarmed by \Gls{Angua}'s transformation}
\Gls{Carrot} realizes that the sight of him reaching for his sword out of instinct scared off
\Gls{Angua}, as she crashes through the window and runs off into the darkness. He then asks
\Gls{Gaspode} to follow her trail, after realizing that the dog can really talk, and was not
telepathically suggesting things to him.

\subsubsection{The gunman stalks his prey from the top of the Tower of Art}
The mysterious gunman thinks about the naivete of \Gls{Edward}'s plan involving the disposal of
every Guildmaster, leading to chaos in the city and the rising need for an autocratic ruler. He
waits with his gun ready at the top of the Tower of Art, for his next target. The next morning,
\Gls{Colon} informs \Gls{Detri} and the new recruits about attending the wedding of \Gls{Vimes} in
their ceremonial uniforms.

\subsubsection{\Gls{Colon} oversees the honor guard for \Gls{Vimes} and \Gls{Ramkin}'s wedding}
\Gls{Colon} is amused by the cooling fans installed on the helmet that \Gls{Cuddy} has made for
\Gls{Detri}, meant to improve his intelligence in the hot summer. \Gls{Gaspode} tries to keep up
with \Gls{Angua}'s trail, through the mess of scents screaming at him from the city docks.
Meanwhile, \Gls{Vimes} gets woken up by \Gls{Ramkin}'s family butler, to get ready for the wedding.

\subsubsection{\Gls{Vimes} prepares for the wedding}
\Gls{Carrot} tells \Gls{Colon} that he has sent \Gls{Nobby} on special duty, to bring back the
corpse of \Gls{Edward} from the tunnel system. He learns that everyone else in the original Night
Watch was already aware of \Gls{Angua}'s identity the day she joined. \Gls{Vimes} arrives at the
Great Hall of the University, where Archchancellor \Gls{Ridcu} greets him, pointing out the ancient
pipe organ being refurbished for the ceremony.

\subsubsection{\Gls{Cuddy} climbs up the Tower of Art upon \Gls{Carrot}'s orders}
\Gls{Cuddy} climbs the spiral staircase of the Tower of Art, having drawn the short straw among the
Night Watch. As \Gls{Vetina}'s carriage starts the ceremonial journey from the palace to the
University, \Gls{Vimes} sees the glint of metal from the top of the Tower of Art, and asks who is
up there. \Gls{Carrot} says \Gls{Cuddy} has been sent there to investigate, before realizing the
gunman is probably using it as a vantage point.

\subsubsection{\Gls{Vetina} is shot by the gunman from the Tower of Art}
The gunman shoots at \Gls{Vetina}, who stands up to greet \Gls{Vimes} and takes the first bullet in
his thigh. \Gls{Carrot} takes the second bullet in his shoulder, as three more rattle the
cobblestones next to the upturned carriage. \Gls{Vimes} believes that the gunman is cornered at the
top of the Tower, since there is only one way down.

\subsubsection{\Gls{Gaspode} and \Gls{Angua} run into \Gls{BigFido} and his pack}
\Gls{Gaspode} tracks \Gls{Angua} to a dead end, and asks her to return to \Gls{Carrot}. She is in
two minds about the issue, until the sound of the gunshots confirms to her that \Gls{Carrot} is in
trouble. She bounds away to the source of the commotion, with \Gls{Gaspode} in pursuit.
\Gls{BigFido} and his pack corner \Gls{Angua}, but \Gls{Gaspode} uses his human voice to get them
to stand down.

\subsubsection{\Gls{BigFido} dies trying to chase down \Gls{Angua}}
\Gls{Angua} uses the confusion created by \Gls{Gaspode}'s voice to snatch him in her jaws, and run
for the rooftops. \Gls{BigFido} tries to follow her, but fails to leap over a wide gap, and falls
to his death. Meanwhile, \Gls{Colon} rushes into the Tower of Art, to find \Gls{Cuddy} lying dead
on the ground, having fallen from a great height. The gunman narrowly misses \Gls{Colon}'s head,
but manages to whack him with a blunt weapon, before running out of the Tower.

\subsubsection{\Gls{Vimes} escorts \Gls{Vetina} and \Gls{Carrot} into the University}
\Gls{Vimes} carries \Gls{Vetina} into the University's Great Hall, where the wizards tend to the
bullet wounds. \Gls{Carrot} surmises that the best way to lure out the gunman would be to announce
the capture of \Gls{Edward}, who is alive but gravely injured. \Gls{Vimes} decides to take charge
as the Captain one last time, with his wedding a few hours away.

\subsubsection{\Gls{Vimes} and \Gls{Carrot} confront \Gls{Cruces} in the tunnels}
\Gls{Vimes} and \Gls{Carrot} find \Gls{Cruces} in the tunnel network under the city, and accuse him
of murdering \Gls{Edward}. \Gls{Vimes} works out the grand plan, which was to pin the blame for
all of the other murders on \Gls{Edward} as well, and to be the hero by turning in his corpse to
the authorities. \Gls{Cruces} puts out the lantern in \Gls{Vimes}' hands, and holds him at
gunpoint.

\subsubsection{\Gls{Angua} dies trying to save \Gls{Carrot} and \Gls{Vimes}}
\Gls{Angua} catches up to \Gls{Vimes} and \Gls{Carrot} in the sewers, only to take all the bullets
meant for them as \Gls{Cruces} fires desperately in the dark tunnel. \Gls{Vimes} chases him as he
runs off to a secret exit that opens up in the Assassins' Guild. \Gls{Carrot} catches up to
\Gls{Vimes} inside the Guildmaster's office, where \Gls{Cruces} shows him the evidence that
\Gls{Edward} had compiled proving his royal lineage.

\subsubsection{\Gls{Carrot} kills \Gls{Cruces} when he threatens \Gls{Vimes} with the gun}
\Gls{Carrot} stabs \Gls{Cruces} to death, by driving his sword through a stone pillar, as
\Gls{Vimes} struggles to make sense of why \Gls{Cruces} was being so deferential to him. Before he
can connect the dots about \Gls{Carrot} being the scion, he is reminded of the wedding that is meant
to start at noon, and taken to the University.

\subsubsection{\Gls{Downey} allows \Gls{Vimes} and \Gls{Carrot} to leave the Guild House}
\Gls{Downey}, delighted that his ascension to Guildmaster is now certain, lets \Gls{Vimes} and
\Gls{Carrot} leave the Guild House with no objection. \Gls{Detri} arrives with his siege bow to
tear open the gates of the Guild House, with \Gls{Carrot} insisting on taking \Gls{Angua}'s body
to the Watch House. As the day wears on, he hears the sounds of the wedding band playing one song
after another, and waits patiently for \Gls{Angua}'s werewolf blood to heal her wounds.

\subsubsection{\Gls{Carrot} receives a promotion from \Gls{Vetina}}
\Gls{Carrot} visits \Gls{Vetina}'s office, and asks for some improvements to the City Watch.
\Gls{Vetina} elevates him to Captain, and suggests that \Gls{Vimes} be allowed to stay on in the
ceremonial position of Commander. \Gls{Carrot} indirectly tells him that he has buried the evidence
gathered by \Gls{Edward} in a safe place where it can never be found, and has no interest in being
known as the royal scion.

\subsubsection{\Gls{Carrot} delivers the new letter of appointment to \Gls{Vimes}}
\Gls{Vetina} shows \Gls{Carrot} the throne of Ankh-Morpork, which turns out to be made of rotting
wood, with a fading layer of gold. \Gls{Carrot} then goes to \Gls{Vimes} at \Gls{Ramkin}'s manor
to hand him his letter of appointment, and watches him elapse into logistical delirium.
\Gls{Gaspode}, frustrated by the cleanliness of the loving home where he is set to retire, breaks
out with his bowl, eager to return to the stray dog lifestyle.