\section{Monstrous Regiment}


\subsection{}
\subsubsection{\Gls{Polly} puts on a fake identity of a young man to enlist in the army}
\Gls{Polly} cuts off her long hair, and sneaks out of her home to enlist in the Borogravian army,
posing as a boy. She believes that her widowed father will be in good hands with the neighbour, who
had a soft spot for him, and wonders what her brother \Gls{Paul} might be doing on the front lines.
She practices her fake identity of \Gls{Oliver}, along with a boyish gait and speech pattern, to
try and fool the recruiters at the next town.

\subsubsection{\Gls{Polly} enlists at the inn in the next town over}
On a hill next to the river crossing, she notices the lack of fresh recruits marching behind the
Sergeant's wagon, and realizes that her village has already lost too many young men to the war. She
approaches the sergeant at the inn, and asks to enlist. Corporal \Gls{Strappi} sitting next to him
is surprised at the sight of a seemingly honest patriot, and pulls out the contract in a hurry.

\subsubsection{\Gls{Jackrum} enlists \Gls{PIgor} after \Gls{Polly}}
Sergeant \Gls{Jackrum} is impressed by \Gls{Polly}'s literacy and her neat handwriting, as other
prospective recruits walk into the inn. One of them speaks with a lisp, and identifies himself as
\Gls{PIgor}. Meanwhile, \Gls{Chinny}, the consul from Ankh-Morpork to the mountain nation of
Zlobenia welcomes \Gls{Vimes} and his forces at a castle on the border with Borogravia.

\subsubsection{\Gls{Chinny} explains the political and religious predicament in Borogravia}
\Gls{Chinny} is alarmed at the sudden inclusivity within the City Watch, when \Gls{Vimes} asks
\Gls{Shoe} to talk to the other zombies stirring to life under the castle. When \Gls{Vimes} asks
why the Borogravians are driven to be in a constant state of war with their neighbours, \Gls{Chinny}
reminds him of the Book of \Gls{Nuggan}, the local God who holds sway over the nation, with his
ever changing list of commandments.

\subsubsection{\Gls{Chinny} and \Gls{Vimes} talk about the possible motives behind the war}
\Gls{Chinny} then talks about \Gls{Duchess}, who is rumoured to be in mourning for the past few
decades, and has not been seen alive by anyone outside her loyal servants for a long time. She is
worshipped as a minor deity by all those who find it too difficult to keep track of the
ever-changing commandments of \Gls{Nuggan}. \Gls{Vimes} realizes that the war is a front to stop
\Gls{Heinrich}, the prince of Zlobenia, from staking his claim to the throne of Borogravia, when
\Gls{Duchess} dies with no children.

\subsubsection{\Gls{Vimes} thinks about the financial interests in Ankh-Morpork}
\Gls{Vimes} explains that Borogravia is causing too much economic harm to Ankh-Morpork, given their
monopoly over the semaphore tower locations, and their belligerence to all trade routes passing
through their lands. \Gls{Chinny} chimes in with the news that a famine is underway in Borogravia,
and that the war is likely to wind down out of simple starvation.

\subsubsection{\Gls{Maladict} the vampire enlists along with some other boys}
\Gls{Polly} watches in surprise as a vampire bearing the Black Ribbon of the Temperance Movement
shows up in expensive robes to enlist with Sergeant \Gls{Jackrum}. He gives the name \Gls{Maladict}
and remains vague about which wealthy family he has connections to. \Gls{Maladict} forces the
barman to bring out his keg of good beer, when \Gls{Polly} complains about the quality of the
liquor, just as a troll barges into the tavern.

\subsubsection{\Gls{Carbo} the troll enlists at the tavern}
\Gls{Polly} watches horrified as the troll named \Gls{Carbo} asks for a silver shilling as proof of
joining the army, and immediately asks the barman for a strong drink that knocks it out cold.
\Gls{Strappi} is overjoyed by the idea of the commision he will get for recruiting a troll, and asks
the privates to spend the night in the nearby shed.

\subsubsection{\Gls{Polly} recalls the letter from her brother \Gls{Paul}}
\Gls{Polly} thinks about her brother \Gls{Paul}, a simpleton who had enlisted in the first draft a
year ago, when he had believed the pamphlets proclaiming the patriotic duty of every able man in the
country. She reads his last letter from the front lines, which talks of the end of the war being
imminent, and hides it in her pack before the rest of her squad wake up.

\subsubsection{\Gls{Polly}'s secret is found out by someone in her squad}
\Gls{Polly} is alarmed to be handed a pair of socks to stuff down her pants by a stranger when she
uses the privy at night. She is surprised that the stranger is aware of her true identity, but
uninterested in blowing the whistle. The next day, \Gls{Strappi} wakes the squad up with the
threat of a diminished breakfast, and gets them packing.

\subsubsection{\Gls{Polly} fends off \Gls{Strappi} when he tries to haze her}
\Gls{Polly} is forced to fight \Gls{Strappi} with a sword, when he feels like some light hazing is
in order. \Gls{Jackrum} arrives to supervise the sparring, and is amused when \Gls{Polly} fights
dirty using the tricks taught to her by retired soldiers in her home. \Gls{Jackrum} is relieved to
see \Gls{Strappi} get no other takers for his invitation to duel, and orders the squad to march to
the mustering grounds for their official armour and weapons.

\subsubsection{\Gls{Strappi} fills in the recruits about the official casus belli}
\Gls{Strappi} spends a morning lecturing the recruits about the instigating factors behind the
current war, and notices most of them dozing off after the first few minutes. Later at night, the
recruits argue among themselves about the white lies peddled by every recruiter, and whether the
war might end by the time it was their turn at the front line.

\subsubsection{\Gls{PIgor} helps some wounded veterans returning from the front lines}
\Gls{PIgor} asks \Gls{Jackrum} for some time to help a group of wounded veterans making their way
back to the mountains. In the meantime, \Gls{Polly} is runs into \Gls{Lofty} in the bushes, who
is also secretly a girl, stuffing socks down her pants. Once the squad resumes their march,
\Gls{Polly} notices how close \Gls{Lofty} is to \Gls{Tonker}, and realizes she must have followed
her partner into the army out of love.

\subsubsection{\Gls{Polly}'s squad marches through a mass of refugees fleeing the front lines}
After the squad marches past a group of villagers heading in the opposite direction with their
possessions, a copy of the Ankh-Morpork Times blows past \Gls{Strappi}, who stamps it into the
muddy ground. \Gls{Polly} manages to pick up a fragment of the front page, which talks about the
Zlobenians taking over Kneck Keep under the command of \Gls{Vimes}, and the rejection by
\Gls{Duchess} of any surrender.

\subsubsection{\Gls{Blouse} addresses the latest batch of fresh recruits}
At the mustering grounds in the deserted city of Plotz, \Gls{Blouse} rides in to peruse the
assembled recruits, and tells them that they are to skip their training period in light of recent
developments at the border. He then hands \Gls{Jackrum} his discharge papers, and tells him that no
other recruiting team has returned with fresh blood. \Gls{Strappi} is alarmed to learn that he is
expected to fight on the front lines, instead of moving through the villages as a recruiter.

\subsubsection{\Gls{Polly} and the recruits meet quartermaster \Gls{Scallot}}
\Gls{Polly} is selected to be \Gls{Blouse}'s personal assistant, and \Gls{Jackrum} points them to
the warehouse containing their official armour and weapons. At the rundown armory, they meet
Corporal \Gls{Scallot}, who is the de-facto quartermaster. He shows them the horrendoues state of
the weapons and armour salvaged from the battlefield, and tells them that no salaries have been
coming in for the past few months.

\subsection{}
\subsubsection{\Gls{Polly} notices how much of a novice \Gls{Blouse} is}
\Gls{Polly} goes up to \Gls{Blouse}'s chambers on the top floor of a tavern, and notices his
clumsy swordsmanship as he finishes practicing. She then spots the beginner's guide to war on his
table, and realizes that he is a complete novice, likely at his rank because of his birth. She asks
the innkeeper for some ingredients for \Gls{Blouse}'s meal, and takes it instead to \Gls{Shufti},
who is busy improvising a palatable dinner.

\subsubsection{\Gls{Maladict} tells \Gls{Polly} that he suspects \Gls{Shufti} of being a woman}
\Gls{Maladict} drags \Gls{Polly} away from the cookfire as \Gls{Scallot} starts to fight over the
liquor with \Gls{Shufti}. He tells her that \Gls{Shufti} is likely to be a girl given how she just
swore, and believes \Gls{Lofty} might be one too. \Gls{Polly} is still unsure about how his opinion
of her, and decides to play along for the moment.

\subsubsection{\Gls{Polly} finds even more undercover women in her squad}
After a hearty dinner where \Gls{Scallot} tells them tales of \Gls{Jackrum}'s exploits in previous
wars, the Sergeant walks in to tell them about the next phase of their trip. After getting some
privacy, \Gls{Polly} confronts \Gls{Shufti} about hiding her womanhood, and realizes that she is
is pregnant out of wedlock, and desperate to find her lover on the front lines. While going to bed,
she spots \Gls{Wazzer} bowing to a figure of the \Gls{Duchess} in a ladylike fashion.

\subsubsection{\Gls{Polly} learns about her Lieutenant's ineptitude}
\Gls{Polly} unfolds a letter she had found in \Gls{Blouse}'s laundry earlier, and finds evidence of
the Lieutenant being a low-ranking paper pusher for the past decade. He had been promoted suddenly
to front-line duty, and was thoroughly inept at the actual act of soldiering. \Gls{Polly} thinks
about the prospect of losing the title to her father's tavern in the absence of \Gls{Paul} as a male
heir, as she goes to sleep.

\subsubsection{\Gls{Polly} ambushes the enemy officers leading the cavalry patrol}
The next morning, \Gls{Polly} finds the inn ransacked, with \Gls{Jackrum} claiming that the last of
the citizens have fled in fear of an enemy raid. When he hears some cavalry approaching, he asks
\Gls{Polly} to distract them as he prepares an ambush. The Zlobenian officers enter the bar, just
as \Gls{Polly} gets rid of her military uniform and dons a barmaid's skirt. She ambushes the
Captain while pretending to serve them some stale beer, and hears screams from the direction of
her squad.

\subsubsection{\Gls{Polly} and \Gls{Maladict} gather up the last of the enemy officers}
\Gls{Polly} finds \Gls{Maladict} taking care of the last of the enemy cavalrymen, as he tells her
about \Gls{Tonker} also being a woman. He then asks her why she is cross-dressing, indicating the
fact that he still believes \Gls{Polly} is male. They return to \Gls{Blouse}'s inn, and restrain
the enemy officers, who are slowly recovering from her attack.

\subsubsection{\Gls{Jackrum} confines the enemy raiders in \Gls{Scallot}'s warehouse}
Inside \Gls{Scallot}'s warehouse, \Gls{Jackrum} oversees the chaining of all the enemy soldiers,
as the enemy Captain identifies himself as \Gls{Horentz} of the Zlobenian Cavalry Regiment.
\Gls{Jackrum} threatens \Gls{Horentz} with violence unless he reveals the reason behind the raid,
and learns that they were sent to capture any fresh recruits massing in the city. \Gls{Horentz} asks
to speak to the commanding officer, and \Gls{Polly} is sent to retrieve \Gls{Blouse}.

\subsubsection{\Gls{Polly} and her squad are bewildered to see \Gls{OttoC} and \Gls{deWorde}}
\Gls{Blouse} receives a report from \Gls{Jackrum} about the enemy raid at midnight, and is surprised
at the lack of casualties. \Gls{Jackrum} salvages the crossbows and swords from the Zlobenians, as
\Gls{Horentz} reminds them of reinforcements on the way. \Gls{OttoC} walks into the inn, and starts
arranging the soldiers into proper poses for his camera, as \Gls{deWorde} starts to interview
\Gls{Horentz}.

\subsubsection{\Gls{Maladict} talks about the newspaper to his squad of village-born hicks}
\Gls{Maladict} tries to explain the idea of a privately owned newspaper, as \Gls{Polly} thinks about
the propaganda spread by her own government in Borogravia. She wonders how anyone would trust any
written document produced by a private organization, as \Gls{Wazzer} desperately tries to argue that
their side is winning the war.

\subsubsection{The recruits in \Gls{Polly}'s squad all reveal themselves to be female}
\Gls{Shufti} reveals to the squad that her real name is \Gls{Jade}, and \Gls{Polly} is forced to
also reveal her own. \Gls{Jackrum} arrives to give them marching orders, as \Gls{Scallot} prepares
to set off with the warhorses to a nearby horse trader, hoping to secure a retirement by selling
them. \Gls{Jackrum} leaves the enemy raiders chained in the tavern, after stripping them of their
equipment and uniforms.

\subsubsection{\Gls{Vimes} intercepts \Gls{deWorde}'s report sent by carrier pigeon}
Someone arranges for the squad's sleeping quarters to burn down a few hours after they leave Plotz,
just like they had in Plum. \Gls{Vimes} has \Gls{BSwires} intercept \Gls{deWorde}'s field report
using his buzzard, and spots \Gls{Heinrich} incognito as Captain \Gls{Horentz} in the photograph.
He wonders if \Gls{Jackrum} and the others are aware that they are holding the enemy prince captive,
and of the political fallout once the prince returns to Zlobenia.

\subsubsection{\Gls{Angua} decides to run to Plots to meet up with \Gls{Heinrich}}
\Gls{Angua} reminds \Gls{Vimes} of the Cult of \Gls{Nuggan}, which was increasingly becoming
impossible for the Borogravians to follow, and offers to run to Plotz using her werewolf form.
Meanwhile, \Gls{Polly} and her squad encounter a ransacked nomad camp, with those inside seemingly
murdered by deserters from their own army. \Gls{Maladict} finds his coffee beans missing, and
\Gls{Polly} also notices some valuables gone from her pack.

\subsubsection{\Gls{Polly} accuses \Gls{Strappi} of pilfering goods from the squad's packs}
\Gls{Polly} decides to blame \Gls{Strappi}, who had deserted just after receiving news of his
front-line duty, and tells \Gls{Jackrum} that the privates have sorted out the missing goods.
\Gls{Polly} is alarmed when \Gls{Blouse} asks her to give him his morning shave, but is let off when
\Gls{Jackrum} walks in to do the job himself, hoping for a private chat with his commanding officer.

\subsubsection{\Gls{Polly} helps \Gls{Blouse} with his horse}
\Gls{Tonker} returns from perimeter duty with some game for their next meal, as \Gls{Jackrum}
informs them of their next moves. He tells them that they are to stay away from roads and move by
night, in order to avoid bands of roving deserters. As the squad prepare to move out, \Gls{Polly}
helps \Gls{Blouse} mount his horse, and gets bitten right in the socks stuffed down her pants.

\subsubsection{\Gls{Polly} figures out that \Gls{Igor} is also a female}
\Gls{Polly} fends off \Gls{Blouse}'s concerns about the groin injury, as he recovers after falling
off the horse. In the night, \Gls{Polly} guesses that \Gls{Igor} is also secretly female, and is
surprised when he admits it immediately. She tells \Gls{Polly} that female Igors are called
\Gls{Igori}, and wonders what mannerism gave it away. The squad eventually arrive at the border,
to see the campfires of the armies, along with some semaphore towers signaling in the distance.

\subsubsection{\Gls{Jackrum} organizes an ambush on the enemy's semaphore tower}
\Gls{Jackrum} is annoyed to learn that \Gls{Blouse} wants to accompany the squad in their sneak
attack on the enemy semaphore tower. The attack is botched when the two halves of the ambush
collide with each other, and two of the three spies are killed in the process. \Gls{Blouse} reminds
\Gls{Jackrum} that waiting for the signaling to end means that the enemy does not know about their
code-book and signaling equipment falling into their hands.

\subsection{}
\subsubsection{\Gls{Polly} finds out about \Gls{Wazzer}'s reasons for enlisting}
As she digs graves for the dead spies, \Gls{Polly} asks \Gls{Wazzer} about her motives for
enlisting. \Gls{Wazzer} tells her that she had an abusive childhood, and that \Gls{Duchess} herself
had asked her to join the army to rise up the ranks and command it. \Gls{Shufti} brews some tea
salvaged from the spies, and asks \Gls{Polly} to head over to \Gls{Jackrum}, who is interrogating
the sole surviving prisoner.

\subsubsection{\Gls{Blouse} decides to be civil and allow the prisoner to speak}
\Gls{Jackrum} is furious to be denied the privilege of beating the information out of the captured
officer, as \Gls{Blouse} insists on respecting the rights of prisoners. \Gls{Polly} arrives with
tea, and is asked to remove the prisoner's gag. He identifies himself as \Gls{Tower}, a Lieutenant
in the ZLobenian army, and recommends they surrender.

\subsubsection{\Gls{Tower} tries to tell \Gls{Blouse} about the state of the Borogravian army}
\Gls{Tower} tells them about the true identity of \Gls{Horentz}, and the fact that the entire
Zlobenian army was now on the lookout for their squad. \Gls{Polly} is alarmed when \Gls{Tower} talks
about reinforcements set to arrive, and finds out that \Gls{Jackrum} has already sent out half the
squad to keep watch.

\subsubsection{\Gls{Jackrum} kills the captured Sergeant, when he tries to escape his chains}
\Gls{Jackrum} shoots \Gls{Tower} dead, when he cuts off his bindings using \Gls{Igori}'s sword, and
tries to hold \Gls{Blouse} hostage. He then tells the squad to erase all signs of the campfire, and
prepare to move out before sunrise. \Gls{Blouse} is transfixed at the sight of his own blood, when
he notices the missing chunk of ear from \Gls{Jackrum}'s shot.

\subsubsection{\Gls{Jackrum} admits to murdering \Gls{Tower}}
\Gls{Jackrum} tells \Gls{Polly} that he did in fact engineer the death of \Gls{Tower}, given that
there was no enemy to hand him over to alive. She notices a gold chain hanging from his neck with a
golden locket on it that he hastily shoves back under his shirt. After serving \Gls{Blouse} his
breakfast at their new hillside camp, she talks to \Gls{Maladict} about their Lieutenant's prospects
at the front line.

\subsubsection{\Gls{Maladict} and \Gls{Polly} investigate \Gls{deWorde}'s wagon}
\Gls{Maladict} identifies the cart traveling close to their camp as the press wagon driven by
\Gls{deWorde}, and is alarmed when the four soldiers escorting it split up to investigate some
noise in the forest. \Gls{Polly} confronts \Gls{deWorde}, who is eager to tell them about the fate
of the Borogravian army, and to get more sound bites from the squad. \Gls{Maladict} and \Gls{Jade}
show up to restrain the four guards from Ankh-Morpork, and decide to take them to their camp.

\subsubsection{\Gls{Jackrum} and \Gls{Polly} escort \Gls{deWorde} and \Gls{OttoC} back to camp}
\Gls{deWorde} identifies \Gls{BSwires} in the sky by the buzzard mount, and is sure that he will be
tracked down by \Gls{Vimes}. \Gls{Polly} and \Gls{Jackrum} are sent down to the road to retrieve
\Gls{deWorde} and his wagon. \Gls{Jackrum} decides to portray \Gls{Blouse} as a military genius
responsible for their tactical victories against \Gls{Heinrich}, as well as the semaphore tower they
had ambushed in the night.

\subsubsection{\Gls{deWorde} has \Gls{OttoC} take pictures of \Gls{Blouse}}
\Gls{deWorde} shows \Gls{Blouse} his newspaper and the attached cartoons, which paint the squad as
brave soldiers standing up to royalty. He then tells the squad that they are the only Borogravian
element not wounded, captured or killed in the war. \Gls{deWorde} and \Gls{OttoC} are surprised to
see \Gls{Blouse} talk at length about compression algorithms and color coded broadcasts as a way of
making the communication network more efficient, as he poses for his photos.

\subsubsection{\Gls{Jackrum} tries to overrule \Gls{Blouse}'s idea of sneaking into Kneck Keep}
\Gls{Jackrum} is amused to see his lies about \Gls{Blouse} come true when \Gls{deWorde} marvels at
his mathematical genius on the way back to the wagon. \Gls{Maladict}'s coffee withdrawal symptoms
start to kick in, putting him in the jungles of Vietnam with helicopters flying in the sky.
\Gls{Polly} insists on following \Gls{Blouse}'s insane idea of finding a way into Kneck Keep, where
the Borogravian generals are likely to be held prisoner.

\subsubsection{\Gls{Maladict} believes that the squad is being tracked}
\Gls{Maladict} tells the squad that he can sense someone following them, but cannot directly sense
them. \Gls{Jackrum} brushes it off as some wild animal, as the squad marches on toward Kneck Keep.
\Gls{Polly} learns that \Gls{Tonker} and \Gls{Lofty} were orphans abused in the monastery in her
home-town, and asks them if they have any plans of going back.

\subsection{}
\subsubsection{\Gls{Polly} tries to ask \Gls{Jackrum} about the medallion around his neck}
\Gls{Jackrum} points out the distant figure crouched in the bushes watching their camp, and
\Gls{Polly} wonders if it might be the werewolf that \Gls{Tower} had mentioned. He becomes testy
when \Gls{Polly} mentions the silver medallion around his neck that might be useful against the
werewolf, and changes the topic to their next move.

\subsubsection{\Gls{Blouse} plays games with the Ankh-Morpork spy network using his semaphore}
\Gls{Blouse} chooses to play along with \Gls{Jackrum} when he mentions some arcane statue justifying
\Gls{Shufti}'s thievery from \Gls{deWorde}'s store of combat rations. The squad enjoys a hearty
meal, and notices the Ankh-Morpork army searching for its lost spy unit using their light semaphore.
He gets the squad to set up the captured semaphore mechanism, and feeds the Ankh-Morpork spies some
false information about their location.

\subsubsection{\Gls{Vimes} receives the latest news about \Gls{Polly}'s squad}
\Gls{Vimes} surveys the troops of the Zlobenian alliance assembled next to Kneck Keep, and thinks
about the coming winter. He realizes that the alliance will not last the winter, and that
Borogravia will eventually take control of the Keep once the gathered armies start bickering amongst
themselves. \Gls{BSwires} returns to report on the progress of \Gls{Polly}'s squad, and reminds him
that \Gls{Angua} is close to being found out.

\subsubsection{\Gls{Polly} and the squad reach the outskirts of Kneck Keep}
\Gls{Shoe} has two of his fingers bitten off by \Gls{BSwires}' bird, as he starts ranting about the
lethargic zombies shambling in the castle's crypt. Meanwhile, \Gls{Jackrum} reminds \Gls{Blouse}
that it would be suicidal to approach Kneck Keep through the main gate. \Gls{Wazzer} starts praying
to the \Gls{Duchess}, and mumbles something about \Gls{Nuggan} guiding their eyes, in their attempt
to find a hidden entrance.

\subsubsection{\Gls{Polly} finds the servants' entrance into Kneck Keep}
\Gls{Polly} and her patrol discover a servant's entrance by the riverside, with washerwomen
going in and out of Kneck Keep through it. They realize that the enemy will not allow anyone bearing
arms to use it, and decide to dress up as washerwomen to try and infiltrate the Keep. They report
their findings to \Gls{Blouse}, after narrowly escaping an enemy patrol with the timely distraction
of some wild animals attracting their attention.

\subsubsection{\Gls{Blouse} wishes to dress up as a washerwoman}
\Gls{Blouse} agrees with \Gls{Polly}'s plan, and insists on dressing up as a washerwoman himself
to infiltrate the Keep. \Gls{Jackrum} bends over in an attempt to conceal his laughter, as the
rest of the squad try desperately to dissuade the Lieutenant, even as he asks \Gls{Igori} to ready
some clothing for his disguise.

\subsubsection{\Gls{Blouse} asks \Gls{Jackrum} about his years of service in the army}
\Gls{Blouse} asks \Gls{Polly} to give him a clean shave, and tells her that he has never learnt to
do it himself. \Gls{Jackrum} arrives to stop \Gls{Polly} from having to shave \Gls{Blouse}, and
stops her from revealing her gender by lying about her age. \Gls{Blouse} is alarmed by the prospect
of taking children into Kneck Keep on a dangerous mission, and starts to question the long service
period in \Gls{Jackrum}'s records.

\subsubsection{\Gls{Maladict} is saved by a miraculous airdrop of coffee beans}
\Gls{Jackrum} manages to feed \Gls{Blouse} a plausible excuse about some clerical error, and lies
about his current age. \Gls{Maladict} is knocked over by a bag of coffee beans dropping from the
sky, just as his withdrawal symptoms threaten to go out of control. The squad decides to attribute
the gift to random chance, when \Gls{Wazzer} says that the \Gls{Duchess} did not offer any help this
time.

\subsubsection{\Gls{Shufti} talks about her lover and the child in her womb}
\Gls{Shufti} tells \Gls{Polly} that her lover had promised to come back for her and the child, but
the draft had made it impossible. She believes that he will be in the Keep along with the others in
the regiment held captive, and hopes that \Gls{Wazzer}'s prayers will work. Meanwhile, \Gls{Polly}
notices \Gls{BSwires}' buzzard circling over their heads high in the sky for an unnaturally long
time.

\subsubsection{\Gls{Jackrum} leads \Gls{Polly} and \Gls{Shufti} to the Borogravian siege camp}
\Gls{Jackrum} reveals to the squad that he knew all along about their secret identities, and chose
to keep quiet in front of \Gls{Blouse}. He then reminds them that following \Gls{Blouse} into the
Keep would require women's clothing, and leads a few of the girls to the siege camp of the
Borogravian army.

\subsubsection{\Gls{Jackrum} finds some dresses at the camp's whorehouse}
\Gls{Jackrum} finds the makeshift whoreshouse at the far end of the siege camp, and manages to
distract the madam long enough for the others to grab several dresses from the storeroom. He gets
the girls out of the camp, just as the alarm is rung, and makes them climb a steep hill to get away
from the patrols.

\subsubsection{\Gls{Jackrum} bids the girls goodbye outside the servants' entrance}
\Gls{Jackrum} refuses to infiltrate Kneck Keep with the girls, and tells them that he will lead
a diversionary attack from the siege camp instead. \Gls{Wazzer} says that the \Gls{Duchess} has
shown her visions of \Gls{Jackrum} going to the town of Scritz in search of a sword. \Gls{Polly}
manages to catch the momentary terror on his face, before he recovers his composure.

\subsubsection{\Gls{Polly} and the girls manage to infiltrate the Keep}
\Gls{Polly} and the girls fail to show their permit, and are taken to a side room for questioning.
The Captain in charge of the gate accuses them of being boys in disguise, but is forced to
reconsider when \Gls{Shufti} lifts her skirt. He asks for \Gls{Daphne} to show the new arrivals to
their posts, leaving the girls surprised to see \Gls{Blouse} in disguise.

\subsubsection{\Gls{Blouse} leads the squad to \Gls{Enid}, the head of the laundry}
\Gls{Blouse}, who still believes that the squad are all boys, congratulates them on their disguise,
and tells them that his own entry had been much easier. He warns them that access to the upper
Keep is heavily restricted, and takes them to the chief maid \Gls{Enid}, who tells them that her
own husband and son are captives in the Keep's dungeon.

\subsubsection{\Gls{Polly} tries to get \Gls{Blouse} to go along with a sensible plan}
\Gls{Wazzer} starts to enter one of her trances again, and \Gls{Polly} pulls her aside just in time
to hear that \Gls{Nuggan} is dead, and that the \Gls{Duchess} herself is greatly weakened by the
xenophobia inside the Borogravian minds. \Gls{Polly} finds \Gls{Blouse} teaching some other girls
how to iron the freshly laundered clothes, and realizes that they all know he is a man. She tells
him that the commandeering the lift used to transport clothes up to the Keep is a better plan than
seducing some guard using his womanly wiles.

\subsubsection{\Gls{Polly} and the squad sneak into the dungeons under Kneck Keep}
The elevator with \Gls{Polly} and her squad on it malfunctions midway up its shaft, and the girls
knock out the two guards escorting them. They decide to dig through a sealed tunnel entrance on the
wall, and find an old cellar inside. \Gls{Blouse} recognizes the zombies as dead military generals
of the past few centuries, as \Gls{Wazzer} is once again possessed by \Gls{Duchess}. The zombies
salute her as she leads the squad deeper into the cellar, until the possession ends.

\subsubsection{\Gls{Polly} and the squad are captured and taken to an empty kitchen}
\Gls{Tonker} talks about deserting the army and helping the Zlobenian invaders, and \Gls{Polly}
calms her down in time for some guards to discover them. The squad is confined to a kitchen, and
\Gls{Polly} decides to let \Gls{Blouse} in on the truth about the squad being female. He takes the
news surprisingly well, and starts talking about the historic records of female warriors across
the cultures on the Disc.

\subsubsection{\Gls{LRust} makes an offer of peace with \Gls{Blouse} and his squad}
\Gls{LRust} arrives along with \Gls{Vimes}, and starts to outline a special deal on offer for the
girls in the squad, along with a cozy retirement for \Gls{Blouse}. \Gls{Polly} wonders why such a
deal has not been offered to the rest of the Borogravian top brass, and notices \Gls{Vimes} smirking
with a cigar at the kitchen door. \Gls{Blouse} refuses the offer after conferring with the girls,
and \Gls{Polly} spots \Gls{Vimes} giving them a thumbs-up on his way out.

\subsubsection{\Gls{Polly} and the girls are imprisoned by a Borogravian Major}
\Gls{Lofty} tells the squad that the ingredients left over in the kitchen larder would be enough
to cause an explosion. Meanwhile, \Gls{Igori} asks the guards to bring some blankets and firewood
for \Gls{Wazzer}, who is unconscious and going cold. After they break out of the kitchen using the
commotion caused by the blast, \Gls{Blouse} frees some Borogravian officers, who promptly have the
girls put in a jail cell for the crime of impersonating men.

\subsubsection{Major \Gls{Clog} tells the girls that they are to be tried}
Major \Gls{Clog} visits the girls in their jail cell, and writes down a full account of their
adventures. He tells them that the Borogravian high command want them to be tried for impersonating
soldiers, since news of women liberating the generals would look very bad. The trial takes place
at a ballroom now repurposed into a command center for the Borogravians, where General \Gls{Froc}
awaits the squad.

\subsubsection{\Gls{Strappi} fails to put \Gls{Polly} and the others in jail}
\Gls{Strappi}, who is now a Captain, offers testimony against the girls, and accuses them of
violating several Nugganite commandments. \Gls{Clog} chimes in to remind \Gls{Froc} that the
commandments are so impractical now that every citizen can be accused of violating one rule or the
other. \Gls{Strappi} is forced to keep quiet when \Gls{Froc} realizes that the subject of
Sergeant \Gls{Jackrum} is about to be broached.

\subsubsection{\Gls{Jackrum} reveals that a significant part of the Borogravian high command is
    female}
As the sounds of the battle outside heat up, \Gls{Jackrum} arrives at the ballroom, and asks to talk
in private to a select group of senior officers. \Gls{Froc} reluctantly agrees when he reminds the
general of his valour in previous wars, and reveals that every single officer sitting remaining
in the ballroom is secretly a woman. \Gls{Froc} confesses to identifying only a small fraction of
the disguised women under his command, and offers \Gls{Polly} and the squad an honourable discharge.

\subsubsection{\Gls{Duchess} asks the top brass to commit themselves to religious reform}
The spirit of \Gls{Duchess} reminds the senior officers of a ball many decades ago when they doubt
her, and asks them to make peace with the enemy alliance. She tells them to go back into the
country and liberate it from the worship of \Gls{Nuggan}, so that it might enter the modern world
along with its neighbours. \Gls{Wazzer} collapses once the possession ends, leaving \Gls{Jackrum}
to organize a surrender proclamation to be carried by \Gls{Polly} to the enemy.

\subsubsection{\Gls{Vimes} tells \Gls{Polly} that the truce was Borogravia's only way forward}
\Gls{Vimes} meets \Gls{Polly} outside the war room of the Zlobenian alliance, and reads through
her letter of truce. He tells her that \Gls{deWorde}'s reporting is only going to garner more
sympathy when the citizens of Ankh-Morpork learn that the squad that defeated \Gls{Heinrich} was
all female. He then reveals that \Gls{Paul} has been in his custody all along, and asks \Gls{Angua}
to take her to him.

\subsubsection{\Gls{Polly} confronts \Gls{Heinrich}, who chooses to play nice for diplomacy's sake}
\Gls{Polly} is relieved to find \Gls{Paul} safe with his crayons, and finds \Gls{deWorde} waiting
for her in the main hall. The interview is interrupted by Prince \Gls{Heinrich} returning from his
wild goose chase triggered by \Gls{Blouse}'s misleading semaphore message, and is learn that the
young soldier who bested him is a woman. In the interest of his geopolitical ambitions, he decides
to smile and shake hands for \Gls{OttoC}, who is ready with his camera.

\subsubsection{\Gls{Polly} learns that \Gls{Jackrum} is also female}
\Gls{Polly} finds \Gls{Jackrum} reminiscing about the figure in his amulet, and is shocked to learn
that he is also secretly female, and had followed his lover into the army long ago. \Gls{Polly}
asks him about surviving family, and learns that \Gls{Jackrum} has a son in Scritz, who is a
successful blacksmith with a wife and many children. She recommends visiting Scritz disguised as a
man, offering a story of honourable discharge for heroic action.

\subsubsection{\Gls{Polly} decides to stop the next war against Zlobenia}
Many months later, \Gls{Polly} receives a package from \Gls{Jackrum} with a family photo, as well
as a notebook containing the details of every single undercover female in the Borogravian army. She
decides to make a backup copy of the information, and gets out her ceremonial uniform to head for
the capital. She decides to enlist again, and is confident that the army can be convinced to let
women join without concealing their gender.