\section{Mort}


\subsection{}
\subsubsection{\Gls{Lezek} decides to find an apprenticeship for his son \Gls{Mort}}
\Gls{Death} inspects the hourglasses lined up in his pocket dimension, representing the lifetimes
of the people of Discworld. Meanwhile, \Gls{Mort}'s father \Gls{Lezek}, who owns a valuable
octarine wine-making operation in the Ramtops, rues his lack of talent for horticulture. \Gls{Lezek}
purchases an oversized poncho for his son, and takes him downhill to the nearby town, where an
impromptu job fair is being held.

\subsubsection{\Gls{Death} takes on \Gls{Mort} as an apprentice}
\Gls{Lezek} tells \Gls{Mort} that he might have to wait till midnight at the town square, if no one
offers him an apprenticeship. At the stroke of midnight, marking the start of a new year,
\Gls{Death} appears next to \Gls{Mort}, offering to take him on as an apprentice. He disguises
himself as an undertaker to \Gls{Lezek}'s vision, and \Gls{Mort} is surprised to find him readily
approve of the offer.

\subsubsection{\Gls{Lezek} bids farewell to \Gls{Mort}}
\Gls{Lezek} shakes hands with \Gls{Death}, formalizing the start of the apprenticeship, as
\Gls{Mort} gets on the white horse, and rides off into the darkness. \Gls{Lezek} tries and to tell
\Gls{Mort} that he should keep an eye out for any daughters of his employer that he might court, and
advance his station in life.

\subsubsection{\Gls{Death} gets \Gls{Mort} some food, and a new outfit for the job}
\Gls{Death} takes \Gls{Mort} to Ankh-Morpork, where the boy is awed by the dirty, bustling markets
and the crowds thronging the various temples. \Gls{Death} takes him to a restaurant, where the
patrons refuse to notice him. \Gls{Death} tells \Gls{Mort} that only wizards and cats could see him
even before it was time for them to die, as he takes him shopping for a fresh outfit and haircut.

\subsubsection{\Gls{Mort} gets his first errand from \Gls{Death} in his pocket dimension}
The next morning, \Gls{Mort} wakes up in \Gls{Death}'s manor, and makes his way to the Great Hall,
where \Gls{Ysabell} greets him, surprised that he is not dead. She takes him to the kitchen, where
\Gls{CAlbert} hands him some breakfast. A bell from \Gls{Death} interrupts his meal, and he is
forced to go up to his study. \Gls{Death} asks him to shovel the dung from the stables for his
first job.

\subsubsection{\Gls{CAlbert} tends the garden in \Gls{Death}'s realm with the help of \Gls{Mort}}
\Gls{Death} calls \Gls{Mort} up to his study later, and tells him that he is to help \Gls{CAlbert}
with any chores that need doing. When \Gls{Mort} asks why he is not out reaping every soul that
dies, \Gls{Death} responds that he is only required in person for special occasions. \Gls{CAlbert}
talks about the real being designed by \Gls{Death}, and bemoans the dreary black color-scheme
for everything, including the garden.

\subsubsection{\Gls{Death} takes \Gls{Mort} along to the palace of Sto Lat}
\Gls{Death} takes \Gls{Mort} along for his latest ride on his white horse \Gls{Binky}, and lands
on top of the castle in Sto Lat. Inside the main hall, \Gls{Mort} is surprised to find that the
people now ignore him just like his master. \Gls{Death} eventually points out the king, set to be
poisoned by his cousin, who has worked his way through the family to be next in line for the
throne.

\subsubsection{\Gls{Mort} fails to stop an assassination, since mortals cannot notice him}
The King of Sto Lat dies when a musician fires a crossbow at his neck, and greets \Gls{Death}, who
is waiting to claim his soul. \Gls{Mort}'s attempt to warn the king fails, and earns him a reprimand
from \Gls{Death}. He feels himself enter the spirit realm, and is unable to interact with the King's
daughter, as she is weeping over his corpse, with the evil uncle standing over her shoulder.

\subsubsection{\Gls{Mort} gets a day off from \Gls{Death}'s realm}
\Gls{Mort} asks for a day off, and \Gls{Death} is alarmed by the request. He relents, before sending
the boy to Ankh-Morpork, with an allowance of gold coins. \Gls{Mort} immediately thinks about the
princess of Sto Lat who had managed to make eye contact with him through \Gls{Death}'s veil of
ignorance, and seeks out a fast horse to meet her.

\subsubsection{\Gls{Mort} escapes some thugs in the Shades district}
\Gls{Mort} manages to subconsciously walk through a wall, similar to \Gls{Death}, when he is
cornered by some thugs in the Shades district. The thugs mistake him for a wizard, before scattering
more dangerous elements converging on them. In the infinite room lined with shelves containing the
hour-glasses of the living, \Gls{Death} is sad to see Princess \Gls{Keli}'s time run out, and
decides to send \Gls{Mort} to collect her soul in his stead.

\subsubsection{\Gls{Mort} convinces a Klatchian family to help him find a horse}
\Gls{Mort} finds himself inside the hovel of a Klatchian family having a meal, and manages to
convince them that he is a demon from hell. The father, believing that helping such a spirit would
bring good fortune, immediately sets out to help him find a steed for the journey to Sto Lat. He
returns with the a gold coin \Gls{Death}, and declares his intent to retire back in Klatch.

\subsubsection{\Gls{Mort} meets with \Gls{ICutwell} in Sto Lat}
\Gls{Mort} makes it to Sto Lat, where he tries and fails to walk through the castle walls for a few
hours. He then goes to the nearest wizard, named \Gls{ICutwell}, and finds him to be a quack,
selling cheap love potions and other trinkets. When \Gls{Mort} takes out one of his gold coins,
\Gls{ICutwell} is transfixed, and starts to agree that he can walk through walls. \Gls{Mort}
realizes that it is time to return to \Gls{Death}'s realm, and is surprised to see his master in
the street outside \Gls{ICutwell}'s home.

\subsubsection{\Gls{Death} gives \Gls{Mort} three souls to reap}
\Gls{Death} gives \Gls{Mort} the three hourglasses, and asks him to take \Gls{Binky} along to reap
their souls. \Gls{Binky} sets off at great speed, to a clearing in the forested hilltops towards
the hub, until it lands next to a witch's cottage. The witch, who is well aware that her time is
near, finishes writing up her will, and gracefully walks out of her cottage, to die on a log
nearby looking out at the valley.

\subsubsection{\Gls{Mort} attends to a monk's soul, that is stuck in a cycle of death and rebirth}
\Gls{Mort} is happy at reaping his first soul, and rushes back to \Gls{Binky}, who prepares to
fly to the next target. It turns out to be a high-ranking monk in a secluded monastic order in
the mountains. The monk's soul greets him, while asking about the usual man who comes for his soul.
\Gls{Mort} recalls in time that the monk's sect must believe in reincarnation, and leaves his soul
in the neighbouring village, to enter the body of a child just being conceived.

\subsubsection{\Gls{Mort} saves \Gls{Keli}'s life by reaping the soul of her assassin}
\Gls{Mort} manages to rush through the window of \Gls{Keli}'s bedroom, and swing his scythe at the
assassin poised next to her bed, ready to stab her. She is relieved to still be alive, and asks
him who he is. \Gls{Mort} wonders how much trouble he is in with \Gls{Death}, as attempts to explain
the nature of his job. He then decides to return to \Gls{Death}'s House, even as \Gls{Keli} wishes
to thank him for saving her life.

\subsubsection{\Gls{Mort} returns to \Gls{Death}'s House after changing reality}
\Gls{Mort} goes to sleep, after reading \Gls{Keli}'s biography in \Gls{Death}'s library, to learn
what the consequences of her death would have been, if he had not disturbed the fabric of reality.
The next day, he tries to talk to \Gls{CAlbert} about his screwup, and learns that the cook has been
\Gls{Death}'s servant for many centuries.

\subsubsection{\Gls{Keli} is deemed not to exist by everyone in her castle}
\Gls{Mort} finds that the biographies in the library have started to disappear or change, and is
alarmed by the effect his impuslive mistake might be having on reality. Meanwhile, \Gls{Keli} deals
with the effects of her death not having occurred at the appointed time, as the servants in the
castle ignore her completely, as if enchanted.

\subsubsection{\Gls{Keli} realizes that \Gls{ICutwell} can see her, unlike her servants}
At \Gls{ICutwell}'s house, she bangs on the door, until the wizard opens it, to deny her admission
once she refuses to buy one of his potions. A while later, she realizes that she was not invisible
to him, and starts knocking on the door again. The gargoyle on the front door helps her out, as she
tries desperately to recall some lesson from her tutors that might aid her.

\subsection{}
\subsubsection{\Gls{Keli} decides to use \Gls{ICutwell} as a bridge to the people around her}
\Gls{Keli} asks \Gls{ICutwell} to cry her future, and is annoyed by his messy home and
scatterbrained reading of a card deck. The cards consider her dead, as well as the lines on her
palm, leading \Gls{ICutwell} to conclude that she is a serious anomaly in the fabric of reality.
She decides not to let history leave her behind, and drags \Gls{ICutwell} back to the palace,
appointing him the Royal Recognizer.

\subsubsection{\Gls{Mort} refuses to tell \Gls{Death} about interfering in \Gls{Keli}'s death}
\Gls{Mort} learns that it is \Gls{Death}'s policy to let people go to whatever kind of afterlife
they believe in, and fails to muster up the courage to reveal his screw-up in \Gls{Keli}'s room.
He covers for \Gls{Ysabell} by saying he was the one fiddling around with the self-writing
biographies in the library, and leaves \Gls{Death}'s study in a sullen mood. \Gls{Ysabell} finds
him outside, and thanks him for letting her crimes go undetected.

\subsubsection{\Gls{Mort} talks to \Gls{Ysabell} in the garden}
\Gls{Mort} rejects \Gls{Ysabell}'s claim that her father brought him to the House as a potential
match for her, as visions of \Gls{Keli} cloud his mind. He blurts out the debacle with \Gls{Keli}'s
reaping, but notices too late that \Gls{Ysabell} is not paying attention. She then starts to lament
her life as a sixteen-year old, stuck in \Gls{Death}'s realm outside the flow of time, and of how
the biographies in the library talk of passionate love.

\subsubsection{\Gls{Mort} visits a tavern near Sto Helit}
\Gls{Mort} finishes his next batch of reapings, and notices an event horizon spreading out from the
castle of Sto Lat, reflecting the survival of Princess \Gls{Keli}. He decides to enter an inn next
to Sto Helit, and is made to drink a hard liquor by the landlord, who means to prank him. Since he
has crossed the event horizon of reality, he is able to handle the liquor with ease, leaving the
villagers stunned.

\subsubsection{\Gls{Mort} notices the shift to the fated reality}
\Gls{Mort} tries to point out the advancing event horizon now making its way through the tavern,
and is horrified when the landlord's shirt changes. He runs out of the door to notice the tavern's
name change from that of \Gls{Keli} to her uncle, and realizes that fate is trying to reassert
itself on Sto Lat, through the creeping advance of the event horizon separating the two realities.

\subsubsection{\Gls{Death} saves a fisherman in Krull island from drowning}
\Gls{Death} finds a fisherman on Krull island get caught up by a powerful fish dragging him into
the river, and saves his life. The fisherman is angry at being returned to his miserable existence,
and is intrigued when the mysterious man in the black hood offers a cryptic answer as to why he
was rescued.

\subsubsection{\Gls{Mort} finds \Gls{ICutwell} in the palace}
\Gls{Mort} makes it to \Gls{ICutwell}'s house, and learns from his pet gargoyle, that he has been
taken by \Gls{Keli} to the palace. He notices the town guards putting up posters showing her face,
and crying out her name for the townsfolk to hear. He rides into the palace, by passing through the
gates, anxious to check if \Gls{Keli} has taken \Gls{ICutwell} as her lover.

\subsubsection{\Gls{ICutwell} explains the nature of history course-correcting}
\Gls{ICutwell} quickly figures out that \Gls{Mort} is the reaper that saved \Gls{Keli}'s life,
and is alarmed to hear about the event horizon closing in around Sto Lat. \Gls{ICutwell} explains
that the dome's job is to make it so that \Gls{Keli} was killed a week ago, and that \Gls{Mort}
had reaped the correct soul, thus setting history back on course.

\subsubsection{\Gls{Mort} realizes that \Gls{CAlbert} was a famous wizard on the Disc}
\Gls{ICutwell} opens a book on magical theory by \Gls{CAlbert}, the founder of Unseen University,
leading to \Gls{Mort} connecting the dots between the chef in \Gls{Death}'s realm and the wizard
who vanished many centuries ago. \Gls{ICutwell} surmises that \Gls{Mort} has until the next night
to try and stop the reality bubble from closing in, and reminds him about the guards outside
\Gls{Keli}'s room.

\subsection{}
\subsubsection{\Gls{Death} enjoys a party thrown by the Patrician of Ankh-Morpork}
\Gls{Death} participates in the costume party held by the Patrician of Ankh-Morpork, to celebrate
the tenth anniversary of his ascent to power. He learns about the concept of fun, as he joins the
conga-line heading snaking its way through the palace, and is determined to acquaint himself with
human pleasures.

\subsubsection{\Gls{Mort} tries to explain the danger to \Gls{Keli}'s life}
\Gls{Mort} enters \Gls{Keli}'s room and finds out that she is intent on facing her destiny out in
the world, away from the comforting embrace of her castle. Meanwhile, \Gls{ICutwell} investigates
the crossbow on her bedside table, and shoots \Gls{Mort} in the back with it, after recovering a
bolt buried in the wall.

\subsubsection{\Gls{Death} tries to amuse himself with at a back-alley gambling den}
\Gls{Death} goes to a dingy alleyway after the party, where a dice game is underway. He throws a
perfect set, and stops time when the goons try to gang up on him, suspecting that he is using
magic to rig the game. He walks away amused by their belief that games of chance hold sway over the
fates of men.

\subsubsection{\Gls{ICutwell} tests his hypothesis about \Gls{Mort} being partially immune to
    danger}
\Gls{ICutwell}'s crossbow bolt goes straight through \Gls{Mort} into the bedpost, leading him to
assume that \Gls{Mort} is immune to dangers he does not see coming. This is later confirmed when
\Gls{Mort} talks about a drink in the local tavern that did not affect him, in spite of being a
hard liquor meant to cause him great pain.

\subsubsection{\Gls{Death} gets drunk at the Mended Drum at closing time}
\Gls{Death} goes to the Mended Drum at closing time, and spends his entire bag of gold coins trying
out the exotic drinks displayed on the shelves. The barman tries to deal with the solitary customer
preventing him from closing shop by gently throwing him out of the bar, while telling him that he
is welcome to return at any time.

\subsubsection{\Gls{Mort} asks \Gls{Ysabell} to help him find \Gls{CAlbert}'s biography}
\Gls{Mort} wakes \Gls{Ysabell} up in the middle of the night, and asks for her help in setting the
timeline right for \Gls{Keli}. He believes that \Gls{CAlbert}'s biography might contain something
useful, and \Gls{Ysabell} leads him to the back-room of the library, where lives longer than five
centuries are held.

\subsubsection{\Gls{Ysabell} finds out how large \Gls{CAlbert}'s biography is}
\Gls{Ysabell} leads the way into the old room behind the library, and tries to find the sole book
still being written on, using the faint sound it might make. She finds the right shelf, and climbs
a ladder, to discover that the entire shelf is dedicated to \Gls{CAlbert}. \Gls{Death} spends the
night awake, sitting next to the Ankh river, wondering how he can capture the human experience
better.

\subsubsection{\Gls{CAlbert} is annoyed by \Gls{Mort} and \Gls{Ysabell} reading his biography}
\Gls{CAlbert} finds \Gls{Mort} and \Gls{Ysabell} in the library, just as \Gls{Mort} reaches the
point in his biography where he is due to push them off the ladder. \Gls{Ysabell} drops the heavy
tome on \Gls{CAlbert}, who rushes off in a huff, refusing to help \Gls{Mort} with his secret mission
to save \Gls{Keli}.

\subsubsection{\Gls{Death} tries to get a new job in Ankh-Morpork}
\Gls{Death} goes to a job broker in Ankh-Morpork, trying to make a change in his monotonous life
as the reaper of souls. The broker is allowed to witness \Gls{Death}'s true form for just a moment,
and fears for his life. \Gls{Death} calms him down, by sending away an angry customer, and reminding
the job broker that he had no marketable skills to speak of.

\subsubsection{\Gls{Mort} and \Gls{Ysabell} try to help \Gls{CAlbert} read \Gls{Death}'s ledger}
The next morning, \Gls{Mort} is woken up by \Gls{Ysabell}, who takes him to \Gls{Death}'s study.
They find \Gls{CAlbert} bemoaning the absence of \Gls{Death}, mumbling about the nodes that need to
be taken care of, with the right souls reaped at the right time. \Gls{CAlbert} tries to explain
that the course of history depends crucially on \Gls{Death} harvesting souls right when they are
meant to die, as \Gls{Ysabell} sets about reading the ledger of souls.

\subsubsection{\Gls{Death} works as a line cook in Ankh-Morpork}
\Gls{Death} takes up a job as line cook at one of Ankh-Morpork's seedier restaurants, and impresses
the owner with his speed and style. For the first time in his existence, \Gls{Death} feels happy,
and content in doing something that brings joy to others. His voice subconsciously becomes more
human, and less spectral.

\subsubsection{\Gls{ICutwell} tells \Gls{Keli} that her time may run out before the coronation}
\Gls{ICutwell} surveys the preparations for \Gls{Keli}'s coronation, and works up the courage to
go to her room, to deliver the bad news that the event horizon might converge on her before the
ceremony. He is impressed by the coronation gown that \Gls{Keli} tries out, calling it an heirloom
from many generations ago.

\subsubsection{\Gls{Mort} threatens \Gls{CAlbert} with a return to the Disc}
\Gls{CAlbert} and \Gls{Ysabell} examine the latest nodes worked out in \Gls{Death}'s ledger, as
\Gls{Mort} speaks with \Gls{Death}'s voice by accident. \Gls{Mort} is given two hourglasses by
\Gls{CAlbert}, who is then shocked when he is threatened with a return to the Disc. \Gls{Mort},
confident that he can control the spectral force inside him, reminds \Gls{CAlbert} that the deal he
struck was with \Gls{Death}.

\subsubsection{\Gls{Mort} receives some help from \Gls{CAlbert} in the form of a spell}
\Gls{Mort} has \Gls{Ysabell} fetch \Gls{CAlbert}'s biography, which reveals the inner workings of
his mind. \Gls{CAlbert} is persuaded to help \Gls{Mort} with the reality bubble, when faced with the
prospect of the Dungeon Dimensions, and writes down a spell that will slow time. \Gls{Mort} is
dismayed at having to reap the latest batch of two souls, on the opposite side of the Disc, and
returning to Sto Lat in time to save \Gls{Keli}.

\subsubsection{\Gls{Mort} witnesses the death of a Grand Vizier in the Agatean Empire}
After he hears \Gls{Binky} take off, \Gls{CAlbert} takes out his old robes and designs a makeshift
hat. He then initiates a teleportation spell, and vanishes from \Gls{Death}'s realm. Meanwhile,
\Gls{Mort} travels with \Gls{Ysabell} to the Agatean Empire, where the young emperor anticipates his
Vizier's attempt to poison him, and turns the tables. \Gls{Mort} reaps the Vizier's soul, and
notices all the monarchs he killed waiting for their revenge in the afterlife.

\subsubsection{\Gls{CAlbert} emerges at the Unseen University to perform the ritual to summon
    \Gls{Death}}
\Gls{CAlbert} appears in the Great Hall of Unseen University, and is disgusted by the statue
memorializing him. He zaps the statue to dust, and the commotion drags out the senior wizards from
the inner halls. He corners \Gls{Rince} in the Great Hall, and asks him to assemble the inner
council of the University, so that they might summon \Gls{Death} using a ritual.

\subsubsection{\Gls{CAlbert} tries to restore the University to its former glory}
\Gls{Mort} guides \Gls{Binky} to a jungle kingdom in Klatch, where a king is being taken by the
citizens to his ritual mummification, and consequent entombment in the pyramids. Meanwhile,
\Gls{CAlbert} sets about restoring order in the University, by outlawing alcohol and tobacco, along
with a compulsory exercise regimen for the residents.

\subsubsection{\Gls{Mort} and \Gls{Ysabell} attend to the last soul shortlisted by \Gls{Death}'s
    ledger}
\Gls{Mort} and \Gls{Ysabell} attend to the soul of a young woman, who is entombed along with the
dying Tsortean King in the pyramid, as he is summoned by \Gls{CAlbert}'s ritual. \Gls{Ysabell}
realizes that he is taking on more and more of \Gls{Death}'s qualities, as if being substituted
into the role of grim reaper.

\subsubsection{\Gls{Ysabell} stops \Gls{Mort} from being dragged into the ritual to summon
    \Gls{Death}}
\Gls{Ysabell} stops \Gls{Mort} from being dragged into the octarine portal with the wizards
waiting on the other side, and reminds him that he is still just the apprentice. At the University,
\Gls{CAlbert} demands more power to be channeled into the ritual, until the real \Gls{Death} is
pulled into the ritual circle from his job as a chef. \Gls{CAlbert} realizes too late that he is
trapped inside the circle along with \Gls{Death}.

\subsubsection{\Gls{Death} works out what \Gls{Mort} has been hiding from him}
\Gls{Death} uses his senses to realize that \Gls{Mort} has interfered with the fabric of reality,
and swears to go back to his original position as the grim reaper. \Gls{Rince} pretends to have
lost \Gls{CAlbert}'s staff, as he tries desperately to ask for it so that he might escape
\Gls{Death}'s clutches. Once the two of them return to \Gls{Death}'s House, the wizards breathe a
sigh of relief at avoiding a return to the old ways of the University.

\subsection{}
\subsubsection{\Gls{Mort} decides to make a desperate attempt to save \Gls{Keli}}
\Gls{Mort} wakes up from \Gls{Ysabell}'s punch, and realizes that the Death that was growing inside
of him is now gone with the summoning ritual. \Gls{Ysabell} reminds him that it might be too late
to save \Gls{Keli}, and \Gls{Mort} decides to race nightfall to Sto Lat, hoping to stay ahead of
the slow-moving light.

\subsubsection{\Gls{ICutwell} protects \Gls{Keli} from the elephant when it breaks loose}
\Gls{ICutwell} examines the approaching bubble of reality, and runs back to the Great Hall, where
an aging elephant has been selected as the ritual sacrifice for the coronation. The elephant
manages to break free from its chains, having sneaked some wine from the ceremonial goblet, and
charges out of the palace, sniffing its way home. In the ensuing commotion, \Gls{ICutwell} leaps
over \Gls{Keli} to protect her, and is surprised to see her uncle pointing a crossbow at them.

\subsubsection{\Gls{Keli} is crowned by \Gls{ICutwell} in a hasty ceremony}
\Gls{ICutwell} sees the reality bubble come through the walls of the palace, and tells \Gls{Keli}'s
uncle that his attempts at seizing power will all be futile, when the bubble collapses onto the
Princess. \Gls{ICutwell} performs an impromptu coronation, as \Gls{Mort} crashes into the Great Hall
and scares off \Gls{Keli}'s uncle. He then decides to take all four of them to \Gls{Death}'s realm,
hoping that time will freeze the collapsing of \Gls{Keli}'s reality bubble.

\subsubsection{\Gls{Mort} challenges \Gls{Death} for his friends' freedom}
Back in \Gls{Death}'s House, \Gls{Mort} is slapped by \Gls{Death}, and challenges him for the
freedom of \Gls{Keli} and \Gls{ICutwell}. \Gls{Ysabell} realizes that \Gls{Death} wishes to be
challenged, and will voluntarily accept defeat in order to escape the burdens of being the grim
reaper. \Gls{Death} duels against \Gls{Mort}, with both of them shattering many hourglasses lined
up along the shelves of the Sand Room.

\subsubsection{\Gls{Death} frees \Gls{Mort} and \Gls{Ysabell} from his service}
\Gls{Death} corners \Gls{Mort} as he eventually gives in to mortal exhaustion, and holds his
hourglass in front of him, with the last of the sand running out. He then turns it over, returning
\Gls{Mort} and \Gls{Ysabell} to the Disc, and freeing them from his realm. A while later,
\Gls{Mort} and \Gls{Ysabell} attend the wedding of \Gls{Keli} and \Gls{ICutwell}, having been
crowned the rulers of Sto Helit using a special deal struck by \Gls{Death} with the Gods.

\subsubsection{\Gls{Death} reconciles his grudges with \Gls{Ysabell} and \Gls{Mort}}
\Gls{Death} attends the wedding, and gives \Gls{Mort} a late present for his own marriage. He
promises to take \Gls{Mort}'s proposal of stepping in as a substitute into consideration, and leaves
to fulfil his duty.