\section{Moving Pictures}


\subsection{}
\subsubsection{\Gls{Deccan}'s soul is collected by \Gls{Death}}
\Gls{Deccan}, the last Keeper of the Holy Wood, dies in his remote seaside shack made of driftwood.
\Gls{Death} comes to reap his soul, and learns that some very important force has been kept out
of the Disc by a long line of guardians, that would end with him.

\subsubsection{\Gls{Dibbl} watches an alchemist marvel at his latest accidental discovery}
\Gls{Dibbl} watches an alchemist come out of his Guild workshop after an explosion blows a hole in
the wall. He mumbles something about cellulose being unstable when heated, and heads back inside to
document his findings. The ghost of the idea liberated from \Gls{Deccan}'s hovel finds \Gls{Dibbl}
a suitable host, and leaps into his mind.

\subsubsection{The \Gls{Bursar} tries to adjust to \Gls{Ridcu} being the new Archchancellor}
The \Gls{Bursar} of Unseen University feels satisfied with the choice \Gls{Ridcu} as the new
Archchancellor, since he is too busy hunting and fishing to look into the day-to-day administration.
As the \Gls{Bursar} hears the last of the explosions from the Alchemists' Guild, the small hole
next to \Gls{Deccan}'s hut starts to enlarge.

\subsubsection{\Gls{Vetina} learns about some exciting new experiment at the Alchemists' Guild}
A spy within the Alchemists' Guild reports to \Gls{Vetina} that they had indulged in some
experiment behind closed doors at night, which involved a rapid clicking noises and flickering
white light. He dismisses the reports as yet another one of their eccentric discoveries, as
\Gls{Silfish}, the President of the Guild, tries to contain his excitement about the new discovery.

\subsubsection{\Gls{Silfish} and his council of Alchemists talk about moving pictures}
\Gls{Silfish} reminds one of his inner council members \Gls{Lully}, that the wizards would take
offense at someone outside the university doing magic. The Guild Secretary \Gls{Sendi} agrees that
their new experiment only involves salamanders and some imps. \Gls{Peavie}, the Treasurer of the
Guild, reminds them of the possibilities for revenue by entertaining the masses.

\subsubsection{\Gls{Silfish} suggests moving to Holy Wood to make more films}
\Gls{Silfish} suggests shooting their next film at \Gls{Deccan}'s abandoned beach, and wonders
how the idea came to him. Meanwhile, \Gls{Peavie} shows them freshly made popcorn, and the
Alchemists find it strangely appropriate for snacking while watching film. \Gls{Silfish} decides to
get ready for the move to Holy Wood, the secluded stretch of beach that was \Gls{Deccan}'s home for
the last few decades.

\subsubsection{\Gls{Tugel} prepares to barely fail the coming exams}
The \Gls{Bursar} explains the orangutan in the library to \Gls{Ridcu}, before showing him the latest
exam results, to point out some \Gls{Tugel}'s scores. Meanwhile, \Gls{Tugel} plans to remain a
student in perpetuity to exploit a generous endowment from his father that requires good enough
performance in the exams to keep the money flowing. \Gls{Ridcu} decides to present him an exam
with a single question to force him to either pass or drop out.

\subsubsection{\Gls{Tugel} runs into \Gls{Silfish} next to the University}
On his way back from the Mended Drum, \Gls{Tugel} runs into \Gls{Silfish}, now a casting director
on the lookout for potential actors. He hands him a business card stating the address of the studio
in Holy Wood, and tells \Gls{Tugel} that he is one of the few people uninterested in appearing in
the moving pictures.

\subsubsection{\Gls{Silfish} waits for a crowd to assemble for his cinemascope}
\Gls{Silfish} goes back to setting up his projector and cloth screen, as \Gls{Dibbl} arrives to
peddle his sausages at the outdoor show. After a crowd gathers to watch the supposed shadow play,
\Gls{Silfish} gives his speech introducing the groundbreaking new technology, and starts cranking
the cinemascope. \Gls{Detri}, now a hired goon doing security gigs, shows up along with
\Gls{Gaspode}, the sentient mongrel.

\subsubsection{\Gls{Stibb} happens to switch question papers with \Gls{Tugel} in the exam}
The next day, \Gls{Stibb} spills ink all over his desk, and asks the chief invigilator to let him
switch to \Gls{Tugel}'s empty desk. He is surprised to see a single question asking what the
student's name is on the paper, and answers it, believing that the ridiculous exam is divine
intervention.

\subsubsection{\Gls{Tugel} blows off his examination for a pilgrimage to Holy Wood}
\Gls{Tugel} finds himself drawn subconsciously to Holy Wood, along with \Gls{Detri}, \Gls{Gaspode}
and \Gls{Dibbl}, who has turned his sausage business over to a dwarf. Meanwhile, a malicious
entity from the Dungeon Dimensions watches the affairs of the Discworld with great interest, having
been drawn by the emergence of moving pictures. After a while, \Gls{Tugel} makes it to Holy Wood,
where the first few wooden houses are being built, and begins the search for a meal.

\subsubsection{\Gls{Tugel} sneaks into \Gls{Silfish}'s studio}
\Gls{Tugel} runs into an actress on her break, and learns that newcomers like him have to wait
forever to be noticed by a casting agent in Holy Wood, to get their chance to act in the moving
pictures. Desperate for a meal, he takes out \Gls{Silfish}'s business card, and decides to sneak
into his studio, instead of waiting in line at the entrance.

\subsubsection{\Gls{Tugel} receives an acting job from \Gls{Silfish} at his studio}
\Gls{Tugel} is happy to see \Gls{Silfish} remember him from the night of the mugging in Ankh-Morpork
and asks for some work in the studio. \Gls{Silfish} is forced to give him an acting role, when it
turns out he has no skills to do any backstage or production work. He sends for his chief cameraman
\Gls{GBird}, who explains that little demons inside the cinemascope capture the pictures on the
cellulose reels.

\subsubsection{\Gls{Dibbl} acquires the role of manager at \Gls{Silfish} studios}
\Gls{Dibbl} hires \Gls{Detri} to knock out the man guarding the gates of \Gls{Silfish}'s studio, and
strolls in with his nest egg safely tucked in his leather bag. He corners \Gls{Silfish} into
accepting his services as a manager, when he realizes how much revenue could come from ticket sales
and concession stands.

\subsubsection{\Gls{Tugel} learns about the skills needed for movie acting}
\Gls{Tugel} learns about the imps powering the video recorder and the salamanders in the cinemascope
which is projected onto the screen. \Gls{GBird} tells him that movie acting is mostly standing
still and looking muscular, unlike stage acting, which involves expressions and dialogue delivery.
He then goes to \Gls{Silfish}'s office, where \Gls{Dibbl} is busy demonstrating his advertising
scheme.

\subsubsection{\Gls{Dibbl} tries to make \Gls{Silfish} understand his marketing plans}
\Gls{Dibbl} explains his idea of taking endorsement deals with local restaurants, as well as showing
posters for upcoming movies at the end of each show. \Gls{Tugel} is confident in his marketing
skills, given how people buy his sausages more than once. \Gls{Silfish} is flummoxed by \Gls{Dibbl}
pointing out the need for spectacles and grand set pieces in the movies, over simple imitiation of
theatre acts.

\subsubsection{\Gls{Dibbl} and \Gls{Silfish} start shooting their next movie}
When an argument between \Gls{Dibbl} and \Gls{Silver} delays shooting, \Gls{Tugel} starts chatting
with his fellow troll actors, who are usually used as stuntmen fighting the main character. One
of the trolls decides to adopt the stage name \Gls{Rock}. \Gls{Tugel} is relieved to learn that
the combat is faked, and tries to match the troll clubs when they swing towards him. \Gls{Silfish}
is annoyed that the actress is engaged in another shooting due to some film exploding earlier.

\subsubsection{\Gls{Tugel} kisses his co-star at the end of his first movie}
\Gls{Tugel} kisses the actress after the end of the final fight scene, as \Gls{Dibbl} insists on
keeping the camera rolling in spite of \Gls{GBird}'s protests. He is confident that romance and
grand spectacle will pull in more audiences, and asks \Gls{Silfish} to try and make bigger reels
to lengthen the duration of the movies. \Gls{Tugel} tells \Gls{Ginger} later that he lost his mind
to some disembodied voices which compelled him to kiss her.

\subsubsection{\Gls{Ridcu} is notified of an old artifact in the University making strange noises}
At the Unseen University, \Gls{Ridcu} and the \Gls{Bursar} respond to \Gls{Whitlow}'s summons,
about an ornate vase that seems to be making loud noises and ejecting lead pellets at her. The
\Gls{Bursar} recognizes the sculpted elephants hanging from the sides of the vase, and recalls it
as the work of former Archchancellor \Gls{Riktor}. None of them work out the fact that it is a
device meant to measure rifts in reality, like a seismometer.

\subsection{}
\subsubsection{\Gls{Tugel} and \Gls{Ginger} lose their job as actors in \Gls{Silfish}'s studio}
At a newly opened mess hall in Holy Wood, \Gls{Ginger} asks \Gls{Tugel} to purchase two bowls of
stew, and introduces him to her friends as the star of the first three reel movie. Back at the
studio, \Gls{Silfish} dismisses \Gls{Tugel} and \Gls{Ginger} for being late, after finishing the
day's shoot. \Gls{Ginger} is dismayed at the prospect of returning to her village, and leaves
\Gls{Tugel} alone to spend the night on the beach.

\subsubsection{\Gls{Dibbl} gets the posters for his next movie from Ankh-Morpork}
\Gls{Dibbl} goes to Ankh-Morpork to source the posters and placards for his marketing campaign,
and starts to notice how natural movie-making seems to people in Holy Wood. Meanwhile,
\Gls{Riktor}'s magic measuring device ejects a pellet with such force that \Gls{Ridcu}'s bottle
shatters.

\subsubsection{\Gls{Tugel}'s movie is sold by \Gls{Dibbl} to \Gls{BezamP}}
\Gls{Tugel} wakes up on the beach, and finds strange looking marine life when he dives underwater.
He notices someone else building a campfire on the strand, and goes there hoping to find some food.
Meanwhile, \Gls{Dibbl} approaches \Gls{BezamP}, the owner of a failing movie theater, with his new
movie starring \Gls{Tugel}. \Gls{BezamP} is intrigued by the poster, and decides to take a chance on
the new movie over the boring documentary scheduled for the day.

\subsubsection{\Gls{Tugel} finds \Gls{Ginger} working as a waitress}
\Gls{Tugel} finds a book chronicling the daily life of \Gls{Deccan} and his predecessors in his
abandoned hut, and takes it after burying his corpse on the beach. He returns to Holy Wood, to
find \Gls{Ginger} working as a waitress, and realizes he will need to look for a new job himself.
Meanwhile, \Gls{BezamP} and his wife are overwhelmed by the popular response to \Gls{Dibbl}'s new
action movie.

\subsubsection{\Gls{Dibbl} hurries to Holy Wood to secure a contract with \Gls{Ginger} and
    \Gls{Tugel}}
\Gls{BezamP} asks \Gls{Dibbl} to make more movies with the starring pair, given the response of
the audiences to their performance. \Gls{Dibbl} realizes his blunder in firing them, and hurries off
to Holy Wood to find the two of them. Meanwhile, \Gls{Rock} finds \Gls{Tugel} on the streets of
Holy Wood, and tells him that he has a starring role in the next troll movie.

\subsubsection{\Gls{Tugel} finds \Gls{Gaspode} in a dark alley of Holy Wood}
\Gls{Tugel} is taken to a troll bar where \Gls{Rock} buys him drinks, and starts talking about
cosmetic surgery to make himself look better on camera. \Gls{Tugel} escapes the bar and goes to a
lonely alley where \Gls{Gaspode} finds him. Meanwhile, \Gls{Dibbl} makes a show of asking
\Gls{Frunt}, the head chef of the mess hall, about \Gls{Tugel}. He tells the diners that he intends
to make \Gls{Tugel} a star, and continues the search.

\subsubsection{\Gls{Gaspode} talks to \Gls{Tugel} about the strangeness of Holy Wood}
\Gls{Gaspode} tells \Gls{Tugel} that it ran away from Ankh-Morpork to escape the life of a caged
curio, and tells him that he looks haunted by Holy Wood dreams. \Gls{Detri} is smitten by \Gls{Ruby}
as she performs in the troll bar, and \Gls{Dibbl} asks around for \Gls{Tugel}'s whereabouts.
Meanwhile, \Gls{Gaspode} talks about his own dreams in which he is a hero that saves the lives of
children, and drags \Gls{Tugel} to meet someone important.

\subsubsection{\Gls{Gaspode} leads \Gls{Tugel} to the other sentient animals in Holy Wood}
On Holy Wood hill, \Gls{Gaspode} leads \Gls{Tugel} to a group of other sentient animals, who had
all migrated from Ankh-Morpork, after suddenly gaining the ability to think and talk. \Gls{Tugel}
asks them about \Gls{Deccan}, and the rabbit tells him that the old man simply chanted something
at regular intervals on the hill, and had fish delivered to him from faraway shores.

\subsubsection{\Gls{Gaspode} helps \Gls{Tugel} and \Gls{Ginger} land a bigger contract}
\Gls{Ginger} runs into \Gls{Tugel} on Holy Wood hill, and \Gls{Dibbl} finds them shortly after.
\Gls{Gaspode} negotiates a much higher daily rate for the two lead actors, when \Gls{Dibbl} tries
to rehire them, and tags along as \Gls{Tugel}'s agent. Meanwhile, \Gls{Dibbl} is busy considering
the novelty of an intelligent dog that can perform tricks for his next movie.

\subsubsection{\Gls{Tugel} arrives at the shooting spot for his next movie}
\Gls{Ridcu} gathers the rest of his inner council just in time for \Gls{Riktor}'s vase to shoot
even more lead pellets at the wall, leaving the wizards afraid for their lives. The next morning,
\Gls{Tugel} is dragged by \Gls{Detri} to the site of the next shoot, where a single camel is being
readied for a chase scene.

\subsubsection{\Gls{Dibbl} prepares the first shoot of the day}
\Gls{Dibbl} leaves the poster printer flummoxed by his strange slogan for the movie, and turns
to \Gls{Tugel} with the costume for the shoot. \Gls{Dibbl} nephew \Gls{Soll}, who is the new
assistant director, reminds him that the movie requires a night-time scene, when they cannot film.
\Gls{Ginger} suggests inserting dialogue that would indicate a bright full moon, and \Gls{Soll}
agrees reluctantly.

\subsubsection{\Gls{Tugel} and \Gls{Ginger} complete their first shoot as stars}
\Gls{Tugel} and \Gls{Ginger} break out of a trance at the end of the shoot, as the others behind
the camera remain awed by their performance. \Gls{Tugel} asks \Gls{Rock} what he did during the
shoot, and learns that he spoke a strange language while following \Gls{Dibbl}'s script faithfully.
After the shoot, \Gls{Tugel} drags \Gls{Gaspode} to a quiet tent, and asks him to explain his
theories about Holy Wood.

\subsubsection{\Gls{Gaspode} tries to tell \Gls{Tugel} about the Holy Wood gripping his mind}
\Gls{Gaspode} explains that Holy Wood has affected the eyes of \Gls{Tugel}, \Gls{Ginger} and
\Gls{Dibbl}, making them behave as if making movies is the only reason they exist. Meanwhile in
deep Klatch, cattle herder \Gls{Azhu} starts to take stock of his new menagerie of animals, as
his stable-boy \Gls{MBu} finishes cleaning up after the handful of elephants. They think about the
order placed by someone in Ankh-Morpork for a thousand elephants, to be paid for in cash.

\subsubsection{\Gls{Ginger} talks about the new jobs available in Holy Wood}
\Gls{Tugel} is shocked to see the change in \Gls{Ginger}, as she starts talking about her
childhood in a remote village, and of the opportunities opening up for people like her because of
Holy Wood. She believes that the next innovation in moving pictures would be the sound added to it,
and looks forward to becoming the most famous person on the Disc.

\subsubsection{The \Gls{Bursar} finds out the purpose of \Gls{Riktor}'s vase}
\Gls{Ridcu} is busy poring over the forest of documents that are the legacy of \Gls{Riktor}, as
the \Gls{Bursar} walks in with news of the vase being moved to a strong room. They hear it eject
more pellets in the distance, and the \Gls{Bursar} snatches a page showing the vase's blueprint,
after he realizes it is a device for measuring rifts in reality.

\subsubsection{\Gls{Ruby} asks \Gls{Detri} to be more modern in his courting rituals}
\Gls{Gaspode} suggests asking for a day off when \Gls{Tugel} bemoans his inability to investigate
the Book of Film he took from \Gls{Deccan}. Meanwhile, \Gls{Ruby} asks \Gls{Detri} to perform some
new courtship rituals based on ideas that come to her out of nowhere. He takes the job of finding
some pretty flowers for her and learning a song very seriously, in the hopes of impressing her.

\subsubsection{\Gls{Gaspode} spots \Gls{Laddie} arriving at \Gls{Dibbl}'s studio}
\Gls{Gaspode} listens intently as \Gls{Tugel} negotiates a paid day off from \Gls{Dibbl}, using the
competing studios as leverage. A new hunting dog from the Ramtop mountains named \Gls{Laddie} is
brought in by \Gls{Soll}, to play a part in \Gls{Dibbl}'s next production. \Gls{Gaspode} is
jealous of the attention given to \Gls{Laddie}, and horrified by its dog-like intelligence ready to
obey every command as long as a suitable reward is waiting at the end.

\subsubsection{\Gls{Gaspode} is impressed by the revenue coming into \Gls{Dibbl}'s studios}
\Gls{Gaspode} wonders why Holy Wood called out to him if not to be a big movie star, as \Gls{Tugel}
talks about the coming paid vacation. He then reminds \Gls{Tugel} to renegotiate his salary as a
percentage of the profits, considering how much \Gls{Dibbl} was making from his shows.

\subsection{}
\subsubsection{\Gls{Gaspode} negotiates a better meal for \Gls{Laddie}}
\Gls{Tugel} watches \Gls{Gaspode} coaching \Gls{Laddie} on how to appeal for a better meal, and
marvels as the show-dog tips over his bowl, forcing \Gls{Detri} to fetch him some raw steak from
the mess hall. \Gls{Gaspode} asks to see the book to check if he can read the script of the older
diary entries, and points out the pictograms of a knight with a sword next to a door.

\subsubsection{The \Gls{Libra} is deeply interested in a segment of film from the newest movie}
After a showing of the latest movie, \Gls{BezamP} is shocked to see the \Gls{Libra} rip off a
segment of film before leaving the theater. When he sticks the pieces of film back together, he
realizes that the missing segment simply showed the bandits chasing the hero on camels. Meanwhile,
\Gls{Gaspode} spots \Gls{Laddie} at the beach, and asks \Gls{Tugel} to keep it entertained by
playing fetch with it.

\subsubsection{The \Gls{Libra} goes to the chamber of the Necrotelicomnicon}
The \Gls{Libra} proceeds to the restricted section of the Library, and finds the chamber holding
the cursed tome called the Necrotelicomnicon. He dons the protective armor needed to stand in
the tome's presence, and prepares to open the stone door guarding the chamber. Meanwhile,
\Gls{Tugel} finds \Gls{Laddie} howling over the unconscious body of \Gls{Ginger}, at the entrance
to a stone temple on Holy Wood Hill.

\subsubsection{\Gls{Tugel} and \Gls{Gaspode} find \Gls{Ginger} at the Holy Wood temple}
\Gls{Gaspode} believes that the sudden appearance of the stone temple is a bad omen, and suggests
getting as far away as possible. Later in the night, the walls of the temple are eroded by the wind
to reveal a faint sculpture of an armored knight, as the door starts to creak open ever so slightly.

\subsubsection{The \Gls{Libra} reads up on the legend of Holy Wood destroying a civilization}
\Gls{Ruby} is exasperated by \Gls{Detri} dragging an entire tree to the back alley of her cabaret,
in an attempt to modernize his courting rituals. Meanwhile, the \Gls{Libra} reads the legend of an
ancient civilization that was destroyed by monsters pouring out of the Gate of Holy Wood. A
guardian in golden armour had then risen to guard the Gate, in exchange for someone chanting the
legend of Holy Wood three times a day.

\subsubsection{\Gls{Tugel} takes \Gls{Ginger} back to her room}
\Gls{Azhu} lets \Gls{MBu} marshal the other elephant herds as the march to Ankh-Morpork begins, with
the assembled group of three hundred elephants. \Gls{MBu} dismisses his concerns about the large
chasms with no bridges available to cross them. \Gls{Tugel} takes \Gls{Ginger} to her home, guided
by the nose of \Gls{Gaspode}. Inside, he discovers a shrine to herself, with lots of posters
adorning the walls.

\subsubsection{\Gls{Tugel} and \Gls{Gaspode} leave \Gls{Ginger}'s room after depositing her}
\Gls{Tugel} senses some alien force similar to magic massed inside \Gls{Ginger}'s room, and decides
to leave hastily. \Gls{Gaspode} believes that she was trying to sneak into the Holy Wood Temple,
under the influence of a sinister force. \Gls{Tugel} goes back to the beach, leaving \Gls{Gaspode}
to wander around with \Gls{Laddie}, who is eventually picked up by her trainers.

\subsubsection{\Gls{Gaspode} listens to the other sentient animals talk about Holy Wood Hill}
\Gls{Gaspode} is surprised to find the other sentient animals having fled Holy Wood Hill, on account
of some eldritch phenomena like voices in the air and sparks in their fur. He dismisses the idea
that Holy Wood might be interested in a cat-and-mouse double act for their movies, and is worried
about the spirit of Holy Wood leaking into the Disc.

\subsubsection{\Gls{Dibbl} writes the script for a new movie after a vivid dream}
\Gls{Dibbl} wakes up from one of his dreams, where he imagines Ankh-Morpork in flames, and starts
to write a movie script based on a romance in the backdrop of a civil war. He insists on having a
mass of elephants as set-pieces for his film, as a way to grab viewer attention. \Gls{Gaspode} spots
\Gls{Ginger} sleepwalking to Holy Wood Hill, and decides to follow her.

\subsubsection{\Gls{Gaspode} gets \Gls{Ginger} to wake up from her trance}
\Gls{Gaspode} sees visions of life as a well-loved dog and realizes that the magic leaking out of
Holy Wood Temple is hypnotizing the humans with similar dreams. He decides not to bite \Gls{Ginger}
in order to break her out of the trance, and nuzzles her knee instead. \Gls{Ginger} wakes up, and
immediately runs back to town, with \Gls{Gaspode} on her trail. The door of the Temple opens a
bit further, after they leave.

\subsubsection{\Gls{Tugel} sees \Gls{Dibbl} busy with erecting sets for his latest movie}
\Gls{Tugel} reaches \Gls{Dibbl}'s studio the next day, to see him arguing with \Gls{Silfish} about
the cost of recreating a set of Ankh-Morpork. He sacks \Gls{Silfish} when his vision is questioned,
and asks \Gls{Soll} to prepare the shooting sets as soon as possible. \Gls{Dibbl} is confident that
setting fire to his model city at the climax of the movie will cement it as the best one ever made
in Holy Wood.

\subsubsection{\Gls{Tugel} learns about \Gls{Ginger}'s sleepwalking}
As \Gls{Dibbl} explains the plot of his new civil-war movie, \Gls{Tugel} points out the need to
fill it with secondary plots to justify its long run-time. Later, \Gls{Tugel} is surprised when
\Gls{Gaspode} reports the night's events to him regarding \Gls{Ginger} and her sleepwalking. He
then proceeds to the set, to find \Gls{Soll} trying desperately to herd the background actors and
other cast members, while keeping \Gls{Ginger} placated.

\subsubsection{\Gls{Ginger} asks \Gls{Tugel} to help her with the night-time trances}
As \Gls{Soll} enters an argument with \Gls{Dibbl} about adding advertisements to the dialogue,
\Gls{Ginger} drags \Gls{Tugel} along for a private chat. She asks him to come to her room at night,
to stop her from sleepwalking to the Holy Wood Temple again. The two of them eventually return to
the set, where \Gls{Soll} is sorting out the last of the reframed dialogue cards.

\subsubsection{\Gls{Soll} takes over the direction of the civil-war movie}
\Gls{Soll} oversees the grand battle scene of the civil-war movie, as \Gls{Dibbl} notices the
inventive advertising hidden in the banners of the two armies. Meanwhile, \Gls{Riktor}'s vase starts
shooting lead pellets at a much higher pace. After the shoot ends, the entire set is burned at the
climax of the movie, with \Gls{Dibbl} promising not to tarnish the script with his marketing ideas.

\subsubsection{\Gls{Laddie} and \Gls{Gaspode} free \Gls{Tugel} from his bindings}
In his study, the \Gls{Bursar} reads \Gls{Riktor}'s description of his reality rift measurement
device, and works out that it is spitting pellets at a thousand times over the safe limit.
\Gls{Tugel} finds himself tied to \Gls{Ginger}'s chair, and realizes that he must have dozed off as
he kept watch by her bed. He asks \Gls{Gaspode} for help, and is surprised to see him fetch
\Gls{Laddie} to chew through the blankets.

\subsubsection{\Gls{Tugel} and the two dogs attempt to rescue \Gls{Ginger}}
\Gls{Tugel} relents to \Gls{Gaspode}'s suggestion of going into the Temple after \Gls{Ginger}, and
makes a torch out of some reeds. When the torch runs out, the darkness is momentarily brightened
by a flash in the distance, leaving him blinded for some time. He finds an ancient theater with some
seats still occupied by skeletons, and heads to the massive screen on the raised podium.

\subsubsection{\Gls{Tugel} finds \Gls{Ginger} in the ancient theater}
\Gls{Tugel} finds \Gls{Ginger} holding a bright torch behind the projection screen, and is
horrified when she asks him to run away in a strange voice. When he accidentally pulls a lever
causing a hidden pit to rise up from the theater floor, \Gls{Ginger}'s trance breaks, and she asks
him to help her escape.

\subsubsection{\Gls{Tugel} and \Gls{Ginger} are trapped in the Temple}
\Gls{Tugel} is dismayed to see the tunnel leading out of the temple collapse, and asks \Gls{Gaspode}
to see if he can squeeze through an opening. The two dogs escape, promising to bring back help,
leaving \Gls{Tugel} alone with \Gls{Ginger} in the darkness. \Gls{Laddie} manages to get the trolls
in their all-night bar to follow him to the Temple, while \Gls{Gaspode}'s pleas for help are
completely ignored.

\subsubsection{\Gls{Rock} and his troll friends rescue \Gls{Tugel} and \Gls{Ginger}}
\Gls{Rock} and the other trolls dig \Gls{Tugel} out of the collapsed corridor, and he hastily
tells them that he had gone there with \Gls{Ginger} for some privacy. \Gls{Ginger} realizes that
the truth about the demonic force controlling her mind was best kept under wraps, and decides not to
object. The rest of the corridor collapses a short while after the trolls leave via the Temple's
front door.

\subsubsection{\Gls{Tugel} and \Gls{Ginger} set out for Ankh-Morpork}
\Gls{Death} comes to the all-night Holy Wood bar to drink alongside \Gls{Detri} and \Gls{Silfish},
who are each lost in their own misery. The next morning, \Gls{Tugel} wakes up to find Holy Wood
engulfed in a thick fog. \Gls{Gaspode} leads him to \Gls{Dibbl}'s studio, where he is waiting with
the finished reels of his new movie, ready to travel to Ankh-Morpork. \Gls{Tugel} gets on the
carriage, to find \Gls{Ginger} already on it, along with both dogs.

\subsubsection{The inner council of Wizards decide to see the civil war movie}
\Gls{Dean} and the others in the inner council of Wizards pass along the poster for \Gls{Dibbl}'s
new movie, and think about bypassing the law stopping them from going out to see movies. They
eventually agree to hide their decision from \Gls{Ridcu}, and dismiss the idea that the lead actor
resembles \Gls{Tugel}.

\subsubsection{The inner council of wizards try to sneak into a movie theater incognito}
\Gls{Dean} and the others help haul \Gls{WPoons} up over the wall, seated on his elaborate
wheelchair. They then decide to wear false beards and take off their hats in order to hide from
their students and staff at the theater.

\subsection{}
\subsubsection{\Gls{Ridcu} helps the \Gls{Bursar} wake up, and listens to his warnings}
Back at the University medical room, the \Gls{Bursar} is woken up by \Gls{Ridcu}, and immediately
starts rambling about the threat to the fabric of reality. Meanwhile, the \Gls{Dean} and the rest
of the council are forced to queue at the movie theater, until the arrival of the stars causes a
stampede. \Gls{Ginger} is alarmed by the crowds thronging the red carpet laid out at the entrance
to the theater.

\subsubsection{\Gls{Tugel} and \Gls{Ginger} greet the crowd at the movie premiere}
\Gls{Tugel} and \Gls{Ginger} observe the dignitaries lined up to greet them at the theater, as
they smile and wave at the crowds on either side of the red carpet. Meanwhile, \Gls{Gaspode} leads
\Gls{Laddie} to his regular haunts, in search of the regular offal treats. \Gls{Ridcu} unveils a
map of the Disc, and traces the direction shown by \Gls{Riktor}'s machine, until he reaches Holy
Wood. The \Gls{Bursar} reminds him that this was the location of the Alchemist Guild's latest
venture.

\subsubsection{\Gls{WPoons} and the wizards prepare to watch the movie}
\Gls{Ridcu} observes a heavy fog in his magic surveillance mirror, and decides to go the movie
premiere with the \Gls{Bursar} to investigate \Gls{Riktor}'s warning. \Gls{Runes} purchases two
tickets for himself and \Gls{WPoons}, and the other wizards decide to sneak in through the toilets
at the back entrance. Once inside, \Gls{WPoons} pulls out his purse and asks them to buy some food
from the concession stands.

\subsubsection{\Gls{Vetina} watches his first movie}
\Gls{Vetina} is intrigued by the adoration for the two movie stars, as he sits down next to them
at the balcony. He spots \Gls{Soll} chastising \Gls{Dibbl} for the advertisements he had tried to
edit into the climax of the movie, and wonders why the lights are being dimmed. Eventually,
\Gls{BezamP}'s daughter starts the screening by playing her pipe organ, as \Gls{Ginger} and
\Gls{Tugel} are reminded of the similarity to the theater inside the Holy Wood Temple.

\subsubsection{\Gls{Gaspode} helps \Gls{Tugel} interrupt the screening}
\Gls{Gaspode} shakes \Gls{Tugel} out of the movie trance, and gets him to investigate the projection
room. After some trial and error, \Gls{Tugel} finally manages to stop the movie, and is horrified
to see the images still moving on the screen. Eventually, the giant projection of \Gls{Ginger} steps
out onto the podium, smashing the ground with every footfall.

\subsubsection{\Gls{Tugel} tries to burn down the theater to stop more monsters escaping}
\Gls{Tugel} helps the theater audience evacuate, as the giant \Gls{Ginger} steps out into the city
by breaking through the walls, and starts laying waste to entire buildings. He decides to heap
some rolls of explosive film at the screen to destroy it, but fails to find any matches in the
projection room.

\subsubsection{\Gls{Gaspode} and \Gls{Laddie} seemingly die trying to blow up the theater}
\Gls{Gaspode} and \Gls{Laddie} volunteer to light the explosive film with a torch, and run into the
theater. \Gls{Gaspode} loses one of his legs, when the monster bites it off in an effort to stop the
film being lit. \Gls{Laddie} picks him up in its mouth and tries to get out of the theater in time.
Meanwhile, \Gls{Tugel} decides to use Holy Wood Magic to summon a horse and sword to chase down the
escaped monster.

\subsubsection{\Gls{Ginger} tries to corner the monster, after realizing the rules binding it}
\Gls{Stibb} is struck by some pellets as \Gls{Riktor}'s device explodes, overloaded by the monster
coming straight for the University Library, to absorb the magic stored in its books. The \Gls{Libra}
fails in his attempt to stab the monster with a pike, as it picks him up to hold him against its
face. \Gls{Ginger} works out that the monster is constrained by the rules of Holy Wood, and asks
the wizards to conjure illusions of flame to scare it.

\subsubsection{\Gls{Tugel} chases the monster up the Tower of Art}
The monster climbs the Tower of Art in desperation, holding the \Gls{Libra} in one of its hands.
\Gls{Tugel} climbs the spiral staircase inside the Tower using the power of Holy Wood Magic to
illuminate his way up. He invokes his boundless stamina and strength as required by the movies to
speed up his ascent up the treacherous stairs.

\subsubsection{The monster is forced to fall to its death}
At the top of the Tower of Art, \Gls{Tugel} tries to distract the monster when he realizes that it
needs to keep focused on maintaining its shape or risk disintegration. \Gls{Ridcu} arrives by
flying broomstick to help him with his crossbow, as the \Gls{Bursar} tries desperately to keep them
airborne. Eventually, \Gls{Tugel} summons a lightning bolt that disorients the monster, making it
fall off the Tower to its death.

\subsubsection{\Gls{Tugel} works out the true purpose of the Book of the Film}
\Gls{Tugel} realizes that the Book of Film is supposed to be read from right to left, when he asks
the \Gls{Libra} to decipher the pictograms in it. He asks \Gls{Ginger} to help him return to Holy
Wood and seal the Temple, in order to stop more monsters from leaking into the Disc. \Gls{Tugel}
and \Gls{Ginger} reach Holy Wood by summoning an imaginary chariot, with \Gls{GBird} following along
with the camera rolling.

\subsubsection{\Gls{Tugel} and \Gls{Ginger} reach Holy Wood}
\Gls{Tugel} tells \Gls{Ginger} that everyone summoned to Holy Wood is a descendant of the
inhabitants who had faced the last coming of the monsters, and that the knight represented a
guardian keeping them at bay. He tells her that she is a descendant of some sort of priestess, who
was tasked with keeping the tale of Holy Wood alive, and singing to the guardian everyday to keep
him awake.

\subsubsection{\Gls{Tugel} and his party try to break the spell of Holy Wood Magic}
\Gls{Tugel} works out that the residents of Holy Wood have been summoned to the ancient theater, and
finds \Gls{Detri} holding up the collapsed entrance. The \Gls{Libra} gets some boulders to take up
the load, allowing \Gls{Detri} to rush into the theater, where the ancient splendour of the theater
tries to merge with the ruined present. He finds the residents glued to their seats, staring at the
projection screen in a trance.

\subsubsection{\Gls{Tugel} raises the guardian of Holy Wood from his slumber}
\Gls{Tugel} realizes that the curse of silence can be broken by a gong next to the statue of the
knight, and asks \Gls{Detri} to try and bang the rusted hammer onto the gong. This breaks the spell
of silence, and awakens the knight. The audience are released from their hypnosis, and manage to
run away from Holy Wood Hill, as the monsters fight the knight, leading to the destruction of the
town in its entirety.

\subsubsection{\Gls{Laddie} and \Gls{Gaspode} are saved by Holy Wood Magic}
The last remains of Holy Wood Magic slowly dissipate, as \Gls{Ruby} decides to take the initiative
with \Gls{Detri}. Meanwhile, \Gls{Ginger} thinks fondly about her time as a star, and tells
\Gls{Tugel} that a future might still be possible for the two of them. When \Gls{Death} comes for
\Gls{Laddie} and \Gls{Gaspode}, as they lay dying under the rubble of \Gls{BezamP}'s theater, the
Holy Wood Magic fills their hourglasses, saving their lives.