\section{Night Watch}


\subsection{}
\subsubsection{\Gls{Vimes} deals with the latest attempt on his life by a Guild Assassin}
\Gls{Vimes} comes out of his manor to investigate the latest foiled attempt on his life, and finds
a trainee assassin sent on a mission to find a vantage point through one of his windows. He learns
that the Assassins' Guild has taken him off their registry, with \Gls{Vetina} being the only other
person afforded that luxury.

\subsubsection{\Gls{Vimes} is concerned about \Gls{Ramkin}'s pregnancy}
\Gls{Vimes} has \Gls{Willi} help him with the ceremonial armour for \Gls{Vetina}'s annual City
Watch parade, and asks about \Gls{Ramkin}'s pregnancy. The butler reminds him that \Gls{Content} is
an experienced midwife, and that the delivery is still some days away according to her estimates.
\Gls{Vimes} sets off to sign some paperwork at the Watch headquarters, and asks for the trainee
assassin to be helped out of the sewage moat outside his room.

\subsubsection{\Gls{Vimes} is alarmed by \Gls{Carcer}'s latest murder}
At the Watch House, \Gls{Vimes} is angered to learn that the serial killer \Gls{Carcer} has
murdered \Gls{AStrong}, bringing his tally to three watchmen. He thinks about the new police
training academy, from which graduates were going off to towns as far off as Uberwald, and forming
a tight-knit network of informants, as they took up positions in the various City Watches.

\subsubsection{\Gls{Vimes} heads to the palace for the annual parade}
\Gls{Vimes} asks Constable \Gls{Igor} to refrain from scuttling \Gls{AStrong}'s corpse for parts,
in keeping with dwarf tradition. He then heads to the palace for the parade, with \Gls{Colon} and
\Gls{Nobby} in tow. \Gls{Ping} asks about the lilac that the senior officers are wearing on their
helmets, and is stonewalled by \Gls{Colon}.

\subsubsection{\Gls{Colon} and \Gls{Nobby} go the graveyard for the annual remembrance}
\Gls{Colon} and \Gls{Nobby} attend a remembrance ceremony for some watchmen buried in the cemetery
behind the Temple of Small Gods. The gravedigger \Gls{Leggie} asks \Gls{Colon} to allow the bodies
to be dug up and moved to the crypt, given how long they had been displayed in the cemetery.
\Gls{Leggie} takes offense at \Gls{Shoe} coming into the graveyard, and is reminded by \Gls{Colon}
that he has the right to be there since he also witnessed some important event in the past.

\subsubsection{\Gls{Carrot} talks about foreign affairs to \Gls{Vimes}}
On their way to the palace, \Gls{Carrot} fills \Gls{Vimes} in on the latest political upheavals in
Uberwald, and the possibility of another wave of refugees flooding the city. \Gls{Vimes}
remembers his time as a constable chasing down criminals and patrolling the streets, and laments his
current predicament as a political icon and shepherd for the City Watch.

\subsubsection{\Gls{Vetina}'s meeting with \Gls{Vimes} is cut short}
\Gls{Vetina} tells \Gls{Vimes} that the annual Watch meeting has already finished, and is
interrupted by an emergency message from \Gls{CheeryL}, claiming to have cornered \Gls{Carcer}.
\Gls{Vimes} decides to attend to the arrest personally, against \Gls{Vetina}'s advice to let one of
his subordinates handle the matter.

\subsubsection{\Gls{CheeryL} talks to \Gls{Vimes} about the standoff against \Gls{Carcer}}
At the city square outside Unseen University, \Gls{CheeryL} informs \Gls{Vimes} that watchmen have
been posted at all the neighbouring rooftops, and that \Gls{BSwires} is airborne on a bird for
surveillance. \Gls{Carcer} has been spotted climbing the tower of the University, and is likely to
escape by rooftop to somewhere away from the wizards.

\subsubsection{\Gls{Vimes} heads to the rooftops to arrest \Gls{Carcer} in person}
\Gls{Vimes} heads up to the University rooftops in pursuit of \Gls{Carcer} after \Gls{Swires}
signals his approximate location from high in the sky. He finds \Gls{Carcer} hunkered down between
some chimneys, taking aim at \Gls{Carrot}, who is on a nearby roof. The approaching stormclouds
finally start their thunder, as \Gls{Vimes} and \Gls{Carcer} fire at each other. They both miss,
since they are focused more on dodging than aiming, and the pursuit begins just as a hailstorm
starts to fall.

\subsubsection{\Gls{Vimes} and \Gls{Carcer} are struck by magic lightning}
\Gls{Vimes} pins one of \Gls{Carcer}'s arms under the Library's domed ceiling, as the glass panes
break under the hail. Just as \Gls{Carcer} reveals his hidden knife, and attempts to stab
\Gls{Vimes}, a bolt of magically charged lightning strikes him. Watchmen flood the University
grounds in pursuit of \Gls{Carcer}, as \Gls{Ridcu} learns from \Gls{Stibb} that the thunderstorm
had discharged a lot of magic collected over its long journey through the plains outside the city.

\subsubsection{\Gls{Stibb} speculates that \Gls{Vimes} has been forcibly displaced in time and
    space}
Inside the library, \Gls{Stibb} speculates that the magical fields under the dome caused by the
books inside, might have moved \Gls{Vimes} in time and space, when they reacted with the magic
discharged by the lightning bolt. \Gls{Vimes} wakes up in a whorehouse, and sees a man in a doctor's
robes tending to his wounds. He notices one of his eyes forced shut, as the doctor asks him not to
disturb the eye-patch.

\subsubsection{\Gls{Vimes} wakes up in the past, having arrived naked and bruised}
\Gls{Vimes} is relieved to know that he is still in Ankh-Morpork, but alarmed when neither the
doctor nor the seamstress recognize him. He decides to offer a fake identity, and calls himself
\Gls{Keel}, after the gravestone in the Watchmen's cemetery memorializing a long-dead policeman.
The woman, calling herself \Gls{Rosie}, tells him that he was found naked sprawled in an alley,
and that Doctor \Gls{Lawn} will need to be paid for the medical assistance.

\subsubsection{\Gls{Vimes} confirms that he has traveled back in time}
\Gls{Vimes} asks \Gls{Rosie} to accompany him to the Watch headquarters, where he can find the
coin to pay her. He finds the manor in Pseudopolis yard unrecognizable, with a butler answering
the door. He then heads to \Gls{Ramkin}'s manor, and asks for the butler \Gls{Willi}. The servant
answering the door tells him that \Gls{Willi} is away. He then spots a teenage \Gls{Ramkin}
threatening him with violence, and chooses to run away from the manor, afraid of her father.

\subsubsection{\Gls{Vimes} makes the connection between \Gls{Rosie} and \Gls{RPalm}}
\Gls{Vimes} works out that \Gls{Rosie} is just \Gls{RPalm}, the eventual leader of the Seamstress
Guild, and recalls \Gls{Lawn} as a doctor from the present. She helps him fend off some street
thugs, and promises to come after him unless he pays the money owed to the doctor. \Gls{Vimes}
realizes he is back in a time before \Gls{Vetina}, since the nighttime curfew is still in place.

\subsubsection{\Gls{Vimes} is arrested by the City Watch in the past}
\Gls{Vimes} is cornered by some Night Watchmen as he attempts to enter the University after the
curfew. He is forced to surrender, as his attempt to hold the sergeant hostage is thwarted by
a fourth hidden watchman jamming a crossbow into the back of his neck. He wakes up some time later
in the jail, and notices \Gls{Carcer} being allowed to go free from a neighbouring cell. On his
way out, \Gls{Carcer} tells \Gls{Vimes} that he has a much easier time in the past, where no one
knows he is a crook.

\subsubsection{\Gls{Vimes} is made to face Captain \Gls{Tilden}}
\Gls{Vimes} asks the sergeant who frees \Gls{Carcer} if the current captain is \Gls{Tilden}, and is
relieved to have worked out how far in the past he has come. He then recalls the tales of
\Gls{Snouty}, the watchman whose broken nose was never set right, and forced him to be on permanent
warden duty. He is handcuffed and taken up to the captain's office in the old Watch House, as he
tries to recall the history of Captain \Gls{Tilden}, who was ex-military, and a stickler for
obeying orders, without any intervening layer of common sense.

\subsubsection{\Gls{Vimes} is kidnapped by \Gls{Sweep}}
\Gls{Tilden} accuses \Gls{Vimes} of beating up \Gls{Keel} and robbing him, and realizes that
the name on the gravestone was a real policeman. He notices an old man sweeping the corridors of
the Watch House, causing \Gls{Tilden} to grow annoyed and ask for him to be removed. \Gls{Vimes}
stands up to try and smash the manacles on \Gls{Tilden}'s head, and suddenly wakes up in a dark
room, with the sweeper introducing himself as \Gls{Sweep}, and calling him by his real name.

\subsubsection{\Gls{Vimes} sees the monks manipulate time to try and get him to co-operate}
\Gls{Vimes} learns from the monk that he is in a secret temple, and has been caught up in an
attempt by their order to fulfil some secret mission. \Gls{Sweep} creates a small closed loop of
\Gls{Vimes} in order to try and convince him that the monks are capable of manipulating time
locally, and sees his future self talk about the trainee assassin who fell into the sewage moat.

\subsubsection{\Gls{Vimes} learns that his other self is out there, fresh on the job as a Watchman}
\Gls{Vimes} learns that the Monks of Time can manipulate time enough to move \Gls{Vimes} from the
Watch House to their monastery in the poor district, while freezing time for the rest of the world.
\Gls{Sweep} then tells him that he believes he cannot get \Gls{Vimes} back to the present until he
fulfills some unknown mission for which he got thrown back to the past. He then points out that the
crossbow shoved into his neck earlier in the night was the fresh \Gls{Vimes}, on his first week as a
Constable.

\subsubsection{\Gls{Sweep} talks to \Gls{Vimes} about time-travel and the nature of the multiverse}
\Gls{Sweep} talks about the multiverse theory, and of how \Gls{Vimes} had to act to save the
timeline and his other self from learning to be a bad cop, under the tutelage of \Gls{Colon} and
the other Watchmen. He reveals that \Gls{Carcer} has murdered the real \Gls{Keel}, who was his
mentor in the original timeline, and that there is no place in the future at the moment where they
can return him.

\subsection{}
\subsubsection{\Gls{Sweep} talks to \Gls{Qu} at the hideout in a previous era}
\Gls{Vimes} dreads going back to a future where his mentor is \Gls{Quirke} or \Gls{Knock}, and
turning out an oblivious coward like \Gls{Colon}, or worse. Meanwhile, \Gls{Sweep} travels back in
time to the secret hideout of the Monks, where he meets \Gls{Qu}, their chief Inventor. \Gls{Qu}
tells him that maintaining the stability of two timelines at once is too difficult, and that
\Gls{Vimes} has a few days left before he goes crazy from the mixing of memories from both
of them.

\subsubsection{\Gls{Vimes} convinces \Gls{Tilden} that he is the newly arrived \Gls{Keel}}
\Gls{Vimes} resigns himself to acting in place of the real \Gls{Keel}, and agrees to be led to the
Watch House to take up the role of mentoring his other self. With time unfrozen, \Gls{Vimes} is
back in \Gls{Tilden}'s office, and manages to convince him that he is in fact \Gls{Keel}, by
answering questions about the goings-on in Pseudopolis. Without giving \Gls{Tilden} a chance to
recover his footing, he quickly has himself sworn into the force as a Sergeant, and takes his badge
of office.

\subsubsection{\Gls{Vimes} thinks about the current ruler of Ankh-Morpork}
\Gls{Vimes} asks \Gls{Snouty} to arrange armour and a sword for him, and have it brought to the
residence of \Gls{Lawn}, who has a spare room for him. He then strides through the city streets at
night, confident in the newfound authority granted by the badge, and flashes it to other watchmen
when they try to stop him for breaking curfew. He recalls the paranoid ruler of Ankh-Morpork from
that time, \Gls{LWind}, and his expansive spy network, the Unmentionables, meant to keep an eye on
anyone plotting to kill him.

\subsubsection{\Gls{Vimes} shows up for his first day at work as \Gls{Keel}}
\Gls{Vimes} convinces \Gls{Lawn} to let him stay in a spare room, and shocks him the next morning
when he sets off to work in his Sergeant's uniform. He gets to the old Watch House, and notices
the lax security, as he lets himself in through the rear entrance. After inspecting the horse
kept at the stables in a state of near-starvation, he settles down at his new desk, reminding
himself that he has been granted seniority over Sergeant \Gls{Knock}.

\subsubsection{\Gls{Vimes} tries to bring some order into the Night Watch}
\Gls{Vimes} chastises the Night Watch for pilfering the money meant to maintain the horse, believing
that \Gls{Tilden} is being kept in the dark. He then asks \Gls{Knock} why he did not bother to
receive any written acknowledgement from the Unmentionables, for the curfew-breakers that he had
driven to them at night.

\subsubsection{\Gls{Vimes} confronts \Gls{Quirke} about letting \Gls{Carcer} walk free}
\Gls{Vimes} demands to know who let \Gls{Carcer} out, and recalls how infamous \Gls{Quirke} was
for his system of bribes and blackmail. \Gls{Quirke} breaks under \Gls{Vimes}' questioning, and
points to the new Constable \Gls{YVimes}, declaring that he shared the money from \Gls{Carcer} with
the new recruit.

\subsubsection{\Gls{Vimes} talks to \Gls{Knock} about the chain of custody}
\Gls{Vimes} dismisses \Gls{Quirke} from the Night Watch, and asks him to report to the Day Watch
immediately, if he wished to keep his job. He then demands that \Gls{Knock} maintain a system of
receipts for every prisoner delivered to the Unmentionables, so that no one could disappear from
the chain of custody by paying off one of the jailers.

\subsubsection{\Gls{Vimes} realizes how stupid \Gls{YVimes} was as a fresh recruit}
\Gls{Vimes} talks to \Gls{YVimes} about taking bribes to let prisoners go free, and reminds him not
to run his mouth, given the wide berth the Unmentionables had in apprehending anyone who said the
slightest thing against \Gls{LWind}. He is infuriated by the goodwill being farmed by \Gls{Snapcase}
in the meantime, just for interacting with the proles, and daring to declare that taxes were too
high.

\subsubsection{\Gls{Vimes} decides to force the Unmentionables into signing for the prisoners}
\Gls{Vimes} signs the sheet presented by \Gls{Coates} bearing seven names of curfew-breakers, and
notices that \Gls{Rosie} is among them. He drives them to the Unmentionables along with the rest of
the Night Watch, and asks the guard to sign a form for transfer of custody. The guard starts to
take offense, and is cowed by a superior officer emerging from the building, identifying himself
as Captain \Gls{Swing}.

\subsubsection{\Gls{Vimes} gets the curfew-breakers out by insisting on paperwork}
\Gls{Vimes} correctly guesses that \Gls{Swing} will not want any more subjects to torture if he has
to sign for them, and gets them dismissed. He then has \Gls{YVimes} drop the curfew-breakers home,
after levying a small fee for the ride. Rumours of \Gls{Vimes} exploiting the Unmentionables' fear
of paperwork spread through the City Watch like wildfire.

\subsubsection{\Gls{Vimes} breaks into the Watch House after the night shift ends}
Back at her home, \Gls{RPalm} wonders out loud what \Gls{Vimes} is playing at, with his open
defiance of the Unmentionables, as her roommate \Gls{Sandra}, an actual seamstress, receives her
newest customer. Meanwhile, \Gls{Vimes} uses his knowledge of the badly sealed windows on the
first floor of the Watch House to break in after everyone else has left, and steal something from
the safe-room using a set of lockpicks borrowed from the evidence locker.

\subsubsection{\Gls{Vimes} brings the Unmentionable who ambushed him to \Gls{Lawn} for treatment}
On his way back home, \Gls{Vimes} is ambushed by the Unmentionables who argued with him earlier
about signing for the prisoners, and beats them up. He brings one of them back to \Gls{Lawn}, and
asks him to set the fractured arm. \Gls{Vimes} decides to drop off the Unmentionable in a dark
alley, after signing his initials in the plaster cast holding his broken arm.

\subsubsection{\Gls{Vimes} recalls the stories about \Gls{Swing} and his police reforms}
\Gls{Vimes} thinks about the policing revolution brought about by \Gls{LWind} appointing \Gls{Swing}
as Captain of the City Watch, and the backwards laws that had led to more crime, more arrests, and
less safety for the very citizens least likely to break the law. The next morning, he runs into
young \Gls{Dibbl}, who has just started his sausage business, hoping to make it big in the city,
and finds a young \Gls{Nobby} stalking him through the alleys.

\subsubsection{\Gls{Vimes} meets some familiar faces in the past}
\Gls{Vimes} catches young \Gls{Nobby}, who is little more than a poor street urchin, and gets him
to be a full-time informant, for a modest salary. He takes \Gls{Nobby} to a dining hall, and asks
the owner to give him one meal a day in exchange for payment in advance. Back at the Watch House,
\Gls{Knock} tells \Gls{Vimes} that the engraved silver inkpot in \Gls{Tilden}'s office has been
misplaced.

\subsubsection{\Gls{Vimes} works on a plan to get \Gls{Tilden} to consider retirement}
\Gls{Vimes} is amused to see the surprise on \Gls{Knock}'s face when the ink-pot is not in his own
locker, or in any of the others. He then goes up to \Gls{Tilden}'s office, and asks him to check if
he accidentally left it in his personal safe. \Gls{Vimes} thinks about how this act of supposed
carelessness might get \Gls{Tilden} to resign, and pave the way for his own promotion.

\subsubsection{\Gls{Vimes} gets \Gls{Knock} to betray \Gls{Coates}}
\Gls{Vimes} confronts \Gls{Knock} outside the Watch House, and coerces him into giving away
\Gls{Coates} as a possible rebel sympathizer. He then refuses the offer to drink at the Broken Drum
after hours, and takes \Gls{YVimes} along for a patrol. He thinks back to \Gls{Tilden}'s talking
about rumours that \Gls{Vimes} was himself a spy for the Unmentionables.

\subsubsection{\Gls{Vimes} knocks out an Unmentionable at the rebel hideout}
At the Assassins' Guild, \Gls{Downey}, who is now a student, tries and fails to hold his peers'
attention by bullying \Gls{Vetina}. Meanwhile, \Gls{Vimes} takes \Gls{YVimes} to patrol on Morphic
Street, per the secret note hidden in one of \Gls{Dibbl}'s sausages. He apprehends an Unmentionable
staking out a rebel meetup spot, and runs into \Gls{Carcer} on his way out.

\subsubsection{\Gls{Carcer} tries and fails to intimidate \Gls{Vimes} using his new job}
\Gls{Carcer}, now promoted to Sergeant by \Gls{Swing} for his innovative ideas about torture,
realizes that \Gls{YVimes} is the green constable next to \Gls{Vimes}, and agrees to play along with
the farce of taking the arrested Unmentionable to the Watch House and finishing the paperwork for
his custody. A while later, two shadowy figures step out of the hideout in Morphic street, as
\Gls{Meserole}'s carriage pulls up.

\subsubsection{\Gls{Vimes} learns about the famous massacre at Dolly Street}
Back at the Watch House, \Gls{Vimes} is glad to see the Constables hunkering down in preparation
for an assault by the Unmentionables, and goes to \Gls{Tilden}'s chamber. He is shocked to see
the doubt and horror on the Captain's face, at the news of a massacre at Dolly Street, supposedly
to quell a protest about rising prices.

\subsubsection{\Gls{Vimes} initiates his plan to stop the civilians from fighting the Night Watch}
\Gls{Vimes} sets up some booby traps for the Unmentionables who he believes will try to break in,
as angry civilians gather outside the Watch House to protest the police brutality at Dolly Street.
He refuses \Gls{Knock}'s idea of arming themselves and barring the gates, and asks him to arrest
the Unmentionables who just fell into the traps.

\subsubsection{\Gls{Vimes} manages to stop any rioting at the main Watch House}
\Gls{Vimes} gets the mob assembled outside the Watch House to disperse, after he makes an elaborate
show of helping one of the instigators who injures himself trying to break a bottle. He narrowly
escapes death when an assassin sent by the Unmentionables misses his crossbow shot, and falls off
a nearby roof to his death. \Gls{Vimes} asks \Gls{Lawn} to make a death certificate for the would-be
assassin, and tend to the two intruders.

\subsubsection{\Gls{Vetina} returns to \Gls{Meserole} after saving \Gls{Keel}'s life}
\Gls{Colon} comes back with some beer, and reports that all the other Watch Houses had faced violent
mobs seeking to break in and fight the watchmen. A while later, \Gls{Vetina} returns to
\Gls{Meserole} who is waiting for him in her wagon, and reports his success at stopping the
assassination of \Gls{Keel}. He wonders if \Gls{Keel} will become an impediment in their planned
coup against \Gls{LWind}, and is surprised when \Gls{Meserole} expresses interest in meeting him.

\subsubsection{\Gls{Vimes} gets one of the Unmentionables to talk}
\Gls{Vimes} watches the three Unmentionables from a peeping hole, as their dead colleague is
wheeled past to an underground cellar. He notices one of them look alarmed, and names him
\Gls{Ferret}. After \Gls{Ferret} sees the other two prisoners being dragged off to the next room,
and hears loud screaming, he is convinced that some serious torture is waiting for him unless he
spills his guts about the Unmentionables and their plan for the night.

\subsubsection{\Gls{Vimes} is taken to the revolutionary hideout}
\Gls{Ferret} realizes too late that the torture was a ploy designed to exploit his fears, and asks
for protective custody from the two Unmentionables who now know that he has snitched. A while later,
\Gls{Vimes} is knocked out by \Gls{Rosie}'s agents, and taken to the revolutionary hideout, where
\Gls{Meserole} lets him in on the plan to depose \Gls{LWind}, and replace him with \Gls{Snapcase},
who seems like the most popular option.

\subsubsection{\Gls{Meserole} asks \Gls{Vimes} to participate in the coup against \Gls{LWind}}
\Gls{Vimes} works out that \Gls{Meserole} is close to convincing all the major guilds in the city
that a less violent patrician will be better for business, and to overthrow \Gls{LWind} using a
quiet assassin behind closed doors. After \Gls{Vimes} refuses to the offer of commanding the City
Watch, in exchange for his participation in the coup, he is allowed to leave. He steps outside, and
realizes that he is very close to the Watch House.

\subsubsection{\Gls{Vimes} rejects \Gls{Meserole}'s offer of participating in the coup}
After \Gls{Vimes} leaves, \Gls{Vetina} steps into the room, having overheard the exchange between
\Gls{Meserole} and \Gls{Keel}. She returns to the party, hoping to persuade more of the Guildmasters
into joining her coup, as \Gls{Vetina} expresses his satisfaction about \Gls{Keel}'s character.

\subsubsection{\Gls{Vimes} receives an update on the riots from \Gls{Nobby}}
The next morning, \Gls{Vimes} hears the news of riots overtaking every other police station from
\Gls{Nobby}, as \Gls{Snouty} informs him that \Gls{Tilden} is not in his chamber. \Gls{Snouty} also
tells him that a special envelope arrived for \Gls{Tilden} early in the morning, after which he
vanished with his silver inkpot.

\subsubsection{\Gls{Vimes} realizes that \Gls{Coates} has a hidden past}
\Gls{Vimes} sets out to train the watchmen in the use of their truncheons, and is surprised by the
martial skill exhibited by \Gls{Coates}. He whispers to \Gls{Vimes} that he learnt his art from the
real \Gls{Keel}, and that he knows \Gls{Vimes} is an impostor. \Gls{Swing} shows up with a few of
his Unmentionables to inform \Gls{Vimes} that a new Captain was on his way with \Gls{Tilden}
retiring, and that police presence in the streets was about to increase, given the atmosphere.

\subsubsection{\Gls{Vimes} seeks out the Monks of Time}
\Gls{Vimes} decides to take on the thankless task of defusing tensions between the citizens and
the City Watch, and asks his men to volunteer for patrol duty. A few of them decline, choosing to
head home to their families and wait out the riots. He decides to ignore the summons from the newly
appointed Captain, and searches for the Monastery of Time using his feet to recall the path they
had taken him along while blindfolded.

\subsubsection{\Gls{Vimes} talks to \Gls{Qu} and \Gls{Sweep} about his mission}
\Gls{Vimes} manages to find \Gls{Sweep}'s rock-garden, and confronts him about the possibility of
getting back to the future. \Gls{Qu} reminds him that if he fills the hole left by \Gls{Carcer}'s
mugging of the real \Gls{Keel}, then he can ensure get \Gls{Vimes} back to his wife and child.
After \Gls{Vimes} leaves, \Gls{Sweep} decides to send out search parties for the one object that he
believes might motivate \Gls{Vimes} to work on his mission.

\subsubsection{\Gls{Vimes} outwits \Gls{RRust}, using his own hatred for the working class}
\Gls{Vimes} realizes that the new Captain is the young \Gls{RRust}, and decides to use his
pride against him. When told that he is being offered a promotion to Lieutenant, along with a
transfer to \Gls{Swing}'s department, he expresses great interest in the offer, and is proved right
when \Gls{LRust} shoots it down, out of sheer pettiness.

\subsubsection{\Gls{Vimes} gets the men ready for an inspection by the new Captain \Gls{RRust}}
\Gls{Vimes} recalls the riots that had spread through the city, as he realizes that the current
timeline has already changed, with a new replacement Captain. He gets the men ready for inspection,
as \Gls{RRust} comes out of his chamber, and groans at the pitiful display of strength. \Gls{RRust}
is taken back by \Gls{Wiglet} openly declaring that \Gls{LWind} being a tyrant is the root cause of
the martial law currently in effect.

\subsubsection{\Gls{Vimes} and the watchmen patrol the streets to enforce martial law}
\Gls{Vimes} gets \Gls{RRust} to accept the fact that the Watchmen are simpletons incapable of
understanding the political nuances of martial law, and reiterates his trust in his men. \Gls{Vimes}
spirals into despair as he stands in front of a barricaded alley, asking the citizens to bow to the
law. He hears many explosions as he blacks out.

\subsubsection{\Gls{Vetina} tries to find out if the Assassins' Guild is taking out \Gls{LWind}}
\Gls{Vetina} asks the porter at the Assassins' Guild if anyone has been sent on a contract to kill
\Gls{LWind}, and is told that he is not authorized to know. He waits for the porter to leave on his
break, and sneaks in to the active duty shelf, to try and read the contracts currently in progress.
\Gls{Vimes} sees a procession of monks pass by, with their firecrackers and ribbons. He sees
\Gls{Ramkin}'s cigar case at his feet, and realizes that this is the anchor to the future, to help
keep his sanity.

\subsubsection{\Gls{Vimes} knocks \Gls{RRust} out, when he orders the civilians to be fired upon}
\Gls{Vimes} refuses to obey \Gls{RRust}'s order to fire at the civilians, when they throw a few
stones over the barricade at his men. When \Gls{RRust} tries to remind him that martial law is in
effect, he knocks out his superior, and asks for some Constables to take \Gls{RRust} back to the
jail.

\subsubsection{\Gls{Vimes} helps the civilians build a better barricade}
\Gls{Vimes} is asked by Mrs. \Gls{Ruther} for help with her father and husband, as they take him up
on his offer to build better barricades on all the entrances to their section of the city. He then
talks to the young \Gls{Shoe}, who believes himself to be a vital member of the revolution, all
while knowing no one else in the organization.

\subsubsection{\Gls{Vimes} fends off a cavalry squad sent by the Patrician to enforce martial law}
When a squad of the Patrician's cavalry arrive at the barricade to ask \Gls{Vimes} about the local
civilians, he tells them that they are all safely tucked away behind it, under the watchful eyes of
his men. The cavalry Captain, who is too intelligent to continue splitting hairs with \Gls{Vimes},
decides to take his squad to a more urgent situation elsewhere in the city, after realizing that
\Gls{Vimes} has nullified any desire for rioting among the locals.

\subsubsection{\Gls{Vimes} heads to \Gls{Swing}'s headquarters}
\Gls{Vimes} decides to push out the barricades to cover a larger area, in spite of the fact that it
would include \Gls{Swing}'s headquarters. He then takes some men to the Unmentionable headquarters,
which is largely deserted. He manages to either knock out the few remaining men, or get them to
flee, before finding the torturer in the underground cellar, and tying him up to a chair.

\subsubsection{\Gls{YVimes} sees the torture that has been going in at \Gls{Swing}'s place}
\Gls{YVimes} is horrified to see the torture victims still alive in the cellar, and tries to kill
the torturer, who is restrained to a chair. \Gls{Vimes} stops him, and tries to remind him that the
law bars him from beating up a captive citizen, regardless of how much he might deserve it. He then
decides to get the prisoners out of the prison, and asks \Gls{YVimes} to lead the way into the jail.

\subsubsection{\Gls{Vimes} kills \Gls{Swing} the Unmentionable headquarters burns down}
\Gls{Vimes} gets \Gls{Colon} to toss a Molotov cocktail into the neighbouring warehouse, once
\Gls{Swing}'s clerk reveals that it is being used as a hidden entrance to the headquarters, as well
as a place to keep corpses. He returns to the cellar, to set the torturer free, and runs into
\Gls{Swing}. In the ensuing fight, \Gls{Vimes} is stabbed in the leg, as he uses the skull-measuring
ruler to kill \Gls{Swing}, and limp out of the building just as the fire starts to spread.

\subsubsection{\Gls{Vimes} has his injuries looked at after returning to the Watch House}
\Gls{Vimes} returns to the Watch House, where \Gls{Lawn} tends to his wounds, and tells him that the
citizens in his barricade have gotten a little too excited with expanding their reach. He sees
\Gls{Shoe} arguing with the people about their motto, and struggle to explain communism to a
shoemaker.

\subsubsection{\Gls{Carcer} gets into the cavalry command post}
\Gls{Carcer} strides into the cavalry command tent, where Major \Gls{Clive} and Captain
\Gls{Wrangle} are to ride out the rest of the night without any further commotion. \Gls{Carcer}
strides in, using his status as an Unmentionable, and informs them that \Gls{Swing} has been killed,
in the arson of his headquarters.

\subsubsection{\Gls{Carcer} puts \Gls{Clive}'s career in jeopardy}
\Gls{Carcer} invokes the martial law granting him the power to ask the military to come to his aid,
and asks for \Gls{Vimes} and his Watch House to be raided. \Gls{Clive} and \Gls{Wrangle} think about
how bad it would be for their careers to refuse, and then have to justify their decision to
\Gls{LWind}, as they recall the curious lack of violence reported in \Gls{RRust}'s jurisdiction.

\subsubsection{\Gls{Vimes} decides to play along with \Gls{Colon}'s plan to expand}
\Gls{Vimes} decides to go along with \Gls{Colon}'s plan to expand their safe-zone to eventually
encompass half of the city, in order to appear heroic to \Gls{YVimes}. He orders any new entrants to
be stripped of their weapons, and reminds \Gls{Colon} that it will be increasingly difficult to
supervise such a large area.

\subsubsection{\Gls{Vimes} issues new orders to \Gls{Dickins}}
\Gls{Vimes} is relieved to see \Gls{Dickins}, and old Sergeant from a different branch of the Night
Watch, assembling his impromptu militia. \Gls{Dickins} reminds him that most of the old men are
former watchmen, and is surprised to see \Gls{Vimes} ask him to reinforce the City Gates, at the
outer periphery of their jurisdiction.

\subsubsection{\Gls{Vimes} thinks about the possible ways that the cavalry might try to breach his
    barricade}
\Gls{Vimes} reminds \Gls{Dickins} that the standard means of dealing with a barricade is to go
around it, and asks for any bridges to be made cavalry-proof. \Gls{Clive} learns that the barricade
has now expanded to include a quarter of the city, and that a lot of the deserters from his own
regiment have been spotted manning it, having taken off their insignia.

\subsubsection{\Gls{Vimes} allows former soldiers to enter the barricade}
\Gls{Vimes} allows \Gls{Colon} to go ahead with his plan of inducting former soldiers into the
barricades, when he is reminded that they are not going to stand for violence against their own
families. \Gls{Vimes} recalls the history books, which mentioned the barricades being broken by a
squad of military sneaking in through a bridge, as he settles down for a nap. He spots \Gls{Dibbl}
settling down with a pot of stew, for the citizens who had little to do except wait out the night.

\subsubsection{\Gls{Clive} is forced to act against the rebel barricade by \Gls{Carcer}}
\Gls{Clive}'s scout returns from his latest patrol to the barricades, with \Gls{Nobby}, who is
caught lurking outside the command post. \Gls{Nobby} wishes to grow up and become a soldier, just
for the perks of looting corpses on the battlefield, and leaves \Gls{Clive} horrified by his
disregard for honour and glory. \Gls{Carcer} arrives with some of his \Gls{Swing}'s men, and manages
to intimidate \Gls{Nobby} into declaring \Gls{Keel} the leader of the rebellion.

\subsubsection{\Gls{Vimes} spots a siege engine being wheeled out to destroy the barricade}
\Gls{Carcer} reminds \Gls{Clive} and \Gls{Wrangle} that their careers would end if the barricade was
still up the next morning, and forces them to assault it head on. A while later, \Gls{Vimes} notices
more people spill into his barricade, as siege weapons are wheeled out to tear it down. He decides
to madden the oxen pulling the siege wagons, using the mob pushing into the barricade entrance to
sneak his way out.

\subsubsection{\Gls{Vimes} destroys the siege engine sent to topple the barricade}
\Gls{Vimes} manages to spook the oxen into throwing off their yokes, and stampeding back the way
they came. The resulting confusion stalls the plan to take the barricade head-on, and destroys the
siege engine. Meanwhile, \Gls{Vimes} realizes that \Gls{LWind} being killed in a well-lit room
surrounded by people, simply means that the coup against him gathered enough strength to go through.
He dreads the new Patrician \Gls{Snapcase}, recalling his record as a tyrant and madman.

\subsubsection{\Gls{Vimes} thinks about the deaths he has prevented, and wonders about the future}
\Gls{Vimes} tries to see if the writing on his cigar case is vanishing, as he changes history by
averting the deaths of watchmen in the clash against the military. He realizes that he is going to
value the lives of the men under his command over his desire to return to his future, as more food
is delivered to the rebel barricade. They take over most of the food warehouses in the city,
prompting more of the citizens to seek shelter within their jurisdiction.

\subsubsection{\Gls{Clive} decides to wash his hands of the barricade fiasco}
\Gls{Vimes} wonders how much longer the city will be able to function without its daily supply of
food and raw material being allowed to enter through the gates. Meanwhile, \Gls{Clive} receives a
report from \Gls{Wrangle} about the non-violent nature of the barricaded citizens, and realizes that
the issue has now become political, and therefore out of his purview.

\subsubsection{\Gls{ASelach} and \Gls{LVentu} learn about the rebellion's success}
Lord \Gls{ASelach} and \Gls{LVentu}, belonging to families considered generational enemies, are
guided by \Gls{Meserole} through the party, while the others in the coup try to isolate and convert
the few aristocrats still loyal to \Gls{LWind}. A representative from the military arrives to tell
the two lords about \Gls{Clive}'s latest report, prompting \Gls{LVentu} to move out with the
regiment stationed at the palace, intent on crushing the rebellion.

\subsubsection{\Gls{Meserole} initiates the assassination of \Gls{LWind}}
\Gls{Meserole} notices some of \Gls{LWind}'s honor guard missing from their patrols, as
\Gls{LVentu} orders a volley of arrows fired over the main barricade. \Gls{Vimes} is caught off
guard, just as he has breakfast brought to him by \Gls{Sandra}. \Gls{LWind} collapses from a
heart attack and dies as the ceremonial birthday cake is brought in, and distributed to the guests.
He finds it odd that the Assassin walks in through the front door, instead of sneaking about.

\subsubsection{\Gls{Snapcase} takes charge as the new Patrician}
\Gls{Vimes} tries to fend off the infantry trying to scale the barricade using grapnels, and finds
it fairly easy to beat them off. He realizes that some foolish commander has decided on a show of
strength, by choosing to assault their stronghold, even at the cost of his soldiers' lives.
Meanwhile, \Gls{Snapcase} is sworn in as the new Patrician, and moves into the palace, in a smooth
operation planned well in advance of \Gls{LWind}'s death.

\subsubsection{\Gls{Snapcase} orders \Gls{Keel} eliminated}
\Gls{Vimes} agrees to a truce offered by the military, once news of \Gls{LWind}'s death spreads
through the city. At the palace, \Gls{Snapcase} decides to offer a general amnesty to the rebels,
but wishes to have \Gls{Keel} eliminated, since he might become a greater threat later.
\Gls{Follett}, Guildmaster of the Assassins is impressed by \Gls{Snapcase}'s pragmatism, but
\Gls{Meserole} immediately orders \Gls{Vetina} to take a carriage to the barricade and warn
\Gls{Keel}.

\subsubsection{\Gls{Snapcase} orders \Gls{Keel} killed}
\Gls{Snapcase} asks his secretary to prepare his inaugural speech, including a plea to the citizens
to unite in the aftermath of \Gls{Keel}'s unfortunate death. He then orders \Gls{Carcer}, now
promoted to Captain of the City Watch, to be brought to him. \Gls{Vimes} watches the celebrations
next to the Watch House, and is alarmed to see some monks vanish all of a sudden.

\subsubsection{\Gls{Vimes} realizes that \Gls{Carcer} is hunting him down}
\Gls{Vimes} jumps into a nearby shop with some of his men, just as crossbow bolts start to fly,
with one of them going straight through \Gls{Wiglet}'s chest. \Gls{Colon} looks out the window, and
sees a large group of crossbowmen forming up outside, and suggests running out the back door.
\Gls{Dickins} takes the lead running through the back alley, just as \Gls{Carcer} breaks into the
shop in search of \Gls{Vimes}.

\subsubsection{\Gls{Vimes} realizes that his men are not going to let him be captured}
\Gls{Vimes} tries to tell the others to dissolve into the crowds, confident that \Gls{Carcer} only
wants him, but faces resistance from the men. They are unsure that they will ever be allowed to
walk free, and choose to set up an ambush against \Gls{Carcer}'s squad. \Gls{Vimes} sees
\Gls{Dickins} pick out some lilacs from a nearby tree, to help them distinguish their own men in
the fight.

\subsubsection{\Gls{Coates} embeds himself inside \Gls{Carcer}'s squad}
\Gls{Coates}, who has fallen in with \Gls{Carcer}'s squad, suggests that \Gls{Keel} will hunker down
at the Watch House, and set an ambush. \Gls{Carcer} is convinced for the moment that \Gls{Coates}
has a vendetta against \Gls{Keel} for being dismissed, and heeds his advice. \Gls{Vimes} springs
a trap for \Gls{Carcer} and his men, with most of the Unmentionables dying. \Gls{Shoe} keeps going
in spite of the bolts in his chest, and finally collapses after \Gls{Carcer} has retreated.

\subsubsection{\Gls{Qu} and \Gls{Sweep} inform \Gls{Vimes} that they are ready to transport him
    back to the future}
\Gls{Coates} betrays \Gls{Carcer}, slicing up some of his men, just as \Gls{Dickins} and some others
jump out of \Gls{Dibbl}'s cart. \Gls{Vimes} knocks out \Gls{YVimes}, and tells \Gls{Coates} that
\Gls{Carcer} needs to be dealt with as soon as possible. Time slows down all of a sudden, and
\Gls{Sweep} appears behind \Gls{Vimes}, with news of his imminent return to the future. \Gls{Qu}
tells \Gls{Vimes} to grab hold of \Gls{Carcer}, to ensure he also returned with him.

\subsubsection{\Gls{Vimes} returns to his original timeline}
\Gls{Vimes} is relieved to see the real \Gls{Keel}'s corpse being wheeled into the alley to
substitute for himself after he return to the future. \Gls{Vimes} returns to the future naked, in
\Gls{Stibb}' laboratory, and is relieved to see \Gls{Carrot} greeting him. He learns that only an
hour has passed in his original timeline, and realizes that \Gls{Carcer} must also have returned
somewhere nearby.

\subsubsection{\Gls{Vimes} gets \Gls{Lawn} to help with his wife's delivery}
\Gls{Vimes} runs to his house, and learns from \Gls{Willi} that \Gls{Ramkin} is having trouble with
her labour. He asks \Gls{Ridcu} to take him to \Gls{Lawn}'s office using his flying broomstick, and
gets the doctor to attend to his wife. He passes out from the exhaustion of time-travel, just after
seeing the child safely wrapped up in \Gls{Ramkin}'s arms.

\subsubsection{\Gls{Vimes} apprehends \Gls{Carcer} at the cemetery}
\Gls{Vimes} waits for \Gls{Carcer} at the cemetery, and manages to subdue him. He resists the urge
to kill him right then, and shackles him for the Watchmen. He promises \Gls{Carcer} a fair trial and
a swift hanging, just as \Gls{Vetina} arrives, curious about the resemblance that \Gls{Vimes} has
to the famous \Gls{Keel}. \Gls{Vimes} asks him to keep his theories about time-travel to himself,
since he cannot prove anything, and is glad to hear that \Gls{Keel}'s former Watch House will be
restored.