\section{Raising Steam}


\subsection{}
\subsubsection{\Gls{DSim} shows the steam engine blueprint to his mother}
Some small business owners transporting fish and fruit from faraway cities to Ankh-Morpork decide to
write a complaint to the newspaper, asking for some way to get their produce across the great
distances while still fresh. \Gls{DSim} loses his father to a furnace accident, prompting his mother
to pack up and move to a village near Sto Lat. Many years later, having grown up with a fascination
for mathematics, \Gls{DSim} shows his mother a blueprint of a steam engine, along with a small
prototype in the shed running on a circular track.

\subsubsection{\Gls{DSim} makes a full-scale steam engine and tests it in his small town}
\Gls{Elsie}, who is a luddite, does not see the value of the steam engine, and gives up working out
the meaning of \Gls{DSim}'s lengthy exposition. She shows him the stash of gold bequeathed by her
father, who was a reformed pirate, and asks \Gls{DSim} to use it for his engineering designs. After
some months of work in his expanded workshop, \Gls{DSim} and his gang of hired hands unveil the
full-scale steam engine to the townsfolk, who still fail to see its commercial value.

\subsubsection{\Gls{Vetina} confers with \Gls{Margo} about consolidating the peace in Uberwald}
\Gls{Vetina} is forced to fight off some highwaymen on his way to meet the political elite of
Uberwald. \Gls{Drumk} wonders why he does not advertise his crest more prominently on the carriage,
so that politically aware bandits might learn to stay away. He talks to \Gls{Margo} about the
opposition to the Peace Accord coming from dwarf factions that are opposed to \Gls{RhysR}, the Low
King. She makes an offhanded comment about the steam engine being invented by someone in a
long-extinct civilization, and wonders what the state of the Disc might be if it was not shunned.

\subsubsection{\Gls{Mag} is saved by \Gls{Bashf}, a hero for the Ankh-Morpork dwarves}
\Gls{Mag}, a dwarf born and raised in Ankh-Morpork, tries to talk his way out of a gang of
fundamentalist dwarves in Schmatlzberg, who try to chastise him for his fashion choices. He is
saved from further violence by \Gls{Bashf}, a reformed priest who now supports reconciliation with
the progressive dwarves of Ankh-Morpork. He asks \Gls{Mag} to try and blend in with his armor and
clothing when visiting his family in Schmatlzberg, since popular sentiment was still against the
progressiveness of the city dwarves.

\subsubsection{\Gls{HarryK} catches the scent of \Gls{DSim}'s steam engine}
\Gls{HarryK} thinks about the most recent spat with his wife, exacerbated by the food poisoning
from stale fish. He starts to wonder how he can leave the garbage collection business behind, and
get into something more suited to a wealthy Ankh-Morporkian lord. He catches the faintest whiff of
burning coal emitted by \Gls{DSim}'s engine, and suddenly gains faith in his plan to diversify his
empire.

\subsubsection{\Gls{DSim} asks \Gls{HarryK} for the time and money needed for a demonstration}
\Gls{Moist} prepares to meet \Gls{Adora}, and makes his peace with the goblins on his new manor's
roof, minding the semaphore tower. He is pleased to see \Gls{Adora} establish a firm grip on the
semaphore network, now fully manned by goblins, and nationalized by \Gls{Vetina} to prevent another
hostile takeover by malicious forces. Meanwhile, \Gls{HarryK} is hypnotized by the working of
\Gls{DSim}'s steam engine, and gives him two days to lay down a test-track to show off its ability
to transport loads.

\subsubsection{\Gls{HarryK} gives \Gls{DSim} the go-ahead for a full demo of the train}
An old miner recounts the story of a dangerous mining collapse deep in the treacle mines under the
city. He details the joint efforts of dwarf and human miners that led to the rescue of the unit
trapped in the collapsed mine, and wishes that current interspecies relations were equally
friendly. Meanwhile, \Gls{HarryK} agrees to some more funding so that \Gls{DSim} can show off the
engine with wagons attached, on a bigger test-track. He is pleased by the prospect of replacing the
foul smell of excrement with the manly smell of burning coal.

\subsubsection{\Gls{Adora} is delighted with the employment of goblins in the semaphore network}
\Gls{Adora} thinks about the rapid increase in the semaphore network's efficiency, with goblins
manning every tower, being capable of working at night with their superior vision. She is brought
her tea by the goblin assistant \Gls{Twili}, and wonders how she can be organizing the extra
profits into a fund that might be used to integrate goblins deeper into Ankh-Morpork society.

\subsubsection{\Gls{HarryK} takes \Gls{DSim} to see the lawyer \Gls{Thun} to draw up agreements}
\Gls{HarryK} offers \Gls{DSim} a formal business contract, and takes him to the Lawyers' Guild,
where the first troll lawyer \Gls{Thun} has just been inducted. \Gls{Thun} decides to be the
mediator between the two of them, and takes on the responsibility of drawing up formal contracts
for their joint venture. They return to \Gls{HarryK}'s compound, only to find \Gls{BSlick} and the
goblins making enquiries about the engine, as \Gls{DSim}'s assistants try to provide satisfactory
answers about the underlying mechanism.

\subsubsection{\Gls{Vetina} talks to \Gls{Moist} about the joint venture between \Gls{HarryK} and
    \Gls{DSim}}
\Gls{Moist} is taken to the palace, where \Gls{Vetina} points out the model train running in
circles on his desk, and likens it to a doodle by \Gls{LeoQ} in one of his notebooks. \Gls{Vetina}
finally comes out of his distracted sulk from having made a mistake in the daily crossword, and
talks about the steam engine being shown off by the late \Gls{NSim}'s son.

\subsubsection{An interspecies wedding is stopped by dwarf priests in Llamedos}
In Llamedos, a country formerly known for precious metals mined underground, faces the end of its
human-dwarf harmony with the arrival of some fundamentalist dwarf priests. They try to stop the
wedding of a dwarf and human, and are stopped by some guests armed with heavy weapons.
Unfortunately, the dwarf bride dies in the fight, leaving the guests devastated. Meanwhile,
\Gls{Vetina} takes \Gls{Moist} through the new suburbs springing up outside the city walls of
Ankh-Morpork, with \Gls{Dibbl} fueling the speculative housing bubble.

\subsubsection{\Gls{DSim} and \Gls{HarryK} present the rail way prototype to \Gls{Vetina}}
\Gls{DSim} welcomes \Gls{Vetina} and \Gls{Moist} to his makeshift shed inside \Gls{HarryK}'s
compound, as the wagons are being attached to his prototype steam engine in preparation for the
trial run. \Gls{HarryK} speculates that the system could haul a lot of cargo very quickly over
distances that now take months to traverse using the road network. \Gls{Moist} asks \Gls{DSim}
why he has put down rails for his train to run on.

\subsubsection{\Gls{Drumk} and \Gls{Moist} are taken on a test drive by \Gls{DSim}}
\Gls{Drumk} goes on the train ride with \Gls{Moist} as \Gls{DSim} takes it through a few laps of
the test track. At the end, \Gls{Drumk} is hypnotized by its whistle, and asks \Gls{DSim} for one
more ride, as \Gls{Moist} gets busy thinking about the comfortable journey that could be made to
Uberwald on one of these trains, complete with sleeping and dining facilities on board.

\subsubsection{\Gls{HarryK} entertains his guests after the test ride}
A while later, \Gls{HarryK} takes the rest of his guests up to his manor for a meal, and \Gls{DSim}
starts talking about taking on a contract with the Post Office for the delivery of inter-city mail.
Meanwhile, \Gls{HarryK} is busy thinking about the tidy sum that could be made from offering rides
on the test track to all the curious citizens who were crowding his compound walls, curious for a
look at the new contraption spewing steam.

\subsubsection{\Gls{Adora} and \Gls{Angua} talk at the site of a semaphore tower which has been
    attacked by dwarves}
\Gls{Adora} is called to the site of a burned semaphore tower by \Gls{Angua}, how comes back from
a patrol of the surroundings. She points out one of the dwarf arsonists lying the wreckage of the
collapsed tower, and reassures \Gls{Adora} that none of the goblins working up top suffered any
serious harm. \Gls{Adora} asks her to pursue the matter with utmost seriousness, and hopes that
\Gls{Vimes} will push for the perpetrators to be charged with treason.

\subsubsection{\Gls{Vetina} decides to act swiftly against the dwarf insurgents hitting the
    semaphore network}
\Gls{Vetina} receives news of a second semaphore tower being attacked by rebel dwarves, and asks
\Gls{Drumk} to send a message to \Gls{RhysR} asking for an investigation. He also orders \Gls{Vimes}
to be notified of the need to set out to Bonk if needed, and considers the attack on the semaphore
network an impediment to the new world government being built on the back of the Peace Accords.

\subsubsection{\Gls{RhysR} listens to \Gls{Ardent} pushing his next agenda at the Meeting Hall}
\Gls{RhysR} thinks about the political unity among the trolls, and envies \Gls{Shine}, the King of
Trolls his easy job. He listens to the report of \Gls{Aeron}, the envoy back from Ankh-Morpork, as
the representatives of various dwarf factions jostle for his attention in the Meeting Hall. He
listens to \Gls{Ardent} argue against the export of fat mined in Schmatlzberg, only to be met with
sharp dissent by a faction of hereditary fat miners.

\subsubsection{\Gls{RhysR} outlaws the dwarf insurgents attacking the semaphore towers}
\Gls{RhysR} makes an argument for progress, and co-operation with the various sentient races of the
Disc, and is shocked when \Gls{AlbreA} tells him that some fundamentalist priests have continued
the attacks on the semaphore towers. He promises to track down and bring the perpetrators to dwarf
justice, as the other factions try to drown out his voice with their objections. \Gls{RhysR}
formally declares the offending dwarves to be terrorists, and excommunicates them from dwarf
society.

\subsubsection{\Gls{Vetina} contemplates the possible opposition to the new railways}
\Gls{Vetina} reads the editorial in the Times complaining about the railway network putting the
coachmen out of their jobs, and wonders how he can avoid the inevitable backlash. Meanwhile, a
dwarf who had witnessed the Koom Valley accords in person recounts the sudden end of hostilities
with the trolls, and the two kings who had been frozen underground playing a board game. He talks
about the reply from \Gls{Vetina} regarding the whereabouts of his eldest son, who got caught up
with the extremist dwarves.

\subsubsection{\Gls{Vetina} asks \Gls{Moist} to go take a look at \Gls{HarryK}'s train ride}
\Gls{Vetina} thinks about the young dwarf who is in prison waiting trial, and hopes to turn him
into a witness that can provide the names of the terrorist leaders. The next morning, \Gls{Vetina}
asks \Gls{Moist} to go investigate the impromptu amusement part that \Gls{HarryK} has opened up
next to the train track, and asks him to bring \Gls{Drumk} back if he is done blowing the train's
whistle to his heart's content.

\subsubsection{\Gls{Moist} sees where he will fit in as the railway network is planned out}
\Gls{Moist} works his way through the crowds lining up to ride the train, and notices \Gls{OttoC}
readying his camera for the Times. He goes to \Gls{HarryK}'s office, and is introduced to
\Gls{Thun}, who outlines a contract between \Gls{HarryK} and \Gls{DSim}, that would give a small
tie-breaking vote to the city, represented by \Gls{Vetina}. \Gls{DSim} walks in, and reminds them
of the need to acquire the land on which the rails will be laid, and \Gls{HarryK} asks \Gls{Moist}
to use his skills in dealing with this thorny issue,

\subsubsection{\Gls{Moist} finds \Gls{Drumk} and leaves the fair ground with him}
\Gls{HarryK} asks \Gls{DSim} if he needs reinforcements for his workshop back home in order to
protect his intellectual property, and is amused to learn that \Gls{DSim} has set up enough booby
traps for that eventuality. Meanwhile, \Gls{Moist} finds \Gls{Drumk} exiting the engine covered in
coal dust and grease, and gets him cleaned up for the trip back to the palace.

\subsubsection{\Gls{Moist} talks about the first train line as \Gls{Vetina} remains skeptical}
\Gls{Colon} and \Gls{Nobby} try to bluff their way through an explanation, when some children
waiting in line ask them how the train works. Meanwhile, \Gls{Vetina} asks \Gls{Drumk} to get
cleaned up, and asks \Gls{Moist} if a train to Uberwald will be viable, given the mountainous
terrain and the bandits. \Gls{Moist} states that the first destination that \Gls{DSim} has in mind
is his own town on the outskirts of Sto Lat, which happens to be the geographical center of every
major city in the region.

\subsection{}
\subsubsection{\Gls{Moist} starts his tedious mission of acquiring land for the railroads}
\Gls{DSim} quickly delegates the task of surveying land and making rails to the local engineers of
Ankh-Morpork, with \Gls{Moist} having the ugly task of convincing the land-owners in between
the city and Sto Lat to give up the land needed by the railway. A few days later, \Gls{Moist} learns
that someone is trying to con land-owners by posing as a different railway company, claiming to have
a better engine soon to be shown off to the Disc.

\subsubsection{\Gls{Moist} reports back to \Gls{HarryK} after dealing with the landowners}
\Gls{Moist} gets back to \Gls{HarryK}'s office with a list of aristocrats provided by \Gls{Drumk},
who had all cut deals with him for the use of their land. The two of them proceed to the newly
installed steelmaking foundry in the compound, pumping out steel rails at an impressive rate using
golems to do the dangerous handling of hot iron.

\subsubsection{\Gls{Moist} learns from \Gls{Vetina} that there is political pressure to get a
    cargo rail to Quirm}
\Gls{HarryK}'s wife \Gls{Effie} takes a special interest in the running of the railways, since
it represents a way out of the excrement and trash business for the family. \Gls{Moist} returns from
his next round of negotiations with the rural landowners, and \Gls{Vetina} reminds him of the need
to establish a rail route to Quirm post haste, in view of the fresh seafood that needs to come into
the city.

\subsubsection{\Gls{Sweep} talks to \Gls{Ridcu} about the steam engine technology's emergence}
\Gls{Sweep} walks into \Gls{Ridcu}'s office at the University, and reports that the \Gls{AbbotH}
is concerned about steam engines coming to the Disc before their time. \Gls{Sweep} states that he
is personally in favour of letting the steam engine into the Disc, and seeing what chaos results
from the progress that it will inevitably cause.

\subsubsection{\Gls{Moist} talks to \Gls{DSim} about troubles with guild certification}
\Gls{Moist} listens to a pitch by \Gls{AJolson} about supplying the food for the train passengers,
as well as the people at the waiting rooms in every railway station. He then finds \Gls{DSim}
sulking next to his engine, having been told by \Gls{Pony} of the Artificers' Guild that he cannot
earn the rank of master before spending a few years at each of the lesser ranks. \Gls{Moist}
consoles \Gls{DSim}, and points out that \Gls{HarryK} would be more than happy to welcome him into
his family, as the husband to his niece \Gls{EmilyK}.

\subsubsection{\Gls{DSim} gives an interview on the eve of his train's launch from Sto Lat}
At the inaugural run of \Gls{DSim}'s train from Sto Lat to Ankh-Morpork, \Gls{Keli} launches the
locomotive from its shed, and \Gls{DSim} brings it to a gentle stop at the platform meant for
passengers to board. \Gls{Moist} recognizes the debacle that could result from the press getting
their hands on \Gls{DSim}, and moves to intercept them. He finds \Gls{DSim} more than capable of
fending off malicious journalists, intent on harassing him with questions about the train's safety.

\subsubsection{\Gls{Moist} and the passengers enjoy the maiden ride of \Gls{DSim}'s locomotive}
\Gls{Effie}'s idea of lavatories on the trains is a big hit, with \Gls{HarryK} making sure that the
waste is collected in a tank for processing in his yard at Ankh-Morpork. \Gls{deWorde} gets the
honour of being the first passenger to step onto the train, with a front-page photograph in the
Times to commemorate the event. After the train arrives at Ankh-Morpork, in a railway station
constructed in \Gls{HarryK}'s compound, he gives a speech announcing that Quirm will be the next
destination serviced by the railway.

\subsubsection{\Gls{BSlick} tries to manage the growing number of recruits in the railway}
\Gls{BSlick} supervises the line of young recruits, and sends a young woman up to \Gls{HarryK}'s
office, when she claims to be capable of speaking every major language on the Disc, and asks for a
job as a translator. When he comes back from his next round of land-acquisitions, \Gls{Moist}
is glad to see two more engines plying the intercity route, as \Gls{HarryK} drags him along to
the engine shed, where the latest prototype steam engine is being finished up.

\subsubsection{\Gls{Stibb} takes the faculty along for their first train ride}
At their manor, \Gls{Adora} tells \Gls{Moist} that the goblins manning the semaphore towers have
now been issued binoculars, and that she has been using them to keep tabs on his movement. They
share a rare day off, and give the staff leave to visit the train station for the evening.
\Gls{Stibb}, who is convinced that the train is merely a mechanical advancement, takes the rest of
the University's faculty on a train ride to the next town, in order to get them to endorse it.

\subsubsection{\Gls{Moist} saves two toddlers from the coming train}
\Gls{Moist} saves two toddlers placing their heads on the railway track to feel the train's
vibrations, and wakes up in the hospital a while later, with \Gls{Lawn} certifying him for
discharge. \Gls{Adora} takes him to the nearby room, where the families of the two children thank
him profusely, as \Gls{deWorde} shows up intending to extract a sound bite about the dangers posed
by the railway network.

\subsubsection{\Gls{Moist} asks \Gls{HarryK} to take railway safety more seriously}
\Gls{Moist} carefully avoids maligning the railway when \Gls{deWorde} tries to ask him about the
reservations held by old people all over the region, regarding the noise and air pollution caused
by the trains. After the interview, he immediately goes to \Gls{HarryK}'s office, and asks him to
take down the amusement train for a week, in order to install some safety features to stop any more
incidents from happening.

\subsubsection{\Gls{Moist} learns about a no-man's land in Quirm, ideal for laying railway tracks}
\Gls{Moist} is invited to the estate of a famous wine-grower in the outskirts of Quirm, as he
struggles to deal with the property inheritance laws guaranteeing a piece of ancestral land to every
child. The \Gls{Marqui} points out a wasteland on the map where bandits roam unchecked, and
\Gls{Moist} asks if the land is state-owned. He is relieved to know that it is, and decides to
come up with a way to rid the area of bandits.

\subsubsection{\Gls{Ardent} tries to systematically spread his insurgent ideology in Ankh-Morpork}
In a dwarf bar somewhere in Ankh-Morpork, an unknown dwarf incites violence among the others,
calling out \Gls{RhysR} for bowind down to \Gls{Vetina}'s political pressure. He points out the
exclusion of dwarves from employment in the railways, even as someone points out that the dwarf
insurgents hitting the semaphore network is likely to be the cause. After the dwarves are
sufficiently riled up, \Gls{Ardent} sneaks out to the next bar, hoping to sow discontent one tavern
at a time.

\subsubsection{\Gls{Moist} enlists \Gls{HarryK} for the cleanup operation in the badlands}
\Gls{Moist} is pleased to see \Gls{HarryK} pounce at the opportunity to clear out the badlands
around Quirm, and possibly claim ownership of the land for the railway line. Against \Gls{Effie}'s
advice, \Gls{HarryK} chooses to accompany his men to the badlands, and asks \Gls{Moist} to meet
him there the next day.

\subsubsection{\Gls{Moist} asks \Gls{Adora} to borrow \Gls{Twili} for a peace mission}
\Gls{Moist} and \Gls{HarryK} watch the gangsters go to town on the bandit camp deep in the badlands,
and eventually reach the \Gls{Marqui}'s manor with all the captured bandits tied up for delivery.
Back at his home, \Gls{Moist} reports on the raid and the resulting transfer of prisoners to
\Gls{Adora}, before asking her to take \Gls{Twili} along to Quirm as a goblin envoy.

\subsubsection{\Gls{Moist} and \Gls{Twili} travel to \Gls{Marqui}'s chateau}
Somewhere in Ankh-Morpork, a progressive dwarf is held captive in a dark cellar by some priests,
awaiting punishment for his crimes of befriending trolls and abandoning the traditional ways of
the dwarves. Meanwhile, \Gls{Moist} takes \Gls{Twili} along to \Gls{Marqui}'s chateau, where the
goblin introduces himself as en envoy to the goblins in the Quirm badlands.

\subsubsection{\Gls{Twili} presents a hopeful future for the Quirmian goblins}
\Gls{Twili} spots a dwarf surveilling \Gls{Moist} from a tree top, as the \Gls{Marqui} hosts them
for dinner at his terrace. The two of them set out into the badlands to meet the goblin squatters,
where \Gls{Twili} gives a grand speech to the Quirmian goblins talking about life as a free citizen
in Ankh-Morpork, with rights and wages for every one of them.

\subsubsection{\Gls{Moist} is forced to lead the Quirmian goblins back to the railway camp}
\Gls{Moist} is forced to follow the Quirmian goblins deeper into the badlands, and \Gls{Twili}
informs him that they falsely believe him to be a great warrior, who can deal with any remaining
threats in their land. \Gls{Twili} points the way to the railway track-laying camp, and believes
that more dwarves are waiting to ambush him there.

\subsubsection{\Gls{Moist} attacks the dwarf assassins with the Quirmian goblins}
\Gls{Moist} finds the track-layers killed by the dwarf squad, and \Gls{Twili} prepares to track
them down using their scent. \Gls{Moist} enters a berserker rage after drinking some herbal tea
offered by a goblin elder, and is told later on that he killed several dwarf assassins the sneak
attack. After fully recovering his senses, \Gls{Moist} immediately realizes the need for an
official recording of the crimes against the railway, and asks for the \Gls{Marqui} to be brought
to the site.

\subsubsection{\Gls{Moist} gets the remaining Quirmian goblins back to Ankh-Morpork}
\Gls{Moist} has the remaining goblins sent to \Gls{HarryK}'s compound along with a hearty meal and
the bodies of their brethren who lost their lives in the ambush. He returns to the golem horse,
which is dutifully frolicking in a nearby meadow, and gets back to his house. \Gls{Adora} informs
him that there is plenty of room in her semaphore network for the Quirmian goblins to put themselves
to use, and congratulates him on his bravery.

\subsubsection{\Gls{Moist} is relieved to find that \Gls{Vimes} approves of his actions}
\Gls{Moist} desperately tries to fend off \Gls{Angua}'s questions about his actions at the railway
camp, as \Gls{Vimes} comes in to interrupt the deposition. He is surprised to see \Gls{Vimes} being
happy with his actions against the dwarf insurgents, and asks him to keep \Gls{Adora} out of the
city for the time being. On his way to the palace, \Gls{Moist} is accosted by a dwarf who informs
him that the priests have him on a kill list which contains \Gls{Vimes} and \Gls{Vetina} as well.

\subsubsection{\Gls{RhysR} puts a fatwa on \Gls{Ardent}}
\Gls{Vetina} asks \Gls{Moist} not to worry too much about the terrorists, and reminds him that
political pressure is being put on \Gls{RhysR} to sort out the trouble with the fundamentalist
dwarves. Meanwhile, \Gls{RhysR} asks for \Gls{Ardent} to be apprehended and brought to him, once
he realizes who is breeding the insurgency among the city dwarves. \Gls{Bashf} echoes his
sentiments, making an appeal to the dwarf God of Creation and his teachings of tolerance.

\subsection{}
\subsubsection{\Gls{DSim}'s prototype engine defends itself against a dwarf saboteur}
A dwarf intending to sabotage the prototype engine sneaks into its shed at night, and is killed when
it blows steam at him in self-defense. \Gls{Nobbs} and \Gls{Colon} arrive some time later upon
hearing the loud train whistle, with \Gls{Nobbs} believing that the train had acted out of its own
accord. The next day, \Gls{DSim} tries to tell \Gls{Moist} that an impromptu religion has sprung up
around the prototype engine, with citizens still going on the joyride in \Gls{HarryK}'s compound
as if it were a pilgrimage.

\subsubsection{\Gls{Moist} prepares to deal with some rural tinkerers dying in an experiment gone
    wrong}
\Gls{Moist} points \Gls{DSim} to a upscale tailor to get ready for his dinner with \Gls{EmilyK}, and
goes to the shed the next day to find \Gls{HarryK} obsessing over a bow tie. Early next morning,
\Gls{HarryK} barges into \Gls{Moist}'s bedroom with news of two blacksmiths dead in a steam engine
experiment out in some remote town. \Gls{Moist} reassures him about the press wanting to cover the
accident, as \Gls{Adora} returns home with news that the accident only involved a primitive boiler.

\subsubsection{\Gls{Moist} gets ahead of the press to visit Scrote after the accident}
\Gls{Moist} travels to Scrote, a small coal-mining town, on his golem horse, and manages to get
there well before anyone from the press. He pays the local barman to escort him to the site of the
accident, and learns that the remains of the two tinkerers are now in a bucket in the bar's
basement. \Gls{Moist} is impressed by \Gls{DSim}'s composure in front of the journalists, as
\Gls{HarryK} gives the discreet go-ahead to establish an academy in Ankh-Morpork to train railway
engineers for the future.

\subsubsection{The dwarf insurgents lose followers, as more of them desert the cause}
The fundamentalists perform a purge of their own ranks, killing all who start to waver in their
faith. Meanwhile, \Gls{Thun} reassures \Gls{HarryK} that the primacy and market dominance of his
Hygienic Railway Company will remain unshakable, even as copycat engineers figure out how to
replicate the steam engine, or even come up with improvements to the basic design.

\subsubsection{\Gls{Vetina} insists on a non-stop train service to Bonk}
\Gls{Vetina} summons \Gls{Moist} to the palace, and asks him to get a non-stop train service to
Uberwald ready as soon as possible. \Gls{Moist} tries to tell him about more urgent and more
achievable targets for the railways, and finds that \Gls{Vetina} is not in the mood to listen.
\Gls{Moist} travels to Scrote to offer a pension from \Gls{HarryK} to the old woman who lost her
sons in the boiler accident, while thinking about the timeline for the express line to Bonk to be
up and running.

\subsubsection{\Gls{Upshot} sees the goblins in the shire start work on their underground railway}
\Gls{Moist} and \Gls{Thun} try to convince \Gls{HarryK} to offer shares in his railway company, in
order to quell dissent about the laying of railway lines, and to spread the risk out among more
investors. Meanwhile, \Gls{Upshot} travels to the goblin settlement in the Shires, where he learns
that some of the goblins working for \Gls{HarryK} have sent back blueprints for a small-scale
underground railway. He is impressed by the goblins' idea of linking all of their settlements using
a fully underground network of trains.

\subsubsection{\Gls{Moist} gets a railway tourism agent to write travel journals for the passengers}
As work on the Quirm line is completed, tracks are laid down for the express line to Uberwald, with
the railway workers building residences next to each workshop and station along the railway lines.
Meanwhile, \Gls{Moist} finds a widow interested in making a travel journal, and asks her to send a
copy of her writing to him for use as promotional material in the railways. \Gls{HarryK} is pleased
to see his comapny get a fair royalty when \Gls{Thun} makes all the toy manufacturers sign contracts
to produce toy trains, complete with human figurines and winding toy tracks.

\subsubsection{\Gls{RhysR} decides to attend the peace summit at Quirm in person, representing the
    dwarves}
\Gls{Moist} takes a sleeping potion from \Gls{Twili}, and spends the entire day sleeping to recover
his strength. Meanwhile, \Gls{RhysR} learns from \Gls{Aeron} that the insurgency is weakening
every day as members realize the economic benefits of integrating with the other kingdoms. The Low
King then confirms his intent to attend the interspecies peace summit at Quirm.

\subsubsection{\Gls{Moist} receives another scolding from \Gls{Vetina} regarding the Uberwald line}
\Gls{Moist} is summoned back to Ankh-Morpork as he supervises the laying of railway lines to
Uberwald, in a tent next to the rail head. Once at the palace, \Gls{Vetina} reminds \Gls{Moist}
about the urgency needed in completing the line to Uberwald, without offering any solid reason why.
\Gls{Moist} is relieved at the news of no more terrorist attacks in the last few months, as
\Gls{Vetina} points out the reports from \Gls{Vimes} and his agents across the kingdoms.

\subsubsection{\Gls{Moist} is forced to reassure the public after the first train accident}
\Gls{Moist} comes up with a plan to speed up the line to Uberwald, and outlines it to \Gls{HarryK}.
He puts emphasis on the idea of \Gls{HarryK} being elevated to Baron from a mere Lord, if the plan
succeeds without any hitches. The first railway accident happens on a private line between some
vineyards in Quirm, when two trains have a had on collision on their single track. \Gls{Moist}
tries to remind everyone through the paper that safety is of vital importance in the operation of
anything as fast and heavy as a train.

\subsubsection{\Gls{AlbreA} is forced to confront \Gls{Ardent}, who consolidates his power in
    Schmatlzberg}
\Gls{AlbreA} notices the growing coup in Schmatlzberg, as \Gls{Ardent} and his followers convince
the dwarf factions one-by-one to side with them over \Gls{RhysR}, who is off to Quirm. Eventually,
\Gls{Ardent} forces a show of hands at the throne room in Schmatlzberg, as \Gls{Albert} leads the
contingent of dwarves still remaining loyal to \Gls{RhysR}.

\subsubsection{\Gls{Margo} communicates news of the coup in Schmatlzberg to other leaders}
\Gls{Margo} receives news of the coup in Schmatlzberg, and flies to the next semaphore tower which
is active, in order to have the news sent to the other power-centers of Uberwald. \Gls{Moist} is
woken up before dawn and summoned to the palace by \Gls{Vetina}'s guards, with \Gls{Adora} annoyed
at the abrupt end of their day off. \Gls{Vetina} asks him to go to Quirm as soon as possible, and
gather up \Gls{RhysR}'s retinue for a swift train ride back to Uberwald, on the new line.

\subsubsection{\Gls{Vimes} sends an armed escort with \Gls{Moist} to accompany \Gls{RhysR}}
\Gls{Vimes} asks \Gls{Moist} to seek out \Gls{Bashf} in Quirm, in order to act as a liaison with the
dwarf contingent from Uberwald. \Gls{DSim} insists on using his first prototype engine for the
special mission, and asks \Gls{Moist} to get on the train to Quirm. Once at Quirm, \Gls{Bashf} takes
him to the manor occupied by the Low King's entourage, and tells him about the suspicions brewing
inside the court.

\subsubsection{\Gls{Moist} gets \Gls{RhysR} and his trusted inner circle out of Quirm}
\Gls{Moist} tells \Gls{RhysR} that he cannot unveil \Gls{Vetina}'s secret plan to get him back to
Uberwald in front of the courtiers, any one of whom might be in league with the coup. \Gls{Moist}
asks for a decoy to be put in place of \Gls{RhysR} at the party downstairs, and escorts the
dignitaries out by the back entrance, on coaches bound for the Quirm terminus.

\subsubsection{\Gls{Moist} and the other bodyguards prepare to escort \Gls{RhysR}, as dictated
    by \Gls{Vimes}}
Once back at \Gls{HarryK}'s manor in Ankh-Morpork, \Gls{RhysR} greets \Gls{Vetina} and the other
dignitaries at the formal dinner, and lets slip the fact that the railway line to Bonk is not yet
fully laid. After the dinner, \Gls{Vimes} makes a show of sending a decoy of the Low King to
Uberwald by road, complete with armed escort. \Gls{Moist} gets suited up as a working-class drunk,
and takes his place in the cheap compartment, with the others accompanying \Gls{RhysR} sitting in
other coaches.

\subsubsection{\Gls{Moist} and \Gls{RhysR} hide out in \Gls{Elsie}'s new home}
The two decoy coaches are set upon by the insurgents, who recognize \Gls{RhysR}'s royal seal painted
on them. The Watchmen make short work of the ambushing terrorists, and take the captured terrorists
back to the city for interrogation. While waiting for the next train at Sto Lat, \Gls{Moist} and
\Gls{RhysR} are escorted to \Gls{Elsie}'s house, which is furnished with the best that money can
buy. \Gls{DSim} arrives a while later, after the Low King has finished his meal and gone to sleep,
to greet his mother before returning to his duties.

\subsubsection{The terrorist dwarves plan to hit the coal resupply stations along the rail route}
The insurgents kill a dwarf from Ankh-Morpork who hands over the locations of the coal-refilling
stations on the route to Uberwald, in an attempt to tie up loose ends. \Gls{Moist} gets on the next
train the day after, with \Gls{RhysR} being disguised as a middle-class businessman. He meets
\Gls{Vimes} and \Gls{Detri} in the guard coach, both incognito as common railway security.

\subsubsection{\Gls{Moist} sniffs out two insurgent dwarves hiding among the passengers}
\Gls{Moist} pulls the emergency cord when he spots two dwarves trying to hide their stress,
summoning \Gls{Vimes} and his watchmen to the cabin. \Gls{Vimes} makes a show of detaining them for
riding without a ticket, and takes them to the private guard cabin to interrogate them individually.
\Gls{Moist} watches \Gls{Vimes} extract a list of names from the two captured dwarves, and applauds
his careful tactics in trying to appear as friendly as possible.

\subsubsection{\Gls{Moist} bides his time in the guard cabin}
\Gls{Moist} watches one small town after another fly past as the train heads to Zemphis, the
outermost station currently serviced by \Gls{HarryK}'s company. At dusk, \Gls{Moist} goes to the
guard van, where \Gls{Twili} prepares coffee for the Watchmen in disguise. He spends some time
on top of the carriage, just to savor the wind blowing in his face, and gets back down in time for
\Gls{Vimes} to return with news of the track-laying up ahead.

\subsubsection{\Gls{Moist} and the escort make it to Zemphis on the regular train service}
The next morning, \Gls{Moist} wakes up to find \Gls{Bashf} deep in conversation with \Gls{RhysR} in
their private carriage, busy discussing how to deal with the supporters of \Gls{Ardent}'s coup.
\Gls{Moist} thinks about the small village settlements in the mountains that will soon have a
cheap and convenient path to the big cities, and prides himself on getting the railways to where is
is. \Gls{Vimes} and \Gls{Moist} escape a poisoned arrow at the Zemphis railway station, while
waiting for the improved prototype engine to catch up to them.

\subsubsection{\Gls{Moist} and the train proceed to the mountain passes using the refurbished
    engine}
The insurgent leaders receive news of two of their spies being captured on the train service to
Zemphis, and refocus all of their remaining resources to the train line. As the new locomotive
heads up to the mountain passes, the insurgents roll boulders down the slopes on either side to
try and trap it by damaging the rails.

\subsubsection{\Gls{Vimes} interrogates more of the insurgents after their attack fails}
The train is forced to slow down as the assailants are dealt with by the trolls and goblins, with
\Gls{Moist} focusing on the coal-feeder and driver's compartments. After the ambush ends,
\Gls{RhysR} asks for the attackers to be taken prisoner so that \Gls{Vimes} might extract more
names from them, hopefully including those of the primary instigators. A while later, some kids
stop the train by waving their clothes on the tracks, talking of a landslide after the blind turn
up ahead.

\subsubsection{\Gls{Moist} takes a break at a small mining town, while another train scouts ahead}
\Gls{Moist} works out that the children triggered the landslide as a prank, and asks their parents
to warn them of the risk to the passengers. He asks them to help clear the blockage, and makes it
to the next station, located in a small mining town. \Gls{CheerF} is put on a decoy train as the
dummy target for the insurgents, as \Gls{Moist} and his party have a hearty meal in the town.

\subsubsection{\Gls{RhysR} saves the train from a derailment trap}
\Gls{RhysR} pulls the emergency brake when he spots the decoy train derailed up front, and
\Gls{Moist}'s sleep is interrupted by the commotion. \Gls{CheeryL} and her crew hide in a nearby
cave, as the last ambushers are killed by the train's boiler, which is rigged to explode. Some
gnomes help refill the train's water reserves, while \Gls{Detri} looks for the railway workers who
were assigned to the bunker.

\subsubsection{\Gls{AlbreA} bides his time in the dwarf prison waiting for \Gls{RhysR} to return}
\Gls{Moist} and the party depart, with the gnomes being inducted into the railway company as
specialist ironworkers. \Gls{Vimes} helps some of the overworked engineers get some sleep, as the
train nears the Wilinus mountain pass, which marks the entrance to Uberwald. Meanwhile, \Gls{AlbreA}
shrugs off \Gls{Ardent}'s attempts to taunt him in the dwarf prison, and reminds him of how quickly
his followers will flip to the Low King's side when he returns to Schmatlzberg.

\subsubsection{\Gls{DSim} worries about crossing the bridge leading to Wilinus Pass}
\Gls{AlbreA} receives the latest semaphore news from a goblin, who has been tasked with delivering
the news to him, and gives his own replies to be sent to \Gls{RhysR}. \Gls{DSim} believes that the
bridge over the chasm leading to Wilinus Pass will not hold the weight of the train, and \Gls{Moist}
reassures him about the secret plan he has brewing.

\subsubsection{\Gls{Moist} pulls out his secret weapon at the chasm to Wilinus Pass}
\Gls{Moist} figures out that the Low King secretly female, and is pleased to see \Gls{RhysR}
confirm the fact in private. He speculates that \Gls{Aeron} and \Gls{RhysR} might be lovers, as he
returns to the engine compartment in time for the train to reach the chasm. \Gls{Moist} points out
that the night-time fog is enchanted to be as strong as solid ground, and gets \Gls{DSim} to
chug full steam ahead onto the bridge.

\subsubsection{\Gls{Moist} and \Gls{Vetina} prepare for the final ambush before reaching Bonk}
\Gls{Moist} hopes that \Gls{Vetina} will never learn of how desperate his last-minute plan had been
at the bridge, as the train settles back down onto the tracks after crossing the chasm. He recalls
\Gls{Vetina}'s strict refusal of the plan to commandeer the city's golem army, while maintaining the
screen of plausible deniability. \Gls{Vimes} and the Watchmen fend off the next ambush, as the
terrorists separate the engine from the rest of the train, causing them to be stranded in the
dangerous mountain path.

\subsubsection{\Gls{Moist} is reunited with the rest of the train}
The troll officers on board the guard carriage pedal the manual bogey, and manage to catch up to the
rest of the train, where the terrorists are trying to get into \Gls{RhysR}'s armored compartment.
\Gls{Vimes} and \Gls{Moist} climb onto the roof to fend off the dwarves leaping in from the
cliffs, as the train enters a long tunnel.

\subsubsection{\Gls{Vimes} receives the latest news about Schmatlzberg from \Gls{Sally}}
\Gls{Moist} breathes a sigh of relief as the train reaches the terminus at Bonk, with the mayor
fervently begging \Gls{RhysR} to restore the peace in Schmatlzberg. \Gls{Sally}, who has been
posted in Bonk by \Gls{Vimes} to act as an agent, reports on the fair treatment of \Gls{AlbreA}
inside the prison, as conveyed to her by some goblins keeping watch inside Schmatlzberg.

\subsubsection{\Gls{RhysR} initiates his retake of Schmatlzberg}
\Gls{RhysR} sends \Gls{Bashf} and \Gls{Aeron} as his messengers into Schmatlzberg, as the rest of
his entourage prepare their weapons for a final confrontation with \Gls{Ardent}'s faction.
\Gls{Vimes} speculates that the dwarves on \Gls{Ardent}'s side are desperate not to lose their lives
for the cause, and will likely lay down their weapons at the first sign of being outnumbered.
\Gls{RhysR} leads the others down to the throne room, with the belligerence largely coming to an
end by the time they arrive.

\subsubsection{\Gls{RhysR} consolidates his position as the Low King}
\Gls{RhysR} condemns \Gls{Ardent} to a trial bu jury, with the victims of his terrorism making up
the bench of jurors. He then decides to come out as female, hoping to drag the gender-agnostic
dwarf society into the modern era. \Gls{Bashf} hands a document to \Gls{RhysR} containing the names
of all the terrorist sympathizers, and asks for them to speak up if they feel that the Low King
does not have the right to the throne.

\subsubsection{\Gls{Moist} sees the engine ascend to godhood}
\Gls{Moist} is alarmed to find the first engine speak to him telepathically, declaring herself a
goddess given life by the prayers of the people who witnessed the railway. \Gls{DSim} arrives with
a heavy heart, at the prospect of leaving his beloved engine in Bonk, since the bridge across
Wilinus pass will take months to rebuild.

\subsubsection{\Gls{Drumk} asks \Gls{Charlie} to leave the palace when \Gls{Vetina} returns}
\Gls{Drumk} thanks \Gls{Charlie} for impersonating \Gls{Vetina} in order to distract the spies
keeping watch on the palace, and sends him back to his day job with a hefty reward. A while later,
\Gls{Moist} and the rest of his party return to the city by road, while the golems stay back in
Uberwald to help with the bridge restoration.

\subsubsection{\Gls{Vetina} gives \Gls{Moist} the most precious gift possible}
\Gls{Moist} watches everyone involved in the railway get medals and other titles at a formal
ceremony in the palace, and is summoned to the Patrician's office a while later. \Gls{Vetina}
reminds \Gls{Moist} that the only reward for him is the privilege of staying alive, to go on the
next adventure when the time comes.