\section{Reaper Man}


\subsection{}
\subsubsection{Some angels discuss \Gls{Death}'s alarming new personality}
Three minor angels tasked with auditing the Disc bicker about the trouble with \Gls{Death}
developing a humanoid personality to go with his physical form. \Gls{Azrael}, who is their superior,
burns one of them for using first-person pronouns, and sets them on the task of taming \Gls{Death}'s
excesses.

\subsubsection{\Gls{Death} receives a warning from a hooded monk}
\Gls{Death} is greeted by a mysterious hooded monk, as he examines his own hourglass stacked among
the endless shelves in his realm. The monk tells him that he is to be deposed from his position as
the grim reaper, and warns him that appealing to higher authorities might cause more trouble.

\subsubsection{Life-forms in the disc talk about their lifespans}
Some mayflies discuss the nature of life and death, even as some of them die at the end of their
twenty-four hour lifespan. Meanwhile, the same conversation goes on at a much slower pace, between
some pine trees, each thousands of years old. \Gls{WPoons}, the oldest wizard at Unseen University,
is thrown a surprise part by his colleagues, to celebrate his impending death.

\subsubsection{\Gls{Death} tells \Gls{CAlbert} about his retirement}
\Gls{Death} tells \Gls{CAlbert} that he has been forced into retirement by \Gls{Azrael}, and shows
him the new hourglass that condemns him to mortality. \Gls{CAlbert} is horrified by the prospect of
returning to the Disc and living out the rest of his lifetime, and hopes to adjust to his new
master with ease.

\subsubsection{\Gls{WPoons} passes on without \Gls{Death} arriving to reap his soul}
The \Gls{Bursar} helps \Gls{WPoons} with his last meal at his farewell party, and sees a plan for
rebirth in the aging wizard's diary. \Gls{WPoons} jokes about reincarnating as a woman, as the
time arrives for his death. The gathered wizards are intrigued when \Gls{WPoons} flops over dead,
but is not attended to by \Gls{Death}, who is obligated to reap every wizard's soul in person.

\subsubsection{\Gls{WPoons} reanimates as a zombie}
\Gls{WPoons} tries to go on to the afterlife, but finds no one waiting to guide his spirit. He
decides to return to his body, and reanimates as an undead man. He fumbles into the dining hall,
having to deal with involuntary processes in his body for the first time. The wizards are angry at
\Gls{WPoons} returning as a zombie, and set about trying to get rid of him.

\subsubsection{\Gls{WPoons} breaks out of the University after sunset}
\Gls{Ridcu} gathers his inner council of wizards to try and find ways to banish \Gls{WPoons} from
the Disc. Meanwhile, \Gls{WPoons} walks through the wall of the University, using his newfound
super strength. \Gls{Shoe} paints an undead support slogan next to the hole in the wall, as
\Gls{Modo}, the dwarf gardener at the University looks on in amusement.

\subsubsection{\Gls{WPoons} tries to end his existence as a zombie and fails}
\Gls{Ridcu} and his council try to make sense of \Gls{WPoons} returning to life, and wonder if there
is an epidemic of new undead being born on the Disc. \Gls{Bursar} wonders if \Gls{Death} himself is
on leave, and the souls of the departed have nowhere to go but back to their own bodies. Meanwhile,
\Gls{WPoons} tries to jump off a bridge with the help of \Gls{Colon}, but fails to drown. He
bemoans the boredom of being undead, and shambles away into the darkness.

\subsubsection{\Gls{Dibbl} shows \Gls{Colon} his infinite collection of snowglobes}
\Gls{Dibbl} hails \Gls{Colon} on his way back to the Watch House, and asks him to peer inside his
underground storeroom. \Gls{Colon} is alarmed to see a cupboard overflowing with snowglobes.
\Gls{Colon} is amused by them, and buys one off \Gls{Dibbl} on the spot. \Gls{Dibbl} is anxious to
organize them into his wagon to sell them on the streets, even as more of them pop into existence
in his cupboard.

\subsubsection{\Gls{WPoons} explores the city for the first time in a century}
\Gls{WPoons} is mugged by some youths, who stick a knife into his chest before running away, once
they realize he is a zombie. \Gls{WPoons} pulls out the knife, and tosses it away nonchalantly,
bemoaning the stain on his fancy robe. He walks into the criminal district of the Ankh-Morpork, and
is immediately ostracized for being undead. Dismayed by the pleasures unavailable to him, he returns
to the University, where the inner council apprehend him.

\subsubsection{\Gls{Ridcu} tries out folk recipes to get rid of zombies}
\Gls{WPoons} goes to his room at the University and tries to sleep, but ends up trying to organize
his memories. \Gls{Ridcu} comes in with some holy artifacts, and is dismayed to see them have no
effect on \Gls{WPoons}. He ushers the council out of \Gls{WPoons}' room, wondering what it would
take to fully kill him, and decides upon burying the zombified wizard under an intersection in the
city.

\subsubsection{\Gls{WPoons} finds a pamphlet from \Gls{Shoe} hidden in his coffin}
\Gls{Ridcu} and his council dig a hole under an intersection in the city, and bury \Gls{WPoons} in
the pit, using an elaborate coffin picked out by him. Once the wizards lower him into the ground
and pile the dirt on his coffin, he discovers a pamphlet from \Gls{Shoe}'s organization for
undead support, left inside the coffin for any undead to find.

\subsubsection{\Gls{Death} goes incognito as a farmhand named \Gls{BillD} in the Ramtop Mountains}
\Gls{Death} rides to the Ramtops, and finds work as a farmhand in Ms. \Gls{Flitw}'s dilapidated
farm, beset by a shortage of capable men to tend the fields. He offers the alias \Gls{BillD} when
the woman suspects him of being a fugitive on the run, given how fancy \Gls{Binky} looks.

\subsection{}
\subsubsection{\Gls{Ridcu} is summoned by the \Gls{Patri}}
\Gls{Dibbl} is amazed at the detailed reconstruction of monuments in Ankh-Morpork inside each of
the snow-globes, as he finishes peddling them to clueless citizens, happy to purchase an amusing
toy. Meanwhile, furniture starts to disassemble on its own at the University, with the \Gls{Patri}
sending a guardsman to fetch \Gls{Ridcu} to ask about the strange phenomena.

\subsubsection{\Gls{Ridcu} and his council make their way through the city in chaos}
\Gls{Ridcu} and his council try to make their way through the city, which is beset by objects coming
to life, absorbing the life-force that \Gls{Death} is no longer harvesting in a timely manner. They
watch several pieces of clothing fly out of windows, and hear the screams of citizens being
squished by their own furniture.

\subsubsection{\Gls{Cake} hears some voices speaking in her mind}
\Gls{Cake} hears some disembodied voices coming from her crystal ball, and goes into the room to
investigate, armed with a frying pan. The ceiling collapses, burying her in rubble, and her sentient
dog \Gls{Ludm} runs in to rescue her. \Gls{Cake} claims that she heard several voices shout all at
once, causing the roof to collapse onto her.

\subsubsection{\Gls{Modo} watches his flowers growing much faster than usual}
\Gls{Modo} observes the rapid pace at which the roses in the University Garden seem to be growing,
and believes it to be the effect of his new compost. \Gls{WPoons} digs his way out of the ground,
asking him if \Gls{Ridcu} and the others are still at the University. \Gls{Modo} tells him that they
have tramped off to the palace, and \Gls{WPoons} decides to use the opportunity to get himself
cleaned up.

\subsubsection{\Gls{Ridcu} meets up with the \Gls{CPriest} at the palace}
At the palace, \Gls{Ridcu} notices a contingent of priests assembled in the Great Hall, and drags
the \Gls{CPriest} to the side, to ask him about the origin of the commotion. The \Gls{CPriest}
is alarmed to learn that neither the gods nor the wizards' magic is the root cause of the
inanimate objects coming to life.

\subsubsection{\Gls{Vetina} calls for an emergency meeting of the Guildmasters}
As the wizards and the priests are persuaded to stop their petty fistfights by \Gls{Ridcu} and the
\Gls{CPriest}, they notice \Gls{Vetina} sneak out of his barricaded room using one of his secret
passageways. He orders the Guildmasters to assemble in his office, and is flummoxed when none of
them accept responsibility for the animated objects.

\subsubsection{\Gls{Cake} learns from \Gls{OMB} that the spirit world is getting crowded}
Meanwhile, \Gls{Cake} helps \Gls{OMB}, her primary spirit contact in the crystal ball, deal with
some challenges to his authority from newer spirits. She decides not to tell the priests about the
sudden increase in disembodied souls crowding the spirit world, and sets off to the University to
try and catch the ear of the wizards.

\subsubsection{\Gls{BillD} tries to fit in with the villagers in his new life}
\Gls{BillD} thinks back to his day as a farmhand, and of how he had quickly finished every single
task set by \Gls{Flitw}. He had then visited the nearby town, and learned some games from the
regulars, who were incapable of seeing his true physical form. Meanwhile, \Gls{Ridcu} decides to
summon \Gls{Death} using a ritual, and dismisses \Gls{Cake} as just another woman gone insane like
the \Gls{Bursar}.

\subsubsection{\Gls{Ridcu} receives a reply from a mysterious spirit, talking about \Gls{Death}'s
    retirement}
\Gls{WPoons} makes it to the address on \Gls{Shoe}'s pamphlet, and finds a support group for the
undead, buried within the wealthy district of the city. Meanwhile, a strange spirit answers the
summoning ritual initiated by \Gls{Ridcu} and informs him that \Gls{Death} has retired. It claims
that a replacement will soon be found, and asks to be patient with the side-effects in the interim.

\subsubsection{\Gls{Shoe} introduces his support group to \Gls{WPoons}}
\Gls{Ridcu} and the council work out the implications of excess life force remaining on the Disc,
and wonder who the new candidate might be for the role of grim reaper. Meanwhile, \Gls{Shoe}
welcomes \Gls{WPoons} to his support group, and introduces other the others assembled there,
including the vampire \Gls{AWink}, and the inverse werewolf \Gls{Lupi}. \Gls{WPoons} is amused to
find that \Gls{Doreen}, \Gls{AWink}'s wife, has embraced the vampire aesthetic, despite being human
herself.

\subsubsection{\Gls{WPoons} returns from \Gls{Shoe}'s meeting to find \Gls{Schl} in his room}
\Gls{WPoons} learns that \Gls{Schl} is a bogeyman with agoraphobia, and uses written notes to try
and scare people instead. After the meeting, \Gls{Lupi} fends off a mugger, and talks about his
lonely existence as a sentient wolf in the forests, before taking his leave. In his room at the
University, \Gls{WPoons} digs out his nest egg, and is surprised to see \Gls{Schl} taking residence
in his cupboard.

\subsubsection{\Gls{Death} is forced out of retirement by the same spirit that dismissed him}
The next day, \Gls{BillD} is invited by \Gls{Flitw} for some tea and polite conversation. He
struggles to keep up with the small talk, and resorts to sitting idly by watching her knit for
hours. The mysterious hooded spirit visits \Gls{BillD} in the barn, and smashes his new hourglass,
releasing all the time trapped within, and ending his retirement. \Gls{Death} goes back to his
House, wondering how anyone could withstand being alive, knowing their time is finite.

\subsection{}
\subsubsection{\Gls{BillD} has a bad dream about his own death}
\Gls{BillD} wakes up from his nightmare the next morning, believing it to be a premonition of his
own end. \Gls{Flitw} finds him in the barn, and makes him some porridge to start the day.
\Gls{BillD} is anxious at the prospect of taking a life for the first time, when the time comes to
slaughter some chickens, and lay rat poison for the coming harvest.

\subsubsection{\Gls{BillD} decides to rescue the innkeeper's daughter}
\Gls{BillD} meets the young daughter of the innkeeper in the town, who is able to see his true form.
She is satisfied with his explanation that he is a living skeleton, and starts repeating the
rumours of \Gls{Flitw} having some hidden treasure in her cottage. Later in the evening, the inn
is on fire, and \Gls{BillD} decides to put aside his policy of non-intervention, when \Gls{Flitw}
warns him that the little girl is trapped inside the building.

\subsubsection{\Gls{WPoons} decides to seek out the advice of \Gls{Cake}}
The \Gls{Libra} refuses entry for \Gls{WPoons}, since he is dead, and \Gls{Schl} suggests they go
talk to the only other expert on life-force, \Gls{Cake}. Along the way, \Gls{Lupi} joins them in his
wolf form, unable to talk but retaining his full human intelligence. Meanwhile, \Gls{Death} rescues
the innkeeper's daughter from the burning inn, by giving her some of his own time. He returns her to
\Gls{Flitw}'s home, and asks for a mundane healer to look at her wounds.

\subsubsection{\Gls{Flitw} helps \Gls{Death} prepare for the end of his own life}
\Gls{Flitw} finds \Gls{BillD} sharpening his scythe in the forge a while later, and accidentally
touches him. The illusion breaks for her, and she realizes that he is indeed \Gls{Death}. She is
alarmed to learn that the new grim reaper will come both for him and the little girl in a few hours,
and helps him sharpen his weapon to try and fight back.

\subsubsection{\Gls{Cake} talks to \Gls{WPoons} about the impending life-force crisis}
\Gls{Cake} talks about the build-up of life-force on the Disc, with nothing to ferry the souls of
the deceased to the afterlife. \Gls{WPoons} spots a snow globe on her shelf identical to the one in
his room, and is intrigued by their intricate design. Meanwhile, \Gls{Modo} is curious to see one
of his compost piles shudder with life, and is glad to see some metallic carts show up in the
garden all of a sudden.

\subsubsection{\Gls{Ridcu} and the inner council save \Gls{Modo} from his compost heap}
\Gls{Ridcu} and the council rescue \Gls{Modo}, who has been swallowed by the sentient heap of
compost. They take him to the University's Great Hall, and are horrified when the compost heap
secretes acid to eat through the wooden doors leading inside. In a last desperate play, \Gls{Ridcu}
throws his bottle of gunpowder enhanced hot-sauce into the compost pile, and it explodes when it
digests the sauce.

\subsubsection{\Gls{BillD} asks the blacksmith \Gls{NSim} to destroy his scythe}
\Gls{BillD} gets to work harvesting the corn with some villagers, and is happy to see his growing
ability to tell them apart based on their unique personalities. He heads to the village blacksmith
\Gls{NSim}, and asks him to melt down his scythe. \Gls{NSim} proudly shows off his prototype
combine harvester, and \Gls{BillD} realizes that his life as a farmhand is soon to become redundant.

\subsubsection{\Gls{Cake} allows \Gls{WPoons} to question \Gls{OMB} about the life-force crisis}
At \Gls{Cake}'s divination room, \Gls{WPoons} asks her to perform a seance to communicate with
\Gls{OMB}. The spirit confirms \Gls{WPoons}' guess that the snowglobes were eggs of some life-form
that hatched into the metalwork trolleys.

\subsubsection{\Gls{Ridcu} is eager to confront the rest of \Gls{Modo}'s compost heaps}
\Gls{Ridcu} retrieves his staff from his room, and notices a metal trolley squashed under his bed.
He joins the inner council in their fight against the remaining compost heaps, and is dismayed to
find that they have not become sentient yet. Meanwhile, \Gls{WPoons} decides to flop over, so that
\Gls{Ludm} might get a chance to leave the house. She insists on carrying him back to the
University, against the wishes of her mother \Gls{Cake}.

\subsubsection{\Gls{Ridcu} and the inner council deal with some runaway trolleys}
In the University Garden, the metal trolleys come alive, and one of them drags the \Gls{Bursar}
along when he tries to stop its escape. \Gls{Ridcu} and the rest of the council give chase, anxious
not to fire any magic that might accidentally hit the \Gls{Bursar}.

\subsubsection{\Gls{WPoons} and his party encounter a sentient trolley in the library}
\Gls{WPoons} is forced to walk through the library door, when the \Gls{Libra} continues to deny
him entry, and calmly shrugs off the ape's attempts to decapitate him. The \Gls{Libra} then spots
a sentient trolley trying to sneak out of the library with some stolen books, and gives chase.
\Gls{Lupi} is injured in the pursuit, and is attended to by \Gls{Ludm}, who believes him to be a
mundane wolf-dog. \Gls{WPoons} and the \Gls{Libra} manage to dismantle the trolley and recover the
books.

\subsection{}
\subsubsection{The \Gls{Bursar} is freed from the trolley hauling him along}
The \Gls{Dean} manages to get a clear shot at the trolley dragging the \Gls{Bursar}, and manages to
wreck it. As the \Gls{Bursar} crawls out of the wreckage, \Gls{Ridcu} realizes that his swear words
are bringing nasty insects to life, by tapping into the life-force saturating the Disc. They notice
more trolleys traveling in a common direction all over the city, and set off in pursuit.

\subsubsection{\Gls{BillD} outperforms a combine harvester}
\Gls{BillD} tires himself out trying to compete with \Gls{NSim}'s combine harvester, as it goes on
its maiden run in a neighbouring cornfield. He is brought back to \Gls{Flitw}'s cottage by the
other farmhands, who are amazed by his efficiency. \Gls{Flitw} notices the start of a hailstorm
and rushes out to save the harvested corn. \Gls{BillD} offers to help, alarmed at the prospect of
his effort going to waste.

\subsubsection{\Gls{NSim} decides not to kill \Gls{BillD}'s scythe}
\Gls{NSim} struggles to make sense of \Gls{BillD}'s demand that his scythe be killed, as he basks in
the successful run of his new machine. He decides not to let such a unique piece of equipment go to
waste, and hides it in his workshop instead of getting to work dismantling it. Meanwhile,
\Gls{Ridcu} and the wizards fail to hold back the tide of trolleys converging to some point outside
the city. They decide to head back to the university to bring more powerful spells along.

\subsubsection{\Gls{WPoons} reads about the founding of parasitic cities}
\Gls{WPoons} reads some books fished out by the \Gls{Libra}, and stumbles upon the description of a
parasitic city, that used metallic trolleys to lure the inhabitants of an actual city, in a form
of predation. Meanwhile, \Gls{Ridcu} and his wizards are surrounded by an every-growing ring of
trolleys, seeking to keep them busy as the rest of the trolleys complete their migration.

\subsubsection{\Gls{BillD} spots the new reaper of souls stalking him}
\Gls{BillD} helps \Gls{Flitw} save the corn from the coming hailstorm, and sees a vision of
\Gls{Death} in the combine harvester, as lightning strikes the fields. \Gls{Flitw} spots a robed
figure on a horse holding a scythe, outlined against the lightning, and asks \Gls{BillD} if the new
reaper of souls has come for him. He decides to harness \Gls{Binky}  take \Gls{Flitw} and the little
girl along to the town, to find his scythe.

\subsubsection{\Gls{BillD} confronts the new grim reaper at midnight using his magical scythe}
\Gls{BillD} vanishes into the blacksmith's shop when the new grim reaper makes his appearance at
the stroke of midnight. He manages to corner the reaper when he prepares to take the little girl's
life. Meanwhile, \Gls{WPoons} notices the trolleys proceed to the next stage of their life-cycle,
by generating thousands of flyers containing news of a discount sale.

\subsubsection{\Gls{WPoons} and the non-humans investigate the trolley heap}
The non-human denizens of the city, including \Gls{WPoons} hear the twisted music emanating from
outside the city. \Gls{Ludm} believes that it is meant to attract humans in the way that a pied
piper attracts rats, and that their inhumanity enables them to see through the illusion. They
travel to the heap of trolleys, and head inside what appears to be a prototype mall.

\subsubsection{\Gls{WPoons} and his party rescue \Gls{Shoe} from some soldier trolleys}
\Gls{WPoons} realizes that the trolleys are like worker bees and that the structure is like a
beehive. They encounter some soldier trolleys fighting \Gls{Shoe} and rescue him. \Gls{Ludm}
comments on the possibility of a queen trolley hidden somewhere inside the mall, as \Gls{WPoons}
tries to work out their next move.

\subsubsection{\Gls{BillD} deals with the new grim reaper with the help of \Gls{Flitw}}
\Gls{BillD} is dismayed to find his scythe absent in the spiritual realm when he visits \Gls{NSim}'s
workshop. He manages to outrun the new grim reaper and heads to \Gls{Flitw}'s cottage, hoping to
find some spectral weapon to put up a fight. \Gls{Flitw} gives \Gls{BillD} some of her own time,
and helps him banish the new grim reaper. He then detects more robed figures converging on the
cottage, possibly more minor angels.

\subsubsection{\Gls{WPoons} and his party find the wizards in the mall}
\Gls{WPoons} and his party are forced deeper underground, where they find the inner council of
wizards in a state of catatonia. \Gls{AWink} is thrown up to the ceiling in bat form, and manages
to bring down a suspicious looking black disc, thus stopping the music and freeing the wizards
from their trance. \Gls{Doreen} notices the trolleys milling about aimlessly, and realizes that the
queen's hold on them is broken.

\subsubsection{\Gls{BillD}'s sabotage of the combine harvester saves his life}
\Gls{WPoons} works out that the queen trolley is built into the very walls and floor of the hive,
as pink tubes emerge from the floor to trap his feet. Meanwhile, the new grim reaper tries to
kill \Gls{BillD} by possessing the combine harvester and charging \Gls{Flitw}'s cottage. The
machine falls to pieces, as a result of \Gls{BillD} sabotaging it out of jealousy at its performance
earlier in the day.

\subsubsection{\Gls{Ridcu} decides to re-enter the mall and rescue \Gls{WPoons}}
\Gls{Ridcu} learns that \Gls{WPoons} is still trapped inside the mall holding off the queen trolley,
and decides to go back in with a squad to rescue him. \Gls{Shoe}, the \Gls{Dean} and the \Gls{Libra}
volunteer to go with him, as the others have their wounds bandaged by \Gls{Ludm}. Meanwhile,
\Gls{BillD} threatens the minor angels when they warn him about \Gls{Azrael}, and summons all the
other reapers to achieve his former power. The \Gls{DRat} manages to evade the summons, and retain
its independent existence.

\subsubsection{\Gls{Dean} and his party rescue \Gls{WPoons} with help from \Gls{Schl}}
The \Gls{Dean} primes several destructive spells on a timer, as \Gls{Shoe} recovers \Gls{WPoons}
using a trolley. \Gls{Schl} shows up to help them out when the queen jams a corridor leading out
of the mall, and reveals his true form after throwing away his portable door. The group makes it
out of the mall, and it implodes into nothingness when the effects of the \Gls{Dean}'s spells get
superimposed.

\subsubsection{\Gls{WPoons} decides to end his undeath, now that souls are being harvested again}
At the University, \Gls{WPoons} is glad to have saved the rest of the city, and declares his intent
to seek release from his undeath. He sets out into the city, to meet one last person, after
persuading \Gls{Cake} to take in \Gls{Lupi} as a pet. \Gls{Doreen} stops \Gls{Shoe} from blurting
out \Gls{Lupi}'s secret, and keeps the charade of \Gls{Ludm}'s abnormality going.

\subsubsection{\Gls{Death} decides to thank \Gls{Flitw} for saving his life}
\Gls{Death} goes to the end of the Universe, where \Gls{Azrael}, the master of all reapers, watches
over Time. Over the protests of the minor angels, \Gls{Death} asks for some Time so that he might
give a final gift to someone, and \Gls{Azrael} grants his request. He comes to \Gls{Flitw}'s house
with some flowers, chocolates, and a diamong stolen from the Temple to Offler. She reminds him that
the harvest dance is due to happen soon, and is shocked to see her unused wedding dress studded with
diamonds.

\subsubsection{\Gls{Death} helps \Gls{Flitw} achieve a happy afterlife}
\Gls{Death} helps the spirit of \Gls{Flitw} dance through the harvest festival, and then takes her
through time to the death of her lover in an avalanche. He gives her the final gift of going to the
same afterlife as her long-lost love. He returns to his realm, and decides not to reabsorb the
\Gls{DRat}, to let it have its own existence.