\section{The Science of Discworld}


\subsection{}
\subsubsection{\Gls{Stibb} tries to explain the value of his new machine to the faculty of Unseen
    University}
\Gls{Stibb} addresses the faculty gathered in the Unseen University courtyard for the demonstration
of his expensive new project. He leads with the potential use of extracting useful energy at low
cost by splitting the thaum, the fundamental unit of narrative causality on the Disc. \Gls{Ridcu}
manages to zero in on the question of a chain reaction and \Gls{Stibb} is forced to admit that
that there is a small chance his machine will blow up the entire Disc.

\subsubsection{\Gls{Ridcu} works out the fact that \Gls{Stibb} already knows the engine will work}
The council leaves for lunch after \Gls{Ridcu} ceremonially flips the lever to start the heat
exchanger that is meant to turn magical energy into heat for the university's boilers. \Gls{Ridcu}
correctly guesses that \Gls{Stibb} had a test run earlier, and reminds him that if the machine did
not end the universe the first time it was switched on, it must be safe enough for extended use.

\subsubsection{\Gls{Stibb} finds his machine working too well}
\Gls{Ridcu} wakes up the next day to find \Gls{Stibb}' machine producing too much energy, and
fights his way to the High Energy Magic building to find out if it can be shut down. \Gls{Stibb}
suggests that an abrupt shutdown might cause some sort of catastrophic implosion, just as \Gls{Hex}
puts forward the suggestion of the Roundworld simulation.

\subsubsection{The \Gls{Dean} triggers the Big Bang of the Roundworld}
\Gls{Stibb} explains to \Gls{Ridcu} that the Roundworld is meant to be a toy world free from the
rules of magic, and was rejected earlier for being too magic-intensive to sustain. The \Gls{Dean}
sticks his finger into the transparent sphere that is now absorbing all the excess magic, and
inadvertently triggers the Big Bang within Roundworld. \Gls{Stibb} gets him to withdraw his hand
just in time for the pocket universe to start forming, as the rest of the council leave for dinner.

\subsubsection{\Gls{Stibb} listens to the faculty argue in favour of further meddling in the
    Roundworld}
\Gls{Stibb} struggles to explain to the faculty that they should not interfere in the Roundworld
anymore, as the \Gls{Dean} tries to gloat about his inadvertent triggering of the Big Bang.
\Gls{Ridcu} observes the Roundworld and fails to identify any magical elements within it that were
so essential to life originating on the Disc.

\subsubsection{\Gls{Stibb} and the faculty observe the formation of pure elements in the Roundworld
    gas clouds}
\Gls{Ridcu} observes the formation of stars and supernovae, and the \Gls{Dean} identifies the first
specks of heavy elements start to form in Roundworld space. \Gls{Ridcu} speculates that the
Roundworld elements look similar to those on the Disc, because the simulation is trying to imitate
the Disc, without any magic to help it along.

\subsubsection{The \Gls{Wrangler} plays some games with students}
The \Gls{Wrangler} is appalled to see the High Energy Magic building filled with students, who
are busy playing games at night instead of observing the Roundworld project. He decides to join
them, finding it too noisy to get any sleep on his own.

\subsubsection{\Gls{Stibb} tries to work out the nature of gravitational attraction}
\Gls{Stibb} carries out some rudimentary experiments with gravitational attraction within the
Roundworld, and realizes that the heavier objects must also be attracted by lighter ones. He then
spots the \Gls{Wrangler} busy playing with the students, and proceeds to investigate.

\subsubsection{\Gls{Stibb} and the faculty observe the first supernovae in Roundworld}
\Gls{Stibb} tries to explain to the faculty that they cannot freely change the rules governing
Roundworld, just as a student runs in with news of elemental gold being spotted in the Roundworld.
\Gls{Stibb} realizes that the Roundworld has mass accreting to form stars, which then explode after
a while, scattering heavy metals into space.

\subsubsection{\Gls{Stibb} demonstrates a planet with water, which quickly freezes in the absence
    of a star}
\Gls{Stibb} shows off a world he designed with liquid water and precipitation, only be dismayed when
the proto-planet freezes over after a few hours. \Gls{Ridcu} decides to have \Gls{Stibb} escorted
to his bedroom to catch up on sleep, and sets to work making a star that might warm up the frozen
planet.

\subsubsection{\Gls{Stibb} asks \Gls{Hex} to find him a volunteer for the trip into Roundworld}
\Gls{Stibb} goes to the Roundworld project the next day, to find the rest of the faculty bombarding
his planet with suns. \Gls{Ridcu} considers it unacceptable that starts cannot be as small as the
one revolving around the Disc, as the planet is made to rotate around its own axis. \Gls{Stibb} asks
\Gls{Hex} if someone can be convinced to enter the Roundworld and report back from the planet's
surface.

\subsubsection{\Gls{Rince} is forced to volunteer for the expedition into Roundworld}
\Gls{Rince} is dragged by the faculty to the High Energy Magic Building, where \Gls{Stibb} explains
that \Gls{Hex} is planning a spell that will make him appear on the Roundworld surface, where he
can witness the conditions first-hand. \Gls{Rince} runs off for a hearty meal, and is emboldened
by the idea of his actual body remaining safe in the University while he spirit-walks in Roundworld.

\subsubsection{\Gls{Stibb} sets \Gls{Rince} off into Roundworld, using the spacesuit designed by
    \Gls{Hex}}
\Gls{Stibb} is amused to see \Gls{Ridcu} talk about the old Omnian teachings that talk about a
spherical world revolving around a central star that gives it heat and light. \Gls{Rince} gets into
the enchanted spacesuit to prepare for his spirit-walk, as \Gls{Ridcu} starts wondering about the
possible emergence of life within Roundworld. \Gls{Stibb} dismisses the idea, convinced that simple
rules governing physics cannot possibly lead to anything as complex as life.

\subsubsection{\Gls{Rince} watches a solar eclipse using the newly installed moon}
\Gls{Rince} arrives at a time of incessant rain in Roundworld, and is repositioned by \Gls{Stibb}
to be close to a landmass. \Gls{Stibb} installs a moon around the Roundworld planet, and \Gls{Rince}
observes the first solar eclipse in the cloudy sky. The tides are then set up by the simple
interaction between the planet's oceans and the moon's attractive force as it revolves around the
planet.

\subsubsection{\Gls{Stibb} struggles to explain the speed limit set by light in Roundworld}
\Gls{Stibb} points out the printouts from \Gls{Hex} that talk about a speed limit in Roundworld,
which is met only by its light. The \Gls{Bursar} absent-mindedly reads the special relativity texts
being printed by \Gls{Hex}, as \Gls{Ridcu} is exasperated by stories of twins aging at different
speeds.

\subsubsection{\Gls{Rince} witnesses the primordial soup of life on the Roundworld planet}
\Gls{Stibb} tells the faculty that they cannot insert life into the Roundworld planet, and suggests
some manipulation of the weather instead. \Gls{Hex} detects life on the Roundworld, even though
\Gls{Rince} cannot see any life-forms at the beach where his apparition is standing. \Gls{Ridcu}
is confused by the output of \Gls{Hex}, as \Gls{Rince} is shrunk down to microscopic size to
investigate some volcanic vents where primordial life begins to form.

\subsection{}
\subsubsection{\Gls{Ridcu} and the faculty obsess over the book on evolution retrieved by the
    \Gls{Libra}}
The \Gls{Libra} accidentally portals into the office of Charles Darwin, while he is busy writing his
book on natural selection. He retreats quickly upon realizing his error, and opts to return with
the first book on evolution that he can get his hands on. Meanwhile, \Gls{Ridcu} recalls their
meeting with the \Gls{EGod}, and believes that evolution can only refine a species, not cause it to
change into something else.

\subsubsection{\Gls{Stibb} and the faculty watch an Ice Age envelop the planet}
\Gls{Rince} is sped through time until he spots some primitive life-forms resembling jellyfish
on the shore. He asks \Gls{Stibb} to take him away, and is fast-forwarded to an Ice Age. The next
day, \Gls{Stibb} returns to the simulation to find the Ice Age ended, and an explosion of
biodiversity in the oceans, including primitive plants that float along with the ocean currents.

\subsubsection{\Gls{Rince} gets struck by a world-ending comet on his latest expedition}
\Gls{Rince} is dragged to the High Energy Magic building when the \Gls{Lugg} is spotted looking
for him in the Roundworld planet. He proposes using its magical storage to smuggle objects back
to the Disc, as \Gls{Ridcu} starts to berate him for his inability to summon it at will. \Gls{Rince}
gets stuck by a comet just as he is investigating some intelligent crabs that have moved onto the
shores from the sea.

\subsubsection{Simple amphibians evolve on the Roundworld planet}
\Gls{Rince} helps a small fish back into the sea when he spots it wriggling along the beach, and
is surprised to find it persist in its attempt to reach an inland pool of freshwater. \Gls{Ridcu}
tries to reconcile members of his council by proposing some ambhibious newts as the standard-bearers
of life on the Roundworld planet, after the latest mass extinction.

\subsubsection{\Gls{Hex} moves the wizards into the age of dinosaurs}
\Gls{Hex} manages to send the entire faculty onto the Roundworld planet using its spirit-walking
spells, and they arrive just in time for another meteorite impacting the open ocean. \Gls{Rince}
warns them of the coming tidal wave, and predicts that another period of volcanic activity will
be triggered by the impact. \Gls{Rince} runs away from the dinosaurs when \Gls{Stibb} fast-forwards
them a few thousand years into the future.

\subsubsection{\Gls{Stibb} and the faculty watch another meteorite wipe out intelligent reptiles}
\Gls{Stibb} reports on the finding of intelligent animals as the faculty observe lizards dominating
the planet for many millions of years, with no pressure on them from the environment whatsoever.
The \Gls{Dean} notices yet another comet coming down on the planet, threatening to wipe out some
budding tribes of tool-making lizards. \Gls{Stibb} suggests ending their spirit-walk so that they
can avoid the simulated pain from the meteorite landing.

\subsubsection{\Gls{Stibb} tries to cheer up the wizards after they see the latest apocalypse}
\Gls{Stibb} tells the despondent faculty that some animals have survived the latest mass extinction,
including mammals that are choosing to return to the seas. The \Gls{Dean} inadvertently gives some 
primitive apes the idea of tool use when he tries to teach them language, before being summoned 
by \Gls{Ridcu}.

\subsubsection{The \Gls{Libra} injects some technology into the tribes of primitive ape-men}
The \Gls{Libra} decides to take matters into his own hands, and enters the Roundworld with 
\Gls{Rince}'s collection of crude flint tools, to help the primitive apes survive against hostile 
predators trying to wipe them out. The \Gls{Libra} helps the ape-men defeat some big cats, and 
teaches them how to make fire, hoping desperately to stop the Roundworld project from being shut 
down.

\subsubsection{The wizards completely miss the evolution of intelligent human life}
\Gls{Rince} and the wizards return to the planet, to find it covered by ice, with an artificial 
intelligence telling \Gls{Hex} that the humans have abandoned the planet long ago. \Gls{Rince} 
realizes that something intelligent enough to escape the hostile planet finally managed to evolve 
without being squashed by the regular catastrophic events, as \Gls{Ridcu} tries to make sense of 
the advanced technology in one of the abandoned colony domes.

\subsubsection{\Gls{Stibb} confirms the shutdown of his magic reactor}
\Gls{Stibb} finds the \Gls{Bursar} inside the magic reactor room, seemingly unaffected by it as 
it gradually winds down to safe levels of magic output. The rest of the faculty satisfy themselves 
with the state of the reactor, and leave the \Gls{Bursar} to his ramblings about astrophysics. 
\Gls{Rince} conveniently forgets to mention the \Gls{Libra}'s meddling with the primitive apes.

\subsubsection{\Gls{Rince} takes the Roundworld away to his office for safekeeping}
\Gls{Rince} is tasked with keeping the Roundworld safe in his office, and notices the \Gls{Bursar} 
teleporting randomly across the University as he cradles the snow-globe in his arms. Inside his 
office, he argues with the \Gls{Libra} about which species might have made it off the planet, just 
as a smaller Discworld flies past the observation platform within the Roundworld universe.