\section{Snuff}


\subsection{}
\subsubsection{\Gls{Vimes} prepares to go on holiday with his family}
\Gls{Vetina} reads a tome on goblin culture, and their fractious relationship with humanity, as
\Gls{Drumk} walks in to remind him of \Gls{Vetina}'s departure. \Gls{Vimes} learns that
\Gls{Haddock} is settling in well as Acting Captain at Quirm, as \Gls{Carrot} arrives with his
letter of vacation signed by the Patrician. \Gls{Vimes} is loath to leave his office even for a day,
but is forced to listen to \Gls{Ramkin}, when she says a visit to the countryside would be good for
\Gls{SamJ}

\subsubsection{\Gls{Vetina} is happy to see \Gls{Vimes} leave without surrendering his badge}
On the carriage to the countryside, \Gls{Vimes} dreads the visit to \Gls{Ramkin}'s estate, called
Ramkin Hall. Meanwhile, \Gls{Vetina} is amused to see that the sealed envelope that was supposed to
contain \Gls{Vimes}' badge is a decoy, and bemoans the new smuggling problem spreading among the
aristocrats in the city.

\subsubsection{\Gls{Vimes} meets the chiefs of staff at Ramkin Hall}
\Gls{Vimes} sees his coach pass through the formal gates to Ramkin Hall, and then across a bridge
on the river Quire. \Gls{Ramkin} informs him that they are now close to Quirm, as they reach the
manor, and notice the staff lining up to receive them. The butler \Gls{Silver} introduces himself,
and points out his wife, who is the head of housekeeping. \Gls{Vimes} detects a note of annoyance
in his greeting, when he asks if they would visit the estate more freqeuntly in the future.

\subsubsection{\Gls{Vimes} learns about the expected levels of skimming at the estate}
\Gls{Willi} tells \Gls{Vimes} in the smoking room that the staff are nicking a percentage of the
estate's budget, but insists that it is within reasonable limits. \Gls{Vimes} believes he is
being eavesdropped on, and chooses not to berate the staff for thieving, and wonders why
\Gls{Ramkin} insisted on keeping the estate, even though she would never use it for years on end.

\subsubsection{\Gls{Vimes} is curious to see the servants refuse to face him}
The next morning, \Gls{Vimes} is annoyed to be woken up by the sounds of animals and birds
screaming in the fields, and learns that the local aristocracy all want them to attend their balls.
\Gls{Vimes} is curious to see the maids all turn their backs to him when he passes by them, and
learns from \Gls{Willi} that this is an old custom that is best left unchallenged.

\subsubsection{\Gls{Ramkin} talks about the origin of the maids refusing to face male guests}
\Gls{Ramkin} explains to \Gls{Vimes} that her grandmother had instituted the rule about housemaids
not looking at or talking to male guests, so that they might avoid risking their chastity during
the many galas held at the estate. \Gls{Vimes} decides not to pursue his egalitarian agenda any
further, and accepts the reality that the countryside would not progress as fast as the city.

\subsubsection{\Gls{Vimes} meets the hermit of Ramkin Hall}
\Gls{Vimes} takes \Gls{SamJ} out for a walk with \Gls{Willi} guiding them, and runs into the
estate hermit, who is in search of his great-grandfather's skull. \Gls{Vimes} learns that every
aristocrat maintained a hermit on their estate as an elaborate lawn ornament, and provided for their
food and shelter in exchange for the aesthetics of a wise sage ready to dispense advice.

\subsubsection{\Gls{Vimes} tries and fails to convince \Gls{Ramkin} to hurry back to the city}
\Gls{Willi} talks about the various members of the Ramkin dynasty who made valuable contributions
to science and engineering, as if to counter \Gls{Vimes}' opinion that all aristocrats were
worthless snobs. Later in the day, \Gls{Ramkin} insists that \Gls{SamJ} should spend more time in
the country, learning about all the land and resources that he will one day inherit.

\subsubsection{\Gls{Ramkin} shows her ancestors to \Gls{SamJ} at the family crypt}
\Gls{Ramkin} decides to take \Gls{SamJ} to the family crypt, for a tour of their ancestors, and
decides to stroll through the country on his own. \Gls{Ramkin} tries to get him to take \Gls{Willi}
along for guidance, but relents when \Gls{Vimes} reminds her that he did fine in the much more
dangerous streets of Ankh-Morpork.

\subsubsection{\Gls{Vimes} meets some denizens of the nearby village}
\Gls{Vimes} eventually makes it to the pub at a nearby village, and asks for something
non-alcoholic. The bartender \Gls{Jiminy} gives him some beet juice, and notices the workmen come
in at the end of their day. The blacksmith \Gls{Jethro} frowns at \Gls{Vimes}, annoyed at the
respect he has to be given just because of his title as Duke. \Gls{Vimes} meanwhile, works out that
\Gls{Jiminy} is a former cop, and that the \Gls{Jethro} is a progressive man stuck in a rural
community.

\subsubsection{\Gls{Vimes} sees \Gls{LRust} at the tavern}
\Gls{Vimes} sees some people starting a game of cricket, and is forced to listen to an enthusiast
explaining the rules. Eventually, he manages to get away when he finds \Gls{LRust}, now confined to
a wheelchair in his old age. \Gls{LRust} asks him if he has come to the countryside on official
business, leading \Gls{Vimes} to suspect that something was being covered up.

\subsubsection{\Gls{Vimes} and \Gls{Ramkin} meet one of her old friends}
\Gls{Vimes} returns to the manor to read a new book to \Gls{SamJ}, and is surprised to learn that
the famous author \Gls{Beedle} has retired to a cottage nearby. \Gls{Ramkin} insists on inviting her
to the manor, and \Gls{Vimes} agrees reluctantly. The next day, \Gls{Ramkin} takes \Gls{Vimes} along
to meet one of her friends, whose daughters are all convinced that the only way ahead for them is to
wait for a relative to die, and marry a gentleman using the inheritance as their dowry.

\subsubsection{\Gls{Vimes} offers some advice to some young ladies hoping for a dowry}
\Gls{Vimes} gives the daughters a spiel about self-respect, and the idea of finding a job that would
give them the power to make their own decisions in life. On the ride back, \Gls{Ramkin} tells him
that she is proud of his speech, and that their mother was very satisfied with him taking the
initiative to knock some sense into the daughters.

\subsubsection{\Gls{Vimes} decides to take up \Gls{Jethro}'s offer of a fistfight}
\Gls{Vimes} is met by \Gls{Jethro} at the tavern, after \Gls{Jiminy} stonewalls his attempts to
learn about any wrongdoing in the countryside. After \Gls{Willi} shows up with a crossbow to
intimidate \Gls{Jethro}, \Gls{Vimes} makes him write up a signed agreement detailing their
fistfight, as the villagers rush to the bar to witness an aristocrat fight a commoner.

\subsubsection{\Gls{Vimes} manages to convince \Gls{Jethro} to reveal the crime being covered up}
\Gls{Vimes} realizes that \Gls{Jethro} is simply coming to terms with wealth inequality, and decides
to go easy on him, ending the fistfight in an apparent draw. He then distracts the audience with a
free round of drinks at the bar, and tells \Gls{Jethro} about his humble beginnings as a poor kid on
the streets of Ankh-Morpork. \Gls{Jethro} is finally persuaded to show \Gls{Vimes} what crime is
being allowed to continue in the countryside, and fixes a meetup at midnight.

\subsubsection{\Gls{Vimes} and \Gls{Ramkin} entertain some guests for dinner}
\Gls{Vimes} asks \Gls{Willi} to go set up at the meeting place before the appointed time, wary that
\Gls{Jethro} might be planning an ambush. He returns home in time for \Gls{SamJ} to read one of his
children's books to him, and prepares to attend the formal dinner later. At the dinner table,
he learns from a retired colonel that there are swamp dragons being bred in the countryside, before
he is abruptly silenced by his wife.

\subsubsection{\Gls{Vimes} finds a goblin's corpse at \Gls{Jethro}'s meetup location}
\Gls{Vimes} figures out that the author \Gls{Beedle} is aware of the crimes being covered up, but
is not part of the wealthy in-group. He also realizes that \Gls{Makepea} is being held back by his
wife from revealing more about the wrong-doings in the countryside. After the party, he heads to the
meetup, and finds a goblin's bloody hand there, with no sign of \Gls{Jethro} whatsoever.

\subsubsection{\Gls{Vimes} tries to track down \Gls{Jethro}, after he finds a severed goblin hand}
\Gls{Vimes} goes to \Gls{Jiminy}'s pub and tries to ask about the goblin murder being covered up.
\Gls{Jiminy} states that he has no intention of poking his nose into affairs that might threaten
his peaceful retirement, and points \Gls{Vimes} in the direction of \Gls{Jethro}'s house, before
shutting the door to the tavern. At night, \Gls{Vimes} is interrupted by the sound of wagons in the
distance rolling over cobblestones, and realizes that a smuggling operation of some sort is in
place.

\subsection{}
\subsubsection{\Gls{Vimes} is surprised to learn that he is under arrest}
\Gls{Vimes} tries to fend off \Gls{Ramkin}'s questions about snooping around local matters, by
telling her that he would hand over the case to the village policeman. He is surprised to see a
young man enter the manor, and introduce himself as Chief Constable \Gls{Upshot}, with intentions to
arrest him and present him to the local court. \Gls{Vimes} overpowers him, before \Gls{Ramkin}
arrives, and tells the two of them that are to attend another formal dinner later.

\subsubsection{\Gls{Upshot} tells \Gls{Vimes} about the charges against him}
\Gls{Upshot} tells \Gls{Vimes} that he is under suspicion for the murder of \Gls{Jethro}, and asks
him to come to the jail, so that he might be presented to the magistrates later. \Gls{Vimes}
agrees, and asks \Gls{Upshot} to come along with him, convinced that he might be next in line for
whoever was tying up loose ends like \Gls{Jethro}.

\subsubsection{\Gls{Upshot} talks about the lessons he learned from his forefathers}
At the jail, \Gls{Upshot} chooses not to tell his mother that he has arrested \Gls{Vimes}, and
tells him in private that his policeman instincts do not signal any criminal intent coming from
\Gls{Vimes}. \Gls{Vimes} is impressed by the lessons imparted to \Gls{Upshot} by his ancestors, who
had all been village sheriffs, as a goblin is thrown into the jail cell.

\subsubsection{\Gls{Vimes} helps \Gls{Upshot} dig for the truth, at \Gls{Stinky}'s insistence}
\Gls{Vimes} decides to take the goblin's cries for justice seriously, and learns that its name is
\Gls{Stinky}. He tells \Gls{Upshot}'s mother that he has some important errands to run with her
son, and leaves the jail cell. Meanwhile, \Gls{Makepea} overhears the bench of magistrates,
headed by his wife, talk about \Gls{Vimes} and his marriage to \Gls{Ramkin}.

\subsubsection{\Gls{Makepea} confronts his wife about the illegal smuggling operation headed by
    \Gls{GRust}}
\Gls{Makepea} learns that \Gls{LRust}'s young son \Gls{GRust} has charmed the magistrates into
framing \Gls{Vimes}, to try and rob him of his rank. He tells the gathered magistrates that the
affair with the goblin children was a vile crime, that they allowed \Gls{GRust} to get away with,
in blatant violation of their duty to the law.

\subsubsection{\Gls{Upshot} and \Gls{Vimes} follow the goblins}
\Gls{Stinky} takes \Gls{Vimes} and \Gls{Upshot} to the same hilltop that \Gls{Jethro} had asked to
meet at, and asks him to provide justice. \Gls{Vimes} tells \Gls{Upshot} that the scuffle with
\Gls{Jethro} at the bar did happen, and realizes that someone probably overheard \Gls{Jethro} asking
to meet at the hill. He insists that the blacksmith has simply gone missing, and chooses to follow
the goblins further into the woods.

\subsubsection{\Gls{Colon} and \Gls{Nobby} check in on \Gls{Gumption}'s tobacco business}
\Gls{Colon} and \Gls{Nobby} visit the newly famous tobacco shop of \Gls{Gumption}, asking about the
effect of the new tobacco taxes on his business. He pretends to be vexed by the increased burden on
his profits, even as \Gls{Colon} notices how posh his clothing and accessories seem to be.
\Gls{Gumption} is eager to have the cops leave, and gives them new cigars fresh from the plantation.
\Gls{Colon} drops the cigar in surprise when he puts it up to his ears, and hears a strange noise.

\subsubsection{\Gls{Vimes} and \Gls{Upshot} travel deeper into the goblin cave system}
In the goblin cave, \Gls{Vimes} feels the scar of the \Gls{SDark} glow on his arm, and realizes that
it has left him with enhanced night vision. \Gls{Upshot} struggles to keep up through the dark
tunnel, as \Gls{Vimes} pushes on, noticing the miscellaneous rubbish gathered as loot by the
goblins. He eventually finds all the goblins assembled in a deep cavern, clutching their crude
flint weapons.

\subsubsection{\Gls{Nobby} and \Gls{Colon} return to the Watch House to investigate the cigar}
\Gls{Vimes} introduces himself to the goblins, and hears them scream for justice, before parting
to reveal the corpse of a fellow goblin. Meanwhile, \Gls{Nobby} drags \Gls{Colon} into \Gls{Igor}'s
hospital in the Watch House, and asks \Gls{Igor} to dismantle the fat cigar gifted by
\Gls{Gumption}. \Gls{CheeryL} recognizes the delicate little pot inside the cigar, and tells
\Gls{Colon} that they are rumoured to contain the soul of a baby goblin.

\subsubsection{\Gls{Vimes} investigates the corpse of the female goblin}
The goblin chieftain tells \Gls{Vimes} that the female goblin's corpse was tossed into the cave a
few days ago, having been drained of all blood, and with a cut in the stomach. \Gls{Vimes} lights
some torches to help \Gls{Upshot} see in the dark, and asks the goblin chief if he can check the
rest of the cave network for signs of \Gls{Jethro}.

\subsubsection{\Gls{Vimes} learns about the circumstances of the female goblin's death}
The goblin chieftain tells \Gls{Vimes} that \Gls{Jethro} would often trade food for iron deposits
in the caves, and tells him that the \Gls{SDark} within him gives him complete access to the caves,
with no objection from the goblins. When \Gls{Upshot} asks him later how he is able to communicate
with the goblins, \Gls{Vimes} refuses to reveal the remnant of the \Gls{SDark} within him, magically
helping him overcome the language barrier.

\subsubsection{\Gls{Vimes} and \Gls{Upshot} run into \Gls{Beedle} inside the goblin caves}
Further inside the goblin caves, \Gls{Vimes} finds a makeshift forge, and believes that this was
where \Gls{Jethro} mined the iron ore. He is surprised to find \Gls{Beedle} teaching some young
goblins, and learns that her star pupil \Gls{TearsM} is taking well to human language. She decides
to lead \Gls{Vimes} out of the caves, and reminds him to ask \Gls{Upshot} about the great goblin
slaughter from three years ago.

\subsubsection{\Gls{Upshot} talks to \Gls{Vimes} about the goblins being enslaved}
\Gls{Upshot} tells \Gls{Vimes} about the slave camps that the goblins had been forced into three
years ago, and of how the magistrates had justified it by calling them vermin to be cleansed.
He then tells \Gls{Vimes} that his father, who was Constable at the time, had lost his nerve after
the incident, and died soon after. \Gls{Vimes} realizes that he is the owner of the lands, and no
one had ever informed him about these happenings.

\subsubsection{\Gls{Vimes} narrates the day's events to \Gls{Ramkin}}
\Gls{Vimes} tells \Gls{Ramkin} about the goblin enslavement, as he returns to the manor, late for
the formal dinner. \Gls{Ramkin} asks him to find \Gls{SamJ} and \Gls{Willi} in the backyard, and
reminds him not to be too harsh in his investigation, potentially upsetting her aristocrat friends
in the countryside.

\subsubsection{\Gls{Willi} tells \Gls{Vimes} about how quickly gossip gets around at the manor}
\Gls{Willi} tells \Gls{Vimes} that news of his movements throughout the day had reached him through
servants coming and going at the manor, and that Dead Man's Copse was visible from the manor
through a telescope. He warns \Gls{Vimes} that \Gls{SamJ} would need guidance in choosing a career
path soon, and suggests enrolling him at Unseen University.

\subsubsection{\Gls{Vimes} asks \Gls{Ramkin} about \Gls{GRust}'s activities in the countryside}
That night, \Gls{Vimes} learns that \Gls{GRust} had purchased a manor in the countryside ten years
ago, against the advice of his father \Gls{LRust}. He decides to wake up the next day and take
\Gls{SamJ} to meet \Gls{Beedle}, hoping to allay any suspicion that he was interrogating her about
the goblin enslavement from three years ago.

\subsection{}
\subsubsection{\Gls{Beedle} tells \Gls{Vimes} about her mother's childhood among goblins}
\Gls{Beedle} welcomes \Gls{Vimes} into her cottage, and wows \Gls{SamJ} with a preprint copy of her
new book about earwax. \Gls{Vimes} then sees \Gls{SamJ} greet \Gls{TearsM} with his usual spiel
about poop, oblivious to any scary stories about goblins that are fed to all human children.
\Gls{Beedle} takes \Gls{Vimes} aside and tells him the story of her mother, who was raised by
goblins before eventually being emancipated by humans, who slaughtered all of her goblin friends in
the process.

\subsubsection{\Gls{Vimes} asks \Gls{Beedle} to let him use her tunnel to the goblin caves}
\Gls{Vimes} baits \Gls{Beedle} into revealing the presence of a tunnel leading to the goblin
hideout from her cottage, and asks her if she knows where \Gls{Jethro} might have gone. He wishes to
use the secret tunnel to enter the goblin caves again, to snoop around for clues. Meanwhile,
\Gls{CheeryL} returns from \Gls{Colon}'s home bearing news about his illness, to report to
\Gls{Carrot}, who is Acting Commander.

\subsubsection{\Gls{Pessimal} talks about troublesome goblin customs}
\Gls{Pessimal} speaks up about the stories regarding goblin mothers eating their newborns in times
of great famine, and believes that goblin religion does not consider this an act of murder.
\Gls{CheeryL} states that the small goblin pot is stuck to \Gls{Colon}'s hands, and that he has
begun to speak in a strange language. \Gls{Pessimal} states that there is no one at the University
with any knowledge of goblin culture, but points out that \Gls{HarryK} outside the city might be
of help.

\subsubsection{\Gls{Vimes} and \Gls{SamJ} travel to the goblin caves}
\Gls{Vimes} walks through the tunnel with \Gls{SamJ}, and eventually reaches the goblin caves,
where \Gls{Beedle} is unpacking sacks of fruits and vegetables. The other goblin girls are awed
by \Gls{TearsM}'s fancy apron, and take turns trying it on. \Gls{Beedle} explains to \Gls{Vimes}
that the goblins were cursed with deficient diets, and that she had managed to get the young females
to slip in some vegetables in the name of healing magic.

\subsubsection{\Gls{Vimes} decides to use one of the goblin pots to search for the missing one}
\Gls{Vimes} learns that one of the three pots on the dead female goblin was missing, and asks
\Gls{Beedle} if the goblins had tried searching for it. He asks to borrow one of the goblin's pots,
so that he might show the villagers what he was searching for, and is surprised to learn that
\Gls{TearsM} expects something valuable from him as collateral. He takes out the picture of
\Gls{SamJ} from his wallet, and is pleased to see that \Gls{TearsM} is satisfied with the offer.

\subsubsection{\Gls{Vimes} gets some leads by intimidating \Gls{Jiminy}}
\Gls{Vimes} persuades \Gls{Jiminy} into revealing what he knows about the goblin pot in, when he
accosts him in the cellar under the tavern. \Gls{Jiminy} talks about seeing a similar box with
a local ruffian named \Gls{Strat}. He then reveals that \Gls{Strat}'s henchman \Gls{TedF} is a
servant of \Gls{LRust}, with \Gls{Vimes} convinced that these were all genuine leads in his
investigation.

\subsubsection{\Gls{Vimes} gets \Gls{Ramkin} to hear the music played by \Gls{TearsM}}
\Gls{Vimes} talks to \Gls{Beedle} about the new leads, after returning \Gls{TearsM}'s pot, and
is awed by the music she plays on the harp in \Gls{Beedle}'s cottage. He rushes back home to get
\Gls{Ramkin} to come along and hear the music, and is surprised to see her agree. \Gls{Ramkin} is
moved by the music, and asks \Gls{Vimes} to immediately start tracking down the new leads, while
expressing her disgust for the local bench of judges.

\subsubsection{\Gls{Vimes} takes \Gls{Upshot} along to arrest \Gls{TedF}}
\Gls{Vimes} decides to get \Gls{Upshot} to join him on the ride to the nearby village, to
interrogate the new suspects. \Gls{Upshot} informs him that \Gls{Stoner}, the clerk working for the
magistrates, had visited him earlier, and reminded him not to look any further into the matter of
the dead goblin.

\subsubsection{\Gls{TedF} is cornered by \Gls{Vimes} and \Gls{Upshot}}
\Gls{TedF} runs out the back door when \Gls{Upshot} announces himself, asking to talk to him.
\Gls{Vimes} trips him up, and reminds him that his part in the tobacco smuggling operation might be
overlooked if he tells them everything about the murder of the female goblin. \Gls{TedF}, eager to
get himself out of any charges to abet murder, tells on \Gls{Strat}.

\subsubsection{\Gls{Vimes} gets \Gls{TedF} to squeal on \Gls{Strat}}
With \Gls{Willi} keeping watch at the front door, \Gls{Vimes} uses a testimony provided by the
\Gls{SDark} to describe the events of the night \Gls{TedF} accompanied \Gls{Strat} to Dead Man's
Copse, and gets him to turn state's witness. \Gls{Vimes} finds a barrel of tobacco in \Gls{TedF}'s
cellar, and is intrigued when \Gls{Upshot} says that it might be used to conceal the smuggling of
something even more valuable.

\subsubsection{\Gls{Vimes} sees the troll narcotics hidden inside the contraband tobacco}
\Gls{Vimes} gets some villagers to empty the tobacco barrel, and finds several packets of troll
narcotics at the bottom. He identifies the drugs as illegal substances, lethally addictive to
most trolls, and takes samples on board his carriage. The rest of the contraband is burned by the
villagers, with \Gls{Vimes} reassuring them that \Gls{Shine} will has a bounty on the destruction of
any such contraband, sure to enrich their simple lives.

\subsubsection{\Gls{Vimes} leaves \Gls{TedF} in the custody of \Gls{Upshot}}
\Gls{Vimes} realizes that \Gls{TedF} is unaware of the troll narcotics being hidden inside the
tobacco, and asks him if he has overheard \Gls{Strat} ever talk about who gives him his orders.
\Gls{TedF}, eager to improve his chances in the trial, tells \Gls{Vimes} that some mention was made
of \Gls{GRust} being the secret patron who kept \Gls{Strat}'s pockets filled. \Gls{Vimes} leaves
\Gls{TedF} in \Gls{Upshot}'s jail cell, and proceeds to go to the manor to get some sleep.

\subsubsection{\Gls{HarryK} receives \Gls{Angua} and \Gls{Carrot} at his house}
\Gls{HarryK}, now sporting the title of Sir, welcomes \Gls{Carrot} and \Gls{Angua} into his
house outside the city walls of Ankh-Morpork, from which he runs a garbage cleaning and sanitizing
business. \Gls{Vetina} is happy to have the city cleaner and smelling better, in exchange for the
slightly illegal business practices in \Gls{HarryK}'s establishment.

\subsubsection{\Gls{BSlick}'s grandma offers advice for \Gls{Colon}'s predicament}
\Gls{BSlick} tells \Gls{Carrot} to bring a bottle of liquor, to induce his aging grandmother into
revealing what she knows about the folklore surrounding goblin pots. \Gls{BSlick}'s grandma tells
\Gls{Carrot} that only a goblin maiden who wishes to have children can wrest the pot from
\Gls{Colon}'s hands, and asks him to come back with more liquor and tobacco in exchange for her
services as a healer.

\subsubsection{\Gls{WMArthur} volunteers to travel to Howondaland to investigate the goblins}
\Gls{Gumption} tells \Gls{CheeryL} that the batch of cigars from which he gifted one to \Gls{Colon}
was procured from Howondaland, where new plantations had been established in the recent years.
\Gls{CheeryL} reports back to \Gls{Carrot}, and is surprised to see \Gls{WMArthur} confident that
he can make the journey there in two days, using one of the migratory birds native to the city.

\subsection{}
\subsubsection{\Gls{Stoner} tells \Gls{Vimes} that he is under arrest}
\Gls{Vimes} thinks in his sleep about his reliance on the \Gls{SDark}, and wonders what would
happen to his credibility if any of its information turned out to be false. He is woken up by
\Gls{SamJ}, who announces that a strange man is waiting for him in the lounge. The man
introduces himself as \Gls{Stoner}, and tells him that he is under arrest for investigating the
goblin murder.

\subsubsection{\Gls{Vimes} watches \Gls{Upshot} deal with a mob trying to kill his prisoner}
\Gls{Vimes} rejects the power of the magistrates, and marches to \Gls{Upshot}'s cottage, and finds
him angry at a mob that attempts to corner his mother. \Gls{Vimes} notices \Gls{Stoner} watching
the fracas from a nearby bush, as \Gls{Willi} stops the mob from running away. \Gls{Upshot}
baits the villagers into taking his authority seriously, and appoints \Gls{Stinky} as a Special
Constable under his command.

\subsubsection{\Gls{Vimes} traps \Gls{Stoner} by claiming he is a valuable informant}
\Gls{Vimes} realizes that \Gls{Stoner} is unlikely to rat out his masters, and makes a show of
thanking him for valuable information, in full view of the assembled mob. He then tells \Gls{Stoner}
that the people believe he has squealed, and that the only safe option left to him is to run to
\Gls{Slant} in the Lawyers' Guild, and beg for a job in the city.

\subsubsection{\Gls{WMArthur} liberates the goblins in the Howondaland work camp}
\Gls{WMArthur}, who has just found out that he is originally a violent subspecies of gnome, as his
bird lands next to some tobacco plantations on Howondaland. He takes out the careless guards
minding the goblins, and takes note of the huge pile of goblin corpses in a corner of the field.
\Gls{TedF} talks about the latest shipment of goblins being taken downriver by \Gls{Strat}, and
reminds \Gls{Vimes} that their progress will be very slow.

\subsubsection{\Gls{Vimes} congratulates \Gls{Willi} on breaking up the mob}
\Gls{Vimes} works out the fact that it was \Gls{Willi} who fired a crossbow bolt in the direction
of \Gls{Upshot}'s mother, triggering his tirade, and ensuring that the hired mob was too scared to
remain interested in its job. He leaves \Gls{TedF} in the care of \Gls{Willi}, who is to guard him
in a locked room at the manor, and sets off with \Gls{Upshot} in pursuit of the barge carrying the
latest shipment of goblins.

\subsubsection{\Gls{Vimes} and \Gls{Upshot} chase after the barge}
\Gls{Vimes} uses the help of \Gls{Stinky} to calm his horse down, and keep up with \Gls{Upshot},
as he gallops along the riverbank to find the barge. He is surprised when \Gls{Upshot} still
considers him a natural rider, and tries desperately not to let his fear of horses shine through.
By sunset, a thunderstorm picks up and starts to gently swell the river, with \Gls{Upshot} talking
about the possibility of a flood.

\subsubsection{\Gls{Upshot} and \Gls{Vimes} follow \Gls{Stinky} onto the barge}
\Gls{Upshot} is alarmed to see the barge sailing down the river in spite of the rough waters, as
\Gls{Vimes} tries to work how the pilot must have been threatened by \Gls{Strat}. The three of them
manage to jump onto the rearmost barge, and make it slowly to the second vessel in the train, just
behind the ox-powered boat taking them downriver. Through the deafening thunderstorm, \Gls{Vimes}
manages to find a chicken farmer seemingly held hostage.

\subsubsection{\Gls{Vimes} helps \Gls{Stinky} free the goblins being trafficked}
The chicken farmer calls himself \Gls{PSFalse}, and swears not to know anything about the goblin
trafficking operation, as \Gls{Vimes} tries to jump onto the next barge. Once on it, he finds
goblins tied up below deck, with a large store of food for them, meant to last several weeks.
\Gls{Stinky} sets about freeing them, as \Gls{Upshot} finds a water trough to help them regain their
strength. \Gls{Vimes} and \Gls{Upshot} take some hammers from \Gls{PSFalse}'s toolbox and prepare
to confront the pilots.

\subsubsection{\Gls{Vimes} learns about the boarders from \Gls{Sillit}'s wife}
\Gls{Vimes} manages to overpower a goon tasked with holding a crossbow aimed at a woman holding a
baby, and learns that he is just hired muscle. The man calls himself \Gls{EddieB}, and promises to
remain silent, as the woman, who introduces herself as \Gls{Sillit}'s wife, tells him about the
impending flood.

\subsubsection{\Gls{TGCharlie} gives a crossbow to \Gls{Vimes}}
\Gls{TGCharlie} greets \Gls{Vimes} in the ox-mill powering the boat, and tells him that at least
two of the four pirates are dead. \Gls{Vimes} retrieves the crossbow from the pirate lying dead next
to him, and heads to the wheelhouse, to confront \Gls{Strat}. At the cabin, he overpowerse a young
man and ties him up, as \Gls{EddieB} reveals himself to be \Gls{Strat}, with the crossbow held to
\Gls{Vimes}'s head.

\subsubsection{\Gls{Vimes} helps \Gls{Sillit} with navigation in the dark}
\Gls{Vimes} tells \Gls{Strat} that he had already sabotaged the crossbow's mechanism, just as
the preliminary flood water rocks the boat, sending him out of the wheelhouse, and possibly into
the wild river. \Gls{Vimes} then finds the captain, \Gls{Sillit}, and uses his night-vision to
help him navigate the stormy waters.

\subsubsection{\Gls{Vimes} helps the goblins come on board the ship, and unties the barges}
\Gls{Vimes} manages to overpower \Gls{TGCharlie} when he objects to bringing the goblins on board,
and asks \Gls{Upshot} to order \Gls{Stinky} and the others to come in. He then disengages the
link to the cargo barges, letting the ship outrun the flooding river, just as \Gls{Strat} jumps into
the wheelhouse to try and kill him.

\subsubsection{\Gls{Vimes} and the others reach Quirm before the flood}
\Gls{Strat} kills \Gls{Stinky} when he stops him from choking \Gls{Vimes} to death, and is stunned
in the process. \Gls{Vimes} ties him up, swearing to see that he hangs for his crimes, as
\Gls{Sillit} announces that Quirm is close by. A while later, he wakes up next to the ship on the
Quirm Dockyard, and is relieved to learn that everyone on it is fine.

\subsubsection{\Gls{Vimes} learns about \Gls{Colon}'s curse}
\Gls{Vimes} is alarmed to learn that the goblins are on a ship that was waiting to take them
somewhere else, and asks for a swift boat to pursue it. He is informed by \Gls{Haddock} that
\Gls{WMArthur} is at the Quirm police headquarters, with news from his expedition to Howondaland.
He asks for \Gls{Colon} to be taken to \Gls{Ramkin}, so that he can find a goblin cave to get rid
of his curse.

\subsubsection{\Gls{Vimes} manages to flip \Gls{Murder}, by threatening his smuggling operation}
\Gls{Vimes} is alarmed to see \Gls{Jethro} on the deck of the ship carrying the goblins, once the
Quirm police boat catches up to it. The Captain of the ship, a famed smuggler named \Gls{Murder},
is persuaded to turn state's witness, and give up the names of whoever made him kidnap \Gls{Jethro},
and take him to Howondaland. \Gls{Murder}'s ship is forced to return to Quirm, where the goblins
are led out of the docks by \Gls{Stinky}.

\subsubsection{\Gls{Vimes} and \Gls{Upshot} return to Ramkin Hall}
\Gls{Vimes} and \Gls{Upshot} board a ship sailing upriver to Ramkin Hall, confident that \Gls{Strat}
will try and sneak onboard to get even. The next morning, \Gls{Vimes} finds \Gls{Nobby} waiting
for him at the riverside port, and asks about \Gls{Colon}. \Gls{Nobby} tells him that \Gls{Colon} is
still on his way, and that a new semaphore tower has been installed next to the manor.

\subsubsection{\Gls{Vimes} is welcomed home by \Gls{Ramkin}}
\Gls{Vimes} returns home to find \Gls{Ramkin} overjoyed at his heroism, claiming that he is free to
have his beloved bacon sandwich for dinner. He asks her if \Gls{Vetina} had originally suggested
going to Ramkin Hall for their vacation, and is dismayed to see that she does not remember. He later
goes to the temporary semaphore tower to find \Gls{Nobby} in the company of a female goblin.

\subsubsection{\Gls{Vimes} learns that \Gls{Colon} has been cured of his goblin curse}
\Gls{Vimes} is amused to see the young goblin look adoringly at \Gls{Nobby}, as he learns that
\Gls{Colon} has been freed from his curse, when the pot was taken off his hands by her. He then
looks up to see \Gls{Stinky} manning the semaphore tower, having learned in a few hours how to use
the cipher and keyboard.

\subsection{}
\subsubsection{\Gls{Vimes} returns to the manor after meeting \Gls{Colon}}
\Gls{Vimes} meets \Gls{Colon}, who seems to be at home among the goblins, enjoying their foraged
mushrooms, and roasted rabbit. He invites \Gls{CheeryL} and \Gls{Colon} to stay on at Ramkin Hall
for as long as they like, given the threat imminent from \Gls{Strat}. Back at the manor,
\Gls{Ramkin} informs \Gls{Vimes} that \Gls{LRust}'s wife had come over to try and talk to her while
he was away.

\subsubsection{\Gls{Vimes} receives some favourable news from Quirm}
\Gls{Vimes} tries to raise alarm about \Gls{Nobby} entering a relationship with the young goblin,
but is told off by \Gls{Ramkin}. He then receives a message at the semaphore tower, talking about
the testimony extracted by the police in Quirm, implicating \Gls{GRust}. At \Gls{Upshot}'s cottage,
he finds \Gls{Jethro}, now a Special Constable, and sees the fire in him, waiting to hold the
aristocracy to account.

\subsubsection{\Gls{Vimes} travels to Quirm with his family, on a luxury cruise ship}
\Gls{Vimes} tries to make the villagers at the pub see the power in collective action, when they
express disgust at the goblin pogroms from three years ago. He gives them free drinks for the
evening, and heads to the manor, to prepare for the family trip down to Quirm. On board the ship,
the captain celebrates his heroism, and puts on an elaborate show for the passengers.

\subsubsection{\Gls{Strat} gets captured by \Gls{Vimes}, when he attempts to kill \Gls{SamJ}}
\Gls{Strat}, who had signed onto the cruise ship as the barman, sedates everyone at the celebration
with his new cocktail, and sneaks into \Gls{SamJ}'s room at night. \Gls{Vimes} incapacitates him,
having anticipated his plan, and tells him that he is probably going to hang, unless his testimony
against \Gls{GRust} pleases \Gls{Vetina} greatly.

\subsubsection{\Gls{Ramkin} prepares the audience for \Gls{TearsM}'s performance on the harp}
\Gls{Ramkin} writes letters to all of her aristocratic acquaintances as \Gls{Vimes} takes \Gls{SamJ}
sightseeing around Quirm. Dignitaries from the troll, dwarf and vampire kingdoms of Uberwald
converge at the Opera House in Ankh-Morpork, for some important event, to be attended by all of the
political bigwigs of the city.

\subsubsection{\Gls{Willi} kills \Gls{Strat} after he manages to break out of his prisoner
    transport}
\Gls{Vimes} gathers the villagers in front of the pub, to await the trial of the self-appointed
board of magistrates, who had let the goblin atrocities go by unquestioned. Meanwhile, the police
escorting \Gls{Strat} from Quirm to Ankh-Morpork crash into a wagon, and the prisoner escapes in
the confusion. \Gls{Willi} corners him a while later, and kills him, to spare \Gls{Vimes} the
trouble of thinking about the possibility of revenge.

\subsubsection{\Gls{Vimes} is annoyed to learn that \Gls{GRust} will not hang for his crimes}
\Gls{Vimes} is angered to learn that \Gls{GRust} will only be exiled to XXXX, since his crimes
against goblins happened before they were elevated to the status of the other sapient races.
\Gls{Vetina} congratulates him on the plan to have \Gls{TearsM} play her music for the ambassadors,
causing the laws about goblins to be amended overnight across all their kingdoms.