\section{Soul Music}


\subsection{}
\subsubsection{\Gls{Susan} deals with \Gls{Butts} trying to chastise her}
Ms. \Gls{Butts}, the headmistress at the elite Quirm School for Young Women, faces the little girl
\Gls{Susan}, having just broken the news of her family having met with an accident. She struggles
to deal with \Gls{Susan}'s powers of antimemetics and small-scale clairvoyance. Meanwhile, \Gls{Imp}
thinks back to his father, who had disparaged his ideas off setting forth from Llamedos to fulfil
his musical dreams.

\subsubsection{\Gls{Death} is lost in thought about \Gls{Flitw}'s death}
An interdimensional shop selling musical instruments manifests in Ankh-Morpork the moment \Gls{Imp}
makes his vow. He hitches a ride to the Circle Sea, and decides to head into Ankh-Morpork, in spite
of common sense dictating that he go to Quirm instead. Meanwhile, \Gls{Albert} notices \Gls{Death} lost in a trance, thinking about the
death of \Gls{Flitw}, and of how she had cursed the aging process.

\subsubsection{\Gls{Susan} tries to fit into school life}
\Gls{Susan} thinks about the warnings given by \Gls{Butts} about the dangers of going into the
nearby town, as she wanders through the school. She continues to ignore classes, and read books on
logic to her heart's content. \Gls{Butts} attempts to catch her, but is reminded of the antimemetic
field.

\subsubsection{\Gls{Death} seeks out an ascetic to learn about the mysteries of human existence}
\Gls{Albert} rants absent-mindedly about \Gls{Death}'s recent decisions, as \Gls{DRat} watches on.
Meanwhile, \Gls{Death} tries to learn from a renowned ascetic about the human ability to forget, and
how important it is in dealing with the misery of life. \Gls{Death} dismisses \Gls{Binky},
dissatisfied with the ascetic's answers, and sets off to find some closure regarding \Gls{Flitw}.

\subsubsection{\Gls{Nobby} and \Gls{Colon} run into \Gls{Imp}}
\Gls{Nobby} and \Gls{Colon} encounter \Gls{Imp} in one of the squares of Ankh-Morpork, and warn
him that the Guild of Musicians will not allow him to operate without a license. \Gls{Imp}, being
a law-abiding citizen of Llamedos, sets out to the Guild House to seek his fortune. \Gls{Colon}
almost spots the interdimensional shop in Ankh-Morpork, before \Gls{Nobby} convinces him that it
has been there for many years now.

\subsubsection{\Gls{Clete} tells \Gls{Imp} and the musicians about the high cost of Guild
    membership}
At the waiting room of the Musicians' Guild, \Gls{Imp} runs into the troll \Gls{LiasB} and the
dwarf \Gls{GlodG}, who also claim to be artists seeking a license. \Gls{LiasB} shows \Gls{Imp} his
set of drum-rocks, as \Gls{GlodG} talks about his prowess with wind instruments. The Guild secretary
Mr. \Gls{Clete} outlines the exorbitant fees for new registrations, and laughs at \Gls{Imp}'s
suggestion that they earn the money by playing some music for a week.

\subsubsection{\Gls{LiasB} breaks \Gls{Imp}'s harp}
As the three musicians spend the last of their money getting a meal at \Gls{Gimlet}'s shop,
\Gls{LiasB} accidentally sits on \Gls{Imp}'s antique harp and breaks it. \Gls{GlodG} suggests they
go the interdimensional music shop, deceived by the illusion that it has always been there, and
tries to get \Gls{Imp}'s spirits up about buying a new instrument.

\subsubsection{\Gls{LiasB} pays for the new instruments with one of his diamond teeth}
\Gls{LiasB} knocks one of his teeth out to pay the music shop owner, when \Gls{GlodG} finds a
guitar with magical reverb for \Gls{Imp}. They go to \Gls{GlodG}'s home to practice, and \Gls{GlodG}
is annoyed at the limited range of sounds that \Gls{LiasB} is able to make by smashing his rocks
together. Meanwhile, \Gls{Susan} sees the \Gls{DRat} sneak up to her in class, and try to attract
her attention

\subsubsection{\Gls{Susan} decides not to take the \Gls{DRat} seriously}
The \Gls{DRat} wakes \Gls{Susan} up in the middle of the night, and gets her to jump out of the
dormitory into the gardens. A raven, acting as its interpreter, tells her that her grandfather
has vanished again, and that she has to accompany the \Gls{Death} to its realm. She considers the
strange events a bad dream, and returns to her bed, just as the raven \Gls{Quoth} is about to reveal
the identity of her grandfather.

\subsubsection{\Gls{Susan} rides \Gls{Binky} and accidentally makes it fly}
\Gls{Susan} decides to take a stroll through the city during sports period, and is accompanied by
\Gls{PJade}, the daughter of a troll king, along with \Gls{Gloria}, the daughter of a high-ranking
dwarf. As they reach the stables, \Gls{Susan} sees \Gls{Binky} being groomed by the some staff,
and takes him for a ride. \Gls{Binky} floats in the air for a moment too long, and the others
dismiss the magic in front of their eyes, to \Gls{Susan}'s amusement.

\subsubsection{\Gls{Susan} meets \Gls{Quoth} in his master's house at night}
\Gls{GlodG} announces to the other musicians that he has found a gig in the Mended Drum. Meanwhile,
\Gls{Susan} runs into a tooth fairy at work as she seeks out the local wizard's house in Quirm City. \Gls{Quoth} lets her into the house, and
tells her that \Gls{Binky} is supposed to take her on an adventure. \Gls{Susan} still struggles to
believe that magical beings are real, and has faint recollections of riding \Gls{Binky} as a child
in a garden of black roses.

\subsubsection{\Gls{Binky} takes \Gls{Susan} to \Gls{Death}'s House}
\Gls{Binky} takes \Gls{Susan} to \Gls{Death} favourite curry house in Ankh-Morpork, where the
owner hastily throws a bag of takeaway when he spots the horse glowing white in the night.
\Gls{Susan} finds the food unpalatable, and throws it away after a single bite. \Gls{Binky} then
takes her to \Gls{Death}'s House, where she wanders through the rooms, marveling at the impossible
geometry inside single hall.

\subsubsection{\Gls{Susan} recalls her early childhood when \Gls{Albert} triggers her memories}
\Gls{Susan} eventually runs into \Gls{Albert} in the kitchen, as he mops up the last of his dinner.
He explains to her that \Gls{Death} is her grandfather, and that she has inherited his role with
his sudden disappearance from his job as the grim reaper. \Gls{Susan} remembers her early visits to
\Gls{Death}'s House many years ago, before her parents had decided to raise her using modern logical
methods, and to forgo her magical heritage.

\subsection{}
\subsubsection{\Gls{Albert} worries for \Gls{Susan}'s mind when she has carry out the duties of
    \Gls{Death}}
After getting \Gls{Susan} to bed, \Gls{Albert} spends the night musing on the idea that she is
being forced to fill in for \Gls{Death}, and wonders how her mind will cope with the full extent
of \Gls{Death}'s memories. A while later, \Gls{Susan} wakes up, and remains unconvinced that she is
supposed to step in as the new reaper of souls.

\subsubsection{\Gls{Imp} and his band play their first gig in the Mended Drum}
\Gls{HDun}, the new owner of the Mended Drum, sets up a stage for band night, in an effort to
revitalize the old tavern's reputation. As \Gls{Imp}'s band start their first song, the meager
audience take to throwing fruit and stones in a few minutes. Meanwhile, \Gls{Susan} manages to
ride into the gates of Ankh-Morpork, past \Gls{Nobby} and \Gls{Colon}, who mistake her for the
real \Gls{Death}.

\subsubsection{\Gls{Susan} starts her first night of harvesting souls}
The \Gls{DRat} guides \Gls{Susan} to her first reaping, at the home of a wealthy old merchant in
Ankh-Morpork. She severs the link to his body once he dies, and is amused to see him complain about
his sons. \Gls{Quoth} arrives to hitch a ride on \Gls{Binky}, as the \Gls{DRat} hands \Gls{Susan}
the next hourglass bearing the name of some hublander.

\subsubsection{\Gls{Susan} notices \Gls{Imp} show up in her list of souls to reap}
\Gls{Susan} sees some hubland tribes fight a small battle, and watches in awe as valkyries swoop
down from the sky to carry off their souls to the afterlife. She reaps the particular soul pointed
out by the \Gls{DRat}, and notices that the third hourglass has the label \Gls{Imp} on it. She
believes that the name is significant, as the memories of \Gls{Death} bleed into her own mind.

\subsubsection{\Gls{Death} enlists in the Klatchian Foreign Legion}
\Gls{Death} signs up in the Klatchian Foreign Legion, at a fortress on the border between Klatch
and Hersheba. The officer who enlists him, struggles to see through the antimemetic effect, and
hastily assigns \Gls{Death} a new name and uniform. Meanwhile, \Gls{Susan} interrupts a drunk dwarf
at the Mended Drum, before he can throw the axe that kills \Gls{Imp}.

\subsubsection{\Gls{Susan} stops \Gls{Imp} from being killed during his debut at the Mended Drum}
The \Gls{DRat} notices \Gls{Imp}'s hourglass run out of sand, even as the band starts to play new
music, inspired by the \Gls{Imp}'s magical guitar. \Gls{Susan} realizes she has screwed with
reality, as the people in the tavern demand one encore after another. A while later, the \Gls{Libra}
returns from the Mended Drum to the University, and sets to work recreating the music he just heard
using the grand pipe organ.

\subsubsection{\Gls{Imp} and \Gls{LiasB} come up with fake names for themselves}
After the show, \Gls{Imp} is alarmed to see his guitar create music by itself, as they indulge in
a well-earned dinner at \Gls{Gimlet}'s restaurant. \Gls{LiasB} decides to use the stage name
\Gls{Cliff}, and \Gls{Imp} follows suit, by coming up with the name \Gls{Buddy}. \Gls{GlodG}
suggests the need for a piano in their ensemble, and points out a new model at the opera house that
they might borrow for a few days.

\subsubsection{\Gls{Susan} thinks about the mysterious force that saved \Gls{Imp}'s life}
\Gls{Ridcu} and the senior wizards are woken up by the \Gls{Libra}'s commotion, with some of them
enjoying the new music, even as \Gls{Ridcu} fires a crossbow at the overloaded organ pipes, causing
an explosion. Meanwhile, \Gls{Susan} tries to make sense of the magical guitar that had suddenly
saved \Gls{Imp}'s life by making new music, and watches the strange blue smoke swirling in the top
chamber of his hourglass.

\subsubsection{\Gls{Cliff} and \Gls{Buddy} steal the modern piano from the opera house}
\Gls{Cliff} and \Gls{Buddy} manage to sneak the piano out of the opera house and past \Gls{Detri},
who is on night watch duty. \Gls{GlodG} is shocked to see \Gls{Cliff} break a hole in his wall, to
get the piano into his house. He thinks about finding someone to play the piano, and wonders if
the \Gls{Libra} could be convinced to take on the job.

\subsubsection{\Gls{Susan} hides the debacle at the Mended Drum from \Gls{Albert}}
\Gls{Susan} returns to \Gls{Death}'s House, and chooses not to tell \Gls{Albert} about her screwup
with \Gls{Imp}, hoping to be taken more seriously. Meanwhile, \Gls{Ridcu} and the wizards have
breakfast the next day, as the University's roof is getting fixed, and notice the that the
\Gls{Libra} has gone missing.

\subsubsection{\Gls{Ridcu} finds out about the \Gls{Libra}'s secret project}
\Gls{Ridcu} is annoyed to hear the \Gls{Dean} practicing guitar riffs early in the morning, as
a merchant arrives demanding his wheels back. \Gls{Ridcu} realizes that the \Gls{Libra} stole those
wheels, and gives the merchant some money as compensation. He hears loud noises of tinkering coming
from the basement, and works out that the \Gls{Libra} is busy building something in his workshop.

\subsubsection{\Gls{Ridcu} believes that the new music is akin to an infectious disease of the mind}
\Gls{Ridcu} then finds \Gls{Runes} in a trance, pretending to play the drums, and shakes him back to
his senses. He realizes that music is taking over the minds of many of his council members, and
seems to be another supernatural threat leaking into the Discworld from some foreign universe. He
reluctantly agrees to go to the Mended Drum with the rest of his council, to investigate the
threat of the captivating music.

\subsubsection{\Gls{GlodG} gets the \Gls{Libra} to join the band}
\Gls{Death} evades his duties as a member of the Klatchian Foreign Legion, by getting his superiors
to ignore his existence. Meanwhile, \Gls{Susan} picks out a modern outfit for herself, and tries to
visit \Gls{Death}, using her memories as a guide. \Gls{GlodG} asks the \Gls{Libra} if he would like
to join the band as the piano player, and is happy to see him agree.

\subsubsection{\Gls{Susan} asks \Gls{Death} about \Gls{Imp}'s hourglass}
\Gls{Susan} decides to travel back in time to \Gls{Death}'s confrontation with \Gls{Mort}. She
arrives in the Hall of Hourglasses just after he banishes \Gls{Mort} and \Gls{Ysabell} to Sto
Helit, after noticing his granddaughter in the shadows. She asks \Gls{Death} what is keeping
\Gls{Imp} alive, and learns that Music has taken over his life, as evidenced by the blue mist fog
in his hourglass.

\subsubsection{\Gls{Death} tries to persuade \Gls{Susan} to see the Duty his way}
\Gls{Death} reminds \Gls{Susan} about his policy of non-interference in the lives of the Disc, and
is alarmed to see her disagree. Meanwhile, \Gls{Buddy} and his band of four make it to the Mended
Drum, taking note of the people crowding the bar. \Gls{Ridcu} and the wizards get prime seats close
to the stage, as the band gets ready for their performance.

\subsubsection{\Gls{Ridcu} assembles with his council for to hear the new music at the Mended Drum}
\Gls{Ridcu} notices \Gls{SLemon} sitting on the next table, with some enforcers from the Musicians'
Guild ready to shake down the band after hours. He also sees \Gls{Susan} with \Gls{Quoth} on her
shoulder sitting far off, and is alarmed when her antimemetic field makes her vanish occasionally.
He dismisses her as one of the Tooth Fairy girls on a night off, as the music starts playing.

\subsubsection{\Gls{Ridcu} watches \Gls{Susan} take down \Gls{SLemon} and his enforcers}
\Gls{Ridcu} is transfixed by the music after a while, as it stops being mere noise and manages to
penetrate his brain. He notices \Gls{Susan} knock out \Gls{SLemon} and his two underlings when they
get up to confront the unlicensed band, and realizes that the music is alive.

\subsubsection{\Gls{Death}'s experiments with trying to forget his memories fail once again}
\Gls{Death} asks to be subjected to more torture, when two days buried up to his neck in the hot
desert sand does not have any effect on his memories. He asks his superior officer if such torture
helps humans forget the past, just as the enemy forces attack from across national borders.

\subsection{}
\subsubsection{\Gls{Vetina} hears about the riot at the Mended Drum, caused by \Gls{Imp}'s music}
\Gls{Vetina} receives news from one of the beggars who acts as an informant, and matches the
eyewitness account to the written report of the riot at the Mended Drum. He dismisses the beggar,
and wonders what kind of paranormal threat the city has to face, given how the wizards at the bar
were dancing along. Meanwhile, \Gls{Susan} wonders if the strange music is a parasite keeping
\Gls{Imp} alive, somehow fending off death itself.

\subsubsection{\Gls{Ridcu} bails out his council after the concert at the Mended Drum}
\Gls{Ridcu} is appalled by his council entering a frenzy at the Mended Drum, making it necessary
for the City Watch to come arrest them. The \Gls{Dean} is hypnotized by the music, and reminded of
the youth he missed out on as a wizard. Meanwhile, \Gls{Imp} and the band are dismayed to see the
bill presented by \Gls{HDun} for the broken furniture.

\subsubsection{\Gls{Dibbl} manages to get a position as the band's manager}
\Gls{Dibbl} walks into the back room of the Mended Drum, sensing the gold-mine that is the band. He
offers to be their manager, and proposes to talk to \Gls{HDun} about the payment for their latest
gig. \Gls{Clete} asks some more thugs from his guild to track down \Gls{Imp} and his band.
Meanwhile, \Gls{GlodG} is happy to sign \Gls{Dibbl}'s contract along with the rest of the band, and
remains optimistic about bigger venues and audiences.

\subsubsection{\Gls{Ridcu} goes to \Gls{Stibb} to try and understand the strange music}
\Gls{Ridcu} goes to the High Energy Magic building, where \Gls{Stibb} and his students have been
busy working on splitting the thaum. He bemoans the state of his faculty, all busy learning to
play musical instruments, and stitching leather jackets. \Gls{Ridcu} produces a sealed mug filled
with music from the Mended Drum, and \Gls{Stibb} is amazed to see it remain detectable so many hours
later.

\subsubsection{\Gls{Susan} sees the music keeping \Gls{Imp}'s biography going past its end}
\Gls{Susan} goes to the hall of biographies in \Gls{Death}'s House, and takes a look at \Gls{Imp}'s
tome. She notices his life story end at the Mended Drum, and the rest of the pages filling up with
music. She is determined to meddle in the affairs of the Disc to make it a better place, and
is repulsed by \Gls{Death}'s policy of strict non-interference.

\subsubsection{\Gls{Blert} is overwhelmed by the demand for his guitars}
\Gls{Blert}, maker of artisanal guitars, watches one customer after another come in, asking for
guitars that sound like \Gls{Buddy}'s. He hesitantly hands them his acoustic guitars, before
realizing that they will never be able to tell the difference. He clears out his entire stock of
guitars, and asks his apprentice to buy some black paint and decorative trinkets to make the next
batch look more attractive.

\subsubsection{\Gls{Stibb} talks about the origin of the universe to \Gls{Ridcu}}
\Gls{Stibb} tries to outline the theory of creation advocated by the Listening Monks, which involves
a complex sound starting the big bang. \Gls{Whitlow} walks in with breakfast, and \Gls{Ridcu} is
alarmed to see the new hair and clothing on her. \Gls{Stibb} muses that the music must be highly
contagious, to have hypnotized someone like Mrs. \Gls{Whitlow}.

\subsubsection{\Gls{Dibbl} talks to \Gls{Imp}'s band about their next gig}
Inspired to form bands of their own by the effects of the new music, \Gls{Crash} and \Gls{Jimbo}
plan out their new troupe in the horse-shed owned by \Gls{Crash}'s father. Meanwhile, \Gls{Dibbl}
produces new band shirts for \Gls{Imp}'s band, for use as merchandise. He promises them a better
venue for the coming night, and tells them that he has negotiated a higher pay than the going
Guild rates.

\subsubsection{\Gls{Dibbl} tells the band that they are to play in a tavern owned by \Gls{Chry}}
Some dwarven lyricists for the Musician's Guild are overcome by the urge to write new lines to go
with the new music. Meanwhile, \Gls{Dibbl} tells the band that they are to play in the Cavern, a
gambling den run by \Gls{Chry} and his troll mafia. \Gls{GlodG} is convinced that he will pay with
his life for entering a troll tavern, and refuses to go.

\subsubsection{\Gls{Dibbl} gets an assistant for the band}
\Gls{Dibbl} introduces a short troll named \Gls{Asphalt}, who is to help the band with hauling their
equipment. He claims to have been an elephant trainer in a circus, until the elephants sat on him
so often that he had to quit. Meanwhile, \Gls{Stibb} is able to isolate the string reverberating
with the new music and seal it in a box. \Gls{Ridcu} decides to seek out the \Gls{Dean} when he
then asks for more samples to study.

\subsubsection{\Gls{Chry} talks about hiring another band to open for \Gls{Buddy}'s group}
As \Gls{Chry} arrives to reassure \Gls{Buddy} and his band about the crowds they will pull,
\Gls{Asphalt} brings some food for them to eat before the show. \Gls{Dibbl} tells them that
\Gls{Chry} has hired another band to open the night, playing similar music to rile up the crowd.
A while later, \Gls{Crash} and his band discover that the guitars peddled by \Gls{Blert} are
falling apart, and decide to set aside their worries before going out on stage.

\subsubsection{\Gls{Buddy} demands the next show be free to attend}
\Gls{Buddy} is disgusted by the idea of people having to pay to create and to listen to music.
Before they start their performance, he asks \Gls{Dibbl} to arrange a show that is free to attend,
and \Gls{Dibbl} immediately visualizes the profits in concessions and merchandise to be made from
the huge audiences.

\subsubsection{\Gls{Susan} arrives at the Cavern to see \Gls{Buddy} play}
As the show gets underway, \Gls{Dibbl} is surprised to find \Gls{Binky} standing next to him
outside the venue. \Gls{Susan} walks in through the security at the gate using her antimemetic
field, and is surprised to find a wizard accosting her. \Gls{Ridcu}, who is able to notice her
in the crowd by concentrating very hard, asks her who she is. She tells him that she is the new
grim reaper, and melts into the crowd.

\subsubsection{\Gls{Dibbl} asks the band to play an encore after they finish their set}
After a few hours playing, the band takes a break, with \Gls{GlodG} and \Gls{Cliff} horrified by
the music they produced involuntarily on stage. \Gls{Buddy} is happy to hear \Gls{Dibbl}'s idea of
a tour taking them through the cities nearby, and asks \Gls{GlodG} if he can give up the fame coming
to him as a member of the band. They are called back for an encore, with \Gls{Dibbl} reluctantly
agreeing to pay them a bonus.

\subsubsection{\Gls{Susan} interferes in the death of \Gls{Buddy} once again}
\Gls{Susan} spooks some enforcers from the Musicians' Guild, who wait at the back entrance of the
cellar to kill \Gls{Buddy} and his band. \Gls{Dibbl} picks up one of the knives dropped by the thugs
as they run away, and hides it from the band. He tells them to focus on the tour, and to rest up at
a luxury hotel, to prepare for the free concert coming up.

\subsubsection{\Gls{Ridcu} drags \Gls{Stibb} back to the University}
\Gls{Stibb} accidentally reveals his string-in-a-box contraption to \Gls{Dibbl}, who is captivated
by the idea of selling the music trapped in a box. \Gls{Ridcu} ushers \Gls{Stibb} away, and finds
the rest of his council in a nearby cafe, drowning in coffee. He orders them back to the University
to face disciplinary action, before realizing that they are the committee in charge of handing out
the punishments.

\subsubsection{\Gls{Vetina} learns about the free concert planned by \Gls{Dibbl}}
After the show, \Gls{FORon} narrates the events of the night to \Gls{Vetina} in his office, and
pulls out a poster announcing the free concert next week. \Gls{Vetina} is intrigued by the possible
reaction of the Musicians' Guild to the poster, and asks for \Gls{Clete} to be brought to him.
Meanwhile, \Gls{Ridcu} drags \Gls{Stibb} to the High Energy Magic building, and asks for the
students to be assembled for a ritual to summon \Gls{Susan}.

\subsubsection{\Gls{Cliff} and \Gls{GlodG} visit the strange music shop}
After \Gls{Buddy} falls asleep, \Gls{GlodG} and \Gls{Cliff} discuss the hold that the magic guitar
has on him, and believe that it is capable of understanding their conversation. They travel to the
music shop next to Unseen University, and notice serial numbers etched on every single instrument
inside. The woman managing the shop claims that the guitar sold to \Gls{Imp} had always been there
in her shelves, when \Gls{GlodG} points out the number one etched on it.

\subsection{}
\subsubsection{\Gls{Susan} tries to warn \Gls{Buddy} in person}
\Gls{GlodG} purchases a gong and drumstick from the lady in the music shop, and pays promptly when
\Gls{Cliff} warns him against bargaining. Meanwhile, \Gls{Susan} sneaks into \Gls{Buddy}'s room,
to try and warn him about the guitar. He dismisses her as an imaginary occult woman, and tells her
that the others in the band had also warned him about the music controlling his life.

\subsubsection{\Gls{Susan} answers \Gls{Ridcu}'s summoning ritual}
\Gls{GlodG} and \Gls{Cliff} search the town for a workshop where they can examine the newly
purchased instruments. Meanwhile, \Gls{Susan} has been summoned by \Gls{Ridcu}'s ritual, performed
with the help of the students. \Gls{Susan} is pleased to be taken seriously by senior wizards, and
claims that the new music is alien to the Disc. \Gls{Ridcu} is smug when his suspicions are
confirmed, just as the students question why she does not resemble \Gls{Death}.

\subsubsection{\Gls{Susan} works out how the new music chooses its hosts}
\Gls{Death} returns from Klatch for another drinking binge at the Mended Drum. Meanwhile,
\Gls{Ridcu} offers \Gls{Susan} some food, and is annoyed to see a change in the University menu.
\Gls{Susan} works out how the music chose \Gls{Imp}, and thanks \Gls{Ridcu} for the helpful advice.
After \Gls{Susan} vanishes, \Gls{Ridcu} wanders into the \Gls{Dean}'s suite, and finds him busy
hammering some rivets into thick leather trousers.

\subsubsection{\Gls{Death} gets dumped into the Ankh river after he gets blackout drunk}
\Gls{Death} manages to remember how to get drunk midway through his lecture about the inevitability
of life in the Mended Drum, and blacks out mid-sentence. He is thrown into the Ankh river when the
denizens find nothing to loot in his robes. Meanwhile, \Gls{Susan} is busy in \Gls{Death}'s House
trying to work out how the music spreads.

\subsubsection{\Gls{Dibbl} tries to enlist more bands for the Free Concert}
\Gls{Dibbl} signs up more gullible groups looking to make it big as musicians, in the hopes of
filling out the Free Concert. Meanwhile, \Gls{Asphalt} takes \Gls{Imp} and his group to Pseudopolis,
for the first stop on their tour. \Gls{Death} joins some Beggars along the shores of the Ankh
river enjoying a late-night drink. He realizes that they exist at the periphery of society, and
will include him with no questions asked.

\subsubsection{\Gls{Clete} decides to take drastic measures to eliminate \Gls{Buddy}}
In the Musicians' Guild, \Gls{Clete} is alarmed by the rise of the free music movement, and decides
to enlist the Assassins' Guild to get rid of \Gls{Buddy}. He overrides \Gls{SLemon}'s warnings, and
believes that the situation will become too dangerous if left to fester. \Gls{Buddy} decides to
play an impromptu concert for the sleepy village where \Gls{Asphalt} makes their first rest stop.

\subsubsection{\Gls{Buddy} escapes death at the hands of some Assassins}
\Gls{Buddy} and the band are richly rewarded by the villagers with food and drink, when the music
takes over their minds. After the rest of them fall asleep, he heads out into the street, to try and
deal with the music withdrawal. \Gls{Susan} once again saves his life by scaring off some Assassins
hired by \Gls{Clete}, and vanishes when the rest of the band come down to investigate the ruckus.

\subsubsection{\Gls{GlodG} and \Gls{Cliff} talk about their secret plan to cure \Gls{Imp}}
\Gls{GlodG} and \Gls{Cliff} whisper to each other about the secret task given to some alchemist in
Ankh-Morpork, which should be ready by the time they finish the tour. Meanwhile, the \Gls{DRat}
enlists the help of \Gls{Quoth} to try and talk some sense into \Gls{Susan}. \Gls{Crash} and his
friends show up at \Gls{Dibbl}'s office to register for the Free Concert, and realize they need a
catchy name.

\subsubsection{\Gls{Albert} takes it upon himself to track down \Gls{Death}}
\Gls{Crash} and his friends walk along the streets at night, and dismiss \Gls{Death} when he
accosts them as one of the beggars. Using \Gls{Quoth} as a translator, the \Gls{DRat} tells
\Gls{Albert} about \Gls{Susan}'s meddling, causing him to insist on going out to find \Gls{Death}
using his wizard powers.

\subsubsection{\Gls{Albert} is alarmed by the time remaining in his hourglass}
\Gls{Albert} takes out his hourglass, and notices how few days he has left, per his arrangement with
\Gls{Death}. The \Gls{DRat} informs him that he last sensed the master's presence in some sandy
place, as \Gls{Albert} sets off on his mission. The band plays their show in Pseudopolis, causing
such a ruckus that the City Watch asks them to leave immediately.

\subsubsection{\Gls{Clete} is shocked to see the Assassins rescind his contract}
\Gls{Clete} is surprised to learn that the Assassins' Guild is rejecting his contract, and thinks
about the hostile takeover of his own Guild that might be imminent, if the new musicians keep
growing in numbers. \Gls{Susan} barges into \Gls{Albert}'s room at the House of \Gls{Death}, and
finds a piece of paper on it with numbers crossed out in decreasing order.

\subsubsection{\Gls{Albert} tries to retrace \Gls{Death}'s steps through the Disc}
\Gls{Albert} investigates the fort at the Klatchian border, and is annoyed to find that \Gls{Death}
has already left the place. The \Gls{DRat} suggests heading to Ankh-Morpork, when \Gls{Albert} asks
where someone would want to go to ensure their anonymity. Meanwhile, \Gls{Buddy} and the band cause
another riot when they play in Sto Lat, before being banished by \Gls{Keli} on threat of arrest.

\subsubsection{\Gls{GlodG} notices the great financial success that the band is having}
\Gls{GlodG} tries to negotiate a bribe with the mayor of Quirm, when they are denied entry and
deemed a public nuisance. The mayor is enticed by the tidy sum \Gls{Asphalt} hands over in advance,
and allows them into the city, against the advice of the City Watch. They evacuate Quirm after the
show, with \Gls{Buddy} once again falling asleep with the magical guitar close to his chest.

\subsubsection{\Gls{Susan} travels in time to her parents' death}
\Gls{Susan} travels in time to the accident that killed her parents, and sees \Gls{Death} show up
to watch their demise. She asks \Gls{Death} if he could have stopped them dying, and listens to the
same tirade about non-interference. Meanwhile, \Gls{Albert} follows the \Gls{Death}'s trail to the
Mended Drum, where he learns from \Gls{HDun} that they threw the mysterious man into the Ankh, after
he went through the entire store of liquor.

\subsubsection{\Gls{Albert} is killed when a thief breaks his hourglass}
\Gls{Albert} dies when a mugger knocks him out, accidentally shattering the hourglass that was
hidden in his robes. The \Gls{DRat} realizes that it will have to continue the search for
\Gls{Death}, and heads to the river Ankh to find a trail. The mugger runs away when he sees the
small skeletal rodent coming to bite his ankles, leaving \Gls{Albert} on the streets.

\subsubsection{\Gls{Dibbl} prepares the venue for \Gls{Buddy}'s Free Concert}
\Gls{Dibbl} oversees the preparations for the Free Concert, and runs into \Gls{Crash}'s band, who
are still deciding on a name for their group. He is overjoyed to see the merchandising deals pour
in, after the shirts and shoes sell out in a few hours.

\subsection{}
\subsubsection{\Gls{Buddy} and his troupe arrive at the Free Concert}
\Gls{Buddy} asks \Gls{Asphalt} to speed back to Ankh-Morpork after they wake up with a horrible
hangover. Meanwhile, \Gls{Ridcu} takes \Gls{Stibb} along to the Free Concert, after placing the
rest of the inner council in house arrest. After reaching the venue for the Free Concert,
\Gls{Cliff} and \Gls{GlodG} present \Gls{Imp} with his ancestral harp, now repaired and tuned by
a workshop in the city.

\subsubsection{\Gls{Buddy} is reunited with his harp}
\Gls{Dibbl} is annoyed at the delay in \Gls{Buddy}'s band starting their show, and goes backstage
to see them chatting about their past. \Gls{Buddy} tries to play the guitars owned by other bands,
and finds the music unpalatable. He is pleased at the familiarity of his harp, and decides to use it
in the coming show.

\subsubsection{\Gls{Buddy} plays a folk song on stage using his ancestral harp}
\Gls{Clete} and his men from the Musicians' Guild watch \Gls{Buddy} take the stage with his band,
and are overwhelmed by the screaming of the crowd. He then notices \Gls{Buddy} staring at an empty
patch of grass in front of the stage, wondering why the band is delaying their set. A while later,
\Gls{Buddy} manages to convince the guitar to let him play a single song on his harp, and starts
to play some folk music.

\subsubsection{\Gls{Buddy} and his band escape the city with the gold after finishing their set}
\Gls{Buddy} thanks the guitar for letting him play his award-winning song for the audience, and
picks it up to begin the main show. \Gls{Ridcu} spots \Gls{Susan} in front of the stage, and decides
to stop \Gls{SLemon} from firing his crossbow at \Gls{Buddy}. After playing their set, the band
escape using a wagon readied by \Gls{Asphalt}, along with all the gold. \Gls{Dibbl} realizes too
late that \Gls{Buddy} is not coming back for an encore, and decides to make do with \Gls{Crash}'s
troupe.

\subsubsection{\Gls{Cliff} and \Gls{GlodG} think about reaching Quirm with the gold}
\Gls{Cliff} and \Gls{GlodG} realize that part of the money is owed to \Gls{Chry}, and wonder if
they can send the share back once they split it up in Quirm. Meanwhile, \Gls{Crash} and his band
wonder if substituting for \Gls{Buddy} will be their big break. \Gls{Stibb} and \Gls{Ridcu} prepare
themselves for some portal to the Dungeon Dimensions that might open up when \Gls{Buddy}'s band
their encore.

\subsubsection{\Gls{Death} finds \Gls{Albert} almost out of time}
\Gls{Death} rescues \Gls{Albert}, who has mere seconds left in his hourglass. He asks for the
whereabouts of \Gls{Susan}, and learns that she is trying to save \Gls{Buddy}. He then asks the
\Gls{DRat} to take care of the comatose \Gls{Albert}, and runs off to find a horse. \Gls{Crash} and
his band fail to play any music, and get attacked by the angry crowd. Meanwhile, \Gls{Colon} and
\Gls{Nobby} watch a second wagon thunder past them with \Gls{Clete} and his cronies on it.

\subsubsection{The inner council find the \Gls{Libra} prototype motorcycle}
The inner council close the crystal ball they had been using to watch the Free Concert, and run to
the Library when they hear a loud scream originating from the cellars. They find the \Gls{Libra}
busy constructing his motorcycle, and marvel at its design. The \Gls{Dean} is transfixed by the
skull and bone handlebars, and the chrome paint on the body, as the \Gls{Bursar} wonders how it is
supposed to run on just two wheels.

\subsubsection{\Gls{Susan} stops \Gls{Buddy}'s wagon from falling over a mountain trail}
\Gls{Death} walks into the cellar, and commandeers the motorcycle, after borrowing the \Gls{Dean}'s
leather jacket. A while later, \Gls{Colon} and \Gls{Nobby} watch him plow through the city gate on
the motorcycle, powered by his own inherent magic. \Gls{Susan} manages to catch up to the cart, and
stop it from going around the blind turn that killer her parents.

\subsubsection{\Gls{Susan} learns about the origin of \Gls{Buddy}'s magical guitar}
\Gls{Buddy} throws the magical guitar into the gorge, as \Gls{Susan} rescues the rest of his band,
just in time for the wagon to lose its traction and plunge down the cliff. \Gls{Susan} asks
\Gls{Buddy} if he bought the guitar from a strange-looking shop, and \Gls{GlodG} is reminded of his
reservations about the shop.

\subsubsection{\Gls{Susan} sees the music and its plan for \Gls{Buddy}}
The music transports \Gls{Susan}'s spirit to the birth of the universe, where it shows her the
origin of all life on the Disc from the primordial chorts of power. When she arrives back at the
cliffside road, she realizes that \Gls{Buddy} and the band have to die in the crash, per the music's
desire to see its champions live short and eventful lives. She then sees \Gls{Death} crash into the
opposing cliff, when the ruined motorcycle flies off the road and sends bones crashing down.

\subsubsection{\Gls{Buddy} plays the music one last time on the magical guitar}
\Gls{Death} corners the music by playing the only chords he knows, on the magical guitar.
\Gls{Susan} realizes that \Gls{Buddy} will have to play some tunes on the guitar so that the music
animating all life on the Disc will not fade away, and hands it to him. He plays some notes,
before \Gls{Death} takes the guitar back and smashes it on the ground.

\subsubsection{\Gls{Death} returns \Gls{Susan} to the night of her escape from the dormitory}
\Gls{Death} transports \Gls{Susan} back in time to the night she sneaked out of her room at
midnight, and tells her that \Gls{Buddy} and the band will live an alternate life, with the music
being out of the picture. She kisses him goodbye, and appreciates the swing he made for her many
years ago.

\subsubsection{\Gls{Susan} realizes that the alternate \Gls{Imp} is in Quirm}
\Gls{Susan} learns that \Gls{Buddy} is now working at a restaurant next to her boarding school, and
runs to meet him. Meanwhile, \Gls{Death} re-installs the swing in his orchard, and resumes his
duties as the grim reaper.