\section{Sourcery}


\subsection{}
\subsubsection{\Gls{Ipslore} mourns the death of his wife}
\Gls{Ipslore} waits with his eighth child next to his burnt house, as \Gls{Death} comes to claim
his soul. He tells \Gls{Death} that he is leaving his octiron staff as a final gift for his
child, and decides to force a destiny upon him. \Gls{Death} advises against it, as \Gls{Ipslore}
curses the wizards of Unseen University for ostracizing him and his wife, forcing them to run to
the edge of the civilized world.

\subsubsection{\Gls{Ipslore} makes one last desperate play to evade \Gls{Death}}
\Gls{Death} takes \Gls{Ipslore} with a lightning bolt to his head, just as the wizard hands his
staff to his infant son. This results in his soul being trapped in the staff, which \Gls{Death}
cannot destroy, lest he interfere with the child's destiny. \Gls{Ipslore} agrees to the loophole
that his son willingly giving his staff away would lead to his downfall from the Archchancellorship
of the University, lording over the same wizards that had excommunicated \Gls{Ipslore}.

\subsubsection{\Gls{Rince} tries to report his findings to \Gls{Spelter}}
\Gls{Rince}, now assistant librarian to the orangutan in charge of the tomes, notices the
creatures in the university fleeing it in a panic, and runs to the bursar's office to investigate.
In his office, \Gls{Spelter} dismisses \Gls{Rince}'s concerns about the foundations trembling, and
the rats fleeing, while offering him some alcohol to calm down.

\subsubsection{\Gls{Rince} escapes the University compound with the \Gls{Lugg} and the \Gls{Libra}}
Out on the University lawn, \Gls{Rince} watches the insects and pests flee the University, along
with the stone gargoyles usually perched up on the rooftops. He goes to his quarters in the library
and wakes the \Gls{Lugg} up from its winter hibernation, and prepares to flee the University,
dragging the \Gls{Libra} with him.

\subsubsection{The Sourceror deals with the wizard set to become the new Archchancellor}
The Sourceror walks to the front entrance of the University, just as the wizards prepare for the
feast of Small Gods' Eve. Meanwhile, the Archchancellor-elect is ambushed in his room by some
unknown wizard, just as the thief lurking in the corridors reaches his chamber. The thief finds the
leather box he is in search of, and opens it to hear a faint voice berating him for being late.

\subsubsection{\Gls{Rince} bemoans his inability to prosper within the University system}
At the Mended Drum, \Gls{Rince} talks fondly of his memories as a child, learning about the old
ways of magic, before the University had formalized it into a system of academic instruction.
The \Gls{Libra} listens half-heartedly, busy nursing its beer, as the \Gls{Lugg} tries to steal
snacks from the other patrons.

\subsubsection{\Gls{Spelter} watches \Gls{Coin} interrupt the crowing of the Archchancellor}
\Gls{Spelter} leads the wizards in the banquet hall as they prepare to welcome the Archchancellor,
and is shocked to find a young boy in white robes burst in through the door, now reduced to a
glowing liquid. \Gls{Skarmer}, a member of the inner council of wizards, tries to ask the boy why
he has barged into the University, and is amused to learn that the boy \Gls{Coin} wants to duel the
strongest wizard present in the hall.

\subsubsection{\Gls{Coin} shocks the assembled wizards by one-upping \Gls{Skarmer}}
\Gls{Skarmer} summons a pocket-dimension created by one of the last sourcerors, a feat considered
difficult even by the standards of eighth-level wizards. He finishes summoning the spherical
orb containing the garden, and is annoyed to see \Gls{Coin} complain about its size. \Gls{Coin}
manages to transport all of the wizards gathered in the dining hall to the pocket dimension, before
returning to them to the University, and making \Gls{Skarmer} vanish in a cloud of smoke.

\subsubsection{\Gls{Spelter} recommends a negotiated truce with \Gls{Coin}}
After letting \Gls{Coin} sit on the Archchancellor's chair per his wishes, and sending him to bed
with a hearty meal, the council of Wizards sit down to debate their future. \Gls{Spelter}, surprised
to see them so rattled that they take his opinion seriously, starts to talk about letting the boy
sit on the ceremonial chair, and guiding his decision-making instead of confronting him head-on.

\subsubsection{\Gls{Carding} and \Gls{Spelter} decide to enter an uneasy alliance}
\Gls{Carding}, one of the council members, shows support for \Gls{Spelter}'s idea, and dismisses
the other senior wizards for the night. \Gls{Carding} and \Gls{Spelter} stay in the meeting hall,
and launch surprise attacks at each other simultaneously. They agree reluctantly to a temporary
truce in trying to mould the boy's mind, fully realizing that betrayal lurked around the corner
waiting for either of them lose their utility.

\subsubsection{\Gls{Carding} talks about the end of sourcery at large}
\Gls{Carding} reveals the old legends of wizards being able to birth sourcerors as their eighth
child, and of how the Gods had found it terribly inconvenient to have such powerful beings on the
Discworld to interfere with their plans. He asks for the enchanted hat of the Archchancellor to
be retrieved, so that they might crown \Gls{Coin}, and continue to shape his mind as they see fit.

\subsubsection{The thief with the Archchancellor's hat forcibly drags \Gls{Rince} along with her}
The mysterious thief who had stolen the Archchancellor's hat from the University greets \Gls{Rince}
in the Mended Drum, and asks him to take on a mission. He declines, telling her he has had his
fill of adventure, just as the \Gls{Patri}'s guards show up to arrest her. A bar fight breaks out,
allowing the two of them to escape upstairs, and escape through a window.

\subsubsection{\Gls{Conina} leads \Gls{Rince} to the Shades district}
The \Gls{AHat} tells \Gls{Rince} that terrible events are in progress at the University, and that
it needs to be taken to Klatch, as soon as possible. The female thief sets off down an alley,
intent on walking into the run-down criminal district of Ankh-Morpork, and makes short work of
the petty thieves that accost them on their way in. She introduces herself as \Gls{Conina}, and
heads into an inn at the center of the district.

\subsubsection{The \Gls{AHat} defends itself from a petty thief}
Someone steals the box containing the \Gls{AHat} from \Gls{Rince}, during the minor scuffle that
breaks out in the tavern, with \Gls{Conina} hurrying out into the back-alley in pursuit. The thief
gets frozen to death by the \Gls{AHat}'s own magic, with \Gls{Rince} accidentally toppling the
frozen man, and making him shatter. \Gls{Conina} notices more criminals start to take an interest
in the \Gls{AHat}, and asks \Gls{Rince} to keep moving.

\subsubsection{\Gls{Conina} and \Gls{Rince} reach the city docks}
\Gls{Conina} explains that she is \Gls{Cohen}'s daughter, and that she has inherited his mad urge
to steal, and his impulse to greet strangers with a knife to the throat. \Gls{Rince} muses that it
must be great for an aspiring barbarian to have these qualities, and she reveals that her dream is
to be a hairdresser, in complete opposition to her violent instincts.

\subsubsection{The \Gls{Lugg} is reunited with \Gls{Rince}}
The \Gls{AHat} tells \Gls{Rince} that it represents the combined power of every archchancellor at
the Unseen University, going back millennia. It uses its magical persuasion to force him to find a
ship ready to sail out of the city, as the \Gls{Lugg} slowly ambles up to them, with many crossbow
bolts and swords sticking out of its body.

\subsubsection{\Gls{Spelter} and \Gls{Carding} talk about the sourceror infusing magic into the
    University}
At the Unseen University, the aura of sourcery seeping into the campus enables the wizards to
perform feats of magic they had only every dreamt of. The \Gls{Libra} locks himself in the main hall
of the library, and reads the history of sourcerors with growing alarm. In the Great Hall,
\Gls{Carding} is pleased by the resurgence of magic into the University, and tells \Gls{Spelter}
that wizarding levels and orders are no longer meaningful.

\subsubsection{\Gls{Coin} makes some changes in the Great Hall of the University}
\Gls{Coin}'s staff flings \Gls{Carding} across the Great Hall when he dares to touch it without
the boy's permission. \Gls{Coin} warns him not to touch the staff, as he sets about redoing the
Great Hall's architecture, turning it into a well-lit modern lobby, complete with glass windows and
marble pillars.

\subsubsection{\Gls{Hakar} is chastised by \Gls{Coin}}
\Gls{Hakar}, a scholar of magical lore, confronts \Gls{Coin}, reminding him of the traditional
process of selecting an archchancellor. \Gls{Coin} in turn, ridicules the wizards, calling them
little more than insects fighting over their few acres of land in the city, and leaving the
\Gls{Patri} to wield real power in the outside world.

\subsubsection{\Gls{Vetina} is teleported against his will to the University}
In the palace of Ankh-Morpork, the \Gls{Patri} reads the latest intelligence reports from his
network of spies, as he thinks back to the centuries of trading-guilds ruling over the city.
As the head of the \Gls{Vetina} family, he thinks about the headache of administering the city,
as he is suddenly teleported to the renovated Great Hall of the University.

\subsubsection{\Gls{Carding} transmutes the \Gls{Patri} into a lizard}
The \Gls{Patri} gets angry at \Gls{Carding} as his pet dog, which was also transported with him,
growls at the octiron staff in \Gls{Coin}'s arms. \Gls{Carding} orders the \Gls{Patri} to be
imprisoned in the wine cellars under the University, reminding him that the wizards had finally
awakened to their true power. He accidentally morphs the \Gls{Patri} into a lizard, and is pleased
at the power now available to him.

\subsection{}
\subsubsection{\Gls{Conina} spots Klatchian slavers approaching their ship}
\Gls{Conina} gives \Gls{Rince} a haircut on board the ship sailing to Al Khali, on the coast of
Klatch across the Circle Sea. She spots some slaver ships approaching them in the distance using
her superhuman vision, leaving \Gls{Rince} to confirm the grim news with the \Gls{AHat}. It asks
him to wear the hat, so that it might use his eyes to see into the distance.

\subsubsection{\Gls{Rince}'s ship is set upon by Klatchian slavers}
On wearing the \Gls{AHat}, \Gls{Rince} sees the dead archchancellors staring at him through his
mind, and is overwhelmed by their combined experience weighing down on him. He takes it off, in
time to hear the alarm being rung as the slaver boats close in. The slavers manage to subdue the
ship's crew using blunt weapons, with the leader making for the afterdeck, where \Gls{Rince}
and \Gls{Conina} are hiding.

\subsubsection{\Gls{Conina} and the \Gls{Lugg} deal with the slavers}
The head slaver talks to \Gls{Rince} about the opportunity of being a eunuch in the emperor's
harem, as the only viable path for a physically feeble wizard, as \Gls{Conina} uses the distraction
to kill his bodyguards. The \Gls{Lugg} swallows the head slaver, trapping him in its pocket
dimension, as \Gls{Conina} jumps down to the main deck, to kill the rest of the slavers.

\subsubsection{The wizards emerge into the city from the gates of the University}
In the city square next to the Unseen University, the stalls and tenements that had sprouted up
over the years are all pushed away by a magical shockwave, with one enterprising merchant made to
vanish for daring to question the wizards marching out of the gates. The rest of them see the
wizards materialize fresh food out of thin air, and realize their livelihoods are under threat in
addition to their lives.

\subsubsection{\Gls{Rince} decides to help the \Gls{AHat} after it is captured by the slavers}
\Gls{Conina} tells \Gls{Rince} that the slavers fled with the \Gls{AHat}, and that they were
likely taking it to Al Khali. \Gls{Rince} initially decides to leave the \Gls{AHat} to its fate,
before his conscience bullies him into going into the city to rescue it.

\subsubsection{\Gls{Spelter} presents his newly sewn archchancellor's hat to \Gls{Carding}}
At the University, the wizards discover the incompatibility of sourcery with intrinsically magical
things, such as their own bodies. \Gls{Spelter} hand-sews a replica of the \Gls{AHat}, which manages
to fool \Gls{Carding}'s critical eye. Meanwhile, the city of Ankh-Morpork receives a facelift,
with the grime and dirt magically swept away, leaving a clean city and sparkling river.

\subsubsection{\Gls{Coin} insists on a coronation ceremony for himself}
The inner council of wizards present the new archchancellor's hat to \Gls{Coin}, who insists on a
grand coronation ceremony, so that the world might know of the true power of wizardkind. He tells
\Gls{Carding} that the wizards living in far away lands will now have the gift of his sourcery to
transport themselves instantly to the site of the new coronation. He also intends to move his seat
of power to a newly constructed palace, condemning the University as a symbol of weakness.

\subsubsection{\Gls{Coin} almost detects the dissent taking shape in \Gls{Spelter}'s mind}
\Gls{Coin} reminds the wizards that they no longer had to depend on dusty tomes and arcane rituals
to perform magic, since he had given them the gift of sourcery. \Gls{Spelter}'s mind starts to
remember the old ways fondly, but \Gls{Carding} stomps on his toes just as he prepares to voice his
nostalgia. The city is put under a midnight curfew, with the citizens being forced to enter a
magical slumber at the appropriate time.

\subsubsection{\Gls{Spelter} talks to the \Gls{Libra} about the possible shuttering of the Library}
\Gls{Spelter} creeps through the University corridors at night, to warn the \Gls{Libra} about the
impending closure of the Library. The \Gls{Libra} tells him about a secret entrance that it uses to
go in and out of the sealed Library, and reassures him that it is keeping the \Gls{Patri} safe in a
glass jar. On his way back to his chambers, \Gls{Spelter} decides to investigate some quiet sobs
coming from the rooms of a senior wizard.

\subsubsection{\Gls{Rince} and \Gls{Conina} get surrounded by thugs in Al Khali}
\Gls{Rince} and \Gls{Conina} reach the Temple of Al Khali, with its famous frescoes and carvings,
while thinking about the best way to track down the \Gls{AHat}. Eventually, \Gls{Conina} decides to
seek out the criminal district, hoping to be ambushed by someone with knowledge of the slavers.
They are ambushed by some thugs armed with crossbows, leading \Gls{Conina} to recall her father's
words about projectile weapons and impossible odds.

\subsubsection{\Gls{Coin} builds the new wizard stronghold out of pure magic}
\Gls{Spelter} tries to tell \Gls{Carding} about the sobbing from last night, but is brushed off,
as \Gls{Coin} is busy crafting a new home for the wizards. He puts the final touches on the
stronghold, before opening a portal to it using his staff. In the oxbow bend of the Ankh river,
\Gls{Coin} summons the new fortress, rising high in the air, and made of solidified magic.

\subsubsection{\Gls{Coin} wishes the death of the wizarding system}
\Gls{Coin} declares his coronation will take place in a week, and that he will force a full moon
on the appointed day. \Gls{Spelter} suppresses the dissent in his heart, and plays along with
\Gls{Coin}'s plan to dissolve the wizarding system, as well as burn down the Library in the
University.

\subsubsection{\Gls{Spelter} is chased by \Gls{Ipslore} through the university's basement}
\Gls{Spelter} is cornered by the \Gls{Ipslore}, trapped in the octiron wand, as he tries to warn
the \Gls{Libra} about the destruction of the Library. He tries to run into the underground kitchens,
but \Gls{Ipslore} keeps up with him easily, melting the cleaver that he attempts to use in
self-defense.

\subsubsection{\Gls{Conina} and \Gls{Rince} sit in \Gls{Creo}'s garden}
\Gls{Conina} and \Gls{Rince} are brought to a walled garden in the middle of Al Khali, where the
mayor of the city, \Gls{Creo}, introduces himself. He orders his men to back off, and offers food
and drink to his guests. \Gls{Rince} recognizes him as the son of the famed assassin, who was
rumoured to be richest man on the Disc. He summons his Grand Vizier \Gls{Abrim}, who reminds the
mayor that the \Gls{AHat} had warned them about the arrival of these two foreigners.

\subsubsection{\Gls{Abrim} decides to talk to the \Gls{AHat} directly}
\Gls{Abrim} has \Gls{Conina} escorted to the seraglio, as \Gls{Rince} is interrogated about the
nature of the \Gls{AHat}. Eventually, the \Gls{AHat} decides to communicate telepathically with
\Gls{Abrim}, promising him a favourable bargain if he were to cut the wizard out of the negotiation.
\Gls{Rince} gets thrown in the snake pit, where he meets a barbarian, wearing woolen underwear.

\subsubsection{\Gls{Rince} accidentally helps \Gls{Nijel} break open a wall in the snake pit}
The \Gls{Lugg} walks into a bar on the outskirts of Al Khali, and gets drunk on the powerful local
liquor, to deal with its separation from \Gls{Conina}. Meanwhile, \Gls{Rince} learns that the
teenage barbarian is named \Gls{Nijel}, and notices the lone snake in the pit trying its best to
go unnoticed. \Gls{Nijel} attempts to open a weak stone block in the wall, and \Gls{Rince} is
shocked that his subconscious attempt to summon magic works, with a fireball blasting the wall
apart.

\subsubsection{\Gls{Rince} and \Gls{Nijel} make it to the palace grounds}
\Gls{Rince} manages to use the magical energy gathering in the palace to summon an elevator to
the surface, where \Gls{Nijel} notices a tall tower erupting from the ground. \Gls{Rince} notices
some familiar old wizards marching out of the white tower, making short work of \Gls{Creo}'s
guards, as they attempt to rush them with swords and sickles. \Gls{Nijel} is horrified by the
dismissive way in which the wizards kill the armed thugs, prompting \Gls{Rince} to ask if this was
the first time he was witnessing murder.

\subsection{}
\subsubsection{\Gls{Nijel} and \Gls{Rince} refocus on rescuing \Gls{Conina}}
\Gls{Nijel} suggests \Gls{Rince} to stop wearing his wizard robes and hat, if he is worried about
being hunted down along with the newly ascended wizards from Ankh-Morpork. \Gls{Rince} is horrified
by the idea, and eventually remembers his original objective of rescuing \Gls{Conina} from the
seraglio. Searching through the palace corridors, they eventually find the entrance to the
seraglio, with only a few guards left inside to protect the women.

\subsubsection{\Gls{Sconn} leads a party to the Library, with orders to burn it down}
A squad of wizards, led by \Gls{Sconn} are tasked with burning down the Library of the Unseen
University, in the middle of the night. \Gls{Sconn} makes quick work of the heavy door leading into
the Library, and asks his men to prepare their matchsticks. One of the wizards spots something
moving close to the domed ceiling.

\subsubsection{\Gls{Sconn} is thrashed by the \Gls{Libra}}
\Gls{Sconn} is attacked by the \Gls{Libra}, and thrown out of the Library with enough force to
bowl over the other wizards cowering in fear. They remind him of the risk in using magic next to
the tomes kept in the Library, and prepare to find some flammable oil to systematically burn down
the bookshelves.

\subsubsection{\Gls{Nijel} and \Gls{Rince} are reunited with \Gls{Conina}}
\Gls{Nijel} manages to perform some sword acrobatics using the guide to barbarian lifestyle written
by \Gls{Cohen}, but manages to get his sword stuck in the ceiling. The harem guards close in on
him, until \Gls{Conina} arrives and sneakily stabs them from behind. \Gls{Rince} is relieved that
he did not have to resort to magic again, as he notices \Gls{Conina} and \Gls{Nijel} staring at
each other, lovestruck.

\subsubsection{\Gls{Conina} and \Gls{Nijel} are smitten with each other}
\Gls{Conina} privately threatens \Gls{Rince} not to reveal her parentage to \Gls{Nijel}, as she
talks about the mayor asking her to tell him stories, as part of her duties in the harem. For his
part, \Gls{Nijel} begs \Gls{Rince} not to reveal how much of a novice he is. Meanwhile, the
\Gls{Lugg} wakes up from its drunken stupor, despondent at being banished by \Gls{Conina}. It
drifts down the Tsort river, and is ambushed midway by some logs.

\subsubsection{\Gls{Rince} and his party reach the sourceror's tower in Al Khali}
At the new tower of sourcery in Al Khali, \Gls{Rince} notices the city guards being transfigured
into small reptiles and rodents, with the architecture being slowly converted into the white marble
preferred by \Gls{Coin}. As they argue about confronting the wizards in the tower, \Gls{Abrim}
steps out of a ruined building, wearing the \Gls{AHat}.

\subsubsection{\Gls{Rince} and his party are mind-controlled by the \Gls{AHat}}
The \Gls{Lugg} shakes off the crocodile ambush, and trots through the desert, reaching a basilisk's
hunting grounds. The beast tries to stare down the \Gls{Lugg} with its magical sight, supposed to
petrify any souls caught in it, and feels the sudden urge to blink. Meanwhile, the \Gls{AHat}
declares its intent to use \Gls{Abrim} as a useful host, and mind-controls \Gls{Rince} into
marching against the sourcerors, along with his companions.

\subsubsection{\Gls{Rince} recalls the history of the Mage Wars}
\Gls{Rince} recounts the story of the Mage Wars aeons ago, with common people being caught in the
crossfire as evenly matched wizards unleashed weapons of mass destruction on each other, stretching
the fabric of reality to its very limit. The \Gls{Lugg} deals with the basilisk, and then a chimera
that ambushes it. It decides to give up the life of freedom, and seek out a master.

\subsubsection{\Gls{Abrim} becomes the \Gls{AHat}'s unwitting host}
\Gls{Abrim}, now possessed by the \Gls{AHat}, seeks out a fight at the entrance to the sourceror's
tower. A wizard shows at the gate, and challenged \Gls{Abrim} to a magical duel. \Gls{Abrim} tells
him that he can also harness sourcery using his centuries of knowledge, and shrugs off all the
magic thrown at him. The \Gls{AHat} lets \Gls{Rince} and his companions loose from its mind-control,
as it focuses on destroying the wizards holed up in the tower.

\subsubsection{\Gls{Rince} and his party meet up with an intoxicated \Gls{Creo}}
\Gls{Rince} and his party run from the magical overload taking over the space around the tower,
and find \Gls{Creo} waking up from a stupor, surrounded by the rubble of his palace. He tells them
that he has never stepped out of his palace grounds, and has no idea where his famed horse stables
are located. Eventually, \Gls{Creo} regains his composure enough to remember the fact that his
magic carpet is in the treasury, causing \Gls{Rince} to recoil in horror.

\subsubsection{\Gls{Rince} and his party traverse the tunnel into the treasury}
The \Gls{Lugg} manages to evade the collateral damage from the Mage War erupting in Al Khali, and
climbs out of the Tsort river, to pursue its new master. Meanwhile, \Gls{Creo} takes \Gls{Rince}
and his party to the palace treasury, where a secret tunnel hidden behind a statue of \Gls{Offler}
leads to the room containing magical artifacts.

\subsubsection{\Gls{Rince} and his party are trapped in the treasury}
\Gls{Rince} is amused by the silly traps laid by \Gls{Creo}'s grandfather, the original architect
of the palace and treasury, until the tunnel roof collapses, trapping him and his party in the
treasury. \Gls{Conina} looks at the magic carpet, lamp and gold ring on a central pedestal, as
\Gls{Creo} mumbles something about his grandfather using those artifacts to build his fortune.

\subsubsection{\Gls{Rince} commandeers the magic carpet, and escapes the collapsing palace}
\Gls{Rince} manages to figure out how the magic carpet works, by speculating that it was programmed
to fly in the opposite direction of any commands spoken to it. He escapes the treasury with his
party, just as the stones of the palace are broken off by the \Gls{AHat}, and magically reassembled
to create a new tower where the sourcerors had formerly assembled their own. \Gls{Rince} believes
that the \Gls{AHat} has won the first battle, and is consolidating its power in Al Khali, before
venturing out into the rest of the Disc.

\subsubsection{\Gls{Rince} negotiates with his conscience on board the magic carpet}
\Gls{Rince} thinks about the helplessness of the common-folk in the Disc, in the face of another
Mage War, as he realizes his conscience is flying the carpet bypassing his conscious mind. It
chastises him for trying to run away from the sourceror at the root of the magic saturating the
world, instead of confronting him, even at the cost of his own life.

\subsubsection{\Gls{Rince} sleepwalks to the waterline, trying to assemble a stone tower}
\Gls{Rince} manages to land the carpet on the coast of the Circle Sea, with \Gls{Conina} building a
simple campfire to allow them to take turns sleeping. She wakes the other up in the middle of the
night, to point out \Gls{Rince} sleepwalking to and from the beach, subconsciously assembling a pile
of stones to build a tower.

\subsubsection{\Gls{Rince} slips away from his party on the magic carpet}
\Gls{Rince} gets shaken awake by \Gls{Nijel}, and notices the magical artillery being exchanged
across the Circle Sea. As the others get busy arguing about the value of wizards to the Disc,
\Gls{Rince} sneaks off with the magic carpet, intent on flying across the Sea to some abstract
enemy waiting in Ankh-Morpork.

\subsubsection{\Gls{Abrim}'s ritual in Al Khali is interrupted by a knock on the door}
In the wizards' tower of Al Khali, \Gls{Abrim} is busy channelling the raw power originating from
the others now subservient to him, as he hears a knock on the door. Surprised at the possibility
of any living thing being left unscathed by the reality-bending effects of their ritual, one of the
junior wizards opens the door to investigate.

\subsubsection{\Gls{Rince} returns to the revamped Ankh-Morpork}
\Gls{Rince} comes out of his angry haze midway to Ankh-Morpork, and realizes the Mage Wars would
eventually lead to the extinction of all life on the Disc. He lands in his home city, and finds it
unrecognizable, alarmed by the cleanliness and orderliness of the streets. He sees the University
deserted, and heads for the ruins of the Library, frantically trying to find the \Gls{Libra} in the
burnt rubble.

\subsubsection{\Gls{Nijel} uses \Gls{Creo}'s magic lamp to summon a \Gls{Genie}}
\Gls{Nijel} pulls out the magic lamp he had nicked from the treasury, as \Gls{Creo} argues with
\Gls{Conina} about their carelessness in allowing \Gls{Rince} to escape. He rubs it and summons a
\Gls{Genie}, in spite of \Gls{Creo}'s insistence that the original lamp that his grandfather had
used to build his fortune was a different one.

\subsection{}
\subsubsection{\Gls{Conina} threatens the \Gls{Genie} into obeying their command}
The \Gls{Genie} tries to get out of his obligations to \Gls{Nijel}, intent on securing his next
home in a lamp-shop, close to the harbour of Ankh-Morpork. \Gls{Conina} threatens the \Gls{Genie}
with the destruction of the lamp, making it take their request seriously. It tells them that it has
little experience with teleportation, and agrees to try to send them to Ankh-Morpork regardless.

\subsubsection{\Gls{Nijel} and his party travel to Ankh-Morpork inside the \Gls{Genie}'s lamp}
\Gls{Nijel} figures out the fact that the \Gls{Genie} has imprisoned them in the lamp, which is
being carried by another version of himself. The \Gls{Genie} tries to explain that this fractal
trick only works as long as the universe fails to catch on to the deception, as \Gls{Nijel} starts
to think really hard about the logistics of their trip to Ankh-Morpork.

\subsubsection{\Gls{Rince} meets up with the \Gls{Libra} and the remnants of the Library}
\Gls{Rince} finds the \Gls{Libra} holed up in the Tower of Art, now abandoned by the wizards, and
is shocked to learn that the tomes of magic all flew away from the Library, to seek refuge in the
tower. He finds the \Gls{Patri} safe in his glass jar, and his pet dog licking his boots. The
\Gls{Libra} gets to work repairing some damaged tomes, as \Gls{Rince} hands it surgical tools from
at impromptu operating table.

\subsubsection{\Gls{Rince} tries to crawl away from his mission to defeat sourcery}
\Gls{Rince} agrees with the \Gls{Libra} that the emergence of sourcery would spell the end of the
world eventually, but insists that someone else should be the one to face the threat this time.
The \Gls{Libra} snatches his hat from him, and threatens to cut it with its shears, as \Gls{Rince}
watches on helplessly. It then places the hat back on his head, to remind him that his instincts
made him the best candidate to stand up to sourcery.

\subsubsection{\Gls{Conina} and her companions steal some horses}
\Gls{Conina} and her party are transported to the outskirts of Quirm, where they notice the Mage
Wars in progress, and the exchange of magical artillery with other strongholds across the Disc.
They find some horses tethered to the rear entrance of a tavern, and decide to steal them, unaware
of the fact that those steeds belonged to \Gls{Death} and his horsemen, currently busy drinking
themselves into a stupor inside the inn.

\subsubsection{\Gls{Carding} defeats \Gls{Abrim} and the \Gls{AHat}}
\Gls{Carding} starts to feel nostalgic about the world before the emergence of \Gls{Coin}, as he
defeats the wizards holed up in Quirm, from the stronghold newly constructed in Ankh-Morpork.
As the wizards under \Gls{Coin}'s control turn their attention to Al Khali, \Gls{Carding} manages
to find a weakness in \Gls{Abrim}'s mental defenses, making him vanish under the weight of the
\Gls{AHat}'s pressure, and causing a chain reaction within the \Gls{AHat}'s tower.

\subsubsection{\Gls{Carding} dies in his attempt to destroy \Gls{Ipslore}}
\Gls{Carding}'s mind returns to \Gls{Coin}'s tower, and he berates the sourceror for allowing
the denizens of the Dungeon Dimensions to appear in the Discworld, along with the flow of raw magic.
\Gls{Ipslore} incinerates \Gls{Carding} when he tries to destroy the staff, leaving the other
wizards stunned at the horror of his body melting into a puddle.

\subsubsection{\Gls{Death} rides away from his horsemen stuck at the tavern}
\Gls{Death} is affronted by his horsemen asking to ride pillion on his steed, and rides off to
harvest some more wizard souls. \Gls{War} and \Gls{Famine} are busy trying to figure out how to
get around, as \Gls{Pesti} raids the tavern's kitchen, looking for food. They decide to wile away
some more time drinking, disregarding the Mage Wars that required their presence.

\subsubsection{\Gls{Hakar} tries to dissuade \Gls{Coin} from  antagonizing the gods}
Meanwhile, \Gls{Hakar} tries to explain the Dungeon Dimension, and speculates that the gods in Cori
Celesti might soon be forced to act against the sourcery. \Gls{Coin} declares war against the gods,
dismissing \Gls{Hakar}'s fears about their power.

\subsubsection{\Gls{Rince} raeches the main chamber at the top of the sourceror's tower}
The \Gls{Libra} reminds \Gls{Rince} that he had the weight of saving the entire world on his
shoulders, as he sets out to confront \Gls{Ipslore} and \Gls{Coin} atop the white tower of the
sourceror. Meanwhile, \Gls{Coin} imprisons the gods in Cori Celesti in a small sphere the size of
a pearl, as \Gls{Rince} manages to reach the top of the tower on his magic carpet.

\subsubsection{\Gls{Rince} gets attacked by \Gls{Ipslore}, against \Gls{Coin}'s wishes}
\Gls{Rince} is puzzled by the famed sourceror being a small boy, and starts to explain the brick
inserted into his sock, that he intends to use as a lethal weapon. \Gls{Coin} resists
\Gls{Ipslore}'s orders to kill the diseenter, insisting that \Gls{Rince} is a harmless jester.
\Gls{Ipslore} flies out of \Gls{Coin}'s arms, and knocks \Gls{Rince} down by slamming into his head
at great speed.

\subsubsection{\Gls{Coin} stops \Gls{Ipslore} from killing \Gls{Rince}}
\Gls{Rince} sees \Gls{Death} materialize next to him, as he enters bullet time, waiting for
\Gls{Ipslore} to slam into his head for the last time. \Gls{Rince} asks \Gls{Death} which wizard's
soul he is here to harvest, and time resumes before he can get an answer. \Gls{Coin} grabs
\Gls{Ipslore} midway through his trajectory, and breaks it into two pieces. \Gls{Hakar} is convinced
that \Gls{Coin} and \Gls{Ipslore} are evenly matched, and recommends fleeing the tower.

\subsubsection{\Gls{Rince} decides to try and help \Gls{Coin} defeat \Gls{Ipslore}}
\Gls{Coin} and \Gls{Ipslore} are locked in a mental battle, \Gls{Rince}'s conscience forces him
to jump into the circle of magical fire to try and help the boy. \Gls{Hakar} and the others
levitate down from the tower, as \Gls{Rince}'s burning hat falls down to the ground, to be quickly
covered in a layer of snow. Meanwhile, the horsemen of \Gls{Death} lounge around in the bar,
having forgotten the Apocalypse that they were supposed to be supervising.

\subsubsection{\Gls{Nijel} recalls the stories about the Apocalypse}
\Gls{Conina} and her party manage to gain control of the flying horses, in time to see clouds
drifting over the land, bringing heavy snow. \Gls{Nijel} asks the \Gls{Genie} about the snow, and
learns that the fable Apocalypse has arrived, signified by the gods vanishing and the Ice Giants
reclaiming the Disc. The \Gls{Genie} decides to repossess his lamp, and vanishes from the Disc,
believing that the end of sentient life is imminent.

\subsubsection{\Gls{Rince} and \Gls{Coin} defeat \Gls{Ipslore}}
\Gls{Rince} wakes up in the Dungeon Dimensions, vaguely recalling \Gls{Death} claiming
\Gls{Ipslore}'s soul when he is distracted by the fight against \Gls{Coin}. He then finds some
Things busy trying to widen a portal into the Discworld so that they can invade, and shakes
\Gls{Coin} awake. Meanwhile, refugees start to return to Al Khali, sensing the end of hostilities
against the mages from Ankh-Morpork.

\subsubsection{\Gls{Nijel} tries to talk the Ice Giants out of their conquest}
\Gls{Nijel} and his party fly hubwards, to find the Ice Giants starting their migration across the
Disc, using their magic to push massive glaciers in front of them to grind down the land. He tries
to negotiate with one of the leaders of the Ice Giants, and is rescued by \Gls{Conina} when forced
off his horse.

\subsubsection{\Gls{Rince} helps \Gls{Coin} escape the Dungeon Dimensions}
\Gls{Rince} decides to use his other sock, after filling it with sand, to distract the Things,
allowing \Gls{Coin} to jump into the portal back to the Discworld. \Gls{Coin} makes it through,
with the \Gls{Libra} beating back a tentacle that wraps around his legs, and is astonished to see
the \Gls{Lugg} jumping into the portal after \Gls{Rince}. The portal flickers and closes, with the
\Gls{Libra} reminding him that \Gls{Rince}'s fate cannot be ascertained from here.

\subsubsection{The \Gls{Libra} frees the Gods of Discworld from their imprisonment}
\Gls{Coin} hands the pearl containing Cori Celesti to the \Gls{Libra}, who throws it far away,
hoping to break the spell of imprisonment by shattering it. The gods of the Discworld emerge, angry
at the Ice Giants for pre-empting their apocalypse, and intervene in the advance of the glaciers.
\Gls{Conina} and \Gls{Nijel} watch fascinated as the snow melts all of a sudden, and the glaciers
retreat back towards the hub.

\subsubsection{\Gls{Conina} and \Gls{Nijel} are turned away by \Gls{Coin} when they ask after
    \Gls{Rince}}
\Gls{Coin} tells \Gls{Conina} and \Gls{Nijel} a story about \Gls{Rince} successfully defeating
\Gls{Ipslore}, before using his magic to alter their memories. He sends them on their way to live a
happy life, and asks the \Gls{Libra} how he can live in Discworld, while resisting the urge to use
his magical powers to alter it. It reveals to him the eventual path chosen by all sourcerors, and
wishes him the best as he steps into a pocket dimension of his own creation.

\subsubsection{\Gls{Creo} and the \Gls{Patri} resume their lives}
\Gls{Creo} finds the daughter of the innkeeper at the Mended Drum eager to tell him all the stories
she knows, and believes he has found his paradise. Meanwhile, the \Gls{Patri} is back to his human
form, only missing his memories for the past few weeks. He struggles to control his instinctive urge
to swipe at some moths with his tongue. The \Gls{Libra} mounts the tattered remains of \Gls{Rince}'s
hat in the Library, hoping he will come back for it some day.