\section{The Truth}


\subsection{}
\subsubsection{\Gls{deWorde} writes his latest newsletter to the nobility}
A rumour about dwarves inventing a means of transmuting lead into gold spreads like wildfire
throughout Ankh-Morpork. \Gls{deWorde} makes a primitive wood-block negative of the message to be
duplicated by the engraver \Gls{Crips} and sent to nearby nobles. He thinks about the handsome
profits in running a business making template letters for dwarves to write home, given the general
illiteracy of his fellow citizens.

\subsubsection{A dwarven cart enter the city late at night}
\Gls{Colon} and \Gls{Nobby} observe a heavily laden cart being pushed into the city through one of
its gates, as they stand watch on a cold foggy night. As they return to the Watch House to end their
shift, they also take note of a small rowboat entering the city through the river Ankh. The
cart being driven by the dwarves loses control in the icy winter, and slides into \Gls{deWorde},
as he is out to deliver his woodblock.

\subsubsection{\Gls{Pin} and \Gls{Tulip} deliver their hostage in Ankh-Morpork}
\Gls{Pin} and \Gls{Tulip} deliver a kidnapped person by rowboat to a contact waiting for them
with a carriage. The hand-off is seen by \Gls{FORon} and \Gls{Gaspode}, who immediately suspect
foul play. Meanwhile, \Gls{deWorde} wakes up groggy, and finds himself in the attic of a workshop,
where the dwarves are setting up a strange contraption that resembles a weaving machine.

\subsubsection{\Gls{deWorde} is introduced to \Gls{Gunil}'s printing press}
\Gls{deWorde} is surprised to see a dwarf demand the original document when he explains the idea
of woodblock printing. The dwarf introduces himself as \Gls{Gunil}, the owner of a new printing
press that is substantially faster than any existing machines. He shows off his mass-produced
posters advertising the business, and hands \Gls{deWorde} a few dozen copies of his newsletter.

\subsubsection{\Gls{deWorde} embraces the idea of expanding his newsletter}
\Gls{deWorde} notices the commotion outside the Bucket, the unofficial policeman's bar, and sneaks
away to his couriers with the newly printed newsletters. He decides to mail the extra copies to
other wealthy people outside the city, who might be able to afford the service. Meanwhile, the
kidnapped person is brought to a manor and confined to the cellar, as some conspirators discuss
alternatives to murdering \Gls{Vetina}.

\subsubsection{\Gls{Ridcu} sends the \Gls{Bursar} to investigate the new printing press}
\Gls{Ridcu} asks the \Gls{Bursar} why the University uses so much money every year at the Guild of
Engravers, and learns that movable type printing is incompatible with magical books. \Gls{deWorde}
walks into \Gls{Gunil}'s press the next day, to see the \Gls{Bursar} arguing about bulk printing
rates, and sees an advertisement being printed for \Gls{Dibbl}.

\subsubsection{\Gls{deWorde} prepares a newsletter about the new printing press in Ankh-Morpork}
\Gls{deWorde} decides to make a newsletter out of the \Gls{Bursar}'s order at the press, and asks
him for his opinion about the new technology. The \Gls{Bursar} is too fixated on the financial
benefits to ponder the magical side effects of the movable letters, and asks for a copy of the
newsletter once it is ready.

\subsubsection{\Gls{Vetina} fends off \Gls{Hughnon}'s attempt at shutting down the printing press}
\Gls{Vetina} reminds \Gls{Hughnon}, representative of the various priestly orders of Ankh-Morpork,
that the new dwarven printing press is helping the trade relationship between the city and
Uberwald. He then reminds \Gls{Hughnon} of the cold snap, and the increased need for coal and fuel
from the dwarf homelands, and dismisses his concerns about the movable type.

\subsubsection{\Gls{Charlie} is persuaded into impersonating \Gls{Vetina}}
\Gls{Vetina} sets out to have a chat with \Gls{Gunil}, after explaining the incessant march of
technology and the need to keep up with the times to a flustered \Gls{Hughnon}. Meanwhile,
\Gls{Tulip} and \Gls{Pin} try to convince \Gls{Charlie}, a lookalike of the Patrician, that he will
be returned to his former life in Pseudopolis with a massive payout after he impersonates
\Gls{Vetina} for a few short days.

\subsubsection{\Gls{Vetina} checks up on \Gls{Gunil}'s printing press}
\Gls{Vetina} walks into \Gls{Gunil}'s press, and is reminded of the Holy Wood fiasco. He wonders if
the press might have been located on the site of some ancient eldritch ritual, as \Gls{Gunil}
loses his patience at the absurdity of his rambling. \Gls{deWorde} pulls \Gls{Gunil} aside to
explain the sway that \Gls{Vetina} held over the city, and gets him to greet the Patrician with
some friendly words.

\subsubsection{\Gls{Tulip} and \Gls{Pin} spy on \Gls{Vetina}}
\Gls{Tulip} and \Gls{Pin} surveil \Gls{Vetina} from a nearby rooftop as he leaves the press, with
\Gls{Tulip} wondering where the entourage is. \Gls{Pin} reminds him that the city elite respect
\Gls{Vetina} highly for the service he does in maintaining the status quo, and is unaware of being
watched by \Gls{Gaspode}.

\subsubsection{\Gls{deWorde} and \Gls{Gunil} finalize the first ever issue of their newspaper}
\Gls{deWorde} thinks about his estranged father, the \Gls{LWorde}, who had wanted him to take
up a more respectable profession as the eldest son of a noble house. He helps \Gls{Gunil} with the
news items for the first ever issue of the Ankh-Morpork Times, and wonders how he is going to find
hundreds of readers who might be interested in reading so much text.

\subsubsection{\Gls{Gaspode} and the outcast beggars decide to distribute the newspaper}
\Gls{FORon} and \Gls{Gaspode} wander into \Gls{Gunil}'s press, and are roped in to distribute the
newspapers for a modest commission. \Gls{Gaspode} is happy to negotiate a better fee for the
beggars who are to sell the newspaper, and walks out of the press satisfied. He returns to the
beggar hangout, and convinces \Gls{DuckM}, \Gls{CoffinH}, \Gls{ASide} and \Gls{Altog} to join the
newspaper distribution network.

\subsubsection{\Gls{Pin} and \Gls{Tulip} meet with \Gls{Slant}, who represents the conspirators}
At the Lawyers' Guild, \Gls{Slant} tells \Gls{Pin} and \Gls{Tulip} that his employers are happy
with their progress, and reassures them that a part of their promised reward is on the way. He
then shows them a dossier compiling all of their crimes in other cities, to be kept as insurance
in case the impersonation of \Gls{Vetina} goes sideways. \Gls{Pin} is impressed by how careful
\Gls{Slant} and his employers seem to be, as \Gls{Tulip} marvels at the artwork in the office.

\subsubsection{\Gls{Sacha} is enticed into working for the newspaper}
\Gls{Sacha} visits \Gls{deWorde} at his home, angry at the loss of business for her grandfather. He
ropes her into working at the press as a writer, and reassures her that the Guild of Engravers would
be taken care of by \Gls{Vetina}. At an art museum, \Gls{Pin} and \Gls{Tulip} are taken to a
dimly lit back-room to meet the conspirators. They insist that \Gls{Vetina} should not be killed
when the impersonation takes place, and remind \Gls{Tulip} that the City Watch employs a werewolf.

\subsubsection{The conspirators reaffirm their decision to dispose of \Gls{Charlie} after the job}
After \Gls{Pin} and \Gls{Tulip} are sent away, a conspirator thinks about the possibility of
using \Gls{Charlie} in the future, until another reminds him of the risk in keeping the double
alive for too long. They intend to clean up all loose ends in their operation, by offering the
Assassins' Guild a contract for \Gls{Pin} and \Gls{Tulip} after the affair.

\subsection{}
\subsubsection{\Gls{Vetina} buys a copy of the first edition of \Gls{deWorde}'s newspaper}
\Gls{Vetina} asks his secretary \Gls{Drumk} to buy a copy of the newspaper from \Gls{FORon} when he
walks by the palace gates at dawn shouting his wares. He asks for a meeting with the heads of the
Engravers' Guild, given how angry they will be at the new technology being allowed to operate in the
city.

\subsubsection{\Gls{deWorde} gets some new stories from \Gls{Sacha} at the press}
\Gls{deWorde} gets to his office after seeing one of his flatmates read the paper at breakfast, and
is surprised at his commission for the day. \Gls{Gunil} believes that lowering the price will help
increase their readership even further, and points him to \Gls{Sacha}, who is waiting in his
makeshift cabin with fresh stories for the next edition.

\subsubsection{\Gls{deWorde} receives a friendly warning from the Patrician}
\Gls{deWorde} is summoned by the Patrician, and told that the Engravers' Guild will likely want to
interfere with his press sometime soon. Meanwhile, \Gls{Dibbl} hastily offers \Gls{Pin} and
\Gls{Tulip} some sausages for free, when he realizes that they are hired thugs who will not hesitate
to kill.

\subsubsection{\Gls{deWorde} faints when trying to stop an attempted suicide stunt}
\Gls{deWorde} tries to climb a tall building and stop a man from jumping off. He then learns that
the man pulls off the stunt regularly, hoping to earn some tobacco money in exchange for climbing
off the roof and ending the traffic jam caused by the spectators. \Gls{deWorde} faints when he
realizes how far from the ground he is, and is woken up later by \Gls{Nobby}.

\subsubsection{\Gls{Pin} and \Gls{Tulip} purchase a pocket organizer powered by an imp}
\Gls{Pin} and \Gls{Tulip} proceed to the new avenue of magical shops opened in the erstwhile
garbage dump behind Unseen University, to purchase a pocket organizer. The shopkeeper reminds
\Gls{Pin} that the imp inside the device can remember anything it hears, and is incapable of making
up lies of its own. He decides to use the imp as a voice recorder at the next meeting with the
conspirators, in order to have an insurance policy against backstabbing.

\subsubsection{\Gls{deWorde} takes on \Gls{Rocky} as a bodyguard at the press}
At his office, \Gls{deWorde} hires \Gls{Rocky} the troll in a hurry, when some heroes drop by to
demand he print a correction in the bar brawl that was reported on. He then sees a zombie willing
to contribute obituaries for a fee, and approves \Gls{Sacha}'s design for a newspaper header.

\subsubsection{\Gls{Pin} and \Gls{Tulip} try to coax \Gls{Charlie} into proceeding with the plot}
\Gls{Pin} and \Gls{Tulip} promise \Gls{Charlie} a bigger payment when he starts to wriggle out of
the impersonation job, citing his inability to look haughty and speak imperiously. Meanwhile,
\Gls{Vetina} reads the next edition of the newspaper, and pulls out his tray of knives upon hearing
an unexpected knock at his office door.

\subsubsection{\Gls{deWorde} hires \Gls{OttoC} as a press photographer}
\Gls{deWorde} tries not to choke on his breakfast when his flatmates \Gls{Windli} and \Gls{Mackle}
discuss the stories in the day's paper seriously. \Gls{Gunil} tells him later that the Engravers'
Guild is looking to set up its own competing newspaper, and suggests the inclusion of foreign
affairs. \Gls{OttoC} shows up in response to the advertisement for a photographer, and reassures
them that he is a reformed vampire, who has sworn off human blood.

\subsubsection{\Gls{deWorde} learns of the boycott by the Engravers' Guild}
\Gls{Wintler} arrives with another one of his novelty vegetables, giving \Gls{OttoC} his first job
as photographer. \Gls{Sacha} informs him of the stonewalling by the Engravers' Guild, and he goes
to \Gls{OttoC}'s dark-room to ask if he can think of a solution. \Gls{OttoC} believes that he can
make the iconograph imps etch the images directly onto a plate using acid, and shows off his
prototype mechanism to \Gls{deWorde}.

\subsubsection{\Gls{deWorde} and his crew go to the palace to report on the alleged murder}
\Gls{OttoC} is alarmed to see a ghostly apparition in the picture painted by the imp, when he used
his new dark light eels. He hastily puts the picture in his pocket, and proceeds to the palace,
as rumours of a murder start to spread. At the palace gates, \Gls{deWorde} threatens \Gls{Detri}
with unfavourable coverage in the paper as a way to get into the palace, and meets \Gls{Vimes} in
the Great Hall.

\subsubsection{\Gls{Vimes} relays the latest news to \Gls{deWorde} at the palace}
\Gls{Vimes} tells \Gls{deWorde} that some servants reported a ruckus in the morning, with
\Gls{Vetina} declaring that he has stabbed \Gls{Drumk}. He was then found unconscious at the stable,
next to a bag of money. \Gls{Vimes} believes that this is highly unusual behaviour for the
Patrician, and asks \Gls{deWorde} to be fair in his reporting. \Gls{OttoC} dissolves into dust form
the intensity of his camera's flash, and \Gls{deWorde} is forced to take the ashes to the kitchen
to be reconstituted.

\subsubsection{\Gls{deWorde} and \Gls{OttoC} take a picture of the crime scene in dark light}
\Gls{deWorde} and \Gls{OttoC} take a photo of \Gls{Nobby} and convince him to let them into the
Patrician's office, where they find \Gls{CheeryL} taking forensic samples. She sees through thier
facade immediately, and angrily asks them to leave when \Gls{OttoC} uses one of his dark eels to
take a picture of the crime scene. Back at the press, \Gls{deWorde} decides to dictate an emergency
edition of the Times to \Gls{Gunil}, given how intriguing the affair at the palace had been.

\subsubsection{\Gls{Slant} tries and fails to threaten \Gls{deWorde}'s operation}
\Gls{Slant} arrives with some troll thugs and \Gls{Carney}, a representative of the Engravers'
Guild, to extort an impossible sum from \Gls{Gunil}. \Gls{deWorde} stops the fighting by threatening
to quote \Gls{Slant} on the fact that the absence of the Patrician's signature on their warrant is
a minor issue, and gets him to leave the premises. He realizes the trouble that might follow, and
decides to talk to \Gls{Vimes} at the Watch Headquarters.

\subsubsection{\Gls{deWorde} tells \Gls{Vimes} about his own analysis of the crime scene}
\Gls{deWorde} notices the gargoyles lining his route from the press to the Watch Headquarters, as
he strolls through the city. He points out several oddities about the crime scene, including the
peppermint meant to confuse any scent trackers, and \Gls{Wuff} having gone missing, in spite of
the maids hearing his loud barking just before the incident. He asks to talk to \Gls{Drumk}, who is
in the medical ward, and is escorted there by \Gls{Angua}.

\subsubsection{\Gls{deWorde} tries to interview \Gls{Drumk} about the attack}
\Gls{Drumk} refuses to talk to \Gls{deWorde} beyond the basic details of the event as he remembered
them. He then sees \Gls{Vetina} fast asleep in a nearby bed, as he is escorted out of the Watch
Headquarters. Afterward, \Gls{Angua} reports to \Gls{Vimes} about how keen \Gls{deWorde}'s eyes are,
and believes that his life is in great danger from the conspirators responsible for the attack on
\Gls{Drumk}.

\subsection{}
\subsubsection{\Gls{Pin} reflects on the botched operation to substitute \Gls{Vetina} with
    \Gls{Charlie}}
\Gls{Pin} and \Gls{Tulip} are accosted by a member of the Thieves' Guild, who does not see
\Gls{Tulip}'s fist coming. \Gls{Tulip} knocks him out, and takes what little money he finds in the
thief's pockets. \Gls{Pin} thinks about the sudden snag in their plans with \Gls{Wuff}, and how
he had been forced to fire his crossbow at the dog to discourage it from chasing them, as they
carried off the real \Gls{Vetina}.

\subsubsection{\Gls{deWorde} thinks about the competing newspaper}
\Gls{deWorde} notices the Engravers' Guild setting up their own newspaper opposite his own, and
learns that their paper dealer is raising prices, with the competition buying up all of the
supply. Meanwhile, \Gls{Slant} chastises \Gls{Pin} for letting \Gls{Wuff} get away, and agrees to
a bonus fee for tracking down and eliminating it. He tells them that the werewolf in the City
Watch might learn something about the kidnapping by talking to \Gls{Wuff}, and that loose ends would
not be tolerated by his clients.

\subsubsection{\Gls{HarryK} decides to help \Gls{deWorde} deal with the Engravers}
\Gls{HarryK} welcomes \Gls{deWorde} and \Gls{Gunil} at his garbage sorting yard, and tells them that
he cannot breach the contract with the Engravers. He points out a cart laden with paper that is
conveniently left unwatched for the moment, and tells \Gls{Gunil} that he expects payment by the
end of the week at the old rates. \Gls{deWorde} is blissfully unaware of the subtext, and is dragged
by \Gls{Gunil} who takes the hint.

\subsubsection{\Gls{HarryK} muses on the idea of his daughter's wedding being on the centerfold}
\Gls{HarryK} has the current edition of the Times read out to him, and realizes that coverage of his
daughter's coming wedding, with color photographs included, would be a great boost to his social
standing in the city. Meanwhile, \Gls{Sacha} goes to \Gls{OttoC}'s cellar when she hears him
cursing, and looks at something on his work-table that he tries desperately to hide.

\subsubsection{\Gls{Sacha} learns about the possible nature of dark light photography}
\Gls{Sacha} learns that dark light is able to take pictures of the past or future, and sometimes
even reveal a mental image that might be weighing on the subject. He shows her the picture of
\Gls{CheeryL} in the Patrician's office, and points out the two figures standing next to each other,
both looking like \Gls{Vetina}. He also shows her a picture of \Gls{deWorde}, with his father
looking over his shoulder.

\subsubsection{\Gls{deWorde} listens to his flatmates discussing the day's news}
\Gls{deWorde} walks \Gls{Sacha} back home after finishing up the latest edition of the Times, and
returns to his hostel in time for dinner. He hears from one of his flatmates that the gemstone
business is seeing a lot of movement of late, while another talks about \Gls{Vetina}'s valuable
contribution to the city's commerce.

\subsubsection{\Gls{Pin} and \Gls{Tulip} fail to track down \Gls{Wuff} using a werewolf}
\Gls{Pin} and \Gls{Tulip} are chased out of the Biers, when they try to recruit one of the
werewolves to track down \Gls{Wuff}. On their way out, \Gls{Pin} buys a newspaper from \Gls{FORon},
and is intrigued to see bounty on the whereabouts of \Gls{Wuff}. Meanwhile, \Gls{Slant} meets with
the conspirators, and reminds them that \Gls{Angua} will punish any werewolf in the city who
co-operates with \Gls{Pin}, and tells them that the likely replacement for \Gls{Vetina} is
\Gls{Scrope}.

\subsubsection{\Gls{Pin} and \Gls{Tulip} steal some silverware from a temple}
\Gls{Pin} and \Gls{Tulip} are forced to knock out a priest, when he walks in on them stealing some
silverware from one of the city's temples. \Gls{Tulip} marvels at the craftsmanship of the
silverware, and is dismayed by the idea that any fence would immediately melt it down for the
silver.

\subsubsection{\Gls{deWorde} prints his theories about \Gls{Vetina} being attacked in his palace}
\Gls{deWorde} rushes to the press in the middle of the night, and wakes the dwarves up to set an
emergency edition of the paper. He works out the fact that the horse laden with the bag of coins was
meant to be a distraction, and that some third party was likely involved in the attack on
\Gls{Vetina}. He finds out at his hostel, that refutations of lies are simply interpreted as a
cover-up, leading more weight to the original false claim.

\subsubsection{\Gls{deWorde} talks to \Gls{DeepB} at the stables}
At the Ankh-Morpork stables, \Gls{deWorde} is accosted by a mysterious voice in the dark, who tells
him that it has a lead on \Gls{Wuff}, and is willing to offer the dog up in exchange for a sizable
bounty. \Gls{deWorde} is skeptical about the voice, until it reminds him to ask \Gls{Vimes} about
previous attempts on \Gls{Vetina}'s life, and mysteriously vanishes after calling itself
\Gls{DeepB}.

\subsubsection{\Gls{deWorde} and the press try to deal with the response to their bounty}
Back at the press, \Gls{deWorde} and \Gls{Gunil} are overwhelmed to see the hundreds of dogs being
presented in response to the bounty. \Gls{Pin} and \Gls{Tulip} arrive dressed as priests, and make
a show of helping \Gls{deWorde} find the specific dog he is looking for. When \Gls{deWorde} hears
\Gls{Pin} mention the correct colour of \Gls{Wuff}' coat, he realizes they are impostors, and
probably agents of the conspirators.

\subsubsection{\Gls{Pin} and \Gls{Tulip} try to sort through the dogs at the press in search of
    \Gls{Wuff}}
\Gls{Pin} threatens \Gls{deWorde} with violence if he lets slip the truth about their disguise, and
fails to notice \Gls{Gunil} communicating with him through the metallic typesetting letters.
\Gls{Gunil} then goes to the cellar to get \Gls{OttoC}, who makes all of his dark eels release their
stored dark light at once. In the resulting chaos, \Gls{Pin} and \Gls{Tulip} are forced to run away
when they see Watchmen approaching the press.

\subsubsection{\Gls{OttoC} provides a distraction for the Watchmen to approach the press}
\Gls{OttoC} is decapitated by \Gls{Tulip}, but simply asks for his head to be laid next to his body
for his accelerated healing to kick in. Once he is fully healed, \Gls{Gunil} stars to berate him for
experimenting with dark light, and refuses to listen to his superstitious beliefs. Meanwhile,
\Gls{Vimes} walks into the office, asking to talk to \Gls{deWorde}.

\subsubsection{\Gls{deWorde} receives affirmation from \Gls{Vimes} regarding the accuracy of his
    source}
\Gls{deWorde} learns that \Gls{Vetina} was seen sneaking into the palace the morning of the attack,
and believes that \Gls{Wuff} would have noticed such unusual behaviour. \Gls{Vimes} works out that
\Gls{deWorde} has some confidential source of information, and asks him indirectly to try and
wrangle something useful from the source.

\subsubsection{\Gls{Pin} and \Gls{Tulip} ditch the sack of dogs in order to outrun the Watch}
\Gls{Sacha} tries to cheer up \Gls{OttoC}, as \Gls{deWorde} takes a look at the dark light
iconograph, to his horror. Meanwhile, \Gls{Pin} and \Gls{Tulip} are annoyed by the persistence of
the City Watch on their tail, and think back to the horrible feeling of the black light washing
over them at the press. They decide to ditch the sacks of puppies over a bridge, and are intrigued
by the absence of any splash.

\subsubsection{\Gls{deWorde} asks \Gls{OttoC} to stop using the dark light eels}
\Gls{Gunil} and the rest of the dwarves are alarmed by the dark light photograph, and the shadows
seemingly alive in the background. \Gls{deWorde} agrees with them, and asks \Gls{OttoC} to stop
using the dark light eels for his photos, even if it means suffering the effects of the sunlight
flash.

\subsection{}
\subsubsection{\Gls{Sacha} explains the financial needs of the newspaper to \Gls{deWorde}}
\Gls{Sacha} berates \Gls{deWorde} for obsessing over the \Gls{Vetina} affair, instead of looking for
avenues like advertising and paid stories to keep the paper profitable. He tries to argue about the
principle of putting the truth in front of people, and is outvoted by the dwarves, who are ready to
print their first color edition. \Gls{deWorde} recognizes the need to consult \Gls{DeepB} again,
and heads off to the stables.

\subsubsection{\Gls{Pin} and \Gls{Tulip} think about their next move after escaping the press}
\Gls{Pin} tries to deal with the horror of the spirits of his former enemies haunting him, as a
result of the dark light photo. He decides to sneak into the press at night, to steal the photo,
and possibly get rid of the vampire. \Gls{Tulip} reminds him that \Gls{Slant} would still be a loose
end, and suggests dealing with the lawyer first.

\subsubsection{\Gls{deWorde} goes to a second meeting with \Gls{DeepB}}
\Gls{FORon} and the beggars rescue the dogs from the river Ankh, and wait for \Gls{Gaspode} to come
deal with them. Meanwhile, \Gls{deWorde} goes to an apothecary to buy a sealed package containing
a scent bomb for the werewolf in the City Watch. He makes a run for the stables with the chequebook
from his apartment, and uses the scented oil to confuse the werewolf when it tries to track him.

\subsubsection{\Gls{DeepB} meets with \Gls{deWorde} once again}
\Gls{DeepB} asks \Gls{deWorde} if he is being followed, and is alarmed when he mentions the scent
bomb he used to distract the werewolf. \Gls{deWorde} then gives the informant a cheque for half of
the promised bounty, and is relieved when \Gls{DeepB} asks him to meet again at midnight. Once
\Gls{deWorde} leaves, \Gls{DeepB} makes a run for it, wondering how angry \Gls{Vimes} would be at
the harm done to \Gls{Angua}.

\subsubsection{\Gls{Boddony} and \Gls{Sacha} break into the Enquirer's basement}
\Gls{Boddony} asks \Gls{Gunil} about the tunnel network underneath the press, and decides to
go take a look at the Enquirer's basement. \Gls{Sacha} follows him out of curiosity, leaving
\Gls{Gunil} to finalize the color printing mechanism for their newest edition. Once they hack
through the weakened planks blocking the tunnel entrances, they reach the basement of the Enquirer,
and find \Gls{Dibbl} busy at work.

\subsubsection{\Gls{Sacha} and \Gls{Gunil} employ \Gls{Dibbl} as a salesman}
\Gls{Gaspode} warns the beggars that a large bounty is up for grabs, and asks them to come up with
a convincing disguise that will throw off \Gls{Pin} and \Gls{Tulip}. Meanwhile, \Gls{deWorde}
returns to the press to find \Gls{Dibbl} being cornered by the dwarves, and accused of writing the
made-up stories in the Enquirer. \Gls{Sacha} asks him if he can sell advertising space in the Times
instead, and offers him a commission for every sale.

\subsubsection{\Gls{Vimes} realizes that \Gls{deWorde} wants to be left alone}
\Gls{deWorde} gives \Gls{Sacha} the key to his family's storeroom in the city, and asks her to pick
out a dress for \Gls{LSelach}'s coming ball. Meanwhile, \Gls{Vimes} asks \Gls{Angua} and
\Gls{Carrot} to call off the Watchmen keeping track of \Gls{deWorde}, and decides to let him fend
for himself. He asks \Gls{Carrot} for updates on \Gls{Scrope}'s election, and is alarmed by his
proposed policies.

\subsubsection{\Gls{deWorde} interviews \Gls{Wuff}, using \Gls{DeepB} as a translator}
\Gls{deWorde} meets \Gls{DeepB} at night, and is led to the beggars' hangout next to an abandoned
garbage dump. He sees \Gls{FORon} reveal \Gls{Wuff} hidden inside his coat, and asks \Gls{Wuff} if
he can translate for the dog. He realizes the absurdity of interviewing a dog, and asks about the
day of the attack. \Gls{Wuff} talks about seeing two masters, and noticing one of them had the
wrong scent. He also mentions two other intruders in the Patrician's office, before biting
\Gls{deWorde} on the ankle.

\subsubsection{\Gls{Pin} and \Gls{Tulip} decide to give up on the contract and leave with their
    bounty}
\Gls{Pin} and \Gls{Tulip} go to \Gls{Slant}'s office, and successfully blackmail him using his
voice recorded by the organizer imp. They knock out the security that he summons, and get away with
their promised payout in precious gems. Once the two of them leave, \Gls{Slant} hurriedly writes a
sealed message for \Gls{LWorde}, and asks a servant to deliver it to him.

\subsubsection{\Gls{deWorde} asks \Gls{FORon} and \Gls{Wuff} to come to the press office}
\Gls{deWorde} is satisfied with the interview, and asks \Gls{FORon} to pose for a photo with
\Gls{Wuff}. When \Gls{DuckM} rejects the idea of having their secret hideout photographed,
\Gls{deWorde} offers them more cash to come to the press instead. Meanwhile, \Gls{Tulip} is alarmed
by the change in \Gls{Pin}'s demeanour, as he struggles with questions of death and rebirth.

\subsubsection{\Gls{Sacha} and \Gls{Rocky} run into \Gls{Charlie} in \Gls{deWorde}'s warehouse}
\Gls{Pin} becomes paranoid about the people he has wronged coming back to haunt him, and possibly
denying his spirit an afterlife. He asks \Gls{Tulip} about his own beliefs regarding rebirth, and
seems to believe that someone is watching him from the shadows. Meanwhile, \Gls{Sacha} and
\Gls{Rocky} go to \Gls{deWorde}'s warehouse, and find some footsteps in the dusty hallways.
\Gls{Sacha} hears someone drunkenly singing in one of the side rooms, as she picks out one of the
dresses for the ball.

\subsubsection{\Gls{Pin} and \Gls{Tulip} decide to avenge \Gls{OttoC}'s insult}
\Gls{Tulip} and \Gls{Pin} return to the warehouse, just as \Gls{Sacha} finds \Gls{Charlie} chained
up in the wine cellar. \Gls{Tulip} knocks out \Gls{Rocky}, as \Gls{Pin} aims his crossbow at her,
intent on taking her hostage till they left the city. A while later, \Gls{deWorde} returns to the
press with \Gls{Wuff} and the beggars, noticing too late that \Gls{Pin} and \Gls{Tulip} have taken
it over.

\subsubsection{\Gls{deWorde} orders his staff to evacuate the burning press building}
\Gls{deWorde} orders the dwarves to evacuate when \Gls{Wuff} launches itself at \Gls{Pin}'s face,
causing his crossbow to fire at a flammable oil lamp. \Gls{Gunil} is dismayed to leave his precious
press behind, and orders \Gls{Boddony} to take some dwarves to block the back entrance. \Gls{Pin}
and \Gls{Tulip} take refuge in the stone cellar, as \Gls{Wuff} runs out with its coat in flames,
just in time for the entire warehouse to go up in flames.

\subsection{}
\subsubsection{\Gls{Pin} kills \Gls{Tulip} out of fear for his own life}
\Gls{Pin} shoots \Gls{Tulip} dead when the molten lead starts to pour into the cellar through the
floor, and is seemingly overcome by guilt for his past crimes. \Gls{Death} arrives to reap
\Gls{Tulip}'s soul, and shows him the lives he cruelly cut short. A while later, the Golem fire
department comes in to put out the fire, with the rain taking care of the last smoldering bits.

\subsubsection{\Gls{Pin} is killed when he tries to choke \Gls{deWorde}}
\Gls{Sacha} and \Gls{deWorde} are lost in thought about expanding their operation with magazines
aimed at dwarves and fashionable women, as \Gls{Gunil} surveys the full extent of the damage. He
laments the loss of his equipment, as \Gls{Boddony} points out the molten lead cooling in puddles
on the floor. \Gls{Pin} emerges from the wreckage and tries to choke \Gls{deWorde}, but is stabbed
by the receipt spike when he brings it up defensively.

\subsubsection{\Gls{deWorde} realizes the story in \Gls{Pin}'s organizer imp}
\Gls{deWorde} finds the organizer imp inside \Gls{Pin}'s jacket, as well as the jewels, which
\Gls{Gunil} starts appraising using a magnifying glass. \Gls{Boddony} reports the presence of a body
encased in molten lead in the cellar, just as \Gls{OttoC} returns with a fresh batch of etching
acids. \Gls{deWorde} checks \Gls{Pin}'s ankle for bite marks, as the story of their attack on
\Gls{Vetina} starts to take shape in his mind.

\subsubsection{\Gls{deWorde} starts to make sense of the conspiracy against \Gls{Vetina}}
When \Gls{deWorde} plays back the imp's recordings, he recognizes an adage used by his father, and
places him as one of the conspirators who employed \Gls{Slant}. He asks \Gls{Gunil} to trade the
jewels for some new printing equipment, and makes plans for a special edition of his paper.
\Gls{Sacha} suggests stealing the press machines in the Enquirer's warehouse next door, and asks
the dwarves to get to work hauling the equipment out.

\subsubsection{\Gls{Carney} is persuaded to allow \Gls{deWorde} the use of his equipment}
\Gls{Carney} is gleeful when he sees \Gls{Sacha} and \Gls{deWorde} come to his office, having
just seen his primary competition lose their entire operation to a massive fire. She threatens
\Gls{Carney} with the crossbow, as \Gls{deWorde} politely asks to borrow one of his press machines
for the night. Meanwhile, \Gls{Gunil} pays off \Gls{Carney}'s staff and security for abandonging
their posts and going home early for the night.

\subsubsection{\Gls{deWorde} is angry at his father's audacity}
\Gls{deWorde} throws a bag of jewels onto \Gls{Carney}'s table, in lieu of their Guild fee, as
\Gls{Sacha} pulls the trigger. \Gls{Carney} faints, even as \Gls{Sacha} realizes the crossbow is
not loaded. \Gls{deWorde} decides to confront his father, believing him to be the leader of the
conspiracy, as \Gls{Gaspode} asks \Gls{Sacha} about the bounty.

\subsubsection{\Gls{deWorde} confronts his father at his mansion}
\Gls{deWorde} struggles with the idea of turning over the material evidence to the Watch, and
letting \Gls{Vimes} deal with \Gls{LWorde}. He decides against it, and walks through the hailstorm
to his father's mansion. Once inside, he asks confirms his father's involvement in the plot, and
is surprised when \Gls{LWorde} asks him to consider exile, in lieu of a swift death.

\subsubsection{\Gls{OttoC} helps \Gls{deWorde} deal with his father's henchmen}
\Gls{OttoC} arrives in his bat form, to knock out the thugs summoned by \Gls{LWorde} to restrain
his son. \Gls{LWorde} realizes that he is cornered, and accepts \Gls{deWorde}'s offer of being
left out of the report in the newspaper. He banishes himself from the city, out of shame at being
branded a traitor to the realm. \Gls{deWorde} then removes the sword sticking out of \Gls{OttoC}'s
chest, and starts to worry about facing \Gls{Vimes}.

\subsubsection{\Gls{Vimes} is forced to let \Gls{deWorde} go free under \Gls{Slant}'s counsel}
\Gls{Vimes} is alarmed to see \Gls{Slant} show up with a bail order for \Gls{deWorde}, who is
accused of hiding crucial information from the City Watch. Once outside, \Gls{deWorde} asks
\Gls{Slant} to help him with the Engravers' Guild and with delaying the appointment of \Gls{Scrope},
in exchange for his own involvement in the affair to be erased from public memory.

\subsubsection{\Gls{deWorde} gets an official statement from the City Council regarding
    \Gls{Vetina}}
At the Palace, \Gls{deWorde} addresses the council of Guild Leaders, asking them if they formally
acquit \Gls{Vetina} of all charges. \Gls{Slant} advices \Gls{Downey} to play along, as \Gls{deWorde}
decides to give credit to \Gls{Vimes} and his Watch for tracking down the conspirators, in the hopes
that this might build goodwill in the long run.

\subsubsection{\Gls{Vetina} congratulates \Gls{deWorde} at the press office}
\Gls{Vetina} arrives at the press, just as \Gls{deWorde} is recruiting more writers for his
special columns, and reassures him that \Gls{Charlie} is hard at work at the Actors' Guild, making a
career out of his appearance. \Gls{deWorde} asks \Gls{Vetina} to grace the wedding of \Gls{HarryK}'s
daughter with his presence, and is happy to learn that he will be fulfilling one of his
long-standing debts with the garbage czar.

\subsubsection{\Gls{deWorde} and \Gls{Sacha} are forced to end their break to write a new story}
Once \Gls{Vetina} leaves, \Gls{deWorde} drags \Gls{Sacha} out for a well-deserved break from work,
and witnesses \Gls{Carrot} saving an old woman from a wayward horse dragging a wagon full of beer.
They get back to the press to write down the latest story, and wonder how they will keep the machine
fed day after day.

