\section{The Shepherd's Crown}


\subsection{}
\subsubsection{\Gls{RobA} meets \Gls{Tiff} at the stone monument next to her village}
\Gls{Tiff} receives a subconscious summons to the stone monument at one end of her village, and is
curious to see \Gls{RobA} there already. He tells her that \Gls{Jeannie} has divined some trouble
emerging from the fairy land, and sent him to keep an eye on the monument, which acts as a
protective barrier between worlds. The two of them go to the Feegle colony, where \Gls{Jeannie}
shows off her latest attempt to spread literacy among the younger Feegles in her brood.

\subsubsection{\Gls{Swiv} thinks about the future of his third and youngest son}
\Gls{Jeannie} tells her that overexerting herself in service of the village would lead to a lonely
future just like \Gls{GWea}, and asks her to take \Gls{Preston} more seriously. \Gls{Swiv}, a
young nobleman in the plains, takes stock of the youngest of his three sons \Gls{GeSw}, having
cheated his way to a life of great wealth and luxury.

\subsubsection{\Gls{GeorgeP} grows up with a thirst for knowledge in his father's mansion}
\Gls{Swiv} grows tired of his son's increasing demand for books, and dismisses his tutor \Gls{Wigg}
after a few years of instruction. \Gls{Swiv}'s wife continues to stress the importance of
education, and encourages \Gls{GeSw} to keep reading. A few years later, \Gls{GeSw} goes out with
the senior stable hand \Gls{McTav} to hunt some foxes who threaten the chickens being raised in
the estate.

\subsubsection{\Gls{GeSw} exiles himself from the estate of \Gls{Swiv}, disgusted by their
    recreational hunting}
\Gls{GeSw} expresses disgust for his father's ritualized fox culling that takes place every year,
and wonders if there must be some humane way to deal with the threat. \Gls{GeSw} gets whipped by
his father for raising objections to the hunt, and decides to set off from the estate with his
pet goat \Gls{Mephi}, and a small loan of gold from \Gls{McTav}, who owes his mother a favour.

\subsubsection{\Gls{GWea}'s death makes the Disc much easier for the elves to invade}
\Gls{GWea} attends to an injured lumberjack in the mountains before returning to her hut, where she
deals with the regular customers and has a small nap. She cleans out her hut, and lies down in
her cottage to prepare for death. \Gls{Death} reaps her soul, and congratulates her on a life
well lived. The death sends magical shockwaves throughout the Disc, as well as the fairy realm,
where elven lord \Gls{Pease} realizes how weak the protective barrier around the Disc has now
become.

\subsubsection{\Gls{Tiff} delivers a set of triplets, one of which is a girl}
\Gls{Tiff} helps \Gls{Milly} deliver twins, and notices after that there is a third baby left to
pull out. She spots \Gls{You} staring at her from the door, and wonders why it is not with
\Gls{GWea} in Lancre. \Gls{Tiff} takes note of how little interest the mother shows in the baby
girl, and decides to visit the home regularly to see if the girl is being raised with as much care
as the boys.

\subsubsection{\Gls{Tiff} and \Gls{Ogg} prepare \Gls{GWea}'s corpse for a quiet burial}
\Gls{Tiff} arrives at \Gls{GWea}'s cottage, and is shown a card by \Gls{Ogg} which names her as
the heir to the steading. \Gls{Tiff} is alarmed by the idea of managing to steadings on her own,
and helps \Gls{Ogg} prepare the corpse for a quiet burial, before anyone else shows up expecting
a funeral. \Gls{Drumk} talks to \Gls{Vetina} about the succession crisis among the witches, and
points out how inconvenient \Gls{Earwig} might turn out to be if she is chosen as the leader.

\subsubsection{\Gls{Ridcu} pays his respects to \Gls{GWea} before any of the witches arrive}
\Gls{Ogg} and \Gls{Tiff} take the corpse of \Gls{GWea} to a spot in the forest and bury her next to
a tree that she had marked previously. \Gls{Tiff} recalls the death of \Gls{GAch}, and of how her
hut had become a shrine for the shepherds afterward. \Gls{Ridcu} shows up well ahead of any other
mourners, and asks \Gls{Ogg} for some private time with the burial mound of \Gls{GWea}. Once he
leaves, other witches start to converge on \Gls{GWea}'s cottage, ostensibly to bicker over her
successor.

\subsubsection{\Gls{Tiff} is crowned the chief witch at \Gls{GWea}'s wake}
\Gls{Tiff} watches \Gls{You} approach her, and the bees from \Gls{GWea}'s hives fly over her head,
as \Gls{Ogg} argues in favour of appointing her as the successor. \Gls{Earwig} is forced to abandon
her own ambitions, and accept \Gls{Tiff} as the unofficial leader of the witches. Meanwhile,
the \Gls{QueenF} thinks about the potential coup building in her palace, and wonders where Lord
\Gls{Pease} has gone off to.

\subsubsection{\Gls{QueenF} talks to \Gls{Swarf} about the technological advancements in the
    Disc}
The \Gls{QueenF} talks to a goblin kidnapped from the Disc, and learns that they have received
status as fully sentient beings, with the right to live freely. The goblin calls himself \Gls{Swarf}
and talks about his contribution to the growing steel industry centered in Ankh-Morpork, along with
the spreading locomotive lines connecting the Disc. \Gls{Swarf} asks her to ride out into the Disc,
and check on \Gls{GWea}'s funeral, while talking about how goblins were integrating too well into
human society.

\subsubsection{\Gls{Tiff} tries her best to service both her village and \Gls{GWea}'s former
    steading}
\Gls{Tiff} sets out some food for \Gls{You} and goes back to her village. She chides \Gls{Milly} for
the unfair treatment to her daughter, and talks to \Gls{Jeannie} about filling \Gls{GWea}'s shoes.
\Gls{Tiff} struggles to manage her two steadings, and finds \Gls{Went} talking about railway jobs
one night at dinner. Her father reminds him of his duties as the inheritor of the farm, as her
mother tries to indirectly point out how \Gls{Tiff} herself had not yet had any children of her
own.

\subsubsection{\Gls{Tick} listens to \Gls{Tiff}'s request for an apprentice}
\Gls{GeSw} shows off some tricks he taught \Gls{Mephi} at a tavern, and surprises the landlord by
stopping a barfight between two of the regulars. The landlord \Gls{Dove} offers to let him stay for
a few days, as \Gls{GeSw} contemplates how best to travel to Lancre. Meanwhile, \Gls{Tiff} feels
overwhelmed by the strain of her job, and works up the courage to ask \Gls{Tick} for help in finding
an apprentice who can pick up the slack in her village, freeing her up to concentrate on Lancre.

\subsubsection{\Gls{Tiff} fends off \Gls{Earwig}'s attempts to make peace with her}
\Gls{Tiff} watches \Gls{Earwig} arrive at \Gls{GWea}'s cottage one morning, and dreads the prospect
of listening to her friendly advice. \Gls{Earwig} insists that she is stretched too thin, and makes
an obtuse comment about \Gls{Ogg} being an unsuitable mentor. \Gls{Tiff} manages to keep her
composure as she rejects \Gls{Earwig}'s assistance, and asks her to leave. She then notices the
Feegles spying on her, and puts them to work doing the laundry of the infirm townsfolk.

\subsubsection{\Gls{Swarf} escapes his bindings as the \Gls{QueenF} observes the train arriving
    at Twoshirts}
The \Gls{QueenF} emerges onto the Disc in the forest next to Twoshirts, and notices the rail track
glinting in the moonlight. The approaching locomotive fills the elves with dread, and the
\Gls{QueenF} immediately starts to wonder how they might use the train for their own ends.
\Gls{Pease}, seemingly unafraid of the huge iron monster, threatens to kill \Gls{Swarf}, who throws
some iron filings to subdue the elves and make his escape.

\subsubsection{\Gls{Tiff} faces disgruntled comments from the peasants in her village}
\Gls{Tiff}'s father receives comments from his friends at the village pub that her service to the
village is important, and that it would be a shame if she relocated to Lancre permanently.
\Gls{Roland} visits \Gls{Tiff} one evening, and tries to warn her about the stretching herself too
thin trying to serve both her steadings. Meanwhile, the \Gls{QueenF} escapes back to the fairy
realm with her raiding party, and tries to downplay the shame of being outwitted by a goblin.

\subsubsection{\Gls{Pease} takes over the elves, after calling out the \Gls{QueenF}'s weaknesses}
\Gls{Pease} sets his coup into motion, and challenges the \Gls{QueenF}'s hold over her warriors. He
tells the gathered nobility that human advancement has almost made them irrelevant, and blames the
\Gls{QueenF} for letting the Feegles exist freely on the Disc. He orders the \Gls{QueenF} to be
deposed, and imprisoned pending their successful conquest of the Disc.

\subsubsection{\Gls{Tiff} decides to help \Gls{GeSw} learn witchcraft}
\Gls{Tiff} receives \Gls{GeSw} in her cottage, and is intrigued by his desire to train as a witch.
She notices how \Gls{Mephi} seems to be unafraid of \Gls{You}, and realizes that \Gls{GeSw} is not
going to reveal any details about his family or childhood. She realizes that her new position as
chief witch puts her in a position to reform the guild, and decides to help the boy learn the
craft.

\subsubsection{\Gls{Ogg} is amazed by \Gls{Mephi}'s tricks}
\Gls{Ogg} arrives at \Gls{Tiff}'s cottage, and is surprised to see \Gls{GeSw} express interest in
becoming a witch. She suggests sending him on elder-care duty for a while, just so he can see the
drudgery and monotony that makes up most of a witch's duties.

\subsection{}
\subsubsection{\Gls{Pease} cleanses the elven nobility of all dissidents}
\Gls{Pease} stabs one of the elven nobles who points out the \Gls{KingEl} still being their
de-facto ruler, and prepares to unleash a full-scale invasion of the Disc. Meanwhile, \Gls{Tick}
asks two young girls to make magic detectors, and decides to send them to \Gls{Tiff} as trainees
once she is convinced of their innate talent.

\subsubsection{\Gls{GeSw} decides to help the semi-retired men in Lancre deal with their boredom}
\Gls{GeSw} notices how little the retired men control their own lives at home, and decides to
confront them one evening at the local tavern. \Gls{SMake} reminds him that the wives have almost
full control over their lives once they stop being the breadwinners of the family. \Gls{GeSw}
proposes the innovative idea of building private attached to their houses, where they can pursue
their hobbies out of sight of their wives.

\subsubsection{\Gls{Tiff} hears news of \Gls{Mephi}'s feats from the townsfolk}
\Gls{Tiff} hears more tales of \Gls{GeSw} putting \Gls{Mephi} to work herding sheep, and is so
impressed with his talents, that she decides to take the boy along to see \Gls{Jeannie}. She is
surprised to learn that \Gls{RobA} and the Feegles have already met him, as he slept in the shed
outside her cottage every night.

\subsubsection{\Gls{Tiff} makes a plan to fly to Ankh-Morpork with \Gls{GeSw}}
\Gls{Tiff} is glad to hear \Gls{Jeannie} recognize the conflict-resolution skills that \Gls{GeSw}
seems to possess, even as she chides her eldest daughter \Gls{Maggie} for wanting to live the life
of a warrior. \Gls{Tiff} decides to travel to the city with \Gls{GeSw} to buy him a broomstick, and
hopes to meet up with \Gls{Preston} at the city hospital.

\subsubsection{\Gls{Tiff} gets \Gls{Shru} to repair \Gls{GWea}'s old broomstick}
At the newly relocated broomstick store, \Gls{Shru} the dwarf welcomes \Gls{Tiff}, and asks her if
any Feegles have come with her. She says no, and hopes that \Gls{RobA} took her request to be left
alone for the day seriously. \Gls{Tiff} uses her pain removal spell to take away the dwarf's back
pain as payment for repairing \Gls{GWea}'s old broom, and asks if there is some stone nearby where
she can safely release the energy.

\subsubsection{\Gls{Tiff} visits \Gls{Preston} at the hospital}
\Gls{Tiff} next takes \Gls{GeSw} to \Gls{Proust}'s joke shop, and she gets her son to show him
around the city. \Gls{Tiff} then starts to ramble about her relationship with \Gls{Preston}, which
seems a non-starter given how busy the two of them are with their jobs. At the hospital,
\Gls{Preston} is happy to see \Gls{Tiff}, and tells her that \Gls{Lawn} is close to finishing up
his training and promoting him to the position of surgeon.

\subsubsection{\Gls{Tiff} cheers \Gls{GeSw} on as he gets to grips with his new broom}
\Gls{Tiff} is surprised to see \Gls{GeSw} pilot his new broomstick with ease, and laughs at him
when his trousers start smoking from all the high-altitude flying. Back at her village, she is woken
up one night by the magical aftershocks of the \Gls{QueenF} being dumped unceremoniously into the
Disc, after her wings are cut off to rid her of any power she might have left.

\subsubsection{\Gls{RobA} brings the unconscious body of the \Gls{QueenF} to his colony}
\Gls{Yan} runs into the Feegle colony with news of a solitary elf appearing next to the stone
monument, and \Gls{RobA} immediately has the body dragged to their mound for \Gls{Jeannie} to
inspect. He tells her that killing an unarmed elf is against Feegle honour, and sends \Gls{Hamish}
over to \Gls{Tiff}'s house to summon her.

\subsubsection{\Gls{Nightsha} reveals her real name to \Gls{Jeannie}, confirming her identity}
\Gls{Jeannie} brings the \Gls{QueenF} to the central hall in her colony, and asks her who she is.
Upon learning the \Gls{QueenF}'s identity, every single Feegle in the clan is surprised to see what
she has now become, in comparison to the tales told by \Gls{RobA} of her grandeur in the fairy
realm. \Gls{Jeannie} confirms the name of the \Gls{QueenF} as \Gls{Nightsha}, a secret that has
been passed on from one leader to the next within the Feegle clans.

\subsubsection{\Gls{Tiff} decides to keep a close eye on \Gls{Nightsha}}
\Gls{Tiff} arrives at the Feegle colony, and decides to take \Gls{Nightsha} along with her as a
captive. SHe tells the Feegles not to harm their prisoner as long as she remains docile, and
enlists \Gls{WMArthur} to stand watch over \Gls{Nightsha}. Meanwhile, \Gls{Parsley} deals with the
sudden spoilage of his beer barrels, and rumours start to spread about the return of the elves.

\subsubsection{\Gls{Tiff} helps \Gls{Nightsha} recover her strength}
The elves raid a lumberjack outpost high up in the mountains, with two trainees being the only
ones to escape the assault. By the time they reach the main camp on the foothills, the elves retreat
back into their realm, leaving death and destruction in their wake. \Gls{Tiff} takes \Gls{Nightsha}
to a spare barn next to her home, and rubs some ointment on her wounds. She notices \Gls{Nightsha}'s
power slowly recovering, and is shocked when the \Gls{QueenF} models her appearance on a village
milkmaid.

\subsubsection{\Gls{Nightsha} watches \Gls{Tiff} go about her day as the village witch}
\Gls{Nightsha} remains surprised that \Gls{Tiff} chose not to kill her when she was at her weakest.
\Gls{Tiff} is satisfied with the offer of helping \Gls{Nightsha} become the Queen of elves once
again, if she can keep them confined to their realm forever. \Gls{Nightsha} is intrigued by
\Gls{Tiff}'s altruistic service to the villagers, and thinks about how atomized elven society is
by comparison.

\subsubsection{\Gls{Magrat} offers her assistance to \Gls{Tiff} against the elves}
\Gls{Magrat} arrives at \Gls{Tiff}'s cottage in Lancre and offers her help in fighting off the
elven invasion. She is shocked to learn that \Gls{Tiff} is harbouring \Gls{Nightsha} in her barn,
and asks her why she is choosing to trust an elf, going against all precedent. \Gls{Magrat} tells
her that she will fly over to \Gls{Roland}'s castle, and convince \Gls{Letitia} to pitch in for the
defense against the elves, especially considering how powerful their mind-control was going to be.

\subsubsection{\Gls{Tiff} kills some elves when they try to kidnap a baby}
\Gls{Tiff} is alerted of a baby being kidnapped by some elves, and reflexively catches up to them
on her broomstick. She burns the elves to ashes using her magic, and returns the baby to her
parents. \Gls{Tiff} flies to Lancre, and tells \Gls{Ogg} about her impulsive use of violence, and
is intrigued by the idea of persuading the \Gls{KingEl} to reclaim his throne in the fairy realm.

\subsubsection{\Gls{Tiff} asks the \Gls{KingEl} to take responsibility for the elven invasion}
\Gls{Tiff} goes to the burial grounds that hold the secret entrance to the pocket dimension
inhabited by the \Gls{KingEl}. She asks \Gls{RobA} and the Feegles to guard the entrance and keep
away any other elven intruders, and proceeds underground on her own. Once she steps into his abode,
the \Gls{KingEl} seems to show no interest in the deaths of other elves, and reminds her of his
grand plan to wait for the inevitable apocalypse that will send humans back to the stone-age.

\subsubsection{\Gls{Pease} tries to convince his fellow elves to buy into his grand vision}
\Gls{Tiff} returns once she realizes that the \Gls{KingEl} is unwilling to stop the invasion, and
wonders if she can offer him some sort of gift that might change his mind. She asks \Gls{RobA} to
build a hobby shed for the \Gls{KingEl}, following the example of \Gls{GeSw}, and hopes that it
might help piece through his apathy. Meanwhile, \Gls{Pease} tires of the pointless mischief that
his fellow elves have been causing on the Disc, and rallies them for a fight against the humans.

\subsubsection{\Gls{Tiff} shows \Gls{Nightsha} the value of co-operation and coexistence}
\Gls{Tiff} takes \Gls{Nightsha} along in her daily rounds, and is happy to see the elf experiment
with altruism. She hopes that elf society might evolve into a less authoritarian and more
co-operative model, similar to how human society had developed from primates.

\subsubsection{\Gls{GeSw} finds success in diverting the attention of unemployed townsfolk into
    new hobbies}
\Gls{GeSw} visits the house of \Gls{Sidew} in Lancre, an old man who kept his house meticulously
tidy, and asks him what hobby he is working on. The old man, who had kept \Gls{Tiff} at arm's
length, takes an instant liking to \Gls{GeSw}, and beckons him into a secret indoor workshop.
Meanwhile, \Gls{Magrat} convinces \Gls{Letitia} to join the resistance against the elves, and let
her innate magical talents shine.

\subsubsection{\Gls{Nightsha} helps out in \Gls{Tiff}'s village by undoing an elven illusion}
\Gls{Nightsha} recognizes an illusion placed by \Gls{Pease} on the river in \Gls{Tiff}'s village,
making it look and smell like an extremely polluted stream. She removes the illusion, as the
Feegles corral the sheep that are spooked by the smells coming from the river. \Gls{Nightsha} starts
to see the value of altruism, and takes note of how a young man working in the railway has brought
back one of his goblin friends on vacation.

\subsubsection{\Gls{GeSw} sees \Gls{Sidew} put the finishing touches on his trebuchet}
\Gls{Sidew} shows off his prototype trebuchet to \Gls{GeSw}, and tells him that his careful study
of dwarf tactics led him to copy one of their siege weapons. He plans to test it in the forests
away form the town, and gushes about his collection of weapons from his time as a soldier.

\subsubsection{\Gls{Tiff} gets \Gls{Nightsha} to show the witches a taste of her power}
\Gls{Tiff} addresses the gathered witches in the Lancre palace, and notices how \Gls{Earwig} seems
to be dismissive of the elven mind-control that they would have to face. She asks \Gls{Nightsha} to
give a demonstration, and reminds her that \Gls{Ogg} will be keeping an eye on her. \Gls{Tiff}
declares that she will go back to her village to defend against the elves when they invade on the
night of the full moon, and asks \Gls{Ogg} to co-ordinate the defense at Lancre.

\subsubsection{\Gls{Tiff} has a dream about her family's ancestral artifact}
\Gls{Tiff} keeps in mind that \Gls{Earwig} seems immune to the elven mind-control, and introduces
the Feegles to the assembly of witches. \Gls{Tiff} goes home and tries to get some sleep, only to
have a dream that shows an ancestral artifact handed down to her by her father speak with the voice
of \Gls{GAch}. She wakes up just as \Gls{GAch}'s two sheepdogs show themselves to her in their
spirit form, and finds the artifact warm to the touch, as the full moon rises.

\subsubsection{\Gls{Lankin} starts off the invasion by breaking into the Disc at the stone monument
    outside Lancre}
\Gls{Tiff} scrambles to fight the elves when \Gls{RobA} tells her that the invasion has begun.
Meanwhile, \Gls{Magrat} dons the mythical armor of from her first confrontation with the
\Gls{QueenF}, and rallies the other witches in the palace to head for the stone monument outside
Lancre. Meanwhile, \Gls{Lankin} oversees the marshalling of his elven troops, and wonders why there
are no humans at the monument to face them.

\subsubsection{\Gls{Lankin} is forced to retreat, as \Gls{Pease} starts his own assault}
\Gls{Lankin} and his troop are repulsed by \Gls{Sidew}'s trebuchet, which throws iron filings high
into the air and negates all the mind-control powers that the elves might use on them. The witches
clean up the powerless elves, who are forced to retreat even as they get mowed down. Meanwhile,
\Gls{Pease} comes out through the portal in \Gls{Tiff}'s village with his squad of elite warriors,
and manages to force the defenders into a stalemate.

\subsubsection{\Gls{Tiff} banishes the invading elves, by forcing the \Gls{KingEl} to take control
    of their army}
\Gls{Pease} kills \Gls{Nightsha} when she tries to parley with him, and points out the future of
co-operation that \Gls{Tiff} had shown her in the last few weeks. She unleashes the power inside her
using the ancestral artifact, and forces the \Gls{KingEl} to take command of the remaining
stragglers. The \Gls{KingEl} casually executes \Gls{Pease} to reassert his dominance, and takes heed
of \Gls{Tiff}'s advice about leaving the Disc forever.

\subsubsection{\Gls{GeSw} goes back home as a royal ambassador and becomes the first male witch on
    the Disc}
After the battle, \Gls{Tiff} tells the council of witches that \Gls{GeSw} will be given control of
\Gls{GWea}'s steading, freeing her up to focus on her own village. \Gls{Verence} decides to grant
\Gls{GeSw} the rank of ambassador, so that he can go home to \Gls{Swiv} with a shiny new coat of
arms glistening on his cloak. \Gls{GeSw}'s mother is pleased to see him succeed, and looks forward
to visiting Lancre as a royal guest.