\section{The Globe}


\subsection{}
\subsubsection{\Gls{Ridcu} and his council of wizards have their break interrupted by elves}
\Gls{Ridcu} has the faculty play a game of magically camouflaged paintball in the forests away
from the University, and is dismayed to see them ignore team boundaries. Just as he gives the order
to return to the University, he feels the temperature drop, indicating an incursion by the elves.
Meanwhile, \Gls{Rince} receives a message in an empty beer bottle when it appears on his shelf next
to the Roundworld project.

\subsubsection{\Gls{Stibb} and \Gls{Ridcu} think about extracting the council from Roundworld}
\Gls{Stibb} reads the note from \Gls{Ridcu}, which mentions the council being trapped in Roundworld,
along with an elven invasion which is preventing their return. He speculates that his magic reactor
would have to be spun up to dangerous levels again to generate enough magic to go into Roundworld
after \Gls{Ridcu}, and \Gls{Hex} remains skeptical about its ability to bring them back without any
harm.

\subsubsection{\Gls{Rince} wonders why \Gls{Ridcu} has asked for the \Gls{Libra} specifically}
\Gls{Rince} points out the note calling for the \Gls{Libra}, and wonders if he knows some way to
bring back the wizards. Meanwhile, the elves start their operation to brainwash the humans of
Roundworld using their hypnotic singing.

\subsubsection{\Gls{Stibb} elaborates his plan to \Gls{Rince}}
In the High Energy Magic building, \Gls{Rince} interrupts \Gls{Stibb} to talk about the wizards
that \Gls{Ridcu} had mentioned meeting in Roundworld. \Gls{Stibb} confirms the idea of using L-space
to traverse the inter-dimensional barrier and end up in a Roundworld library, somehow making it back
to the specific point in Roundworld time that the faculty happened to be at.

\subsubsection{\Gls{Rince} and \Gls{Stibb} are led by the \Gls{Libra} through L-space}
The \Gls{Libra} sets aside the potential chastisement from the secret masters of L-space, and leads
the other two wizards through the hidden dimension, until they emerge in a simple library on
Roundworld. \Gls{Rince} is glad to see the \Gls{Lugg} functioning normally, in spite of the total
absence of magic on Roundworld.

\subsubsection{\Gls{Hex} successfully communicates with \Gls{Stibb} through the dimension gap}
The \Gls{Libra} knocks out a man dressed in black robes when he enters the small reading room and
unsheaths his sword. \Gls{Hex} speaks to \Gls{Stibb} through a crystal ball, and recommends stealing
the strange man's purse before fleeing the building. \Gls{Hex} asks the \Gls{Libra} to get a shave
and wear some robes, so that he can blend in with the other wizards and avoid unwanted attention
from the locals.

\subsubsection{\Gls{Hex} guides \Gls{Stibb} to the town where \Gls{Ridcu} is stranded}
\Gls{Hex} informs the wizards that elven influence has converted the greatest minds of the
Roundworld into alchemists and astrologers, bent on pursuing magic that does not exist within the
rules of Roundworld. They enter the town pointed out by \Gls{Hex} and find \Gls{Ridcu} boozing in
the tavern with his group of wizards. \Gls{Rince} is surprised to find some Roundworld alchemists
among them, clothed in the same robes.

\subsubsection{\Gls{Ridcu} is focused on undoing the brainwashing of the elves}
\Gls{Ridcu} introduces the roundworld alchemist named \Gls{JDee}, who has fit in well with the
wizards, as \Gls{Rince} takes note of how thorough the elves have been in their brainwashing.
\Gls{Ridcu} asks \Gls{Hex} to perform some spells back at the University to figure out how the
elves have affected the Roundworld, as \Gls{Rince} asks if they even have the right to poke their
noses into the planet's affairs.

\subsubsection{\Gls{Stibb} warns \Gls{Ridcu} of the time left before the next apocalypse}
\Gls{Stibb} does some rough calculations to come to the conclusion that the Roundworld is to face
its next catastrophe in a thousand years, and that the current civilization of humans is the one
that escapes the planet in time. \Gls{Ridcu} realizes how daunting their task will be in setting
the humans on the track of scientific advancement, and freeing them from elven hegemony.

\subsubsection{\Gls{Stibb} talks about stopping the elves meddling with proto-humans}
\Gls{Stibb} tells the wizards that \Gls{Hex} has traced the elves to millions of years in the
Roundworld's past, where they have tampered with the ancestors of humans. \Gls{Ridcu} recalls the
primitive apes that he had visited earlier, and wonders how the elves might have found them smart
enough to influence.

\subsubsection{\Gls{Rince} and the wizards chase the elves into the distant past}
\Gls{Rince} reads a play in \Gls{JDee}'s library, and tucks it into his robes as the wizards get
ready with their iron weapons for the jump into Roundworld's past. The wizards vanishing into the
past immediately sends ripples out into the present, making \Gls{JDee} disappear, along with all
traces of human civilization. The \Gls{Libra} is left behind with \Gls{Hex} in the site of the
city, now an uninhabited swamp-land.

\subsubsection{\Gls{Rince} almost traps the \Gls{QueenF} using the \Gls{Lugg}}
As the other wizards assault the elves trying to mind-control some humans in a forest clearing,
the \Gls{QueenF} spots \Gls{Rince} cowering behind some trees and asks him what they are doing in
Roundworld. He signals for the \Gls{Lugg} to pounce, but the \Gls{QueenF} proves too quick to get
caught in its jaws. The wizards tie iron trinkets to their staves to overwhelm the elves and send
them fleeing into the dusk, and the ones that get killed turn to dust.

\subsubsection{The wizards chase the elves away and change the evolution of human culture}
The wizards get transported by \Gls{Hex} to \Gls{JDee}'s time, with a future version of \Gls{Rince}
warning him privately to hold his breath. They land in a muddy river delta, and find a crude village
made of thatched huts, who seem to be primitive compared to \Gls{JDee}'s town. \Gls{Rince}
approaches one of the tribal men, and figures out that interfering with the elves in the past has
changed the humans of the future for the worse.

\subsubsection{The \Gls{Libra} joins the wizards as they observe the primitive humans}
The rest of the wizards watch \Gls{Rince} approach the proto-human village, and notice the savages
try to eat his wizard hat. The village elder takes the wizards to an ancient tree hit by lightning,
and \Gls{Rince} concludes that the tribe cannot make fire of their own. The \Gls{Libra} appears
through another time portal as the tribals attack \Gls{Ridcu} for lighting up his pipe.

\subsubsection{\Gls{Rince} talks to the charred tree after he climbs on it to escape the fighting}
The \Gls{Libra} tells \Gls{Rince} that humanity never advances to the point of speech because of
their meddling in the distant past, and is angry that there are no libraries for him to navigate in.
\Gls{Rince} climbs the great charred tree and finds out that it can talk. He believes it to be the
last remaining way for \Gls{Hex} to communicate with them in the Roundworld.

\subsubsection{\Gls{Ridcu} decides to stop himself from fighting off the elves}
\Gls{Rince} theorizes that the world is too comfortable for the proto-humans to bother with
story-telling or technological advancement. \Gls{Ridcu} wonders what they might have changed in the
past to produce such drastic effects downstream, and refuses to accept the idea that success means
surviving more than it means making progress. \Gls{Stibb} explains the multiverse theory, and
insists that stable time loops are not set in stone, as \Gls{Ridcu} plans to go back and stop the
elves being chased away.

\subsubsection{The wizards go back to the past to stop themselves from driving the elves away}
A fight breaks out among the pairs of wizards when \Gls{Stibb} mentions that the ones that get
left behind will stop existing after the others are transported back to \Gls{JDee}'s time.
\Gls{Rince} tosses a coin to determine which of his selves will leave, and wonders if stopping the
other set of wizards from driving the elves away will have restored \Gls{JDee}'s present.

\subsubsection{\Gls{JDee} greets the \Gls{QueenF} at his home}
The \Gls{QueenF} pulls up in a carriage to \Gls{JDee}'s home, and the wizards wonder why the elves
are still interfering in human society. \Gls{JDee} is blissfully unaware of the temporal mixup,
and the wizards remember every detail of their adventure while he thinks the magic circle drawn
by \Gls{Hex} did absolutely nothing.

\subsubsection{The \Gls{QueenF} taunts the wizards in \Gls{JDee}'s home}
The \Gls{QueenF} gloats about her success in shaping Roundworld society with her tales of magic,
and reminds the wizards that they have no power to fight her in their current state. \Gls{Ridcu}
tries to warn her about the impending apocalypse, and the \Gls{QueenF} simply laughs off the notion
of saving the humans of Roundworld by putting them on the path to technological progress.

\subsubsection{\Gls{Ridcu} asks \Gls{GWea} for help with the elves}
\Gls{Stibb} reveals the fact that \Gls{Hex} has broken into the semaphore encryption, and that they
can use it to send messages for free, by impersonating one of the wealthy Guilds in the city who
use the network all day. \Gls{Ridcu} dictates a message for \Gls{GWea}, asking for her opinion on
the elf problem within Roundworld.

\subsubsection{\Gls{Ridcu} asks the \Gls{Libra} for books within L-space that might be useful}
\Gls{Ridcu} receives a response from \Gls{GWea}, asking him to go back to a different time in the
Roundworld's past and meddle with the elven influence. The \Gls{Libra} desperately tries to look
through L-space for books from alternate futures that might be of help, as \Gls{Ridcu} reminds him
that he can go out of the room while they look through those books.

\subsubsection{The wizards are transported to \Gls{Nikl} in his workshop by the beach}
\Gls{Stibb} asks \Gls{Hex} to take the wizards to ancient Greece, where they witness him discover
the law of buoyancy. \Gls{Ridcu} realizes that science might be more useful if people who pursue
it form a guild, with internal certification and a peer review process. They are then taken to an
abandoned beach, where \Gls{Nikl} welcomes them into his workshop, and shows them a crude pendulum
clock. \Gls{Nikl} is horrified by the idea of using the clock to tell the time, or using the
rudimentary gramophone to listen to the voices of wise men after they are dead.

\subsubsection{\Gls{Nikl} narrates the tale of his master's experiments}
\Gls{Nikl} talks about his master \Gls{Phoci} constructing elaborate experiments to prove one of
the old philosophers right, only for the results to conclude the exact opposite. He talks about how
\Gls{Phoci} had despaired at the idea of the stalwarts being proved wrong, and fled the country out
of shame. \Gls{Rince} and the \Gls{Libra} check out the local theater on a whim once they get back
to \Gls{JDee}'s house.

\subsubsection{\Gls{Rince} wishes to change the Roundworld timeline to guarantee the existence of
    WIllian Shakespeare}
\Gls{Rince} speculates that teaching the Roundworld humans to make art might lead to the eventual
destruction of the elves, and recalls how focused the audience looked at the theater. \Gls{Rince}
wishes to travel back in time once again, to tinker with the art made by cavemen, so that the
medieval period will be suitable for someone like William Shakespeare to turn up and move public
sentiment with his extraordinary plays.

\subsubsection{\Gls{Rince} leads the wizards into the past to give humanity the gift of art}
The wizards go back to prehistoric times and help teach the proto-humans about art. The \Gls{QueenF}
eventually catches up with them, suspicious of some plot to overthrow her, but is flummoxed when
\Gls{Ridcu} tells her that they are simply helping the humans develop their imagination.
\Gls{Rince} manages to come up with the idea of make-believe magic with the help of \Gls{Hex} to
temporarily give the rituals some meaning.

\subsubsection{\Gls{Rince}'s tries to teach some peasants to act}
In the past, \Gls{Rince}'s attempts to teach some peasants how to act in theater is interrupted by
the \Gls{QueenF}, who cannot let go of her paranoia about the wizards. \Gls{Rince} insists that he
is simply trying to make human culture more vibrant, and bemoans the absence of potatoes in his
part of the Roundworld.

\subsubsection{\Gls{Rince} talks about the second stage of his plan}
After finishing the first phase of \Gls{Rince}'s plan to seed human culture with art, the wizards
assemble in \Gls{JDee}'s library to go over the results. \Gls{Runes} wonders if they have cheated
by showing the humans the end products of the evolution of their culture as a form of bootstrap
paradox, and \Gls{Stibb} merely points to the multiverse theory as a way to resolve the logical
conflict.

\subsubsection{\Gls{Stibb} talks about the success of religion within Roundworld}
\Gls{Stibb} points out how the dominant religion in \Gls{JDee}'s kingdom is similar to Omnianism,
and that there are no traces whatsoever of divine presence anywhere in Roundworld. The other wizards
are impressed by the development of human imagination, given how strong the influence of religion
seems to be, even as scientific enquiry is taking its baby steps in standing up to religious dogma.

\subsubsection{\Gls{Rince} intends to bring William Shakespeare into existence}
The wizards then spend several days interfering with history to make sure that William Shakespeare
is born, and grows up to be in a position to write his plays. \Gls{Hex} tells them that he lives in
the same city as \Gls{JDee}, and tells \Gls{Rince} the good news about potatoes being imported from
the Americas.

\subsubsection{The \Gls{QueenF} fails to understand \Gls{Rince}'s grand plan against the elves}
The \Gls{QueenF} reads the script that she snatched from \Gls{Rince}, and finds in it a favourable
description of elves. She is convinced that the wizards are trying to stop William Shakespaere from
putting on the play, and cannot fathom \Gls{Rince}'s plan to make humanity lose their innate fear of
the elves by depicting them as benevolent beings on stage.

\subsubsection{\Gls{Ridcu} feeds Shakespeare the ideas for his plays}
The wizards get drunk with Shakespeare and talk about their adventures on the Discworld,
inadvertently seeding his mind with the ideas that lead to his famous plays. The next morning,
\Gls{Rince} asks them if they made a mistake in talking extensively about the Disc to a Roundworld
human, as the other wizards deal with their hangover. \Gls{Hex} warns them that the possibility of
the play being interrupted and Shakespeare dying in the ensuing riot is still within reach.

\subsubsection{The \Gls{QueenF} works out \Gls{Rince}'s grand plan}
At the first showing of Shakespeare's play, the \Gls{QueenF} finds \Gls{Rince} backstage, and is
horrified to learn she had got his plan wrong. \Gls{Rince} states that concrete depictions of elves
as harmless beings on stage will erode any fear that humans might have, and spell doom for the
continued existence of the elves in Roundworld.

\subsubsection{\Gls{Rince} and the wizards exit Roundworld using a portal opened by \Gls{Hex}}
The wizards are forced to get on stage at the end of the play to stop the \Gls{QueenF} from
obstructing it. After the audience disperses, they use the chaos to make a run for \Gls{JDee}'s
home, where \Gls{Hex} opens a portal to take them back to the Disc, reminding them that the
Roundworld humans were now on track to escape the coming apocalypse.