\section{The Wee Free Men}


\subsection{}
\subsubsection{\Gls{Tick} senses an inter-dimensional intrusion happening somewhere on the Disc}
\Gls{Tick} observes an intrusion into the Disc by some other realm, by performing a rudimentary
experiment close to a barn, where she is forced to eke out a meager living. She believes that the
place where the incursion is happening is another witch's territory, and rejects her companion's
idea of going to her aid.

\subsubsection{\Gls{Tiff}'s leisurely day at the river is interrupted by a strange monster}
\Gls{Tiff} relaxes by a river, and is shocked to see some small blue men covered in tattoos rowing
a boat the size of a coconut shell. One of them warns another about some grave threat that is on the
way, and they row away at speed without paying her any attention whatsoever. She spots the river
suddenly bubbling with steam, and steps back just in time to avoid a humanoid monster coming out
from the river and trying to grab her.

\subsubsection{\Gls{Tiff} returns to her family farm}
Using her scrying abilities, \Gls{Tick} spots the two Nac Mac Feegles warn the little girl before
rowing away on their boat, and wonders if the nine-year-old girl is the witch in charge of that
territory. \Gls{Tiff} returns to her family farm, which has been leased from the \Gls{Baron} for
many generations, and gets to work as the dairymaid.

\subsubsection{\Gls{Tiff} decides to return to the river to help the Feegles}
\Gls{Tiff} goes to the kitchen, aware that her family is busy with the annual shearing season, and
looks at the small bookshelf left by \Gls{GAch}, who passed away a few years ago. She spots a book
about fairy tales, and spots the entry about the Feegles. She decides to go back to the river with
a wide frying pan, and some sweets for the Feegles, and drags her brother \Gls{Went} along.

\subsubsection{\Gls{Tiff} uses the sweets to bait out the \Gls{Jenny}}
\Gls{Tiff} sets the sweets as bait for the monster, and whacks it with the frying pan when it comes
out to try and eat \Gls{Went}, who is busy trying to undo the knots in the sack. The Feegles watch
her deal with the monster, hiding behind some bushes, and are impressed by her lack of fear. They
believe they have correctly identified the witch of the territory, even if it is a little girl.

\subsubsection{\Gls{Tick} hurries to the Aching family farm, to take charge of \Gls{Tiff}'s
    education}
\Gls{Tick} enters the chalk lands of the Aching family farm, and realizes that she cannot perform
any magic on such unstable ground. Her companion, which is hidden in her hat, tells her that she
can still rely on her guile, as a procession of traveling craftsmen goes past. She decides to
teach the child how to perform magic in her stead, confident that \Gls{Tiff} will not suffer the
same handicaps she does.

\subsubsection{\Gls{Tiff} is told to take her questions about the \Gls{Jenny} to \Gls{Tick}}
\Gls{Tiff} goes to the camp set up by the traveling teachers, and asks the zoologist about the
\Gls{Jenny} she beat up earlier. The teacher tells her that he does not know of any animal
matching her description, and sends her to \Gls{Tick}'s squalid-looking tent as revenge for all
the annoying questions she asked at last year's camp.

\subsubsection{\Gls{Tiff} tells \Gls{Tick} the story of her encounter with the \Gls{Jenny}}
\Gls{Tiff} correctly recognizes that the \Gls{Baron} will crack down on any conspicuous witches
entering his lands, and calls out \Gls{Tick} for being a witch in disguise. \Gls{Tick}'s companion,
which happens to be a sentient toad, activates the mechanism in her hat which raises the pointy
end, as \Gls{Tiff} watches on unimpressed. \Gls{Tiff} narrates the story about encountering the
\Gls{Jenny}, and \Gls{Tick} congratulates her on using a frying pan made of iron, which happens to
be the \Gls{Jenny}'s only weakness.

\subsubsection{\Gls{Tiff} thinks about how reality is different from the book of fairy tales}
\Gls{Tiff} recalls her own grandmother's fame as a veterinarian capable of dealing with all
sheep-related illnesses, and contrasts it to the stereotypical witch depicted in her book of fairy
tales. She then recalls the other old woman who lived in the village, and was shunned by the
populace as an evil witch.

\subsubsection{\Gls{Tiff} tells \Gls{Tick} about the ostracism of \Gls{Snapp} and her subsequent
    death}
\Gls{Tiff} starts to craft an argument that \Gls{GAch} was indeed a witch, and not just an old
woman with a lifetime of experience and knowledge when it came to botany and animal husbandry.
She then talks about old Mrs. \Gls{Snapp}, who was left to die out in the cold winter when none of
the villagers helped her, condemning her as a witch. \Gls{Tick} remains skeptical, never having
heard of \Gls{Snapp}'s name, as \Gls{Tiff} narrates the story of the \Gls{Baron} setting fire to her
hut on the hill, and killing her cat after his son \Gls{Roland} went missing near her home.

\subsubsection{\Gls{Tiff}'s first lesson with \Gls{Tick} comes to an end}
\Gls{Tiff} pays \Gls{Tick} some food for her guidance, and refuses to reveal anything about the
Feegles she saw in the river. \Gls{Tick} realizes the girl is hiding information from her, and lets
the issue go for the moment. The makeshift school day ends, with all the teachers packing up their
tents, and \Gls{Tiff} goes to the top of the barren hill next to the village. She feels snow fall
on her face for a moment when she closes her eyes, and wonders what \Gls{Tick} meant by a major
invasion.

\subsubsection{\Gls{Toad} shares \Gls{Tick}'s high opinion of \Gls{Tiff}}
\Gls{Toad} believes that \Gls{Tick} was impressed by \Gls{Tiff}'s empathy for \Gls{Snapp}, and is
confident that the girl has all the makings of a powerful witch. \Gls{Tick} remains skeptical that
a witch can prosper in a land of unstable soft rock such as chalk, and fondly recalls her own
upbringing in a land of hard granite.

\subsubsection{\Gls{Tiff} falls asleep in her bedroom along with her two older sisters}
\Gls{Tick} decides to go get help, and tells \Gls{Toad} that it will have to keep \Gls{Tiff} safe
in the interim. Meanwhile, \Gls{Tiff} fondly recalls going to the sheepdog trials with \Gls{GAch} as
a child, and of how the village looked up to her as the best judge of a shepherd's ability to train
his dogs. She is joined in her bedroom by \Gls{Ratbag}, the family's pet cat, and falls asleep
thinking about the secret entrance to the witch's school that \Gls{Tick} had promised to show her.

\subsubsection{\Gls{Tiff} saves the Feegles from \Gls{Ratbag} by coughing loudly}
\Gls{Tiff} is woken up by some Feegles whispering under her bed, before moving to the doll house in
one corner of the bedroom. She remains careful not to make any noise, for fear of driving them away,
and is forced to cough when \Gls{Ratbag} seems to be close to waking up. The Feegles stop fighting
the rundown dolls in the dollhouse, and flee when they hear her cough, while wondering how they can
confirm that the little girl is indeed the witch they are looking for.

\subsubsection{\Gls{Tiff} steps out of her house at night and watches the Feegles steal a sheep}
Unable to sleep, \Gls{Tiff} steps out quietly into the misty night with \Gls{GAch}'s book of fairy
tales, and turns to the page showing a detailed drawing of some fairies, complete with a Feegle
on one side making a rude hand gesture. She hears some of them arguing in the garden outside, and
steps out just in time to spot them carrying a sheep away by its four legs. She then hears a
commotion at the henhouse, and stops two more Feegles from stealing some eggs.

\subsubsection{\Gls{Tiff} threatens the Feegles to stop stealing from the farm}
\Gls{Tiff} finds her mother waking up at dawn, and lies to her about the events at the henhouse.
\Gls{Tiff} shouts in her garden to the Feegles to stop interfering with her farm, believing they
can hear her even if they choose to to show it. A while later, she sees a Feegle help her with her
chores as she is busy churning butter, and realizes how strong they are for their size.

\subsubsection{\Gls{Tiff} realizes how eager the Feegles are to get on her good side}
\Gls{Tiff} manages to get all of her chores done by threatening the Feegles, as well as getting them
to put the stolen sheep back in its field. She recalls a story in the book of fairy tales that
mentioned some fairies who would help people with chores in exchange for some milk. She quickly
realizes that the Feegles are different, and wishes she could ask \Gls{Tick} for advice.

\subsubsection{\Gls{Tiff}'s world is invaded by the headless horseman from a snowy land}
As \Gls{Tiff} walks to the village, the land suddenly becomes a snowy forest, with a headless
horseman chasing after her. She runs to the village, until one of the Feegles tells her to turn
around and stare the horseman down. As she does so, a bigger Feegle drops onto the horse's head from
a branch, and concusses it using a headbutt. The other Feegles them assault the horseman, forcing
him to flee, and the real world to reassert itself around \Gls{Tiff}.

\subsubsection{\Gls{Tiff} listens to the \Gls{Toad}'s theory about the paranormal phenomena}
\Gls{Tiff} meets the \Gls{Toad} at the site of \Gls{Tick}'s tent, and narrates the events of the
last day. The \Gls{Toad} is surprised by how helpful the Feegles have been, and tells her that they
are known for their belligerent nature. It then tells her that \Gls{Tick} suspects an
interdimensional invasion is in progress, and believes that the loss of the local witch is what is
attracting the invaders to \Gls{Tiff}'s home country.

\subsubsection{\Gls{Tiff} learns of her brother \Gls{Went} having gone missing}
\Gls{Tiff} makes an offhand comment about teaching \Gls{Ratbag} a lesson about killing baby birds,
and watches in fascination as a Feegle sticks some feathers to itself, hoping to attract the cat
and kick it in the head. She then puts \Gls{Toad} away just in time for her mother to rush into the
house, asking if she has seen \Gls{Went} recently. She searches every cupboard in the house, and
realizes that her entire family has returned from their workday to help look for the boy.

\subsection{}
\subsubsection{\Gls{Tiff} sees the Feegles assembled for the first time}
\Gls{Tiff} wishes out loud that she could track down \Gls{Went}, aware that the Feegles would not
show themselves when surrounded by so many humans. \Gls{Tiff} takes the \Gls{Toad}'s advice, and
fetcher her father's strong liquor as an offering to draw the Feegles out of hiding. They crawl
out of the nooks and corners in the dairy, still seemingly scared of \Gls{Tiff}. She forgives them
for stealing the sheep, and is alarmed when they say that thieving is in their nature, whether they
need the food or not.

\subsubsection{The Feegles warn \Gls{Tiff} not to speak the name of the \Gls{QueenF}}
The chief spokesman of the Feegles introduces himself as \Gls{RobA}, when the others insist that he
has to answer the witch's question. \Gls{Tiff} wonders why the Feegles need someone to save them,
and why \Gls{Toad} is stopped from mentioning the \Gls{QueenF}, as if it were some kind of bad omen.
\Gls{Tiff} recalls \Gls{GAch} resolving a dispute about the \Gls{Baron}'s prize hunting dog which
had killed some sheep for sport.

\subsubsection{\Gls{Tiff} decides to track down her brother using the Feegles as guides}
\Gls{Tiff} leaves a note for her family, and packs a first aid kit so she can go along with the
Feegles to find her brother. She is surprised when they ask her to lift up her boots so they can
haul her along like they did with the lamb, with the \Gls{Toad} reminding her that they are much
stronger than they look.

\subsubsection{\Gls{Tiff} goes to \Gls{GAch}'s ruined hut along with the Feegles}
\Gls{Tiff} is carried to the burned remains of \Gls{GAch}'s hut, and recalls how the entire village
had come together to give her a grand burial next to her hut, before burning it to the ashes. Her
two pet sheepdogs had observed the rituals with great interest, and vanished the next day, never to
be seen again. The Feegles look up in the sky, waiting for \Gls{Hamish} to show up with news of
where the \Gls{QueenF} was last seen.

\subsubsection{\Gls{Tiff} realizes she will have to travel to the icy world of the \Gls{QueenF}}
\Gls{Hamish} lands from his bird, and drops safely to the ground using his makeshift parachute. The
other Feegles ask him if he saw the \Gls{QueenF} kidnapping the boy, and he says he lost track of
her when she vanished into her own dimension. \Gls{RobA} warns \Gls{Tiff} that the other dimension
is a place where dreams come true, even if they are nightmares. \Gls{Tiff} grows desperate, and
asks to be taken to the leader of the Feegles, even as \Gls{RobA} points out that \Gls{GAch} never
graced them with a visit to their cave.

\subsubsection{\Gls{Tiff} deals with the \Gls{QueenF}'s hounds by drawing them into the real world}
\Gls{Tiff} once again feels the cold wind blow over her, as the \Gls{QueenF} projects her power
into a circle around \Gls{GAch}'s hut, burying the feegles in several inches of snow. Three of her
hounds surround \Gls{Tiff}, with fire in their eyes and sharp fangs poking out of their mouths.
She runs out of the circle of snow, and correctly guesses that the dogs have no power in the
real world. She manages to beat all three of them up, with the help of the Feegles, and watches
the snow world fade away along with the dogs.

\subsubsection{\Gls{RobA} explains the Feegle theory of the Disc being an afterlife}
\Gls{RobA} seems unbothered by his fellow Feegles that died fighting the hounds, and tells
\Gls{Tiff} that it is their belief that the Discworld is the good afterlife that they are sent to,
as a reward. \Gls{Tiff} takes \Gls{Toad} out, and is surprised when it insists on bringing the
owner of the hounds to trial for the fracas. The Feegles pick up the corpses of their brethren, and
prepare to bury them so that humans will not come across their remains.

\subsubsection{\Gls{Tiff} goes to the underground hideout of the Feegles}
The Feegles take \Gls{Tiff} to their underground colony, which is located next to the burial mound
of one of the old village chieftains. She finds the opening very small from the outside, but is led
to a comfortably large room within, where the Feegles are busy with their domestic duties. A
female Feegle named \Gls{Fion} claims to speak for their leader, and reassures her that \Gls{Went}
will not come to any harm for a while.

\subsubsection{\Gls{Wullie} reveals the Feegles' agreement with \Gls{GAch}}
\Gls{Wullie} lets slip the fact that \Gls{GAch} had an agreement with the Feegles to keep away
the predators in exchange for the occasional sheep for their colony. \Gls{Tiff} realizes that more
of \Gls{GAch}'s supposed witchcraft is just other beings doing the dirty work for her. She regrets
not getting to know \Gls{GAch} better, and recalls the time when she won a porcelain statue of a
shepherdess at the nearby fair.

\subsubsection{\Gls{Tiff} is asked to proceed to the Feegle leader's chamber}
\Gls{Tiff} recalls showing the shepherdess statue to \Gls{GAch}, and of how she would stare at it
for a while, without making any comments. Eventually, the Feegle bagpiper plays his pipes to herald
the opening of the door to the leader's chamber. \Gls{Toad} recommends taking the bottle of liquor
along as a gift to the leader, as \Gls{Tiff} tries to crawl through the hole.

\subsubsection{\Gls{Tiff} learns about the true motive behind the kidnapping of \Gls{Went}}
The \Gls{Kelda} welcomes \Gls{Tiff} into her chamber full of gold, and reassures her that the
\Gls{QueenF} will not harm \Gls{Went} any time soon, if he has been taken to her dimension. She then
tells \Gls{Tiff} that the \Gls{QueenF} is likely testing her ability to hold back the fairy
dimension fron invading the Discworld, and hopes that she can carry the burden as well as \Gls{GAch}
did.

\subsubsection{\Gls{Kelda} dies after appointing \Gls{Tiff} her successor}
In spite of \Gls{Fion}'s protests, \Gls{Kelda} appoints \Gls{Tiff} her successor, in exchange for
a means to enter the \Gls{QueenF}'s realm. \Gls{Tiff} learns that the Feegle leaders are always
female, and rarely have daughters who succeed them in the same nest. The \Gls{Kelda} dies after
enjoying one last drink of \Gls{GAch}'s signature liquor, and asks \Gls{William} to play her
favourite tune as she lays dying.

\subsubsection{\Gls{Tiff} learns about the process of electing a new leader of the Feegles}
\Gls{Tiff} recalls \Gls{GAch} telling her a story about some sailor who was fated to chase a large
whale endlessly around the Discworld's sea, and then thinks about the day she had found \Gls{GAch}
dead in her hut. As the other Feegles go about their somber rituals, \Gls{Tiff} asks \Gls{William}
why the leadership cannot be inherited by \Gls{Fion}. \Gls{William} tells her that he is the last
remaining brother of the deceased \Gls{Kelda}, and that he will be returning to his home in the
mountains after the business with the \Gls{QueenF} is concluded.

\subsubsection{\Gls{Tiff} decides to send a written note home explaining her absence}
\Gls{Tiff} wonders where she can find a place where time is warped, and wonders why the \Gls{Kelda}
gave her such a cryptic clue with her dying breath. She comes out of the tunnel, and realizes she
is constantly being shadowed by a group of Feegles on guard duty. She tells them to leave her alone,
and asks for \Gls{Hamish} to come down and take a written note to drop into her farm. The note
simply states that she is getting \Gls{Went} back and that he is not hurt in any way.

\subsubsection{\Gls{Tiff} learns that the \Gls{QueenF} last appeared next to some stone monuments}
\Gls{BigJock}, the young bagpiper in training, tells \Gls{Tiff} that \Gls{Hamish} has a very
effective system for training birds from a young age, as he points out the location where the
\Gls{QueenF} had first manifested her snow. \Gls{Tiff} recalls the place being littered with stone
monoliths arranged in simple shapes, and of how she had played there as a child while finding it
unremarkable.

\subsubsection{\Gls{Tiff} is forced to choose a warrior to mate with}
\Gls{Tiff} is called back to the tunnel, where she notices the Feegles preening themselves as if
to prepare for some sort of mating ritual. \Gls{RobA} sheepishly tries to broach the subject of
getting the new leader to pick a mate amongst the clan's dominant males, causing \Gls{Tiff} to
think about how the \Gls{Kelda} intended for her to solve this problem. She excuses herself out of
the tunnel, and asks the \Gls{Toad} for advice on the surface.

\subsubsection{\Gls{Tiff} postpones her marriage to \Gls{RobA} indefinitely}
\Gls{Tiff} tells the Feegles that she chooses to marry \Gls{RobA} at a time many millions of years
into the future, and sees the relief on his face at having avoided the thorny issue. \Gls{Fion} is
exasperated by the diplomatic answer, and \Gls{RobA} reminds her that the marriage is just a ritual
that needs to be dealt with every time a new leader comes to power.

\subsubsection{\Gls{Tiff} finds the entrance by noticing a time anomaly near one of the stones}
\Gls{Tiff} starts to read from \Gls{GAch}'s book of sheep pathology, as the Feegles gather around
her to watch in amazement. She spots one of \Gls{Went}'s favourite candies littered on the ground
next to the monoliths, and spots a trail leading to a gate shaped monument. She realizes that she
needs to believe the gate will take her to the land of the fairies as she walks through it.
\Gls{Tiff} notices a bird appearing to be in two places at once, and realizes that the stone arch is
twisting time to cover up the existence of a portal.

\subsection{}
\subsubsection{\Gls{William} plays his bagpipes to disorient and confuse the black hounds}
\Gls{William} takes out his special bagpipes when \Gls{RobA} spots an army of greyhounds sent by
the \Gls{QueenF} to deal with them. The utlrasonic notes leave the dogs in immense pain, as the
Feegles themselves cover their ears to avoid the damage. \Gls{RobA} suggests moving along before
the \Gls{QueenF} sends someone stronger to deal with the intruders.

\subsubsection{\Gls{RobA} explains the eventual fate of all children kidnapped by the \Gls{QueenF}}
\Gls{RobA} explains that the time dilation in the fairy realm would mean that \Gls{Went} would
eventually be kicked out by the \Gls{QueenF} when she grew tired of him, only to return to a Disc
several decades in the future. \Gls{William} warns her that other children have been kidnapped
before, and never quite got out of the dreaming mindset even after being rescued from the fairy
realm.

\subsubsection{\Gls{Tiff} breaks out of an infinite dream trap set by a drome}
\Gls{Tiff} is trapped in a dream by a small monster in the fairy realm called a drome, but manages
to notice enough oddities about the constructed reality to break out with the help of the Feegles.
\Gls{William} tells her that the drome traps its victims in a never-ending dream by making them eat
delicious food within it, and \Gls{Tiff} realizes her own mind was sending her warning signals by
making some details deliberately wrong.

\subsubsection{\Gls{Tiff} walks through the snowy forest, noticing the shapeshifting trees}
\Gls{Tiff} recalls \Gls{GAch} helping a donkey when its master had overburdened it, and repeating
the lesson that someone had to speak up for those that had no power. As \Gls{Tiff} makes her way
through the snowy forest, she notices the trees become more real and detailed the more she stares
at them, and theorizes that the snow is just a way of hiding the lack of reality in the fairy world
needed to give the landscape all the detail it needs.

\subsubsection{\Gls{BigJock} repulses the flying fairies by singing a bad poem}
The Feegles are suddenly met upon by a swarm of smaller fairies with winds, and push \Gls{Tiff} down
onto the ground so she will not get bitten to death. \Gls{BigJock} busts out one of his bad poems,
offending the flying fairies so much that they give up the attack and retreat to their nests.
\Gls{Tiff} realizes how powerful words are in this dimension, and notices a stag running towards
her through the forest, while being chased by two of the black hounds.

\subsubsection{\Gls{Tiff} spots \Gls{Roland}, the long-lost boy, in the fairy realm}
\Gls{Tiff} spots a boy on a white horse with a small whip, and realizes it is \Gls{Roland}, the
\Gls{Baron}'s missing son from all those years ago. The Feegles cut out the underside of the boy's
saddle as she distracts him for a minute, causing him to fall off the horse when he orders it to
charge. \Gls{Tiff} asks the Feegles not to attack him when is lying helpless in the snow, and sees
him running away back into the forest.

\subsubsection{\Gls{Tiff} falls into another dream-trap, this time featuring a costume party}
\Gls{Tiff} is once again sucked into a dream-trap when she chases through the forest after
\Gls{Roland}, and finds herself in a costume ball, with an elaborate banquet laid at one end of the
room. The Feegles eventually show up wearing small masks and suits, telling her that this drome must
be particularly powerful, to be able to generate a large crowd of people into which it can embed
itself.

\subsubsection{\Gls{Tiff} works out the drome's disguise within the dream-trap}
\Gls{Tiff} is tempted to take a bite of the fancy cheeses laid out on the buffet table, but recovers
control of her urges just in time. She spots \Gls{Roland} sitting alone in a room, and tries to warn
him about the dream. When he responds in alien language, she realizes it is the drome in disguise,
and cuts its head off to break out of the dream-trap.

\subsubsection{\Gls{Tiff} pursues \Gls{Roland} to a clearing with some tame dromes}
Back in the fairy realm, \Gls{Tiff} asks \Gls{Roland} how she can track down the \Gls{QueenF}, and
if he wants to escape to the Discworld along with her. He tells her that it is impossible to find
an exit, and walks off into the forest. She walks uphill in pursuit of \Gls{Roland}'s tracks
through the snow, and finds a group of four dromes with golden collars sitting in a square. She
decides to walk through them, aware of the fact that the next dream-trap would be much more
elaborate.

\subsubsection{\Gls{Tiff} wakes up in a scene out of a fairy tale}
\Gls{Tiff} realizes that the Feegles are still trapped in the last dream, and is transported to a
scene out of a fairy tale, where she is just as small as they are. She finds herself in a field of
flowers on a hot summer day, and a clearing where more miniature people are gathered around a man
cracking nuts with a hammer. She passes through the crowd, and listens to a man in a white beard
trying to warn her in an alien language.

\subsubsection{\Gls{Roland} talks about life in the fairy realm as a prisoner}
\Gls{Roland} finds her in the dream, just as the \Gls{Toad} tells her that she is only imagining the
hot summer day. He is horrified to learn that he has been trapped in the fairy realm for a year, and
believes that he has been there only for a day or two. He explains that some prisoners in the fairy
realm had returned even after getting the chance to escape back to their home worlds, and reveals
to \Gls{Tiff} that the \Gls{QueenF} only punishes children who try to upset her.

\subsubsection{The \Gls{QueenF} confronts }
\Gls{Tiff} finds \Gls{Went} crying in a nearby clearing, surrounded by huge piles of candy in all
flavours. He picks him up, and is surprised when the \Gls{QueenF} taunts her from somewhere she
cannot be seen. When the \Gls{QueenF} makes herself visible, \Gls{Tiff} immediately blurts out the
fact that her appearance is simply what she wishes she looked like.

\subsubsection{\Gls{Tiff} gets under the \Gls{QueenF}'s skin by making a rude comment}
\Gls{Tiff} recalls \Gls{GAch} interfering in the trial of an orphaned woman who had been caught
kidnapping a child in the village, and making good on the favour owed to her by the \Gls{Baron}.
\Gls{Tiff} then asks the \Gls{QueenF} if she has ever shown any kindness in her life, and has a
single friend who will defend her freedom.

\subsubsection{\Gls{Tiff} tries to run away from the \Gls{QueenF} and circumnaviates the dream
    world}
\Gls{Tiff} further offends the \Gls{QueenF}, and is slapped in response. She lands next to her iron
frying pan, and manages to land a glancing blow on the \Gls{QueenF}, giving her the chance to grab
\Gls{Went} and run away. She spots \Gls{Roland} in the earlier clearing, and learns too late that
running in a straight line will take her back to the \Gls{QueenF}'s garden. Two of the
\Gls{QueenF}'s enforcers surround her, and the \Gls{QueenF} asks her in a polite voice to surrender
\Gls{Went} and walk away.

\subsubsection{\Gls{Tiff} is saved by the Feegles after she finds a way for them to enter the
    dream-trap}
The Feegles attack the \Gls{QueenF} when \Gls{Tiff} lets them into the dream by breaking the last
nut that the nut-cracker was having difficulty with. They force the \Gls{QueenF} to flee, and attack
all of the assembled fairy soldiers, subduing them within seconds. \Gls{Tiff} manages to break out
of the dream-trap using her mind, and the Feegles run out of the forest carrying her and
\Gls{Roland}, who is now unconscious.

\subsubsection{\Gls{Tiff} thinks of a way to avoid confronting the nightmare creatures head-on}
\Gls{Tiff} decides not to leave the Feegles behind when the \Gls{QueenF} sends an army of nightmares
creatures to chase them down. She orders the force to approach a nearby tree with a small drome
hiding in the bushes. She decides to make use of the sea depicted in \Gls{GAch}'s favourite brand of
tobacco, to try and craft a dream-trap that might keep the creatures busy.

\subsubsection{\Gls{Tiff} takes everyone else into the scene on the tobacco pouch}
\Gls{Tiff} constructs a dream out of the tobacco label, and finds herself in a rowboat along with
the Feegles. She hauls \Gls{Went} and \Gls{Roland} into the boat, and asks them to start rowing to
the distant lighthouse. \Gls{RobA} points out a stormcloud in the distance, believing it to be
the \Gls{QueenF}'s attempt at penetrating the dream. She notices a representation of her own boat
on the tobacco pouch's label in her apron pocket, and realizes she is trapped in a recursive pocket
dimension.

\subsubsection{\Gls{Tiff} gets the whale to stop pursuing her and chase the captain's ship}
\Gls{Tiff} recognizes the whale from her dreams rise up from the water surface and start to chase
her. She orders the Feegles to keep rowing, and hopes that the pirate will stop the whale from
swallowing her by interfering at the last moment, just like in her dreams. The whale is forced to
chase the ship when it shows up, in accordance with the rules of \Gls{Tiff}'s dream.

\subsubsection{\Gls{Tiff} and the Feegles reach the island with the lighthouse}
\Gls{Tiff} spots the drome sitting on the jetty, entranced by the sea, as the Feegles pull up to
disembark. She believes it is reliving a vision of its home world, and asks the Feegles to leave it
be. They warn her to stay back as they investigate the lighthouse, and unsheath their swords,
confident that the \Gls{QueenF} will be waiting to ambush them.

\subsubsection{\Gls{Tiff} notices the Feegles mistake lamp oil for strong liquor}
\Gls{Tiff} watches the calm sea for a while, until she hears the sound of glass breaking inside the
lighthouse. She works out that the Feegles have drunk the lamp oil stored in a reinforced cupboard
at the top of the lighthouse, and hopes that walking through its door will end the dream, just like
usual.

\subsubsection{\Gls{Tiff} escapes from the fairy realm just as a tsunami hits her dream}
\Gls{Tiff} spots the sign of a coming tsunami too late, and just manages to exit the dream as the
wave crashes into the island. She drags \Gls{Roland}'s unconscious body through the snowy forest
back to the portal, and lays him down next to the stone monument. She notices the monument
collapse soon after, and wonders if the Feegles might have survived the dream-trap, along with
\Gls{Went}.

\subsection{}
\subsubsection{\Gls{Tiff} receives help from \Gls{GAch} and her legendary sheepdogs}
\Gls{Tiff} sees the \Gls{QueenF} slowly start to invade the Disc, and taunt her inability to
rescue her brother. She feels a hailstorm start to fall, and the cold creeping up on her limbs,
causing her to fall down onto the artificial snow being manifested by the \Gls{QueenF}. \Gls{Tiff}
manages to summon help from an apparition of \Gls{GAch}, and sees her two sheepdogs chase the
hailstorm away. She turns around to see \Gls{GAch} wearing the same ornate blue dress as the doll,
before vanishing with a smile on her face.

\subsubsection{\Gls{Tiff} banishes the \Gls{QueenF} using the powers of the land under her feet}
The \Gls{QueenF} summons some lawyers when the Feegles manage to break out her realm into the
Disc, and terrifies them with legal jargon. The \Gls{Toad} recalls its prior life as a lawyer when
it hears the arguments, and tells \Gls{Tiff} that it was polymorphed by a fairy godmother a long
time ago. \Gls{Tiff} banishes the \Gls{QueenF} back to her realm, using the land's own power to
become immune to her mind-control.

\subsubsection{\Gls{Tiff} sees three witches arriving by broomstick}
\Gls{Tiff} gives the Feegles leave to sell the fairy gold looted from the dream with the tsunami,
and asks \Gls{Roland} to take \Gls{Went} along to the village. \Gls{William} reassures her on a
job well done, as the rest of the Feegles rush off before the gold turns into mud. \Gls{Tick}
arrives by broomstick with \Gls{Ogg} and \Gls{GWea}, to ask her how she dealt with the \Gls{QueenF}.

\subsubsection{\Gls{GWea} and \Gls{Ogg} welcome \Gls{Tiff} into the local witch society}
\Gls{GWea} tells \Gls{Tiff} that she will be welcome to apprentice with a senior witch nearby when
she turns older, and congratulates her on her quick thinking in the fairy realm. \Gls{GWea} manages
to work out the events of the past day using her magic, and takes off with the others when she
senses \Gls{Tiff}'s father rushing to the \Gls{GAch}'s hill with some villagers.

\subsubsection{\Gls{Tiff} thinks about the Feegles, and about her future as a witch}
\Gls{Tiff} receives news from the Feegles that a new leader is coming to take over their clan, thus
freeing her up to focus on the witchcraft. She listens to the \Gls{Baron} fill in the blanks about
the fairy land, believing that \Gls{Roland} was the hero who rescued the other two children trapped
there with him. She warns \Gls{Roland} not to be cruel when he takes over the role from his father,
and tells him that a part of her will always be watching over the village.