\section{The Amazing Maurice and his Educated Rodents}


\subsection{}
\subsubsection{\Gls{Mauri} and the rodents try to reason with their human accomplice}
In a carriage headed to Uberwald, \Gls{Mauri} tries to argue with someone else that the scam they
are running is ethically justifiable, since they take money away from governments who might put it
to use for violent wars. The driver feels spooked by the low squeaky voices he can hear coming from
the coach, even through there is only one passenger left. Eventually, a highwayman stops them in the
rainy night, and asks for their bag of cash.

\subsubsection{\Gls{Mauri} turns the tables on a bandit who tries to waylay his coach}
The boy tells the bandit that the money is on a sack tied to the roof, just as \Gls{Mauri} the cat
asks him to play a warning note on his flute to warn the rats. \Gls{Peach}, the head rat, tells
\Gls{Mauri} that they cannot steal the coach even if the driver has fled, and \Gls{Mauri} settles
for stealing the bandit's horse. The boy gets down from the carriage, and takes the horse, as
the bandit remains very still, waiting for the rats to scurry out of his trousers.

\subsubsection{\Gls{Mauri} thinks back to his sudden sentience in the garbage dump behind
    Unseen University}
\Gls{Mauri} recalls gaining sentience one day, when he looked into a puddle in the garbage dump
behind Unseen University, and understood the idea of self. He then thinks about finding the rats
living in the same dump also being sentient, and coming up with the idea of the rat-catching scam
that uses the flute-playing boy. The party reach the outskirts of a small village, and \Gls{Mauri}
is forced to field further questions from the rats.

\subsubsection{\Gls{Mauri} reminds the sentient rats about their long-term goal}
\Gls{Mauri} fends off questions from \Gls{Beans}, a young albino rat that was born just after the
Awakening, as the old leader \Gls{Hamn} sits back and struggles with his newfound intelligence.
\Gls{Mauri} reminds them that their grand plan of starting a new civilization on a deserted island
requires a hefty investment, and that he represents their best shot of fulfilling their dream.

\subsubsection{\Gls{Mauri} is forced to put an end to his rat-catching scam after the next town}
\Gls{Peach} and \Gls{Beans} make an appeal to \Gls{Hamn} to end the usual scam with this next town,
and set off to find the boats for their voyage after splitting the spoils with \Gls{Mauri}. When the
boy offers no objection to \Gls{Beans}, \Gls{Mauri} decides to make their final scam a grand affair.
\Gls{Peach} sets the bandit's horse loose, since they cannot sell it in town without raising
suspicion.

\subsubsection{\Gls{Mauri} and the young boy notice food rationing in the town}
At the town square, \Gls{Mauri} notices the townsfolk staring at him, as the boy points out how the
villagers look much poorer than the architecture might suggest. They spot a notice board announcing
a handsome reward for rat tails, and spot some watchmen controlling a long queue at the town's
rat-house. \Gls{Mauri} wanders into the building, and finds food being rationed strictly for the
townsfolk.

\subsubsection{\Gls{Mauri} and the boy run into some rat-catchers}
The boy plays some music for the people standing in line, as \Gls{Mauri} comes out of the building,
to spot two rat catchers approaching with their bags of rat-tails. The rat catchers' dogs are cowed
by \Gls{Mauri} speaking human words to them, as one of the rat-catchers drops a bundle of tails on
the ground. When the boy goes to pick them up, the rat-catcher warns him about the possibility of
getting the plague from the tails, and brushes off the questions about why they don't fear touching
the tails themselves.

\subsubsection{A villager offers to purchase \Gls{Mauri} so that he can catch more rats}
A villager comes out of the ration house, and asks to buy \Gls{Mauri} off the boy. The boy refuses,
and the villager reminds him that money does not mean much in the town with its food scarcity.
\Gls{Mauri} suggests staying in town and uncovering the scam that is clearly in progress, and
reassures the boy that \Gls{Hamn} can deal with the rat-catchers on his own.

\subsubsection{A girl in black identifies \Gls{Mauri} as an enchanted cat that can talk}
A girl wearing black notices the boy talking to \Gls{Mauri}, and asks him why he is in town. She
makes up a story about the boy being a wizard's apprentice who got sick of his workplace and stole
the enchanted cat on his way out. She catches \Gls{Mauri} talking when she spooks him by saying that
the villager probably wanted to buy him for food rather than catching rats.

\subsubsection{\Gls{Peach} and the leaders set up a base of operations underneath the town}
\Gls{Peach} lights a small candle in a cellar underneath the town, as the rats gather for their
debriefing. \Gls{Hamn} refuses to bother with the finer details of the plan, and leaves the
organizing to \Gls{Beans}, who claims to have enough eyesight left to tell the candlelight from the
darkness. \Gls{Darktan}, the engineer rat, points out that the town has no rats in the dark tunnels
so suitable for their lifestyle.

\subsubsection{\Gls{Darktan} gives orders to the three groups of rats in the clan}
\Gls{Darktan} sends off a group of juvenile rats to urinate on the food-grain stores in the town,
and turns to the group of older rats, who are tasked with stealing food from the kitchens. He then
turns to the final group, consisting of the trap disposal and detection rats, who are to survey the
town and get rid of as many traps as possible before the others groups can get to work.

\subsubsection{\Gls{Peach} continues filling in her scroll of laws laid down by \Gls{Beans}}
\Gls{Peach} writes down a new edict formulated by \Gls{Beans}, which states that rats should not
kill other rats. She thinks back to how the senior rats all listened to him, now that they were in
unfamiliar cognitive territory. She then goes off to find \Gls{Hamn} isolating himself from the
other rats, seemingly trying to fight off some disease caused by his old age.

\subsubsection{\Gls{Malicia} introduces herself to \Gls{Mauri} and the boy \Gls{Keith}}
The girl in black takes \Gls{Mauri} and the boy to her home, and tells them that her father is
the town's mayor. She talks about the food rationing as a result of the rat infestation, and how
this has destroyed the town's bustling tourism industry. \Gls{Mauri} asks her for her name, and
she tells him it is \Gls{Malicia}. The boy reveals for the first time that his name is \Gls{Keith},
and that he was an orphan raised by the Ankh-Morpork Guild of Musicians.

\subsubsection{\Gls{Malicia} immediately works out \Gls{Mauri}'s scam}
\Gls{Malicia} tells \Gls{Mauri} that she has a fairly comfortable life as the mayor's daughter, but
for the strict rationing of food. \Gls{Mauri} notices \Gls{Sardines} rappelling down from the
kitchen roof behind \Gls{Malicia}, and tries desperately to signal for a retreat. \Gls{Sardines}
gets caught in a trap, and is rescued by \Gls{Keith} just in time for the spiky jaws to snap shut.
\Gls{Malicia} connects the dots, and theorizes that the intelligent rats are a part of the scam
being perpetrated by \Gls{Keith}, with help from \Gls{Mauri}.

\subsubsection{\Gls{Sardines} talks about how unusual the town is compared to all their previous
    venues}
\Gls{Sardines} remarks on the curious absence of native rats in the town, and \Gls{Malicia} asks him
if he is excluding his own clan of intelligent rats from the count. \Gls{Malicia} hears
\Gls{Sardines} talk about the local rats in all the other towns they go to, and of how they can
be made to comply with \Gls{Mauri}'s plan. \Gls{Mauri} points out that the rat-catchers have been
passing off shoelaces as rat tails, with a story about the plague acting as a safeguard against
close examination.

\subsection{}
\subsubsection{\Gls{Darktan} receives bad news during one of his trap defusal demonstrations}
\Gls{Darktan} demonstrates a tricky trap defusal to the novices in his squad, with \Gls{Nouri}
quickly realizing she is out of her depth when it comes to remembering the intricate details of each
model. \Gls{Darktan} pencils in the trap on his map, as he receives reports of the local mundane
rats lying dead next to the poisoned food in the tunnels. A runner from the urination squad runs to
\Gls{Darktan} with reports of a new model of trapped one of his squadmates.

\subsubsection{\Gls{Malicia} proposes a raid of the rat-catchers' shed at night}
\Gls{Malicia} tells \Gls{Mauri} and \Gls{Keith} that her father has received a lot of complaints
from the townsfolk regarding a fresh wave of rats, and has sent for the two rat-catchers. She
suggests breaking into the rat-catchers' shed and learning about the fake rat-tails that they are
using to abuse the bounty that has been declared.

\subsubsection{\Gls{Darktan} observes the advanced trap after one of the scouts dies to it}
\Gls{Darktan} comes to the new trap, and notices the others in the squad wondering what happens to
the self after death, and mumbling something about the \Gls{DRat} ready to take them to the
afterlife. He warns them not to venture further into the tunnel with the sophisticated trap, and
wonders why there is so much more poison than live local rats.

\subsubsection{\Gls{Darktan} comes up against a new kind of paralytic poison in the tunnels}
\Gls{Darktan} returns to the tunnel hub, to be dragged to be shown another rat that has died to a
new poison that causes paralysis. He asks for a live trap to be brought so that it can be
euthanized, and is exasperated when news comes of a live native rat being spotted after many days
searching under the town.

\subsubsection{\Gls{Malicia} picks the lock of the rat-catchers' office}
\Gls{Malicia} leads the way through the city streets to the rat-catchers' office, which is heavily
padlocked. She takes out a bent hairpin from her bag of tools, as \Gls{Mauri} watches on in
fascination. She manages to pick the lock before he can finish his statement about how this was a
real-life lock, and not one from her fairy tales.

\subsubsection{\Gls{Hamn} lets \Gls{Darktan} deal with the new trap}
\Gls{Hamn} and the other leaders let \Gls{Beans} interrogate the native rat, as \Gls{Darktan}
recalls smelling a large population of rats close to the place where it was found. \Gls{Hamn}
decides not to strike against \Gls{Beans} for suggesting they keep the native rat as a pet, and lets
\Gls{Darktan} dictate the strategy for the expedition into the hidden rat farm. \Gls{Peach} and the
other senior rats are surprised that \Gls{Hamn} is so diplomatic all of a sudden, in contrast with
his animal instincts.

\subsubsection{\Gls{Keith} falls through a secret trapdoor in the rat-catchers' shed}
\Gls{Malicia} insists on finding a secret passage inside the rat-catchers' shed, and tries to lean
on the walls hoping to trigger some sort of secret switch. \Gls{Keith} wanders the shed, noticing
that the sugar was being stored right next to the rat poisons, until he runs into a small rat-hole
in a wall. \Gls{Malicia} pulls a lever inside the rat-hole, causing \Gls{Keith} to fall through a
trapdoor.

\subsubsection{\Gls{Darktan} remains cautious in tracking down the rat-farm}
\Gls{Darktan} uses one of the few remaining mechanical rat toys to scout a tunnel leading to a wide
drainpipe. The toy gets caught in a trap, and \Gls{Hamn} starts to lose patience with the slow pace
of the expedition. \Gls{Darktan} points out that the warn tunnels are used to pump geothermal water
to the town's baths. \Gls{Hamn} smells some poison, and agrees with \Gls{Darktan}'s suggestion to
let another native rat run away when it sees them coming.

\subsubsection{\Gls{Darktan} and \Gls{Hamn} prepare to scout the rat-farm}
\Gls{Darktan} takes out a small spike crafted for him by \Gls{Keith}, and points out the sword that
was in the picture book of animal stories that they had stolen shortly after Awakening. \Gls{Hamn}
insists on being part of the vanguard, anxious to prove his dominant position in the clan to
potential challengers like \Gls{Darktan}.

\subsubsection{\Gls{Keith} and \Gls{Malicia} explore the underground cellar stocked with food}
\Gls{Keith} falls on some sacks of grain, and points out a ladder for \Gls{Malicia} to use as she
looks down through the trapdoor. \Gls{Mauri} tries to make sense of the hoarded food in the cellar,
and how the rat-catchers seemed too dumb to pull off such an elaborate scam. \Gls{Malicia} is
convinced that the rat-catchers have simply killed off all the rats and hoarded the food for
themselves.

\subsubsection{\Gls{Keith} is reunited with \Gls{Hamn} and the rat leaders in the rat-farm}
\Gls{Keith} wonders why the shed has lots of wire-netting, given that dead rats do not need to be
caged. \Gls{Mauri} runs into \Gls{Sardines} scurrying out of a door at the other end of the cellar,
talking about some evil thing that requires all of them to come look. \Gls{Peach} and \Gls{Beans}
watch most of the exploring rats run past them as they flee the cellar. \Gls{Hamn} and \Gls{Darktan}
stay in the rat-farm, as \Gls{Keith} breaks down the door to let in \Gls{Malicia}.

\subsubsection{The rat catchers enter the rat-farm, and confront \Gls{Keith}}
\Gls{Mauri} hears someone coming down the ladder and tells everyone to run for their lives. He
runs into a small drain-pipe in the darkness, as the rat-catchers confront the two kids.
\Gls{Malicia} accuses them of hoarding the town's food supply, and asks them who their boss is. They
knock her out after getting tired of her chattering, and turn to \Gls{Keith}. After \Gls{Keith}
tries and fails to hit them, he is left with a broken flute and bleeding lips.

\subsubsection{\Gls{Mauri} watches the rat-catchers deal with \Gls{Hamn}}
\Gls{Mauri} watches the rat-catchers grab \Gls{Hamn} when he tries to save \Gls{Keith}, and take him
to the special cage full of hardy cannibalistic rats. \Gls{Hamn} manages to summon his inner rage to
keep the few remaining rats wary, and the rat-catchers wonder how he will do at the nightly
rat-hunts where other rat-catchers set their terriers against hordes of rats.

\subsubsection{\Gls{Mauri} struggles with a disembodied voice of a rat God}
\Gls{Mauri} listens to the rat-catchers talk about some expensive rat-piper that the mayor is due
to hire soon, as a mysterious force causes them to suddenly find it a good idea. He watches the
rat-catchers drag the children out of the rat-farm, and is left to find a way out through the dark
tunnels. He listens to the same disembodied voice asking him who he is, and turn hostile when it
realizes he is a cat.

\subsubsection{\Gls{Mauri} narrowly escapes the rat terminators hunting him down}
\Gls{Mauri} manages to resist the hypnotic voice long enough to crawl into an underground sewage
pit that leaves him caked in fermented mud. He figures out that the voice can see through his eyes,
and shuts them. He leaps onto the roof using a collapsed beam, and manages to avoid the rat
terminators trying to hunt him down since his own scent is masked by the sewage.

\subsection{}
\subsubsection{\Gls{Mauri} meets up with the rat leaders in the next cellar}
\Gls{Mauri} makes it to the next room with his eyes still closed, and is alarmed by his conscience
starting to gnaw at him, asking him to try and rescue the two kids. He meets up with \Gls{Peach}
and \Gls{Darktan}, who talk about the disembodied voice which spooked the rest of the clan, causing
them to scatter into the tunnels. \Gls{Beans} points out the need to come up with a plan to rescue
\Gls{Hamn}, forcing \Gls{Mauri} to reconsider his own plan to flee the town.

\subsubsection{\Gls{Mauri} describes the rat-catcher arenas where their dogs hunt down native rats}
\Gls{Mauri} describes the rat-catchers organizing show-matches where their terriers hunt down some
native rats thrown into an arena surrounded by high walls. \Gls{Darktan} is alarmed by the
possibility of \Gls{Hamn} meeting the same fate, and \Gls{Peach} insists that their own clan will be
able to organize a proper fight against the dogs if met with the same predicament.

\subsubsection{\Gls{Mauri} admits to having eaten one of the Awakened rats a long time ago}
\Gls{Sardines} returns from his scouting mission with \Gls{Nouri}, and describes the rat arena at
the edge of town, which has an overwhelming scent of dogs. \Gls{Darktan} decides to mount a rescue
operation to get \Gls{Hamn} out of the arena, and goes off to gather the other rats in his elite
force. Meanwhile, \Gls{Mauri} admits to having eaten one of their clan early on in the garbage dump,
and guesses that he gained sentience indirectly beacuse of this.

\subsubsection{\Gls{Keith} and \Gls{Malicia} struggle to think of a way out of their bindings}
\Gls{Mauri} is shocked to see \Gls{Beans} forgive him, after asking if he feels remorseful for
having eaten one of the Awakened rats. He reluctantly agrees to help \Gls{Beans} look for the kids,
as his conscience starts to overcome his sense of self-preservation. Meanwhile, \Gls{Malicia} asks
\Gls{Keith} if he has some convenient secret powers that might help them get out of their bindings.
\Gls{Keith} tries to remind her that they are not in a story, and that he is not a hero in disguise.

\subsubsection{\Gls{Mauri} leads \Gls{Peach} and \Gls{Beans} to the two bound kids}
\Gls{Malicia} is shocked to learn that there are more sentient rats, as \Gls{Mauri} guides them to
the cellar where the kids are locked up. \Gls{Peach} tries to light a candle stub, as \Gls{Keith}
warns \Gls{Malicia} not to make fun of the clan's names. \Gls{Peach} then gets to work cutting out
the kids' bindings with her knife, as \Gls{Malicia} watches amazed.

\subsubsection{\Gls{Sardines} leads the rats to the fighting arena}
\Gls{Sardines} leads \Gls{Darktan} and \Gls{Nouri} to the rat arena, and points to the ground level
from a high loft, where the dogs are kept tied up before the rat-hunts. \Gls{Darktan} looks at a
broken lantern nearby, and asks \Gls{Sardines} if he can lower himself using the elastic string he
picked up a while ago.

\subsubsection{\Gls{Hamn} is lowered into the rat arena with the dog \Gls{Jacko} on the hunt}
\Gls{Nouri} watches \Gls{Darktan} take out a match, and prepare to set fire to the barn where the
arena has been set up. He tells her to continue the arson in case he dies trying to set fire to the
haystacks scattered in the barn. \Gls{Hamn} is put into the pit with the other rats, and talks in
a human voice, when the other native rats flee from \Gls{Jacko}.

\subsubsection{\Gls{Darktan} and \Gls{Sardines} rescue \Gls{Hamn} from the rat-arena}
\Gls{Jacko} recalls the beatings he had received when he bit humans as a pup, and is flummoxed by
the rat that is talking human language. \Gls{Sardines} uses his bungee rope to rescue \Gls{Hamn},
with \Gls{Darktan} acting as a counterweight to haul them up into the beams. \Gls{Darktan} lets go
of the lamp he is holding, which lands on \Gls{Jacko}'s upturned nose, stunning him.

\subsubsection{\Gls{Darktan} escapes from the rat arena by biting \Gls{Jacko} in the genitals}
\Gls{Darktan} leaves \Gls{Jacko} bewildered when he refuses to run in fear, and instead takes his
chances with biting the dog's genitals. \Gls{Jacko} tries to escape the pit by standing up against
its walls, and allows \Gls{Darktan} to scurry across its back and leap out. \Gls{Darktan} then runs
across the barn, with the other dogs in hot pursuit, until he spots a gap in the planks for him to
dive into.

\subsubsection{\Gls{Keith} and \Gls{Mauri} poison the sugar used by the rat-catchers}
\Gls{Mauri} is taunted by the disembodied voice again, which calls itself `\Gls{Spider}', and
insists it will haunt his dreams, even if it cannot control his mind. Meanwhile, the rat-catchers
get back to their hut from the chaos at the arena, and make plans to close up their operation and
flee the town. \Gls{Mauri} tells them that he has liberated the kids, and they have mixed the rat
poison into the sugar the two of them just used in their tea.

\subsubsection{\Gls{Keith} and \Gls{Mauri} ask the rat-catchers about their motives}
\Gls{Darktan} falls into a rusted rat-trap, which \Gls{Nouri} manages to identify as a very old
model propped up by a single spring. She gnaws through the spring, stopping the claws from crushing
\Gls{Darktan} to death, just as he starts to accept his impending death. Meanwhile, \Gls{Keith}
interrogates the rat-catchers about their cruel treatment of the native rats, while reminding them
of how switftly the poison will kill them unless they take the antidote.

\subsubsection{\Gls{Spider} tries to influence \Gls{Mauri}'s mind during the interrogation}
\Gls{Spider} agrees with the rat-catchers when they outline their plan to artificially select for
rats that could stand up to the dogs in the arena, causing \Gls{Mauri} to almost lose his footing
on the roof beams of the hut. \Gls{Mauri} struggles against the voice of \Gls{Spider}, and asks
the rat-catchers what experiment they have been doing in the next cellar.

\subsubsection{\Gls{Darktan} refuses to set fire to the rat-arena, after his near-death experience}
The rat-catchers begrudgingly admit that they have created a rat-king in the next cellar, and hurry
to the food storage in the basement, where \Gls{Keith} tells them that there one dose of antidote
left. \Gls{Darktan} is poised with his lit match over a large haystack, but refuses to drop it,
seeing as how the humans in the rat-arena are all trapped in the barn with the doors shut tight.

\subsubsection{\Gls{Malicia} uses her history of tall tales to get rid of the angry mob}
\Gls{Malicia} reveals to \Gls{Keith} that the poison she mixed into the sugar was merely a laxative,
and shocks him by revealing that the antidote downstairs is also the same laxative. \Gls{Keith} is
relieved not to have to worry about killing the rat-catchers, just as a mob shows up to the front
door of the rat-catchers' office. \Gls{Malicia} tells them the truth about the events of the last
few hours, and they turn around, believing that she is telling one of her incredulous stories yet
again.

\subsubsection{\Gls{Hamn} dies surrounded by his clan}
\Gls{Mauri} runs around in the tunnels underneath the town, trying to track down \Gls{Beans}. He
arrives at the geothermal baths, and finds something red in the gutters that lead out from it.
Meanwhile, \Gls{Hamn} dies after returning to the central base of the clan, surrounded by his
lieutenants in the darkness. \Gls{Darktan} orders for the old rat to be formally buried instead of
eaten, and draws a sketch that will mark his grave.

\subsubsection{\Gls{Sardines} warns \Gls{Darktan} about potential challenges to his leadership}
\Gls{Sardines} recommends to \Gls{Darktan} that he play along with the story being spread by
\Gls{Nouri}, about him facing down the \Gls{DRat}, and returning with his life. He warns
\Gls{Darktan} that other senior rats will be trying to stake their claim to the leadership, as
\Gls{Darktan} expresses his concerns about \Gls{Beans} having gone missing.

\subsubsection{\Gls{Mauri} finds some of \Gls{Peach}' treasured possessions}
\Gls{Mauri} tracks down the book of children's stories usually hauled by \Gls{Peach}, and wonders
if she was forced to leave it behind in some sort of scuffle. The voice of \Gls{Spider} shows
\Gls{Mauri} that he is trapped by a line of the terminator rats, and asks him to keep going
forward, if he wishes to find the location of the disembodied voice.

\subsubsection{\Gls{Spider} takes control over the minds of the two kids}
\Gls{Spider} uses its mind-control on the two kids, persuading them to open the trapped rats in the
rat-farm, and forgetting all about the stories they have heard about rat kings. \Gls{Keith} tries
to recall something about rat-pipers, as \Gls{Malicia} moves to the trapdoor, to let the rats out
of the cages in the farm.

\subsubsection{\Gls{Peach} lights a matchstick in desperation, and \Gls{Sardines} catches its scent}
\Gls{Peach} and \Gls{Beans} are trapped in a dark tunnel, surrounded by the rat terminators, and
wonder what they can do against the voice of \Gls{Spider} in their heads. Meanwhile, \Gls{Darktan}
draws some blood from his own chest-wound, and smears it on the foreheads of his elite squad, as a
way to keep them focused on the smell of the sulphur coming from \Gls{Peach}' matchstick.
\Gls{Sardines} is worried that they have to go through the rat-farm in pursuit of the scent.

\subsubsection{\Gls{Mauri} is led to the place where \Gls{Spider} is holding \Gls{Beans} captive}
\Gls{Mauri} reaches the rat-farm, to see \Gls{Beans} and \Gls{Peach} surrounded by more of the
large terminator rats. \Gls{Spider} talks to \Gls{Beans} telepathically, outlining its plan to
spread its new clan of hardy rats to the nearby towns, to take revenge on the humans who gave them
the status of vermin.

\subsubsection{\Gls{Spider} tries and fails to recruit \Gls{Beans} to its ideology}
\Gls{Beans} rejects \Gls{Spider}'s idea of taking the fight to humans, when he realizes that it
considers individual rats expendable, and believes totally in artificial selection of the toughest
rats, even at the cost of all the weaklings. \Gls{Mauri} feels the pain that \Gls{Spider} tries to
inflict onto \Gls{Beans}'s mind, as his newest memories start to fade away. He sees \Gls{Spider}
lose its patience with \Gls{Beans}, and give the order to its soldiers to close in for the kill.

\subsubsection{\Gls{Keith} and \Gls{Malicia} are saved by the timely arrival of \Gls{Darktan}'s
    squad}
\Gls{Keith} and \Gls{Malicia} break out of their trance just as they are about to open up the cages
in the rat farms. They realize they have been tricked by \Gls{Spider}, just as the rat terminators
start to pour out of the adjacent cellar. \Gls{Darktan} arrives with his clan in time to save them
from \Gls{Spider}'s soldiers, and asks \Gls{Keith} to open the door to the room with the ladder
leading up to the ground level.

\subsection{}
\subsubsection{\Gls{Mauri} kills \Gls{Spider} by freeing the rats with the knotted tails}
\Gls{Mauri} loses almost all of his sentient mind, and is guided by instinct to attack \Gls{Spider},
when it stumbles out of the darkness to gloat. \Gls{Mauri}'s little remaining intelligence makes
him tear at the tails of the rat-king, freeing the constituent rats and ending the mind-control
that \Gls{Spider} has over the others. \Gls{Peach} accidentally sets fire to some straw in the
cellar, causing the rat soldiers to flee after they are suddenly released from \Gls{Spider}'s hold.

\subsubsection{\Gls{Mauri} successfully saves \Gls{Beans} by bargaining with \Gls{Death}}
\Gls{Mauri} limps out of the rat farm, with the flames now blazing, and slumps down next to
\Gls{Darktan} with \Gls{Beans} in his mouth. He dies, and bargains with \Gls{Death} for the life of
\Gls{Beans} by offering two of his own nine lives. \Gls{Death} is so surprised by a cat asking for
a rat's life to be spared, that he grants the request.

\subsubsection{\Gls{Mauri} comes back to life, and immediately starts scheming}
\Gls{Mauri} comes back to life, and \Gls{Keith} informs him that \Gls{Beans} is recovering from his
burns, after coughing out a lot of mucus from his lungs. \Gls{Mauri} is reminded of the Rat Pipe who
is set to come to town and work his magic on the rats. He rejects \Gls{Keith}'s idea of caging up
the native rats to stop them from following the \Gls{Piper}, and decides to come up with a better one.

\subsubsection{\Gls{Dopp} watches amazed as some of \Gls{Darktan}'s rats catch \Gls{Spider}'s
    soldier rat}
\Gls{Darktan} gets his squads organized to go clear out the tunnels underneath the town, and to
gather any stray native rats that they might find in the process. At sunrise, \Gls{Dopp} watches
some rats chase down a large native rat in his guard cabin at the town's only watch house, and
is shocked when one of the rats salutes him before dragging off the native rat. He decides to call
this a hallucination caused by bad alcohol, even as he hears a faint chorus coming from the pipes.

\subsubsection{\Gls{Knopf} and \Gls{Dopp} try to greet the \Gls{Piper}}
\Gls{Dopp} and his corporal \Gls{Knopf} are alarmed to see the rat piper ride into town, with an
old man leading a donkey cart close behind. The \Gls{Piper} asks for the mayor to be brought to him,
as well as a hearty breakfast for himself. \Gls{Dopp} feels insulted, but is quickly reminded by
\Gls{Knopf} that the \Gls{Piper} was famous for being able to influence human minds with his music,
even to the point of getting people to drown themselves in a river.

\subsubsection{\Gls{Dopp} brings the mayor to the town square}
\Gls{Dopp} hurries to the mayor's home, and finds him fretting about \Gls{Malicia}, who hasn't been
home all night. The two of them hurry to the town square, to see the \Gls{Piper} criticizing the
sausages brought by \Gls{Knopf}, with some curious townsfolk already forming a crowd around him.
The mayor is asked to see the \Gls{Piper}'s assistant, who promptly lists out the charges for
ridding the town of its rats.

\subsubsection{\Gls{Keith} challenges the \Gls{Piper} according to \Gls{Mauri}'s plan}
\Gls{Keith} interferes with the mayor's desperate pleading, and claims that he can charm more rats
than the \Gls{Piper}. \Gls{Mauri} hides in the crowd, and asks for \Gls{Keith} to be given a chance,
given how he might be cheaper than the \Gls{Piper}. The \Gls{Piper} decides to give \Gls{Keith} a
chance, and agrees to part with his magical rat pipe if he loses the challenge.

\subsubsection{\Gls{Darktan} ensures that no rats in the town can hear the \Gls{Piper}'s tune}
\Gls{Sardines} dances along the street when \Gls{Keith} blows a tune on the old trombone owned by
\Gls{Knopf}. When it is the \Gls{Piper}'s turn to charm some rats, \Gls{Darktan} gives the signal
for everyone in his clan to plug their ears with cotton wool. \Gls{Malicia} checks that the native
rats in the farm are soundproofed using some blankets, as the others in the clan block the tunnel
network with mud to stop the sound propagation.

\subsubsection{\Gls{Keith} learns about the true nature of the \Gls{Piper}}
The \Gls{Piper} takes \Gls{Keith} to the town square, away from any townsfolk, and congratulates him
on his victory. He offers \Gls{Keith} his pipe, and tells him that it merely blows a supersonic
note that rats find repulsive. \Gls{Keith} is surprised to learn that the rest of the tales
surrounding the \Gls{Piper} are all made-up, and are designed to intimidate the rural people of the
Disc into paying his fee.

\subsubsection{\Gls{Keith} puts the second part of his plan into motion}
\Gls{Keith} asks the \Gls{Piper} to play a simple tune audible to humans, and guarantees him that
the rats will follow him out of the town as if charmed. The \Gls{Piper} agrees to play along, and is
surprised when \Gls{Keith} offers him half of the bounty put up by the mayor. \Gls{Darktan} receives
the signal for the exodus, and ensures that some of his squad guide the town's native rats behind
the \Gls{Piper} as he plays his fancy tune.

\subsubsection{\Gls{Malicia} asks her father to make a deal with the Awakened rats}
The townsfolk are all pleased to see the rats follow the piper to a bridge, and jump into the river.
\Gls{Darktan}'s clan rats are reminded to use their instinctive swimming ability to wash up on
a short distance downriver, and make their way back to town. \Gls{Malicia} asks her father to gather
the town council, and negotiate a permanent settlement with \Gls{Darktan}, even as her father finds
it horrifying to hear a rat talk human words.

\subsubsection{\Gls{Mauri} presents his ideas about the Awakened rats to the town council}
\Gls{Mauri} outlines his plan to have the rats be a formal pest control unit for the town, as well
as a tourism novelty that might bring in lots of revenue. The mayor has his reservations, until the
other in his council start to think of the financial opportunity in selling souvenirs and rat-themed
merchandise. \Gls{Darktan} and \Gls{Beans} take \Gls{Mauri} aside, and ask him if the grand plan to
move to a deserted island is to be exchanged for a co-operative relationship with the folk in the
small town.

\subsubsection{\Gls{Keith} talks to \Gls{Malicia} about settling down in the town permanently}
The mayor seems to go along with \Gls{Mauri}'s plan, just as \Gls{Malicia} returns the children's
picture book to \Gls{Peach}, after restoring it to the best of her ability. The mayor takes
\Gls{Darktan} to his office away from the furious negotiations in progress at the town hall, and
talks about the burden of leadership. Meanwhile, \Gls{Malicia} tells \Gls{Keith} that she does not
have any sisters, and hopes he will settle down in the town.

\subsubsection{\Gls{Mauri} moves on to his next adventure, as the rats settle down in the town}
The town prospers as a tourist hub for its rat-themed attractions, including the massive clock where
rats strike the gongs, and the elaborate song and dance shows put on by \Gls{Sardines}. Meanwhile,
\Gls{Mauri} goes over to the next town, and spots another poor orphan down on his luck, so that
he can start another one of his adventures.