\section{Thief of Time}


\subsection{}
\subsubsection{\Gls{Death} watches the Auditors plan to wipe out intelligent life on the Disc}
\Gls{Wen} comes out of a cave after achieving enlightenment, and tells his apprentice \Gls{Clod}
that he can now manipulate time. Meanwhile, the \Gls{DRat} shows off its new contraption proving
that buttered toast always falls butter side down, as \Gls{Death} watches amused. He then goes to
his mirror, where he notices the Auditors scheming to get rid of intelligent life on the Disc, since
it messed with their idea of order and lawfulness.

\subsubsection{\Gls{Ogg} is visited by the same man through many stages of her life}
A mysterious man knocks on the door of \Gls{Ogg} at midnight, asking for her services as a midwife.
She points out her inexperience, and is shocked to see the stranger vanish. The stranger visits her
again twenty years later, having traveled through time to ask for her services once again. She is
visited a third time when she is an experienced old woman, and agrees to perform the delivery.

\subsubsection{\Gls{Jeremy} is forced to defend the accuracy of his clocks}
The \Gls{DRat} finishes showing the visions of \Gls{Ogg} to \Gls{Death}, making him realize that
\Gls{Susan} would need to be enlisted once again. \Gls{Jeremy}, an orphan raised and trained by
the Clockmakers' Guild, receives a wealthy customer at his shop. The lady introduces herself as
\Gls{Myria}, and starts asking questions about the limits of accuracy he is able to achieve.

\subsubsection{\Gls{Myria} offers \Gls{Jeremy} the chance to build a truly accurate clock}
\Gls{Myria} tells \Gls{Jeremy} that she can offer him the finest metal alloys, and a large bounty
for building the Disc's first accurate clock. She correctly guesses that the honour of achieving
this feat is of much greater interest to him than any payment in gold, and hands him a book of
fairy tales as a lead.

\subsubsection{\Gls{Susan} is summoned by \Gls{Death} for help with his latest problem}
\Gls{Susan}, now a schoolteacher at a progressive school that discourages competitiveness and
rigour, applies the curriculum she learnt from her own school to teach the children about time
zones. She sees a letter from \Gls{Death} appear on her desk, and is angry at her regular life
being intruded upon by her grandfather.

\subsubsection{\Gls{MNov} and \Gls{Rinpo} discuss the issue of \Gls{Ludd}}
In the high mountains at the Hub of the Discworld, the temple of the History Monks lies in the
highest, most remote slopes of all. The \Gls{MNov} talks to \Gls{Rinpo}, assistant to the
\Gls{AbbotH}, about \Gls{Ludd}, the talented child scouted by Master \Gls{Soto}, in their
Ankh-Morpork branch. The \Gls{MNov} claims that \Gls{Ludd} is an apprentice in the Thieves' Guild,
who happens to be so fast with his hands that he might be subconsciously manipulating time.

\subsubsection{\Gls{Rinpo} suggests pawning \Gls{Ludd} off to \Gls{Sweep}}
The \Gls{MNov} bemoans his inability to get \Gls{Ludd} to comply with his curriculum, and claims
that he is too smart to fit into the school at the monastery. \Gls{Rinpo} in turn, suggests
attaching \Gls{Ludd} to \Gls{Sweep}, who is another problematic monk stationed in Ankh-Morpork as
punishment.

\subsubsection{\Gls{Jeremy} is forced to deal with \Gls{Igor} sent by \Gls{Myria}}
\Gls{Jeremy} has a vivid dream of a story he read in the book of fairy tales, about a watchmaker
who tried to imprison \Gls{Time}. He wakes up the next morning, and is surprised to find a package from
Uberwald containing \Gls{IgorA} inside a crate. \Gls{Jeremy} finds a letter from \Gls{Myria} in the
crate, and realizes that she sent \Gls{IgorA} through the new employment agency for the network of
Igors.

\subsubsection{\Gls{Ludd} meets \Gls{Sweep} and is appalled by his austere life}
\Gls{Ludd} arrives at \Gls{Sweep}'s garden in Ankh-Morpork, and hands him the letter from the
\Gls{AbbotH} of the History Monks. He is shocked to see someone as celebrated as \Gls{Sweep} living
a modest life, ranked lower than the novice monks. \Gls{Sweep} leads him into the temple, and ushers
him into a side-room meant for practicing martial arts. A junior monk unaware of his identity
challenges him to single combat, and the master asks \Gls{Sweep} not to do any real damage.

\subsubsection{\Gls{Jeremy} shows \Gls{IgorA} the plans for a Glass Clock}
\Gls{Jeremy} wakes up from his latest dream about the Glass Clock that imprisoned \Gls{Time}, and
finds detailed sketches for it scrawled on his bedsheets. He realizes that he has been writing in
his sleep, desperate to pass on the information to his waking self, and shows \Gls{IgorA} the plans.
\Gls{IgorA} causally identifies it as a clock his grandfather had built, which had suddenly vanished
from existence by changing the timeline.

\subsubsection{\Gls{Sweep} takes \Gls{Ludd} further into the Temple of History}
\Gls{Sweep} gets the challenger to back down when he announces his name, and takes \Gls{Ludd} along
to the next room, where he is told to catch some fast moving balls ejected by a machine with rows
of holes in it. \Gls{Ludd} fails to catch them as they are too fast, and \Gls{Sweep} tells him that
he slowed them down just enough to not cause damage.

\subsubsection{\Gls{Ludd} almost falls into the pit of colored sand within the Temple of History}
\Gls{Ludd} is amazed by a large room with a pit of colored sand, trying and failing to arrange
itself into spontaneous ordered patterns. He falls off one of the narrow rope bridges above the
chasm, and has a flashback to \Gls{Soto} recruiting him into the Temple of History, when he fails
one of his jobs as a novice Thief. Back in the present, \Gls{Sweep} catches \Gls{Ludd} at the
edge of the bridge, and hauls him back up, asking him to keep his eyes closed to avoid the vertigo.

\subsubsection{\Gls{Ludd} is led out of the Mandala chamber by \Gls{Sweep}}
\Gls{Ludd} is escorted to a tunnel leading out of the sand room, as the other monks marvel at the
vivid patterns taking shape where the boy would have otherwise landed. Back in the distant past,
\Gls{Wen} tells \Gls{Clod} to gather some colored sand to build the Mandala, and establishes the
Temple of History in a time bubble which endlessly repeats the same day of good weather.

\subsubsection{\Gls{Sweep} talks to the \Gls{AbbotH} about \Gls{Ludd}'s innate talent}
\Gls{Sweep} enters the \Gls{AbbotH}'s chamber, where he is just a toddler in his latest
reincarnation, and is asked for his opinion about \Gls{Ludd}. He chooses to hide the fact that
the Mandala reacted to his presence, and only talks about the boy's ability to predict where the
fast-ball would be launched.

\subsubsection{\Gls{Susan} tries to fend off \Gls{Frout}'s attempts to chastise her}
\Gls{Frout}, the headmistress of \Gls{Susan}'s school, and pioneer of the new method of Learning
by Play, tries to argue with \Gls{Susan} about her stringent teaching methods. \Gls{Susan} in turn,
tells her that she is preparing the children for a better future as skilled adults, unafraid of
the superhuman beings they might encounter in daily life. The \Gls{DRat} shows up in \Gls{Frout}'s
room, forcing \Gls{Susan} to pause time, and listen to its message.

\subsection{}
\subsubsection{\Gls{Death} tells \Gls{Susan} that the time is coming to an end}
\Gls{Sweep} watches the senior monks tell the \Gls{AbbotH} that \Gls{Ludd} is now too old to pass
through their training regimen, and takes it upon himself to teach him their methods. Meanwhile,
\Gls{Death} talks to \Gls{Susan} at a gentleman's club next to her school, and tells her that he
sees time freezing at some point next week. He suspects the Auditors are at play again, and asks
her for help investigating the threat.

\subsubsection{\Gls{Susan} learns about the child of \Gls{Time}, who is superpowered like her}
\Gls{Death} tells \Gls{Susan} that the fairy tale about the Glass Clock capturing \Gls{Time} is
based on true events, and that the History Monks had to borrow many centuries worth of time from a
prehistoric era to rectify the damage. He is then forced to reveal the son birthed by the Goddess
of \Gls{Time} long ago, when she fell in love with a human.

\subsubsection{\Gls{Hopkins} does a regular check on \Gls{Jeremy}}
\Gls{Hopkins}, the Secretary of the Clockmakers' Guild, comes to \Gls{Jeremy}'s home to check in
on his sanity, and is shocked to find \Gls{IgorA} answer the door. He tops up \Gls{Jeremy}'s
medication, and is delighted to see him indulging in a new hobby, as he walks through the workshop
strewn with crystals. After \Gls{Hopkins} leaves, \Gls{Jeremy} pours the medicine into a sink, and
tells \Gls{IgorA} that it dulls his mind.

\subsubsection{\Gls{Susan} accepts \Gls{Death}'s mission}
\Gls{Susan} returns to \Gls{Frout}'s office, and writes a letter requesting a few days off, before
resuming time. Her subliminal suggestions work, and \Gls{Frout} grants her request, while refusing
her demand for a pay raise. After finishing up the school day and sending the children home,
\Gls{Susan} thinks about the possibility that \Gls{Death} is once again prompting her to do his
dirty work for him.

\subsubsection{\Gls{Sweep} talks to \Gls{Ludd} about his learnings in Ankh-Morpork}
\Gls{Sweep} shows \Gls{Ludd} a yellowing copy of the Ankh-Morpork Tourist Guide, stuffed with
words of wisdom. \Gls{Ludd} spots the claim that the city has everything written on the back cover,
and \Gls{Sweep} tells him that he interpreted it to mean that he could also find enlightenment
there. \Gls{Sweep} then tells \Gls{Ludd} that most stories of his heroism are exaggerated, and that
he never uses violence to achieve his ends.

\subsubsection{\Gls{Ludd}'s duel with \Gls{Sweep} is stopped by an emergency summons}
\Gls{Ludd} returns the small trinket stolen from \Gls{Sweep}, who is surprised at his innate ability
to manipulate time. \Gls{Ludd} then challenges \Gls{Sweep} to a duel in the gym, and is alarmed to
see fear cloud his face. The duel is interrupted when a senior monk runs in to call an emergency
meeting in the Mandala chamber, for all monks approved to step out of the monastery.

\subsubsection{\Gls{Sweep} senses a massive leak in the time storage devices of the monastery}
\Gls{Ludd} senses a disturbance in the valley below the monastery, as \Gls{Sweep} takes him to the
Mandala chamber the long way round. He senses the time storage devices leaking, and expects a
ruckus in the monastery once the others detect the anomaly. A long time ago, \Gls{Wen} tests out
his first time storage device by rewinding and replaying \Gls{Clod}'s words.

\subsubsection{\Gls{Sweep} marvels at \Gls{Ludd}'s ability to handle the time storage units}
In the time vault, \Gls{Sweep} finds the caretaker dead from a massive discharge of time that aged
him fifty thousand years in an instant. He gathers the other monks in the vault, and tells them to
get ready for an emergency shutdown of the time storage units. \Gls{Sweep} is surprised by
\Gls{Ludd}'s instinct for balancing the loads on time sources and sinks in the vault, and lets him
pair up containers in order to stem the leakage of time.

\subsubsection{\Gls{Death} collects the vault-keeper's soul after the time leak is stopped}
When \Gls{Death} comes to collect the vault keeper's soul, he notices his hourglass still having
time left, and tells him that he has died too early for his next scheduled reincarnation. When
the vault keeper points out \Gls{Ludd}'s impressive handling of the time leakage, \Gls{Death} is
alarmed to see no-one at the control center visible to him.

\subsubsection{\Gls{Sweep} talks to the \Gls{AbbotH} about the possibility of a glass clock being
    made}
\Gls{Sweep} tells the vault keepers to forget the heroics of \Gls{Ludd}, and take the credit for
dealing with the time leaks. He decides not to reveal the full extent of his abilities to the
\Gls{AbbotH}, and swiftly drags him away from the vault. They travel to the Mandala chamber, where
the \Gls{AbbotH} asks \Gls{Sweep} about the disturbance he felt in the plains. He guesses correctly
that someone is close to making a glass clock again, considering how the time storage units went
haywire the last time.

\subsubsection{\Gls{Sweep} manipulates the \Gls{AbbotH} into approving his tour of Ankh-Morpork}
In the \Gls{AbbotH}'s room, \Gls{Sweep} is forbidden from going to Uberwald, where the last glass
clock had been built. The \Gls{AbbotH} then concedes \Gls{Sweep}'s request to train his new
student in Ankh-Morpork, while the new batch of field operatives poke around in Uberwald for leads.
\Gls{Sweep} asks \Gls{Ludd} to pack up and leave the Monastery, and claims that the new glass clock
is likely being built in the city.

\subsection{}
\subsubsection{\Gls{Sweep} visits \Gls{Qu} to borrow his portable time storage units}
\Gls{Sweep} visits \Gls{Qu}'s workshop next to the monastery, and asks for the two portable time
storage units he has been working on. \Gls{Qu} tries to give him some of his newest concealed
weapons, but \Gls{Sweep} declines his offer. He leaves via the back door with \Gls{Ludd}, having
masked the time storage units to look like bedrolls.

\subsubsection{\Gls{IgorA} expresses his concerns about \Gls{Myria}}
\Gls{Sweep} is impressed by the ease with which \Gls{Ludd} is able to keep up with his time-walk
through the snowy mountains outside the Monastery's bubble of eternal spring. Meanwhile, \Gls{IgorA}
tries to tell \Gls{Jeremy} that \Gls{Myria} seems to be floating on the ground sometimes, and has
his concerns dismissed. He then wonders how she beat him to the city, when he was traveling by
express coach, given that she had hired him and \Gls{Jeremy} on the same day.

\subsubsection{\Gls{IgorA} suspects foul play in \Gls{Myria}'s demeanour}
\Gls{IgorA} is happy with his meticulous approach to contracting the pieces for the glass clock to
the artisans in Ankh-Morpork, in a way that did not give away the final design. \Gls{Myria} is
impressed by \Gls{Jeremy}'s progress, and hastily refuses his offer for dinner. After she leaves,
\Gls{IgorA} once again notices her hovering over the pavement, and decides to tail her into a dead
end where she vanishes.

\subsubsection{\Gls{Sweep} talks to \Gls{Ludd} about the first glass clock}
\Gls{Sweep} tells the story of the first glass clock in Uberwald many years ago, and of how he had
been too late to stop the lightning rod triggering the trapping of \Gls{Time}. He then talks about a
secret psalm written by \Gls{Wen}, in the form of a love song for \Gls{Time}, who he described as a
woman. \Gls{Ludd} works out that the portable time storage units are meant to sustain them in case
the second glass clock works, freezing all time.

\subsubsection{\Gls{Myria} has second thoughts about discarding the human form}
\Gls{Myria}, an auditor inhabiting a body crafted by the others, realizes that they cannot read
her mind, and decides not to tell them about the pleasures of being mortal. She plays along with
their plan to get the glass clock done, and immediately abandon the vessel, while thinking about of
ways to remain mortal.

\subsubsection{\Gls{Sweep} and \Gls{Ludd} encounter a captured yeti}
\Gls{Sweep} confronts a group of hunters holding a yeti captive, and distracts them, as \Gls{Ludd}
uses his time-slowing abilities to take them down. He then orders \Gls{Ludd} to climb into the
yeti's arms so they can rest on the way to Ankh-Morpork. When \Gls{Ludd} is alarmed at being forced
to do the dirty work in the encounter, while \Gls{Sweep} tried to get the hunters to recognize him.

\subsubsection{\Gls{IgorA} becomes more suspicious of \Gls{Myria}}
\Gls{IgorA} points out the difficulties that show up to halt their progress after every visit by
\Gls{Myria}, and has his concerns dismissed by \Gls{Jeremy}. He then has her followed, and learns
that she is taking in the city's culture to the fullest, while never visiting a restaurant or having
food delivered to her quarters.

\subsubsection{\Gls{Susan} goes to a library to read about \Gls{Time}}
\Gls{Susan} goes through the history books, while making note of the obvious attempts to surgically
remove inconvenient parts of the past. She then thinks about the absurdity of \Gls{Time} having a
child with a mortal man, and reminds herself of her own inherited talents. \Gls{Binky} arrives to
take her on the hunt for \Gls{Time}'s child, with the \Gls{DRat} and \Gls{Quoth} in tow.

\subsubsection{\Gls{Ludd} watches \Gls{Sweep} decapitate the yeti}
\Gls{Ludd} is alarmed to see the yeti at peace with \Gls{Sweep}'s idea of cutting its head off.
He learns that the \Gls{AbbotH} has made a special arrangement with them of cyclically going
extinct and reincarnating at the species level, while wondering what use \Gls{Sweep} could possibly
have for the head.

\subsubsection{\Gls{Death} gives \Gls{Susan} the hourglasses of \Gls{Sweep} and \Gls{Ogg}}
\Gls{Death} reaps the soul of a serial dwarf killer in Ankh-Morpork, and is glad to see \Gls{Susan}
arrive. He tells her that the end of the world requires the horsemen to ride out into the world,
leaving him incapable of tracking down the glass clock. He hands her the hourglasses of \Gls{Sweep}
and the midwife who delivered the son of \Gls{Time}, while telling her that the boy was likely to
be in the monk's company.

\subsubsection{\Gls{Sweep} talks about they yeti practice of save-scumming life}
\Gls{Sweep} explains to \Gls{Ludd} that the yeti have evolved the ability to save-scum through
life by resetting themselves to a predetermined checkpoint in time, with full memory of what
happened in their personal future before it got reset. The decapitated yeti returns itself to the
time before its head was cut off, and continues the journey downhill.

\subsubsection{\Gls{Susan} visits \Gls{Ogg} to find out about the child of \Gls{Time}}
\Gls{Susan} visits \Gls{Ogg}'s cottage, and asks about the mysterious man who might have summoned
her for a delivery. She notices \Gls{Ogg} struggling against violating the privacy of the mother,
and tries to appeal to her good nature by reminding her that the boy needs to know about his
heritage. She then notices a small hourglass on \Gls{Ogg}'s shelf, and learns that it was a day's
time given as payment for her services.

\subsubsection{\Gls{Ogg} narrates the story of delivering \Gls{Time}'s daughter}
\Gls{Death} finds \Gls{Pesti} in a nursing home, and reminds him of the summons to ride out into
the world, ahead of the coming Apocalypse. Meanwhile, \Gls{Ogg} talks about delivering the child of
\Gls{Time}, and contradicts \Gls{Susan} when she claims it was a boy who was abandoned at the
Thieves' Guild.

\subsubsection{\Gls{Myria} is suspected of foul play by the other Auditors}
\Gls{Myria} thinks about the small problems holding up \Gls{Jeremy}'s glass clock, and tries to
hide the fact that she is causing the delays herself when the other Auditors interrogate her. They
decide to give shape to six more human forms, so that they can check in on \Gls{Jeremy}'s progress
themselves. \Gls{Myria} tries to get them to don suitable disguises, and insists on allowing their
bodies to breathe.

\subsubsection{\Gls{Ludd} and \Gls{Sweep} steal a witch's broomstick}
\Gls{Ludd} asks \Gls{Sweep} about the human settlement down in the valley, and learns that they are
going to steal a broom from one of the witches to fly to Ankh-Morpork. \Gls{Sweep} then points out
a raven that has been tailing them for a while, and \Gls{Ludd} dismisses it as coincidence.
\Gls{Quoth} is outwitted by \Gls{Sweep} into revealing his true nature, and curses the \Gls{DRat}
for sending it undercover.

\subsubsection{\Gls{Sweep} flies to Ankh-Morpork with \Gls{Ludd}}
\Gls{Death} finds \Gls{Famine} and is dismayed to learn that he is unwilling to ride out to herald
the Apocalypse. Meanwhile, \Gls{Sweep} tries to tell \Gls{Ludd} that they cannot slow time on the
broomstick, for fear of reacting with its innate magical field. They follow the network of
semaphore towers leading to Ankh-Morpork, gliding far above the ground.

\subsubsection{\Gls{Jeremy} and \Gls{IgorA} face the accountants of \Gls{Myria}}
The Auditors come to \Gls{Jeremy}'s workshop with \Gls{Myria}, and engineer a thunderstorm when
\Gls{IgorA} tells them that the clock cannot be jumpstarted with stored electricity. \Gls{Hopkins}
shows up on one of his regular visits, and remarks on the beauty of the glass clock, oblivious to
the supernatural visitors standing in the workshop.

\subsubsection{\Gls{Sweep} asks \Gls{Ludd} to try and locate the glass clock ahead of the lightning
    strike}
\Gls{Sweep} asks \Gls{Ludd} to summon his latent powers when they reach the gates of Ankh-Morpork,
running through the fields when the thunderclouds make flying too risky. \Gls{Ludd} is surprised to
see \Gls{Sweep} push the limits of safe time-manipulation as taught in the monastery, and manages
to keep up without knowing how.

\subsection{}
\subsubsection{\Gls{Myria} sabotages the glass clock}
\Gls{Myria} is astonished to see the other auditors come up with the excuse of religion to avoid
the tea and biscuits presented by \Gls{IgorA}, as \Gls{Hopkins} takes his cup. \Gls{Jeremy}'s
psychosis starts to show itself, prompting \Gls{Hopkins} to give him a large dose of his medicine.
\Gls{Myria} decides to use the distraction to throw a hammer at one of the delicate glass mechanisms
pivotal to the glass clock's functioning.

\subsubsection{\Gls{Death} is surprised to see all the other horsemen express disdain for the
    Apocalypse}
\Gls{Death} visits \Gls{War}, who is now retired from his life as the patron of conflict, and lives
a quiet life with his wife, a former valkyrie. He is dismayed to see the changes in \Gls{War}'s
outlook on his duties, and realizes he will be the only horseman to ride out for the Apocalypse.

\subsubsection{\Gls{Ludd} is too late to stop the glass clock from starting up}
\Gls{Myria}'s hammer is caught midair by one of the Auditors, and \Gls{Jeremy} sets the glass clock
in motion ahead of the lightning storm gathering above the city. Meanwhile, \Gls{Ludd} runs to
the lightning rod rising above the city's skyline, and notices \Gls{Sweep} failing to keep up with
the extreme time-dilation. He is too late to stop the activation of the glass clock, and watches
time freeze.

\subsubsection{\Gls{Soak} mysteriously breaks through the time freeze}
\Gls{Soak} is somehow able to break through the freezing of time, and brings out his fancy horse to
investigate the activation of another glass clock. \Gls{Ludd} notices a bottle of milk left by
\Gls{Soak} in the place where \Gls{Sweep} had been before the freeze. As he realizes that he cannot
wind up his own portable time storage, \Gls{Susan} shows up to help him, after confirming that he
is not a threat.

\subsubsection{\Gls{Susan} saves \Gls{Ludd} from an Auditor in \Gls{Jeremy}'s workshop}
\Gls{Susan} enters \Gls{Jeremy}'s workshop after reassuring \Gls{Ludd} that \Gls{Soak} would keep
\Gls{Sweep} safe. She identifies \Gls{IgorA} and \Gls{Hopkins}, and wonders where the real designer
of the glass clock has gone off to. When an Auditor shows up, she asks \Gls{Ludd} to hide and kills
it with a wrench.

\subsubsection{\Gls{Sweep} recovers in \Gls{Soak}'s dairy}
\Gls{Sweep} wakes up in \Gls{Soak}'s dairy, and realizes that he is the secret fifth horseman that
left before they were formally introduced to the world as a group. Meanwhile, \Gls{Susan} and
\Gls{Ludd} come out onto the street, and notice hundreds of Auditors converging on a city square.
\Gls{AudWhi} declares himself the leader of the Auditors, and puts a stop to more of them adopting
human forms.

\subsubsection{\Gls{Susan} helps \Gls{Ludd} realize that he can move through frozen time by himself}
\Gls{Susan} figures out that \Gls{Ludd} does not need the portable time storage unit to keep moving
through the frozen world, and asks him to use his instinct to point the way forward. Meanwhile,
\Gls{Sweep} tries to get \Gls{Soak} to reveal his real name, and realizes that he will have to work
it out himself.

\subsubsection{\Gls{Susan} and \Gls{Ludd} sneak through the Art Museum}
\Gls{AudWhi} watches the other mortal Auditors start to pick up expertise on different subjects,
now that their minds are closed to each other. He realizes that decisions used to be made by
consensus, precisely so that no blame could be assigned to any particular Auditor. \Gls{Susan} leads
\Gls{Ludd} through the Art Museum, and notices the mortal Auditors busy appreciating art in the
main gallery.

\subsubsection{\Gls{AudWhi} asks the other Auditors to track down the intruders in the Museum}
\Gls{AudWhi} asks a group of Auditors to investigate the art in the museum, and they respond by
deconstructing the paintings down to their constituent atoms. They fight off a group of Auditors
trying to corner them, and notice others trying to study their moves. In the attic, \Gls{Myria}
rescues them from another group seeking to kill them, and asks them to follow her to safety.

\subsubsection{\Gls{Myria} tells \Gls{Ludd} that \Gls{Jeremy} is his brother}
\Gls{Myria} tells \Gls{Ludd} that the man who made the glass clock is his brother, and decides to
keep the truth hidden for the moment. She explains that the taste of food is capable of shutting
down the mind of a mortal Auditor, since they have no history of sensory experience as intense as
chocolate. \Gls{Susan} thinks back to \Gls{Ogg} telling her that \Gls{Time} had given birth to
twins that were temporally not the same age.

\subsubsection{\Gls{Susan} reveals the true relationship between \Gls{Jeremy} and \Gls{Ludd}}
\Gls{Susan} tells \Gls{Ludd} that \Gls{Jeremy} is not his twin brother, but is another version of
him from the past. She points out the fact that \Gls{Ludd}'s words are being mouthed by the
unconscious \Gls{Jeremy}, and pinches the watchmaker's hand to see the pain replicated in
\Gls{Ludd}'s face. Against her advice, \Gls{Ludd} touches \Gls{Jeremy}'s palm, making both of them
vanish in a flash of blinding white.

\subsubsection{\Gls{Myria} deals with the Auditors stopping them from leaving the Art Museum}
\Gls{Susan} finds an elevator to take her down, and \Gls{Myria} leaves a box of chocolate on the
floor for the Auditors waiting to apprehend them. The sensory overload kills all of the Auditors
keeping watch, and \Gls{Susan} contemplates jumping off a balcony using a drainpipe for support.
\Gls{Ludd}, who has now become a mass of immaterial blue wisps, tells her to head to the glass
clock so that he can recover his strength.

\subsection{}
\subsubsection{\Gls{Susan} asks \Gls{Myria} to take as many chocolates as she can for self-defense}
\Gls{Susan} suggests resupplying at a local chocolatier, before they run into Auditor reinforcements
sent by \Gls{AudWhi}. Meanwhile, \Gls{Sweep} correctly guesses \Gls{Soak}'s real name as they walk
past an undertaker's office. Inside the chocolate shop, \Gls{Susan} suggests the new name
\Gls{Unity} for \Gls{Myria}, and asks her to load up on the chocolates stacked on the shelves.

\subsubsection{\Gls{Sweep} tries to appeal to \Gls{Soak}'s pride and vanity}
\Gls{Sweep} calls out \Gls{Kaos} by his real name, and reminds him that humanity has moved on from
the early days when he inspired fear and reverence. He successfully gets \Gls{Kaos} riled up, by
reminding him that the Auditors would reduce the world to pure order, leaving no one to worship or
fear him. \Gls{Kaos} hurries back to his dairy to dig out his old armour, leaving \Gls{Sweep} to
fend off \Gls{AudWhi} and his horde.

\subsubsection{\Gls{Susan} saves \Gls{Sweep} from the mortal Auditors}
\Gls{Sweep} is saved from \Gls{AudWhi} and the horde of Auditors by \Gls{Susan} and \Gls{Unity},
as they throw their chocolate at the crowd. \Gls{Susan} then winds up \Gls{Sweep}'s portable time
storage unit, and tells him that \Gls{Ludd} has become a disembodied spirit. Meanwhile, \Gls{Death}
attempts to ask the Auditors to stop the time freeze, and is interrupted by a mysterious figure in
white robes.

\subsubsection{\Gls{Death} and his three horsemen fight the Auditors}
\Gls{Death} waits for the other three horsemen to assemble in the pocket dimension of the Auditors,
and reminds them that the Apocalypse of frozen time was offensive to all life on the Disc. The
horsemen charge the Auditors, as the Angel heralding the apocalypse hastily searches his book for
\Gls{Kaos}, who is missing.

\subsubsection{\Gls{Sweep} takes on the Auditors patrolling the streets}
\Gls{Ludd} tells \Gls{Susan} that he can detect \Gls{Death} fighting the Auditors in their home
realm, and asks her to move closer to the glass clock. He asks \Gls{Sweep} to distract the Auditors
scouring the streets, while \Gls{Susan} escorts him to \Gls{Jeremy}'s workshop. \Gls{Sweep} gets
ready to save-scum his own life like the yeti, and steps out onto the street with his broom.

\subsubsection{\Gls{Kaos} joins the other horsemen in their fight against the Auditors}
\Gls{Kaos} joins the fight against the Auditors, much to the relief of \Gls{Death}. Meanwhile,
\Gls{Unity} is captured by the mortal Auditors commanded by \Gls{AudWhi}, as \Gls{Sweep} manages to
rewind his body back to life. \Gls{Sweep} throws the last few chocolates into his mouth as it opens
reflexively from the shock of hearing the monk's voice after just decapitating him.

\subsubsection{\Gls{Sweep} escapes the Auditors, as a fight for leadership breaks out between them}
\Gls{Susan} is dragged into the glass clock's event horizon by \Gls{Ludd}, who stops her body from
being compressed to the point of death. \Gls{Sweep} is pleased to see the other mortal Auditors
fight amongst themselves for leadership, and sneaks off with \Gls{Unity}, as the fight in the
Auditors' home realm comes to an end.

\subsubsection{\Gls{Ludd} takes over the role of \Gls{Time} from his mother}
\Gls{Susan} finds herself on the other side of the glass clock's event horizon, and sees \Gls{Wen}
embrace his son \Gls{Ludd}, who has now recovered a human form. \Gls{Wen} takes her to a private
garden, which represents a frozen moment in time, as \Gls{Ludd} inherits the duties of his mother,
finally freeing her to rest alongside her lover. He breaks the glass clock, shattering history,
and depositing \Gls{Susan} in a muddy riverbank.

\subsubsection{\Gls{Susan} and her party arrive at the monastery}
\Gls{Susan} and \Gls{Ludd} travel to prehistoric times, where \Gls{Sweep} is busy saving \Gls{Unity}
from a mammoth. She tells \Gls{Unity} that they have to start putting history back together again,
and drags her to the present. \Gls{Sweep} takes them to the monastery of the History Monks, which
is insulated from the time-freeze by \Gls{Wen}'s blessing.

\subsubsection{\Gls{Susan} and \Gls{Unity} help \Gls{Ludd} repair history}
\Gls{Susan} and \Gls{Unity} put out the fires in the time storage vault, and grease the bearings as
\Gls{Ludd} uses the last of his energy setting history back into shape. He vanishes as the vaults
start spinning at their correct speeds again, and \Gls{Sweep} asks the two ladies to escape before
the monks come asking for an explanation.

\subsubsection{\Gls{Soto} sees \Gls{IgorA} and \Gls{Hopkins} rescued from \Gls{Jeremy}'s home}
\Gls{Unity} asks \Gls{Susan} to help her die, after reminding her that any mortal Auditors left
over would succumb to their dreams, given their unfamiliarity with human notions of horror.
Meanwhile, \Gls{Soto} watches \Gls{Jeremy}'s workshop being salvaged, with \Gls{IgorA} and
\Gls{Hopkins} coming out unharmed by the explosion that destroyed the building.

\subsubsection{\Gls{Ludd} and \Gls{Sweep} fight in the Iron Dojo}
\Gls{Ludd} enters the Iron Dojo with \Gls{Sweep}, eager to know his final secret, and is bested by
a martial art he never revealed to anyone in the monastery. The two of them come out of the Dojo,
in violation of its rules, and the \Gls{AbbotH} is eager to present \Gls{Ludd} with his monk robes.
\Gls{Ludd} instead requests to be appointed a sweeper, and \Gls{Sweep} takes on the duty of
ordaining him.

\subsubsection{\Gls{Kaos} helps \Gls{Unity} achieve a death of her choice}
\Gls{Kaos} makes a vat of chocolate for \Gls{Unity} to dive into, and \Gls{Death} waits to reap her
soul afterward. He is glad to have \Gls{Kaos} back with the other horsemen, and is surprised to see
him return to his dairy farm. \Gls{Ludd} disappears from the monastery after \Gls{Sweep} tells him
that he does not expect any gift from his apprentice on the occasion of his graduation.

\subsubsection{\Gls{Ludd} tries to make up with \Gls{Susan}}
\Gls{Ludd} appears in the stationery cupboard of \Gls{Susan}'s classroom, and hopes to rekindle
the romantic connection they had shared in their adventures.