\section{Thud!}


\subsection{}
\subsubsection{\Gls{Vimes} has \Gls{Willi} read the latest news out loud}
One morning, \Gls{Willi} informs \Gls{Vimes} about the racial tensions rising in the city,
instigated by \Gls{Hamcr}, a new dwarf demagogue. He listens to \Gls{Willi} read the newspaper
report about Watchmen preventing race riots, and groans at the leak that a vampire is about to be
inducted into the force.

\subsubsection{\Gls{Vimes} is met with protestors outside the Watch House}
\Gls{Vimes} is reminded to head to the painter's shop for the family portrait with \Gls{Ramkin}
and his son \Gls{SamJ}. Meanwhile, some dwarves conspire in a dark cellar to frame a troll for some
crime, in their attempt to sow division between the city's dwarf and troll populations. At the
Watch House, \Gls{Vimes} sees a large group protesting the hiring of a vampire, and spots the
photographer \Gls{OttoC}, now free to use his iconograph as a member of the press.

\subsubsection{\Gls{Vimes} thinks back to the meeting with \Gls{Vetina} and the vampires}
\Gls{Vimes} asks \Gls{CheeryL}, now promoted to Sergeant, if they will be able to smuggle the
vampire into the Watch House, and learns that \Gls{Angua} has already brought them in through the
rear entrance. \Gls{Vimes} recalls the meeting in \Gls{Vetina}'s office, where some representatives
of the Uberwald Vampire Association had asked for a vampire to be admitted to the City Watch, to
promote racial harmony.

\subsubsection{\Gls{Vimes} is coerced into accepting a vampire in the City Watch}
\Gls{Vimes} walks into \Gls{Vetina}'s trap, and is forced to accept an interview with \Gls{Sally},
a vampire candidate recommended by \Gls{JSmith}, the vampire representative from Uberwald. He
realizes the diplomatic value to Ankh-Morpork in having a highly visible vampire serving in the
City Watch, and accepts their request. In the present, \Gls{Angua} shows \Gls{Sally} around the
Watch House, while resisting the instinct to bite her throat, given her vampire scent.

\subsubsection{\Gls{Pessimal} insists on being thorough in his investigation}
\Gls{Pessimal} wishes to have an office to himself, and get to work on evaluating the finances of
the City Watch. \Gls{Vimes} is alarmed to hear that he needs to interview members of the Watch, and
is reminded of the powers granted to by \Gls{Vetina} to the auditor. \Gls{Colon} walks in next,
complaining about a fresh round of disquiet among the dwarves in the Watch. \Gls{Vimes} thinks about
his new role as the owner of a tavern for former cops, and a valuable source of underworld news.

\subsubsection{\Gls{Vimes} recalls the history of dwarf-troll tensions in Ankh-Morpork}
\Gls{Vimes} thinks about the times when Koom Valley Memorial day would involve light clashes
between dwarves and trolls, and of the recent times when he had managed to keep the two parades
from spilling into outright violence. He then recalls the news of the fundamentalist \Gls{Hamcr},
calling for the eradication of all troll-kind from the Disc, and fanning the flames of racial
tension in the city.

\subsubsection{\Gls{Vimes} sees tensions rising between the trolls and dwarves in the Watch}
\Gls{Vimes} rushes to the canteen, to see a scuffle almost breaking out between some dwarves and
trolls on his force. He asks them to put aside their racial hatred, and step out into the city to
keep the peace. Back in his office, he runs into \Gls{Angua}, and realizes too late that the he
was supposed to interview the vampire candidate.

\subsubsection{\Gls{Colon} and \Gls{Nobby} learn about the theft of a mural}
\Gls{Colon} and \Gls{Nobby}, now patrolling in the safest part of the city, talk about \Gls{Nobby}'s
latest love interest, a cabaret dancer named \Gls{Tawnee}. A while later, they are accosted by
Sir \Gls{RStitch} at the Royal Museum of Art, with claims of a burglary. He leads them into the
Museum's main hall, and shows them that the huge mural depicting the Battle of Koom Valley is
missing.

\subsubsection{\Gls{RStitch} tells \Gls{Colon} about the value of the stolen mural}
\Gls{RStitch} tells \Gls{Colon} that he was overseeing renovations at the museum, and that the
mural had been covered up with heavy cloth. \Gls{Nobby} meanwhile, looks at the other pieces
exhibits in the Museum, wondering why mundane pieces of furniture are considered priceless works of
art. \Gls{Nobby} and \Gls{Colon} consider the prospect of protecting the city from the imminent race
riots, and choose to work instead on the mural theft.

\subsubsection{\Gls{RStitch} offers some more details about the painter \Gls{Rascal}}
\Gls{RStitch} returns from the basement with \Gls{Rascal}'s collected notes, which imply that
the artist went mad with the effort of completing the mural, and had hidden some clue to a treasure
supposedly buried in Koom Valley. \Gls{RStitch} also insists that the rolled-up mural would be
very difficult to conceal, and that there are gargoyles watching all three entrances to the museum.

\subsubsection{\Gls{Vimes} learns of \Gls{Hamcr}'s death}
\Gls{Vimes} gets through the interview with \Gls{Sally}, and is impressed at her sincerity when it
comes to helping keep the peace. He asks her to sign the paperwork in \Gls{CheeryL}'s office, just
as \Gls{Carrot} barges in with news of \Gls{Hamcr} being murdered. On the way back to the Watch
House, \Gls{Nobby} tries to come up with a modus operandi for the art theft, with increasingly
elaborate schemes that impress even \Gls{Colon}.

\subsubsection{\Gls{Vimes} tries to make sense of the conflict between dwarf law and the city's
    norms}
\Gls{Vimes} is annoyed to learn that the dwarves in the city had decided to keep the news of
\Gls{Hamcr} to themselves, in violation of the law. \Gls{Carrot} talks about the nature of
surface and underground law in Uberwald, and of the fundamentalist dwarves might feel that the
City Watch does not have jurisdiction in their affairs.

\subsubsection{\Gls{Vimes} heads to \Gls{Hamcr}'s house in the dwarf enclave}
\Gls{Vimes} struggles to use his new pocket organizer, cursing the imp inside when it reminds him
of the portrait session with \Gls{Ramkin}. He sends \Gls{Haddock} along to tell her about the
emergency that had come up, as he proceeds to \Gls{Hamcr}'s residence to investigate. In the
dwarf enclave, \Gls{Vimes} notices many dwarves milling about in the streets, as if waiting for the
race riots to start.

\subsubsection{\Gls{Vimes} is allowed to enter \Gls{Hamcr}'s residence}
\Gls{Vimes} gets the guards in front of \Gls{Hamcr}'s house to go in and ask for permission from
someone higher up, choosing not to barge in using the force of his authority. A while later,
\Gls{Vimes} is allowed into the building, and notices the sound of a pump deep underground,
periodically making thumping noises. \Gls{Helmc} ushers him into his office, introducing himself
as \Gls{Hamcr}'s spokesman above ground.

\subsubsection{\Gls{Ardent} reluctantly decides to help \Gls{Vimes} talk to the priests}
When \Gls{Helmc} refuses to let \Gls{Vimes} see the corpse downstairs, a dwarf in heavy robes
enters the room, introducing himself as \Gls{Ardent}, the interpreter of \Gls{Hamcr}. He leads
\Gls{Vimes} down an elevator, to a large underground cavern illuminated by worms from the dwarf
mines. On their way to the dwarf priests down below, \Gls{Ardent} leads \Gls{Vimes} and \Gls{Angua}
through a network of tunnels, pointing out the flood walls that had been erected to keep the river
out.

\subsubsection{\Gls{Brick} fails to recall what he had been doing the night of \Gls{Hamcr}'s death}
A troll named \Gls{Brick} tries to recover from some heavy intoxication, and recalls the rumours
of \Gls{Hamcr} being murdered by some other troll. He tries and fails to recall where he was the
last night, and decides to blend in with the other trolls to allay suspicion.

\subsubsection{\Gls{Ardent} forces the dwarves to let \Gls{Vimes} leave the enclave}
\Gls{Ardent} forces the dwarves outside \Gls{Hamcr}'s house to give way for \Gls{Vimes} and his
crew, after one of them throws a brick at a dwarf Corporal standing guard alongside \Gls{Detri}.
\Gls{Vimes} despairs at \Gls{OttoC} waiting outside the Watch House with his iconograph, ready to
snap a picture of \Gls{Detri} hauling the dwarf miscreant to jail.

\subsection{}
\subsubsection{\Gls{Vimes} gets the dwarf priests to take \Gls{Carrot} on as the investigator}
Back at the Watch House, \Gls{Vimes} thinks about the meeting with the dwarf priests, and their
reluctant agreement to \Gls{Carrot} being appointed the chief investigator into \Gls{Hamcr}'s
death. He sees reports of more trolls and dwarves resigning from the Watch, as well as the first
set of inquiries from \Gls{Pessimal}, asking about \Gls{Nobby}.

\subsubsection{\Gls{Vimes} asks \Gls{Carrot} to take \Gls{Sally} along to \Gls{Hamcr}'s residence}
\Gls{Carrot} tries to get \Gls{Vimes} to segregate the patrols by species, and is stonewalled when
\Gls{Vimes} recalls the importance of the oath. He asks \Gls{Carrot} to take \Gls{Angua} and
\Gls{Sally} along with him, since no outside light sources would be allowed into the mine by
\Gls{Hamcr}'s priests.

\subsubsection{\Gls{Vimes} has \Gls{Gooseb} scour through the transport census}
\Gls{Sally} turns the prank on her fellow Constables, as \Gls{Carrot} comes by to pick her up for
the murder investigation. \Gls{Vimes} gets his \Gls{Gooseb} to verify some expense reports on his
desk, and asks it to verify if carts carrying soil out of the city have gone up in the recent weeks.
The \Gls{Gooseb} dives into his pile of paperwork, to look for extra deliveries of timber and steel,
which would be used to prop up the newly dug tunnels.

\subsubsection{\Gls{Vimes} is summoned by \Gls{Chry} to the troll hideout}
\Gls{Detri} knocks out one of the two lackeys sent by \Gls{Chry}, the head of the troll mafia, as
they demand \Gls{Vimes} drop by his hideout for a meeting. \Gls{Vimes} realizes that \Gls{Chry}
probably wants to address the rumours that \Gls{Hamcr} was murdered by a troll, and asks \Gls{Detri}
to form a squad to accompany him.

\subsubsection{\Gls{Chry} tells \Gls{Vimes} that he is pursuing his own enquiry into \Gls{Hamcr}'s
    murder}
Inside \Gls{Chry}'s hideout, \Gls{Vimes} sees the mafia file out of the room, and settles down to
discuss \Gls{Hamcr}'s murder. \Gls{Chry} insists that no troll could have done it, and expresses
concern over the new drugs saturating young troll society. He wishes \Gls{Vimes} would take charge
of the investigation over \Gls{Carrot}, since his name carries much more weight in troll society.

\subsubsection{\Gls{Vimes} hurries back home to play with his son}
\Gls{Vimes} gets \Gls{Detri} to investigate a drug distribution hub hinted at by \Gls{Chry},
convinced that he was offering the tip as a gesture of goodwill. He then hurries back home to
\Gls{SamJ}, to read him his little picture book. \Gls{Vimes} falls asleep out of sheer exhaustion,
and wakes to see \Gls{Carrot} waiting for him with his report from \Gls{Hamcr}'s murder scene.

\subsubsection{\Gls{Carrot} leads his squad to \Gls{Hamcr}'s mine}
\Gls{Carrot} reminds \Gls{Angua} and \Gls{Sally} that the dwarves are not aware of their
night-vision as the guards at \Gls{Hamcr}'s mine let them in without any questions. \Gls{Ardent}
leads \Gls{Carrot} and his squad to a chalk outline in the room where \Gls{Hamcr} was found dead,
and accedes to his request about interviewing all the dwarves who were in the mine at the time of
the murder.

\subsubsection{\Gls{Angua} finds the scent of a troll in the mine}
\Gls{Angua} is intrigued by how well \Gls{Sally} will control her vampiric instincts around a
corpse, as they are led deeper into the mine. She manages to track the faint smell of a troll, high
on some sort of drug, and asks for \Gls{Ardent} to open a watertight door. He goes off into the
mine, and returns with a squad of flamethrower-wielding guards, afraid that the perpetrator might
still be inside the mine.

\subsubsection{\Gls{Vimes} learns about the manipulation of the crime scene by \Gls{Ardent} and the
    dwarf priests}
\Gls{Vimes} outlaws the use of flamethrowers above ground, and scoffs at the clues planted at the
crime scene. \Gls{Carrot} is confident that the dwarves are lying about where and when \Gls{Hamcr}
was killed, and verifies the wrist tattoo that identifies the corpse. He also outlines the riot
control measures in place for the supposed race riots being planned at the city centre.

\subsubsection{\Gls{Vimes} is impressed by \Gls{Carrot}'s preparations for the riot}
\Gls{Vimes} talks to \Gls{Carrot} about the curious timing of \Gls{Sally}'s arrival at the city,
coinciding roughly with \Gls{Hamcr}'s. He asks for \Gls{Hancock}, one of their alumni currently in
the employ of the Semaphore Guild, to run a background check on \Gls{Sally}. Meanwhile, \Gls{Brick}
decides to hide in plain sight, marching along in the troll procession on Koom Valley remembrance
day.

\subsubsection{\Gls{Vimes} signs up \Gls{Pessimal} for the citizen militia}
\Gls{Vimes} decides to get \Gls{Pessimal} off his back by forcibly enlisting him into the citizen
militia, now being outfitted by \Gls{Colon} to assist in riot-control. He gets \Gls{Colon} and
\Gls{Willi}, who has also volunteered, to terrify \Gls{Pessimal} with their nonchalant descriptions
of the misery of police work.

\subsubsection{\Gls{Vimes} tries to spook \Gls{Pessimal}, and is surprised by his sincerity}
\Gls{Vimes} leaves \Gls{Pessimal} in the capable hands of \Gls{Detri}, as the Watchmen assemble
for the two processions. The troll contingent start to beat their drums, and sing songs of honour
and glory, as \Gls{Vimes} desperately tries to think of some way to stop the racial tensions from
boiling over. \Gls{Vimes} is surprised to see \Gls{Pessimal} taking his role as acting Constable
seriously, as they make the final preparations.

\subsubsection{\Gls{Angua} runs into \Gls{Sally} at an underground well}
\Gls{Angua} goes to the wealthy district of the city in pursuit of a chemical scent from
\Gls{Hamcr}'s mine, and finds a hastily dug tunnel network leading to an underground well. At the
well, she finds three dead dwarves, and is shocked to see \Gls{Sally} materialize from a swarm of
bats, to inform her that the bodies are only a day old. \Gls{Angua} decides to investigate the
tunnel further, realizing that it is slowly falling apart with the mud seeping through the walls.

\subsubsection{\Gls{Angua} and \Gls{Sally} find another dwarf dead along the tunnel}
\Gls{Angua} finds another dead dwarf deeper into the tunnel, slumped next to a watertight hatch.
She notices the sign that the dwarf drew in his blood, now infested with glow-worms, and rummages
around in his cloak for any possessions. She finds a letter, and decides to leave by a side-chamber
that \Gls{Sally} suggests is a path to the surface.

\subsection{}
\subsubsection{\Gls{Vimes} inspects the aftermath of the drunk processions}
\Gls{Vimes}, having been treated for his broken ribs by \Gls{Igor}, thinks about his devious plan
of mixing sleeping pills with the booze supplied to the revelers. He learns from \Gls{Carrot} that
\Gls{Pessimal} was the only other policeman injured, and is summoned to the palace by \Gls{Vetina}.
He tries to fight the sleep deprivation, as \Gls{Ramkin} sends a carriage to the palace, insisting
that he catch up on sleep.

\subsubsection{\Gls{Angua} and \Gls{Sally} emerge from the ground under \Gls{Tawnee}'s cabaret}
\Gls{Angua} and \Gls{Sally} manage to navigate the tunnels flooding with mud, to emerge under the
cabaret, where they can smell \Gls{Nobby}'s scent. \Gls{Angua} thinks about emerging naked and
covered in slime, since her emergency robes are lost in the collapsing tunnels, and begs \Gls{Sally}
to transform into bats and fly out for help.

\subsubsection{\Gls{Angua} asks \Gls{Nobby} and \Gls{Colon} for help}
\Gls{Angua} manages to find \Gls{Nobby} above ground, and demands that he send a woman to the
cellars with some cleaning supplies and a change of clothes. At the palace, \Gls{Vetina}
congratulates \Gls{Vimes} on his handling of the racial tensions, and chooses not to press him on
the source of the liquor fortified with sleep medication. He is shocked to learn that \Gls{Pessimal}
took on some trolls in the scuffle, and is being treated for a broken arm.

\subsubsection{\Gls{Brick} injures \Gls{Vimes} and \Gls{Pessimal} before being restrained}
\Gls{Brick} recalls seeing \Gls{Vimes} march up to his position, and swinging his club out of
instinct. He then remembers \Gls{Pessimal} trying to swing at his knees, before being casually
flicked away. \Gls{Detri} then knocks him out, putting an end to the hostilities. \Gls{Vetina}
is remorseful for allowing \Gls{Hamcr} to spread his gospel unimpeded.

\subsubsection{\Gls{Vetina} talks about politics in Uberwald, and its relation to \Gls{Hamcr}}
\Gls{Vetina} talks about the communique from \Gls{RhysR}, the Low King of the Uberwald Dwarves,
asking for the murder of \Gls{Hamcr} to be resolved as soon as possible. He reminds \Gls{Vimes}
that certain clans of dwarves and trolls would try to use the murder as a means of agitating against
the diplomacy bridging the two species for the moment.

\subsubsection{\Gls{Brick} considers his options with the investigation closing in on him}
\Gls{Brick} recalls his time in \Gls{Hamcr}'s mine, where he had indeed lost one of the skulls from
his necklace. As the effects of the sleep medication wear off the next day, he realizes that he is
likely to be framed for the murder, even though his club was not the one found next to the corpse.
He seeks out \Gls{Shine}, hoping to use the spirit's wisdom to get out of his predicament.

\subsubsection{\Gls{Shine} delivers \Gls{Brick} to \Gls{Carrot} at the Watch House}
\Gls{Shine} delivers \Gls{Brick} to the custody of \Gls{Carrot}, just as \Gls{Angua} and \Gls{Sally}
return from the cabaret, wearing thin gowns and high heels. \Gls{Shine} tells them that \Gls{Brick}
has useful information for them, and vanishes in a blinding flash of light. \Gls{Brick} rejects
\Gls{Pessimal}'s offer of being his lawyer, and blurts out his memory of one dwarf clubbing another
in \Gls{Hamcr}'s mine when he was down there.

\subsubsection{\Gls{Detri} helps \Gls{Brick} give his testimony at the Watch House}
\Gls{Detri} takes charge of \Gls{Brick}'s recover from drug addiction, as he talks to \Gls{Vimes}
about witnessing one dwarf murder another in the mines under the city. The stone egg left behind by
\Gls{Shine} falls to the floor, and breaks in half to reveal a piece of paper with an address on it.
\Gls{Detri} remains cagey about questions regarding \Gls{Shine}, and simply asks \Gls{Vimes} to
visit the address to quench his curiosity.

\subsubsection{\Gls{Carrot} tells \Gls{Vimes} about the expedition to dig out the dwarf's corpse}
\Gls{Carrot} warns \Gls{Vimes} that the symbol drawn by the dead dwarf is a bad omen, and suggests
that it remain well lit at all times. He informs the dwarf's family about his death, and sets out
with a group of his neighbours to dig for the corpse. He tells \Gls{Vimes} that the dwarves had been
ordered by the priests to dig according to some plan, and were to stop periodically to listen for
sounds in the tunnels.

\subsubsection{\Gls{Vimes} meets \Gls{Shine} at the antique shop}
At the antique shop, \Gls{Vimes} is led to an underground game room, where men of all species are
busy playing games. He is led aside by \Gls{Shine}, who introduces himself as a diamond troll, and
the rightful king of all trolls. \Gls{Vimes} struggles to make sense of the revelation, until
\Gls{Shine} takes off a glove to show \Gls{Vimes} his solid diamond body, and tells him that he can
regulate his brain temperature voluntarily, keeping himself intelligent even in the heat.

\subsubsection{\Gls{Shine} tries to help \Gls{Vimes} indirectly}
\Gls{Shine} offers \Gls{Vimes} some cryptic clues about the secret of Koom Valley, and claims that
he has already worked out the secret buried in the Codex written by \Gls{Rascal}. \Gls{Vimes}
decides not to take \Gls{Shine}'s advice seriously, until he accurately predicts that \Gls{Detri}
will arrive with news of the trolls being summoned to Koom Valley.

\subsubsection{\Gls{Vimes} realizes that the dwarf priests have fled with their artifact}
\Gls{Vimes} is dismayed to hear that both the dwarves and trolls have started to marshal their
forces outside Koom Valley. He asks \Gls{Detri} to send out a lookout notice for the dwarf priests,
who have managed to find some buried artifact that can talk, and probably escaped the city. He asks
for \Gls{Carrot} to allow the dwarves to bring out the corpses found underground, in order to avoid
bad optics in the press.

\subsubsection{\Gls{Vimes} and his family are attacked by the dwarf priests}
\Gls{Vimes} is ambushed at his home by the dwarf priests, and manages to rescue \Gls{SamJ} from
them. He then asks \Gls{Willi}, who dealt with most of them, to check on the nanny, as he heads to
the dragon pen. The last priest tries to use his flamethrower on \Gls{Ramkin}, but fails to burn
through her thick protective robes.

\subsubsection{\Gls{Vimes} takes his family to the Watch House for safety}
\Gls{Willi} tells \Gls{Vimes} that one of the dwarf invaders was killed immediately, and another
had died after being tied up, foaming green at the mouth. \Gls{Vimes} decides to evacuate his
manor for the night, and move to the Watch Headquarters. Once there, \Gls{Carrot} informs
\Gls{Vimes} that several dwarf artifacts called Devices have been left behind by the priests, and
that the only talking Device is a Cube, used as a voice recorded lasting millennia.

\subsubsection{\Gls{Vimes} meets the dwarf community leaders in his office}
\Gls{Angua} reluctantly tags along as \Gls{Sally} decides to return to the cabaret to thank
\Gls{Tawnee} for the help cleaning up. \Gls{Angua} struggles against her werewolf instincts telling
her to kill \Gls{Sally}, and is hesitant about befriending her. He allows the dwarf contingent to
come into his office, after leaving their weapons down below, while struggling to hold back his
anger at their tolerance for \Gls{Hamcr}.

\subsubsection{\Gls{Vimes} reluctantly agrees to use \Gls{Bashf} as a witness for the dwarves}
One of the dwarf contingent introduces himself as \Gls{Bashf}, a former priest, and now a member
of \Gls{Shine}'s underground game-bar. The other dwarves vouch for him, and \Gls{Vimes} to take him
along when he interrogates \Gls{Helmc} in the underground jail. \Gls{Vimes} realizes that he might
lose control of his temper, and agrees with \Gls{Bashf}.

\subsubsection{\Gls{Vimes} starts his interrogation using the board game to distract \Gls{Helmc}}
\Gls{Angua}, \Gls{Sally} and \Gls{CheeryL} try to socialize with \Gls{Tawnee}, and discover her
insecurities about her body, that \Gls{Nobby} has probably taken advantage of. Using the board game
to divert \Gls{Helmc}'s terror, \Gls{Vimes} asks him about the events preceding the death of
\Gls{Hamcr}. \Gls{Helmc} starts with \Gls{Ardent}, who was his teacher in the mines at Uberwald,
and talks about a spat between the priests, when one of them had tried to destroy the Cube.

\subsubsection{\Gls{Helmc} dies of fright when the lights go out in the jail cell}
\Gls{Helmc} dies of fright when the candle goes out in the interrogation room, with \Gls{Vimes}
growing angry at \Gls{Colon} for suppressing the report about the stolen mural. \Gls{Bashf} promises
\Gls{Vimes} that he will tell the truth about the handling of \Gls{Helmc}, and asks him to consider
a visit to Koom Valley to pursue the priests.

\subsubsection{\Gls{Vimes} tries to work out the secret hidden in the mural}
\Gls{Vimes} learns that \Gls{Rascal} might have been the former owner of the Cube that drove him mad
with its talk, and got disposed of in the well that the dwarf priests had now dug up. He spreads out
a map of the city in the Watch House, with \Gls{RStitch} to help him read the Codex of Koom Valley.
\Gls{Vimes} is convinced that he is close to solving the puzzle of the mural.

\subsubsection{\Gls{Ramkin} tells \Gls{Vimes} that she has a copy of the mural from her childhood}
\Gls{Ramkin} barges in with some tea, just as \Gls{RStitch} is talking about the significance of
the mural. She tells them that her family owned the mural before it was donated to the museum, and
that a small-scale copy that she drew for a school project should still be in the attic of the
Watch House.

\subsection{}
\subsubsection{\Gls{Vimes} decides to travel to the original Koom Valley battleground}
\Gls{Visit} tracks down \Gls{Angua} and the other women, as they stagger out of a bar, drunk to
the point of blacking out. He tells them that \Gls{Vimes} has asked for their help in the Koom
Valley situation. \Gls{Vimes} inspects the replica of the painting in the Watch House attic, and
makes up his mind to visit the place in person. \Gls{Ramkin} insists on coming along with
\Gls{SamJ}, and asks \Gls{Willi} to start packing.

\subsubsection{\Gls{Vetina} tries to stop \Gls{Vimes} from visiting Koom Valley unprotected}
\Gls{Vetina} warns \Gls{Vimes} that the \Gls{SDark} might be a demonic entity summoned by the
dying dwarf to curse all the others that were in the mine. \Gls{Vimes} refuses to take the magical
threat seriously, and asks for leave to take a small squad with him to Koom Valley.

\subsubsection{\Gls{Vimes} asks \Gls{Ridcu} for help traveling to Koom Valley}
\Gls{Vimes} visits \Gls{Ridcu} in secret at the Unseen University, and asks for help traveling to
Koom Valley. \Gls{Ridcu}, wishing to keep any help off the record, asks him to bring his retinue of
two carriages to the back entrance of the University in some time, and promises a safe magical
boost to their journey.

\subsubsection{\Gls{Vimes} inspects the changes made by \Gls{Ridcu} and his wizards}
The \Gls{SDark} tries and fails to penetrate someone's mind and use them as its champion. Meanwhile,
\Gls{Vimes} gives in to his sleep deprivation until he is woken up by \Gls{Carrot}, and examines the
enchanted carriages. The wizards had stuck magic broomsticks under the wagons to compensate for
their weight, and installed curious saddles for the horses with knobs on them.

\subsubsection{\Gls{Vimes} and his party use the cabbage powered speedwagons}
\Gls{Vimes} sets off with \Gls{Willi} driving the carriage, and is amused to hear that \Gls{Sally}
has sent a coded message back to Uberwald using the Semaphore towers. The carriages erupt into
super-speed using the power of cabbages, and take them at sixty miles an hour all the way to Quirm.
The second carriages crashes as they try to slow down, with the cabbage farms coming to an end, but
\Gls{Ramkin} is relieved that her wagon landed smoothly.

\subsubsection{\Gls{Willi} successfully drives the speedwagon at maximum speed}
\Gls{Willi} reminds \Gls{Vimes} that the dwarves could have used their own flying broomsticks, and
suggests speeding up their own carriages to fifth gear to try and catch up. \Gls{Vimes} decides to
call a halt, to prepare the retinue for the extreme speed. \Gls{Ramkin} recommends resting for the
night, as they reach a town close to Koom Valley. \Gls{Bashf} warns \Gls{Vimes} that the valley
was very dangerous after dark, and supports \Gls{Ramkin}'s idea of resting up.

\subsubsection{\Gls{Ramkin} meets her friend at the town next to Koom Valley}
\Gls{Ramkin} greets her friend and schoolmate, who is now the wife of the town magistrate, as
\Gls{Vimes} and the party settle down at a nearby inn. \Gls{Angua} detects \Gls{Sally} morphing into
a swarm of bats and sneaking out of her room at night, but chooses not to tell anyone.

\subsubsection{\Gls{Vimes} tries to navigate to the place where \Gls{Rascal} set the mural}
\Gls{Angua} smells a lot of dwarves setting up camp downriver from Koom Valley, to wait for the
day of remembrance, when they would recreate the battle with the trolls. \Gls{Vimes} struggles to
use \Gls{Ramkin}'s copy of the mural to find the exact vantage point where the viewer was supposed
to be when surrounded by it.

\subsubsection{\Gls{CheeryL} advises \Gls{Vimes} not to descend into the pit}
\Gls{CheeryL} points out the dwarf priests and their dig site up ahead, just as \Gls{Vimes} is
ready to give up on his effort to find the secret of the mural. He spots a rope going down the
pit, and decides to descend without waiting for the others to catch up. A voice in his head tells
him to overrule \Gls{CheeryL}'s warnings, and to find a tunnel close to the surface.

\subsubsection{\Gls{Vimes} falls into an underground river and is swept along its course}
\Gls{Vimes} obeys the voice in his head, and lets go of the rope, falling into an underground river.
He is deposited far downstream, having been bruised and battered by the many waterfalls in the
river's course. \Gls{Vimes} then uses the matchsticks given by \Gls{CheeryL} to realize that he is
far underground in a cavern, with no immediate way out.

\subsubsection{\Gls{Vimes} struggles to crawl through the underground cavern}
\Gls{Vimes} realizes that he is having a close brush with death, when \Gls{Death} shows up sitting
next to him reading a book. He notices some glow-worms crawling along the cavern walls, and decides
to follow them in the hopes of finding a path to the surface. Meanwhile, \Gls{Ramkin} is heartbroken
by \Gls{Vimes} not showing up to read his son's picture book, and takes it upon herself to do the
reading.

\subsubsection{\Gls{Vimes} corners the dwarf priests who murdered \Gls{Hamcr}}
\Gls{Vimes} manages to find the dwarf priests, and mows through the soldiers guarding them, fueled
only by rage. \Gls{Sally} shows up to defend him from some other dwarves with crossbows, as the
last of the dwarf soldiers decide to flee, leaving the priests to their fate. The \Gls{SDark} tries
to take over \Gls{Vimes}, but is repulsed by some part of his subconscious mind, that acts as an
internal watchdog.

\subsubsection{\Gls{Angua} rescues \Gls{Vimes} after he rejects the \Gls{SDark}}
\Gls{Angua} also reaches the mine, and brings \Gls{Vimes} out to the surface, after he stops himself
from striking down the dwarf priests. She tells him that a dwarf regiment sent by \Gls{RhysR} is
now holding them prisoner, and shows him around the mine, where several trolls and dwarves lie
fossilized.

\subsubsection{\Gls{Angua} and \Gls{Bashf} fill \Gls{Vimes} in on their pursuit}
\Gls{Angua} tells \Gls{Vimes} that the dwarves had decided to co-operate with them, once \Gls{Bashf}
worked his magic using his priestly words. \Gls{Bashf} arrives to tell \Gls{Vimes} that the demon
had likely taken over his body once he fell into the pit, and guided him to the underground cavern.
It had then decided to let go of him, once it realized it could not exert total control over his
mind.

\subsubsection{\Gls{Vimes} comes to a standoff with \Gls{RhysR}}
\Gls{Vimes} joins his squad to wait for \Gls{RhysR} and his elite troops, wondering if the Cube had
been confiscated from the dwarf priests. A while later, \Gls{RhysR} arrives, and is surprised to
learn that his dwarf regiment has scoured the mine several times and failed to find the Cube.
\Gls{RhysR} decides not to snatch the Cube from \Gls{Nobby}, who had snatched it up in the chaos of
their skirmish, believing it was a precious jewel.

\subsubsection{\Gls{Vimes} and \Gls{RhysR} ask the dwarves to listen to the Cube}
\Gls{Vimes} realizes that the cube will only speak when it hears a dwarfish word said out loud, and
works out that it is a word that sounds like chickens squawking. The Cube repeats the voices of
dwarf and troll generals, who had gathered at Koom Valley to sign a peace treaty, but were swept up
by a storm, to die together in the underground cavern.

\subsubsection{\Gls{Ardent} dies trying to defend the dark priests and their bigotry}
\Gls{Ardent} tries to defend the priests by saying that hatred of the trolls was at the heart of
their culture, as \Gls{Vimes} realizes that the secret of Koom Valley was the corpses of trolls and
dwarves lying together underground. \Gls{Bashf} is forced to kill \Gls{Ardent} when he raises his
axe to strike \Gls{RhysR}, just as they receive news of \Gls{Shine} approaching the cavern with his
contingent of trolls.

\subsubsection{\Gls{Vimes} sees the new monument to peace between the dwarves and trolls}
\Gls{Vimes} visits the underground cavern the next day, as it is being made into a memorial for
the troll and dwarf kings who had died playing a board game with each other. He then finds
\Gls{Sally}, and asks her to use her contacts with \Gls{RhysR}, to get \Gls{Ardent} and the dwarf
priests sent to \Gls{Vetina} for a formal trial.

\subsubsection{\Gls{Vimes} gets his family portrait taken, using \Gls{OttoC}'s iconograph}
\Gls{Vimes} has his family portrait taken outside the monument in Koom Valley, and then attends the
official signing of the peace treaty between \Gls{RhysR} and \Gls{Shine}. He realizes that his
reputation gave the dwarves the cover they needed to dig into the cavern, without raising suspicion
among the trolls.

\subsubsection{\Gls{Carrot} asks \Gls{Vetina} to approve the construction of a subway system}
\Gls{Carrot} shows off a strange dwarf Device to \Gls{Vetina} at \Gls{Hamcr}'s mine under
Ankh-Morpork, and claims that it can power an entire underground railway network. He then asks for
an increase in the strength of the Watch, to staff the new subway system, in spite of the exorbitant
costs to the city.