\section{Unseen Academicals}


\subsection{}
\subsubsection{A night watchman in Ankh-Morpork sees a ghost holding a ball}
A nightwatchman at the Ankh-Morpork Museum of Art is spooked by faint sobbing coming from the
basement, and is found by the day shift buried in the rubble of an explosion. He is transferred to
a pet shop, and decides to keep the story of a shiny ghost holding a ball above her head to himself.

\subsubsection{\Gls{Smee} and \Gls{Nutt} carry out their daily duties in the Unseen University}
Candle Keeper \Gls{Smee} goes about his rounds one morning at the Unseen University, with his new
assistant \Gls{Nutt} following along. He shows the young boy the everlasting flame known as the
Emperor, kept faithfully lit for many centuries by a long line of Candle Keepers. The two of them
watch the Inner Council chase a duck through the corridor, leaving \Gls{Smee} stranded at the top
platform of the Emperor.

\subsubsection{\Gls{Smee} sees how smart \Gls{Nutt} can grow up to be}
\Gls{Nutt} improvises a rope for \Gls{Smee} to use as a rappel when the faculty break the step
ladder on their stampede through the corridor. \Gls{Smee} warns \Gls{Nutt} that he will be safe and
have a stable career if he performs his duties faithfully as assistant Candle Keeper. Meanwhile,
\Gls{Stibb}, the new Master of Traditions, reads out loud from the Book of Traditions for the Inner
Council at their lounge.

\subsubsection{\Gls{Hix} asks about the need to follow elaborate traditions from centuries ago}
\Gls{Ridcu} explains to \Gls{Hix}, the newest member of the faculty in the Department of Post-Mortem
Communications, that upholding traditions was the most sacrosanct duty of the council. Meanwhile,
\Gls{Stibb} tries to congratulate \Gls{Rince}, who was the ceremonial duck to be chased for the
evening, and finds the rest of the Wizards distracted by the beauty of the new servant \Gls{Juliet}.

\subsubsection{\Gls{Stibb} is forced to listen to another one of \Gls{Ridcu}'s angry tirades}
\Gls{Stibb} accidentally triggers \Gls{Ridcu}'s anger about the \Gls{Dean} resigning his position,
in favour of a better-paying job at a different university. \Gls{Ridcu} is horrified by the idea of
a senior wizard subjecting himself to an interview by the common folk, and considers the
\Gls{Dean}'s betrayal worse than dying on the job.

\subsubsection{\Gls{Stibb} decides to investigate the Book of Traditions}
\Gls{Stibb} is intrigued by the Book of Traditions seemingly flipping to a specific page of its
own volition, and sets about reading it. The rest of the faculty busy themselves with their
pre-breakfast snack, brought by a different newly hired maid. Meanwhile, \Gls{Glen} is annoyed to
see \Gls{Juliet} arrive late to the Night Kitchen of the University, having stayed overtime to
watch a football match.

\subsubsection{\Gls{Stibb} talks about an endowment that requires the formation of a football team}
\Gls{Stibb} reads about a sizable endowment to the University, that requires their participation in
the annual football leagues. \Gls{Ridcu} and the rest of the council point out that they stopped
participating many decades ago, when the games started to get too violent for a gentleman, and
\Gls{Stibb} points out that they risk losing the endowment unless the University fields a team in
the coming year.

\subsubsection{\Gls{Nutt} thinks about his cushy job away from bigoted humans in Ankh-Morpork}
\Gls{Nutt} thinks about his job as the maintainer of the University's water supply systems deep
in the cellars, and thanks \Gls{Trev} for the quiet posting away from all the other staff. He
thinks about his early life as a goblin in some remote village, and all the ostracism he had to
face before he secured the job at Unseen University.

\subsubsection{\Gls{Trev} greets \Gls{Nutt} at the end of his shift}
\Gls{Trev} returns from his football match, and thanks \Gls{Nutt} for taking over his shift.
\Gls{Nutt} is happy to see some people too busy with their present lives to recall the ancient
hatred against goblins, based on stories treachery and evil from centuries ago. He decides to make
an effort to fit in with the other staff, and agrees to accompany \Gls{Trev} to the Kitchens for a
snack.

\subsubsection{\Gls{Glen} gives some food to \Gls{Trev} and \Gls{Nutt}}
\Gls{Glen} is surprised to see \Gls{Nutt}, and mistakes him for a zombie when she spots his grey
skin. He tells her that he is a young goblin, and does not have horns yet. \Gls{Glen} is happy to
give him some food from the oven, as \Gls{Trev} gets angry at the sight of \Gls{Juliet}, and starts
arguing about football with her.

\subsubsection{\Gls{Glen} and \Gls{Juliet} return home from the University}
\Gls{Glen} is alarmed to see \Gls{Juliet} busy herself with a fashion magazine, and decides to
return home for the day. The two of them board the public wagon, and \Gls{Glen} makes sure to
flaunt her home team's scarf, in an effort to make peace with the football hooligans in her
neighbourhood.

\subsubsection{\Gls{Ridcu} forces the rest of the faculty to play football}
\Gls{Ridcu} insists that the Wizards have to try and win, instead of forfeit the game as \Gls{Stibb}
recommends. He recalls stories of his grandfather doing very well in some games a long time ago, as
the other wizards grimace at the thought of trading blows with peasants. The rest of the faculty are
suddenly forced to take the game seriously when \Gls{Stibb} calculates the blow to their food
budget with the loss of the endowment.

\subsubsection{\Gls{Ridcu} learns about the \Gls{Dean} trying to entice \Gls{Stibb}}
\Gls{Ridcu} storms out of the lounge, with \Gls{Stibb} trailing him, intent on asking about the
newly admitted goblin \Gls{Nutt}. He reminds \Gls{Ridcu} that he is doing twelve different jobs at
the moment, and has turned down a very attractive offer from the University at Brazeneck.
\Gls{Ridcu} is angry at the \Gls{Dean} trying to poach more of his faculty, but is pleased to learn
that \Gls{Stibb} declined the offer.

\subsubsection{\Gls{Trev} and \Gls{Juliet} express interest in each other}
\Gls{Nutt} recalls the advice from \Gls{Ladyship}, who had sent him to Ankh-Morpork to find a job
that would help him hide from humanity, when \Gls{Trev} asks him to come watch a football match.
Meanwhile, \Gls{Glen} is alarmed to see \Gls{Juliet} ask about \Gls{Trev}, and tries to explain
that he is a good-for-nothing cretin, with no prospects and no hobbies outside football.

\subsubsection{\Gls{Nutt} recalls his early life in a vampire's estate in Uberwald}
\Gls{Nutt} thinks back to his childhood in the manor of a wealthy vampire in Uberwald, and recalls
the dwarf and troll royalty who would often visit. He thinks about his efforts to improve his
literacy, and his fast-improving ability to read and digest books. His mistress, the \Gls{Ladyship}
had given him free rein of her estate, and asked all the staff to help him learn any trades that
piqued his interest.

\subsubsection{\Gls{Vetina} talks to \Gls{Ridcu} about legalizing and regulating football}
\Gls{Nutt} decides to use his night-vision to roam the cellars of the University, having finished
his candle-making quota early on in his night shift. Meanwhile, \Gls{Ridcu} goes to \Gls{Vetina}'s
office at the Palace, and is surprised to hear the Patrician express his disdain for the growing
popularity of football. He intends to formalize the sport, like he did the Thieves' Guild, and
hopes that the damage to property and public order will be controlled once the new legislation
passes.

\subsubsection{\Gls{Vetina} asks about \Gls{Nutt} and the football league}
\Gls{Vetina} suggests to \Gls{Ridcu} that the University take up the task of organizing the reformed
football league, and asks about the \Gls{Dean}'s new job in Pseudopolis. He then asks about
\Gls{Nutt}, who has seemingly been sent to the University on the behest of the \Gls{Ladyship} from
Uberwals. \Gls{Ridcu} says that the goblin has been described by \Gls{Smee} as cunning, and is
surprised when \Gls{Vetina} talks about a bright future for \Gls{Nutt}.

\subsubsection{\Gls{Ridcu} makes his plans for the new football league}
\Gls{Ridcu} recalls the news about \Gls{Margo} sending the goblin to \Gls{Vetina} for safekeeping,
after a high-profile diplomatic visit to Ankh-Morpork. On his way back to the University,
\Gls{Ridcu} finds a boy sporting a football scarf, and asks him where he might watch a match later
in the day. The boy tells him to come to a back-alley nearby, after receiving a small payment. He
asks \Gls{Stibb} to set \Gls{Hex} to the task of finding a new sports master, and calls a council
meeting.

\subsubsection{\Gls{Nutt} asks \Gls{Glen} about \Gls{Juliet}}
\Gls{Nutt} tells \Gls{Glen} that he is going to see a football match with \Gls{Trev}, and asks
about \Gls{Juliet}. \Gls{Glen} warns him about \Gls{Trev} trying to approach \Gls{Juliet}, and
talks about the ancient football rivalry between different neighbourhoods of the city. Back at
the candle vats, \Gls{Nutt} tells \Gls{Trev} about \Gls{Juliet}, and is alarmed to see his reaction
when he hears her last name.

\subsubsection{\Gls{Nutt} indulges \Gls{Trev}'s wish to receive a friendly punch}
\Gls{Nutt} is confused when \Gls{Trev} punches him in the arm, and learns that such gestures of
camaraderie are needed when blending in with the football audience. \Gls{Nutt} lightly taps
\Gls{Trev} back, and is surprised to see \Gls{Trev} complain about the weakness of his own punch.
Meanwhile, \Gls{Ridcu} has the council fish out some trousers and shirts, so that they might look
like common labourers at the football match.

\subsubsection{\Gls{Glen} thinks about her second job selling cosmetics to trolls}
\Gls{Ridcu} has two of the University's bouncers \Gls{Ottomy} and \Gls{Nobbs} escort them to the
football match, in case they face any violence. Meanwhile, \Gls{Glen} gets ready to peddle some
cosmetics to the newly wealthy troll working-class of Ankh-Morpork, and is interrupted by
\Gls{Juliet} taking her to the football match in progress.

\subsubsection{The \Gls{Libra} observes some familiar faces in the audience of the football match}
The \Gls{Libra} settles down on a high roof to watch the football game, and spots \Gls{Nutt} in
the crowd along with \Gls{Trev}. He thinks back to \Gls{Glen}, who was kind enough to bake him some
banana pies, as she enters the crowd, followed by the Wizards. Meanwhile, \Gls{Trev}'s complaints
about the strength of \Gls{Nutt}'s punch are interrupted by \Gls{Andy} and \Gls{Carter}. \Gls{Trev}
explains to \Gls{Nutt} that they are the sons of star players in his favourite team, and his
friends.

\subsection{}
\subsubsection{\Gls{Trev} and \Gls{Nutt} run into \Gls{Glen}}
\Gls{Hix} leads the Wizards through the crowd gathering outside the football pitch, after
\Gls{Ottomy} explains the loosening of the rules over the decades. Meanwhile, \Gls{Trev} and
\Gls{Nutt} are separated from \Gls{Andy} and his gang of hooligans, as they jostle through the
crowds to get a better view of the game. Eventually, they run into \Gls{Glen}, who refuses to
believe that \Gls{Nutt} plowed his way through the crowd using a pie cart. \Gls{Juliet} discreetly
hands a badge of her own team to \Gls{Trev}, who is afraid of being found with enemy colors on him.

\subsubsection{\Gls{Nutt} scores a long-range goal, and makes the goalpost collapse}
\Gls{Nutt} catches the ball when it flies above the cart, as \Gls{Trev} dives under it, dragging
\Gls{Juliet} with him for safety. \Gls{Glen} stands by shocked, as \Gls{Nutt} asks where the ball
is supposed to be thrown, just in time \Gls{Nutt}'s throw to hit the goalpost, and make it collapse.
\Gls{Trev} drags the other three away from the crowd thronging to the supposed scorer, and
\Gls{Glen} berates \Gls{Nutt} for scoring as a mere spectator.

\subsubsection{\Gls{Nutt} and \Gls{Trev} are trapped between two gangs}
\Gls{Nutt} is forced to reveal his life as a slave chained to a forge, when \Gls{Trev} asks him how
he has so much strength. He then suggests to \Gls{Trev} that he should write a poem to express his
love, just as they run into \Gls{Juliet}'s brothers. \Gls{Andy} and his gang catch up to them,
bristling for a fight. \Gls{Trev} manages to calm the two groups down by reminding them about jail,
just as \Gls{Nutt} makes an offhand comment that makes \Gls{Alg} hit him hard in the chest.

\subsubsection{\Gls{Trev} asks for \Gls{Nutt} to be taken to the hospital}
\Gls{Trev} despairs at \Gls{Nutt} bleeding out on the street, and is happy to see some Watchmen
approach. The two gangs flee the scene, leaving \Gls{Trev} to ask for an emergency delivery of
\Gls{Nutt} to the Lady Sybil Free Hospital. \Gls{Death} visits \Gls{Nutt} at the hospital bed,
and tells him that he will live again, showing his hourglass with the sand falling upwards.
Meanwhile, \Gls{Trev} is taken to the Watch House, where \Gls{Angua} gets his statement, and notices
the badge gifted by \Gls{Juliet} fall out of his pocket.

\subsubsection{\Gls{Angua} tries to extract information from \Gls{Trev}}
\Gls{Angua} tries to ask \Gls{Trev} about \Gls{Nutt}'s origins, and is interrupted by \Gls{Lawn},
who returns from the hospital with news of \Gls{Nutt} waking up and eating a sandwich, as if there
was nothing wrong with him. \Gls{Trev} is horrified to learn that they let \Gls{Nutt} walk out of
the hospital, even if Doctor \Gls{Lawn} insists that the goblin was in good health. Once outside
the Watch House, \Gls{Trev} is accosted by \Gls{Carter}, who asks him if the gang is in trouble with
the cops.

\subsubsection{\Gls{Trev} meets \Gls{IgorS} on his way out of the Watch House}
\Gls{Trev} sees the futility of a life in the football gangs, and asks \Gls{Carter} to tell
\Gls{Andy} that he will never join them again. He is accosted by \Gls{IgorS}, now a surgeon working
at the Lady Sybil Hospital, and asked about \Gls{Nutt}. \Gls{Trev} once again denies any knowledge
of \Gls{Nutt}'s past, and is alarmed to see \Gls{IgorS} warning him about the potential danger that
the goblin poses.

\subsubsection{\Gls{Glen} realizes that \Gls{Ottomy} has seen her and \Gls{Juliet} at the game}
\Gls{Glen} drags \Gls{Juliet} to the Night Kitchen, and tries to coach her about a false story about
doing oven duty all night. \Gls{Ottomy} walks in for some tea, asking them if they were at the game
earlier that night. \Gls{Glen} says no, and is dismayed to see him describe someone resembling
\Gls{Juliet} being spotted with a supporter of another team. He then tells them that he had to
escort the Wizards to the game where they took notes, as if to prepare for some big event.

\subsubsection{\Gls{Glen} reads a summons out loud for \Gls{Stollop}}
Back home, \Gls{Glen} is shown an envelope by \Gls{Stollop}, bearing the seal of the Patrician. He
is worried about penalties for unpaid taxes, and asks her to read it out loud. \Gls{Glen} tells him
that he has been invited to a meeting at the University to discuss the reformed football league,
as a captain of one of the teams.

\subsubsection{\Gls{Glen} and \Gls{Juliet} return to the University after learning about \Gls{Nutt}}
\Gls{Glen} learns from \Gls{Stollop} that a supporter of a different club died in an altercation
after the night's game, and is worried it might be \Gls{Trev}. She runs to the University, and is
surprised to find \Gls{Juliet} following her. \Gls{Trev} arrives a while later to find them in the
kitchen, with all the stored food eaten, and collapses from sleep deprivation. \Gls{Glen} helps him
to a mattress, and asks him about \Gls{Nutt}.

\subsubsection{\Gls{Nutt} talks to \Gls{Glen} about coming back to life}
\Gls{Nutt} suddenly wakes up, and starts talking about \Gls{Trev}'s father, who died a hero in the
football community. \Gls{Trev} is overwhelmed by the emotions from his childhood rearing up, and
\Gls{Nutt} leaves to get a comfortable mattress for him. \Gls{Nutt} is not sure how he came back
to life, and apologizes for eating all of the ready pies in the kitchen. \Gls{Glen} is dismayed to
learn that he enjoyed the football game, and the spectating experience.

\subsubsection{\Gls{Glen} reads about the return to classic football rules}
\Gls{Glen} returns home with \Gls{Juliet} as \Gls{Nutt} busies himself in a nearby room with poetry
books. She wakes up the next day to find \Gls{Juliet} at the front door, with the day's newspaper
in her hands. A full page article proclaiming the return of proper football covers the front-page,
along with urns provided by the Guild of Historians, depicting the players. \Gls{Juliet} then points
out the advertisement for a fashion show organized by a dwarf-owned boutique, and begs \Gls{Glen} to
come with her.

\subsubsection{\Gls{Nutt} writes a love poem for \Gls{Trev} to give to \Gls{Juliet}}
\Gls{Nutt} hands the love poem to \Gls{Trev}, and reminds him that his presence will make it more
difficult for \Gls{Juliet} to appreciate it. \Gls{Trev} is transfixed by the idea of \Gls{Juliet}
falling in love with him by the power of the poem, and eagerly signs his name at the bottom of the
paper.

\subsubsection{\Gls{Glen} watches the faculty meeting discuss the new football league}
\Gls{Ridcu} asks \Gls{Stibb} to summarize the logistics of organizing a reformed football league,
as the others in the Council speculate about the convenient timing of the ancient urn turning up in
the Art Museum. \Gls{Stibb} reminds them of the food, violence and chanting that are vital parts of
the football experience, as \Gls{Ridcu} notices the interest with which \Gls{Glen} is listeining
to the proceedings.

\subsubsection{\Gls{Glen} is forced to speak her mind when \Gls{Ridcu} insists}
\Gls{Glen} accidentally lets slip that the Council knows very little about the modern state of
football, and \Gls{Ridcu} asks her to elaborate. \Gls{Ridcu} and the faculty fondly reminisce
about their own experience at the football games on their parents' shoulders, and \Gls{Ridcu} is
forced to point out \Gls{Vetina}'s success with reforming the Guild of Thieves and Assassins.

\subsubsection{\Gls{Glen} tries to gain entry to the banquet organized by \Gls{Vetina}}
\Gls{Glen} comes out of the faculty lounge, to find \Gls{Polly}, the chief maid of the day shift
waiting for her. She asks about getting assigned to the upcoming banquet, and learns that it is
under the chief butler's control. \Gls{Ridcu} calls for a practice match later in the day, as the
Council disperses from the meeting.

\subsubsection{\Gls{Juliet} becomes a model for \Gls{Sharn}'s fashion show}
\Gls{Glen} and \Gls{Juliet} go to the upscale dwarf boutique, and are overwhelmed by the ostentation
on display. The owner of the shop, Madam \Gls{Sharn}, invites them backstage, as \Gls{Pepe} the
tailor gets ready for the fashion show. She has \Gls{Juliet} walk across the room, and \Gls{Pepe} is
overjoyed by her potential as a model for their clothes. \Gls{Glen} thinks about the impropriety of
taking up the offer, but accepts on \Gls{Juliet};s behalf when she hears about the pay.

\subsubsection{\Gls{Ridcu} organizes a trial game for the Wizards}
\Gls{Ridcu} asks to blow the ceremonial whistle recovered from the office of the long dead Professor
of Sports, and is possessed by his spirit for a few seconds. \Gls{Hix} insists that it was merely
a statutory act of mischief per his contract, as \Gls{Stibb} takes the whistle from him for his
role as referee. He makes a long list of notes about how the game might be improved, starting with
the shape of the ball, and the nature of the goals.

\subsubsection{\Gls{Glen} dozes off and misses most of the fashion show}
\Gls{Glen} is given a seat at the front row, as \Gls{Juliet} puts on a dwarf beard styled in the
current feminine fashion, and models the clothing developed by \Gls{Pepe} and \Gls{Sharn}. After
the show, \Gls{Juliet} is overwhelmed by the applause, and tells \Gls{Glen} that she has been
offered an exclusive contract to model at the other branches of the boutique.

\subsubsection{\Gls{Juliet} is made to pose for the newspapers after the show}
After the show ends, \Gls{Juliet} is ferried to a back-room, where photographers from the city's
magazines wait eagerly to take pictures of the latest phenomenon in dwarf modeling. \Gls{Glen} asks
for the washroom, and accidentally wanders into the warehouse downstairs, where she sees \Gls{Pepe}
drinking some champagne. He tells her that he is a human who managed to get himself inducted into
dwarfdom, once \Gls{Sharn} realizes his skills in fashion design.

\subsubsection{\Gls{Glen} decides to sit on the modeling contract for a day}
\Gls{Glen} insists on taking some time to think over the modeling contract offered by \Gls{Sharn},
and takes \Gls{Juliet} home after the party. \Gls{Sharn} is confident that \Gls{Glen}'s
protectiveness will give way to the financial opportunity at hand, if they accept the job.
Meanwhile, \Gls{Stibb} and \Gls{Ridcu} travel to the Cabinet of Curiosity, the alleged depository of
an infinity of perfect specimens of any non-organic object less than a certain size.

\subsubsection{\Gls{Ridcu} decides to have a copy of the football made by a dwarf workshop}
\Gls{Ridcu} gets a bouncy spherical football from the Cabinet, once it completes its
multidimensional search for a perfect specimen. In a corridor outside, he runs into \Gls{Trev} and
\Gls{Nutt}, with \Gls{Stibb} trying to think about making a replica of the ball before the deadline
to return it was up. \Gls{Stibb} is taken aback by \Gls{Nutt}'s analysis of the ball's structure,
and \Gls{Ridcu} suggests sending them to the dwarf workshops with a bag of gold for the express job.

\subsubsection{\Gls{Andy} tries to bully \Gls{Trev} again, but is stopped by \Gls{Nutt}}
\Gls{Glen} tells \Gls{Juliet} that she will open a bank account for her, so that she can hide
the modeling pay from her father, who will waste it all at the tavern. \Gls{Nutt} stops \Gls{Andy}
from stabbing \Gls{Trev} with his sword, when he feels the need to assert his street value to his
new band of followers. \Gls{Andy} is forced to drop the sword when \Gls{Nutt} crushes his hand,
and \Gls{Trev} hastily picks it up as they run away from the confused gang of hooligans.

\subsubsection{\Gls{Nutt} offers a dwarf the exclusive rights to make spherical footballs}
\Gls{Nutt} goes to a dwarf workshop, and asks for a copy of the football, to be made with newly
discovered rubber. The dwarf is unsure about the payment, but is cowed when \Gls{Trev} offers him a
license to make as many copies as he wants for other customers in the city. \Gls{Glen} realizes that
she has made \Gls{Juliet} just as risk-averse as her, when she expresses no interest in signing up
for the modeling gig.

\subsubsection{\Gls{Nutt} and \Gls{Trev} get a replica football made at the dwarf workshop}
\Gls{Nutt} pays the dwarf for a knife that \Gls{Trev} takes from the shelves, afraid of retribution
from \Gls{Andy} and his gang. He notices some vampires keeping watch over the workshop, as
\Gls{Nutt} tries to downplay their presence. \Gls{Nutt} suggests handing over the remaining gold
to \Gls{Stibb}, to repair \Gls{Trev}'s reputation with the faculty, and possibly get a promotion.

\subsubsection{\Gls{Glen} goes to the University Kitchen, after seeing \Gls{Juliet} on the front
    page}
\Gls{Glen} deposits the modeling payout in the Royal Bank on the way to her job, and finds
\Gls{Nutt} waiting for her with a letter to \Gls{Juliet} from \Gls{Trev}. She debates opening the
letter without \Gls{Juliet} present, talking excitedly about her front-page picture in dwarf
clothing and silver beard.

\subsubsection{\Gls{Glen} reads the letter for \Gls{Juliet} supposedly written by \Gls{Trev}}
\Gls{Juliet} asks \Gls{Glen} to read the love letter to her, and fails to understand the fancy
words. She asks for a summary at the end, and \Gls{Glen} tries to simplify the message for her,
while realizing that \Gls{Trev} likely had someone else pen it for him. Meanwhile, \Gls{Pepe} and
\Gls{Sharn} are overwhelmed by the media attention at their store, and try desperately to recall
where \Gls{Juliet} lives, so that they can get her back for another show.

\subsection{}
\subsubsection{\Gls{RhysR} decides to take the new trade opportunities from \Gls{Sharn} seriously}
\Gls{RhysR} receives the front-page spread of \Gls{Juliet}'s photo as a dwarf, and is forced to
placate the dwarf priests, who try to argue that a human posing as a dwarf is blasphemy. He makes
plans to get \Gls{Sharn} to place a large order for her new fabric to be made in the dwarf mines of
Uberwald. Meanwhile, \Gls{Ridcu} inspects the replica football, and is impressed by its similarity
to the real one.

\subsubsection{\Gls{Stibb} and \Gls{Ridcu} observe the impromptu football game}
\Gls{Stibb} returns the original football to the Cabinet of Curiosity, as \Gls{Ridcu} sets up an
impromptu football match in the Great Hall. \Gls{Rince}, now promoted to Emeritus Professor, in
recognition for saving the world several times out of sheer dumb luck, tries to weasel out of
playing the game, but is forced to remain by \Gls{Ridcu}. \Gls{Stibb} then points out \Gls{Bengo},
a visiting professor from Quirm, as the ball is kicked toward an ancient shifting mural on one wall
of the Hall.

\subsubsection{\Gls{Nutt} and \Gls{Trev} offer some advice to \Gls{Ridcu} about goalkeeping rules}
\Gls{Nutt} shows up to offer advice about the \Gls{Libra} being allowed to touch the ball with his
hands, when he scoops it out of the air, and \Gls{Smee} tries to berate him for shirking his duties.
\Gls{Ridcu} takes pity on \Gls{Nutt}, when he is reminded of \Gls{Vetina}'s seriousness regarding
the goblin's safety, and allowed to leave without any trouble.

\subsubsection{\Gls{Glen} decides to enter the cosmetics marketing industry seriously}
\Gls{Glen} takes \Gls{Sharn}'s advice about the cosmetics industry to heart, and sells all of her
current stock of troll lipstick. She returns to the manufacturer, and offers him advice about
branching out into troll footwear, clothing and perfume, before setting off to the University.
Meanwhile, \Gls{Ridcu} struggles to control his temper when the \Gls{Dean} walks in, as the newly
appointed Archchancellor of Brazenec University in Pseudopolis.

\subsubsection{\Gls{Ridcu} argues with the \Gls{Dean} about the traditions of Unseen University}
\Gls{Ridcu} is alarmed to learn that one of \Gls{Stibb}'s brightest students has been poached to be
a professor by the \Gls{Dean}, and starts up an argument about football. The two Archchancellors
almost come to blows about the ancient decorative hat, until \Gls{Stibb} proposes an
inter-collegiate football match for possession of said hat. \Gls{Ridcu} and the \Gls{Dean} seem
placated by the idea, and proceed to lunch, leaving the rest of the faculty to continue their match.

\subsubsection{\Gls{Nutt} starts to talk about the essence of football}
\Gls{Nutt}'s lecture is interrupted by \Gls{Nobbs}, who asks \Gls{Stibb} why such a well-spoken
person is forced to make candles all day. \Gls{Stibb} recalls \Gls{Ridcu}'s words of warning, and
changes the subject to the rules of football. \Gls{Nutt} in turn, wishes to have \Gls{Trev} in the
University team, given his footwork with the metal cans lying around in the cellar. \Gls{Nutt} is
happy to be given the role of team selector and coach, as he asks to take them to a ballet school
for some lessons.

\subsubsection{\Gls{Ridcu} and \Gls{Stibb} listen to the new team chant}
The next day, \Gls{Ridcu} tries to get \Gls{Stibb} wound up by mentioning his student's promotion
to professor, and the copying of his computer Hex. He finds \Gls{Stibb} happy to see his student
succeed, and too burdened by all the responsibility pawned off to him by the Inner Council to care
about professorship. They proceed to the Great Hall, where practice is halted by the arrival of the
Professor of Music, with a new chant for their team.

\subsubsection{\Gls{Nutt} prepares to make a show of lighting the chandelier in the Great Hall}
\Gls{Ridcu} denies \Gls{Nutt}'s request to put on a show of football moves, to be exhibited at the
banquet later that night. \Gls{Glen} arrives at the University some time later, and decides to
violate \Gls{Whitlow}'s unwritten rule barring maids from the night shift from working special
events. In the Great Hall, she finds \Gls{Nutt} trying to persuade \Gls{Smee} that he will light
the main chandelier after the guests arrive, using a trick. \Gls{Smee} realizes that leaving the
Hall might absolve him of responsibility, and speeds off.

\subsubsection{\Gls{Vetina} gets the two Archchancellors to agree to an exhibition football match}
\Gls{Whitlow} tries to chastise \Gls{Glen} for coming to the Great Hall, but is forced to let go
when \Gls{Ridcu} congratulates her on the useful advice. He asks \Gls{Nutt} if he has something
planned for the chandelier, and is surprised to learn that the goblin can speak fifteen languages.
A while later, \Gls{Vetina} arrives at the University, and persuades the two Archchancellors to
arrange a football match between the two universities with the sentient \Gls{AHat} as the prize.

\subsubsection{\Gls{Nutt} performs some complex alchemy to light the chandelier from the floor}
\Gls{Nutt} lights the chandelier instantaneously using dwarven alchemy, although it seems like magic
to the layman. \Gls{Stibb} confirms that no magic has been used, by looking at his thaumometer, as
\Gls{Ridcu} drags \Gls{Nutt} aside to ask how he did it. Meanwhile, \Gls{Glen} spots \Gls{Stollop}
stealing some silverware, and warns him to put it back, lest \Gls{Vetina} notice his thieving.

\subsubsection{\Gls{Glen} sees \Gls{Vetina} end the dinner with a speech introducing the new league}
\Gls{Glen} watches \Gls{Vetina} give his speech to the assembled football captains, as \Gls{Trev}
and \Gls{Bengo} put on a show with the new spherical ball. He has a copy of the new rulebook
supplied to each of them, and invites them to field a team against the Unseen Academicals, with the
constraint that the Wizards could not use any magic in the game.

\subsubsection{\Gls{Vetina} surprises \Gls{Ridcu} and the \Gls{Dean} with his knowledge of football}
\Gls{Vetina} is shocked to see one of the captains accost him in the lounge, as he is busy
discussing the league with the two Archchancellors. They are surprised when he narrates in great
detail the reasons for the captain doing badly the last few seasons, and urges him to consider the
new league as a way to improve his standing in the city.

\subsubsection{\Gls{Glen} decides to confront \Gls{Vetina} about the football reforms}
\Gls{Glen} reads the new football rules in the paper the next morning, and is incensed by the
Patrician's attempt to take away a game loved by the masses, and reshape it into something else.
She goes to the palace using some of her baked pastries to bribe the guards, just as \Gls{Vetina}
asks \Gls{Drumk} to let her in.

\subsubsection{\Gls{Glen} tries to question \Gls{Vetina}'s methods at the banquet}
\Gls{Vetina} tells \Gls{Glen} that he is merely saving the football captains from a life of violence
on the streets, and an early death in an attempt to be heroic. \Gls{Glen} gives up on questioning
his reforms, and asks him why he is not drunk. \Gls{Vetina} tells her that he is merely acting
sober, and that he had just as much to drink as the captains at the banquet. He thanks her for
taking care of \Gls{Nutt} on her way out.

\subsubsection{\Gls{Glen} takes \Gls{Pepe} to the University to see \Gls{Juliet}}
On her way to the University, \Gls{Glen} is accosted by \Gls{Pepe}, who tells her that every single
magazine writer is looking for \Gls{Juliet}, in order to write a big profile-piece. She takes him
to the Night Kitchen, only to find the kitchen a mess from someone baking a batch of pies without
telling her. She finds \Gls{Juliet} sleeping in a corner, and congratulates her on the quality of
her pies.

\subsubsection{\Gls{Glen} encourages \Gls{Juliet} to go out and be a model}
\Gls{Glen} asks \Gls{Juliet} to be bold and take the risks she never could, before handing over the
bank book where her modeling payout was deposited. She then asks \Gls{Juliet} to set aside her
feelings for \Gls{Trev}, and go pursue the modeling career with \Gls{Sharn}. After \Gls{Juliet}
leaves, \Gls{Glen} decides not to mourn the loss of control over her friend's life, and is surprised
to see \Gls{Conc} come to the kitchen, talking about \Gls{Nutt} being sick.

\subsubsection{\Gls{Nutt} asks \Gls{Trev} to help him psychoanalyse himself}
\Gls{Nutt} lies on a mattress in the candle vats, complaining about the dark thoughts in his mind
trying to break through. \Gls{Trev} asks him if he can perform a hypnotic suggestion on himself,
like how he helped \Gls{Trev} confront the fantasy about his father's life as a football player.
\Gls{Trev} performs the start of the hypnosis by using a tin can as a pendulum, and \Gls{Nutt}
starts to interrogate himself.

\subsubsection{\Gls{Trev} and \Gls{Glen} oversee \Gls{Nutt}'s hypnosis}
\Gls{Nutt} asks the others to bind him in heavy chains, as he starts the analysis. He forces
himself to open a strange door that \Gls{Ladyship} had warned him not to open in her castle. He
finds a book titled Orc in the cupboard, just as two sentient birds drop out of the pipes in the
candle vat, shouting a warning about \Gls{Nutt}. \Gls{Glen} screams to draw people to the cellar,
just as the birds vanish in a hurry.

\subsubsection{\Gls{Glen} and \Gls{Trev} are joined by \Gls{Juliet} in the cellar}
\Gls{Glen} is surprised to learn that \Gls{Nutt} is an orc, as \Gls{Nobbs} arrives with some other
bakers in answer to the commotion. \Gls{Nutt} seems to be in control of his emotions, and the
crowd agree that he poses no threat, until he manages to tear apart the chains binding him with
little effort. The crowd runs away, as \Gls{Juliet} arrives to say goodbye to \Gls{Trev}.

\subsubsection{\Gls{Glen} confronts \Gls{Nutt} and tells him to fight against his nature}
\Gls{Trev} wishes \Gls{Juliet} the best and encourages her to go out and follow her dreams, leaving
\Gls{Glen} suspicious about the sincerity of his feelings. \Gls{Trev} points \Gls{Glen} to
\Gls{Nutt}'s private force in the cellars, where she finds him sulking. She asks him to get up and
continue being useful to the University, by training the football team. Afterward, she goes to the
Library, to find the \Gls{Libra} ready with a copy of the book, which shows some gruesome images of
orc violence.

\subsubsection{\Gls{Hix} and \Gls{CharlieS} help \Gls{Glen} learn about orcs}
The \Gls{Libra} drags \Gls{Glen} to \Gls{Hix}'s office, where the assistant \Gls{CharlieS} is
exasperated at having to explain the history of orcs all over again. \Gls{Hix} tells them that
\Gls{Ridcu} came to him with the same questions earlier, and is aware of \Gls{Nutt}'s real identity.
\Gls{CharlieS} pulls out the last few seconds of a human fighter in a battle against orcs long ago,
and plays it for \Gls{Glen} on a magic mirror.

\subsubsection{\Gls{Glen} comes up with a plan to convince \Gls{Nutt} that he is not inherently
    evil}
\Gls{Glen} notices something odd in the playback, and asks to see it zoomed in. She notices riders
with whips driving the orcs forward, and realizes that they were merely manufactured en masse for
use as weapons of war. \Gls{Hix} offers her a more substantial job in his Department, and is sad to
see her refuse. She returns to the kitchen, to find \Gls{Ottomy} fretting about the presence of an
orc at the University.

\subsubsection{\Gls{Glen} disposes of the crab gifted to her for dinner}
\Gls{Glen} tells \Gls{Ottomy} that \Gls{Ridcu} is already aware of \Gls{Nutt}'s identity, and
welcomes him to go lodge a complaint. She then throws the crab gifted by her friend into the river,
choosing not to cook it for dinner. \Gls{Trev} and \Gls{Juliet} return from football practice, with
news of \Gls{Nutt}'s disappearance. They say that \Gls{Nutt}'s toolbox is missing from his forge,
and believe that he might be heading back to \Gls{Ladyship}'s castle in Uberwald.

\subsubsection{\Gls{Glen} and the others find \Gls{Nutt} on the road to Sto Lat}
\Gls{Glen} decides to go after \Gls{Nutt}, when she notices the sentient birds no longer squeaking
in the background. \Gls{Trev} and \Gls{Juliet} accompany her, as they head to a night coach service,
and bargain for overnight travel to Sto Lat. On the way there, they find the sentient birds trying
to harass \Gls{Nutt}, who is lying down on the side of the road.

\subsubsection{\Gls{Glen} and the party reach Sto Lat}
\Gls{Glen} is pleased to find the fellow passengers warming to \Gls{Nutt}, and reminding him that
he should not be sorry for who he is. \Gls{Glen} advises the sentient birds to return to
\Gls{Ladyship}, before any of the passengers decide to punish them for haranguing \Gls{Nutt}.
Once the carriage reaches Sto Lat, the driver is happy to take them back on the return trip, and
fondly remembers \Gls{Juliet}'s kiss.

\subsubsection{\Gls{Glen} runs into \Gls{Ladyship}'s assistant at the rest stop}
\Gls{Nutt} offers to help another mail coach fit a horseshoe to clear up the traffic jam at the
rest stop, leaving the others to rest. \Gls{Glen} finds someone fitting \Gls{Margo}'s description
come out of the tavern, and asks her comapanion about \Gls{Nutt}. The companion responds by asking
if \Gls{Nutt} has ever been a danger to the people around him, and promises to convey \Gls{Glen}'s
concerns to the \Gls{Ladyship}.

\subsubsection{\Gls{Nutt} tells \Gls{Glen} about the love poem}
\Gls{Nutt} uses his horse-whispering skills to put a new horseshoe onto the waiting horse, even as
the owner reminds the others about how ill-mannered it usually is. \Gls{Trev} quickly steps in to
demand a return ride to Ankh-Morpork as payment for the late-night express job. \Gls{Nutt} tells
\Gls{Glen} that he wrote the poem for her, and is amused to see her shed tears of joy. \Gls{Trev}
calls for them to board the express coach going back, as \Gls{Nutt} remains worried about the stigma
of being an orc.

\subsubsection{\Gls{Glen} and the party return to Ankh-Morpork}
\Gls{Glen} and \Gls{Nutt} decide not to pursue their romance for the time being, and are surprised
to see a large crowd at the gates of the University. \Gls{Stibb} escorts them in through a side
entrance, and tells them that the paper has printed a front-page piece on \Gls{Nutt} being an orc.
He talks about the tabloids spreading misinformation about orc behaviour, and speculates that
\Gls{Vimes} will want \Gls{Nutt} in protective custody.

\subsection{}
\subsubsection{\Gls{Glen} and \Gls{Juliet} go to football practice with \Gls{Nutt}}
\Gls{Glen} is joined by \Gls{Pepe}, as \Gls{Nutt} insists on going to the other side of the city
for football practice. \Gls{Vimes} decides to arrange an escort for them, given how much resentment
is spreading through the city with news of \Gls{Nutt} being an orc. \Gls{Pepe} catches up to
\Gls{Trev}, who leaves to find \Gls{Andy}, and offers him some protective armour for the coming
game. He anticipates mob violence from all of the football hooligans not prepared to follow their
captains.

\subsubsection{\Gls{Trev} learns from \Gls{Carter} that \Gls{Andy} is planning a riot}
\Gls{Trev} visits \Gls{Carter}, who is down with an infected cut, from discouraging \Gls{Andy} the
previous night in his plan to cause a riot at the exhibition match. \Gls{Trev} is amazed by
\Gls{Carter}'s sudden bravery, and makes plans to track \Gls{Andy} down before the match, along with
the other hooligan leaders.

\subsubsection{\Gls{Trev} finds \Gls{Nutt} talking to a reporter from the Times}
\Gls{Trev} reaches the empty field where teams are practicing, and finds \Gls{Dibbl} peddling his
merchandise. He sees some stands being put up for the spectators, and finds \Gls{Stibb} explaining
the offside rule to the captains. \Gls{Andy} shows up with his custom jersey bearing a number and
name, to identify himself from the back. He then spots \Gls{Nutt} giving a verbose lecture to a
Times reporter intending to make a lifestyle piece on him.

\subsubsection{\Gls{Trev} and \Gls{Glen} warn \Gls{Vetina} in person about \Gls{Andy}'s plans}
\Gls{Trev} warns \Gls{Nutt} and \Gls{Glen} about the foul play being planned by \Gls{Andy}, only
to see \Gls{Glen} decide to inform \Gls{Vetina} personally. \Gls{Vetina} welcomes \Gls{Glen} at his
office, as \Gls{Margo} is in the middle of her negotiations. He listens to \Gls{Trev}'s warning, and
reassures them that the referees will be present on the field to ward off any attempts at violence.
After they leave, \Gls{Margo} asks him if he expected \Gls{Glen} to barge in, and is amused when he
says yes.

\subsubsection{\Gls{Trev} goes to \Gls{Pepe}'s shop for the armoured football uniforms}
\Gls{Trev} asks \Gls{Glen} and \Gls{Nutt} to accompany him with two bottles of wine for \Gls{Pepe},
as he tries to fight off \Gls{Nutt}'s request to play on the team the next day. Meanwhile, the
rest of the team is forced to adhere to a strict diet, and denied any alcohol for the day.
\Gls{Pepe} gives \Gls{Nutt} and \Gls{Trev} a special set of reinforced clothing, that is capable of
perfectly reflecting any blunt force aimed at it.

\subsubsection{\Gls{Ridcu} leads the team to the stadium on match day}
\Gls{Pepe} invites \Gls{Glen} and \Gls{Juliet} to front-row seats for the football match, bought by
\Gls{Sharn} to advertise her new clothing line. Before the team sets out from the University to the
arena, \Gls{Ridcu} informs them that \Gls{Whitlow} has organized some maids into a cheerleading
squad. When the Watch escort takes them to the stadium, they find \Gls{Vimes} in a bad mood,
wondering how much violence and rioting the game will lead to.

\subsubsection{\Gls{Trev} notices the two teams being assembled for the anthem}
\Gls{Vimes} warns \Gls{Ridcu} that the Watch will not step onto the field to interfere, and is
skeptical of the \Gls{Dean}'s claim that no magic would be used during the match. After \Gls{Vimes}
leaves, the \Gls{Dean} summons the captain of the challenging team \Gls{Hogget}, along with the
two teams. \Gls{Trev} notices that \Gls{Andy} has also come to the realization that the referee
himself will have no access to his magic inside the playing field, as he notices the \Gls{Dean}
wrap up his staff.

\subsubsection{\Gls{deWorde} tries faithfully to document the game for his paper}
As the game begins, \Gls{deWorde} decides to find a megaphone, so that he can make the details of
the game known to the audience in real time. After \Gls{Bengo} scores two goals in the first half,
\Gls{Ridcu} decides to gift one of the goals to the enemy team, hoping to reinforce their feelings
of inferiority. \Gls{Stibb} congratulates him on his psychological warfare, as \Gls{deWorde} spots
\Gls{Juliet} in her dwarf costume, in the VIP box.

\subsubsection{\Gls{Dean} is forced to overlook a foul against \Gls{Bengo}}
When the \Gls{Dean} is busy watching someone else, \Gls{Andy} and his teammates injure \Gls{Bengo}
with a nasty tackle, leading to his removal from the field. \Gls{Lawn} arrives with his kit to
help \Gls{Bengo} at the sidelines, as \Gls{Nutt} prepares to enter the game as a substitute. The
\Gls{Libra} eats a banana does with sleeping pills thrown to him from the stands, and \Gls{Trev}
is forced to enter the game as well.

\subsubsection{\Gls{Trev} is convinced to step in as a substitute when the audience chants his
    father's name}
\Gls{Pepe} is alarmed to see the crowd chant against \Gls{Nutt}, and makes them change their chant
to one honouring \Gls{Trev}'s father. Meanwhile, \Gls{Andy} scores another goal, and \Gls{Ridcu}
is injured, forcing \Gls{Nobbs} to take up the captaincy. After the half-time whistle, the
\Gls{Dean} decides to end the game with the next goal, given how much violence seemed to be
simmering in the audience.

\subsubsection{\Gls{Trev} scores the winning goal with his tin can}
\Gls{Trev} gives \Gls{Glen} his old tin can, and she is surprised to hear it talk when the match
becomes too close to call. The \Gls{Libra} returns to his goalkeeping duties, and \Gls{Trev} misses
one shot on goal after another. \Gls{Glen} arranges for \Gls{Nobbs} to kick the ball out of play,
and substitutes it with the tin can, which \Gls{Trev} has masterful control of. He scores, ending
the game, and the audience mysteriously chants the ancient song of football.

\subsubsection{\Gls{Andy} fails to harm \Gls{Trev} after the game ends}
\Gls{Andy}'s attempt to wound \Gls{Trev} is thwarted by \Gls{Pepe}'s new fabric, which returns the
force to his own body. \Gls{Nutt} then restrains him, and starts joking about the force needed to
tear his head off his neck. \Gls{Glen} and \Gls{Nutt} go to see one of \Gls{Hix}'s amateur drama
productions, and then visit \Gls{Margo} at the palace.

\subsubsection{\Gls{Margo} tells \Gls{Nutt} about his grand mission with the wild orcs}
\Gls{Margo} tells \Gls{Vetina} that \Gls{Nutt} might be a valuable leader for the last remaining
bands of orcs in their remote mountain communities, as \Gls{Nutt} and \Gls{Glen} arrive at the
Great Hall. \Gls{Nutt} takes up \Gls{Margo}'s offer of helping the wild orcs enter civilization, and
\Gls{Glen} is happy to leave her job behind and go with him.
