\section{Wintersmith}


\subsection{}
\subsubsection{\Gls{RobA} and the Feegles sense the \Gls{Wint} coming to visit \Gls{Tiff}'s village}
\Gls{RobA} peeks out of his colony's chimney after a heavy snow storm, and wonders if the \Gls{Wint}
has tracked down \Gls{Tiff} to her village. He sets out to find the hero who will save her from
the winter spirit, even as the rest of his clan warn him of the risk involved. Meanwhile, \Gls{Tiff}
is dismayed by her inability to assuage her family's worries regarding the newborn lambs suffering
in the sudden cold.

\subsubsection{\Gls{Tiff} uses her own body as a conduit to transfer heat to the snow}
\Gls{Tiff} asks her father to ensure a large bonfire is continuously kept burning on the hill next
to the village, and learns that her brother \Gls{Went} is missing, having gone off with the
shepherds to rescue the lambs in the birthing pens. She prepares her heat transfer spell, and walks
to the lambing pens that are buried in several feet of snow. She uses her own body as a conduit for
the heat from the bonfire, and makes it consume wood at an alarming rate, in order to melt a path
through the pens.

\subsubsection{\Gls{Tiff} rescues her brother just as she runs out of magic to melt through the
    snow}
\Gls{Tiff} eventually runs out of heat when the villagers run out of fuel to feed the fire. She
manages to find \Gls{Went} at the last moment, and hands him off to a shepherd for rescue. The
\Gls{Wint} smiles at her when it senses her caught in his trap.

\subsubsection{\Gls{Tiff} brings a kitten along for \Gls{GWea}}
\Gls{Tiff} visits \Gls{GWea} at her cottage, as part of the regular informal checkups on senior
witches, to ensure they don't go sociopathic from all the isolation and stress. \Gls{GWea} remains
aloof until \Gls{Tiff} mentions how successful \Gls{Earwig} has been with her new book and fancy
jewelry for young witches. \Gls{GWea} is shocked to find a white kitten inside her gift bag, and
\Gls{Tiff} says it will keep her company in her lonely cottage.

\subsubsection{\Gls{Tiff} leaves \Gls{GWea}'s cottage, satisfied that the kitten will be taken in}
\Gls{Tiff} is caught by \Gls{GWea} when she tries to camouflage herself outside \Gls{GWea}'s house
to see if she will take the kitten back in after she is left alone. \Gls{GWea} is impressed by the
strength of her camouflage, and tells her not to worry about the kitten. She shows off the heat
transfer spell, and reminds \Gls{Tiff} that the way every witch performs the same magic is wildly
different, and cannot be learned through explicit instruction.

\subsubsection{\Gls{Tiff} thinks about her time helping \Gls{Treason} as part of her trainee
    curriculum}
\Gls{Tiff} thinks about her time in \Gls{Treason}'s cottage, and her shock at the witch's permanent
use of animals to see and hear the outside world since her own organs had given up long ago. She
thinks about how \Gls{Treason} refers to \Gls{GWea} as a little girl, being more than a century old
herself, and of how she has taken on the role of magistrate for her village.

\subsubsection{\Gls{Tiff} takes \Gls{Treason} to a dancing ceremony in the forest}
One day, \Gls{Tiff} is surprised to hear \Gls{Treason} talk about some ceremony she has to attend,
and asks her to prepare the broomstick for stormy weather. Once \Gls{Tiff} takes \Gls{Treason} to
the clearing deep inside the forest, she is asked to act as the old woman's eyes, and sit still in
front of the bonfire staring at the dancers. \Gls{Treason} warns her that the air will get much
colder as the dance proceeds, and asks her to put on her heavy cloak.

\subsubsection{\Gls{Tiff} violates \Gls{Treason}'s orders and participates in the winter dance}
\Gls{Tiff} recognizes the dancers as the same ones that came to her village every spring to herald
the coming of summer, and wonders why \Gls{Treason} warned her against looking away from them.
Eventually, the drumbeats take over her mind, forcing her to enter the dance herself. She hears a
disembodied voice ask her who she is, and then crashes into the dancers, disturbing their rhythm and
sending them crashing.

\subsubsection{\Gls{Treason} keeps \Gls{Tiff} safe from the \Gls{Wint}}
\Gls{Tick} finishes one of her stealth missions scouting for young girls showing magical talent in
villages that shunned witches. She has a sudden thought about \Gls{Tiff}, and creates a magic
detector, only to watch it explode in a ball of frost. Meanwhile, \Gls{Treason} watches over
\Gls{Tiff} as she sleeps in the upstairs bedroom, confident that the \Gls{Wint} will not be able to
track her close to the cottage.

\subsubsection{\Gls{RobA} talks to \Gls{Treason} about his mission to save \Gls{Tiff}}
\Gls{RobA} and his squad of Feegles get caught creeping through \Gls{Treason}'s basement, and are
forced to admit the truth about their obligation to protect \Gls{Tiff}, who was their clan leader
for a few short days. \Gls{RobA} talks about \Gls{Jeannie}'s premonitions about their colony being
covered in a thick layer of snow, and of \Gls{Tiff} wearing a crown as the Feegles freeze to death.

\subsubsection{\Gls{Treason} tries desperately to keep the \Gls{Wint} from getting to \Gls{Tiff}}
\Gls{Treason} realizes that the \Gls{Wint} has found \Gls{Tiff} when the fierce wind suddenly dies
down, and goes up to her room. She asks the Feegles to load up the fireplace with wood, so that
the \Gls{Wint} will not be able to sneak into the room through the chimney or the window frames.
The Feegles remind \Gls{Treason} that they had also witnessed \Gls{Tiff} dancing with the \Gls{Wint}
at the ceremony, and of how it was now obsessed with finding her.

\subsubsection{\Gls{Tiff} observes \Gls{Treason}'s book showing a depiction of the \Gls{Wintler}}
After \Gls{Tiff} wakes up, \Gls{Treason} explains to her that the empty space in the winter dance
was not meant for her to occupy, and asks her to fetch a book from her shelf, which depicts the
\Gls{Wint} as a wizened old man, next to the spirit of summer being shown as a tall beautiful woman.
\Gls{Treason} tells \Gls{Tiff} that her innate magical talent has given special meaning to her
interference with the winter dance.

\subsubsection{\Gls{Tiff} tries to put up with \Gls{Treason}'s insults}
\Gls{Tiff} runs out of the cottage and screams for the \Gls{Wintler}, only to find an invisible
spirit hand her the silver pendant gifted by \Gls{Roland}. The pendant is so cold that it leaves her
palm frostbitten, and the Feegles carry her back into the house for \Gls{Treason} to look at her
injury. She chides \Gls{Tiff} for accepting the pendant from the spirit, forcing \Gls{Tiff} to
point out how necessary it is for her to feel powerful.

\subsubsection{\Gls{Treason} explains the need for psychological warfare when it comes to preserving
    value as a witch}
\Gls{Treason} asks the Feegles to get out of the cottage and ensure that the \Gls{Wint} is indeed
leaving the area. Once she is sure of their privacy, she asks \Gls{Tiff} about the pendant, and
tells her that \Gls{GWea}'s ideas about putting on a show are essential to surviving in rural
societies. The sentient cheese block named \Gls{Horace} breaks into the dairy yet again, and eats
some butter that \Gls{Tiff} had been churning.

\subsubsection{\Gls{Tiff} responds to \Gls{Roland}'s letter talking about life in the village}
\Gls{Tiff} reads the letter from \Gls{Roland}, keeping in mind the fact that the Feegles had already
opened the envelope and gone through it as part of their imperative to guard her. She starts to
write a response, just as \Gls{Horace} thinks about walking out of the cottage through the back
door. Meanwhile, \Gls{Tick} negotiates travel to Lancre using the mail coach by abusing her
authority as a witch, and claiming to be a two pound parcel with postage attached to her sleeve.

\subsubsection{\Gls{RobA} steals \Gls{Tiff}'s diary in order to read the latest entries}
\Gls{Tick} fails to take note of the \Gls{Wint}'s presence in the snowflakes falling on her dress,
as she sets off on the mail coach to the mountains. After \Gls{Tiff} falls asleep, \Gls{RobA} steals
her diary and takes it to the rest of the Feegles, who are waiting for him in a clearing away from
the cottage.

\subsubsection{The Feegles reflect on \Gls{Jeannie}'s plan to use \Gls{Tiff} as a counterbalance
    to \Gls{Roland}}
\Gls{RobA} struggles to make sense of the code in \Gls{Tiff}'s diary, as \Gls{Yan} reminds them of
the \Gls{Baron}'s attempts to expand agriculture in the village. \Gls{Jeannie} is worried about the
clan's colony being plowed over if \Gls{Roland} goes along with his father's plan to sow wheat
around the village, and hopes to curtail his greed by getting \Gls{Tiff} to marry him.

\subsection{}
\subsubsection{\Gls{GWea} and \Gls{Tick} talk about the predicament facing \Gls{Tiff}}
\Gls{GWea} notices the odd snowflakes falling in her area, as her white kitten named \Gls{You}
stares intently at the falling snow. Inside her cottage, \Gls{Tick} waits for dinner to finish
stewing, and talks about the possible ways of getting the \Gls{Wint} to leave \Gls{Tiff} alone.
\Gls{GWea} is convinced that the \Gls{Wint} is obsessed with the girl, and that the only way for
her to get rid of the spirit is to play her part in the story.

\subsubsection{\Gls{Roland} barricades himself from his controlling aunts}
\Gls{RobA} returns the diary to \Gls{Tiff}, and shows her the snowflakes raining down on
\Gls{Treason}'s cottage, which are all identical images of her. Meanwhile, \Gls{Roland} locks
himself in a tower to protect himself from his two aunts, who are likely to be left with the power
should the \Gls{Baron} succumb to illness. He looks over his store of provisions, and prepares to
step out of the seemingly locked room using a secret tunnel.

\subsubsection{\Gls{Tiff} learns of \Gls{Treason}'s impending death}
\Gls{Tiff} is embarrassed by all the harm being done to the people in the mountains by the
premature snowfall. \Gls{Treason} tells her that she is about to die in the next few days, and
gives her some letters to deliver. She also asks the Feegles to prepare for a lavish pre-death
funeral party, and sends \Gls{Tiff} with letters for the food and drink that will be needed.

\subsubsection{\Gls{Tiff} attends the trainee witches' regular gathering}
\Gls{Tiff} goes to the regular meetings held by \Gls{Anna} for trainee witches, and tells them
that \Gls{Treason} is about to pass on. \Gls{Anna} asks her if \Gls{Treason} mentioned who would be
inheriting her cottage, and is horrified by the idea that she could be passed over for \Gls{Tiff},
who is much younger. She is dismayed to see that none of the other girls noticed the strange
snowflakes, and tells \Gls{Petulia} on her way back to \Gls{Treason}'s house.

\subsubsection{\Gls{Petulia} talks to \Gls{Tiff} about the \Gls{Wint}'s interest in her}
\Gls{Petulia} tells \Gls{Tiff} that she is interested in one of the boys in her village, who happens
to be the son of a large-scale pig farmer. \Gls{Tiff} feels the frostbite scar twinge all of a
sudden, and wonders if the \Gls{Wint} will show up at the funeral party. Meanwhile, the Feegles
overhear the exchange, and \Gls{GWea} uses a saucer of ink as a scrying ball to eavesdrop on the
conversation.

\subsubsection{\Gls{GWea} and \Gls{Tick} discuss the cause of the \Gls{Wint}'s obsession with
    \Gls{Tiff}}
\Gls{GWea} speculates that \Gls{Tiff} might have inadvertently substituted herself for the spirit
of summer in the dance, and gotten the \Gls{Wint} to believe she is a manifestation of his
destined partner. \Gls{Tick} asks her who she has in mind as \Gls{Treason}'s replacement, and
reminds her of \Gls{Anna} being \Gls{Earwig}'s star pupil.

\subsubsection{\Gls{Tiff} and \Gls{Petulia} see the \Gls{Wint} make delicate roses out of ice}
\Gls{Tiff} wakes up before sunrise, unable to sleep with the funeral party coming up. She goes out
into the garden, and sees the roses made of thin ice waving in the wind, before the \Gls{Wint} asks
her if she likes them, by making her speak the words with her own mouth. \Gls{Tiff} runs back
indoors to fetch \Gls{Petulia}, and shows her the roses. The \Gls{Wint} then talks through
\Gls{Petulia}, spooking her into silence.

\subsubsection{\Gls{Tiff} sees \Gls{Treason}'s psyop evolve all by itself}
\Gls{Tiff} listens to the townsfolk talk about \Gls{Treason} fondly, as they deliver the supplies
for the funeral party. She realizes how effective the propaganda has become, as \Gls{Petulia} chimes
in with memories of people in far away villages mentioning the scary-looking cottage that
\Gls{Treason} inhabited.

\subsubsection{\Gls{Tiff} learns about the rumours surrounding \Gls{Treason}'s successor}
\Gls{Tiff} goes around on catering duty as the witches arrive for the funeral party. One of the
other trainees lets her in on the fact that \Gls{GWea} has suggested her as \Gls{Treason}'s
successor, as the groups of gossiping witches look at her carefully as she walks past with trays
of snacks. A while later, \Gls{Anna} approaches her, asking if she has any real interest in becoming
\Gls{Treason}'s successor.

\subsubsection{\Gls{Tiff} learns about \Gls{Anna} being the likely candidate for \Gls{Treason}'s
    cottage}
\Gls{Tiff} thinks about her adventurous life, and of how being a village witch is a life of
thankless drudgery caring for people too stupid to get out of their own way. She wishes \Gls{Anna}
the best when she expresses interest in \Gls{Treason}'s position, and hopes to reform the village
using \Gls{Earwig}'s ideas of modern witchcraft.

\subsubsection{\Gls{Tiff} watches \Gls{Treason} prepare for her death}
\Gls{Tiff} tells \Gls{Tick} that \Gls{Anna} will struggle to manage the village, and goes out to
the back garden to find the Feegles stealing from the food stores. She cleans up after the witches
leave, and \Gls{Treason} asks her if there is any unfinished food in the larder. She then wears a
fancy night dress instead of her black robes and goes to sleep in her bed instead of the rocking
chair.

\subsubsection{\Gls{Treason} gets ready in the morning to walk into her grave}
\Gls{Treason} gifts \Gls{Tiff} the uncensored dictionary from her shelf, and approves her request to
also take along the book of mythological tales. \Gls{Treason} then tells her that the villagers will
feel only relief when they hear of her death, and wonders how \Gls{Anna} will win their approval
using her fancy trinkets.

\subsubsection{\Gls{Tiff} puts \Gls{Treason} to rest with a short sermon}
\Gls{Treason} is surprised to find the villagers gathered outside her cottage for her death, and
makes an elaborate show of winding down her mechanical clock, which was rumoured to contain her
artificial heart. She lies down in the grave, and \Gls{Tiff} watches \Gls{Death} come reap her soul.
She then hears \Gls{Bigchin} play a mournful song on his bagpipes, before returning to the goatshed
to get on with the day's chores.

\subsubsection{\Gls{GWea} saves \Gls{Tiff} from the \Gls{Wint}'s advances}
\Gls{Tiff} realizes that it is her birthday at noon, and goes out to see the \Gls{Wint} waiting
for her in the form of a man-shaped fog. She slaps him impulsively when he grabs hold of her hand,
and continues to mistake her for the spirit of Summer. \Gls{GWea} emerges from the garden hedges,
and banishes him for the time being. She asks for \Gls{Tiff}'s silver pendant, claiming that the
\Gls{Wint} is using it to track her.

\subsubsection{\Gls{GWea} takes \Gls{Tiff} away from \Gls{Treason}'s cottage}
\Gls{GWea} greets \Gls{Earwig} with an icy stare and polite conversation when she arrives with
\Gls{Anna} to take over the cottage. She then hastily drags \Gls{Tiff} around get \Gls{Treason}'s
old broomstick, so that they can travel to \Gls{Ogg}'s house in Lancre town to lie low. \Gls{GWea}
asks the Feegles to get there on foot, and hatches a plan to get rid of the silver pendant.

\subsubsection{\Gls{Tiff} gets rid of the silver pendant at the Lancre bridge}
\Gls{Tiff} throws away the silver pendant into the Lancre river, in accordance with \Gls{GWea}'s
plan to set the \Gls{Wint} on a wild goose chase into the open seas. She struggles not to show her
grief for the only keepsake she has ever been gifted in her life, but understands \Gls{GWea}'s point
about collateral damage that the \Gls{Wint} might cause in courting her. Meanwhile, the \Gls{Wint}
seeks to fashion a human body for itself, and sets out to find the special ingredients that might
get it to work.

\subsubsection{\Gls{Tiff} finds the \Gls{Wint} invading her dreams}
\Gls{Tiff} falls asleep in \Gls{Ogg}'s spare bedroom, and finds herself in a dream on board the
ship shown on \Gls{GAch}'s favourite brand of tobacco. She hears the voice of the \Gls{Wint} ask her
to be his bride, and spots a huge iceberg looming ahead of the ship, fashioned in her image. She
then sees hands rising from grates built into the ship's deck, seeming to hold prisoners who are
busy moaning in pain.

\subsubsection{\Gls{Tiff} dreams a strange dream where the \Gls{Wint} has made an iceberg in her
    image}
The Feegles manage to break into \Gls{Tiff}'s dream, and get to work stopping the ship from crashing
into the \Gls{Tiff}-shaped iceberg. The ship glances past the iceberg, sending fragments of sharp
ice onto the deck, and bruising \Gls{Tiff}'s hands from the effort of turning the steering wheel.
Her dream ends abruptly when one of \Gls{Ogg}'s daughters-in-law brings her the morning tea, and
tells her that \Gls{Ogg} is in the next room being served breakfast in bed.

\subsection{}
\subsubsection{\Gls{Tiff} wakes up from her dream and takes note of \Gls{Ogg}'s luxurious home}
\Gls{Tiff} wakes up and asks the Feegles if the dream was real. \Gls{Wullie} tells her that the
iceberg is in fact real, but not the rest of the events. She look at the faint bruising on her
fingertips, and dresses for the day, while thinking of the luxurious life that \Gls{Ogg} has built
for herself. When some floorboards erupt from the bedroom floor and start sprouting leaves,
\Gls{Ogg} walks in with news that \Gls{Tiff} has the power of fertile feet.

\subsubsection{\Gls{Tiff} learns that she is gaining the powers of the \Gls{Summer}}
\Gls{Ogg} listens to \Gls{Tiff} talk about the dance, and her accidental involvement with the
summoning of the \Gls{Wint}. She gets \Gls{Tiff} to wear thick slippers to stop her feet from
touching any organic matter, just as \Gls{GWea} arrives at the Ogg house with \Gls{Tick}. \Gls{Tiff}
correctly works out the fact that she is slowly gaining the powers of the \Gls{Summer}, as a result
of how the \Gls{Wint} seems to be confusing her with the goddess.

\subsubsection{\Gls{Tick} talks about the role that \Gls{Tiff} will have to play as the
    \Gls{Summer}}
\Gls{Tick} explains the story attached to the cycle of seasons, and believes that \Gls{Tiff} has
substituted for the \Gls{Summer} in a way that leaves the goddess without a role. \Gls{Tiff} recalls
that she heard two voices ask her who she was when she stepped into the dance, and wonders if, as
\Gls{Ogg} grows some fresh vegetables using the power of fertility in her feet.

\subsubsection{\Gls{RobA} borrows a book on romance in order to help \Gls{Tiff} charm the
    \Gls{Wint}}
\Gls{Tiff} learns about the rumoured abilities of the \Gls{Summer}, just as \Gls{GWea} lets
\Gls{You} out of her hat, so that it can run into \Gls{Ogg}'s kitchen for some milk. \Gls{RobA}
gets the Feegles into his makeshift scarecrow uniform, and goes to some traveling librarians for a
book on romance. He helps them retrieve their oxen in the heavy blizzard as payment for borrowing
the book.

\subsubsection{\Gls{Tiff} reads the romance novel brought to her by the Feegles}
\Gls{Tiff} goes around the town with \Gls{Ogg} on her medical visits, and sees an example of
\Gls{GWea}'s exceptional palliative care. She returns to find the romance novel under her pillow,
and is curious about the library stamp on its front page. She spends the night reading as much of
it as she can, while taking note of how far away it is from the reality of life on the farm.

\subsubsection{\Gls{Wint} starts the process of gathering the chemical ingredients to make a man}
The \Gls{Wint} talks to some children in Ankh-Morpork who are busy building a snowman. He learns
from them about the chemical composition of a human body, and sets out to find the elements that he
believes can be assembled into a human form. \Gls{Anna} shows up the next day looking ragged, and
asks to be allowed to dig up the skulls from \Gls{Treason}'s grave. \Gls{Tiff} agrees to help her
with the people in \Gls{Treason}'s jurisdiction for a while, and tells \Gls{Ogg} in private that
\Gls{GWea} must have put \Gls{Anna} up to the task just to humiliate \Gls{Earwig}.

\subsubsection{\Gls{Tiff} listens to the \Gls{Wint} mistake her for the \Gls{Summer}}
When \Gls{Tiff} stays up with a fresh corpse watching \Gls{Anna} sleeping soundly, the \Gls{Wint}
talks to her about becoming human, and tells her that he has made many more icebergs to court her.
In the morning, the two of them say their prayers before the old man's funeral, and head back to
\Gls{Treason}'s cottage, where they learn about a difficult delivery that needs their oversight.

\subsubsection{\Gls{Tiff} reads \Gls{Roland}'s letter about attending a banquet}
\Gls{Tiff} receives some more letters from \Gls{Roland}, and is angry at the fact that he went to
a party at the neighbouring lord's castle. She reads about him interacting with the lord's daughter
at the party, and in convinced that his evil aunts are scheming to distract him from the commoner
that \Gls{Tiff} is. Part of her mind reminds her that he might be trying to politely rebuff the
lord's daughter, just as she is trying to keep the \Gls{Wint} at arm's length.

\subsubsection{\Gls{Tiff} meets \Gls{Anoia} when she goes to the kitchen for some cutlery}
\Gls{Tiff} tries to find a spoon in the kitchen drawer, and curses when it gets stuck. The Goddess
\Gls{Anoia} manifests herself in response to her cursing, and helps clear up the blockage. She
realizes that \Gls{Tiff} is the new avatar of the \Gls{Summer}, and tells her that a God has not
fallen in love with a mortal for quite a long time. She tells her to deny the \Gls{Wint}'s courtship
outright, and bring a time of eternal summer to the Disc.

\subsubsection{\Gls{Tiff} promises to help \Gls{Anna} learn the skills needed to tend the village}
\Gls{Tiff} spots \Gls{Anna} at the front door the next morning, and learns that she is having
trouble keeping up with the problems in her jurisdiction. \Gls{Tiff} tells her that she is being
set up by \Gls{GWea} to fail spectacularly, just so that she can show the world how ineffective
\Gls{Earwig}'s new theory of witchcraft really is. \Gls{Tiff} promises to round up the other
trainees to come along to \Gls{Treason}'s cottage when they have spare time, so that they can help
\Gls{Anna} learn the trade.

\subsubsection{\Gls{Tiff} secures the help of the other trainees in saving \Gls{Anna}'s cottage}
\Gls{Tiff} gets \Gls{Petulia} to agree with her plan to assist \Gls{Anna} in secret, so that
\Gls{GWea} cannot play her petty politics with \Gls{Earwig}. On her way back to Lancre, she thinks
about one of the other girls telling her that \Gls{Anna} was jealous of her talent, and doubly so
of her lack of vanity.

\subsubsection{\Gls{Tiff} talks to the \Gls{Wint} using the power of the \Gls{Summer}}
\Gls{Tiff} gets off her broomstick on an isolated hill, and feels the \Gls{Summer} hijack her voice
to call on the \Gls{Wint}. She wrestles back some control over her voice, and tells the \Gls{Wint}
to stop pulling elaborate stunts to win her favour. She manages to intimidate him into leaving her
alone, and is alarmed to hear him say that he will have a human form ready for the next ritual
dance at the end of winter.

\subsubsection{\Gls{Tiff} receives the \Gls{Summer}'s horn of plenty as a Hogswatch present}
\Gls{Tiff} receives the magical horn of plenty on Hogswatch day as a present, when it drops out of
the sky leaving a crater in \Gls{Ogg}'s garden. \Gls{GWea} arrives shortly to point out the picture
in the book of mythology, that shows the horn overflowing with fresh produce harvested every summer.
\Gls{You} disappears into the horn, which turns out to be a pocket dimension much larger on the
inside. \Gls{GWea} demands that the kitten come back immediately, and only hears a faint meow in
response.

\subsubsection{\Gls{GWea} and \Gls{Ogg} work out the purpose of the horn}
\Gls{GWea} asks the Feegles in hiding to come out, and sends them into the horn after \Gls{You}.
The kitten runs out of the horn followed shortly by the Feegles, when \Gls{Tiff} tries to blow it
using its pointy end. A while later, \Gls{Ogg} works out how to use it as an infinite food source,
and gets \Gls{Tiff} to order a pile of sandwiches. \Gls{Tiff} wakes up later at night, to find out
that the horn has learned to understand even \Gls{You}, and is producing an infinity of chickens in
response to its meows.

\subsubsection{The \Gls{Wint} builds a human form for himself}
\Gls{Tiff} accidentally causes an acorn to sprout when she touches it in the forest outside Lancre.
She buries it in some soil after scooping out the layer of snow on top, and sets off to help
\Gls{Anna}. After she is gone, \Gls{GWea} builds a wall of snow around the fast-growing sapling to
keep it safe from the cold winds. Meanwhile, the \Gls{Wint} tests out his new human form made of
ice, and feels the experience of sentience for the first time.

\subsubsection{\Gls{Tiff} wears herself out trying to help Lancre town}
\Gls{Tiff} uses the horn of plenty to keep up a steady supply of food as a severe cold snap follows
Hogswatch day. The villages are forced to tunnel through the snow to keep warm, and wild animals are
reduced to death by starvation. \Gls{GWea} shows \Gls{Tiff} the oak tree that she charmed into
growing, and points out how it is thriving amongst the bare trees laden with snow. She asks
\Gls{Tiff} to return to her village, in advance of the approaching cold months, and try to help them
with her newfound powers.

\subsubsection{\Gls{Wint} tries to confront \Gls{Tiff}, but is banished by \Gls{Anna}}
The \Gls{Wint} makes a crude attempt at masquerading as a man, and walks into a coaching inn asking
for the whereabouts of \Gls{Treason}. He offers a gold coin to the innkeeper for the answer, and
sets off in search of \Gls{Tiff}. He finds \Gls{Tiff} at \Gls{Treason}'s cottage, and asks her to
finish the dance. \Gls{Anna} comes out wearing all of the horrifying cosmetics from the joke shop
in Ankh-Morpork, and hurls a fireball at the \Gls{Wint}, which melts his human form.

\subsubsection{\Gls{Anna} asks \Gls{Tiff} to fly home before the \Gls{Wint} returns}
\Gls{Anna} gives \Gls{Tiff} her modern broom, and asks her to flee to her home, without waiting for
the \Gls{Wint} to reassemble a human form and track her down again. \Gls{GWea} watches \Gls{Tiff}
leaving using her ink bowl, and tells \Gls{RobA} that a hero will need to be found who can enter the
Underworld and retrieve the real \Gls{Summer} in time for the end of winter. She suggests seeking
out \Gls{Roland} in \Gls{Tiff}'s village, and reminds him that the hero will have to be capable of
facing the enemies within his own mind.

\subsubsection{\Gls{Tiff} sees the undelivered mail for her from \Gls{Roland}}
\Gls{Tiff} flies home, and is forced to stop at Twoshirts for the night. She sleeps in the barn
behind a merchandise store, and hears the faint voice of the \Gls{Summer} asking her if she is
happy to have taken her powers for a pitiful dance with the \Gls{Wint}. She wakes up the next
morning, and sees the backlog of mail from \Gls{Roland} that the mailman has been unable to deliver,
because of the snow jamming the routes into the mountain.

\subsubsection{The Feegles ask \Gls{Roland} to help rescue the \Gls{Summer} from the Underworld}
\Gls{Tiff} lands at her village, and sends the broom back to \Gls{Anna}, before greeting her
family. She takes the day off to draw some paintings using \Gls{Roland}'s newly gifted art supplies,
and wonders if the weather being colder than usual is part of the \Gls{Wint}'s unrequited love for
her. The Feegles track down \Gls{Roland} within his castle, and are dismayed by his amateur
swordsmanship. He surprises them by reciting the tale of the hero rescuing \Gls{Summer} from the
Underworld, having read it in one of his books.

\subsubsection{\Gls{Tiff} accidentally gives away her location to the \Gls{Wint}}
The Feegles assemble themselves into an old suit of armour to give \Gls{Roland} some sparring
practice, and retreat to their colony until night time when he insists on visiting the sick
\Gls{Baron}. \Gls{Went} catches a huge fish in the river, and struggles to haul it back home at
dusk. As her mother cooks the fish for dinner, \Gls{Tiff} notices the lure still hanging from its
discarded head. She only realizes that it is the silver pendant after touching it, and senses the
\Gls{Wint} coming to the village.

\subsubsection{The \Gls{Wint} takes \Gls{Tiff} to his own realm}
Back in the present, \Gls{Hamish} picks up his assistant from the village, and notices that
\Gls{Tiff} has been kidnapped by the \Gls{Wint}, as the intense snowstorm withdraws from the
village. \Gls{Tiff} wakes up in the \Gls{Wint}'s palace, and wanders until she finds a throne
room with a crown and fancy robes, seemingly set out for her. She asks the \Gls{Wint} to let her go,
and is horrified to learn that she is in his own realm, where even \Gls{Death} cannot reach her.

\subsubsection{\Gls{Roland} crosses the river of the Underworld with the Feegles}
\Gls{Yan} shows \Gls{Roland} the secret to entering the Underworld, as he dons the heavy armour
and sword meant to make him the hero. \Gls{RobA} tells him to hurry along, and reassures him that
any underground tunnel can be used to enter the Underworld. He sees people wandering around the
purgatory, with \Gls{RobA} pointing out the monsters that ate memories now infesting the place. They
reach the river of the Underworld, and \Gls{Roland} pays \Gls{Death} the two pennies needed to
secure passage across the river.

\subsubsection{\Gls{Roland} decides to kill the dementia demons in the Underworld}
\Gls{Death} is annoyed by the Feegles singing merry songs as they cross the river, and leaves
quickly after receiving the two pennies from \Gls{Roland}. \Gls{Roland} then insists on killing the
dementia demons crowding the far bank, reminding himself of his father's tragic illness that robbed
him of his memories.

\subsubsection{\Gls{RobA} leads \Gls{Roland} through the Underworld}
\Gls{RobA} leads the way through the corpse of a three-headed dog, and points out how fancy the
Underworld used to be in earlier times. \Gls{Roland} throws his heavy sword into the river, once he
learns that he cannot use it against any of the dementia demons, and follows the Feegles to a
clearing, where the \Gls{Summer} is held comatose by a crowd of the same demons.

\subsubsection{\Gls{Roland} rescues the \Gls{Summer} from her coma in the Underworld}
\Gls{Tiff} realizes that the \Gls{Wint} has spared her village from the curse of eternal winter, and
sincerely believes that all the deaths his curse will bring to the Disc are a fair price to pay in
order to have her as his bride. Meanwhile, \Gls{Roland} finds the \Gls{Summer} bearing the form of
\Gls{Tiff}, and kisses her to wake her up from the magical sleep. The dementia demons start to
close in when they turn around to escape, and the Feegles tell \Gls{Death} that they will stay
back in the Underworld unless he lets them leave with the two others free of charge.

\subsubsection{\Gls{Tiff} banishes the \Gls{Wint} using her heat transfer spell}
\Gls{Roland} cuts through the mass of demons using his imagination to bring forth the sword he used
to practice his moves in the tower. \Gls{RobA} is glad to see his plan work, and gets them out of
the Underworld using his Feegle magic. Meanwhile, \Gls{Tiff} kisses the \Gls{Wint} while using her
heat transfer spell to melt his core of ice, and banish him. The cycle of seasons is restored, and
the palace of ice melts into water within seconds, leaving her standing a knee-deep pool of clear
water on a sunny afternoon.

\subsubsection{\Gls{Tiff} is reunited with \Gls{Roland} and the Feegles}
\Gls{Tiff} returns the horn of plenty to the \Gls{Summer}, who reveals her contempt for any mortal
attempt at meddling in the affairs of Gods. \Gls{Tiff} then spots \Gls{Roland} running to her with
the Feegles, and finds the nail that the \Gls{Wint} had used to build himself washing up amidst
the floodwater.

\subsubsection{\Gls{Tiff} assembles at the Town square of Lancre for the summer dance}
\Gls{Tiff} visits \Gls{GWea}, and lets her know that she is aware of her grand plan to humiliate
\Gls{Earwig} using \Gls{Anna} as a pawn. She then walks with her to the summer dance in Lancre
town, and notices the charmed oak tree growing at frightening speed. \Gls{Tiff} spots the golden
eyes of the \Gls{Summer} in the townsfolk watching the dance, and gives away the nail of the
\Gls{Wint} to the collection bowl as it gets passed around. Meanwhile, \Gls{RobA} decides to learn
how to read, given that \Gls{GWea} considered it one of the hallmarks of being a hero.