\section{Witches Abroad}


\subsection{}
\subsubsection{\Gls{Desi} prepares for her death, by passing on her mission to \Gls{GWea}}
Someone readies an armored scarecrow in a forest clearing, with the intention of finding a missing
girl. \Gls{Desi} writes her will in the comfort of her cottage, and looks in the mirror where
\Gls{Lilith}, her fellow fairy godmother, taunts her inability to find a protege. When \Gls{Death}
arrives to reap her soul, she starts to explain how delicate the profession of fairy godmothering
is, and wonders if her gambit to get \Gls{GWea} to Genua will work.

\subsubsection{\Gls{Lilith} gets ready to put her plans into motion, after the death of \Gls{Desi}}
\Gls{Desi} is afraid of the power of stories, and hopes that she can coerce \Gls{GWea} along with
the coven to interfere with \Gls{Lilith}'s meddling in Genua. She then lies down in the grave she
has prepared, and asks \Gls{Death} to take her soul. Meanwhile, \Gls{Lilith} looks at her pair of
mirrors in Genua, showing an infinity of reflections in them, and is pleased at the death of
\Gls{Desi}.

\subsubsection{\Gls{GWea} decides to visit \Gls{Desi}'s hut to pay her respects}
\Gls{GWea} discusses the dying out of senior witches at the latest coven meeting, and \Gls{Brevis}
alarms her with news of a nearby town opting to hire a wizard from Ankh-Morpork instead. \Gls{GWea}
wonders about having \Gls{Magrat} take on \Gls{Desi}'s territory temporarily, and decides to visit
her cottage to see if there are any valuables to be saved. \Gls{Ogg} decides to join her, intent on
pilfering anything of value she can set her sights on.

\subsubsection{\Gls{Lilith} uses reflective surfaces to surveil the area for some object}
The hunter who covers up \Gls{Desi}'s corpse finds an envelope inside her hut, threatening him with
a mysterious hunting accident unless he delivers the package next to him to the right address. He is
afraid of the witch's power from beyond the grave, and takes the package with him. Meanwhile,
\Gls{Lilith} uses her power of surveillance through mirror surfaces, to search for some object that
\Gls{Desi} kept from her, and wonders if the young witch \Gls{Magrat} has been given custody of it.

\subsubsection{\Gls{GWea} and \Gls{Ogg} search \Gls{Desi}'s house for her artifact}
\Gls{GWea} and \Gls{Ogg} arrive at \Gls{Desi}'s cottage, and try to make a show of not having any
interest in the fairy godmother's artifact. When \Gls{GWea} accidentally takes a look in the mirror,
she sees \Gls{Lilith} staring back at her, and smashes it in a rare show of anger. Meanwhile,
\Gls{Magrat} thinks about her new self-defense classes as she considers the journey to
self-discovery, and wonders what distant lands she might have to go to in search of it.

\subsubsection{\Gls{Magrat} receives \Gls{Desi}'s magic wand as an inheritance}
\Gls{Magrat} receives a parcel from the hunter, containing a slim wand made of white wood, and a
letter asking her to go to Genua and stop the marriage of \Gls{EllaS} with the prince. \Gls{GWea}
passes off the shattering of the mirror as an accident, and \Gls{Ogg} wisely decides not to pry.
A while later, \Gls{Magrat} walks in with \Gls{Desi}'s magic wand, leaving \Gls{GWea} appalled that
\Gls{Desi} chose her as the next wand-bearer.

\subsubsection{\Gls{GWea} and \Gls{Ogg} fall for \Gls{Desi}'s reverse psychology}
\Gls{GWea} reads the note left by \Gls{Desi}, and blatantly ignores the postscript asking
\Gls{Magrat} not to involve the senior witches in her mission to Genua. \Gls{Magrat} is forced to
play along with \Gls{GWea} in an attempt to keep hold of the magic wand, and \Gls{Ogg} is happy to
set off the next day. \Gls{GWea} gets home, and immediately buries her only mirror underground, in
order to avoid \Gls{Lilith}'s spying.

\subsubsection{The three witches prepare to leave for Genua}
\Gls{Jason} receives instructions from \Gls{Ogg} about caring for her cottage in her absence, as
the town of Lancre gathers around to see the witches depart. \Gls{GWea} tries to nitpick \Gls{Ogg}'s
dress, and is forced to comply when \Gls{Magrat} offers an excuse about the wild fashion trends in
foreign kingdoms. \Gls{Ogg} decides to take \Gls{Greebo} along, believing him to be too attached
to her to be left behind.

\subsubsection{The three witches run into a dwarf mine with some trapped miners}
On their way to Genua, the witches decide to follow \Gls{Desi}'s maps, and land their broomsticks
on a remote dwarf outpost high in the mountains. The leader of the outpost welcomes them in once
he learns that they are witches, and can help him with a caved-in mineshaft. She asks him to order
the disaster site to be emptied, while noting how little he cares about the trapped miners, when
compared to the loss of valuable ore.

\subsubsection{\Gls{Magrat} turns the loose rocks in the mine into pumpkins}
\Gls{Magrat} manages to turn the rocks blocking off the mining shaft into pumpkins, and the miners
are soon able to dig a hole back to the main hall of the mine. The leader asks \Gls{GWea} if how
far their powers of transmutation go, and she quickly replies that they can only do pumpkins.
\Gls{Magrat} is confused by the wand's magic, given that she thought very hard to put pumpkins out
of her mind when waving it.

\subsubsection{The witches are given a boat to take them to Genua}
The leader of the dwarf mine arranges for a small boat that will take the witches to Genua, using
the underground river flowing beneath the mountains. \Gls{Magrat} realizes she will have to do all
the rowing, but is reassured by the fact that they are going downriver. \Gls{Ogg} takes out the food
packed by the dwarves, and finds several discs of traditional dwarf bread, just as a strange
creature tries to catch up to them and board their boat.

\subsubsection{\Gls{Lilith} watches \Gls{Magrat} turn the boat into a pumpkin}
Once the boat reaches the open skies, and starts to approach a waterfall, \Gls{Magrat} decides to
use her wand again. She ends up morphing the boat into a pumpkin, as \Gls{Ogg} grabs \Gls{Greebo}
and escape on her broomstick. Meanwhile, \Gls{Lilith} spies on the three witches, and wonders why
\Gls{Desi} has entrusted the wand to someone as inept as \Gls{Magrat}.

\subsubsection{\Gls{Lilith} calms down her prince charming, the \Gls{Duc}}
\Gls{Lilith} thinks about the convenient alternative to borrowing magic from other sources that the
infinite mirror images are able to give her. The \Gls{Duc}, whose manor she is currently
occupying, asks her how much longer he will need to wait for his story to end with a kiss from
\Gls{EllaS}. She reassures him that things are proceeding as mandated by the story, and tells him
not to worry about the swamp witch \Gls{Gogol}, or the three witches who are on their way with
\Gls{Desi}'s wand.

\subsubsection{The three witches manage to fly over the waterfall, without any injuries}
\Gls{Lilith} thinks about the illusion that had elevated the \Gls{Duc} from a poor street urchin
to aristocracy, and hopes that the spell will remain undetectable for just a while longer.
Meanwhile, \Gls{Magrat} manages to rescue most of their belongings from the river, as \Gls{Ogg}
saves \Gls{GWea} using her own broomstick. They make camp to recover for the night, and set off
into the dark forests ahead.

\subsubsection{\Gls{Magrat} is surprised to receive special treatment at a small town's inn}
The three witches decide not to fly over the forest at night, and land at a small town by sunset.
They enter the town's only tavern, filled with silent people watching them intently out of sheer
novelty. \Gls{Magrat} is surprised to see a woman pat her on the back out of pity, as the landlord
leads them to their rooms for the night. She is further alarmed to get one of the two rooms for
herself, and recalls the garlic hanging on every doorway of the inn.

\subsubsection{A bat tries and fails to get into the witches' rooms at night}
At night, a bat trying to get into the witches' rooms is annoyed by its failure, and thinks about
returning to the castle nearby before dawn. \Gls{Greebo} steps on it to stop it from morphing into
some other form, and decides to use it as entertainment for the night. Meanwhile, \Gls{Lilith}
supervises the trial of yet another old citizen who is refusing to adopt her new guidelines for
life in Genua.

\subsubsection{\Gls{Pleas} tells \Gls{Gogol} about the latest round of punishments at the palace}
\Gls{Lilith} orders the offender to be taken to the refurnished dungeons beneath the castle for
reprogramming. Mes. \Gls{Pleas}, a cook working her role in the town as per \Gls{Lilith}'s strict
behavioural rules, reports the latest imprisonment to \Gls{Gogol}, who has her stall set up in
the marketplace.

\subsubsection{\Gls{Gogol} asks \Gls{Pleas} for the latest news on \Gls{EllaS}}
\Gls{Gogol} uses her third eye to see the arrival of three women to Genua, and tells \Gls{Pleas}
that they will make contact with her first. She asks after \Gls{EllaS}, and learns that the little
girl is being kept under house arrest by her sisters. Meanwhile, \Gls{Magrat} sees a strange dream,
where a face resembling \Gls{GWea} smiles at her from a mirror's surface, before vanishing a moment
later. She wakes up a few hours later to see a band outside the tavern, seemingly celebrating some
happy occasion.

\subsubsection{\Gls{Greebo} inadvertently saves the small town from the local vampire}
\Gls{Magrat} wakes up the other two witches, telling them that the townsfolk have a huge bonfire
going, and are burning some garlic as a part of some ritual. The witches wrongly believe that they
are celebrating the death of some rich landlord, as a fancy banquet is laid out for them.
\Gls{Greebo}, who ate the vampire from the nearby castle in his bat form, faces slight indigestion,
and is otherwise fine.

\subsubsection{The witches make their way through the foreign kingdoms on the way to Genua}
The three witches discuss the idea of turning a huge tree into a commercial airliner, by scaling up
the magic used in their broomsticks. Some days later, \Gls{Ogg} manages to lead the witches from
one rest stop to another using her half-baked vocabulary. The innkeepers are all happy to help
them with food and rooms when they see the bag of coins presented by \Gls{GWea}. Eventually, they
reach warmer climates, and accidentally end the bull run festival in a local village by staring
down the charging bulls.

\subsubsection{\Gls{GWea} tries to make sense of \Gls{Desi}'s notes on \Gls{Lilith} and Genua}
A few days later, \Gls{GWea} reads one of \Gls{Desi}'s travel diaries on Genua, where she mentions
that the old Baron has been killed, and that his lover is a swamp witch trying to fight back against
the new ruler. She also mentions that the best time to seize power is the grand carnival, when chaos
is most likely to rule the city's streets. On a troll-powered cruise ship, \Gls{Ogg} loses most of
the money in a gambling con, and is appalled when \Gls{GWea} intends to win it back using magic.

\subsubsection{\Gls{GWea} puts her plan to swindle the card sharks into action}
\Gls{GWea} puts on a show of being a frail old woman at the cruise ship's bar, and gets the con-men
to rope her into their game. \Gls{Ogg} and \Gls{Magrat} go to the bar to stop the use of magic in
the card game, believing that it will the wrong kind of divine attention. \Gls{GWea} goes through
the charade of winning the first few games, as the con-men led by \Gls{Frank} give her winning
hands.

\subsubsection{\Gls{GWea} successfully wins back all of \Gls{Ogg}'s lost cash from \Gls{Frank}}
\Gls{Ogg} and \Gls{Magrat} watch from the main deck as a large crowd gathers around the card table,
with \Gls{GWea} systematically winning every big hand. \Gls{Frank} eventually goes all in when he
sees a winning hand, only to be defeated by an obscure rule that requires an even bigger stroke of
luck for \Gls{GWea}. She swiftly returns to the living quarters with her winnings, and tells
\Gls{Magrat} that \Gls{Dissmass} taught her how to play without using any magic.

\subsubsection{\Gls{GWea} and \Gls{Ogg} save a castle from a curse of eternal sleep}
The three witches hastily leave the cruise ship by broomstick, and fly over a strange castle, choked
with overgrown vegetation. Once \Gls{Ogg} breaks a window pane to get inside, she warns the others
that everyone inside the castle looks asleep, seemingly for a long time. \Gls{Ogg} destroys the
spinning wheel next to a sleeping princess, who then wakes up bleary-eyed. \Gls{Magrat} is intrigued
when the princess seems to recognize \Gls{GWea}, and asks her why she is still there.

\subsection{}
\subsubsection{\Gls{GWea} is mistaken for someone else by the people in the sleeping castle}
\Gls{Ogg} and \Gls{GWea} talk about stories repeating themselves all over the Disc, and claim that
they have come across similar sleeping castles in the past, or at least heard of it second-hand.
\Gls{Magrat}'s attempts to solve the issue with her magic wand are rebuffed immediately, and some
guards start to string their bows after recognizing \Gls{GWea}. The three witches get away on their
broomsticks, and \Gls{Magrat} remains curious about why \Gls{GWea} seemed so familiar to the people
in the sleeping castle.

\subsubsection{\Gls{Ogg} and \Gls{GWea} decide to interfere in a Red Riding Hood story that is in
    progress}
As they walk through a forest, the three witches run into a little girl in a red cloak, taking some
goodies to her ailing grandma. \Gls{Magrat} tells the girl that the three of them are fairies, as
\Gls{Ogg} recalls a previous occurrence of the Little Red Riding Hood story where the grandmother's
body was never found. \Gls{Ogg} and \Gls{GWea} decide to leave \Gls{Magrat} with the little girl,
and go see the wicked wolf who is likely waiting in the grandmother's cottage.

\subsubsection{\Gls{GWea} and \Gls{Ogg} knock out the wolf that is supposed to eat the grandma}
\Gls{GWea} and \Gls{Ogg} enter the grandmother's cottage, after introducing themselves as fairies
who are ready to clean her house in exchange for some food. They see the bed where the grandma is
supposed to be asleep, and tell her to hide in the attic instead. When the wolf arrives on cue to
kill the grandma, \Gls{GWea} lets it in, and knocks it out with a frying pan, as it tries to eat
\Gls{Ogg}, who is lying in bed wearing the grandma's clothes.

\subsubsection{\Gls{GWea} examines the mind of the big bad wolf, and finds that it is trying to be
    human}
\Gls{GWea} decides to examine the wolf's mind, after noting that it is heavily malnourished, and on
the verge of starvation. She notices the wolf's mind going mad in the attempt to mimic human
activity, going against every instinct it originally has as a wild animal that avoids civilization.
She has one of the local woodcutters put the wolf out of its misery, and is surprised to see it
willingly lie down with its neck exposed, wishing to be killed.

\subsubsection{\Gls{GWea} refuses to elaborate when asked about the semi-sentient animals}
\Gls{GWea} threatens the villagers with violence, unless they build a new hut for the grandma, and
include her in their village. On their way out of the village, \Gls{Magrat} is dissatisfied with
\Gls{GWea}'s vague answers about the half-sentient animals being spotted in the surrounding forests.
\Gls{GWea} suspects that someone else has been using them as practice for some grand plan, that she
expects to see in Genua.

\subsubsection{A farmhouse falls down from the sky on \Gls{Ogg}'s head}
Eventually, the three witches reach a yellow brick road leading to Genua, as \Gls{Magrat} gets into
a row with \Gls{GWea} over her refusal to use magic when solving problems. All of a sudden, a
farmhouse drops on \Gls{Ogg}'s head, and the other two witches fear for her life. They find her
inside the house, protected by her armoured hat, which made a large hole in the floor as the house
fell.

\subsubsection{\Gls{GWea} convinces the dwarves to come into the farmhouse for some dwarf bread}
\Gls{Magrat} notices a group of singing dwarfs come to the back door, and ask her if the house
that landed on the witch killed her. \Gls{Magrat} says that \Gls{Ogg} is only concussed, and is
surprised when they ask for her red boots. \Gls{GWea} confronts them, and realizes that they are
trapped in some confused fairy tale that compels them to steal the boots off a witch after the
house lands on her. She entices them using the untouched dwarf bread \Gls{Magrat} has been
carrying all this while, and asks them to come in for some questioning.

\subsubsection{\Gls{Lilith} asks \Gls{EllaS}'s sisters to keep an eye on the coming guests}
\Gls{Lilith} is annoyed when the farmhouse does not kill the witches, in violation of the story's
happy endings. She talks to \Gls{EllaS}'s sisters, and tells them to let the witches meet her when
they get to Genua. She promises to return their voices to them as an incentive if they play their
part in the \Gls{EllaS}'s story faithfully.

\subsubsection{\Gls{Magrat} manages to get the witches into Genua by pretending to be cleaners}
The three witches reach the outskirts of Genua, and get trapped in a swamp when they mistake the
algae for grass. A while later, they fly to the road leading up to the main gate, and find
themselves at the back of a long queue. At the gates, the guards deny them entry for being too
dirty, until \Gls{Magrat} tells them they are cleaning staff, and points to the broomsticks. The
guards summon their captain, who is convinced by the story, even as \Gls{GWea} barely holds back her
anger at being mistaken for a commoner.

\subsubsection{The witches struggle to find an inn for the night}
The witches find no luck with accommodations, with the grand carnival bringing a huge tourist
population into the city. \Gls{GWea} is alarmed by the citizens not knowing about the idea of
witches, as \Gls{Ogg} bullies a bartender into making drinks for the three of them. \Gls{GWea}
remains angry at \Gls{Magrat}, and tags along when they find an empty stable for the night.

\subsubsection{\Gls{Magrat} decides to put the wand to good use}
At dawn, \Gls{Magrat} sneaks out of the stable wearing one of her fancy gowns, hoping to help the
kingdom using the power of \Gls{Desi}'s magic wand. \Gls{Ogg} sees her leave, and asks \Gls{GWea}
to follow along in the belief that she will get herself into trouble inevitably. \Gls{Magrat} comes
very close to understanding that \Gls{Desi} had asked her not to involve the other two witches only
as a trick of reverse psychology.

\subsubsection{\Gls{GWea} watches the justice system of Genua at work}
\Gls{Magrat} goes to \Gls{EllaS}'s house per the descriptions in \Gls{Desi}'s notes, only to find it
deserted. Meanwhile, \Gls{Ogg} sneaks into the castle disguised as a cleaning lady, and heads to the
underground brewery in the hopes of getting a drink. \Gls{GWea} finds a thief being decapitated for
his crimes in a public event, and realizes that the witches in Genua are in charge of running the
place. She also spots two animals enchanted to look like humans, when she scans the minds of the
crowd at the public execution.

\subsubsection{\Gls{Pleas} makes contact with \Gls{Ogg}, and takes her to see \Gls{Gogol}}
\Gls{EllaS} greets \Gls{Magrat} at her home's back door, and is surprised that her fairy godmother
has shown up without any jingling bells or fairy dust. Meanwhile, \Gls{GWea} follows the polymorphed
humans as they get into a carriage, and proceed to \Gls{EllaS}'s house. She notices the dilapidated
state of the house, and realizes that all this is part of some story in progress. In the palace
kitchens, \Gls{Pleas} spots \Gls{Ogg}, and engages her in some small talk, before taking her along
to \Gls{Gogol}'s hut.

\subsubsection{\Gls{Ogg} finds \Gls{Gogol} after some prompting from \Gls{Pleas}}
\Gls{Ogg} makes her way to \Gls{Gogol}'s tent, once she realizes that \Gls{Pleas} has run away in
fear of being spotted by the city guards. She takes a bowl of \Gls{Gogol}'s soup, and congratulates
her on the taste. \Gls{Gogol} calls herself a voodoo witch, and talks about her own branch of magic,
as \Gls{GWea} finds them by following \Gls{Greebo}'s trail.

\subsubsection{\Gls{Magrat} tries to do \Gls{Desi}'s job without raising \Gls{EllaS}'s suspicions}
A while later, \Gls{Gogol} leads \Gls{Ogg} and \Gls{GWea} to her home, which is a cottage in a
swamp infested with alligators, who seem to have a symbiotic relationship with the voodoo witch.
Meanwhile, \Gls{EllaS} talks about \Gls{Lilith} coming by to tell her that her destiny was to marry
the \Gls{Duc}, regardless of how repulsive she found him. \Gls{Magrat} tries to play along with
\Gls{EllaS}'s idea that she is \Gls{Desi} in disguise, and tries to avoid looking ignorant about her
role as fairy godmother.

\subsubsection{\Gls{GWea} and \Gls{Ogg} are introduced to \Gls{Gogol}'s zombie \Gls{Satur}}
Inside \Gls{Gogol}'s cottage, \Gls{GWea} overcomes her disgust with \Gls{Satur}, once she sees that
he has some unfinished business that compels him to come back to life as a zombie, animated by
\Gls{Gogol}'s voodoo. \Gls{Greebo}'s attempts to scare \Gls{Gogol}'s pet cockerel \Gls{Legba} fail
miserably, when it hops onto a scarecrow with a jacket and tophat on, and stares back defiantly at
the cat.

\subsubsection{\Gls{Gogol} narrates the story of the \Gls{Duc} taking over the city}
\Gls{Gogol} states that the old ruler of Genua had been popular before he was poisoned, with the
\Gls{Duc} mysteriously turning up at the palace with a hastily written will making him the heir.
\Gls{GWea} correctly guesses that the old ruler must have had a daughter who is now being kept under
house arrest, and will be forced to marry the \Gls{Duc} to secure his claim to power. She then
explains that the \Gls{Duc} is being protected by powerful magic that she cannot defeat by herself.

\subsection{}
\subsubsection{\Gls{GWea} admits that \Gls{Lilith} is her sister}
\Gls{GWea} grows angry at the mention of the evil witch who is controlling the \Gls{Duc}, and is
ultimately responsible for the state of Genua. When \Gls{Ogg} persists, \Gls{GWea} is forced to
admit that \Gls{Lilith} is her sister, and that the mirrors are how she spies on the world outside
the palace. When a alligator eats \Gls{GWea}'s hat, \Gls{Gogol} offers one of her own reserve hats
as a replacement.

\subsubsection{\Gls{EllaS} talks about her life as a prisoner in the manor}
\Gls{EllaS} describes the two mute sisters who keep watch on her, and the idea that the chores are
meant to encourage her to marry the \Gls{Duc} out of frustration. \Gls{Magrat} tries feebly to talk
about emancipation, and is dismayed to learn that the wedding is progressing as per \Gls{Lilith}'s
plans.

\subsubsection{\Gls{GWea} reveals the truth about her sister \Gls{LilyW}}
\Gls{GWea} talks about her childhood, and of how her sister \Gls{LilyW} had been kicked out for
using magic to entrap young boys. \Gls{Ogg} believes that she would have adopted a false name when
she came to Genua, and realizes that the long-refined mirror magic is the source of \Gls{Lilith}'s
power.

\subsubsection{\Gls{GWea} talks about her sister's motive in taking control of Genua}
\Gls{GWea} and \Gls{Ogg} rescue \Gls{Magrat} when the two morphed sisters corner her inside
\Gls{EllaS}'s house. \Gls{GWea} reveals that they are snakes, charmed by \Gls{LilyW} using the
mirrors that amplify magic, to appear as humans. \Gls{GWea} claims that \Gls{Lilith} is allowing
stories to exist in Genua by feeding its people to them, and gaining power as a side-effect.

\subsubsection{The witches put their plan into action on the night of the grand carnival}
As the first of the processions get underway on carnival night, \Gls{Ogg} goes to the city watch's
mess hall, and tempts them with some strong alcohol before they get on with the night shift.
\Gls{Magrat} uses her broomstick to fly up to the high window in \Gls{EllaS}'s house, and breaks
into the room holding her wedding dress. \Gls{Gogol} gets ready to fulfil her part of the plan,
and reminds \Gls{Satur} that his undeath will come to an end, even if they succeed in putting
\Gls{EllaS} on the throne.

\subsubsection{The three witches sabotage \Gls{Lilith}'s preparations for the ball}
\Gls{Magrat} stares at the dress, which reminds her of dreams featuring princes and royal balls. She
starts to cut up the dress, ostensibly to ruin \Gls{Lilith}'s plans for \Gls{EllaS}'s grand wedding.
\Gls{GWea} deals with the horses in the shed, as \Gls{Magrat} turns the ceremonial coach into a
pumpkin. \Gls{Ogg} gets the soldiers to pass out drunk, by supplying them with strong alcohol, and
is relieved that every part of \Gls{Lilith}'s stoy for the grand ball has been dealt with.

\subsubsection{\Gls{Lilith} watches the three witches fall right into her trap}
\Gls{Lilith} observes the witches performing their sabotage, and takes out the second magic wand,
in an attempt to undo their damage. The three witches watch the parade wind its way around the
inner city, as \Gls{Lilith} goes to \Gls{EllaS}'s house to get some assemble some mice for her
spell.

\subsubsection{\Gls{GWea} sets \Gls{Greebo} to work by morphing it into a man}
\Gls{GWea} comes to the realization that \Gls{Lilith} must have a magic wand of her own, when
\Gls{Magrat} recalls \Gls{EllaS} talking about two fairy godmothers. They spot the gleaming carriage
making its way through the streets with \Gls{EllaS} inside, and decide to waylay it using their
broomsticks. \Gls{GWea} morphs \Gls{Greebo} into a strong man, with \Gls{Ogg} confident that it is
smart enough to understand their instructions.

\subsubsection{\Gls{Magrat} is made to take \Gls{EllaS}'s place at the royal ball, in order to
    avoid raising \Gls{Lilith}'s alarm}
\Gls{GWea} asks \Gls{Greebo} to stop the white carriage, and the cat is able to intimidate the
coachmen and horses by sensing that they are morphed mice. \Gls{EllaS} is rescued by \Gls{Magrat},
just as \Gls{Legba} lands nearby with some sort of message from \Gls{Gogol}. \Gls{GWea} confers with
it out of earshot of the other witches, and tells \Gls{Magrat} that she is going to take
\Gls{EllaS}'s place at the ball.

\subsubsection{\Gls{Magrat} enters the palace courtyard where the ball is to take place}
\Gls{Magrat} is made to wear \Gls{EllaS}'s dress and mask, with \Gls{GWea} changing the color of
her hair to match. At the palace, \Gls{Magrat} makes a show of arrogance and self-assuredness that
gets her entry into the palace, with the other two witches flying to the top on their broomsticks.
Meanwhile, \Gls{Magrat} is introduced by the butler as a mysterious stranger, as she steps into the
courtyard where the ball is to take place. She is followed shortly by \Gls{Death}, and then by
\Gls{Greebo} wearing a cat mask.

\subsubsection{\Gls{Ogg} and \Gls{GWea} discover the \Gls{Duc}'s secret identity in his bedroom}
\Gls{Ogg} and \Gls{GWea} land on a tower, and climb down some stairs into the royal bedroom. They
notice flies swarming the room, and see a trapdoor covering up something horrific. They exit the
room and knock out one two of the aristocratic guests in order to steal their outfits for the ball.
\Gls{Ogg} is concerned that the power of the story might make \Gls{Magrat} fall in love with the
\Gls{Duc} if they were to kiss at the ball.

\subsubsection{\Gls{Ogg} and \Gls{GWea} try to remain undercover at the ball}
\Gls{Ogg} and \Gls{GWea} make their way to the buffet spread at the courtyard, while noticing that
\Gls{Magrat} is sitting alone next to some plants. \Gls{Ogg} complements \Gls{GWea} on her ability
to hypnotize \Gls{Magrat} into thinking she is a pretty princess capable of attracting the attention
of any prince at the ball. \Gls{GWea} goes off to dance with some military man, to keep up
appearances, while \Gls{Casan} greets \Gls{Ogg}.

\subsubsection{The \Gls{Duc} arrives at the ball with \Gls{Lilith} by his side}
A horn is blown to signal the arrival of the \Gls{Duc}, and \Gls{Ogg} immediately sees the family
resemblance in \Gls{Lilith}'s face. The \Gls{Duc} proceeds to the opposite end of the courtyard,
where \Gls{Magrat} is waiting for him, surrounded by other aristocrats trying to charm her.
\Gls{GWea} is worried that she will not be able to interrupt the story, as \Gls{Casan} asks
\Gls{Ogg} for a dance with \Gls{GWea}.

\subsubsection{\Gls{Magrat} runs out of the ball, and leaves one of her glass slippers behind}
\Gls{Ogg} goes to the clock's mechanism room high up above the courtyard, and gets \Gls{Casan} to
pull out one of the gears. The clock speeds up greatly, and the gongs that signal midnight start
to go off many hours ahead of schedule. The clock striking midnight ends \Gls{GWea}'s hypnosis,
allowing \Gls{Magrat} to see the fact that the \Gls{Duc} is a morphed animal. She runs out of the
palace, with \Gls{GWea} taking the opportunity to derail the story by smashing the glass slipper to
bits before the \Gls{Duc} can pick it up.

\subsubsection{\Gls{Magrat} attempt to escape the palace is ruined by the snake sisters}
With a group of followers from Genua's underclass assembled in her cottage, \Gls{Gogol} fuels a
ritual that brings power into the body of \Gls{Satur}, who happens to be the former ruler of the
city. The two snake sisters apprehend \Gls{Magrat} and bring her back to the courtyard, where
\Gls{Lilith} asks the \Gls{Duc} to check her other slipper.

\subsubsection{The \Gls{Duc} turns out to be a frog morphed into human form by \Gls{Lilith}}
\Gls{Ogg} comes up to the \Gls{Duc} and tells him to try the glass slipper on her feet, when
\Gls{Lilith} points out the need to scour the city for the original owner of the slippers. She
realizes that \Gls{GWea} is trying to interfere with the story, as \Gls{Magrat} works out the truth
that the \Gls{Duc} is a frog morphed into human form by \Gls{Lilith}'s magic.

\subsection{}
\subsubsection{\Gls{EllaS} is taken to \Gls{Gogol}'s cottage for safekeeping}
\Gls{Lilith} refuses to listen to \Gls{GWea}'s accusations, and imprisons the three of them. She
intends to go through with her plan of marrying \Gls{EllaS} to the \Gls{Duc}, thereby sealing the
spell that turns him into a man for half the day. Meanwhile, \Gls{EllaS} is led by \Gls{Legba} to
the swamp, where \Gls{Gogol} welcomes her into the cottage. She commands the cottage to rise on
its four legs, and move to the river for safety.

\subsubsection{\Gls{Greebo} and \Gls{Satur} help the three witches escape their prison cell}
The three witches are imprisoned in a high tower with magic-immune locks, and watch \Gls{Casan}
patrol the corridor outside their cell. He claims to have joined the palace guard, and reminds them
that the palace is heavily fortified to prevent their escape. A while later, \Gls{Legba} lands on
the cell's window, shortly followed by \Gls{Satur} tearing a hole in the brick wall. The three
witches are stopped by some guards, but notice \Gls{Greebo} sneaking in from behind to help them.

\subsubsection{\Gls{Satur} kills the \Gls{Duc} when \Gls{Lilith} forces him back to his animal form}
\Gls{Lilith} tries desperately to hurl magic at \Gls{Satur}, when he disrupts the ball, and shrugs
off the crossbow bolts fired at him. She vacuums all the magic around her, turning \Gls{Greebo} and
the \Gls{Duc} back to their animal forms, with \Gls{Satur} quickly squashing the frog under his
heavy boots.

\subsubsection{\Gls{GWea} shows off her power to \Gls{Gogol}, and goes to deal with \Gls{Lilith}}
\Gls{Gogol} turns up to try and take \Gls{Lilith}'s place as the de-facto ruler of the city, only
for \Gls{GWea} to object to her plan. \Gls{Gogol} challenges \Gls{GWea} to a fight, and insists on
taking care of \Gls{Lilith} using her own voodoo methods. When \Gls{Gogol} uses her voodoo doll to
hurt \Gls{GWea}, she reverses the link, and burns the doll by placing her hand over a torch, all
while remaining unharmed herself.

\subsubsection{\Gls{Magrat} and \Gls{Ogg} decide to help \Gls{GWea}}
\Gls{Magrat} convinces \Gls{Ogg} to go up to the tower in order to back up \Gls{GWea}. \Gls{Ogg}
remains confident that \Gls{GWea} can deal with \Gls{Lilith} on her own, but goes along regardless.
Meanwhile, \Gls{EllaS} ends the ball in her first act as ruler of the city, and drags off the
attendees to the carnival, which is still in progress outside the wealthy inner district.

\subsubsection{\Gls{Satur} goes to the afterlife, having fulfilled his mission}
\Gls{Death} reaps \Gls{Satur}'s soul, and puts an end to his undeath. \Gls{Gogol} asks him not to
reveal the fact that they are \Gls{EllaS}'s real parents, and returns to the swamp. \Gls{Magrat}
knocks out the snake sisters, when her fight-or-flight instincts finally force her to put her
self-defense into practice.

\subsubsection{\Gls{GWea} jumps off the tower as if avoiding the confrontation with \Gls{Lilith}}
\Gls{GWea} asks \Gls{Lilith} to leave the godmothering behind, and return home, only for
\Gls{Lilith} to laugh at her feeble request. \Gls{GWea} then tries to remind \Gls{Lilith} that
turning the world into stories carries the drawback of having those stories end. \Gls{GWea} jumps
off the tower with her broom, after making a show of admitting her defeat and pleading for the lives
of her fellow witches. \Gls{Lilith} remains confident that \Gls{GWea} is deceiving her, but allows
them to run to help her.

\subsubsection{\Gls{Ogg} and \Gls{Magrat} run down to the ground to help \Gls{GWea}}
\Gls{Ogg} and \Gls{Magrat} spot \Gls{Death} walking up the spiral staircase to \Gls{LilyW}'s tower,
and speed up their descent. \Gls{GWea} flies into \Gls{LilyW}'s room, and breaks one of the two
mirrors in her hall. \Gls{LilyW}'s reflections reach out into the real world, and drag her into
their won dimension, where \Gls{Death} tells her that she is trapped forever between life and
death.

\subsubsection{\Gls{GWea} falls into the same trap as \Gls{Lilith}, but finds a way out}
\Gls{GWea}'s comatose body is taken to \Gls{Gogol}'s hut, so that her bloodied hands can be
bandaged up after removing the glass shards. \Gls{Ogg} recalls seeing all the mirrors in
\Gls{LilyW}'s hall explode into tiny shards, and wonders if \Gls{GWea} is stuck in some mental
prison. Meanwhile, \Gls{Death} asks \Gls{GWea} the same question as \Gls{Lilith}, but she is able to
immediately look down at herself and identify it as the real one, thus earning her way out of the
prison.

\subsubsection{The three witches leave Genua after getting rid of \Gls{Desi}'s magic wand}
\Gls{Magrat} disposes of the magic wand in the Genua river, and the three witches return home,
after \Gls{Ogg} makes sure that \Gls{GWea} has fully returned to her senses after the ordeal in the
mirror dimension.