\section{Wyrd Sisters}


\subsection{}
\subsubsection{\Gls{GWea} and \Gls{Ogg} hold their regular meeting with \Gls{Magrat}}
On a stormy night in the Ramtop Mountains, a group of three witches talk over tea and snacks, with
\Gls{Ogg} and \Gls{GWea} congratulating \Gls{Magrat} on her performative screeching voice. A coach
rides through a forest road in the mountains, desperately trying to outpace some hooded horsemen
trying to shoot at the occupants.

\subsubsection{\Gls{Verence} realizes that he is trapped as a ghost and cannot pass on to the
    afterlife}
King \Gls{Verence} wakes up in spirit form after being stabbed in the back, and looks at the
courtiers hurrying to inspect the scene of the crime. He recognizes Lord \Gls{Felmet} smirking in
the background, and realizes he must have sent the assassin, as \Gls{Death} appears to reap the
king's soul in person. \Gls{Death} takes a second look at the King's hourglass and realizes that he
still has unfulfilled business in the Disc, and has to be a ghost haunting the palace for a while.

\subsubsection{\Gls{Verence} notices his child being taken away from the palace}
\Gls{Death} leaves without answering any of \Gls{Verence}'s questions about his life as a ghost,
and the king walks through the walls of the palace to the nursery. He notices the baby missing from
its cradle, and tries to follow the carriage rushing out of the palace yard. Another ghostly voice
tells him that he cannot wander far from his place of death, as he finds it impossible to follow the
carriage out of the palace.

\subsubsection{\Gls{GWea} confronts the three soldiers chasing down the baby}
The three witches watch a man bearing a sleeping toddler in his hands run into their hut, and die
shortly after with crossbow bolts sticking out of his back. \Gls{GWea} kills the lead soldier
chasing the baby, after rejecting his demand to stand aside, and asks one of the underlings to flee
to foreign lands. The third soldier escapes to report back to his master, with \Gls{GWea} deeming
it unnecessary to hunt him down.

\subsubsection{\Gls{Verence} meets the ancient King \Gls{Champot}, who also haunts the castle}
\Gls{GWea} notices the same badge on the uniforms of the carriage driver as well as the guard
captain who shot him dead. \Gls{Magrat} finds a crown in the carriage, and realizes that the child
is the heir of \Gls{Verence}, King of Lancre. Meanwhile, \Gls{Verence} is greeted by the other
ghost, who introduces himself as King \Gls{Champot}, who built the Lancre castle a thousand years
ago and was murdered by his nephew in a power-grab.

\subsubsection{\Gls{Felmet} and his wife argue about the loose ends in their coup}
\Gls{Felmet} surveys the forest surrounding the palace, as his wife \Gls{LFel} complains about how
much better their old residence in rural Lancre had been. He thinks about the systematic culling of
\Gls{Verence}'s loyal bodyguards, as well as court physicians unwilling to rule his that his death
had been natural. \Gls{Felmet} wonders where the crown has been hidden, and looks out over the
tall cliff to the Lancre river running below, as his wife berates him for letting the heir escape.

\subsubsection{\Gls{Ogg} and \Gls{GWea} discuss the safety of the heir to Lancre}
As the head cook of the palace is busy playing cards with the \Gls{Fool}, the returning horseman
reaches the palace, and asks to be led to \Gls{Felmet}, so that he can report on the witches he
encountered. Meanwhile, \Gls{GWea} gives in to \Gls{Ogg}'s insistence that they keep the baby and
raise it in secret. She realizes that the baby needs to be taken away somewhere far, possibly to
one of \Gls{Ogg}'s children or grandchildren.

\subsubsection{\Gls{GWea} sees the crown recount its history when she tries it on}
\Gls{GWea} tries on the crown, as \Gls{Ogg} takes the baby into \Gls{Magrat}'s kitchen for a wash.
She feels the lives of all the Kings of Lancre flash across her mind, as the crown plays a flashback
of its entire existence over the centuries. \Gls{GWea} takes it off in a hurry, as \Gls{Magrat}
comments on a subconscious need to try on the crown.

\subsubsection{\Gls{Magrat} mentions the traveling theater troupe to \Gls{GWea}}
\Gls{Magrat} talks about the plays that \Gls{Whemper} used to drag her to in the towns, and of how
the prop crowns looked much more ostentatious and flashy than the real thing. \Gls{GWea} realizes
that a traveling theater troupe might be the best place to hide the heir, and asks \Gls{Ogg} to
get ready to leave for the town.

\subsubsection{\Gls{GWea} watches her first theater play}
At the theater, \Gls{GWea} makes a huge commotion, unaware of the pretend nature of the performance.
After \Gls{Magrat} explains to her that the supposed dead body is actually alive, \Gls{GWea} then
notices that the female parts are all being played by men in wigs putting on shrill voices. In the
next scene, \Gls{GWea} fails to realize that the royalty on stage are all actors, and triumphantly
gets up to point out the king's murderer, thereby ruining the climax.

\subsubsection{The three witches run into \Gls{Vitol}, the troupe manager}
After the audience leave, \Gls{GWea} pokes around the props, slowly coming to the realization that
the entire thing is make-believe. \Gls{Vitol}, the manager of the troupe who played the central role
in the play, finds them in the process of supervising the disassembling of their stage. \Gls{GWea}
manages to shake herself out of the trance of his hypnotic voice, and asks to speak to him in
private.

\subsubsection{\Gls{Felmet} plans a crackdown on the witches in Lancre, hoping to find the missing
    heir to \Gls{Verence}}
\Gls{LFel} learns from a minister that the witches are tolerated in Lancre as a valuable medical
asset to the remote village communities. \Gls{Felmet} asks if they pay taxes to the crown, and
realizes that this can be an excuse to have them rounded up. He wonders if there was a witness to
the murder of his cousin \Gls{Verence} on the dark night where he had arranged for the Great Hall
to be empty.

\subsubsection{\Gls{Ogg} and \Gls{GWea} get the \Gls{Vitol} couple to adopt the baby}
\Gls{Ogg} and \Gls{GWea} manage to convince \Gls{Vitol} and his wife to adopt the baby, and sweeten
the deal by offering them some cash for the expense of childcare. The aging childless couple are
overjoyed to receive the baby, and wisely choose not to pry about its heritage. \Gls{Ogg} simply
tells them that they are its godmothers, as \Gls{Magrat} comes into inform \Gls{GWea} that the real
crown has been buried in the prop box, amidst the other jewelry.

\subsubsection{The three witches give the baby some gifts, in the way of old folk tales}
\Gls{Magrat} suggests giving the little boy three gifts, in the tradition of witch godmothers from
the old tales. After the drunk \Gls{Ogg} is helped by \Gls{GWea} to her home, \Gls{Magrat} wishes
for the baby to make friends with ease. As she settles down to sleep, \Gls{Ogg} wishes for the baby
to have a good memory, and \Gls{GWea} for her part, wishes it grows up to fulfil its own childhood
ambitions.

\subsubsection{\Gls{Felmet} tries to make sense of the witches and their hold on the people of
    Lancre}
The men sent by \Gls{Felmet} to arrest \Gls{GWea} return empty-handed, and refuse to say anything
beyond the witch kindly offering them some tea and biscuits in her cottage. He believes that
\Gls{GWea} used her powers to show the soldiers visions of forbidden pleasure in an attempt to
brainwash them, and turns to the \Gls{Fool}, who is seated below the throne. He learns that the
\Gls{Fool}'s family are hereditary jesters in the court of Lancre, and asks him about the value of
witches to the rural people.

\subsubsection{\Gls{LFel} scolds \Gls{Felmet}'s leniency after the witches are not arrested}
\Gls{LFel} asks for the soldiers to be made an example of, and \Gls{Felmet} placates her by
pointing out how precarious their own claim on the throne is until the crown is recovered. He tries
to suppress his pain from having rubbed his hands bloody, trying to wash off the guild of stabbing
\Gls{Verence}. He also recalls the faint whispering in his dreams, always on the edge of perception.

\subsubsection{The three witches prepare for their next monthly meeting}
\Gls{GWea} flies to Lancre town on her faulty broomstick, dreading the bustling household that
\Gls{Ogg} has made for herself, with her extended family helping run the place. \Gls{Magrat} arrives
with her new pet tortoise, and is taunted for her inability to hold on to a single familiar for
too long. The two senior witches offer excuses for missing the last month's full-moon meeting, as
\Gls{Magrat} prepares the crystal ball for peering into the baby's life.

\subsubsection{\Gls{Felmet} listens to his taxman's failure to wrangle any money out of the witches}
\Gls{Felmet} hears a report from his taxman, who talks about the witches politely refusing to hear
his reasoning, and turning him away without any payment. He wonders how the people of Lancre are
able to take no notice of the change in rulership, as if one King is as good as the last, as the
\Gls{Fool} tries to entertain him with some jests. \Gls{Felmet} continues to grow paranoid about
the metaphorical blood on his hands, and continues to try and grab the people's attention with
one stunt after another.

\subsubsection{\Gls{GWea} finds something terrible growing inside her mind}
\Gls{Hwel}, the dwarf banished from his underground community for being too imaginative, gets to
work on his latest script for \Gls{Vitol}'s troupe. He fails to keep an eye on young \Gls{Tomjon},
who fishes around in the prop box filled with crowns. On Hogswatchnight that year, \Gls{GWea}
senses unrest in the forest, and performs a mental sweep of the lands to try and locate the source.
Finally, she peers into her own mind, and is appalled by what she finds.

\subsubsection{\Gls{Felmet} blames the witches for the earthquake in Lancre town}
Later in the night, \Gls{Felmet} runs out of his room as an earthquake shakes Lancre castle, asking
the \Gls{Fool} if the region has a history of tremors. He dismisses the \Gls{Fool}'s pleas and
states his suspicions that the witches are triggering the earthquake to punish him for his
intrusions.

\subsubsection{The \Gls{Fool} accidentally gives \Gls{LFel} a good idea to deal with the witches}
\Gls{LFel} asks the \Gls{Fool} to explain his idea of fighting the hegemony of the witches using
the power of rumour and propaganda. The \Gls{Fool} explains that his training at the Guild in
Ankh-Morpork has taught him that lies repeated often enough can be used to malign anyone, as
\Gls{LFel} listens with great interest. \Gls{Felmet} is annoyed by his hands continuing to bleed
in spite of the use of files and sandpaper to clean them.

\subsubsection{\Gls{GWea} and \Gls{Magrat} go to \Gls{Ogg}'s house in Lancre town}
\Gls{GWea} realizes that something inside the ground has suddenly become sentient, and rushes to the
ancient stone monument that is the usual meeting place for the coven. \Gls{Magrat} joins her there,
and the two of them decide to head to \Gls{Ogg}'s house in Lancre town, where the Hogswatchnight
party is well underway.

\subsection{}
\subsubsection{The three witches summon a demon in \Gls{Ogg}'s house for questioning}
\Gls{Ogg} listens patiently to \Gls{Magrat}'s story about a strange mind high in the mountains,
seemingly lost in search of someone. She then leaves the party, and takes the two witches to her
private storeroom to perform a demon summoning. The demon delights at its ability to provide
misleading answers to the first two questions, and is appalled when \Gls{GWea} threatens it outright
unless it explains what is going on in the mountains.

\subsubsection{\Gls{GWea} threatens the demon into providing clear answers}
The demon tells \Gls{GWea} that the land itself has awoken, angry at the absence of a king that
cares for it. \Gls{GWea} dismisses it, wondering how the very ground can suddenly become sentient,
and whether this has to do with the recent coup at Lancre Castle. \Gls{GWea} returns home, and
starts to believe that the forest is seeing thoughts in her head, when she starts to seriously
entertain the idea that the land is alive, and has a mind of its own.

\subsubsection{\Gls{GWea} addresses the animals of the forest, who assemble in front of her hut}
As the sun rises on Hogswatchday, \Gls{GWea} steps out into her garden, to find several forest
creatures assembled to stare at her, in seeming violation of the food chain. She also notices birds
staring at her from every tree surrounding her cottage, and rejects the idea of meddling with the
rulership of Lancre. She states that her policy of non-intervention in the affairs of government is
more paramount than the forest's desire for well-being.

\subsubsection{\Gls{Tomjon} utters his first words as a three year old}
\Gls{Tomjon} utters his first words at the age of three, which happen to be a rendition of
\Gls{Vitol}'s fancy monologue from one of his plays. \Gls{Hwel} runs to fetch \Gls{Vitol}, and
gathers the troupe for more demonstrations by the little boy. \Gls{Vitol} is concerned about his
son's gift being the result of some meddling by the witches, as his wife reassures him that
\Gls{Tomjon} will grow up to be a fine theater actor.

\subsubsection{\Gls{Verence} puts his plan into action by trapping \Gls{Greebo} in the castle}
\Gls{Verence} wanders his castle, taking note of the large number of ancestors haunting the halls,
and finds himself being stared at by \Gls{Greebo} in the Great Hall. He puts his plan into action,
and gets \Gls{Greebo} to follow him into an abandoned storage room. Once the cat is inside,
\Gls{Verence} uses his well-practiced ghostly power to latch the door shut, believing that the witch
who owned the cat would be forced to come investigate.

\subsubsection{\Gls{Magrat} runs into the \Gls{Fool} on a hill, and sees him run away}
Sitting concealed in some bushes on the hills next to the palace, the \Gls{Fool} recalls his
childhood before being sent to the Fools' Guild in Ankh-Morpork for training. He then hears someone
singing, and stands up to find \Gls{Magrat} plucking medicinal flowers. He is spooked by the idea of
being cursed for disturbing a witch's meditation, and runs away to the palace before she can ask
him any questions.

\subsubsection{The witches talk about dissatisfaction with \Gls{Felmet} at their monthly meeting}
At their next meeting, \Gls{Ogg} and \Gls{GWea} notice how distracted \Gls{Magrat} is, and bemoan
her carelessness when it comes to donning a proper witch's outfit. \Gls{Ogg} talks about the visit
from the mayor of Lancre, asking her to do something about the new King, and mentions the fact that
\Gls{Greebo} is missing. \Gls{GWea} explains the assembly of wild animals in her yard, and explains
that the kingdom has become sentient in the face of mistreatment by \Gls{Felmet}.

\subsubsection{\Gls{Ogg} and \Gls{GWea} disagree about \Gls{Magrat} pursuing the \Gls{Fool}}
\Gls{Magrat} mentions the \Gls{Fool} in Lancre Castle, and \Gls{Ogg} talks about his mother being
a minor noble from a nearby kingdom. \Gls{Ogg} goads \Gls{Magrat} into pursuing her interest in the
\Gls{Fool}, causing a rift between her and \Gls{GWea}, who is a staunch believer in witches
remaining celibate.

\subsubsection{\Gls{Magrat} decides to force the \Gls{Fool} to like her using \Gls{Whemper}'s magic}
\Gls{Magrat} pores over \Gls{Whemper}'s notes at her cottage, hoping to find a spell that will
reveal the \Gls{Fool}'s real name and make him fall in love with her. She then sets out at dawn to
gather ingredients for the love potion, in accordance with \Gls{Whemper}'s detailed instructions.
Meanwhile, \Gls{Ogg} follows the trail of \Gls{Greebo}'s mind to the castle, and enters it through
the servants' gate. She recognizes one of the maids as a daughter-in-law, and proceeds through the
corridor just as \Gls{Felmet} comes out of his chamber.

\subsubsection{\Gls{Magrat} learns from \Gls{Shawn} that \Gls{Ogg} has been imprisoned in the
    palace}
\Gls{Magrat} spots \Gls{Shawn}, the youngest son of \Gls{Ogg}, running through the meadows outside
Lancre town, and stops him. He tells her that \Gls{Ogg} has been imprisoned in the castle by
\Gls{Felmet}, and that he is running to the neighbouring town to get the word out to his siblings.
\Gls{Magrat} is annoyed when \Gls{Shawn} suggests bringing \Gls{GWea} to deal with the situation,
and storms off to her cottage.

\subsubsection{\Gls{Ogg} sees the ghost of King \Gls{Verence} in the dungeon}
In the palace cellars, \Gls{Ogg} remains unconcerned by the various torture implements laid out in
front of her, and \Gls{Felmet} becomes flustered by her refusal to play along. After he leaves,
\Gls{Verence} comes out of a corner, and is surprised to learn that \Gls{Ogg} cannot magic her way
out of her chains. \Gls{Ogg} hopes desperately that the other witches will come to her rescue, as
\Gls{Verence} tries to explain his revenge plan.

\subsubsection{\Gls{GWea} arrives at Lancre Castle to rescue \Gls{Ogg} from \Gls{Felmet}}
\Gls{GWea} listens to \Gls{Shawn}'s reports of lies being spread around Lancre about the witches
cursing common-folk, and decides to help out \Gls{Ogg}, if only to repatriate the image of the
witches. \Gls{Magrat} fusses over her fancy robes as she prepares to make a grand entrance at the
palace as well. As a crowd gathers in the palace's front yard, \Gls{GWea} arrives by broomstick,
and trudges past the palace guards intent on stopping the torture that is supposedly in progress.

\subsubsection{\Gls{LFel} tries to get the torture of \Gls{Ogg} started with an elaborate ritual}
\Gls{LFel} makes a show of the elaborate torture implements, as the \Gls{Fool} fails to light the
candle. \Gls{Felmet} grows annoyed, and asks him to keep watch outside the dungeon, while grabbing
the matchbox from him. The ghost of \Gls{Verence} tells \Gls{Ogg} how he died, and \Gls{Ogg}
narrates the entire incident to the horror of \Gls{Felmet}. \Gls{Verence} struggles to lift his
knife, which is on the tray of torture tools, as he thinks about stabbing \Gls{Felmet} to death as
revenge.

\subsubsection{\Gls{Magrat} enters the palace, only to be caught by \Gls{Felmet}'s guards}
\Gls{Magrat} is allowed to enter the palace with no guards willing to stop her, and wanders into the
Great Hall, unable to find entrance to the dungeon. Two of \Gls{Felmet}'s personal guard apprehend
her, intending to take her to another cell in the dungeon. The \Gls{Fool} provides a distraction,
allowing her to knock one of the men out with her metal rings, and threaten the other with her
knife.

\subsubsection{\Gls{Magrat} opens the door to the dungeon using the power of the forest}
The \Gls{Fool} is shocked when \Gls{Magrat} offhandedly calls him by his real name, and tells her
that he had been named after King \Gls{Verence} likely for good luck. \Gls{Magrat} takes no notice
of this, and focuses on opening the door to the dungeon. She decides to use the spring-time energy
in the forests, and channels the growth spurt into the wooden door. \Gls{GWea} arrives just in time
to escort the two of them to safety, as the door bursts into root and leaf, seeking to shoot up
towards the sunlight.

\subsubsection{\Gls{GWea} confronts Duke \Gls{Felmet} and asks him to flee}
The \Gls{Fool} reminds \Gls{Magrat} and \Gls{GWea} about the original rescue plan, leading them to
barge into the dungeon. They find \Gls{Felmet} and his wife cowering in a corner, and the ghost of
\Gls{Verence} trying to stab them with his knife. \Gls{GWea} gets him to stand down, stating that
the dead should not be able to kill the living. \Gls{Felmet} stands up to her, and rejects her idea
of abdicating the throne in order to save himself.

\subsubsection{\Gls{Felmet} gets the witches to back off when they ask him to abdicate}
\Gls{Felmet} reminds \Gls{GWea} that she cannot interfere in matters of state since she is bound by
the norms of witchcraft. When she reminds him of the missing heir, he tells her that he has plenty
of time to prepare for some young man with a sword to march into the castle seeking his rightful
throne. The three witches are forced to concede his point, and leave the castle in a huff.

\subsubsection{\Gls{Magrat} makes a deal with the \Gls{Fool} to meet outside the Castle}
The \Gls{Fool} gets \Gls{Magrat} to agree to a meeting by the pool a few days later, as she thinks
about \Gls{Whemper}'s instructions for courting young men. Meanwhile, \Gls{Ogg} and \Gls{GWea} think
about the sanctity of their non-intervention policy, as \Gls{LFel} summons the \Gls{Fool} back to
the dungeon. On her way out of the castle, \Gls{Ogg} picks up some rubble according to her deal with
\Gls{Verence}.

\subsubsection{\Gls{Felmet} gets the tentative rioters to go home, using \Gls{GWea}'s words of
    reassurance}
\Gls{Felmet} shows up at the front entrance to his keep, and forces the witches to smile and wave
at the gathered rioters in order to placate their anger. \Gls{GWea} tells the people to go home, and
realizes that \Gls{Felmet} is in one of his manic breaks. She storms out of the castle compound,
with the other two witches trying to see what plan she has in mind.

\subsubsection{\Gls{GWea} listens to \Gls{Verence} make his plea}
\Gls{GWea} abhors the idea of asking other witches in the region for their help, and wonders why
there is a strong culture of paranoia and suspicion among the practitioners of magic throughout the
Disc. The faint ghost of \Gls{Verence} is able to now manifest next to them using the rubble carried
out by \Gls{Ogg}, and greets \Gls{GWea}. The ghost asks them if they are going to wait some more
years for the heir to return, before vanishing.

\subsubsection{\Gls{GWea} decides not to wait around for \Gls{Tomjon} to grow up and challenge
    \Gls{Felmet} for the throne}
\Gls{GWea} almost gets run over by a carriage, and is saved at the last moment by \Gls{Magrat}, who
pulls her into a ditch. She is incensed at the loss of social standing that the witches have had to
suffer under \Gls{Felmet}'s rule, and decides not to wait for \Gls{Tomjon} to grow up. Meanwhile,
\Gls{LFel} is intrigued by the \Gls{Fool}'s idea of propaganda as a weapon, and asks him to find
a playwright who can create a play that whitewashes the murder of \Gls{Verence}.

\subsubsection{\Gls{Greebo} is rescued by the \Gls{Fool}}
\Gls{Greebo} is intrigued by the \Gls{Fool}'s friendly tone of voice when he comes to the locked
storeroom, and climbs on his back. The \Gls{Fool} promptly leaves the Castle to deliver \Gls{Greebo}
to \Gls{Ogg}'s home to make good on his deal with the witch. At the coven meeting, \Gls{Ogg}
mentions an ancient witch from Skund, who had put the entire castle to sleep for many decades when
faced with a similar problem of succession.

\subsubsection{\Gls{GWea} explains her preposterous plan to \Gls{Ogg} and \Gls{Magrat}}
\Gls{GWea} comes up with an even more outrageous plan, which involves moving the entire Kingdom
into the future, as \Gls{Ogg} listens in horror. \Gls{GWea} outlines her plan to use the forest
itself to store the vast amount of magic required for the ritual, and the three witches hurry back
to their respective homes to prepare.

\subsubsection{The \Gls{Fool} loses his way in the forest at night}
The \Gls{Fool} loses his way in the forest at dusk, as he plans to deliver \Gls{Greebo} to
\Gls{Magrat}'s cottage, hoping to impress her. \Gls{Greebo} slinks off into the undergrowth, eager
to get back to business mating with any stray cats that he might come across, leaving the \Gls{Fool}
to seek high ground in order to find his bearings.

\subsection{}
\subsubsection{\Gls{Magrat} boosts \Gls{GWea}'s broomstick using her own reserves of magic}
\Gls{Magrat} waits on her broomstick at the northern border of Lancre to help refuel \Gls{GWea}'s
broomstick midair. After draining most of her own magic into \Gls{GWea}, \Gls{Magrat} glides down
gently to the ground, where she unexpectedly makes a soft landing after running out of magic to keep
her broom afloat. She lands on the \Gls{Fool}, who gets away with only minor injuries, before asking
her to lead the way to high ground.

\subsubsection{\Gls{GWea} loses control of her broomstick high above Lancre}
\Gls{GWea} starts the second part of her journey, with \Gls{Ogg} joining her above the forests of
Lancre. As she prepares to receive another infusion of power, her broomstick suddenly loses control,
and nosedives through the clouds. Meanwhile, the \Gls{Fool} describes his strict upbringing in the
Guild at Ankh-Morpork, and asks her when she graduates from an apprentice to a witch.

\subsubsection{\Gls{Ogg} hides some information from \Gls{GWea}, who is anxious to complete her
    time travel spell}
\Gls{Ogg} rescues \Gls{GWea} by catching her in the middle of her fall, and takes her to Lancre
Bridge, secure in the knowledge that her grandchildren are in position to perform the rest of the
ritual. \Gls{GWea} is not sure what \Gls{Ogg} has in mind, and completes the rest of the incantation
once she alights on the bridge, with the Lancre Castle ahead of her on its tall cliff.

\subsubsection{\Gls{GWea} remains suspicious of \Gls{Ogg}'s meddling in her time-travel spell}
\Gls{GWea} is unsure how \Gls{Ogg} managed to influence her time travel spell, as \Gls{Verence}
congratulates her on bringing the entire kingdom of Lancre fifteen years into the future. \Gls{Ogg}
suggests looking for \Gls{Tomjon} in Ankh-Morpork, confident that he will have ended up there in
pursuit of his destiny.

\subsubsection{\Gls{Tomjon} supervises the construction of \Gls{Vitol}'s new theater building}
At the outskirts of Ankh-Morpork, \Gls{Hwel} watches the new theater being built, on the advice of
\Gls{Tomjon}. He recalls the speed with which their troupe had grown in popularity and wealth, led
by the histrionics of young \Gls{Tomjon}, and of how \Gls{Vitol} had finally been persuaded to
settle down. \Gls{Tomjon} wakes up from one of his nightmares, where he sees the three witches
looking in at him through a crystal ball. \Gls{Hwel} consoles him, while reminding him that he
should not wander out into the wilderness at night.

\subsubsection{\Gls{Tomjon} stops a bar fight with his oratory skills}
\Gls{Tomjon} decides to go out for a drink, and asks \Gls{Hwel} to accompany him. At the Mended
Drum, a bar fight breaks out when the \Gls{Libra} is called a monkey by a thug new to the city.
\Gls{Tomjon} decides to stop the bar brawl by calling for silence, and launching into one of the
soliloquies from \Gls{Hwel}'s plays.

\subsubsection{\Gls{Tomjon} stops the \Gls{Fool} being mugged in a dark alley}
\Gls{Tomjon} spots the \Gls{Fool} being mugged by some licensed thieves, and gets them to return
the substantial sum of silver coins to their victim. He then uses his powers of persuasion to get
the rest of the money they had stolen earlier from others, by way of legal fees. The \Gls{Fool} is
impressed by \Gls{Tomjon}'s charm, and wishes to treat them to some drinks. \Gls{Hwel} notices the
strong resemblance between the two boys, but thinks nothing of the fact.

\subsubsection{The \Gls{Fool} realizes that \Gls{Tomjon} is part of the traveling theater troupe}
After getting drunk in a dwarf bar, \Gls{Tomjon} performs one of his tragic speeches in a female
voice, leading the dwarfs to realize that the girl in the play they had all seen earlier was in
fact a man in makeup. The \Gls{Fool} is relieved to learn that \Gls{Hwel} and \Gls{Tomjon} are part
of the theater troupe, and tells them about \Gls{LFel}'s mission to make a propaganda play to
whitewash their legacy.

\subsubsection{\Gls{Vitol} convinces \Gls{Hwel} to take on \Gls{LFel}'s contract}
\Gls{Vitol} explains the exorbitant interest being charged by \Gls{Chry} for the construction loans,
and encourages \Gls{Hwel} to take on the \Gls{Fool}'s contract, since it comes with a sizable
payout. Leaving \Gls{Hwel} to work on the new script, \Gls{Tomjon} settles in for the night, only
to see nightmares again of the three witches brewing a fancy potion in some forest. The \Gls{Fool},
who is forced to lodge in the Fools' Guild, also wakes up when \Gls{Tomjon} does, but believes this
is simply the uncomfortable bedding keeping him awake.

\subsubsection{\Gls{Hwel} decides to accompany \Gls{Tomjon} to Lancre to watch over him}
\Gls{Tomjon} decides to tour Lancre with some of the junior artists before the theater is built,
with \Gls{Vitol} refusing to continue the conversation in order to avoid any mention of the boy's
heritage. \Gls{Tomjon} decides to sneak into \Gls{Hwel}'s room, and reads the latest draft of the
play, as the dwarf is fast asleep. The next day, \Gls{Hwel} insists on accompanying \Gls{Tomjon} to
Lancre, with \Gls{Vitol} suspecting that destiny has come to take the boy away from him.

\subsubsection{\Gls{GWea} confirms \Gls{Tomjon} departing the city to return to Lancre}
\Gls{GWea} peers into \Gls{Ogg}'s crystal ball, confident that \Gls{Tomjon} is departing
Ankh-Morpork with a group of armed companions specifically because their summoning spell worked. She
believes there can be no other reason for him to return to Lancre, and wonders if the ingredients
they substituted in the ritual might have caused issues. After \Gls{GWea} leaves the meeting,
\Gls{Magrat} confronts \Gls{Ogg} about their policy of not intervening in government.

\subsubsection{\Gls{Ogg} tells \Gls{Magrat} that intervening in affairs of state is a pragmatic
    decision}
\Gls{Ogg} starts to list the material benefits to her family that are bound to follow from helping
\Gls{Tomjon} oust \Gls{Felmet}, as \Gls{Magrat} thinks fondly about the \Gls{Fool}. She asks to
borrow the crystal ball, and \Gls{Ogg} agrees, knowing full well why she needs it. The \Gls{Fool}
starts his return journey to Lancre on a cargo boat, considering how little money he has left over,
while the people of Lancre slowly start to work out that the kingdom has been catapulted some years
into the future.

\subsubsection{\Gls{Hwel} watches \Gls{Tomjon}'s oratory fail for the first time}
\Gls{Hwel} notices that his new play is not receiving any love from the village audiences unlike all
of the older ones. When the troupe gets waylaid by some bandits, \Gls{Tomjon} starts to recite one
of his monologues at them, only to hear the faint voices of the witches. Some time later, the
chief bandit is killed by a jug of frozen milk dropping on his head from a great height, and
\Gls{Hwel} decides to call it a freak accident.

\subsubsection{The witches help the troupe escape some bandits trying to rob them}
\Gls{Wims}, a young apprentice in the troupe, gathers up the pieces of the expensive milk jug and
stores them in the prop box, as the troupe sets off again towards Lancre. The witches notice the
troupe losing their way through the mountains, with \Gls{Magrat} chastising \Gls{GWea} for the loss
of her antique milk jug.

\subsection{}
\subsubsection{\Gls{GWea} helps put \Gls{Tomjon} on the right track to Lancre}
\Gls{GWea} pretends to be an old woman gathering wood, in her attempt to help \Gls{Tomjon} and his
party on the path to Lancre. She gives him the right directions, and walks away before \Gls{Wims}
is able to remind \Gls{Tomjon} about the tradition of helping mysterious old women who offer them
good guidance.

\subsubsection{\Gls{Hwel} and the caravan reach Lancre with the help of the three witches}
\Gls{Hwel} loses patience with \Gls{Magrat} and \Gls{Ogg} when they also mysteriously show up to
guide their caravan toward Lancre. He is annoyed to see \Gls{Ogg} take the offer of meat and beer
seriously, before hopping onto the carriage to share their supper. Eventually, the caravan reaches
Lancre, with \Gls{Ogg} pointing out the palace on its high cliff, and the sweeping forests which
made up the majority of the land.

\subsubsection{\Gls{Hwel} shows his script to \Gls{Felmet} at the Palace}
\Gls{Ogg} reports to \Gls{GWea} that \Gls{Tomjon} and his troupe look like mere actors. \Gls{GWea}
is confident that the play is just a ruse to get into the Castle and close to \Gls{Felmet}.
Meanwhile, \Gls{Hwel} presents his script to \Gls{Felmet}, who is pleased with the results. He asks
for the bonus payment, and decides to take whatever the Duke offers, in order to perform the play
and get out of Lancre as soon as physically possible.

\subsubsection{The \Gls{Fool} asks \Gls{Magrat} to watch the play with him from a tower}
The \Gls{Fool} tells \Gls{Magrat} all about the timing of the play, and tells her that \Gls{Felmet}
expects the witches to gatecrash the event. He is dismayed when \Gls{Magrat} seems preoccupied by
something, and leaves without seeing the expensive fancy necklace he bought for her. The next night,
\Gls{Magrat} is stopped by the \Gls{Fool} as the other two witches enter the Castle by the servants'
entrance. He asks her to come to a guard tower, which will offer a good vantage point for the play
to be staged in the courtyard.

\subsubsection{\Gls{Tomjon} plays a fictional evil King \Gls{Verence} in the play}
\Gls{Hwel} struggles with the opening minutes of the play, as the apprentices get their lines wrong,
and mess up their costumes. \Gls{Tomjon}, who is to play the Evil King, finds the original crown of
Lancre in the prop box, which happens to be the only serviceable prop left for him to use.
\Gls{Verence} is shocked to see \Gls{Tomjon} on stage playing a fictionalized version of himself,
and recognizes the crown on the boy's head as his own.

\subsubsection{\Gls{GWea} decides to stop the play after realizing its power to influence the
    people}
\Gls{GWea} notices the magic of the theater stealing over the audience, as \Gls{Tomjon} launches
into his first speech. She realizes how effective the play is going to be in rehabilitating
\Gls{Felmet}, and in ruining the social status of the witches. As the play breaks for the second
act, she decides to drag \Gls{Ogg} out of the audience to deal with \Gls{Felmet}, who is smiling at
her in triumph.

\subsubsection{\Gls{Felmet}'s personal guard capture the three actors playing the witches}
\Gls{Tomjon} wonders if the play is trying to rewrite itself as it is being performed, as he wanders
the castle grounds during the intermission. He feels a sudden cold breeze rustle through his
clothing in the warm summer afternoon, and runs back to the stage afraid of some supernatural
entity haunting him. Meanwhile, \Gls{Felmet}'s guard captain arrests the three novice actors who
are still wearing witch costumes, since has no idea of theater as an art form.

\subsubsection{The three witches are pushed onto the stage to play their parts by \Gls{Hwel}}
As the three witches sit backstage discussing the script for the play, \Gls{GWea} suggests altering
the lines so that they are portrayed more favourably. \Gls{Hwel} finds them, and pushes them next
to the stage, believing them to be the novice actors tasked with playing the witches' roles.
\Gls{GWea} decides to play along, as \Gls{Hwel}'s shouted demand for some thunder to start the play
is answered by a real bolt of lightning hitting the castle.

\subsubsection{\Gls{Death} takes the place of the actor lined up to play him}
\Gls{Hwel} is angry at the repeated interruptions by \Gls{GWea} as \Gls{Tomjon} delivers his speech,
until she finishes her spell, and forces entirely new dialogue to come from the mouths of the
actors. The play now shows \Gls{Felmet} and his wife planning to murder \Gls{Verence}, and
\Gls{Death} himself takes the place of the actor who is supposed to play him. He struggles to get
through his lines, with \Gls{Tomjon} helping him.

\subsubsection{\Gls{Felmet} goes insane when the play goes off the rails}
\Gls{Felmet} loses control of his mind, and starts to rant about the night of \Gls{Verence}'s
murder. He inadvertently implicates himself and his wife, with the ghost of \Gls{Verence} possessing
\Gls{Tomjon} to accuse him of regicide. The \Gls{Fool} also chimes in with an eyewitness account of
the murder, stating that he was there in a corner of the Great Hall on the night of the killing.
\Gls{Felmet} then stabs everyone on stage with a prop dagger, and wanders off, believing that he
has silenced all the witnesses to his crimes.

\subsubsection{\Gls{Felmet} dies after wandering through the castle, looking forward to haunting
    the Castle as a ghost}
\Gls{GWea} stops \Gls{LFel} from interrupting the grand reveal that \Gls{Tomjon} is the heir to
Lancre, and \Gls{Ogg} simply knocks out the duchess when she continues to scream at them. The guards
decide to take the side of the witches, fully believing in the propaganda spread by \Gls{LFel} about
their wicked powers of polymorphing. The duke throws himself off the Castle walls into the
Lancre river, and \Gls{Death} is pleased to finally reap his soul after the long wait.

\subsubsection{\Gls{Tomjon} hopes to avoid his destiny as the King of Lancre}
\Gls{Tomjon} thinks about the prospect of giving up his acting career if he accepts the throne of
Lancre, and looks around desperately for someone to take his place. He spots \Gls{Magrat} staring
at him, and talking animatedly to \Gls{GWea} while staring back and forth at him and the \Gls{Fool}.
\Gls{GWea} declares a while later that the coronation will be held the next day, and dismisses the
elite of Lancre who had been invited by \Gls{Felmet} to the play.

\subsubsection{\Gls{Tomjon} is relieved to see \Gls{Magrat} bringing the \Gls{Fool} to the
    coronation ceremony to declare him the second heir to \Gls{Verence}}
\Gls{Tomjon} refuses to be the King, when the ancient Crown of Lancre is presented to him by the
mayor of the town. \Gls{Hwel} tells him that the only acceptable escape is to appoint a sibling as
King, and \Gls{Magrat} drags the \Gls{Fool} onto the stage just as \Gls{Tomjon} wonders where he
can find an emergency brother or sister.

\subsubsection{\Gls{GWea} and \Gls{Ogg} try to console \Gls{Magrat} after the coronation of the
    \Gls{Fool}}
A month later, \Gls{GWea} and \Gls{Ogg} recall the coronation ceremony fondly at their coven
meeting, as \Gls{Magrat} bemoans how little time \Gls{VerSec} has for her. In a neighbouring town,
\Gls{Hwel} counts the substantial gold reward given to them by \Gls{VerSec}, as \Gls{Tomjon} looks
forward to expanding the theater in Ankh-Morpork.

\subsubsection{\Gls{VerSec} waits for \Gls{Magrat} to return to her cottage}
\Gls{VerSec} goes to \Gls{Magrat}'s cottage with some gifts, and falls asleep waiting for her to
return. He has his jester's outfit returned to the Guild in Ankh-Morpork, to symbolize his
resignation as a fool. \Gls{LFel} breaks out of her prison, and runs into the forest, only to be
confronted by another gathering of the animals.

\subsubsection{\Gls{Magrat} is told that the \Gls{Fool} and \Gls{Tomjon} were both born to someone
    other than \Gls{Verence}}
\Gls{Magrat} is horrified to learn that \Gls{Tomjon} and \Gls{VerSec} are indeed half-brothers, but
their father is not King \Gls{Verence}. She realizes that the appearance of propriety is more
important to the commoners than any underlying truth, as they disperse for the month after their
coven meeting.